### 2014-05-19 article.tex
Author order isn't set

 %\documentclass[wcp,gray]{jmlr} % test grayscale version
\documentclass[wcp]{jmlr}

 % The following packages will be automatically loaded:
 % amsmath, amssymb, natbib, graphicx, url, algorithm2e

 %\usepackage{rotating}% for sideways figures and tables
\usepackage{longtable}% for long tables

 % The booktabs package is used by this sample document
 % (it provides \toprule, \midrule and \bottomrule).
 % Remove the next line if you don't require it.
\usepackage{booktabs}
 % The siunitx package is used by this sample document
 % to align numbers in a column by their decimal point.
 % Remove the next line if you don't require it.
\usepackage[load-configurations=version-1]{siunitx} % newer version
 %\usepackage{siunitx}
\usepackage[utf8]{inputenc}

 % The following command is just for this sample document:
\newcommand{\cs}[1]{\texttt{\char`\\#1}}

% % Define an unnumbered theorem just for this sample document:
%\theorembodyfont{\upshape}
%\theoremheaderfont{\scshape}
%\theorempostheader{:}
%\theoremsep{\newline}
%\newtheorem*{note}{Note}

 % change the arguments, as appropriate, in the following:
\jmlrvolume{1}
\jmlryear{2010}
\jmlrworkshop{Neural Connectomics Workshop}

\title[Connectomics challenge]{Inferring Neural Networks from Imaging Using Partial Correlation and Sample Weighting.}

 % Use \Name{Author Name} to specify the name.
 % If the surname contains spaces, enclose the surname
 % in braces, e.g. \Name{John {Smith Jones}} similarly
 % if the name has a "von" part, e.g \Name{Jane {de Winter}}.
 % If the first letter in the forenames is a diacritic
 % enclose the diacritic in braces, e.g. \Name{{\'E}louise Smith}

 % Two authors with the same address
%  \author{\Name{Author Name1\nametag{\thanks{with a note}}} \Email{abc@sample.com}\and
%   \Name{Author Name2} \Email{xyz@sample.com}\\
%   \addr Address}

 % Three or more authors with the same address:
 \author{}

 % Authors with different addresses:
 % \author{\Name{Author Name1} \Email{abc@sample.com}\\
 % \addr Address 1
 % \AND
 % \Name{Author Name2} \Email{xyz@sample.com}\\
 % \addr Address 2
 %}

\editor{Editor's name}
 % \editors{List of editors' names}

\begin{document}

\maketitle

\begin{abstract}
This is the abstract for this article.
\end{abstract}
\begin{keywords}
List of keywords
\end{keywords}
\cite{*}
\section{Introduction}
\label{sec:intro}
\section{Motivation \& objectives}
\section{Winning method}
\section{Results}
\section{Discussion on the evaluation metric}
\section{Comparison with other methods}

\bibliography{jmlr-sample}

\appendix

\section{First Appendix}\label{apd:first}

This is the first appendix.

\end{document}

### 2014-05-20 article.tex
Re-work table of content
First bg and issue

@@
 \end{abstract}
+
 \begin{keywords}
@@
 \end{keywords}
-\cite{*}
-\section{Introduction}
-\label{sec:intro}
-\section{Motivation \& objectives}
-\section{Winning method}
-\section{Results}
-\section{Discussion on the evaluation metric}
-\section{Comparison with other methods}
 
-\bibliography{jmlr-sample}
+\section{Introduction}\label{sec:intro}
 
-\appendix
+% BG : brain, complex organ
 
-\section{First Appendix}\label{apd:first}
+Understanding how the brain works is a key to understand and to treat
+brain pathologies and disorders such as Parkinson's disease, epilepsy.
+Retrieving the connectomes, neurons connectivity map, will shed new lights on
+the anatomical and functional connectivity of the brain.
+The human brain is a complex biological organ, which is formed by 100
+billions of neurons with 7000 synaptic connections on average. Inferring the
+neuron connectivity network through dissection would be an impossible
+and daunting task.
 
-This is the first appendix.
+% Issue : we have data, but need to have to infer the connectome
+Cutting edge optical devices (TODO CITE) allows to track simultaneously
+the neural activity of thousands of neurons through the fluorescent
+calcium indicator. From those imaging signals, the following inverse problem
+is set: inferring the network connectivity from the chemical signals.
+
+\section{Method}
+
+\section{Empirical experiments}
+\subsection{Datasets}
+\subsection{Metrics}
+\subsection{Data filtering}
+\subsection{Signal distribution}
+\subsection{ROC AUC results}
+\subsection{AUPRC}
+
+\section{Conclusion}
+
+\bibliography{references}
 

### 2014-05-20 article.tex
First solution paragraph

@@
 
-\title[Connectomics challenge]{Inferring Neural Networks from Imaging Using Partial Correlation and Sample Weighting.}
+\title[Connectomics challenge]{Inferring neural networks from imaging using
+                               partial correlation and sample weighting}
 
@@
 
+% Solution
+In this paper, we describe a simple and a theoretically grounded approach
+based on partial correlation to infer the neural connectivity network.
+This is also the winning method of the Connectomics challenge.
+
 \section{Method}

### 2014-05-20 article.tex
wording

@@
 
-\title[Connectomics challenge]{Inferring neural networks from imaging using
-                               partial correlation and sample weighting}
+\title[Connectomics challenge]{Inferring neural networks from fluorescent
+                               calcium imaging using partial correlation and
+                               sample weighting}
 
@@
 the neural activity of thousands of neurons through the fluorescent
-calcium indicator. From those imaging signals, the following inverse problem
-is set: inferring the network connectivity from the chemical signals.
+calcium indicator. The neuron connectivity network could be inferred
+from those neuron activity signals.
 

### 2014-05-20 article.tex
Pointer for writing
Add some notation
wording

@@
 % BG : brain, complex organ
-
 Understanding how the brain works is a key to understand and to treat
@@
 % Issue : we have data, but need to have to infer the connectome
+% TODO Shed light on the difficulty of the inverse problem:
+% noise, time scale (optical imaging speed vs neuron speed), decay of
+% fluorescent signal.
 Cutting edge optical devices (TODO CITE) allows to track simultaneously
@@
 \section{Method}
+
+% Introduce notation + goal in mathematical score
+Given $X \in \mathcal{R}^{n \times p}$  a set of $p$ time series of fluorescent
+calcium concentration of size $n$ from $p$ neurons, the goal is to infer the
+connectivity network $y \in \left\{0, 1\right\}^{p \times p}$ where
+non zero values indicate that the neuron $i$ have an outward connection to
+the neuron $j$.
+
+% Introduce partial correlation
+% Introduce directivity
+% Introduce filtering
 

### 2014-05-22 article.tex
add todo
problem definition + partial correlation + filtering

--- 2014-05-20 article.tex
@@
 \documentclass[wcp]{jmlr}
+
+%% Personnal package
+\usepackage{enumerate}
 
@@
  % Three or more authors with the same address:
- \author{}
+ \author{Todo authors}
 
@@
 \begin{abstract}
-This is the abstract for this article.
+Understanding how the brain works is a key to understand and to treat
+brain pathologies and disorders such as Parkinson's disease, epilepsy.
+Retrieving the connectomes, neurons connectivity map, will shed new lights on
+the anatomical and functional connectivity of the brain.
+The connectomics challenge
+
 \end{abstract}
@@
 % Issue : we have data, but need to have to infer the connectome
-Cutting edge optical devices (TODO CITE) allows to track simultaneously
+% TODO Shed light on the difficulty of the inverse problem:
+% noise, time scale (optical imaging speed vs neuron speed), decay of
+% fluorescent signal.
+Cutting edge optical devices [todo cite] allows to track simultaneously
 the neural activity of thousands of neurons through the fluorescent
@@
 
+The neural connectivity inference consists in highlighting, from observational data, direct relationships between neurons.
+One way to emphasize the connections between neurons is to represent them by a (un)directed graph with $p$ nodes, where each node represents a neuron, and an edge $e_{ij}$ which represents a direct link from neuron  $i$ to neuron $j$.
+If the graph is undirected, then $e_{ij}$ is equal to $e_{ji}$  for all $i,j$.
+
 % Solution
@@
 based on partial correlation to infer the neural connectivity network.
-This is also the winning method of the Connectomics challenge.
+This is also the winning method of the Connectomics challenge [todo cite].
 
@@
 
+\paragraph{Problem definition\\}
+
+% Introduce notation + goal in mathematical score
+% TODO check convention for y_{ij}
+Formally, the challenge problem may be formulated by the following statement : 
+\textit{Given $X \in \mathcal{R}^{n \times p}$  a set of $p$ time series of fluorescent
+calcium concentration of size $n$ from $p$ neurons, the goal is to infer the
+connectivity network $y \in \left\{0, 1\right\}^{p \times p}$ where
+non zero values indicate that the neuron $i$ have an outward connection to
+the neuron $j$.}
+
+The challenge was stated as an unsupervised learning problem.
+The particularity of unsupervised inference is the network recovery solely based on observational data.
+Other approaches have been considered to infer biochemical networks, e.g.
+gene regulatory network, such as supervised learning [todo cite] or transfer learning [todo cite], but these learning processes require, as starting point, a partial knowledge of the target network or known networks similar to the unknown one.
+
+% Introduce partial correlation
+\paragraph{Partial correlation\\}
+
+A common association measure is the Pearson correlation coefficient. 
+\begin{align}
+\rho_{ij} = \dfrac{cov(I,J)}{\sigma_I \sigma_J}
+\end{align}
+Even if \textit{correlation does not imply causation} [todo cite], it may give an insight on the underlying connectivity network.
+Nevertheless, the main challenge in inferring a network is to distinguish direct from indirect interactions [de la Fuente et al., 2004].
+While the classical correlation coefficient characterize both direct and indirect interactions, the partial correlation coefficient quantifies association between variables conditionally on one or several other variables (the number of variables considered being the order of the partial correlation coefficient).
+[Shipley, 2002] suggests to consider correlation coefficients of all possible orders, i.e.
+conditioned on every subsets of the set of $p-2$ other variables, in order to take into account multiple indirect paths between a given pair of variables.
+An obvious limitation to calculate high-order coefficient is the number of samples in conditioned data sets.
+Considering the large number of samples at our disposal in the connectomics challenge, we only consider the highest order of partial correlation coefficient.
+We thus try to estimate partial correlation of order $p-2$ $\rho_{ij | \mathcal{V}^{-i,j}}$.
+A way to find these coefficient [todo cite?] is to take the inverse of the covariance matrix to get the partial correlation matrix of order $p-2$, also known as the precision matrix [todo cite] .
+
+% Introduce directivity
+\paragraph{Directivity}
+
+% Introduce filtering
+\paragraph{Filtering\\}
+
+The filtering process is made of three main parts:
+
+\begin{enumerate}[i.]
+\item A low-pass filter: we consider four shapes of local averaging, 
+\item A high pass filter : we apply the asymmetric discrete derivative,
+\item A non-linear filter: we re-weight samples depending on the current activity of the systems in order to favour the association measure when directly connected neurons are firing together, while artificially reducing the association measure in case of extreme network activity, i.e.
+high when a network firing is happening and low when no neuron is active.
+\end{enumerate}
+
 \section{Empirical experiments}
 \subsection{Datasets}
+
+\paragraph{Improvement of each stage of our approach\\}
+\paragraph{Comparison with other methods\\}
+
 \subsection{Metrics}

### 2014-05-22 article.tex
correlation does not imply causation

@@
 Considering the large number of samples at our disposal in the connectomics challenge, we only consider the highest order of partial correlation coefficient.
-We thus try to estimate partial correlation of order $p-2$ $\rho_{ij | \mathcal{V}^{-i,j}}$.
+We thus try to estimate partial correlation matrix as the inferred network where a matrix element, denoted by $\rho_{ij | \mathcal{V}^{-i,j}}$, is the partial correlation coefficient of order $p-2$ between neurons $i$ and $j$.
+Note that this matrix is symmetric and thus it is impossible to determine the causal mechanism behind the interaction (I directly causes J, J directly causes I or both [de la Fuente, 2004])\footnote{Two other causal mechanisms may be implied by a non-zero partial coefficient.
+First, the pair of variables may be induced by a common (hidden) variable and second, I (respectively J) is conditionally correlated to a hidden variable affecting J (resp.
+I) [de la Fuente, 2004].} .
 A way to find these coefficient [todo cite?] is to take the inverse of the covariance matrix to get the partial correlation matrix of order $p-2$, also known as the precision matrix [todo cite] .

### 2014-05-23 article.tex
Add jmlr.cls, break long lines

@@
  % Remove the next line if you don't require it.
-\usepackage[load-configurations=version-1]{siunitx} % newer version
+%\usepackage[load-configurations=version-1]{siunitx} % newer version
  %\usepackage{siunitx}
@@
 
-The neural connectivity inference consists in highlighting, from observational data, direct relationships between neurons.
-One way to emphasize the connections between neurons is to represent them by a (un)directed graph with $p$ nodes, where each node represents a neuron, and an edge $e_{ij}$ which represents a direct link from neuron  $i$ to neuron $j$.
-If the graph is undirected, then $e_{ij}$ is equal to $e_{ji}$  for all $i,j$.
+The neural connectivity inference consists in highlighting, from observational
+data, direct relationships between neurons. One way to emphasize the
+connections between neurons is to represent them by a (un)directed graph with
+$p$ nodes, where each node represents a neuron, and an edge $e_{ij}$ which
+represents a direct link from neuron  $i$ to neuron $j$. If the graph is
+undirected, then $e_{ij}$ is equal to $e_{ji}$  for all $i,j$.
 
@@
 
-The challenge was stated as an unsupervised learning problem.
-The particularity of unsupervised inference is the network recovery solely based on observational data.
-Other approaches have been considered to infer biochemical networks, e.g.
-gene regulatory network, such as supervised learning [todo cite] or transfer learning [todo cite], but these learning processes require, as starting point, a partial knowledge of the target network or known networks similar to the unknown one.
+The challenge was stated as an unsupervised learning problem. The particularity
+of unsupervised inference is the network recovery solely based on observational
+data. Other approaches have been considered to infer biochemical networks, e.g.
+gene regulatory network, such as supervised learning [todo cite] or transfer
+learning [todo cite], but these learning processes require, as starting point,
+a partial knowledge of the target network or known networks similar to the
+unknown one.
 
@@
 \end{align}
-Even if \textit{correlation does not imply causation} [todo cite], it may give an insight on the underlying connectivity network.
-Nevertheless, the main challenge in inferring a network is to distinguish direct from indirect interactions [de la Fuente et al., 2004].
-While the classical correlation coefficient characterize both direct and indirect interactions, the partial correlation coefficient quantifies association between variables conditionally on one or several other variables (the number of variables considered being the order of the partial correlation coefficient).
-[Shipley, 2002] suggests to consider correlation coefficients of all possible orders, i.e.
-conditioned on every subsets of the set of $p-2$ other variables, in order to take into account multiple indirect paths between a given pair of variables.
-An obvious limitation to calculate high-order coefficient is the number of samples in conditioned data sets.
-Considering the large number of samples at our disposal in the connectomics challenge, we only consider the highest order of partial correlation coefficient.
-We thus try to estimate partial correlation matrix as the inferred network where a matrix element, denoted by $\rho_{ij | \mathcal{V}^{-i,j}}$, is the partial correlation coefficient of order $p-2$ between neurons $i$ and $j$.
-Note that this matrix is symmetric and thus it is impossible to determine the causal mechanism behind the interaction (I directly causes J, J directly causes I or both [de la Fuente, 2004])\footnote{Two other causal mechanisms may be implied by a non-zero partial coefficient.
-First, the pair of variables may be induced by a common (hidden) variable and second, I (respectively J) is conditionally correlated to a hidden variable affecting J (resp.
-I) [de la Fuente, 2004].} .
-A way to find these coefficient [todo cite?] is to take the inverse of the covariance matrix to get the partial correlation matrix of order $p-2$, also known as the precision matrix [todo cite] .
+
+Even if \textit{correlation does not imply causation} [todo cite], it may give
+an insight on the underlying connectivity network. Nevertheless, the main
+challenge in inferring a network is to distinguish direct from indirect
+interactions [de la Fuente et al., 2004]. While the classical correlation
+coefficient characterize both direct and indirect interactions, the partial
+correlation coefficient quantifies association between variables conditionally
+on one or several other variables (the number of variables considered being the
+order of the partial correlation coefficient). [Shipley, 2002] suggests to
+consider correlation coefficients of all possible orders, i.e. conditioned on
+every subsets of the set of $p-2$ other variables, in order to take into
+account multiple indirect paths between a given pair of variables.  An obvious
+limitation to calculate high-order coefficient is the number of samples in
+conditioned data sets. Considering the large number of samples at our disposal
+in the connectomics challenge, we only consider the highest order of partial
+correlation coefficient. We thus try to estimate partial correlation matrix as
+the inferred network where a matrix element, denoted by $\rho_{ij |
+\mathcal{V}^{-i,j}}$, is the partial correlation coefficient of order $p-2$
+between neurons $i$ and $j$. Note that this matrix is symmetric and thus it is
+impossible to determine the causal mechanism behind the interaction (I directly
+causes J, J directly causes I or both [de la Fuente, 2004])\footnote{Two other
+causal mechanisms may be implied by a non-zero partial coefficient. First, the
+pair of variables may be induced by a common (hidden) variable and second, I
+(respectively J) is conditionally correlated to a hidden variable affecting J
+(resp. I) [de la Fuente, 2004].} . A way to find these coefficient [todo cite?]
+is to take the inverse of the covariance matrix to get the partial correlation
+matrix of order $p-2$, also known as the precision matrix [todo cite] .
 
@@
 \item A high pass filter : we apply the asymmetric discrete derivative,
-\item A non-linear filter: we re-weight samples depending on the current activity of the systems in order to favour the association measure when directly connected neurons are firing together, while artificially reducing the association measure in case of extreme network activity, i.e.
+\item A non-linear filter: we re-weight samples depending on the current
+    activity of the systems in order to favour the association measure when
+    directly connected neurons are     firing together, while artificially
+    reducing the association measure in case of extreme network activity, i.e.
     high when a network firing is happening and low when no neuron is active.

### 2014-05-23 article.tex
empty tabs

--- 2014-05-22 article.tex
@@
 \paragraph{Improvement of each stage of our approach\\}
+
+\begin{table}[h!]
+\begin{tabular}{|c|c||c|c|c|c|c|c|} \hline
+\# & Stage & normal-1 & normal-2 & normal-3 & normal-4 & normal-5 & normal-6 \\ \hline
+1 & Inverse correlation & & & & &  &  \\ \hline
+2 & Pre-processing & & & & &  &  \\ \hline
+3 & PCA & & & & &  &  \\ \hline
+4 & Weighting & & & & &  &  \\ \hline
+5 & Averaging & & & & &  &  \\ \hline
+
+\end{tabular}
+\end{table}
+
+Note that we choose the \textit{best} threshold for stages 1 to 4.
+
 \paragraph{Comparison with other methods\\}
+\begin{table}[h!]
+\begin{tabular}{|c|c||c|c|c|c|c|c|} \hline
+\# & Stage & normal-1 & normal-2 & normal-3 & normal-4 & normal-5 & normal-6 \\ \hline
+1 & Inverse correlation & & & & &  &  \\ \hline
+2 & Correlation & & & & &  &  \\ \hline
+3 & GENIE3 & & & & &  &  \\ \hline
+4 & GTE & & & & &  &  \\ \hline
 
+\end{tabular}
+\end{table}
 \subsection{Metrics}

### 2014-05-23 article.tex
tabs

--- 2014-05-23 article.tex
@@
 
+\subsection{Metrics}
+\subsection{Data filtering}
+\subsection{Signal distribution}
+\subsection{ROC AUC results}
 \paragraph{Improvement of each stage of our approach\\}
@@
 \begin{tabular}{|c|c||c|c|c|c|c|c|} \hline
-\# & Stage & normal-1 & normal-2 & normal-3 & normal-4 & normal-5 & normal-6 \\ \hline
-1 & Inverse correlation & & & & &  &  \\ \hline
-2 & Pre-processing & & & & &  &  \\ \hline
-3 & PCA & & & & &  &  \\ \hline
-4 & Weighting & & & & &  &  \\ \hline
-5 & Averaging & & & & &  &  \\ \hline
+\# & Stage & normal-1 & normal-2 & normal-3 & normal-4 \\ \hline
+1 & Inverse correlation & & & & \\ \hline
+2 & Pre-processing & & & &\\ \hline
+3 & PCA & & & &  \\ \hline
+4 & Weighting & & & &  \\ \hline
+5 & Averaging & & & &  \\ \hline
 
@@
 Note that we choose the \textit{best} threshold for stages 1 to 4. 
+\paragraph{Comparison with other methods\\}
 
-\paragraph{Comparison with other methods\\}
 \begin{table}[h!]
-\begin{tabular}{|c|c||c|c|c|c|c|c|} \hline
-\# & Stage & normal-1 & normal-2 & normal-3 & normal-4 & normal-5 & normal-6 \\ \hline
-1 & Inverse correlation & & & & &  &  \\ \hline
-2 & Correlation & & & & &  &  \\ \hline
-3 & GENIE3 & & & & &  &  \\ \hline
-4 & GTE & & & & &  &  \\ \hline
+\begin{tabular}{|c|c||c|c|c|c|} \hline
+\# & Stage & normal-1 & normal-2 & normal-3 & normal-4 \\ \hline
+1 & Inverse correlation & & & &\\ \hline
+2 & Correlation & & & &\\ \hline
+3 & GENIE3 & & & & \\ \hline
+4 & GTE & & & & \\ \hline
 
@@
 \end{table}
-\subsection{Metrics}
-\subsection{Data filtering}
-\subsection{Signal distribution}
-\subsection{ROC AUC results}
 \subsection{AUPRC}

### 2014-05-28 article.tex
Break line after 80 char
remove duplicate
add some defect of optical devices

@@
 neuron connectivity network through dissection would be an impossible
-and daunting task.
+and a daunting task.
 
 % Issue : we have data, but need to have to infer the connectome
-% TODO Shed light on the difficulty of the inverse problem:
-% noise, time scale (optical imaging speed vs neuron speed), decay of
-% fluorescent signal.
 Cutting edge optical devices [todo cite] allows to track simultaneously
 the neural activity of thousands of neurons through the fluorescent
-calcium indicator. The neuron connectivity network could be inferred
-from those neuron activity signals.
-
-The neural connectivity inference consists in highlighting, from observational data, direct relationships between neurons.
-One way to emphasize the connections between neurons is to represent them by a (un)directed graph with $p$ nodes, where each node represents a neuron, and an edge $e_{ij}$ which represents a direct link from neuron  $i$ to neuron $j$.
-If the graph is undirected, then $e_{ij}$ is equal to $e_{ji}$  for all $i,j$.
+calcium indicator. Those devices have however a sampling rate smaller
+than the neuron firing speed and takes only two dimensional image, which may lead
+to superpose the activity of different neurons. Furthermore, the
+decay of the fluorescent calcium signal is slow compare to its rise.
+The neural connectivity inference consists in highlighting, from observational
+data, direct relationships between neurons. One way to emphasize the
+connections between neurons is to represent them by a (un)directed graph with
+$p$ nodes, where each node represents a neuron, and an edge $y_{ij}$ which
+represents a direct link from neuron  $i$ to neuron $j$. If the graph is
+undirected, then $y_{ij}$ is equal to $y_{ji}$  for all $i,j$.
 
@@
 
-The challenge was stated as an unsupervised learning problem.
-The particularity of unsupervised inference is the network recovery solely based on observational data.
-Other approaches have been considered to infer biochemical networks, e.g.
-gene regulatory network, such as supervised learning [todo cite] or transfer learning [todo cite], but these learning processes require, as starting point, a partial knowledge of the target network or known networks similar to the unknown one.
+The challenge was stated as an unsupervised learning problem. The particularity
+of unsupervised inference is the network recovery solely based on
+observational data. Other approaches have been considered to infer biochemical
+networks, e.g. gene regulatory network, such as supervised learning [todo cite]
+or transfer learning [todo cite], but these learning processes require, as
+starting point, a partial knowledge of the target network or known networks
+similar to the unknown one.
 
@@
 \end{align}
-Even if \textit{correlation does not imply causation} [todo cite], it may give an insight on the underlying connectivity network.
-Nevertheless, the main challenge in inferring a network is to distinguish direct from indirect interactions [de la Fuente et al., 2004].
-While the classical correlation coefficient characterize both direct and indirect interactions, the partial correlation coefficient quantifies association between variables conditionally on one or several other variables (the number of variables considered being the order of the partial correlation coefficient).
-[Shipley, 2002] suggests to consider correlation coefficients of all possible orders, i.e.
-conditioned on every subsets of the set of $p-2$ other variables, in order to take into account multiple indirect paths between a given pair of variables.
-An obvious limitation to calculate high-order coefficient is the number of samples in conditioned data sets.
-Considering the large number of samples at our disposal in the connectomics challenge, we only consider the highest order of partial correlation coefficient.
-We thus try to estimate partial correlation matrix as the inferred network where a matrix element, denoted by $\rho_{ij | \mathcal{V}^{-i,j}}$, is the partial correlation coefficient of order $p-2$ between neurons $i$ and $j$.
-Note that this matrix is symmetric and thus it is impossible to determine the causal mechanism behind the interaction (I directly causes J, J directly causes I or both [de la Fuente, 2004])\footnote{Two other causal mechanisms may be implied by a non-zero partial coefficient.
-First, the pair of variables may be induced by a common (hidden) variable and second, I (respectively J) is conditionally correlated to a hidden variable affecting J (resp.
-I) [de la Fuente, 2004].} .
-A way to find these coefficient [todo cite?] is to take the inverse of the covariance matrix to get the partial correlation matrix of order $p-2$, also known as the precision matrix [todo cite] .
+Even if \textit{correlation does not imply causation} [todo cite], it may give
+an insight on the underlying connectivity network. Nevertheless, the main
+challenge in inferring a network is to distinguish direct from indirect
+interactions [de la Fuente et al., 2004]. While the classical correlation
+coefficient characterize both direct and indirect interactions, the partial
+correlation coefficient quantifies association between variables conditionally
+on one or several other variables (the number of variables considered being
+the order of the partial correlation coefficient). [Shipley, 2002] suggests to
+consider correlation coefficients of all possible orders, i.e. conditioned
+on every subsets of the set of $p-2$ other variables, in order to take into
+account multiple indirect paths between a given pair of variables.  An obvious
+limitation to calculate high-order coefficient is the number of samples in
+conditioned data sets. Considering the large number of samples at our disposal
+in the connectomics challenge, we only consider the highest order of partial
+correlation coefficient. We thus try to estimate partial correlation matrix as
+the inferred network where a matrix element, denoted by
+$\rho_{ij | \mathcal{V}^{-i,j}}$, is the partial correlation coefficient of
+order $p-2$ between neurons $i$ and $j$. Note that this matrix is symmetric
+and thus it is impossible to determine the causal mechanism behind the
+interaction (I directly causes J, J directly causes I or both
+[de la Fuente, 2004])\footnote{Two other causal mechanisms may be implied
+by a non-zero partial coefficient. First, the pair of variables may be induced
+by a common (hidden) variable and second, I (respectively J) is conditionally
+correlated to a hidden variable affecting J (resp. I) [de la Fuente, 2004].} .
+A way to find these coefficient [todo cite?] is to take the inverse of the
+covariance matrix to get the partial correlation matrix of order $p-2$, also
+known as the precision matrix [todo cite] .
 
@@
 \item A high pass filter : we apply the asymmetric discrete derivative,
-\item A non-linear filter: we re-weight samples depending on the current activity of the systems in order to favour the association measure when directly connected neurons are firing together, while artificially reducing the association measure in case of extreme network activity, i.e.
-high when a network firing is happening and low when no neuron is active.
+\item A non-linear filter: we re-weight samples depending on the current
+      activity of the systems in order to favour the association measure when
+      directly connected neurons are firing together, while artificially
+      reducing the association measure in case of extreme network activity,
+      i.e. high when a network firing is happening and low when no neuron is
+      active.
 \end{enumerate}

### 2014-05-28 article.tex
wording

@@
 Understanding how the brain works is a key to understand and to treat
-brain pathologies and disorders such as Parkinson's disease, epilepsy.
+brain pathologies and disorders such as Parkinson's disease and epilepsy.
 Retrieving the connectomes, neurons connectivity map, will shed new lights on
-the anatomical and functional connectivity of the brain.
-The human brain is a complex biological organ, which is formed by 100
+the anatomical and functional connectivity of the brain. However,
+the human brain is a complex biological organ, which is formed by 100
 billions of neurons with 7000 synaptic connections on average. Inferring the
@@
 
-% Issue : we have data, but need to have to infer the connectome
 Cutting edge optical devices [todo cite] allows to track simultaneously
 the neural activity of thousands of neurons through the fluorescent
-calcium indicator. Those devices have however a sampling rate smaller
-than the neuron firing speed and takes only two dimensional image, which may lead
-to superpose the activity of different neurons. Furthermore, the
-decay of the fluorescent calcium signal is slow compare to its rise.
-The neural connectivity inference consists in highlighting, from observational
-data, direct relationships between neurons. One way to emphasize the
-connections between neurons is to represent them by a (un)directed graph with
-$p$ nodes, where each node represents a neuron, and an edge $y_{ij}$ which
-represents a direct link from neuron  $i$ to neuron $j$. If the graph is
-undirected, then $y_{ij}$ is equal to $y_{ji}$  for all $i,j$.
+calcium indicator.
+From those observational data, the neural connectivity inference consists in
+highlighting direct relationships between neurons. However, those imaging
+systems have a sampling rate smaller than the neuron firing speed and are
+limited only two dimensional image, which may lead to superpose the activity
+of different neurons. Furthermore, the decay of the fluorescent calcium signal
+is slow compare to its rise.
+
+Since only observational data are available, the network recovery is set as an
+unsupervised learning problem. Whenever a partial knowledge of the target
+network or known networks highly similar to the unknown one is available,
+supervised learning [todo cite] and transfer learning  [todo cite] based
+approach could be considered to infer networks.
 
@@
 
+One way to emphasize the connections between neurons is to represent them by a
+(un)directed graph with $p$ nodes: each node represents a neuron, and each
+edge $y_{ij}$ represents a direct link from neuron  $i$ to neuron $j$. If the
+graph is undirected, then $y_{ij}$ is equal to $y_{ji}$  for all $i,j$.
+
 % Introduce notation + goal in mathematical score
@@
 
-The challenge was stated as an unsupervised learning problem. The particularity
-of unsupervised inference is the network recovery solely based on
-observational data. Other approaches have been considered to infer biochemical
-networks, e.g. gene regulatory network, such as supervised learning [todo cite]
-or transfer learning [todo cite], but these learning processes require, as
-starting point, a partial knowledge of the target network or known networks
-similar to the unknown one.
+From a probabilistic point of view, the newtwork
+
+% Plan:
+% introduce the notion of dependance/independance
+% Introduce correlation => Estimator of I(X; Y)
+%                       => Issue indirect effect
+% Introduce partial correlation => Estimator of I(X; Y | Z)
+%                               => Symmetric measure
+% Introduce a custom solution to make the Y matrix assymetric
+% Introduce Filtering
 

### 2014-05-28 article.tex
wording
Add the notion of independance

@@
 
+% Introduce notation + goal in mathematical score
+% TODO check convention for y_{ij}
 One way to emphasize the connections between neurons is to represent them by a
@@
 graph is undirected, then $y_{ij}$ is equal to $y_{ji}$  for all $i,j$.
+The unsupervised task may be formulated as:
+\textit{Given $X \in \mathcal{R}^{n \times p}$  a set of $p$ time series of
+fluorescent calcium concentration of size $n$ from $p$ neurons, the goal is to
+infer the connectivity graph $y \in \left\{0, 1\right\}^{p \times p}$.}
 
-% Introduce notation + goal in mathematical score
-% TODO check convention for y_{ij}
-Formally, the challenge problem may be formulated by the following statement :
-\textit{Given $X \in \mathcal{R}^{n \times p}$  a set of $p$ time series of fluorescent
-calcium concentration of size $n$ from $p$ neurons, the goal is to infer the
-connectivity network $y \in \left\{0, 1\right\}^{p \times p}$ where
-non zero values indicate that the neuron $i$ have an outward connection to
-the neuron $j$.}
+% introduce the notion of dependance/independance
+From a probabilistic point of view, the inference of the undirected network
+can be formulated as inferring the conditional independence between neurons
+$i$ and $j$ conditionally to all other neurons
+$i \perp j | 1,\ldots,p \backslash \left\{i, j\right\}$. Note that
+the unconditional independence $i \perp j$ between  $i$ and $j$ doesn't allow to
+infer the graph due to indirect effect. For instance if neurons $A, B, C$ have
+the connectivity graph $A \rightarrow B \rightarrow C$, then we have the
+dependence $A \not\perp C$ and the conditional independence $A \perp C | B$.
 
-From a probabilistic point of view, the newtwork
-
-% Plan:
-% introduce the notion of dependance/independance
 % Introduce correlation => Estimator of I(X; Y)

### 2014-05-30 article.tex
add todo
Reformulate probability part

@@
 
-% introduce the notion of dependance/independance
+% introduce the notion of dependence / independence
+% TODO add a more formal definition of independence.
 From a probabilistic point of view, the inference of the undirected network
-can be formulated as inferring the conditional independence between neurons
-$i$ and $j$ conditionally to all other neurons
-$i \perp j | 1,\ldots,p \backslash \left\{i, j\right\}$. Note that
-the unconditional independence $i \perp j$ between  $i$ and $j$ doesn't allow to
-infer the graph due to indirect effect. For instance if neurons $A, B, C$ have
-the connectivity graph $A \rightarrow B \rightarrow C$, then we have the
-dependence $A \not\perp C$ and the conditional independence $A \perp C | B$.
+can be formulated as inferring conditional dependences and
+independences. Each neuron signal $i$ is a random continuous variable $X_i$,
+which follows a probability density function $p_\mathcal{X_i}(x_i)$.
+Two neurons $X_i$, $X_j$ will be said conditionally independent
+$X_i \perp X_j | X_1,\ldots,X_p \backslash \left\{X_i, X_j\right\}$ to all
+others neuron if
+\begin{align*}
+&p_{X_i, X_j | X_1,\ldots,X_p \backslash \left\{X_i, X_j\right\}}
+    (x_i, x_j | x_1,\ldots,x_p \backslash \left\{x_i, x_j\right\}) \\
+=&p_{X_i | X_1,\ldots,X_p \backslash \left\{X_i, X_j\right\}}
+    (x_i | x_1,\ldots,x_p \backslash \left\{x_i, x_j\right\})
+p_{X_j | X_1,\ldots,X_p \backslash \left\{X_i, X_j\right\}}
+    (x_j | x_1,\ldots,x_p \backslash \left\{x_i, x_j\right\})
+\end{align*}
+for all real numbers $x_1,\ldots,x_p $ such that
+$p_{X_1,\ldots,X_p \backslash \left\{X_i, X_j\right\}}
+ (x_1,\ldots,x_p \backslash \left\{x_i, x_j\right\}) > 0$.
+Thus if $X_i \not\perp X_j | X_1,\ldots,X_p \backslash \left\{X_i, X_j\right\}$,
+then we have the edge $i-j$ in the undirected graph.
 

### 2014-05-30 article.tex
Introduce gaussian hypothesis

@@
 % introduce the notion of dependence / independence
-% TODO add a more formal definition of independence.
 From a probabilistic point of view, the inference of the undirected network
@@
 Two neurons $X_i$, $X_j$ will be said conditionally independent
-$X_i \perp X_j | X_1,\ldots,X_p \backslash \left\{X_i, X_j\right\}$ to all
-others neuron if
+to a set of neurons $X_1,\ldots,X_p \backslash \left\{X_i, X_j\right\}$, denoted
+by  $X_i \perp X_j | X_1,\ldots,X_p \backslash \left\{X_i, X_j\right\}$,  if
 \begin{align*}
@@
 
-% Introduce correlation => Estimator of I(X; Y)
-%                       => Issue indirect effect
+Under the hypothesis that the neurons follow a jointly Gaussian distribution
+$p_{X_1,\ldots,X_p}(x_1,\ldots,x_p) \sim \mathcal{N}(\mu; \Sigma)$
+of mean vector $\mu$ and of covariance matrix $\Sigma$, two neurons $X_i$
+and $X_j$ are independent $X_i \perp X_j$ if they have zero correlation
+coefficient and are conditionally independent to all others neurons
+$X_i \perp X_j | X_1,\ldots,X_p \backslash \left\{X_i, X_j\right\}$ if they
+have zero partial correlation coefficient. Even if \textit{independence
+does no imply causation}, it gives insight on the underlying connectivity
+network.
+
+% Introduce correlation => Estimator of I(X; Y) => Issue indirect effect
+The Pearson correlation coefficient $\rho_{ij}$ is an association measure
+and defined by
+\[
+\rho_{ij} = \frac{\Sigma_{ij}}{\sqrt{\Sigma_i \Sigma_j}}.
+\]
+
 % Introduce partial correlation => Estimator of I(X; Y | Z)
 %                               => Symmetric measure
-% Introduce a custom solution to make the Y matrix assymetric
+
+% Introduce a custom solution to make the Y matrix asymmetric
 % Introduce Filtering
@@
 
-A common association measure is the Pearson correlation coefficient.
+A common association measure is the
 \begin{align}

### 2014-05-30 article.tex
Present (partial) correlation from an independence perspective

--- 2014-05-30 article.tex
@@
 % introduce the notion of dependence / independence
-% TODO add a more formal definition of independence.
 From a probabilistic point of view, the inference of the undirected network
 can be formulated as inferring conditional dependences and
-independences. Each neuron signal $i$ is a random continuous variable $X_i$,
+independences.  Even if \textit{independence
+does no imply causation}[todo cite], it gives insight on the underlying connectivity
+network. Each neuron signal $i$ is a random continuous variable $X_i$,
 which follows a probability density function $p_\mathcal{X_i}(x_i)$.
 Two neurons $X_i$, $X_j$ will be said conditionally independent
-$X_i \perp X_j | X_1,\ldots,X_p \backslash \left\{X_i, X_j\right\}$ to all
-others neuron if
+to a set of neurons $X_1,\ldots,X_p \backslash \left\{X_i, X_j\right\}$, denoted
+by  $X_i \perp X_j | X_1,\ldots,X_p \backslash \left\{X_i, X_j\right\}$,  if
 \begin{align*}
@@
  (x_1,\ldots,x_p \backslash \left\{x_i, x_j\right\}) > 0$.
+
+Under the hypothesis that the neurons follow a jointly Gaussian distribution
+$p_{X_1,\ldots,X_p}(x_1,\ldots,x_p) \sim \mathcal{N}(\mu; \Sigma)$
+of mean vector $\mu$ and of covariance matrix $\Sigma$, two neurons $X_i$
+and $X_j$ are independent $X_i \perp X_j$ if they have zero Pearson correlation
+coefficient
+\[
+\rho_{X_iX_j} = \frac{\Sigma_{ij}}{\sqrt{\Sigma_{ii} \Sigma_{jj}}}
+\]
+and are conditionally independent to all others neurons
+$X_i \perp X_j | X_1,\ldots,X_p \backslash \left\{X_i, X_j\right\}$ if they
+have zero partial correlation coefficient
+\[
+\rho_{X_i, X_j | X_1,\ldots,X_p \backslash \left\{X_i, X_j\right\}} =
+\frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii} \Sigma^{-1}_{jj}}}.
+\]
+
+% Correlation => Issue indirect effect
+% Partial correlation => better estimate of the graph  => Symmetric measure
+
 Thus if $X_i \not\perp X_j | X_1,\ldots,X_p \backslash \left\{X_i, X_j\right\}$,
@@
 
-% Introduce correlation => Estimator of I(X; Y)
-%                       => Issue indirect effect
-% Introduce partial correlation => Estimator of I(X; Y | Z)
-%                               => Symmetric measure
-% Introduce a custom solution to make the Y matrix assymetric
+% Introduce a custom solution to make the Y matrix asymmetric
 % Introduce Filtering

### 2014-06-03 article.tex
Possible extensions
Warn about reprocical
Discuss partial correlation in term of independance and relate to the literature

@@
 
-\paragraph{Problem definition\\}
-
 % Introduce notation + goal in mathematical score
@@
 infer the connectivity graph $y \in \left\{0, 1\right\}^{p \times p}$.}
+The main challenge in the inference of the network $y$
+is to distinguish direct from indirect interactions [de la Fuente et al., 2004].
+For instance with the simple interaction graph $A \rightarrow B \rightarrow C$,
+we want to distinguish direct interactions $A \rightarrow B$ and $B \rightarrow C$
+from the indirect interaction $A \rightarrow C$.
 
@@
 does no imply causation}[todo cite], it gives insight on the underlying connectivity
-network. Each neuron signal $i$ is a random continuous variable $X_i$,
+network. For instance, the graph $A \rightarrow B \rightarrow C$ translates the
+following dependances and independances: $A \not\perp B$, $A \not\perp B | C$,
+$B \not\perp C$, $B \not\perp C | A$, but $A \perp C | B$ and  $A \not\perp C$.
+
+Each neuron signal $i$ is a random continuous variable $X_i$,
 which follows a probability density function $p_\mathcal{X_i}(x_i)$.
@@
 $p_{X_1,\ldots,X_p \backslash \left\{X_i, X_j\right\}}
- (x_1,\ldots,x_p \backslash \left\{x_i, x_j\right\}) > 0$.
+(x_1,\ldots,x_p \backslash \left\{x_i, x_j\right\}) > 0$. Note that this
+reciprocal is true only under additional hypotheses.
 
@@
 % Partial correlation => better estimate of the graph  => Symmetric measure
+While the correlation coefficient is unable to distinguish between
+direct and indirect interaction, the partial correlation coefficient
+aims to infer only direct ones through the conditioning over all the other
+variables. In previous studies [Shipley, 2002], it has been suggested
+consider correlation coefficients of all possible orders [Shipley, 2002],
+i.e. conditioned on every subsets of the set of $p-2$ other variables, in order
+to take into account multiple indirect paths between a given pair of variables.
+An obvious limitation to calculate high-order coefficient is the number of
+samples in conditioned data sets \textcolor{red}{AJ: Est ce que ce ne sera pas
+à la fois $p$ and $n$?}. Given the high number of samples $n$
+in the Connectomics challenge, we only consider the highest order of partial
+correlation coefficient.
 
-Thus if $X_i \not\perp X_j | X_1,\ldots,X_p \backslash \left\{X_i, X_j\right\}$,
-then we have the edge $i-j$ in the undirected graph.
-
-% Introduce a custom solution to make the Y matrix asymmetric
-% Introduce Filtering
-
-% Introduce partial correlation
-\paragraph{Partial correlation\\}
-
-A common association measure is the
-\begin{align}
-\rho_{ij} = \dfrac{cov(I,J)}{\sigma_I \sigma_J}
-\end{align}
-Even if \textit{correlation does not imply causation} [todo cite], it may give
-an insight on the underlying connectivity network. Nevertheless, the main
-challenge in inferring a network is to distinguish direct from indirect
-interactions [de la Fuente et al., 2004]. While the classical correlation
-coefficient characterize both direct and indirect interactions, the partial
-correlation coefficient quantifies association between variables conditionally
-on one or several other variables (the number of variables considered being
-the order of the partial correlation coefficient). [Shipley, 2002] suggests to
-consider correlation coefficients of all possible orders, i.e. conditioned
-on every subsets of the set of $p-2$ other variables, in order to take into
-account multiple indirect paths between a given pair of variables.  An obvious
-limitation to calculate high-order coefficient is the number of samples in
-conditioned data sets. Considering the large number of samples at our disposal
-in the connectomics challenge, we only consider the highest order of partial
-correlation coefficient. We thus try to estimate partial correlation matrix as
-the inferred network where a matrix element, denoted by
-$\rho_{ij | \mathcal{V}^{-i,j}}$, is the partial correlation coefficient of
-order $p-2$ between neurons $i$ and $j$. Note that this matrix is symmetric
+Note that this matrix is symmetric
 and thus it is impossible to determine the causal mechanism behind the
@@
 by a common (hidden) variable and second, I (respectively J) is conditionally
-correlated to a hidden variable affecting J (resp. I) [de la Fuente, 2004].} .
-A way to find these coefficient [todo cite?] is to take the inverse of the
-covariance matrix to get the partial correlation matrix of order $p-2$, also
-known as the precision matrix [todo cite] .
+correlated to a hidden variable affecting J (resp. I) [de la Fuente, 2004].}
+
+% Introduce a custom solution to make the Y matrix asymmetric
+% Introduce Filtering
 
 % Introduce directivity
-\paragraph{Directivity}
 
 % Introduce filtering
-\paragraph{Filtering\\}
 
@@
 
+% Possible extensions
+% partial autocorrelation function (sometimes "partial correlation function")
+% conditional independence test
+
 \bibliography{references}

### 2014-06-03 article.tex
wording

@@
 
-Note that this matrix is symmetric
-and thus it is impossible to determine the causal mechanism behind the
-interaction (I directly causes J, J directly causes I or both
-[de la Fuente, 2004])\footnote{Two other causal mechanisms may be implied
+%  Partial correlation => Symmetric measure
+Since this matrix is symmetric, it is not possible to infer the causal
+mechanism behind the interaction (I directly causes J, J directly causes I or
+both [de la Fuente, 2004]). Futhermore two other causal mechanisms may be implied
 by a non-zero partial coefficient. First, the pair of variables may be induced
 by a common (hidden) variable and second, I (respectively J) is conditionally
-correlated to a hidden variable affecting J (resp. I) [de la Fuente, 2004].}
+correlated to a hidden variable affecting J (resp. I) [de la Fuente, 2004].
 

### 2014-06-03 article.tex
typo
Start to speak about directivity

@@
 
-%  Partial correlation => Symmetric measure
-Since this matrix is symmetric, it is not possible to infer the causal
+Since the partial correlation is symmetric, it is not possible to infer the causal
 mechanism behind the interaction (I directly causes J, J directly causes I or
-both [de la Fuente, 2004]). Futhermore two other causal mechanisms may be implied
+both [de la Fuente, 2004]). Furthermore two other causal mechanisms may be implied
 by a non-zero partial coefficient. First, the pair of variables may be induced
@@
 % Introduce a custom solution to make the Y matrix asymmetric
-% Introduce Filtering
-
 % Introduce directivity
+% TODO better link
+%      add that we make the count matrix antisymmetric (count - count.T)
+%      say that we normalize and stack
+Some causal information (directivity of the links) were retrieved from the
+data by comparing activity of each couple of neurons between two subsequent
+time steps. The directivity method tries to detect variation of fluorescence
+signal of a neuron $j$ due to a neuron $i$. This method counts the number of
+times that $X_{t+1,j} - X_{t, i} \in [f_1, f_2]$ where $f_1$ and $f_2$ are
+parameters of the method.
 

### 2014-06-04 article.tex
Add todo
start to better explain directivity
Add references

@@
 The main challenge in the inference of the network $y$
-is to distinguish direct from indirect interactions [de la Fuente et al., 2004].
+is to distinguish direct from indirect interactions \cite{de2004discovery}.
 For instance with the simple interaction graph $A \rightarrow B \rightarrow C$,
@@
 aims to infer only direct ones through the conditioning over all the other
-variables. In previous studies [Shipley, 2002], it has been suggested
-consider correlation coefficients of all possible orders [Shipley, 2002],
+variables. In previous study \cite{shipley2002cause}, it has been suggested
+consider correlation coefficients of all possible orders,
 i.e. conditioned on every subsets of the set of $p-2$ other variables, in order
@@
 mechanism behind the interaction (I directly causes J, J directly causes I or
-both [de la Fuente, 2004]). Furthermore two other causal mechanisms may be implied
+both ). Furthermore two other causal mechanisms may be implied
 by a non-zero partial coefficient. First, the pair of variables may be induced
 by a common (hidden) variable and second, I (respectively J) is conditionally
-correlated to a hidden variable affecting J (resp. I) [de la Fuente, 2004].
+correlated to a hidden variable affecting J (resp. I) \cite{de2004discovery}.
 
@@
 %      say that we normalize and stack
-Some causal information (directivity of the links) were retrieved from the
+%      specify f_1 and f_2
+In the hope to improve performance, some causal information (directivity of
+the links) were added by stacking the partial correlation score matrix
+with
+
+from the
 data by comparing activity of each couple of neurons between two subsequent
 time steps. The directivity method tries to detect variation of fluorescence
-signal of a neuron $j$ due to a neuron $i$. This method counts the number of
-times that $X_{t+1,j} - X_{t, i} \in [f_1, f_2]$ where $f_1$ and $f_2$ are
-parameters of the method.
+signal of a neuron $j$ due to a neuron $i$. A connectivity score
+between the two neurons $i$ and $j$ is given by
+\[
+z_{ij} = \sum_{t=1}^n I(X_{t+1,j} - X_{t, i} \in [f_1, f_2])
+\]
+
+where $f_1$ and $f_2$ are parameters of the method and $I(\bullet)$ is the
+indicator function. Finally, a
 

### 2014-06-04 article.tex
wording

@@
 \jmlrvolume{1}
-\jmlryear{2010}
+\jmlryear{2014}
 \jmlrworkshop{Neural Connectomics Workshop}
@@
 aims to infer only direct ones through the conditioning over all the other
-variables. In previous study \cite{shipley2002cause}, it has been suggested
+variables. In previous study \cite{shipley2002cause}, it has been suggested to
 consider correlation coefficients of all possible orders,
-i.e. conditioned on every subsets of the set of $p-2$ other variables, in order
-to take into account multiple indirect paths between a given pair of variables.
-An obvious limitation to calculate high-order coefficient is the number of
-samples in conditioned data sets \textcolor{red}{AJ: Est ce que ce ne sera pas
-à la fois $p$ and $n$?}. Given the high number of samples $n$
+i.e. conditioned on every subsets of the set of $p-2$ other variables. This
+would take into account multiple indirect paths between a given pair of
+variables. An obvious limitation to estimate correctly high-order coefficients
+is the number of samples. However given the high number of samples $n$
 in the Connectomics challenge, we only consider the highest order of partial
@@
 
-Since the partial correlation is symmetric, it is not possible to infer the causal
-mechanism behind the interaction (I directly causes J, J directly causes I or
-both ). Furthermore two other causal mechanisms may be implied
-by a non-zero partial coefficient. First, the pair of variables may be induced
-by a common (hidden) variable and second, I (respectively J) is conditionally
-correlated to a hidden variable affecting J (resp. I) \cite{de2004discovery}.
+Since the partial correlation is a symmetric, the causal mechanism behind the
+interaction ($A$ directly causes $B$, $B$ directly causes $A$ or both ) can't
+be infered. Moreover, two other causal mechanisms might be implied while having
+a non-zero partial coefficient: (i) a pair of variables is induced by a
+common (hidden) variable; (ii) $A$ (respectively $B$) is conditionally
+correlated to a hidden variable affecting $B$ (resp. $A$)
+\cite{de2004discovery}.
 

### 2014-06-04 article.tex
correctly explain directivity

@@
 % Introduce directivity
-% TODO better link
-%      add that we make the count matrix antisymmetric (count - count.T)
-%      say that we normalize and stack
-%      specify f_1 and f_2
-In the hope to improve performance, some causal information (directivity of
-the links) were added by stacking the partial correlation score matrix
-with
-
-from the
-data by comparing activity of each couple of neurons between two subsequent
-time steps. The directivity method tries to detect variation of fluorescence
-signal of a neuron $j$ due to a neuron $i$. A connectivity score
-between the two neurons $i$ and $j$ is given by
+In our last submission in hope to improve performance, some causal information
+(directivity of the links) were added by stacking the partial correlation score
+matrix with an pairwise activation heuristics. This method computes an
+activation score $z_{ij}$ based the variation of fluorescence signal of a neuron
+$j$ due to a neuron $i$ over all timesteps:
 \[
-z_{ij} = \sum_{t=1}^n I(X_{t+1,j} - X_{t, i} \in [f_1, f_2])
+z_{ij} = \sum_{t=1}^n I(X_{t+1,j} - X_{t, i} \in [f_1, f_2]) -  I(X_{t+1,i} - X_{t, j} \in [f_1, f_2])
 \]
-
-where $f_1$ and $f_2$ are parameters of the method and $I(\bullet)$ is the
-indicator function. Finally, a
+where $f_1$ and $f_2$ are parameters of the method and $I$ is the
+indicator function.
 

### 2014-06-04 article.tex
some wording precision

@@
 
-\section{Method}
+\section{Network inference methodology}
 
@@
 (directivity of the links) were added by stacking the partial correlation score
-matrix with an pairwise activation heuristics. This method computes an
+matrix with an pairwise activation heuristics. This method computes an anti-symmetric
 activation score $z_{ij}$ based the variation of fluorescence signal of a neuron
@@
 % Introduce filtering
+\section{Signal filtering methodology}
 

### 2014-06-04 article.tex
Improve abstract

--- 2014-06-04 article.tex
@@
 the anatomical and functional connectivity of the brain.
-The connectomics challenge
+In the context of the Connectomics challenge, we propose a pre-processing and a simple approach in order to achieve a high performance inference of the connectivity network.
+We put in perspective our method by comparing with other inference method such as GTE [], another method proposed to infer a neural network from calcium fluorescent imaging, and Genie3 [], a tree-based approach very competitive in several gene inference challenge (i.e.
+DREAM4 and DREAM5).\\
+
+% Discussion on the metrics?
 
@@
 \begin{keywords}
-List of keywords
+Network inference - Precision matrix - GENIE3
 \end{keywords}

### 2014-06-05 article.tex
start filtering section
describe linear filters

@@
 
-% Introduce filtering
 \section{Signal filtering methodology}
 
+% Explain why we need to filter
+% TODO
+
+% Filtering methodology
+Prior inferring the network, the fluorescent calicum time series are smoothed
+using several linear and non linear filters. A low-pass filter is first applied
+for all valid value of $t$
+\[
+X^\prime_{t,i} = \sum_{l=-3}^2 a_l X_{t+l,i} \forall i
+\]
+where the $a_l$ coefficient were taken in one of the four following tuples:
+$(\left\{a_l\right\}_{l=-3}^2)=(0, 0, 1, 1, 1, 1)$,
+$(\left\{a_l\right\}_{l=-3}^2)=(0, 0, 1, 1, 1, 0)$,
+$(\left\{a_l\right\}_{l=-3}^2)=(1, 1, 1, 1, 0, 0)$ or
+$(\left\{a_l\right\}_{l=-3}^2)=(0.4, 0.8, 1, 1, 0, 0)$.
+
+The next step is to apply a high-pass filter to the signal:
+\[
+X^{\prime\prime}_{t,i} = X^{\prime}_{t,i} - X^{\prime}_{t-1,i}
+\forall i, \forall t \in \left\{2, \ldots, n\right\}
+\]
+
+5 kinds
+of filtering technique: (i) a low pass filter, (ii) a high pass filter, (iii)
+a high thresholding filter
+
 The filtering process is made of three main parts:
+
+% There are 4 filters:
+%     1/ smoothing filter (see filtering argument)
+%     2/ hard thresholding filter (see threshold argument)
+%     3/ non-linear filter: x[i] = x[i] ** 0.9
+%     4/ non-linear filter based on the neuron activations
+
+ %  X_new = np.diff(X_new, axis=0)
+ %  thresh1 = X_new < threshold * 1
+ %  thresh2 = X_new >= threshold * 1
+ %  X_new[thresh1] = 0
+ %  X_new[thresh2] = pow(X_new[thresh2], 0.9)
 

### 2014-06-05 article.tex
Explain low-pass, high-pass, hard-tresholding, power filter

--- 2014-06-04 article.tex
@@
 
-% Introduce filtering
 \section{Signal filtering methodology}
 
-The filtering process is made of three main parts:
+% Explain why we need to filter
+% TODO
+
+% Filtering methodology
+Prior inferring the network, the fluorescent calcium time series are smoothed
+using several linear and non linear filters. A low-pass filter, a high-pass
+filter and a non linear hard-thresholding based filter are
+applied for each possible time step $t$
+\begin{align}
+X^\prime_{t,i} &= \sum_{l=-3}^2 a_l X_{t+l,i} \forall i, \\
+X^{\prime\prime}_{t,i} &= X^{\prime}_{t,i} - X^{\prime}_{t-1,i} \forall i, \\
+X^{\prime\prime\prime}_{t,i} &= {X^{\prime\prime}_{t,i}}^{0.9} I(X^{\prime\prime}_{t,i} \geq f_3) \forall i,
+\end{align}
+where the $a_l$ coefficients were taken in one of the four following tuples
+$(\left\{a_l\right\}_{l=-3}^2)=(0, 0, 1, 1, 1, 1)$,
+$(\left\{a_l\right\}_{l=-3}^2)=(0, 0, 1, 1, 1, 0)$,
+$(\left\{a_l\right\}_{l=-3}^2)=(1, 1, 1, 1, 0, 0)$ or
+$(\left\{a_l\right\}_{l=-3}^2)=(0.4, 0.8, 1, 1, 0, 0)$ and $f_3$ is the minimal
+fluorescence signal .
+
+%     4/ non-linear filter based on the neuron activations
 
 \begin{enumerate}[i.]
-\item A low-pass filter: we consider four shapes of local averaging,
-\item A high pass filter : we apply the asymmetric discrete derivative,
 \item A non-linear filter: we re-weight samples depending on the current

### 2014-06-05 article.tex
wording

@@
 
-%     4/ non-linear filter based on the neuron activations
-
-\begin{enumerate}[i.]
-\item A non-linear filter: we re-weight samples depending on the current
+Then we apply a non-linear filter based on the current
 activity of the systems in order to favour the association measure when
@@
 active.
-\end{enumerate}
 

### 2014-06-05 article.tex
Add weighted base filter

@@
 \begin{align}
-X^\prime_{t,i} &= \sum_{l=-3}^2 a_l X_{t+l,i} \forall i, \\
+X^\prime_{t,i} &= \sum_{l=-3}^2 c_l X_{t+l,i} \forall i, \\
 X^{\prime\prime}_{t,i} &= X^{\prime}_{t,i} - X^{\prime}_{t-1,i} \forall i, \\
@@
 \end{align}
-where the $a_l$ coefficients were taken in one of the four following tuples
-$(\left\{a_l\right\}_{l=-3}^2)=(0, 0, 1, 1, 1, 1)$,
-$(\left\{a_l\right\}_{l=-3}^2)=(0, 0, 1, 1, 1, 0)$,
-$(\left\{a_l\right\}_{l=-3}^2)=(1, 1, 1, 1, 0, 0)$ or
-$(\left\{a_l\right\}_{l=-3}^2)=(0.4, 0.8, 1, 1, 0, 0)$ and $f_3$ is the minimal
-fluorescence signal .
+where the $c_l$ coefficients were taken in one of the four following tuples
+$(\left\{c_l\right\}_{l=-3}^2)=(0, 0, 1, 1, 1, 1)$,
+$(\left\{c_l\right\}_{l=-3}^2)=(0, 0, 1, 1, 1, 0)$,
+$(\left\{c_l\right\}_{l=-3}^2)=(1, 1, 1, 1, 0, 0)$ or
+$(\left\{c_l\right\}_{l=-3}^2)=(0.4, 0.8, 1, 1, 0, 0)$ and $f_3$ is a parameter
+of the hard-threshold filter.
 
 Then we apply a non-linear filter based on the current
-activity of the systems in order to favour the association measure when
-directly connected neurons are firing together, while artificially
+activity of the systems in order to favor the association measure when
+a medium size set of neurons are firing together, while artificially
 reducing the association measure in case of extreme network activity,
 i.e. high when a network firing is happening and low when no neuron is
-active.
+active:
+\begin{align}
+a_t &= \sum_{i=1}^p X^{\prime\prime\prime}_{t,i} +
+                   \frac{1}{2} X^{\prime\prime\prime}_{t-1,i} \forall t \in T\\
+r_t &= \frac{a_t}{\max_{l \in T}{a_l}} \\
+X^{\prime\prime\prime\prime}_{t,i} &=
+\left\{
+  \begin{array}{l}
+    1  : r_t < 0\\
+    {(X^{\prime\prime\prime}_{t,i} + 1)^{(a_t^{-1} + 1)}}^{g(r_t)} : r_t \geq 0
+  \end{array}
+\right.
+\end{align}
+where $g(x) = b_1 I(f_4 < x < f_5) + b_2  I(f_5 \leq x < f_6) +
+b_3 (I(x\leq f_4) + I(f_ 6 \leq x))$ is a piecewise continuous function of
+parameters $b_1, b_2, b_3, f_4, f_5, f_6$.
+
+% TODO speak about why averaging
 
@@
 
-\begin{table}[h!]
+\begin{table}[htb]
+\centering
 \begin{tabular}{|c|c||c|c|c|c|c|c|} \hline
@@
 
-\begin{table}[h!]
+\begin{table}[htb]
+\centering
 \begin{tabular}{|c|c||c|c|c|c|} \hline

### 2014-06-05 article.tex
Speak about pca noise filtering
Merge paragraph
put details in a footnote

@@
 
+% Introduce a custom solution to make the Y matrix asymmetric
+% Introduce directivity
 Since the partial correlation is a symmetric, the causal mechanism behind the
 interaction ($A$ directly causes $B$, $B$ directly causes $A$ or both ) can't
-be infered. Moreover, two other causal mechanisms might be implied while having
-a non-zero partial coefficient: (i) a pair of variables is induced by a
-common (hidden) variable; (ii) $A$ (respectively $B$) is conditionally
-correlated to a hidden variable affecting $B$ (resp. $A$)
-\cite{de2004discovery}.
-
-% Introduce a custom solution to make the Y matrix asymmetric
-% Introduce directivity
+be inferred.\footnote{Also note that two other causal mechanisms might be
+implied while having a non-zero partial coefficient: (i) a pair of variables
+is induced by a common (hidden) variable; (ii) $A$ (respectively $B$) is
+conditionally correlated to a hidden variable affecting $B$ (resp. $A$)
+\cite{de2004discovery}.} \cite{de2004discovery}.
 In our last submission in hope to improve performance, some causal information
@@
 
+Finally since there is a high correlation between neurons, we made a
+low-rank hypothesis and perform noise filtering through a principal component
+approach [TODO cite]. From the $p$ eigen vectors, we only kept the $80\%$ of
+those which have the largest eigen value.
+
   % TODO speak about why averaging

### 2014-06-05 article.tex
wip explain averaging

@@
 
-% Introduce a custom solution to make the Y matrix asymmetric
-% Introduce directivity
-Since the partial correlation is a symmetric, the causal mechanism behind the
-interaction ($A$ directly causes $B$, $B$ directly causes $A$ or both ) can't
-be inferred.\footnote{Also note that two other causal mechanisms might be
-implied while having a non-zero partial coefficient: (i) a pair of variables
-is induced by a common (hidden) variable; (ii) $A$ (respectively $B$) is
-conditionally correlated to a hidden variable affecting $B$ (resp. $A$)
-\cite{de2004discovery}.} \cite{de2004discovery}.
-In our last submission in hope to improve performance, some causal information
-(directivity of the links) were added by stacking the partial correlation score
-matrix with an pairwise activation heuristics. This method computes an anti-symmetric
-activation score $z_{ij}$ based the variation of fluorescence signal of a neuron
-$j$ due to a neuron $i$ over all timesteps:
-\[
-z_{ij} = \sum_{t=1}^n I(X_{t+1,j} - X_{t, i} \in [f_1, f_2]) -  I(X_{t+1,i} - X_{t, j} \in [f_1, f_2])
-\]
-where $f_1$ and $f_2$ are parameters of the method and $I$ is the
-indicator function.
-
 \section{Signal filtering methodology}
@@
 b_3 (I(x\leq f_4) + I(f_ 6 \leq x))$ is a piecewise continuous function of
-parameters $b_1, b_2, b_3, f_4, f_5, f_6$.
+parameters $b_1, b_2, b_3, f_4, f_5, f_6$. The coefficient were tuned
+for each set of coefficient $\left\{c_l\right\}_{l=-3}^2$.
 
@@
 low-rank hypothesis and perform noise filtering through a principal component
-approach [TODO cite]. From the $p$ eigen vectors, we only kept the $80\%$ of
-those which have the largest eigen value.
+approach [TODO cite]. From the $p$ eigen vectors, we only kept $80\%$ of
+the eigen vectors which have the largest eigen value.
 
-  % TODO speak about why averaging
+\section{Stacking methodology}
+
+% Speak about why averaging
+In order to improve performance, we stacked the partial correlation matrix
+from a reasonable of combinaison TODO continue
+
+% Introduce a custom solution to make the Y matrix asymmetric
+% Introduce directivity
+Since the partial correlation is a symmetric, the causal mechanism behind the
+interaction ($A$ directly causes $B$, $B$ directly causes $A$ or both ) can't
+be inferred.\footnote{Also note that two other causal mechanisms might be
+implied while having a non-zero partial coefficient: (i) a pair of variables
+is induced by a common (hidden) variable; (ii) $A$ (respectively $B$) is
+conditionally correlated to a hidden variable affecting $B$ (resp. $A$)
+\cite{de2004discovery}.} \cite{de2004discovery}.
+In our last submission in hope to improve performance, some causal information
+(directivity of the links) were added by stacking the partial correlation score
+matrix with an pairwise activation heuristics. This method computes an anti-symmetric
+activation score $z_{ij}$ based the variation of fluorescence signal of a neuron
+$j$ due to a neuron $i$ over all timesteps:
+\[
+z_{ij} = \sum_{t=1}^n I(X_{t+1,j} - X_{t, i} \in [f_1, f_2]) -  I(X_{t+1,i} - X_{t, j} \in [f_1, f_2])
+\]
+where $f_1$ and $f_2$ are parameters of the method and $I$ is the
+indicator function.
 

### 2014-06-05 article.tex
add todo
Wording about the stacking

@@
 
+\section{Signal filtering methodology}
+\label{sec:filter}
+% Explain why we need to filter
+% TODO
+
+% Filtering methodology
+Prior inferring the network, the fluorescent calcium time series are smoothed
+using several linear and non linear filters. A low-pass filter, a high-pass
+filter and a non linear hard-thresholding based filter are
+applied for each possible time step $t$
+\begin{align}
+X^\prime_{t,i} &= \sum_{l=-3}^2 c_l^k X_{t+l,i} \forall i, \\
+X^{\prime\prime}_{t,i} &= X^{\prime}_{t,i} - X^{\prime}_{t-1,i} \forall i, \\
+X^{\prime\prime\prime}_{t,i} &= {X^{\prime\prime}_{t,i}}^{0.9} I(X^{\prime\prime}_{t,i} \geq f_3) \forall i,
+\end{align}
+where the $c_l^k$ coefficients were taken in one of the four following tuples
+$\left\{c_l^1\right\}=(0, 0, 1, 1, 1, 1)$,
+$\left\{c_l^2\right\}=(0, 0, 1, 1, 1, 0)$,
+$\left\{c_l^3\right\}=(1, 1, 1, 1, 0, 0)$ or
+$\left\{c_l^4\right\}=(0.4, 0.8, 1, 1, 0, 0)$ and $f_3$ is a parameter
+of the hard-threshold filter.
+
+Then we apply a non-linear filter based on the current
+activity of the systems in order to favor the association measure when
+a medium size set of neurons are firing together, while artificially
+reducing the association measure in case of extreme network activity,
+i.e. high when a network firing is happening and low when no neuron is
+active:
+\begin{align}
+a_t &= \sum_{i=1}^p X^{\prime\prime\prime}_{t,i} +
+                   \frac{1}{2} X^{\prime\prime\prime}_{t-1,i} \forall t \in T\\
+r_t &= \frac{a_t}{\max_{l \in T}{a_l}} \\
+X^{\prime\prime\prime\prime}_{t,i} &=
+\left\{
+  \begin{array}{l}
+    1  : r_t < 0\\
+    {(X^{\prime\prime\prime}_{t,i} + 1)^{(a_t^{-1} + 1)}}^{g(r_t)} : r_t \geq 0
+  \end{array}
+\right.
+\end{align}
+where $g(x) = b_1 I(f_4 < x < f_5) + b_2  I(f_5 \leq x < f_6) +
+b_3 (I(x\leq f_4) + I(f_ 6 \leq x))$ is a piecewise continuous function of
+parameters $b_1, b_2, b_3, f_4, f_5, f_6$. The coefficient were tuned
+for each set of coefficient $\left\{c_l^k\right\}$.
+
+Finally since there is a high correlation between neurons, we made a
+low-rank hypothesis and perform noise filtering through a principal component
+approach [TODO cite]. From the $p$ eigen vectors, we only kept $80\%$ of
+the eigen vectors which have the largest eigen value.
+
 \section{Network inference methodology}
-
+\label{sec:inference}
 % Introduce notation + goal in mathematical score
@@
 
-\section{Signal filtering methodology}
+\section{Stacking methodology}
+\label{sec:stacking}
+% Speak about why averaging
+%In order to improve performance, we stacked the partial correlation matrix
 
-% Explain why we need to filter
-% TODO
+Our first guess was that introduce an ensemble method would improve performance
+[cite papers which praise ensemble methods]. Among all parameters of our method,
+we choose to average over two parameters, i.e. over multiple combinations of the
+hard-threshold value $f_3$ and the pattern of the low-pass filter $c_l$. In order to 
+free ourself from the choice of a probability distribution for the $(f_3,c_l)$ combinations,
+we choose a uniform distribution for the threshold distribution (in a given interval of 
+values) within each filtering process and perform a weighted average for the low-pass 
+filter pattern. Formally, the low-pass filter
 
-% Filtering methodology
-Prior inferring the network, the fluorescent calcium time series are smoothed
-using several linear and non linear filters. A low-pass filter, a high-pass
-filter and a non linear hard-thresholding based filter are
-applied for each possible time step $t$
 \begin{align}
-X^\prime_{t,i} &= \sum_{l=-3}^2 c_l X_{t+l,i} \forall i, \\
-X^{\prime\prime}_{t,i} &= X^{\prime}_{t,i} - X^{\prime}_{t-1,i} \forall i, \\
-X^{\prime\prime\prime}_{t,i} &= {X^{\prime\prime}_{t,i}}^{0.9} I(X^{\prime\prime}_{t,i} \geq f_3) \forall i,
+y_{stacking} = \sum_{k=1}^{k=4}  w_k \sum_{f_3 \in T} f(X, k, f_3)
 \end{align}
-where the $c_l$ coefficients were taken in one of the four following tuples
-$(\left\{c_l\right\}_{l=-3}^2)=(0, 0, 1, 1, 1, 1)$,
-$(\left\{c_l\right\}_{l=-3}^2)=(0, 0, 1, 1, 1, 0)$,
-$(\left\{c_l\right\}_{l=-3}^2)=(1, 1, 1, 1, 0, 0)$ or
-$(\left\{c_l\right\}_{l=-3}^2)=(0.4, 0.8, 1, 1, 0, 0)$ and $f_3$ is a parameter
-of the hard-threshold filter.
+where $f(X, k, f_3)$ applies the filtering and inference methodologies (as described 
+in sections \ref{sec:filter} and \ref{sec:inference}) with a  given value $f_3$ for the
+hard-threshold among a set of thresholds $T$ and the $k^{th}$ low-pass filter pattern.
 
-Then we apply a non-linear filter based on the current
-activity of the systems in order to favor the association measure when
-a medium size set of neurons are firing together, while artificially
-reducing the association measure in case of extreme network activity,
-i.e. high when a network firing is happening and low when no neuron is
-active:
-\begin{align}
-a_t &= \sum_{i=1}^p X^{\prime\prime\prime}_{t,i} +
-                   \frac{1}{2} X^{\prime\prime\prime}_{t-1,i} \forall t \in T\\
-r_t &= \frac{a_t}{\max_{l \in T}{a_l}} \\
-X^{\prime\prime\prime\prime}_{t,i} &=
-\left\{
-  \begin{array}{l}
-    1  : r_t < 0\\
-    {(X^{\prime\prime\prime}_{t,i} + 1)^{(a_t^{-1} + 1)}}^{g(r_t)} : r_t \geq 0
-  \end{array}
-\right.
-\end{align}
-where $g(x) = b_1 I(f_4 < x < f_5) + b_2  I(f_5 \leq x < f_6) +
-b_3 (I(x\leq f_4) + I(f_ 6 \leq x))$ is a piecewise continuous function of
-parameters $b_1, b_2, b_3, f_4, f_5, f_6$. The coefficient were tuned
-for each set of coefficient $\left\{c_l\right\}_{l=-3}^2$.
-
-Finally since there is a high correlation between neurons, we made a
-low-rank hypothesis and perform noise filtering through a principal component
-approach [TODO cite]. From the $p$ eigen vectors, we only kept $80\%$ of
-the eigen vectors which have the largest eigen value.
-
-\section{Stacking methodology}
-
-% Speak about why averaging
-In order to improve performance, we stacked the partial correlation matrix
-from a reasonable of combinaison TODO continue
-
+\section{Causal discovery methodology}
 % Introduce a custom solution to make the Y matrix asymmetric
@@
 interaction ($A$ directly causes $B$, $B$ directly causes $A$ or both ) can't
-be inferred.\footnote{Also note that two other causal mechanisms might be
+be inferred\footnote{Also note that two other causal mechanisms might be
 implied while having a non-zero partial coefficient: (i) a pair of variables
@@
 conditionally correlated to a hidden variable affecting $B$ (resp. $A$)
-\cite{de2004discovery}.} \cite{de2004discovery}.
+\cite{de2004discovery}.}\cite{de2004discovery}.
 In our last submission in hope to improve performance, some causal information
@@
 where $f_1$ and $f_2$ are parameters of the method and $I$ is the
-indicator function.
+indicator function. % TODO say that we use only the 3 first filters for this
 

### 2014-06-05 article.tex
add weights and normalization in stacking

@@
 \begin{align}
-y_{stacking} = \sum_{k=1}^{k=4}  w_k \sum_{f_3 \in T} f(X, k, f_3)
+y_{stacking} =  \dfrac{1}{\sum_{k\in\{1,..,4\}} w_k |T_k|} \sum_{k=1}^{k=4}  w_k \sum_{f_3 \in T_k} f(X, k, f_3)
 \end{align}
@@
 in sections \ref{sec:filter} and \ref{sec:inference}) with a  given value $f_3$ for the
-hard-threshold among a set of thresholds $T$ and the $k^{th}$ low-pass filter pattern.
+hard-threshold among a set of thresholds $T_k$ of size $|T_k|$ and the $k^{th}$ low-pass filter pattern associated 
+to a weight $w_k$ whose values are $w_1 = 0.01 , w_2 =1, w_3 = 0.7, w_4 = 0.9$.
 

### 2014-06-05 article.tex
fix wording
introduce (stacked) predicted adjacency matrix

@@
 values) within each filtering process and perform a weighted average for the low-pass 
-filter pattern. Formally, the low-pass filter
+filter pattern. Formally, the stacked predicted adjacency matrix can be formulated by
 
@@
 \end{align}
-where $f(X, k, f_3)$ applies the filtering and inference methodologies (as described 
-in sections \ref{sec:filter} and \ref{sec:inference}) with a  given value $f_3$ for the
+where $f(X, k, f_3)$ gives the predicted adjacency matrix, i.e. applies the filtering and inference methodologies (as described 
+in sections \ref{sec:filter} and \ref{sec:inference}), with a  given value $f_3$ for the
 hard-threshold among a set of thresholds $T_k$ of size $|T_k|$ and the $k^{th}$ low-pass filter pattern associated 
@@
 conditionally correlated to a hidden variable affecting $B$ (resp. $A$)
-\cite{de2004discovery}.}\cite{de2004discovery}.
+\cite{de2004discovery}.} \cite{de2004discovery}.
 In our last submission in hope to improve performance, some causal information

### 2014-06-05 article.tex
Motivation for directivity

@@
 values) within each filtering process and perform a weighted average for the low-pass 
-filter pattern. Formally, the stacked predicted adjacency matrix can be formulated by
+filter pattern. Formally, the stacked predicted adjacency matrix $y_{stacking}$ can be formulated by
 
@@
 % Introduce directivity
-Since the partial correlation is a symmetric, the causal mechanism behind the
-interaction ($A$ directly causes $B$, $B$ directly causes $A$ or both ) can't
+Since the partial correlation is a symmetric measure, the causal mechanism behind the
+interaction ($A$ directly causes $B$, $B$ directly causes $A$ or both) can not
 be inferred\footnote{Also note that two other causal mechanisms might be
@@
 conditionally correlated to a hidden variable affecting $B$ (resp. $A$)
-\cite{de2004discovery}.} \cite{de2004discovery}.
-In our last submission in hope to improve performance, some causal information
-(directivity of the links) were added by stacking the partial correlation score
-matrix with an pairwise activation heuristics. This method computes an anti-symmetric
-activation score $z_{ij}$ based the variation of fluorescence signal of a neuron
-$j$ due to a neuron $i$ over all timesteps:
+\cite{de2004discovery}.} directly from a symmetric adjacency matrix.
+
+By not taking into account the directivity for directed links, we systematically 
+make a true positive and a false positive for such links (see a more detailed 
+discussion about the chosen metric in section \ref{sec:metric}). Therefore, 
+performance might be improved by predicting an asymmetric adjacency matrix.  
+Hoping to orientate correctly the most obvious directed links, we attempt to 
+retrieve some causal information, i.e. the directivity of the links, by computing 
+and stacking with our symmetric adjacency matrix a matrix of pairwise activation 
+heuristics. This method computes an anti-symmetric activation score $z_{ij}$ 
+based the variation of fluorescence signal of a neuron $j$ due to a neuron $i$ 
+over all timesteps:
 \[
@@
 \end{table}
-\subsection{AUPRC}
+\subsection{Discussion about the metric}
+\label{sec:metric}
 

### 2014-06-06 article.tex
wording

@@
 Cutting edge optical devices [todo cite] allows to track simultaneously
-the neural activity of thousands of neurons through the fluorescent
+the neural activity of thousands of neurons through a fluorescent
 calcium indicator.
@@
 systems have a sampling rate smaller than the neuron firing speed and are
-limited only two dimensional image, which may lead to superpose the activity
+limited to two dimensional image, while the neuronal network is three dimensional
+structure, which may lead to superpose the observed activity
 of different neurons. Furthermore, the decay of the fluorescent calcium signal

### 2014-06-06 article.tex
wording

@@
 systems have a sampling rate smaller than the neuron firing speed and are
-limited to two dimensional image, while the neuronal network is three dimensional
-structure, which may lead to superpose the observed activity
+limited to two dimensional image, while the neuronal network is a
+three dimensional structure, which may lead to superpose the observed activity
 of different neurons. Furthermore, the decay of the fluorescent calcium signal
-is slow compare to its rise.
+is slower than its rise.
 

### 2014-06-06 article.tex
link to the challenge website
add todo
move goal to the introduction
remove duplicated content

@@
 the anatomical and functional connectivity of the brain.
-In the context of the Connectomics challenge, we propose a pre-processing and a simple approach in order to achieve a high performance inference of the connectivity network.
-We put in perspective our method by comparing with other inference method such as GTE [], another method proposed to infer a neural network from calcium fluorescent imaging, and Genie3 [], a tree-based approach very competitive in several gene inference challenge (i.e.
-DREAM4 and DREAM5).\\
+In the context of the Connectomics challenge, we propose a pre-processing and
+a simple approach in order to achieve a high performance inference of the
+connectivity network.
+We put in perspective our method by comparing with other inference method such
+as GTE [], another method proposed to infer a neural network from calcium
+fluorescent imaging, and Genie3 [], a tree-based approach very competitive
+in several gene inference challenge (i.e. DREAM4 and DREAM5).
 
@@
 \begin{keywords}
-Network inference - Precision matrix - GENIE3
+Network inference - Partial correlation - Precision matrix - GENIE3
 \end{keywords}
@@
 % BG : brain, complex organ
-Understanding how the brain works is a key to understand and to treat
-brain pathologies and disorders such as Parkinson's disease and epilepsy.
-Retrieving the connectomes, neurons connectivity map, will shed new lights on
-the anatomical and functional connectivity of the brain. However,
-the human brain is a complex biological organ, which is formed by 100
+% TODO remove redundant information from the abstract
+The human brain is a complex biological organ, which is formed by 100
 billions of neurons with 7000 synaptic connections on average. Inferring the
 neuron connectivity network through dissection would be an impossible
-and a daunting task.
+and a daunting task. Cutting edge optical devices [todo cite] allow to track
+simultaneously the neural activity of thousands of neurons through a fluorescent
+calcium indicator.
 
-Cutting edge optical devices [todo cite] allows to track simultaneously
-the neural activity of thousands of neurons through a fluorescent
-calcium indicator.
 From those observational data, the neural connectivity inference consists in
@@
 
+% Introduce notation + goal in mathematical score
+% TODO check convention for y_{ij}
+One way to emphasize the connections between neurons is to represent them by a
+(un)directed graph with $p$ nodes: each node represents a neuron, and each
+edge $y_{ij}$ represents a direct link from neuron  $i$ to neuron $j$. If the
+graph is undirected, then $y_{ij}$ is equal to $y_{ji}$  for all $i,j$.
+The unsupervised task may be formulated as:
+\textit{Given $X \in \mathcal{R}^{n \times p}$  a set of $p$ time series of
+fluorescent calcium concentration of size $n$ from $p$ neurons, the goal is to
+infer the connectivity graph $y \in \left\{0, 1\right\}^{p \times p}$.}
+The main challenge in the inference of the network $y$
+is to distinguish direct from indirect interactions \cite{de2004discovery}.
+For instance with the simple interaction graph $A \rightarrow B \rightarrow C$,
+we want to distinguish direct interactions $A \rightarrow B$ and $B \rightarrow C$
+from the indirect interaction $A \rightarrow C$.
+
 % Solution
@@
 based on partial correlation to infer the neural connectivity network.
-This is also the winning method of the Connectomics challenge [todo cite].
+This is also the winning method of the Connectomics challenge
+\footnote{\url{http://connectomics.chalearn.org/}}.
 
@@
 \label{sec:inference}
-% Introduce notation + goal in mathematical score
-% TODO check convention for y_{ij}
-One way to emphasize the connections between neurons is to represent them by a
-(un)directed graph with $p$ nodes: each node represents a neuron, and each
-edge $y_{ij}$ represents a direct link from neuron  $i$ to neuron $j$. If the
-graph is undirected, then $y_{ij}$ is equal to $y_{ji}$  for all $i,j$.
-The unsupervised task may be formulated as:
-\textit{Given $X \in \mathcal{R}^{n \times p}$  a set of $p$ time series of
-fluorescent calcium concentration of size $n$ from $p$ neurons, the goal is to
-infer the connectivity graph $y \in \left\{0, 1\right\}^{p \times p}$.}
-The main challenge in the inference of the network $y$
-is to distinguish direct from indirect interactions \cite{de2004discovery}.
-For instance with the simple interaction graph $A \rightarrow B \rightarrow C$,
-we want to distinguish direct interactions $A \rightarrow B$ and $B \rightarrow C$
-from the indirect interaction $A \rightarrow C$.
 

### 2014-06-06 article.tex
re-order pagraph
remove todo
todo
introduce T notatino

@@
 % BG : brain, complex organ
-% TODO remove redundant information from the abstract
 The human brain is a complex biological organ, which is formed by 100
@@
 is slower than its rise.
-
-Since only observational data are available, the network recovery is set as an
-unsupervised learning problem. Whenever a partial knowledge of the target
-network or known networks highly similar to the unknown one is available,
-supervised learning [todo cite] and transfer learning  [todo cite] based
-approach could be considered to infer networks.
 
@@
 
+Since only observational data are available, the network recovery is set as an
+unsupervised learning problem. Whenever a partial knowledge of the target
+network or known networks highly similar to the unknown one is available,
+supervised learning [todo cite] and transfer learning  [todo cite] based
+approach could be considered to infer networks.
+
 % Solution
@@
 applied for each possible time step $t$
+% TODO fix first equation is wrong due notation change
 \begin{align}
@@
 
-Then we apply a non-linear filter based on the current
+Then we apply on all remaining timesteps $T$ a non-linear filter based on the current
 activity of the systems in order to favor the association measure when

### 2014-06-06 article.tex
improve stacking section

@@
 \label{sec:stacking}
+
 % Speak about why averaging
-%In order to improve performance, we stacked the partial correlation matrix
-
-Our first guess was that introduce an ensemble method would improve performance
-[cite papers which praise ensemble methods]. Among all parameters of our method,
-we choose to average over two parameters, i.e. over multiple combinations of the
-hard-threshold value $f_3$ and the pattern of the low-pass filter $c_l$. In order to
-free ourself from the choice of a probability distribution for the $(f_3,c_l)$ combinations,
-we choose a uniform distribution for the threshold distribution (in a given interval of
-values) within each filtering process and perform a weighted average for the low-pass
-filter pattern. Formally, the stacked predicted adjacency matrix $y_{stacking}$ can be formulated by
-
+The quality of the signal filtering and network inference is dependent upon
+good hyper-parameter selection, which are themselves dependent on the properties
+of the targeted network and measurement conditions, e.g. signal to noise ratio.
+Ensemble methods are known to improve robustness with respect to parameter
+selection [todo cite] and improve performance [todo cite].
+A weighted average $y_{stack}$ of partial correlation matrices was made
+by varying uniformly the hard-threshold value (parameter $f_3$) and the design
+of the low-pass filter (coefficients $c_l$). The stacked connectivity score
+matrix $y_{stacking}$ is given by
 \begin{align}
-y_{stacking} =  \dfrac{1}{\sum_{k\in\{1,..,4\}} w_k |T_k|} \sum_{k=1}^{k=4}  w_k \sum_{f_3 \in T_k} f(X, k, f_3)
+y_{stack} =  \dfrac{1}{\sum_{k\in\{1,..,4\}} w_k |T_k|} \sum_{k=1}^{k=4}  w_k \sum_{f_3 \in T_k} f(X, k, f_3)
 \end{align}
-where $f(X, k, f_3)$ gives the predicted adjacency matrix, i.e. applies the filtering and inference methodologies (as described
-in sections \ref{sec:filter} and \ref{sec:inference}), with a  given value $f_3$ for the
-hard-threshold among a set of thresholds $T_k$ of size $|T_k|$ and the $k^{th}$ low-pass filter pattern associated
-to a weight $w_k$ whose values are $w_1 = 0.01 , w_2 =1, w_3 = 0.7, w_4 = 0.9$.
+where $f(X, k, f_3)$ gives the predicted adjacency matrix, i.e. applies the
+filtering and inference methodologies (as described
+in sections \ref{sec:filter} and \ref{sec:inference}), with a  given value
+$f_3$ for the hard-threshold among a set of thresholds $T_k$ of size $|T_k|$
+and the $k^{th}$ low-pass filter pattern associated to a weight $w_k$ whose
+values are $w_1 = 0.01 , w_2 =1, w_3 = 0.7, w_4 = 0.9$.
 

### 2014-06-06 article.tex
todo + wording

@@
 
-By not taking into account the directivity for directed links, we systematically
-make a true positive and a false positive for such links (see a more detailed
+By ignoring the directivity, we systematically
+make a true positive and a false positive for direct link (see a more detailed
 discussion about the chosen metric in section \ref{sec:metric}). Therefore,
@@
 indicator function. % TODO say that we use only the 3 first filters for this
+
+% TODO speak that we should set the diagonal to the minimum to gain some
+% performance.
 

### 2014-06-06 article.tex
rework strucutre + add reference for datasets
Add dataset description

@@
 This is also the winning method of the Connectomics challenge
-\footnote{\url{http://connectomics.chalearn.org/}}.
+\footnote{\url{http://connectomics.chalearn.org/}}. For reproducibility, the
+source code of the method is available at
+\url{https://github.com/asutera/kaggle-connectomics} under 3-clause BSD
+license.
 
-\section{Signal filtering methodology}
-\label{sec:filter}
+\section{Methodology}
+\section{Signal filtering} \label{sec:filter}
 % Explain why we need to filter
@@
 
-\section{Network inference methodology}
+\subsection{Network inference through partial correlation}
 \label{sec:inference}
@@
 
-\section{Stacking methodology}
+\subsection{Stacking partial correlation matrix}
 \label{sec:stacking}
@@
 
-\section{Causal discovery methodology}
+\subsection{Causal discovery methodology}
 % Introduce a custom solution to make the Y matrix asymmetric
@@
 
-\section{Empirical experiments}
-\subsection{Datasets}
+\section{Experiments}
+\subsection{Accuracy assessment protocol}
+% Datasets
+To assess our method, we have used four datasets provided by the organizer
+of the Connectomics challenge : normal-1, normal-2, normal-3, normal-4. Those
+datasets are time series of size $n=179500$ of image calcium from simulated
+neuronal network \cite{stetter2012model} with $p=1000$ neurons. The networks
+to inferred have around 15000 arcs or a density of $0.15\%$.
 
-\subsection{Metrics}
-\subsection{Data filtering}
-\subsection{Signal distribution}
-\subsection{ROC AUC results}
+% Metrics : ROC AUC an AUPRC
+% We assess the accuracy of the neuronal network
+
+\subsection{Data filtering and Signal distribution}
+
+\subsection{Inference of neuronal network}
+
 \paragraph{Improvement of each stage of our approach\\}
@@
 4 & GTE & & & & \\ \hline
-
 \end{tabular}
@@
 % conditional independence test
+% Speak about the complexity and parallelization of the methods
 

### 2014-06-06 article.tex
describe metrics

@@
 source code of the method is available at
-\url{https://github.com/asutera/kaggle-connectomics} under 3-clause BSD
+\url{https://github.com/asutera/kaggle-connectomics} under BSD 3-clauses
 license.
@@
 \section{Experiments}
-\subsection{Accuracy assessment protocol}
 % Datasets
@@
 % Metrics : ROC AUC an AUPRC
-% We assess the accuracy of the neuronal network
+The network inference task can be viewed as a binary classification task
+where one have to correctly classified the presence or the absence of edges
+in the connectivity graph. Given the ground true network
+$y_{i,j} \in \left\{0, 1\right\}$, the connectivity score matrix
+$\hat{y}_{i,j} \in \mathcal{R}$ inferred by a given modeling technique
+can be thresholded by a value $\tau \in \mathcal{R}$ to evaluate its performance. In this
+context, we first define the notion of
+true positive $tp(\tau) = \sum_{i=1}^p \sum_{j=1}^p I(y_{i,j} = 1, \hat{y}_{i,j} \geq \tau)$,
+true negative $tn(\tau) = \sum_{i=1}^p \sum_{j=1}^p I(y_{i,j} = 0, \hat{y}_{i,j} < \tau)$,
+false negative $fn(\tau) = \sum_{i=1}^p \sum_{j=1}^p I(y_{i,j} = 1, \hat{y}_{i,j} < \tau)$ and
+false positive $fp(\tau) = \sum_{i=1}^p \sum_{j=1}^p I(y_{i,j} = 0, \hat{y}_{i,j} \geq \tau)$,
+which is also called the confusion matrix.
+
+We assess the accuracy of the network inference using the area under
+the ROC curve (ROC AUC) obtained by varying the threshold
+$\tau$ of the true positive rate $tpr(\tau) = tp(\tau) / (tp(\tau) + fn(\tau))$
+as a function of the false positive rate
+$fpr(\tau) = tn(\tau) / (tn(\tau) + fp(\tau))$. In section (TODO ref),
+we also compare the same methods with the area under the precision-recall
+curve obtained by varying the threshold
+$\tau$ of the precision $P(\tau) = tp(\tau) / (tp(\tau) + fp(\tau))$
+as a function of the recall $R(\tau) = tp(\tau) / (tp(\tau) + fn(\tau))$,
+which is an information retrieval measure.
 

### 2014-06-06 article.tex
typo + abbreviation for auprc

@@
 
-% Metrics : ROC AUC an AUPRC
+% Metrics : ROC AUC and AUPRC
 The network inference task can be viewed as a binary classification task
@@
 we also compare the same methods with the area under the precision-recall
-curve obtained by varying the threshold
+(AUPRC) curve obtained by varying the threshold
 $\tau$ of the precision $P(\tau) = tp(\tau) / (tp(\tau) + fp(\tau))$

### 2014-06-06 article.tex
wording + better math

@@
 the ROC curve (ROC AUC) obtained by varying the threshold
-$\tau$ of the true positive rate $tpr(\tau) = tp(\tau) / (tp(\tau) + fn(\tau))$
+$\tau$ of the true positive rate $tpr(\tau) = \frac{tp(\tau)}{tp(\tau) + fn(\tau)}$
 as a function of the false positive rate
-$fpr(\tau) = tn(\tau) / (tn(\tau) + fp(\tau))$. In section (TODO ref),
+$fpr(\tau) = \frac{tn(\tau)}{tn(\tau) + fp(\tau)}$. In section (TODO ref),
 we also compare the same methods with the area under the precision-recall
-(AUPRC) curve obtained by varying the threshold
-$\tau$ of the precision $P(\tau) = tp(\tau) / (tp(\tau) + fp(\tau))$
-as a function of the recall $R(\tau) = tp(\tau) / (tp(\tau) + fn(\tau))$,
-which is an information retrieval measure.
+(AUPRC) curve, an information retrieval metrics, obtained by varying the threshold
+$\tau$ of the precision $P(\tau) = \frac{tp(\tau)}{tp(\tau) + fp(\tau)}$
+as a function of the recall $R(\tau) = \frac{tp(\tau)}{tp(\tau) + fn(\tau)}$.
 

### 2014-06-06 article.tex
Use booktabs for tbale

@@
  %\usepackage{rotating}% for sideways figures and tables
-\usepackage{longtable}% for long tables
+% \usepackage{longtable}% for long tables
 
@@
 
-\paragraph{Improvement of each stage of our approach\\}
+\begin{table}[htb]
+\centering
+\caption{Improvement of each stage of our approach Note that we choose the
+         \textit{best} threshold for stages 1 to 4.}
+\begin{tabular}{*{5}{l}}
+\toprule
+Stage               & normal-1 & normal-2 & normal-3 & normal-4 \\
+\midrule
+Inverse correlation & & & & \\
+Pre-processing      & & & & \\
+PCA                 & & & & \\
+Weighting           & & & & \\
+Averaging           & & & & \\
+\bottomrule
+\end{tabular}
+\end{table}
 
@@
 \centering
-\begin{tabular}{|c|c||c|c|c|c|c|c|} \hline
-\# & Stage & normal-1 & normal-2 & normal-3 & normal-4 \\ \hline
-1 & Inverse correlation & & & & \\ \hline
-2 & Pre-processing & & & &\\ \hline
-3 & PCA & & & &  \\ \hline
-4 & Weighting & & & &  \\ \hline
-5 & Averaging & & & &  \\ \hline
-
+\caption{Comparison with other methods}
+\begin{tabular}{*{5}{l}}
+\toprule
+Methods             & normal-1 & normal-2 & normal-3 & normal-4 \\
+\midrule
+Correlation         & & & & \\
+Partial correlation & & & & \\
+Our approach        & & & & \\
+GENIE3              & & & & \\
+GTE                 & & & & \\
+\bottomrule
 \end{tabular}
@@
 
-Note that we choose the \textit{best} threshold for stages 1 to 4.
-\paragraph{Comparison with other methods\\}
-
-\begin{table}[htb]
-\centering
-\begin{tabular}{|c|c||c|c|c|c|} \hline
-\# & Stage & normal-1 & normal-2 & normal-3 & normal-4 \\ \hline
-1 & Inverse correlation & & & &\\ \hline
-2 & Correlation & & & &\\ \hline
-3 & GENIE3 & & & & \\ \hline
-4 & GTE & & & & \\ \hline
-\end{tabular}
-\end{table}
 \subsection{Discussion about the metric}

### 2014-06-06 article.tex
Add acknowledgements

@@
 % Speak about the complexity and parallelization of the methods
+\begin{scriptsize}
+\paragraph{Acknowledgements.} A. Joly and G. Louppes are research
+fellows of the FNRS, Belgium.  A. Sutera is supported by a F.R.I.A. scholarship.
+This work is supported by PASCAL2 and the IUAP
+DYSCO, initiated by the Belgian State, Science Policy Office.
+Computational ressources have been provided by the Consortium des Équipements
+de Calcul Intensif (CÉCI), funded by the Fonds de la Recherche Scientifique de
+Belgique (F.R.S.-FNRS) under Grant No. 2.5020.11
+\end{scriptsize}
 

### 2014-06-06 article.tex
wording

@@
 where one have to correctly classified the presence or the absence of edges
-in the connectivity graph. Given the ground true network
-$y_{i,j} \in \left\{0, 1\right\}$, the connectivity score matrix
-$\hat{y}_{i,j} \in \mathcal{R}$ inferred by a given modeling technique
-can be thresholded by a value $\tau \in \mathcal{R}$ to evaluate its performance. In this
-context, we first define the notion of
+of the graph. The connectivity score matrix
+$\hat{y}_{i,j} \in \mathcal{R}$ inferred by a modeling technique
+can be thresholded by a value $\tau \in \mathcal{R}$ to evaluate its performance.
+Given the ground true network $y_{i,j} \in \left\{0, 1\right\}$, we first define the notion of
 true positive $tp(\tau) = \sum_{i=1}^p \sum_{j=1}^p I(y_{i,j} = 1, \hat{y}_{i,j} \geq \tau)$,
@@
 false negative $fn(\tau) = \sum_{i=1}^p \sum_{j=1}^p I(y_{i,j} = 1, \hat{y}_{i,j} < \tau)$ and
-false positive $fp(\tau) = \sum_{i=1}^p \sum_{j=1}^p I(y_{i,j} = 0, \hat{y}_{i,j} \geq \tau)$,
-which is also called the confusion matrix.
+false positive $fp(\tau) = \sum_{i=1}^p \sum_{j=1}^p I(y_{i,j} = 0, \hat{y}_{i,j} \geq \tau)$.
+Those four numbers formed the confusion matrix.
 
@@
 we also compare the same methods with the area under the precision-recall
-(AUPRC) curve, an information retrieval metrics, obtained by varying the threshold
+curve (AUPRC), an information retrieval metrics, obtained by varying the threshold
 $\tau$ of the precision $P(\tau) = \frac{tp(\tau)}{tp(\tau) + fp(\tau)}$

### 2014-06-06 article.tex
wording

--- 2014-06-06 article.tex
@@
  %\usepackage{rotating}% for sideways figures and tables
-% \usepackage{longtable}% for long tables
+\usepackage{longtable}% for long tables
 
@@
 the anatomical and functional connectivity of the brain.
-In the context of the Connectomics challenge, we propose a pre-processing and
-a simple approach in order to achieve a high performance inference of the
-connectivity network.
-We put in perspective our method by comparing with other inference method such
-as GTE [], another method proposed to infer a neural network from calcium
-fluorescent imaging, and Genie3 [], a tree-based approach very competitive
-in several gene inference challenge (i.e. DREAM4 and DREAM5).
+
+In the context of the Connectomics challenge, we propose a simple algorithm made of four stages to achieve a network inference of high quality.
+
+We put in perspective our method by comparing with other inference method such as GTE [], another method proposed to infer a neural network from calcium fluorescent imaging, and Genie3 [], a tree-based approach very competitive in several gene inference challenge (i.e.
+DREAM4 and DREAM5).\\
 
@@
 \begin{keywords}
-Network inference - Partial correlation - Precision matrix - GENIE3
+Network inference - Precision matrix - GENIE3
 \end{keywords}
@@
 % BG : brain, complex organ
-The human brain is a complex biological organ, which is formed by 100
+Understanding how the brain works is a key to understand and to treat
+brain pathologies and disorders such as Parkinson's disease and epilepsy.
+Retrieving the connectomes, neurons connectivity map, will shed new lights on
+the anatomical and functional connectivity of the brain. However,
+the human brain is a complex biological organ, which is formed by 100
 billions of neurons with 7000 synaptic connections on average. Inferring the
 neuron connectivity network through dissection would be an impossible
-and a daunting task. Cutting edge optical devices [todo cite] allow to track
-simultaneously the neural activity of thousands of neurons through a fluorescent
+and a daunting task.
+
+Cutting edge optical devices [todo cite] allows to track simultaneously
+the neural activity of thousands of neurons through the fluorescent
 calcium indicator.
-
 From those observational data, the neural connectivity inference consists in
@@
 systems have a sampling rate smaller than the neuron firing speed and are
-limited to two dimensional image, while the neuronal network is a
-three dimensional structure, which may lead to superpose the observed activity
+limited only two dimensional image, which may lead to superpose the activity
 of different neurons. Furthermore, the decay of the fluorescent calcium signal
-is slower than its rise.
-
-% Introduce notation + goal in mathematical score
-% TODO check convention for y_{ij}
-One way to emphasize the connections between neurons is to represent them by a
-(un)directed graph with $p$ nodes: each node represents a neuron, and each
-edge $y_{ij}$ represents a direct link from neuron  $i$ to neuron $j$. If the
-graph is undirected, then $y_{ij}$ is equal to $y_{ji}$  for all $i,j$.
-The unsupervised task may be formulated as:
-\textit{Given $X \in \mathcal{R}^{n \times p}$  a set of $p$ time series of
-fluorescent calcium concentration of size $n$ from $p$ neurons, the goal is to
-infer the connectivity graph $y \in \left\{0, 1\right\}^{p \times p}$.}
-The main challenge in the inference of the network $y$
-is to distinguish direct from indirect interactions \cite{de2004discovery}.
-For instance with the simple interaction graph $A \rightarrow B \rightarrow C$,
-we want to distinguish direct interactions $A \rightarrow B$ and $B \rightarrow C$
-from the indirect interaction $A \rightarrow C$.
+is slow compare to its rise.
 
@@
 based on partial correlation to infer the neural connectivity network.
-This is also the winning method of the Connectomics challenge
-\footnote{\url{http://connectomics.chalearn.org/}}. For reproducibility, the
-source code of the method is available at
-\url{https://github.com/asutera/kaggle-connectomics} under BSD 3-clauses
-license.
+This is also the winning method of the Connectomics challenge [todo cite].
 
-\section{Methodology}
-\section{Signal filtering} \label{sec:filter}
+\section{Signal filtering methodology}
+\label{sec:filter}
 % Explain why we need to filter
@@
 applied for each possible time step $t$
-% TODO fix first equation is wrong due notation change
 \begin{align}
@@
 
-Then we apply on all remaining timesteps $T$ a non-linear filter based on the current
+Then we apply a non-linear filter based on the current
 activity of the systems in order to favor the association measure when
@@
 
-\subsection{Network inference through partial correlation}
+\section{Network inference methodology}
 \label{sec:inference}
+% Introduce notation + goal in mathematical score
+% TODO check convention for y_{ij}
+One way to emphasize the connections between neurons is to represent them by a
+(un)directed graph with $p$ nodes: each node represents a neuron, and each
+edge $y_{ij}$ represents a direct link from neuron  $i$ to neuron $j$. If the
+graph is undirected, then $y_{ij}$ is equal to $y_{ji}$  for all $i,j$.
+The unsupervised task may be formulated as:
+\textit{Given $X \in \mathcal{R}^{n \times p}$  a set of $p$ time series of
+fluorescent calcium concentration of size $n$ from $p$ neurons, the goal is to
+infer the connectivity graph $y \in \left\{0, 1\right\}^{p \times p}$.}
+The main challenge in the inference of the network $y$
+is to distinguish direct from indirect interactions \cite{de2004discovery}.
+For instance with the simple interaction graph $A \rightarrow B \rightarrow C$,
+we want to distinguish direct interactions $A \rightarrow B$ and $B \rightarrow C$
+from the indirect interaction $A \rightarrow C$.
 
@@
 
+Let us consider that each neuron signal $i$ is a random continuous variable $X_i$
+which follows a probability distribution $p_{X_i}$ and let us denote by $p_{X_i,X_j|\mathcal{Z}}$ the 
+joint probability distribution of neurons $X_i$ and $X_j$ conditioned on a subset of variables $\mathcal{Z}$ (eventually empty). Let us define $\mathcal{V}$
+the set of all neurons $X_1, ..., X_p$ and $\mathcal{V}^{-i,j}$ the same set without
+neurons $X_i$ and $X_j$.
+
 Each neuron signal $i$ is a random continuous variable $X_i$,
@@
 Two neurons $X_i$, $X_j$ will be said conditionally independent
-to a set of neurons $X_1,\ldots,X_p \backslash \left\{X_i, X_j\right\}$, denoted
-by  $X_i \perp X_j | X_1,\ldots,X_p \backslash \left\{X_i, X_j\right\}$,  if
-\begin{align*}
-&p_{X_i, X_j | X_1,\ldots,X_p \backslash \left\{X_i, X_j\right\}}
-    (x_i, x_j | x_1,\ldots,x_p \backslash \left\{x_i, x_j\right\}) \\
-=&p_{X_i | X_1,\ldots,X_p \backslash \left\{X_i, X_j\right\}}
-    (x_i | x_1,\ldots,x_p \backslash \left\{x_i, x_j\right\})
-p_{X_j | X_1,\ldots,X_p \backslash \left\{X_i, X_j\right\}}
-    (x_j | x_1,\ldots,x_p \backslash \left\{x_i, x_j\right\})
-\end{align*}
-for all real numbers $x_1,\ldots,x_p $ such that
-$p_{X_1,\ldots,X_p \backslash \left\{X_i, X_j\right\}}
-(x_1,\ldots,x_p \backslash \left\{x_i, x_j\right\}) > 0$. Note that this
-reciprocal is true only under additional hypotheses.
+to a set of neurons $\mathcal{V}^{-i,j}$, denoted
+by  $X_i \perp X_j | \mathcal{V}^{-i,j}$,  if $p_{X_i,X_j|\mathcal{V}^{-i,j}} = p_{X_i|\mathcal{V}^{-i,j}}  p_{X_j|\mathcal{V}^{-i,j}} $.
+%for all real numbers $x_1,\ldots,x_p $ such that
+%$p_{X_1,\ldots,X_p \backslash \left\{X_i, X_j\right\}}
+%(x_1,\ldots,x_p \backslash \left\{x_i, x_j\right\}) > 0$. Note that this
+%reciprocal is true only under additional hypotheses.
 
@@
 
-\subsection{Stacking partial correlation matrix}
+\section{Stacking methodology}
 \label{sec:stacking}
+% Speak about why averaging
+%In order to improve performance, we stacked the partial correlation matrix
 
-% Speak about why averaging
-The quality of the signal filtering and network inference is dependent upon
-good hyper-parameter selection, which are themselves dependent on the properties
-of the targeted network and measurement conditions, e.g. signal to noise ratio.
-Ensemble methods are known to improve robustness with respect to parameter
-selection [todo cite] and improve performance [todo cite].
-A weighted average $y_{stack}$ of partial correlation matrices was made
-by varying uniformly the hard-threshold value (parameter $f_3$) and the design
-of the low-pass filter (coefficients $c_l$). The stacked connectivity score
-matrix $y_{stacking}$ is given by
+Our first guess was that introduce an ensemble method would improve performance
+[cite papers which praise ensemble methods]. Among all parameters of our method,
+we choose to average over two parameters, i.e. over multiple combinations of the
+hard-threshold value $f_3$ and the pattern of the low-pass filter $c_l$. In order to 
+free ourself from the choice of a probability distribution for the $(f_3,c_l)$ combinations,
+we choose a uniform distribution for the threshold distribution (in a given interval of 
+values) within each filtering process and perform a weighted average for the low-pass 
+filter pattern. Formally, the stacked predicted adjacency matrix $y_{stacking}$ can be formulated by
+
 \begin{align}
-y_{stack} =  \dfrac{1}{\sum_{k\in\{1,..,4\}} w_k |T_k|} \sum_{k=1}^{k=4}  w_k \sum_{f_3 \in T_k} f(X, k, f_3)
+y_{stacking} =  \dfrac{1}{\sum_{k\in\{1,..,4\}} w_k |T_k|} \sum_{k=1}^{k=4}  w_k \sum_{f_3 \in T_k} f(X, k, f_3)
 \end{align}
-where $f(X, k, f_3)$ gives the predicted adjacency matrix, i.e. applies the
-filtering and inference methodologies (as described
-in sections \ref{sec:filter} and \ref{sec:inference}), with a  given value
-$f_3$ for the hard-threshold among a set of thresholds $T_k$ of size $|T_k|$
-and the $k^{th}$ low-pass filter pattern associated to a weight $w_k$ whose
-values are $w_1 = 0.01 , w_2 =1, w_3 = 0.7, w_4 = 0.9$.
+where $f(X, k, f_3)$ gives the predicted adjacency matrix, i.e. applies the filtering 
+and inference methodologies (as described in sections \ref{sec:filter} and \ref{sec:inference}), 
+with a  given value $f_3$ for the hard-threshold among a set of thresholds $T_k$ 
+of size $|T_k|$ and the $k^{th}$ low-pass filter pattern associated to a weight $w_k$ 
+whose values are $w_1 = 0.01 , w_2 =1, w_3 = 0.7, w_4 = 0.9$.
 
-\subsection{Causal discovery methodology}
+\section{Causal discovery methodology}
 % Introduce a custom solution to make the Y matrix asymmetric
@@
 interaction ($A$ directly causes $B$, $B$ directly causes $A$ or both) can not
-be inferred\footnote{Also note that two other causal mechanisms might be
+be directly inferred\footnote{Also note that two other causal mechanisms might be
 implied while having a non-zero partial coefficient: (i) a pair of variables
@@
 conditionally correlated to a hidden variable affecting $B$ (resp. $A$)
-\cite{de2004discovery}.} directly from a symmetric adjacency matrix.
+\cite{de2004discovery}.} from a symmetric adjacency matrix.
 
-By ignoring the directivity, we systematically
-make a true positive and a false positive for direct link (see a more detailed
+By not taking into account the directivity for directed links, we systematically 
+make a true positive and a false positive for such links (see a more detailed 
 discussion about the chosen metric in section \ref{sec:metric}). Therefore, 
@@
 
-% TODO speak that we should set the diagonal to the minimum to gain some
-% performance.
+\section{Empirical experiments}
+In this section, we will present some experiments on challenge datasets to show 
+the good performance of our method and compare it to other inference methods. 
+Since it was the metric used during the challenge, we will compare inference methods
+regarding the area under the ROC curve. However, we will discuss about this in section
+\ref{sec:metric}.
 
-\section{Experiments}
-% Datasets
-To assess our method, we have used four datasets provided by the organizer
-of the Connectomics challenge : normal-1, normal-2, normal-3, normal-4. Those
-datasets are time series of size $n=179500$ of image calcium from simulated
-neuronal network \cite{stetter2012model} with $p=1000$ neurons. The networks
-to inferred have around 15000 arcs or a density of $0.15\%$.
+\paragraph{Datasets \\}
+To assess the quality of our method, we use four network, denoted as \textit{normal-\{1,2,3,4\}}, similar to networks, i.e., the same number of neurons, used to rank challenge participants.
+Note that our parameter tuning was mainly on \textit{normal-1} dataset and partly on \textit{normal-4} dataset, therefore it may justify why these networks are better retrieved despite the fact that some might be simpler to infer.
 
-% Metrics : ROC AUC and AUPRC
-The network inference task can be viewed as a binary classification task
-where one have to correctly classified the presence or the absence of edges
-in the connectivity graph. Given the ground true network
-$y_{i,j} \in \left\{0, 1\right\}$, the connectivity score matrix
-$\hat{y}_{i,j} \in \mathcal{R}$ inferred by a given modeling technique
-can be thresholded by a value $\tau \in \mathcal{R}$ to evaluate its performance. In this
-context, we first define the notion of
-true positive $tp(\tau) = \sum_{i=1}^p \sum_{j=1}^p I(y_{i,j} = 1, \hat{y}_{i,j} \geq \tau)$,
-true negative $tn(\tau) = \sum_{i=1}^p \sum_{j=1}^p I(y_{i,j} = 0, \hat{y}_{i,j} < \tau)$,
-false negative $fn(\tau) = \sum_{i=1}^p \sum_{j=1}^p I(y_{i,j} = 1, \hat{y}_{i,j} < \tau)$ and
-false positive $fp(\tau) = \sum_{i=1}^p \sum_{j=1}^p I(y_{i,j} = 0, \hat{y}_{i,j} \geq \tau)$,
-which is also called the confusion matrix.
-
-We assess the accuracy of the network inference using the area under
-the ROC curve (ROC AUC) obtained by varying the threshold
-$\tau$ of the true positive rate $tpr(\tau) = \frac{tp(\tau)}{tp(\tau) + fn(\tau)}$
-as a function of the false positive rate
-$fpr(\tau) = \frac{tn(\tau)}{tn(\tau) + fp(\tau)}$. In section (TODO ref),
-we also compare the same methods with the area under the precision-recall
-(AUPRC) curve, an information retrieval metrics, obtained by varying the threshold
-$\tau$ of the precision $P(\tau) = \frac{tp(\tau)}{tp(\tau) + fp(\tau)}$
-as a function of the recall $R(\tau) = \frac{tp(\tau)}{tp(\tau) + fn(\tau)}$.
-
-\subsection{Data filtering and Signal distribution}
-
-\subsection{Inference of neuronal network}
+\subsection{Data filtering}
+\subsection{Signal distribution}
+\subsection{ROC AUC results}
+\paragraph{Improvement of each stage of our approach\\}
 
@@
 \centering
-\caption{Improvement of each stage of our approach Note that we choose the
-         \textit{best} threshold for stages 1 to 4.}
-\begin{tabular}{*{5}{l}}
-\toprule
-Stage               & normal-1 & normal-2 & normal-3 & normal-4 \\
-\midrule
-Inverse correlation & & & & \\
-Pre-processing      & & & & \\
-PCA                 & & & & \\
-Weighting           & & & & \\
-Averaging           & & & & \\
-\bottomrule
+\begin{tabular}{|c|c||c|c|c|c|c|c|} \hline
+\# & Stage & normal-1 & normal-2 & normal-3 & normal-4 \\ \hline
+1 & Inverse correlation & & & & \\ \hline
+2 & Pre-processing & & & &\\ \hline
+3 & PCA & & & &  \\ \hline
+4 & Weighting & & & &  \\ \hline
+5 & Averaging & & & &  \\ \hline
+
 \end{tabular}
@@
 
+Note that we choose the \textit{best} threshold for stages 1 to 4.
+\paragraph{Comparison with other methods\\}
+
 \begin{table}[htb]
 \centering
-\caption{Comparison with other methods}
-\begin{tabular}{*{5}{l}}
-\toprule
-Methods             & normal-1 & normal-2 & normal-3 & normal-4 \\
-\midrule
-Correlation         & & & & \\
-Partial correlation & & & & \\
-Our approach        & & & & \\
-GENIE3              & & & & \\
-GTE                 & & & & \\
-\bottomrule
+\begin{tabular}{|c|c||c|c|c|c|} \hline
+\# & Stage & normal-1 & normal-2 & normal-3 & normal-4 \\ \hline
+1 & Inverse correlation & & & &\\ \hline
+2 & Correlation & & & &\\ \hline
+3 & GENIE3 & & & & \\ \hline
+4 & GTE & & & & \\ \hline
+
 \end{tabular}
 \end{table}
-
 \subsection{Discussion about the metric}
@@
 % conditional independence test
-% Speak about the complexity and parallelization of the methods
 

### 2014-06-06 article.tex
add comment

--- 2014-06-06 article.tex
@@
 
+\textcolor{red}{AJ: Should we keep the following paragraph? While interesting
+                this might not be relevant for a 6 page abstract.}
 Since only observational data are available, the network recovery is set as an

### 2014-06-06 article.tex
add dot

--- 2014-06-06 article.tex
@@
 \jmlryear{2014}
-\jmlrworkshop{Neural Connectomics Workshop}
+\jmlrworkshop{\textcolor{red}{Neural Connectomics Workshop}}
 
@@
                                calcium imaging using partial correlation and
-                               sample weighting}
+                               sample weighting \textcolor{red}{plus court}}
+
+Simple and robust inference of connectomes using partial correlation coefficients
+
+%% 
+Discovery/Infering/Retrieving/... connectomes 
+Robust
+Using partial correlation
+[from calcium imaging]
+
+\textcolor{red}{Discussion on the order of the partial correlation}
 
@@
  \author{Todo authors}
+
+%% Proposition (sujet à changements : on en discutera):
+% Antonio
+% {Aaron, Arnaud, Vincent} : aucune préférence pour ma part
+% Gilles
+% Damien?
+% Pierre?
 
@@
 the anatomical and functional connectivity of the brain.
-In the context of the Connectomics challenge, we propose a pre-processing and
-a simple approach in order to achieve a high performance inference of the
-connectivity network.
+
+In the context of the Connectomics challenge, we propose a simple 
+algorithm made of four stages to achieve a network inference of high quality.
+
 We put in perspective our method by comparing with other inference method such
 as GTE [], another method proposed to infer a neural network from calcium
-fluorescent imaging, and Genie3 [], a tree-based approach very competitive
-in several gene inference challenge (i.e. DREAM4 and DREAM5).
+fluorescent imaging, and Genie3 [], a tree-based approach very competitive in
+several gene inference challenge (i.e. DREAM4 and DREAM5).\\
 
@@
 
+\textcolor{red}{Motiviation pour l'inverse : retirer les liens indirects} \\
+
 % introduce the notion of dependence / independence
@@
 of mean vector $\mu$ and of covariance matrix $\Sigma$, two neurons $X_i$
-and $X_j$ are independent $X_i \perp X_j$ if they have zero Pearson correlation
+and $X_j$ are independent $X_i \perp X_j$ if the Pearson correlation
 coefficient
 \[
-\rho_{X_iX_j} = \frac{\Sigma_{ij}}{\sqrt{\Sigma_{ii} \Sigma_{jj}}}
+\rho_{X_iX_j} = \frac{\Sigma_{ij}}{\sqrt{\Sigma_{ii} \Sigma_{jj}}} = 0,
 \] 
 and are conditionally independent to all others neurons
-$X_i \perp X_j | X_1,\ldots,X_p \backslash \left\{X_i, X_j\right\}$ if they
-have zero partial correlation coefficient
+$X_i \perp X_j | X_1,\ldots,X_p \backslash \left\{X_i, X_j\right\}$ if the partial correlation coefficient
 \[
 \rho_{X_i, X_j | X_1,\ldots,X_p \backslash \left\{X_i, X_j\right\}} =
-\frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii} \Sigma^{-1}_{jj}}}.
+\frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii} \Sigma^{-1}_{jj}}} = 0.
 \]
@@
 conditionally correlated to a hidden variable affecting $B$ (resp. $A$)
-\cite{de2004discovery}.} directly from a symmetric adjacency matrix.
+\cite{de2004discovery}.} from a symmetric adjacency matrix.
 
@@
 \[
-z_{ij} = \sum_{t=1}^n I(X_{t+1,j} - X_{t, i} \in [f_1, f_2]) -  I(X_{t+1,i} - X_{t, j} \in [f_1, f_2])
-\]
+z_{ij} = \sum_{t=1}^n 1(X_{t+1,j} \ge X_{t, i} \in [f_1, f_2]) -  1(X_{t+1,i} \ge X_{t, j} \in [f_1, f_2])
+\] \textcolor{red}{to rewrite}
 where $f_1$ and $f_2$ are parameters of the method and $I$ is the
@@
 \section{Experiments}
+
 % Datasets
@@
 neuronal network \cite{stetter2012model} with $p=1000$ neurons. The networks
-to inferred have around 15000 arcs or a density of $0.15\%$.
+to inferred have around 15000 arcs or a density of $0.15\%$ and are similar to those
+used to rank challenge participants.
+
+Note that our parameter tuning was mainly on \textit{normal-1} dataset and
+partly on \textit{normal-4} dataset, therefore it may justify why these
+networks are better retrieved despite the fact that some might be simpler to
+infer.
 
@@
 % Speak about the complexity and parallelization of the methods
+
 \begin{scriptsize}
-\paragraph{Acknowledgements.} A. Joly and G. Louppes are research
-fellows of the FNRS, Belgium.  A. Sutera is supported by a F.R.I.A. scholarship.
-This work is supported by PASCAL2 and the IUAP
-DYSCO, initiated by the Belgian State, Science Policy Office.
-Computational ressources have been provided by the Consortium des Équipements
-de Calcul Intensif (CÉCI), funded by the Fonds de la Recherche Scientifique de
-Belgique (F.R.S.-FNRS) under Grant No. 2.5020.11
+
+\paragraph{Acknowledgements.} A. Joly and G. Louppe are research fellows of
+the FNRS, Belgium. We also thank Damien for pizzas.  A. Sutera is supported by
+a F.R.I.A. scholarship.
+
 \end{scriptsize}

### 2014-06-06 article.tex
fix to compil

@@
                                calcium imaging using partial correlation and
-                               sample weighting \textcolor{red}{plus court}}
+                               sample weighting \textcolor{red}{plus court} : Simple and robust inference of connectomes using partial correlation coefficients
+?}
 
-Simple and robust inference of connectomes using partial correlation coefficients
-
-%% 
-Discovery/Infering/Retrieving/... connectomes 
-Robust
-Using partial correlation
-[from calcium imaging]
-
-\textcolor{red}{Discussion on the order of the partial correlation}
+% %% 
+% Discovery/Infering/Retrieving/... connectomes 
+% Robust
+% Using partial correlation
+% [from calcium imaging]
 
@@
 % Discussion on the metrics?
+%\textcolor{red}{Discussion on the order of the partial correlation}
 

### 2014-06-09 article.tex
an intuitive version of the preprocessing

@@
 \usepackage{enumerate}
+\usepackage{bbold}
 
@@
 
-\title[Connectomics challenge]{Inferring neural networks from fluorescent
-                               calcium imaging using partial correlation and
-                               sample weighting \textcolor{red}{plus court} : Simple and robust inference of connectomes using partial correlation coefficients
-?}
+% \title[Connectomics challenge]{Inferring neural networks from fluorescent
+%                                calcium imaging using partial correlation and
+%                                sample weighting \textcolor{red}{plus court} : Simple and robust inference of connectomes using partial correlation coefficients
+% ?}
+
+\title[Inference of connectomes using partial correlation coefficients]{Simple and robust inference of connectomes using partial correlation coefficients}
 
@@
 Retrieving the connectomes, neurons connectivity map, will shed new lights on
-the anatomical and functional connectivity of the brain.
-
+the anatomical and functional connectivity of the brain.\\
 In the context of the Connectomics challenge, we propose a simple 
-algorithm made of four stages to achieve a network inference of high quality.
-
+algorithm made of four stages, using preprocessing and partial correlation to achieve a network inference of high quality.\\
 We put in perspective our method by comparing with other inference method such
-as GTE [], another method proposed to infer a neural network from calcium
+as GTE \cite{stetter2012model}, another method proposed to infer a neural network from calcium
 fluorescent imaging, and Genie3 [], a tree-based approach very competitive in
@@
 source code of the method is available at
-\url{https://github.com/asutera/kaggle-connectomics} under BSD 3-clauses
+\url{https://github.com/asutera/kaggle-connectomics}  BSD 3-clauses
 license.
@@
 % TODO
+
+\textcolor{red}{AS: Après avoir discuté avec Gilles, une autre façon de présenter les choses qui est moins rigoureuse que l'approche de AJ mais plus "motivée"}
+
+% Information in burst not in value --> filtering with hard-threshold
+% Considering the average delay between two neurons, low frequency event can be neglected --> high-pass filter
+% Condidering noise, high frequency event can be neglected --> low-pass filter
+
+%\paragraph{Motivation\\}
+Intuitively, connectivity information between two neurons may be retrieved from successive and slightly delayed burst events.
+In case of a directed relationship, the burst order should be the same while in case of an undirected relationship, it could change.
+Therefore, the fluorescent signal can be reduced to a binary signal representing the activity of a neuron.
+This is the idea behind the filter $g_1$:
+\begin{align}
+g_1(X^i_t) = (X^i_t)^{0.9} \mathbb{1}(X^i_t \ge h)
+\end{align}
+where ... .
+
+Considering the short delay for a communication between neurons, slow events can be neglected to retrieve direct relationships.
+Note that the average time delay is about $1ms$ or $2ms$ while the fluorescent signal time resolution is $20ms$.
+Let us also highlight that even if two neurons are spatially far from each other, the information is expected in the same time step or at most in the next time step.
+It is therefore not necessary to keep low-frequency event and we thus apply a high-pass filter $g_2$:
+\begin{align}
+g_2(X^i_t) = \sum_{l=-3}^{2} c^k_l X^i_{t+l} 
+\end{align}
+where ... .
+
+However, the signal, by the imaging capture process we suppose, is very noisy.
+A low-pass filter seems a good way to smooth the signal and only keep relevant informations.
+We thus choose to consider the discrete derivative of the signal $g_3$:
+\begin{align}
+g_3(X_t^i) = X^i_t - X^i_{t-1}
+\end{align}
+where ... .
+
+We thus define our preprocessing function $g$ as 
+\begin{align}
+g(X_t^i) = g_1(g_3(g_2(X_t^i))).
+\end{align}
+
+Then we apply a non-linear filter based on the current activity of the systems in order to favor the association measure when a medium size set of neurons are firing together, while artificially reducing the association measure when the activity is extremely high, i.e.
+in case of a network burst.
+
+\begin{align}
+g_4(X_t^i) = (X_t^i + 1)^{\left( 1 + \dfrac{1}{a_t} \right)} &\text{ with } a_t = \sum_{i=1}^p \left ( X_t^i + \dfrac{1}{2} X_{t-1}^i \right ) \\
+g_5(X_t^i) = (X_t^i)^{h(r_t)} &\text{ with } r_t = \frac{a_t}{\max_{l \in T}{a_l}} \\
+\end{align}
+
+where $h(x)$ is a 4-piecewise continuous functions whose parameters were tuned for each low-pass filter.
+
+\hrule
 
@@
 for each set of coefficient $\left\{c_l^k\right\}$.
+\hrule
 

### 2014-06-09 article.tex
fix the citation

@@
 
-\section{Methodology}
 \section{Signal filtering} \label{sec:filter}
@@
 \textcolor{red}{AS: Après avoir discuté avec Gilles, une autre façon de présenter les choses qui est moins rigoureuse que l'approche de AJ mais plus "motivée"}
+Prior inferring the network, the fluorescent calcium time series are smoothed
+using several linear and non linear filters.
 
@@
 can be formulated as inferring conditional dependences and
-independences.  Even if \textit{independence
+independences.  Even if \textit{correlation
 does no imply causation}[todo cite], it gives insight on the underlying connectivity

### 2014-06-09 article.tex
Some modifs to the proposition of alternate version + Alternate version of inference process. Note: Both versions should be merged.

@@
 
-\textcolor{red}{AS: Après avoir discuté avec Gilles, une autre façon de présenter les choses qui est moins rigoureuse que l'approche de AJ mais plus "motivée"}
-Prior inferring the network, the fluorescent calcium time series are smoothed
-using several linear and non linear filters.
+\textcolor{red}{AS: Après avoir discuté avec Gilles, une autre façon de
+présenter les choses qui est moins rigoureuse que l'approche de AJ mais plus
+"motivée" --> Certains aspects pourraient être incorporés dans la version de AJ.}
+
+Prior inferring the network, the fluorescent calcium time series
+are smoothed using several linear and non linear filters.
 
@@
 
-%\paragraph{Motivation\\}
-Intuitively, connectivity information between two neurons may be retrieved from successive and slightly delayed burst events.
-In case of a directed relationship, the burst order should be the same while in case of an undirected relationship, it could change.
-Therefore, the fluorescent signal can be reduced to a binary signal representing the activity of a neuron.
-This is the idea behind the filter $g_1$:
-\begin{align}
-g_1(X^i_t) = (X^i_t)^{0.9} \mathbb{1}(X^i_t \ge h)
-\end{align}
-where ... .
+%\paragraph{Motivation\\} Intuitively, connectivity information between two
+neurons may be retrieved from successive and slightly delayed burst events. In
+case of a directed relationship, the burst order should be the same while in
+case of an undirected relationship, it could change. Therefore, the
+fluorescent signal can be reduced to a binary signal representing the activity
+of a neuron. This is the idea behind the filter $g_1$:  \begin{align}
+g_1(X^i_t) = (X^i_t)^{0.9} \mathbb{1}(X^i_t \ge h) \end{align} where ... .
 
-Considering the short delay for a communication between neurons, slow events can be neglected to retrieve direct relationships.
-Note that the average time delay is about $1ms$ or $2ms$ while the fluorescent signal time resolution is $20ms$.
-Let us also highlight that even if two neurons are spatially far from each other, the information is expected in the same time step or at most in the next time step.
-It is therefore not necessary to keep low-frequency event and we thus apply a high-pass filter $g_2$:
-\begin{align}
-g_2(X^i_t) = \sum_{l=-3}^{2} c^k_l X^i_{t+l} 
-\end{align}
-where ... .
+Considering the short delay for a communication between neurons, slow events
+can be neglected to retrieve direct relationships. Note that the average time
+delay is about $1ms$ or $2ms$ while the fluorescent signal time resolution is
+$20ms$. Let us also highlight that even if two neurons are spatially far from
+each other, the information is expected in the same time step or at most in
+the next time step. It is therefore not necessary to keep low-frequency event
+and we thus apply a high-pass filter $g_2$: \begin{align} g_2(X^i_t) =
+\sum_{l=-3}^{2} c^k_l X^i_{t+l}  \end{align} where ... .
 
 However, the signal, by the imaging capture process we suppose, is very noisy.
-A low-pass filter seems a good way to smooth the signal and only keep relevant informations.
-We thus choose to consider the discrete derivative of the signal $g_3$:
-\begin{align}
-g_3(X_t^i) = X^i_t - X^i_{t-1}
-\end{align}
-where ... .
+A low-pass filter seems a good way to smooth the signal and only keep relevant
+informations. We thus choose to consider the discrete derivative of the signal
+$g_3$: \begin{align} g_3(X_t^i) = X^i_t - X^i_{t-1} \end{align} where ... .
 
-We thus define our preprocessing function $g$ as 
-\begin{align}
-g(X_t^i) = g_1(g_3(g_2(X_t^i))).
-\end{align}
-
-Then we apply a non-linear filter based on the current activity of the systems in order to favor the association measure when a medium size set of neurons are firing together, while artificially reducing the association measure when the activity is extremely high, i.e.
-in case of a network burst.
+Then we apply a non-linear filter based on the current activity of the systems
+in order to favor the association measure when a medium size set of neurons
+are firing together, while artificially reducing the association measure when
+the activity is extremely high, i.e. in case of a network burst.
 
@@
 
-where $h(x)$ is a 4-piecewise continuous functions whose parameters were tuned for each low-pass filter.
+where $h(x)$ is a 4-piecewise continuous functions whose parameters were tuned
+for each low-pass filter.
 
+Hence, we define our preprocessing function $G$ as 
+\begin{align}
+G(X_t^i) = g_5 \bullet g_4 \bullet g_1 \bullet g_3 \bullet g_2(X_t^i).
+\end{align}
+
+\vspace{1em}
 \hrule
+\vspace{1em}
 
@@
 
-\textcolor{red}{Motiviation pour l'inverse : retirer les liens indirects} \\
+\textcolor{red}{Motivation pour l'inverse : retirer les liens indirects. Pareil: proposition de AS  et certains choses pourraient être incorporées dans la version de AJ.} \\
+
+From a probabilistic point of view, the inference of the undirected network
+can be formulated as inferring conditional dependences and independences. Even
+if \textit{correlation does no imply causation}[todo cite], it gives insight
+on the underlying connectivity network.
+
+Let us consider see neurons as random variables $\mathcal{X}_i$ which follows
+a probability density function $p_{\mathcal{X}_i}$ and let us denote by
+$p_{\mathcal{X}_i,\mathcal{X}_j|\mathcal{Z}}$ the joint probability
+distribution between neurons $i$ and $j$ conditioned on a subset of neurons
+$\mathcal{Z}$ (eventually empty). Let us define $\mathcal{V}$ the set of all
+neurons $\mathcal{X}_1, \dots, \mathcal{X}_p$, and by $\mathcal{V}^{i,j}$ the
+same set without neurons $\mathcal{X}_i$ and $\mathcal{X}_j$.
+
+ First, if we want to highlight
+relationships between without considering the distinction between direct and
+indirect links, the Pearson correlation matrix, i.e. each element $(i,j)$ of a
+such matrix is the correlation coefficient between neurons $\mathcal{X}_i$ and $\mathcal{X}_j$.
+
+However the connectivity network to infer is only made of direct relationships
+which can be defined as a relation between neurons that still exists when
+conditioned on all other neurons or, in other words, there is not intermediary
+between those two neurons. 
+Under the hypothesis that neurons follow a jointly Gaussian distribution $p_{\mathcal{X}_1, \dots, \mathcal{X}_p} \sim \mathcal{N}(\mu; \Sigma)$, two neurons $\mathcal{X}_i$ and $\mathcal{X}_j$ are independent $\mathcal{X}_i\perp \mathcal{X}_j$ if the Pearson correlation coefficient $\rho_{X_iX_j} = \frac{\Sigma_{ij}}{\sqrt{\Sigma_{ii} \Sigma_{jj}}} = 0,$
+and are conditionally independant to all others neurons $\mathcal{X}_i \perp \mathcal{X}_j |\mathcal{V}^{i,j}$ if the partial correlation coefficient (of order $p-2$) $\rho_{X_i, X_j | \mathcal{V}^{i,j}} =
+\frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii} \Sigma^{-1}_{jj}}} = 0.$ 
+Therefore, by definition, the partial correlation coefficient between two neurons only estimates the direct relationship between them.
+
+In previous study \cite{shipley2002cause}, it has been suggested to
+consider correlation coefficients of all possible orders,
+i.e. conditioned on every subsets of the set of $p-2$ other variables. This
+would take into account multiple indirect paths between a given pair of
+variables. An obvious limitation to estimate correctly high-order coefficients
+is the number of samples. However given the high number of samples $n$
+in the Connectomics challenge, we only consider the highest order of partial
+correlation coefficient.
+
+\vspace{1em}
+\hrule
+\vspace{1em}
 

### 2014-06-09 article.tex
Fix stacking notation

@@
 of a neuron. This is the idea behind the filter $g_1$:  \begin{align}
-g_1(X^i_t) = (X^i_t)^{0.9} \mathbb{1}(X^i_t \ge h) \end{align} where ... .
+g_1^q(X^i_t) = (X^i_t)^{0.9} \mathbb{1}(X^i_t \ge q) \end{align} where ... .
 
@@
 the next time step. It is therefore not necessary to keep low-frequency event
-and we thus apply a high-pass filter $g_2$: \begin{align} g_2(X^i_t) =
+and we thus apply a high-pass filter $g_2$: \begin{align} g_2^k(X^i_t) =
 \sum_{l=-3}^{2} c^k_l X^i_{t+l}  \end{align} where ... .
@@
 
+% We then define our preprocessing function $G$ as
+% \begin{align}
+% G(X_t^i) = g^q_1(g_3(g_2(X_t^i))).
+% \end{align}
+
 Then we apply a non-linear filter based on the current activity of the systems
@@
 \begin{align}
-g_4(X_t^i) = (X_t^i + 1)^{\left( 1 + \dfrac{1}{a_t} \right)} &\text{ with } a_t = \sum_{i=1}^p \left ( X_t^i + \dfrac{1}{2} X_{t-1}^i \right ) \\
-g_5(X_t^i) = (X_t^i)^{h(r_t)} &\text{ with } r_t = \frac{a_t}{\max_{l \in T}{a_l}} \\
+h_1(X_t^i) = (X_t^i + 1)^{\left( 1 + \dfrac{1}{a_t} \right)} &\text{ with } a_t = \sum_{i=1}^p \left ( X_t^i + \dfrac{1}{2} X_{t-1}^i \right ) \\
+h_2(X_t^i) = (X_t^i)^{r(a_t)} &\text{ with } r_t = \frac{a_t}{\max_{l \in T}{a_l}} \\
 \end{align}
 
-where $h(x)$ is a 4-piecewise continuous functions whose parameters were tuned
+where $r(x)$ is a 4-piecewise continuous functions whose parameters were tuned
 for each low-pass filter.
+
+% Hence, we define our preprocessing function $H$ as 
+% \begin{align}
+% H(X_t^i) = h_2 \bullet h_1 \bullet G(X).
+% \end{align}
 
@@
 \begin{align}
-G(X_t^i) = g_5 \bullet g_4 \bullet g_1 \bullet g_3 \bullet g_2(X_t^i).
+G^{q,k}(X_t^i) = h_2 \bullet h_1 \bullet g^q_1 \bullet g_3 \bullet g_2^k(X_t^i).
 \end{align}
+
+Finally since there is a high correlation between neurons, we made a
+low-rank hypothesis and perform noise filtering through a principal component
+approach [TODO cite]. From the $p$ eigen vectors, we only kept $80\%$ of
+the eigen vectors which have the largest eigen value.
 
@@
 for each set of coefficient $\left\{c_l^k\right\}$.
-\hrule
 
@@
 \begin{align}
-y_{stack} =  \dfrac{1}{\sum_{k\in\{1,..,4\}} w_k |T_k|} \sum_{k=1}^{k=4}  w_k \sum_{f_3 \in T_k} f(X, k, f_3)
+y_{stack} =  \dfrac{1}{\sum_{k\in\{1,..,4\}} w_k |T_k|} \sum_{k=1}^{k=4}  w_k \sum_{q \in T_k} G^{q,k}(X_t^i)
 \end{align}

### 2014-06-09 article.tex
fix causal notation
break at 80

@@
 
-\begin{abstract}
-Understanding how the brain works is a key to understand and to treat
-brain pathologies and disorders such as Parkinson's disease, epilepsy.
-Retrieving the connectomes, neurons connectivity map, will shed new lights on
-the anatomical and functional connectivity of the brain.\\
-In the context of the Connectomics challenge, we propose a simple 
-algorithm made of four stages, using preprocessing and partial correlation to achieve a network inference of high quality.\\
-We put in perspective our method by comparing with other inference method such
-as GTE \cite{stetter2012model}, another method proposed to infer a neural network from calcium
-fluorescent imaging, and Genie3 [], a tree-based approach very competitive in
-several gene inference challenge (i.e. DREAM4 and DREAM5).\\
+\begin{abstract} Understanding how the brain works is a key to understand and
+to treat brain pathologies and disorders such as Parkinson's disease,
+epilepsy. Retrieving the connectomes, neurons connectivity map, will shed new
+lights on the anatomical and functional connectivity of the brain.\\ In the
+context of the Connectomics challenge, we propose a simple  algorithm made of
+four stages, using preprocessing and partial correlation to achieve a network
+inference of high quality.\\ We put in perspective our method by comparing
+with other inference method such as GTE \cite{stetter2012model}, another
+method proposed to infer a neural network from calcium fluorescent imaging,
+and Genie3 [], a tree-based approach very competitive in several gene
+inference challenge (i.e. DREAM4 and DREAM5).\\
 
@@
 are firing together, while artificially reducing the association measure when
-the activity is extremely high, i.e. in case of a network burst.
-
-\begin{align}
-h_1(X_t^i) = (X_t^i + 1)^{\left( 1 + \dfrac{1}{a_t} \right)} &\text{ with } a_t = \sum_{i=1}^p \left ( X_t^i + \dfrac{1}{2} X_{t-1}^i \right ) \\
-h_2(X_t^i) = (X_t^i)^{r(a_t)} &\text{ with } r_t = \frac{a_t}{\max_{l \in T}{a_l}} \\
-\end{align}
+the activity is extremely high, i.e. in case of a network burst. \begin{align}
+h_1(X_t^i) = (X_t^i + 1)^{\left( 1 + \dfrac{1}{a_t} \right)} &\text{ with }
+a_t = \sum_{i=1}^p \left ( X_t^i + \dfrac{1}{2} X_{t-1}^i \right ) \\
+h_2(X_t^i) = (X_t^i)^{r(a_t)} &\text{ with } r_t = \frac{a_t}{\max_{l \in
+T}{a_l}}  \end{align}
 
@@
 
-% Filtering methodology
-Prior inferring the network, the fluorescent calcium time series are smoothed
-using several linear and non linear filters. A low-pass filter, a high-pass
-filter and a non linear hard-thresholding based filter are
-applied for each possible time step $t$
-% TODO fix first equation is wrong due notation change
-\begin{align}
-X^\prime_{t,i} &= \sum_{l=-3}^2 c_l^k X_{t+l,i} \forall i, \\
-X^{\prime\prime}_{t,i} &= X^{\prime}_{t,i} - X^{\prime}_{t-1,i} \forall i, \\
-X^{\prime\prime\prime}_{t,i} &= {X^{\prime\prime}_{t,i}}^{0.9} I(X^{\prime\prime}_{t,i} \geq f_3) \forall i,
-\end{align}
-where the $c_l^k$ coefficients were taken in one of the four following tuples
-$\left\{c_l^1\right\}=(0, 0, 1, 1, 1, 1)$,
-$\left\{c_l^2\right\}=(0, 0, 1, 1, 1, 0)$,
-$\left\{c_l^3\right\}=(1, 1, 1, 1, 0, 0)$ or
-$\left\{c_l^4\right\}=(0.4, 0.8, 1, 1, 0, 0)$ and $f_3$ is a parameter
-of the hard-threshold filter.
+% Filtering methodology Prior inferring the network, the fluorescent calcium
+time series are smoothed using several linear and non linear filters. A low-
+pass filter, a high-pass filter and a non linear hard-thresholding based
+filter are applied for each possible time step $t$ % TODO fix first equation
+is wrong due notation change \begin{align} X^\prime_{t,i} &= \sum_{l=-3}^2
+c_l^k X_{t+l,i} \forall i, \\ X^{\prime\prime}_{t,i} &= X^{\prime}_{t,i} -
+X^{\prime}_{t-1,i} \forall i, \\ X^{\prime\prime\prime}_{t,i} &=
+{X^{\prime\prime}_{t,i}}^{0.9} I(X^{\prime\prime}_{t,i} \geq f_3) \forall i,
+\end{align} where the $c_l^k$ coefficients were taken in one of the four
+following tuples $\left\{c_l^1\right\}=(0, 0, 1, 1, 1, 1)$,
+$\left\{c_l^2\right\}=(0, 0, 1, 1, 1, 0)$, $\left\{c_l^3\right\}=(1, 1, 1, 1,
+0, 0)$ or $\left\{c_l^4\right\}=(0.4, 0.8, 1, 1, 0, 0)$ and $f_3$ is a
+parameter of the hard-threshold filter.
 
@@
 
-\textcolor{red}{Motivation pour l'inverse : retirer les liens indirects. Pareil: proposition de AS  et certains choses pourraient être incorporées dans la version de AJ.} \\
+\textcolor{red}{Motivation pour l'inverse : retirer les liens indirects.
+\Pareil: proposition de AS  et certains choses pourraient être incorporées
+\dans la version de AJ.}
 
@@
 conditioned on all other neurons or, in other words, there is not intermediary
-between those two neurons. 
-Under the hypothesis that neurons follow a jointly Gaussian distribution $p_{\mathcal{X}_1, \dots, \mathcal{X}_p} \sim \mathcal{N}(\mu; \Sigma)$, two neurons $\mathcal{X}_i$ and $\mathcal{X}_j$ are independent $\mathcal{X}_i\perp \mathcal{X}_j$ if the Pearson correlation coefficient $\rho_{X_iX_j} = \frac{\Sigma_{ij}}{\sqrt{\Sigma_{ii} \Sigma_{jj}}} = 0,$
-and are conditionally independant to all others neurons $\mathcal{X}_i \perp \mathcal{X}_j |\mathcal{V}^{i,j}$ if the partial correlation coefficient (of order $p-2$) $\rho_{X_i, X_j | \mathcal{V}^{i,j}} =
-\frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii} \Sigma^{-1}_{jj}}} = 0.$ 
-Therefore, by definition, the partial correlation coefficient between two neurons only estimates the direct relationship between them.
+between those two neurons.  Under the hypothesis that neurons follow a jointly
+Gaussian distribution $p_{\mathcal{X}_1, \dots, \mathcal{X}_p} \sim
+\mathcal{N}(\mu; \Sigma)$, two neurons $\mathcal{X}_i$ and $\mathcal{X}_j$ are
+independent $\mathcal{X}_i\perp \mathcal{X}_j$ if the Pearson correlation
+coefficient $\rho_{X_iX_j} = \frac{\Sigma_{ij}}{\sqrt{\Sigma_{ii}
+\Sigma_{jj}}} = 0,$ and are conditionally independant to all others neurons
+$\mathcal{X}_i \perp \mathcal{X}_j |\mathcal{V}^{i,j}$ if the partial
+correlation coefficient (of order $p-2$) $\rho_{X_i, X_j | \mathcal{V}^{i,j}}
+= \frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii} \Sigma^{-1}_{jj}}} = 0.$
+Therefore, by definition, the partial correlation coefficient between two
+neurons only estimates the direct relationship between them.
 
@@
 
-Let us consider that each neuron signal $i$ is a random continuous variable $X_i$
-which follows a probability distribution $p_{X_i}$ and let us denote by $p_{X_i,X_j|\mathcal{Z}}$ the 
-joint probability distribution of neurons $X_i$ and $X_j$ conditioned on a subset of variables $\mathcal{Z}$ (eventually empty). Let us define $\mathcal{V}$
-the set of all neurons $X_1, ..., X_p$ and $\mathcal{V}^{-i,j}$ the same set without
-neurons $X_i$ and $X_j$.
+Let us consider that each neuron signal $i$ is a random continuous variable
+$X_i$ which follows a probability distribution $p_{X_i}$ and let us denote by
+$p_{X_i,X_j|\mathcal{Z}}$ the  joint probability distribution of neurons $X_i$
+and $X_j$ conditioned on a subset of variables $\mathcal{Z}$ (eventually
+empty). Let us define $\mathcal{V}$ the set of all neurons $X_1, ..., X_p$ and
+$\mathcal{V}^{-i,j}$ the same set without neurons $X_i$ and $X_j$.
 
-Each neuron signal $i$ is a random continuous variable $X_i$,
-which follows a probability density function $p_\mathcal{X_i}(x_i)$.
-Two neurons $X_i$, $X_j$ will be said conditionally independent
-to a set of neurons $\mathcal{V}^{-i,j}$, denoted
-by  $X_i \perp X_j | \mathcal{V}^{-i,j}$,  if $p_{X_i,X_j|\mathcal{V}^{-i,j}} = p_{X_i|\mathcal{V}^{-i,j}}  p_{X_j|\mathcal{V}^{-i,j}} $.
+Each neuron signal $i$ is a random continuous variable $X_i$, which follows a
+probability density function $p_\mathcal{X_i}(x_i)$. Two neurons $X_i$, $X_j$
+will be said conditionally independent to a set of neurons
+$\mathcal{V}^{-i,j}$, denoted by  $X_i \perp X_j | \mathcal{V}^{-i,j}$,  if
+$p_{X_i,X_j|\mathcal{V}^{-i,j}} = p_{X_i|\mathcal{V}^{-i,j}}
+p_{X_j|\mathcal{V}^{-i,j}} $.
+
 %for all real numbers $x_1,\ldots,x_p $ such that
@@
 Under the hypothesis that the neurons follow a jointly Gaussian distribution
-$p_{X_1,\ldots,X_p}(x_1,\ldots,x_p) \sim \mathcal{N}(\mu; \Sigma)$
-of mean vector $\mu$ and of covariance matrix $\Sigma$, two neurons $X_i$
-and $X_j$ are independent $X_i \perp X_j$ if the Pearson correlation
-coefficient
-\[
-\rho_{X_iX_j} = \frac{\Sigma_{ij}}{\sqrt{\Sigma_{ii} \Sigma_{jj}}} = 0,
-\] 
-and are conditionally independent to all others neurons
-$X_i \perp X_j | X_1,\ldots,X_p \backslash \left\{X_i, X_j\right\}$ if the partial correlation coefficient
-\[
-\rho_{X_i, X_j | X_1,\ldots,X_p \backslash \left\{X_i, X_j\right\}} =
-\frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii} \Sigma^{-1}_{jj}}} = 0.
-\]
+$p_{X_1,\ldots,X_p}(x_1,\ldots,x_p) \sim \mathcal{N}(\mu; \Sigma)$ of mean
+vector $\mu$ and of covariance matrix $\Sigma$, two neurons $X_i$ and $X_j$
+are independent $X_i \perp X_j$ if the Pearson correlation coefficient \[
+\rho_{X_iX_j} = \frac{\Sigma_{ij}}{\sqrt{\Sigma_{ii} \Sigma_{jj}}} = 0, \]
+and are conditionally independent to all others neurons $X_i \perp X_j |
+X_1,\ldots,X_p \backslash \left\{X_i, X_j\right\}$ if the partial correlation
+coefficient \[ \rho_{X_i, X_j | X_1,\ldots,X_p \backslash \left\{X_i,
+X_j\right\}} = \frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii}
+\Sigma^{-1}_{jj}}} = 0. \]
 
@@
 
-By ignoring the directivity, we systematically
-make a true positive and a false positive for direct link (see a more detailed
-discussion about the chosen metric in section \ref{sec:metric}). Therefore,
-performance might be improved by predicting an asymmetric adjacency matrix.
-Hoping to orientate correctly the most obvious directed links, we attempt to
-retrieve some causal information, i.e. the directivity of the links, by computing
-and stacking with our symmetric adjacency matrix a matrix of pairwise activation
-heuristics. This method computes an anti-symmetric activation score $z_{ij}$
-based the variation of fluorescence signal of a neuron $j$ due to a neuron $i$
-over all timesteps:
-\[
-z_{ij} = \sum_{t=1}^n 1(X_{t+1,j} \ge X_{t, i} \in [f_1, f_2]) -  1(X_{t+1,i} \ge X_{t, j} \in [f_1, f_2])
-\] \textcolor{red}{to rewrite}
-where $f_1$ and $f_2$ are parameters of the method and $I$ is the
-indicator function. % TODO say that we use only the 3 first filters for this
+By ignoring the directivity, we systematically make a true positive and a
+false positive for direct link (see a more detailed discussion about the
+chosen metric in section \ref{sec:metric}). Therefore, performance might be
+improved by predicting an asymmetric adjacency matrix. Hoping to orientate
+correctly the most obvious directed links, we attempt to retrieve some causal
+information, i.e. the directivity of the links, by computing and stacking with
+our symmetric adjacency matrix a matrix of pairwise activation heuristics.
+This method computes an anti-symmetric activation score $z_{ij}$ based the
+variation of fluorescence signal of a neuron $j$ due to a neuron $i$ over all
+timesteps: \[ z_{ij} = \sum_{t=1}^n \mathbb{1}(X_{t+1,j} \ge X_{t, i}) \cdot
+\mathbb{1}(f_1\le X_t^i \le f_2) -  \mathbb{1}(X_{t+1,i} \ge X_{t, j}) \cdot
+\mathbb{1}(f_1 \le X_t^j \le f_2) \]  where $f_1$ and $f_2$ are parameters of
+the method and $I$ is the indicator function. % TODO say that we use only the
+3 first filters for this
 

### 2014-06-10 article.tex
FIX compilation
some small changes

@@
 
-%\paragraph{Motivation\\} Intuitively, connectivity information between two
+%\paragraph{Motivation\\} 
+Intuitively, connectivity information between two
 neurons may be retrieved from successive and slightly delayed burst events. In
 case of a directed relationship, the burst order should be the same while in
-case of an undirected relationship, it could change. Therefore, the
+case of an undirected relationship, it might change. Therefore, the
 fluorescent signal can be reduced to a binary signal representing the activity
@@
 the next time step. It is therefore not necessary to keep low-frequency event
-and we thus apply a high-pass filter $g_2$: \begin{align} g_2^k(X^i_t) =
-\sum_{l=-3}^{2} c^k_l X^i_{t+l}  \end{align} where ... .
+and we thus choose to consider the discrete derivative of the signal, i.e. a
+high-pass filtered version, $g_2$:  \begin{align} g_2(X_t^i) = X^i_t -
+X^i_{t-1} \end{align} where ... .
 
@@
 A low-pass filter seems a good way to smooth the signal and only keep relevant
-informations. We thus choose to consider the discrete derivative of the signal
-$g_3$: \begin{align} g_3(X_t^i) = X^i_t - X^i_{t-1} \end{align} where ... .
-
+informations. We thus apply the filter
+$g_3$: 
+\begin{align} g_3^k(X^i_t) =
+\sum_{l=-3}^{2} c^k_l X^i_{t+l}  \end{align} where ... .
 % We then define our preprocessing function $G$ as
@@
 
-where $r(x)$ is a 4-piecewise continuous functions whose parameters were tuned
+\textcolor{red}{miss the case where activity < 0->1} where $r(x)$ is a 4-piecewise continuous functions whose parameters were tuned
 for each low-pass filter.
@@
 \begin{align}
-G^{q,k}(X_t^i) = h_2 \bullet h_1 \bullet g^q_1 \bullet g_3 \bullet g_2^k(X_t^i).
+G^{q,k}(X_t^i) = h_2 \bullet h_1 \bullet g^q_1 \bullet g_2 \bullet g_3^k(X_t^i).
 \end{align}
@@
 approach [TODO cite]. From the $p$ eigen vectors, we only kept $80\%$ of
-the eigen vectors which have the largest eigen value.
+the eigen vectors which have the largest eigen value \textcolor{red}{fig?}.
 
@@
 
-% Filtering methodology Prior inferring the network, the fluorescent calcium
+% Filtering methodology 
+Prior inferring the network, the fluorescent calcium
 time series are smoothed using several linear and non linear filters. A low-
@@
 \textcolor{red}{Motivation pour l'inverse : retirer les liens indirects.
-\Pareil: proposition de AS  et certains choses pourraient être incorporées
-\dans la version de AJ.}
+Pareil: proposition de AS  et certains choses pourraient être incorporées
+dans la version de AJ.}
 
@@
 
-Let us consider see neurons as random variables $\mathcal{X}_i$ which follows
+Let us consider the neurons as random variables $\mathcal{X}_i$ which follows
 a probability density function $p_{\mathcal{X}_i}$ and let us denote by
@@
 
- First, if we want to highlight
-relationships between without considering the distinction between direct and
-indirect links, the Pearson correlation matrix, i.e. each element $(i,j)$ of a
-such matrix is the correlation coefficient between neurons $\mathcal{X}_i$ and $\mathcal{X}_j$.
+% Without considering indirect/direct --> Correlation matrix
+
+First, if we want to highlight relationships between neurons without
+considering the distinction between direct and indirect links, the Pearson
+correlation matrix, i.e. each element $(i,j)$ of a such matrix is the
+correlation coefficient between neurons $\mathcal{X}_i$ and $\mathcal{X}_j$, can computed.
+
+% However, we only want direct links --> partial correlation
 

### 2014-06-10 article.tex
merge both version of filtering

@@
 \section{Signal filtering} \label{sec:filter}
+
 % Explain why we need to filter
-% TODO
-
-\textcolor{red}{AS: Après avoir discuté avec Gilles, une autre façon de
-présenter les choses qui est moins rigoureuse que l'approche de AJ mais plus
-"motivée" --> Certains aspects pourraient être incorporés dans la version de AJ.}
 
@@
 are smoothed using several linear and non linear filters.
+Considering the short delay for a communication between neurons, slow events
+can be neglected to retrieve direct relationships. The average time
+delay is indeed about $1ms$ or $2ms$ while the fluorescent signal time
+resolution is $20ms$. Let us also highlight that even if two neurons are
+spatially far from each other, the information is expected in the same time
+step or at most in the next time step. Thus very low frequency event can be neglected.
+However, the image fluorescence calcium signal is also very noisy. Thus,
+A low-pass filter (Equation \ref{eq:low-pass}) is first applied followed by a
+high-pass filter (Equation \ref{eq:high-pass}), the discrete derivative of
+the signal,
+\begin{align}
+X^\prime_{t,i} &= \sum_{l=-3}^2 c_l^k X_{t+l,i} \forall i, \label{eq:low-pass}\\
+X^{\prime\prime}_{t,i} &= X^{\prime}_{t,i} - X^{\prime}_{t-1,i} \forall i, \label{eq:high-pass}
+\end{align}
+where the $c_l^k$ coefficients were taken in one of the four
+following tuples
+$\left(c_l^1\right)_{l=-3}^2=(0, 0, 1, 1, 1, 1)$,
+$\left(c_l^2\right)_{l=-3}^2=(0, 0, 1, 1, 1, 0)$,
+$\left(c_l^3\right)_{l=-3}^2=(1, 1, 1, 1, 0, 0)$ or
+$\left(c_l^4\right)_{l=-3}^2=(0.4, 0.8, 1, 1, 0, 0)$.
 
-% Information in burst not in value --> filtering with hard-threshold
-% Considering the average delay between two neurons, low frequency event can be neglected --> high-pass filter
-% Condidering noise, high frequency event can be neglected --> low-pass filter
-
-%\paragraph{Motivation\\} 
-Intuitively, connectivity information between two
-neurons may be retrieved from successive and slightly delayed burst events. In
-case of a directed relationship, the burst order should be the same while in
-case of an undirected relationship, it might change. Therefore, the
-fluorescent signal can be reduced to a binary signal representing the activity
-of a neuron. This is the idea behind the filter $g_1$:  \begin{align}
-g_1^q(X^i_t) = (X^i_t)^{0.9} \mathbb{1}(X^i_t \ge q) \end{align} where ... .
-
-Considering the short delay for a communication between neurons, slow events
-can be neglected to retrieve direct relationships. Note that the average time
-delay is about $1ms$ or $2ms$ while the fluorescent signal time resolution is
-$20ms$. Let us also highlight that even if two neurons are spatially far from
-each other, the information is expected in the same time step or at most in
-the next time step. It is therefore not necessary to keep low-frequency event
-and we thus choose to consider the discrete derivative of the signal, i.e. a
-high-pass filtered version, $g_2$:  \begin{align} g_2(X_t^i) = X^i_t -
-X^i_{t-1} \end{align} where ... .
-
-However, the signal, by the imaging capture process we suppose, is very noisy.
-A low-pass filter seems a good way to smooth the signal and only keep relevant
-informations. We thus apply the filter
-$g_3$: 
-\begin{align} g_3^k(X^i_t) =
-\sum_{l=-3}^{2} c^k_l X^i_{t+l}  \end{align} where ... .
-% We then define our preprocessing function $G$ as
-% \begin{align}
-% G(X_t^i) = g^q_1(g_3(g_2(X_t^i))).
-% \end{align}
-
-Then we apply a non-linear filter based on the current activity of the systems
-in order to favor the association measure when a medium size set of neurons
-are firing together, while artificially reducing the association measure when
-the activity is extremely high, i.e. in case of a network burst. \begin{align}
-h_1(X_t^i) = (X_t^i + 1)^{\left( 1 + \dfrac{1}{a_t} \right)} &\text{ with }
-a_t = \sum_{i=1}^p \left ( X_t^i + \dfrac{1}{2} X_{t-1}^i \right ) \\
-h_2(X_t^i) = (X_t^i)^{r(a_t)} &\text{ with } r_t = \frac{a_t}{\max_{l \in
-T}{a_l}}  \end{align}
-
-\textcolor{red}{miss the case where activity < 0->1} where $r(x)$ is a 4-piecewise continuous functions whose parameters were tuned
-for each low-pass filter.
-
-% Hence, we define our preprocessing function $H$ as
-% \begin{align}
-% H(X_t^i) = h_2 \bullet h_1 \bullet G(X).
-% \end{align}
-
-Hence, we define our preprocessing function $G$ as
+Connectivity information between two neurons may be retrieved from successive
+and slightly delayed burst events. At a local level, direct link
+between two neurons will have shorter delay between fluorescence
+peaks than undirected links. However, the fluorescence signal has a slow
+decay compare to its rise. Therefore, we filter those unrelevant information
+with a hard thresholding filter
 \begin{align}
-G^{q,k}(X_t^i) = h_2 \bullet h_1 \bullet g^q_1 \bullet g_2 \bullet g_3^k(X_t^i).
+X^{\prime\prime\prime}_{t,i} &=
+{X^{\prime\prime}_{t,i}}^{0.9} I(X^{\prime\prime}_{t,i} \geq f_3) \forall i
+\label{eq:hard-treshold-filter}
 \end{align}
-
-Finally since there is a high correlation between neurons, we made a
-low-rank hypothesis and perform noise filtering through a principal component
-approach [TODO cite]. From the $p$ eigen vectors, we only kept $80\%$ of
-the eigen vectors which have the largest eigen value \textcolor{red}{fig?}.
-
-\vspace{1em}
-\hrule
-\vspace{1em}
-
-% Filtering methodology 
-Prior inferring the network, the fluorescent calcium
-time series are smoothed using several linear and non linear filters. A low-
-pass filter, a high-pass filter and a non linear hard-thresholding based
-filter are applied for each possible time step $t$ % TODO fix first equation
-is wrong due notation change \begin{align} X^\prime_{t,i} &= \sum_{l=-3}^2
-c_l^k X_{t+l,i} \forall i, \\ X^{\prime\prime}_{t,i} &= X^{\prime}_{t,i} -
-X^{\prime}_{t-1,i} \forall i, \\ X^{\prime\prime\prime}_{t,i} &=
-{X^{\prime\prime}_{t,i}}^{0.9} I(X^{\prime\prime}_{t,i} \geq f_3) \forall i,
-\end{align} where the $c_l^k$ coefficients were taken in one of the four
-following tuples $\left\{c_l^1\right\}=(0, 0, 1, 1, 1, 1)$,
-$\left\{c_l^2\right\}=(0, 0, 1, 1, 1, 0)$, $\left\{c_l^3\right\}=(1, 1, 1, 1,
-0, 0)$ or $\left\{c_l^4\right\}=(0.4, 0.8, 1, 1, 0, 0)$ and $f_3$ is a
-parameter of the hard-threshold filter.
+where $f_3$ is a parameter of the hard-threshold filter and the $0.9$
+exponent reduce the difference between peaks values.
 
@@
 active:
-\begin{align}
-a_t &= \sum_{i=1}^p X^{\prime\prime\prime}_{t,i} +
-                   \frac{1}{2} X^{\prime\prime\prime}_{t-1,i} \forall t \in T\\
-r_t &= \frac{a_t}{\max_{l \in T}{a_l}} \\
-X^{\prime\prime\prime\prime}_{t,i} &=
+\begin{equation}
+X^{\prime\prime\prime\prime}_{t,i} =
 \left\{
@@
 \right.
-\end{align}
+\text{ with }
+\left\{
+  \begin{array}{ll}
+    a_t &= \sum_{i=1}^p X^{\prime\prime\prime}_{t,i} +
+                       \frac{1}{2} X^{\prime\prime\prime}_{t-1,i} \forall t \in T\\
+    r_t &= \frac{a_t}{\max_{l \in T}{a_l}} \\
+  \end{array}
+\right.
+\end{equation}
 where $g(x) = b_1 I(f_4 < x < f_5) + b_2  I(f_5 \leq x < f_6) +
@@
 parameters $b_1, b_2, b_3, f_4, f_5, f_6$. The coefficient were tuned
-for each set of coefficient $\left\{c_l^k\right\}$.
+for each set $i\in\left\{1, 2, 3, 4\right\}$ of coefficient
+$\left(c_l^i\right)_{l=-3}^2$.
 
@@
 approach [TODO cite]. From the $p$ eigen vectors, we only kept $80\%$ of
-the eigen vectors which have the largest eigen value.
+the eigen vectors which have the largest eigen value. In the context of the
+challenge, this assumption was verified on all provided dataset
 

### 2014-06-10 article.tex
smaller abstract (remove \)

@@
 epilepsy. Retrieving the connectomes, neurons connectivity map, will shed new
-lights on the anatomical and functional connectivity of the brain.\\ In the
+lights on the anatomical and functional connectivity of the brain. In the
 context of the Connectomics challenge, we propose a simple  algorithm made of
 four stages, using preprocessing and partial correlation to achieve a network
-inference of high quality.\\ We put in perspective our method by comparing
+inference of high quality. We put in perspective our method by comparing
 with other inference method such as GTE \cite{stetter2012model}, another
@@
 and Genie3 [], a tree-based approach very competitive in several gene
-inference challenge (i.e. DREAM4 and DREAM5).\\
+inference challenge (i.e. DREAM4 and DREAM5).
 

### 2014-06-10 article.tex
remove todo

@@
 low-rank hypothesis and perform noise filtering through a principal component
-approach [TODO cite]. From the $p$ eigen vectors, we only kept $80\%$ of
+approach. From the $p$ eigen vectors, we only kept $80\%$ of
 the eigen vectors which have the largest eigen value. In the context of the

### 2014-06-10 article.tex
Merge both part on partial correlation

@@
 
-\textcolor{red}{Motivation pour l'inverse : retirer les liens indirects.
-Pareil: proposition de AS  et certains choses pourraient être incorporées
-dans la version de AJ.}
-
 From a probabilistic point of view, the inference of the undirected network
@@
 distribution between neurons $i$ and $j$ conditioned on a subset of neurons
-$\mathcal{Z}$ (eventually empty). Let us define $\mathcal{V}$ the set of all
-neurons $\mathcal{X}_1, \dots, \mathcal{X}_p$, and by $\mathcal{V}^{i,j}$ the
+$\mathcal{Z}$ (possibly empty). Two neurons $X_i$, $X_j$
+will be said conditionally independent to a set of neurons
+$\mathcal{Z}$ (possibly empty), denoted by  $X_i \perp X_j | \mathcal{Z}$,  if
+$p_{\mathcal{X}_i,\mathcal{X}_j|\mathcal{Z}} = p_{\mathcal{X}_i|\mathcal{Z}}
+p_{\mathcal{X}_j|\mathcal{Z}}$. The reciprocal is not true without
+additional hypotheses.  Let us define $\mathcal{V}$ the set of all
+neurons $\mathcal{X}_1, \dots, \mathcal{X}_p$, and by $\mathcal{V}^{-i,j}$ the
 same set without neurons $\mathcal{X}_i$ and $\mathcal{X}_j$.
 
-% Without considering indirect/direct --> Correlation matrix
-
-First, if we want to highlight relationships between neurons without
-considering the distinction between direct and indirect links, the Pearson
-correlation matrix, i.e. each element $(i,j)$ of a such matrix is the
-correlation coefficient between neurons $\mathcal{X}_i$ and $\mathcal{X}_j$, can computed.
-
-% However, we only want direct links --> partial correlation
-
-However the connectivity network to infer is only made of direct relationships
-which can be defined as a relation between neurons that still exists when
-conditioned on all other neurons or, in other words, there is not intermediary
+The connectivity network to infer is only made of direct relationships
+which defined relation between neurons that still exists when
+conditioned on all other neurons. In other words, there is not intermediary
 between those two neurons. Under the hypothesis that neurons follow a jointly
@@
 correlation coefficient (of order $p-2$) $\rho_{X_i, X_j | \mathcal{V}^{i,j}}
-= \frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii} \Sigma^{-1}_{jj}}} = 0.$
+= \frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii} \Sigma^{-1}_{jj}}} = 0$,
+where $\Sigma^{-1}_$ is the inverse of the covariance matrix.
 Therefore, by definition, the partial correlation coefficient between two
@@
 In previous study \cite{shipley2002cause}, it has been suggested to
-consider correlation coefficients of all possible orders,
-i.e. conditioned on every subsets of the set of $p-2$ other variables. This
-would take into account multiple indirect paths between a given pair of
-variables. An obvious limitation to estimate correctly high-order coefficients
-is the number of samples. However given the high number of samples $n$
-in the Connectomics challenge, we only consider the highest order of partial
-correlation coefficient.
-
-\vspace{1em}
-\hrule
-\vspace{1em}
-
-% introduce the notion of dependence / independence
-From a probabilistic point of view, the inference of the undirected network
-can be formulated as inferring conditional dependences and
-independences.  Even if \textit{correlation
-does no imply causation}[todo cite], it gives insight on the underlying connectivity
-network. For instance, the graph $A \rightarrow B \rightarrow C$ translates the
-following dependances and independances: $A \not\perp B$, $A \not\perp B | C$,
-$B \not\perp C$, $B \not\perp C | A$, but $A \perp C | B$ and  $A \not\perp C$.
-
-Let us consider that each neuron signal $i$ is a random continuous variable
-$X_i$ which follows a probability distribution $p_{X_i}$ and let us denote by
-$p_{X_i,X_j|\mathcal{Z}}$ the  joint probability distribution of neurons $X_i$
-and $X_j$ conditioned on a subset of variables $\mathcal{Z}$ (eventually
-empty). Let us define $\mathcal{V}$ the set of all neurons $X_1, ..., X_p$ and
-$\mathcal{V}^{-i,j}$ the same set without neurons $X_i$ and $X_j$.
-
-Each neuron signal $i$ is a random continuous variable $X_i$, which follows a
-probability density function $p_\mathcal{X_i}(x_i)$. Two neurons $X_i$, $X_j$
-will be said conditionally independent to a set of neurons
-$\mathcal{V}^{-i,j}$, denoted by  $X_i \perp X_j | \mathcal{V}^{-i,j}$,  if
-$p_{X_i,X_j|\mathcal{V}^{-i,j}} = p_{X_i|\mathcal{V}^{-i,j}}
-p_{X_j|\mathcal{V}^{-i,j}} $.
-
-%for all real numbers $x_1,\ldots,x_p $ such that
-%$p_{X_1,\ldots,X_p \backslash \left\{X_i, X_j\right\}}
-%(x_1,\ldots,x_p \backslash \left\{x_i, x_j\right\}) > 0$. Note that this
-%reciprocal is true only under additional hypotheses.
-
-Under the hypothesis that the neurons follow a jointly Gaussian distribution
-$p_{X_1,\ldots,X_p}(x_1,\ldots,x_p) \sim \mathcal{N}(\mu; \Sigma)$ of mean
-vector $\mu$ and of covariance matrix $\Sigma$, two neurons $X_i$ and $X_j$
-are independent $X_i \perp X_j$ if the Pearson correlation coefficient \[
-\rho_{X_iX_j} = \frac{\Sigma_{ij}}{\sqrt{\Sigma_{ii} \Sigma_{jj}}} = 0, \]
-and are conditionally independent to all others neurons $X_i \perp X_j |
-X_1,\ldots,X_p \backslash \left\{X_i, X_j\right\}$ if the partial correlation
-coefficient \[ \rho_{X_i, X_j | X_1,\ldots,X_p \backslash \left\{X_i,
-X_j\right\}} = \frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii}
-\Sigma^{-1}_{jj}}} = 0. \]
-
-% Correlation => Issue indirect effect
-% Partial correlation => better estimate of the graph  => Symmetric measure
-While the correlation coefficient is unable to distinguish between
-direct and indirect interaction, the partial correlation coefficient
-aims to infer only direct ones through the conditioning over all the other
-variables. In previous study \cite{shipley2002cause}, it has been suggested to
 consider correlation coefficients of all possible orders,

### 2014-06-10 article.tex
make more precision

@@
 the eigen vectors which have the largest eigen value. In the context of the
-challenge, this assumption was verified on all provided dataset
+challenge, this assumption was deduced from ground truth of provided network.
 
@@
 = \frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii} \Sigma^{-1}_{jj}}} = 0$,
-where $\Sigma^{-1}_$ is the inverse of the covariance matrix.
+where $\Sigma^{-1}$ is the inverse of the covariance matrix.
 Therefore, by definition, the partial correlation coefficient between two
@@
 variation of fluorescence signal of a neuron $j$ due to a neuron $i$ over all
-timesteps: \[ z_{ij} = \sum_{t=1}^n \mathbb{1}(X_{t+1,j} \ge X_{t, i}) \cdot
+timesteps:
+\[
+z_{ij} = \sum_{t=1}^n \mathbb{1}(X_{t+1,j} \ge X_{t, i}) \cdot
 \mathbb{1}(f_1\le X_t^i \le f_2) -  \mathbb{1}(X_{t+1,i} \ge X_{t, j}) \cdot
-\mathbb{1}(f_1 \le X_t^j \le f_2) \]  where $f_1$ and $f_2$ are parameters of
-the method and $I$ is the indicator function. % TODO say that we use only the
-3 first filters for this
-
-% TODO speak that we should set the diagonal to the minimum to gain some
-% performance.
+\mathbb{1}(f_1 \le X_t^j \le f_2)
+\]
+where $f_1$ and $f_2$ are parameters of the method and $I$ is the indicator
+function. \footnote{Only the filter defined by Equations \ref{eq:low-pass},
+\ref{eq:high-pass} and \ref{eq:hard-treshold-filter}}.
 
@@
 as a function of the recall $R(\tau) = \frac{tp(\tau)}{tp(\tau) + fn(\tau)}$.
+Since there is no self connection (neuron connected to itself), we set
+the diagonal elements of $\hat{y}_{i,j}$ to the minimum.
 

### 2014-06-10 article.tex
make more precision

@@
 = \frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii} \Sigma^{-1}_{jj}}} = 0$,
-where $\Sigma^{-1}$ is the inverse of the covariance matrix.
+where $\Sigma^{-1}_$ is the inverse of the covariance matrix.
 Therefore, by definition, the partial correlation coefficient between two

### 2014-06-10 article.tex
more explicit wording

--- 2014-06-10 article.tex
@@
 Connectivity information between two neurons may be retrieved from successive
-and slightly delayed burst events. At a local level, direct link
-between two neurons will have shorter delay between fluorescence
+and slightly delayed burst events. Direct links
+between two neurons should have shorter delay between fluorescence
 peaks than undirected links. However, the fluorescence signal has a slow
@@
 \end{align}
-where $f_3$ is a parameter of the hard-threshold filter and the $0.9$
+where $f_3 \geq 0$ is a parameter of the hard-threshold filter and the $0.9$
 exponent reduce the difference between peaks values.

### 2014-06-11 article.tex
add tabs + values for inverse correlation (roc)

@@
 \centering
-\caption{Improvement of each stage of our approach Note that we choose the
-         \textit{best} threshold for stages 1 to 4.}
+\caption{Inverse correlation (ROC). Improvement of each stage of our approach. Note that we choose the
+         \textit{best} threshold (\textcolor{red}{for now 0.11}) for stages 1 to 4.}
 \begin{tabular}{*{5}{l}}
@@
 \midrule
-Inverse correlation & & & & \\
-Pre-processing      & & & & \\
-PCA                 & & & & \\
-Weighting           & & & & \\
+Nothing             & 0.777 & 0.767 & 0.772 & 0.774 \\
+PCA                 & 0.780 & 0.770 & 0.776 & 0.777 \\
+Weights             & 0.780 & 0.769 & 0.776 & 0.777 \\
+Weights + PCA       & 0.783 & 0.772 & 0.779 & 0.780 \\
+H-T                 & 0.893 & 0.891 & 0.891 & 0.886 \\
+H-T + PCA           & 0.894 & 0.892 & 0.891 & 0.886 \\
+H-T + Weights       & 0.899 & 0.897 & 0.896 & 0.891 \\
+H-T + Weights + PCA & 0.900 & 0.898 & 0.896 & 0.892 \\
+P-A                 & 0.925 & 0.925 & 0.924 & 0.923 \\
+P-P + PCA           & 0.926 & 0.926 & 0.925 & 0.923 \\
+P-P + Weights       & 0.931 & 0.930 & 0.928 & 0.927 \\
+P-P + Weights + PCA & 0.932 & 0.931 & 0.930 & 0.928 \\
 Averaging           & & & & \\
@@
 \centering
-\caption{Comparison with other methods}
+\caption{Inverse correlation (P-R). Improvement of each stage of our approach. Note that we choose the
+         \textit{best} threshold (\textcolor{red}{for now 0.11}) for stages 1 to 4.}
+\begin{tabular}{*{5}{l}}
+\toprule
+Stage               & normal-1 & normal-2 & normal-3 & normal-4 \\
+\midrule
+Nothing             & & & & \\
+PCA                 & & & & \\
+Weights             & & & & \\
+Weights + PCA       & & & & \\
+H-T                 & & & & \\
+H-T + PCA           & & & & \\
+H-T + Weights       & & & & \\
+H-T + Weights + PCA & & & & \\
+PCA                 & & & & \\
+P-P + PCA           & & & & \\
+P-P + Weights       & & & & \\
+P-P + Weights + PCA & & & & \\
+Averaging           & & & & \\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{table}[htb]
+\centering
+\caption{Correlation. Improvement of each stage of our approach. Note that we choose the
+         \textit{best} threshold (\textcolor{red}{for now 0.11}) for stages 1 to 4.}
+\begin{tabular}{*{5}{l}}
+\toprule
+Stage               & normal-1 & normal-2 & normal-3 & normal-4 \\
+\midrule
+Nothing             & 0.681 (0.028) & & & \\
+hard-threshold      & 0.876 (0.143) & & & \\
+Pre-processing      & 0.857 (0.100) & & & \\
+PCA                 & & & & \\
+Weighting           & 0.826 (0.079) & & & \\
+Averaging           & & & & \\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{table}[htb]
+\centering
+\caption{Comparison with other methods (for now, $t = 0.11$)}
 \begin{tabular}{*{5}{l}}

### 2014-06-11 article.tex
add values for inverse correlation (pr)

@@
 \midrule
-Nothing             & & & & \\
-PCA                 & & & & \\
-Weights             & & & & \\
-Weights + PCA       & & & & \\
-H-T                 & & & & \\
-H-T + PCA           & & & & \\
-H-T + Weights       & & & & \\
-H-T + Weights + PCA & & & & \\
-PCA                 & & & & \\
-P-P + PCA           & & & & \\
-P-P + Weights       & & & & \\
-P-P + Weights + PCA & & & & \\
+Nothing             & 0.070 & 0.064 & 0.068 & 0.072\\
+PCA                 & 0.076 & 0.070 & 0.075 & 0.079\\
+Weights             & 0.074 & 0.067 & 0.072 & 0.076\\
+Weights + PCA       & 0.080 & 0.073 & 0.079 & 0.083\\
+H-T                 & 0.264 & 0.260 & 0.269 & 0.241\\
+H-T + PCA           & 0.266 & 0.263 & 0.273 & 0.244\\
+H-T + Weights       & 0.280 & 0.273 & 0.281 & 0.251\\
+H-T + Weights + PCA & 0.284 & 0.278 & 0.285 & 0.255\\
+PCA                 & 0.322 & 0.324 & 0.323 & 0.312\\
+P-P + PCA           & 0.347 & 0.352 & 0.355 & 0.341\\
+P-P + Weights       & 0.333 & 0.334 & 0.327 & 0.313\\
+P-P + Weights + PCA & 0.364 & 0.366 & 0.359 & 0.344\\
 Averaging           & & & & \\

### 2014-06-11 article.tex
add values for correlation

--- 2014-06-10 article.tex
@@
 \midrule
-Inverse correlation & & & & \\
-Pre-processing      & & & & \\
-PCA                 & & & & \\
-Weighting           & & & & \\
+Nothing             & 0.777 & 0.767 & 0.772 & 0.774 \\
+PCA                 & 0.780 & 0.770 & 0.776 & 0.777 \\
+Weights             & 0.780 & 0.769 & 0.776 & 0.777 \\
+Weights + PCA       & 0.783 & 0.772 & 0.779 & 0.780 \\
+H-T                 & 0.893 & 0.891 & 0.891 & 0.886 \\
+H-T + PCA           & 0.894 & 0.892 & 0.891 & 0.886 \\
+H-T + Weights       & 0.899 & 0.897 & 0.896 & 0.891 \\
+H-T + Weights + PCA & 0.900 & 0.898 & 0.896 & 0.892 \\
+P-P                 & 0.925 & 0.925 & 0.924 & 0.923 \\
+P-P + PCA           & 0.926 & 0.926 & 0.925 & 0.923 \\
+P-P + Weights       & 0.931 & 0.930 & 0.928 & 0.927 \\
+P-P + Weights + PCA & 0.932 & 0.931 & 0.930 & 0.928 \\
 Averaging           & & & & \\
@@
 \centering
-\caption{Comparison with other methods}
+\caption{Inverse correlation (P-R). Improvement of each stage of our approach. Note that we choose the
+         \textit{best} threshold (\textcolor{red}{for now 0.11}) for stages 1 to 4.}
+\begin{tabular}{*{5}{l}}
+\toprule
+Stage               & normal-1 & normal-2 & normal-3 & normal-4 \\
+\midrule
+Nothing             & 0.070 & 0.064 & 0.068 & 0.072\\
+PCA                 & 0.076 & 0.070 & 0.075 & 0.079\\
+Weights             & 0.074 & 0.067 & 0.072 & 0.076\\
+Weights + PCA       & 0.080 & 0.073 & 0.079 & 0.083\\
+H-T                 & 0.264 & 0.260 & 0.269 & 0.241\\
+H-T + PCA           & 0.266 & 0.263 & 0.273 & 0.244\\
+H-T + Weights       & 0.280 & 0.273 & 0.281 & 0.251\\
+H-T + Weights + PCA & 0.284 & 0.278 & 0.285 & 0.255\\
+P-P                 & 0.322 & 0.324 & 0.323 & 0.312\\
+P-P + PCA           & 0.347 & 0.352 & 0.355 & 0.341\\
+P-P + Weights       & 0.333 & 0.334 & 0.327 & 0.313\\
+P-P + Weights + PCA & 0.364 & 0.366 & 0.359 & 0.344\\
+Averaging           & & & & \\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{table}[htb]
+\centering
+\caption{Correlation (ROC). Improvement of each stage of our approach. Note that we choose the
+         \textit{best} threshold (\textcolor{red}{for now 0.11}) for stages 1 to 4.}
+\begin{tabular}{*{5}{l}}
+\toprule
+Stage               & normal-1 & normal-2 & normal-3 & normal-4 \\
+\midrule
+Nothing             & 0.681 & 0.699 & 0.683 & 0.681\\
+Weights             & 0.695 & 0.713 & 0.697 & 0.694\\
+H-T                 & 0.876 & 0.873 & 0.877 & 0.869\\
+H-T + Weights       & 0.886 & 0.884 & 0.891 & 0.877\\
+P-P                 & 0.857 & 0.850 & 0.843 & 0.832\\
+P-P + Weights       & 0.826 & 0.823 & 0.817 & 0.799\\
+Averaging           & & & & \\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{table}[htb]
+\centering
+\caption{Correlation (P-R). Improvement of each stage of our approach. Note that we choose the
+         \textit{best} threshold (\textcolor{red}{for now 0.11}) for stages 1 to 4.}
+\begin{tabular}{*{5}{l}}
+\toprule
+Stage               & normal-1 & normal-2 & normal-3 & normal-4 \\
+\midrule
+Nothing             & 0.028 & 0.699 & 0.025 & 0.026\\
+Weights             & 0.031 & 0.713 & 0.027 & 0.028\\
+H-T                 & 0.143 & 0.873 & 0.150 & 0.129\\
+H-T + Weights       & 0.153 & 0.884 & 0.170 & 0.132\\
+P-P                 & 0.100 & 0.850 & 0.079 & 0.083\\
+P-P + Weights       & 0.079 & 0.823 & 0.067 & 0.064\\
+Averaging           & & & & \\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{table}[htb]
+\centering
+\caption{Comparison with other methods (for now, $t = 0.11$)}
 \begin{tabular}{*{5}{l}}

### 2014-06-11 article.tex
add directivity and stacking entries in tabs

@@
 Averaging           & & & & \\
+Directivity         & & & & \\
+Stacking            & & & & \\
 \bottomrule

### 2014-06-11 article.tex
values for directivity

--- 2014-06-11 article.tex
@@
 Averaging           & & & & \\
+Stacking            & & & & \\
 \bottomrule
@@
 \centering
-\caption{Comparison with other methods (for now, $t = 0.11$)}
+\caption{Comparison (ROC) with other methods (for now, $t = 0.11$)}
 \begin{tabular}{*{5}{l}}
@@
 GTE                 & & & & \\
+Directivity         & 0.535 & 0.526 & 0.533 & 0.535 \\
+Our approach + dir  & & & & \\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{table}[htb]
+\centering
+\caption{Comparison (P-R) with other methods (for now, $t = 0.11$)}
+\begin{tabular}{*{5}{l}}
+\toprule
+Methods             & normal-1 & normal-2 & normal-3 & normal-4 \\
+\midrule
+Correlation         & & & & \\
+Partial correlation & & & & \\
+Our approach        & & & & \\
+GENIE3              & & & & \\
+GTE                 & & & & \\
+Directivity         & 0.012 & 0.012 & 0.012 & 0.012\\
+Our approach + dir  & & & & \\
 \bottomrule

### 2014-06-11 article.tex
force the separation between tabs and ref/ack
add values for comparison between methods

@@
 
-\begin{table}[htb]
+\begin{table}[H]
 \centering
@@
 \midrule
-Nothing             & 0.028 & 0.699 & 0.025 & 0.026\\
-Weights             & 0.031 & 0.713 & 0.027 & 0.028\\
-H-T                 & 0.143 & 0.873 & 0.150 & 0.129\\
-H-T + Weights       & 0.153 & 0.884 & 0.170 & 0.132\\
-P-P                 & 0.100 & 0.850 & 0.079 & 0.083\\
-P-P + Weights       & 0.079 & 0.823 & 0.067 & 0.064\\
+Nothing             & 0.028 & 0.028 & 0.025 & 0.026\\
+Weights             & 0.031 & 0.030 & 0.027 & 0.028\\
+H-T                 & 0.143 & 0.128 & 0.150 & 0.129\\
+H-T + Weights       & 0.153 & 0.145 & 0.170 & 0.132\\
+P-P                 & 0.100 & 0.087 & 0.079 & 0.083\\
+P-P + Weights       & 0.079 & 0.071 & 0.067 & 0.064\\
 Averaging           & & & & \\
@@
 \midrule
-Correlation         & & & & \\
-Partial correlation & & & & \\
+Correlation                & 0.886 & 0.884 & 0.891 & 0.877\\
+Partial correlation (best) & 0.932 & 0.931 & 0.930 & 0.928 \\
 Our approach               & & & & \\
@@
 \midrule
-Correlation         & & & & \\
-Partial correlation & & & & \\
-Our approach        & & & & \\
+Correlation (best)         & 0.153 & 0.145 & 0.170 & 0.132 \\
+Partial correlation (best) & 0.364 & 0.366 & 0.359 & 0.344 \\
+Our approach (best)        & & & & \\
 GENIE3                     & & & & \\
@@
 \paragraph{Acknowledgements.} A. Joly and G. Louppe are research fellows of
-the FNRS, Belgium. We also thank Damien for pizzas.  A. Sutera is supported by
+the FNRS, Belgium.  A. Sutera is supported by
 a F.R.I.A. scholarship.

### 2014-06-11 article.tex
wording

@@
 
-Note that our parameter tuning was mainly on \textit{normal-1} dataset and
-partly on \textit{normal-4} dataset, therefore it may justify why these
+Note that our parameter tuning was mainly done on the \textit{normal-1} dataset
+and partly on \textit{normal-4} dataset, therefore it may justify why these
 networks are better retrieved despite the fact that some might be simpler to

### 2014-06-11 article.tex
wording + f_3 -> tau

@@
 X^{\prime\prime\prime}_{t,i} &=
-{X^{\prime\prime}_{t,i}}^{0.9} I(X^{\prime\prime}_{t,i} \geq f_3) \forall i
+{X^{\prime\prime}_{t,i}}^{0.9} I(X^{\prime\prime}_{t,i} \geq \tau) \forall i
 \label{eq:hard-treshold-filter}
 \end{align}
-where $f_3 \geq 0$ is a parameter of the hard-threshold filter and the $0.9$
+where $\tau \geq 0$ is a parameter of the hard-threshold filter and the $0.9$
 exponent reduce the difference between peaks values.
@@
 A weighted average $y_{stack}$ of partial correlation matrices was made
-by varying uniformly the hard-threshold value (parameter $f_3$) and the design
+by varying uniformly the hard-threshold value (parameter $\tau$) and the design
 of the low-pass filter (coefficients $c_l$). The stacked connectivity score
@@
 \end{align}
-where $f(X, k, f_3)$ gives the predicted adjacency matrix, i.e. applies the
+where $f(X, k, \tau)$ gives the predicted adjacency matrix, i.e. applies the
 filtering and inference methodologies (as described
 in sections \ref{sec:filter} and \ref{sec:inference}), with a  given value
-$f_3$ for the hard-threshold among a set of thresholds $T_k$ of size $|T_k|$
+$\tau$ for the hard-threshold among a set of thresholds $T_k$ of size $|T_k|$
 and the $k^{th}$ low-pass filter pattern associated to a weight $w_k$ whose
@@
 where $f_1$ and $f_2$ are parameters of the method and $I$ is the indicator
-function. \footnote{Only the filter defined by Equations \ref{eq:low-pass},
-\ref{eq:high-pass} and \ref{eq:hard-treshold-filter}}.
+function. Prior computing $z_{ij}$ only the filter defined by Equations
+\ref{eq:low-pass}, \ref{eq:high-pass} and \ref{eq:hard-treshold-filter} were
+used.
 

### 2014-06-11 article.tex
small modifs

--- 2014-06-11 article.tex
@@
 \midrule
-Correlation                & 0.886 & 0.884 & 0.891 & 0.877\\
+Correlation (best)         & 0.886 & 0.884 & 0.891 & 0.877\\
 Partial correlation (best) & 0.932 & 0.931 & 0.930 & 0.928 \\

### 2014-06-11 article.tex
save bibliography place
acknowledge dysco and pascal
wording + ref in metrics section

@@
 to inferred have around 15000 arcs or a density of $0.15\%$ and are similar to those
-used to rank challenge participants.
-
-Note that our parameter tuning was mainly done on the \textit{normal-1} dataset
-and partly on \textit{normal-4} dataset, therefore it may justify why these
-networks are better retrieved despite the fact that some might be simpler to
-infer.
+used to rank challenge participants. Note that our parameter tuning was mainly
+done on the \textit{normal-1} dataset and partly on \textit{normal-4} dataset,
+therefore it may justify why these networks are better retrieved despite the
+fact that some might be simpler to infer.
 
@@
 The network inference task can be viewed as a binary classification task
-where one have to correctly classified the presence or the absence of edges
-of the graph. The connectivity score matrix
-$\hat{y}_{i,j} \in \mathcal{R}$ inferred by a modeling technique
-can be thresholded by a value $\tau \in \mathcal{R}$ to evaluate its performance.
-Given the ground true network $y_{i,j} \in \left\{0, 1\right\}$, we first define the notion of
+where one has to correctly classified the presence or the absence of edges
+of the graph. Given the ground true network $y_{i,j} \in \left\{0, 1\right\}$,
+the connectivity score matrix $\hat{y}_{i,j} \in \mathcal{R}$
+and threshold value $\tau$, we first define the notion of
 true positive $tp(\tau) = \sum_{i=1}^p \sum_{j=1}^p I(y_{i,j} = 1, \hat{y}_{i,j} \geq \tau)$,
@@
 false negative $fn(\tau) = \sum_{i=1}^p \sum_{j=1}^p I(y_{i,j} = 1, \hat{y}_{i,j} < \tau)$ and
-false positive $fp(\tau) = \sum_{i=1}^p \sum_{j=1}^p I(y_{i,j} = 0, \hat{y}_{i,j} \geq \tau)$.
-Those four numbers formed the confusion matrix.
+false positive $fp(\tau) = n - tp(\tau) - tn(\tau) -fn(\tau)$.
 
@@
 as a function of the false positive rate
-$fpr(\tau) = \frac{tn(\tau)}{tn(\tau) + fp(\tau)}$. In section (TODO ref),
+$fpr(\tau) = \frac{tn(\tau)}{tn(\tau) + fp(\tau)}$.  As suggested in
+\cite{schrynemackers2013protocols},
 we also compare the same methods with the area under the precision-recall
-curve (AUPRC), an information retrieval metrics, obtained by varying the threshold
+curve (AUPRC) obtained by varying the threshold
 $\tau$ of the precision $P(\tau) = \frac{tp(\tau)}{tp(\tau) + fp(\tau)}$
-as a function of the recall $R(\tau) = \frac{tp(\tau)}{tp(\tau) + fn(\tau)}$.
+as a function of the recall $R(\tau) = \frac{tp(\tau)}{tp(\tau) + fn(\tau)}$
+in section (todo ref).
 Since  there is no self connection (neuron connected to itself), we set
-the diagonal elements of $\hat{y}_{i,j}$ to the minimum.
+the diagonal elements of $\hat{y}_{i,j}$ to the minimum prior evaluation.
 
@@
 \paragraph{Acknowledgements.} A. Joly and G. Louppe are research fellows of
-the FNRS, Belgium.  A. Sutera is supported by
-a F.R.I.A. scholarship.
+the FNRS, Belgium.  A. Sutera is  is recipient of
+a F.R.I.A. fellowship of F.R.S.-FNRS, Belgium.
+This work is supported by PASCAL2 and the IUAP DYSCO, initiated by the
+Belgian State, Science Policy Office.
 
@@
 
+\newpage
+\clearpage
+
+% We allow the bibliography to be added on top of the 6 pages.
+% Supplementary material may be added in the form or a URL pointed to from
+% the paper.
 \bibliography{references}

### 2014-06-11 article.tex
detailed

@@
 low-rank hypothesis and perform noise filtering through a principal component
-approach. From the $p$ eigen vectors, we only kept $80\%$ of
+analysis. From the $p$ eigen vectors, we only kept $80\%$ of
 the eigen vectors which have the largest eigen value. In the context of the
@@
 of the low-pass filter (coefficients $c_l$). The stacked connectivity score
-matrix $y_{stacking}$ is given by
+matrix $y_{stack}$ is given by
 \begin{align}

### 2014-06-11 article.tex
FIX stacking description

@@
 selection [todo cite] and improve performance [todo cite].
-A weighted average $y_{stack}$ of partial correlation matrices was made
-by varying uniformly the hard-threshold value (parameter $\tau$) and the design
-of the low-pass filter (coefficients $c_l$). The stacked connectivity score
-matrix $y_{stack}$ is given by
+A weighted average $\hat{y}$ of partial correlation matrices was estimated
+from the timeseris $X \in \mathcal{R}^{n \times p}$
+by varying unifthe hard-threshold value $\tau \in \mathcal{T}$  and the design
+of the low-pass filter (coefficients
+$(c_l)_{-3}^2 \forall l \in \left\{1,\ldots,4\right\}$)
 \begin{align}
-y_{stack} =  \dfrac{1}{\sum_{k\in\{1,..,4\}} w_k |T_k|} \sum_{k=1}^{k=4}  w_k \sum_{q \in T_k} G^{q,k}(X_t^i)
+\hat{y} = \frac{1}{\sum_{l=1}^4 w_l |\mathcal{T}|} \sum_{l=1}^4  w_l \sum_{\tau \in \mathcal{T}} G^{\tau,m}(X)
 \end{align}
-where $f(X, k, \tau)$ gives the predicted adjacency matrix, i.e. applies the
-filtering and inference methodologies (as described
-in sections \ref{sec:filter} and \ref{sec:inference}), with a  given value
-$\tau$ for the hard-threshold among a set of thresholds $T_k$ of size $|T_k|$
-and the $k^{th}$ low-pass filter pattern associated to a weight $w_k$ whose
-values are $w_1 = 0.01 , w_2 =1, w_3 = 0.7, w_4 = 0.9$.
+where $G^{k, \tau}(X)$ gives the connectivity score matrix for
+a given  $\tau$ and a set of coefficient $c_l$. following
+the methodology described in previous section, associated to a weight
+$w_p$ whose values are $w_1 = 0.01 , w_2 =1, w_3 = 0.7, w_4 = 0.9$.
 

### 2014-06-13 article.tex
new proposal for the title
set author given discussion

@@
 
-\title[Inference of connectomes using partial correlation coefficients]{Simple and robust inference of connectomes using partial correlation coefficients}
+% \title[Inference of connectomes using partial correlation coefficients]{Simple and robust inference of connectomes using partial correlation coefficients}
+
+\title{Connectome inferences using partial correlation from imaging calcium signal}
 
@@
  % Three or more authors with the same address:
- \author{Todo authors}
-
-%% Proposition (sujet à changements : on en discutera):
-% Antonio
-% {Aaron, Arnaud, Vincent} : aucune préférence pour ma part
-% Gilles
-% Damien?
-% Pierre?
+ % \author{ Antonio Sutera %\and
+ %         % \Name{Arnaud Joly} \and
+ %         % \Name{Vincent Fran\c{c}ois-Lavet} \and
+ %         % \Name{Aaron Qiu} \and
+ %         % \Name{Gilles Louppes} \and
+ %         % \Name{Damien Ernst} \and
+ %         % \name{Pierre Geurts}}
+ %         }
+\author{Antonio Sutera,
+        Arnaud Joly,
+        Vincent François-Lavet,
+        Aaron Qiu, \\
+        Gilles Louppes,
+        Damien Ernst,
+        Pierre Geurts}
 

### 2014-06-13 article.tex
Correction dans le nom de Gilles
Clean introduction

@@
 
-\begin{abstract} Understanding how the brain works is a key to understand and
-to treat brain pathologies and disorders such as Parkinson's disease,
-epilepsy. Retrieving the connectomes, neurons connectivity map, will shed new
-lights on the anatomical and functional connectivity of the brain. In the
+\begin{abstract}
+Understanding how the brain works is a key
+to treat brain disorders such as Parkinson's disease,
+epilepsy. Retrieving connectomes, the neurons wiring map, will shed a new
+light on the anatomical and functional connectivity of the brain. In the
 context of the Connectomics challenge, we propose a simple  algorithm made of
 four stages, using preprocessing and partial correlation to achieve a network
-inference of high quality. We put in perspective our method by comparing
-with other inference method such as GTE \cite{stetter2012model}, another
-method proposed to infer a neural network from calcium fluorescent imaging,
-and Genie3 [], a tree-based approach very competitive in several gene
-inference challenge (i.e. DREAM4 and DREAM5).
+inference of high quality. We put in perspective our method
+with other inference methods such as GTE (\cite{stetter2012model}) and Genie3
+(\cite{huynhthu2010inferring}).
 
@@
 % BG : brain, complex organ
-The human brain is a complex biological organ, which is formed by 100
-billions of neurons with 7000 synaptic connections on average. Inferring the
-neuron connectivity network through dissection would be an impossible
-and a daunting task. Cutting edge optical devices [todo cite] allow to track
-simultaneously the neural activity of thousands of neurons through a fluorescent
-calcium indicator.
-
-From those observational data, the neural connectivity inference consists in
-highlighting direct relationships between neurons. However, those imaging
-systems have a sampling rate smaller than the neuron firing speed and are
-limited to two dimensional image, while the neuronal network is a
-three dimensional structure, which may lead to superpose the observed activity
-of different neurons. Furthermore, the decay of the fluorescent calcium signal
-is slower than its rise.
+The human brain is a complex biological organ, formed by 100
+billions of neurons with 7000 synaptic connections on average.
+Cutting edge optical devices have been developed to track in real-time
+the neuronal activity of thousands of neurons through a fluorescent
+calcium indicator  [todo cite]. Automatic and analytical methods are required to infer
+the connectomes from those time series.
 
@@
 % TODO check convention for y_{ij}
-One way to emphasize the connections between neurons is to represent them by a
-(un)directed graph with $p$ nodes: each node represents a neuron, and each
-edge $y_{ij}$ represents a direct link from neuron  $i$ to neuron $j$. If the
-graph is undirected, then $y_{ij}$ is equal to $y_{ji}$  for all $i,j$.
-The unsupervised task may be formulated as:
-\textit{Given $X \in \mathcal{R}^{n \times p}$  a set of $p$ time series of
-fluorescent calcium concentration of size $n$ from $p$ neurons, the goal is to
-infer the connectivity graph $y \in \left\{0, 1\right\}^{p \times p}$.}
-The main challenge in the inference of the network $y$
-is to distinguish direct from indirect interactions \cite{de2004discovery}.
-For instance with the simple interaction graph $A \rightarrow B \rightarrow C$,
-we want to distinguish direct interactions $A \rightarrow B$ and $B \rightarrow C$
-from the indirect interaction $A \rightarrow C$.
-
-\textcolor{red}{AJ: Should we keep the following paragraph? While interesting
-                this might not be relevant for a 6 page abstract.}
-Since only observational data are available, the network recovery is set as an
-unsupervised learning problem. Whenever a partial knowledge of the target
-network or known networks highly similar to the unknown one is available,
-supervised learning [todo cite] and transfer learning  [todo cite] based
-approach could be considered to infer networks.
+The connectomes is represented by a (un)directed graph $G = (V, E)$ comprising
+a set of nodes $V$ and a set of edges $E \subseteq \left\{(i, j) \in V \times
+V\right\}$, (un)ordered pair from $V$.
+Each node $i \in V$ represents a neuron, and each edge $(i, j) \in E$
+represents a direct link from neuron $i$ to neuron $j$.
+The network inference task is set as follows :
+\textit{Given the observations $(x^i \in \mathcal{R}^{|V|})_{i=1}^n $
+along $n$ periods of time of the $|V|$ neurons, the goal is to infer the
+adjacency matrix $A : a_{i,j} = I((i, j) \in E)$ of the graph $G$,
+where $I$ is the indicator function.}
 
@@
 In this paper, we describe a simple and a theoretically grounded approach
-based on partial correlation to infer the neural connectivity network.
-This is also the winning method of the Connectomics challenge
-\footnote{\url{http://connectomics.chalearn.org/}}. For reproducibility, the
-source code of the method is available at
-\url{https://github.com/asutera/kaggle-connectomics}  BSD 3-clauses
-license.
+based on partial correlation\footnote{Source code is available at
+\url{https://github.com/asutera/kaggle-connectomics}.} to infer the neural
+network, which is the winning method of the Connectomics challenge
+\footnote{\url{http://connectomics.chalearn.org}}.
 
 \section{Signal filtering} \label{sec:filter}
+
+% Defects of the imaging device
+and will have to cope with
+a slower sampling rate than the neuron firing speed, a superposition
+of the activity of several neurons and the slow decay of fluorescent calcium
+indicator.
 
@@
 \label{sec:inference}
+
+% The main challenge in the inference of the network $y$
+% is to distinguish direct from indirect interactions \cite{de2004discovery}.
+% For instance with the simple interaction graph $A \rightarrow B \rightarrow C$,
+% we want to distinguish direct interactions $A \rightarrow B$ and $B \rightarrow C$
+% from the indirect interaction $A \rightarrow C$.
 

### 2014-06-13 article.tex
better notation

@@
  %         % \Name{Aaron Qiu} \and
- %         % \Name{Gilles Louppes} \and
+ %         % \Name{Gilles Louppe} \and
  %         % \Name{Damien Ernst} \and
@@
         Aaron Qiu, \\
-        Gilles Louppes,
+        Gilles Louppe,
         Damien Ernst,
@@
 The network inference task is set as follows :
-\textit{Given the observations $(x^i \in \mathcal{R}^{|V|})_{i=1}^n $
-along $n$ periods of time of the $|V|$ neurons, the goal is to infer the
+\textit{Given the observations $(x_t \in \mathcal{R}^{|V|})_{t=1}^T $
+along $T$ periods of time of the $|V|$ neurons, the goal is to infer the
 adjacency matrix $A : a_{i,j} = I((i, j) \in E)$ of the graph $G$,

### 2014-06-13 article.tex
rewrote section on partial correlation

@@
 low-rank hypothesis and perform noise filtering through a principal component
-analysis. From the $p$ eigen vectors, we only kept $80\%$ of
+analysis. From the $p$ eigen vectors, we kept $80\%$ of
 the eigen vectors which have the largest eigen value. In the context of the
@@
 
-\subsection{Network inference through partial correlation}
+\subsection{Network inference through weighted average partial correlation
+            coefficients}
 \label{sec:inference}
 
-% The main challenge in the inference of the network $y$
-% is to distinguish direct from indirect interactions \cite{de2004discovery}.
-% For instance with the simple interaction graph $A \rightarrow B \rightarrow C$,
-% we want to distinguish direct interactions $A \rightarrow B$ and $B \rightarrow C$
-% from the indirect interaction $A \rightarrow C$.
+Let us denote the fluorescence calcium indicators of all neuron
+as a set of random variables $V = \left\{V_1, \ldots, V_{|V|}\right\}$, which follows
+a joint probability distribution $p_\mathcal{V}$, and by
+$V^{-i,j}$ the set of all variables except $V_i$ and $V_j$.
+Two random variables $V_i$ and $V_j$ are said to be conditionally independent
+to a (possibly empty) set of random variables $Z$, denoted by $V_i \perp V_j | Z$,
+if the joint conditional probability distribution factorizes
+$p_{\mathcal{V}_i, \mathcal{V}_j|\mathcal{Z}} = p_{\mathcal{V}_i|\mathcal{Z}}
+p_{\mathcal{V}_j|\mathcal{Z}}$.  The inference of the undirected network
+can be formulated as inferring conditional dependences
+$V_i \not\perp V_j | V^{-i,j}$ between all pair of fluorescence signal
+$i$ and $j$, in other words the inferred network will be
+$\hat{A}: \hat{a}_{i,j} = I(V_i \not\perp V_j | V^{-i,j}), i, j \in V$.
 
-From a probabilistic point of view, the inference of the undirected network
-can be formulated as inferring conditional dependences and independences. Even
-if \textit{correlation does no imply causation}[todo cite], it gives insight
-on the underlying connectivity network.
+Since all neurons are assumed to be connected to at least one neuron,
+we thus have by definition $V_i \not\perp V_j$. However,  two random
+variables $A$ and $B$ might be dependent taken alone ($A \not\perp B$), but not
+once we observe a third variables $C$ ($A \perp B | C$).
+The conditioning over all other random variables $V^{-i,j}$ is thus necessary
+to avoid predicting an edge when two neurons are not directly connected.
 
-Let us consider the neurons as random variables $\mathcal{X}_i$ which follows
-a probability density function $p_{\mathcal{X}_i}$ and let us denote by
-$p_{\mathcal{X}_i,\mathcal{X}_j|\mathcal{Z}}$ the joint probability
-distribution between neurons $i$ and $j$ conditioned on a subset of neurons
-$\mathcal{Z}$ (possibly empty). Two neurons $X_i$, $X_j$
-will be said conditionally independent to a set of neurons
-$\mathcal{Z}$ (possibly empty), denoted by  $X_i \perp X_j | \mathcal{Z}$,  if
-$p_{\mathcal{X}_i,\mathcal{X}_j|\mathcal{Z}} = p_{\mathcal{X}_i|\mathcal{Z}}
-p_{\mathcal{X}_j|\mathcal{Z}}$. The reciprocal is not true without
-additional hypotheses.  Let us define $\mathcal{V}$ the set of all
-neurons $\mathcal{X}_1, \dots, \mathcal{X}_p$, and by $\mathcal{V}^{-i,j}$ the
-same set without neurons $\mathcal{X}_i$ and $\mathcal{X}_j$.
-
-The connectivity network to infer is only made of direct relationships
-which defined relation between neurons that still exists when
-conditioned on all other neurons. In other words, there is not intermediary
-between those two neurons. Under the hypothesis that neurons follow a jointly
-Gaussian distribution $p_{\mathcal{X}_1, \dots, \mathcal{X}_p} \sim
-\mathcal{N}(\mu; \Sigma)$, two neurons $\mathcal{X}_i$ and $\mathcal{X}_j$ are
-independent $\mathcal{X}_i\perp \mathcal{X}_j$ if the Pearson correlation
-coefficient $\rho_{X_iX_j} = \frac{\Sigma_{ij}}{\sqrt{\Sigma_{ii}
-\Sigma_{jj}}} = 0,$ and are conditionally independant to all others neurons
-$\mathcal{X}_i \perp \mathcal{X}_j |\mathcal{V}^{i,j}$ if the partial
-correlation coefficient (of order $p-2$) $\rho_{X_i, X_j | \mathcal{V}^{i,j}}
-= \frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii} \Sigma^{-1}_{jj}}} = 0$,
-where $\Sigma^{-1}$ is the inverse of the covariance matrix.
-Therefore, by definition, the partial correlation coefficient between two
-neurons only estimates the direct relationship between them.
-
-In previous study \cite{shipley2002cause}, it has been suggested to
-consider correlation coefficients of all possible orders,
-i.e. conditioned on every subsets of the set of $p-2$ other variables. This
-would take into account multiple indirect paths between a given pair of
-variables. An obvious limitation to estimate correctly high-order coefficients
-is the number of samples. However given the high number of samples $n$
-in the Connectomics challenge, we only consider the highest order of partial
-correlation coefficient.
-
-\subsection{Stacking partial correlation matrix}
-\label{sec:stacking}
+If the random variables $V$ follows a joint Gaussian distribution
+$p_\mathcal{V} \sim \mathcal{N}(\mu; \Sigma)$ of mean vector $\mu$ and
+covariance matrix $\Sigma$, we have the conditional independence
+$V_i \perp V_j | V^{-i,j}$ if the partial correlation coefficient
+\[
+\rho_{V_i, V_j | V^{-i,j}}
+= \frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii} \Sigma^{-1}_{jj}}}.
+\]
+is equal zero. The partial correlation gives a connectivity score
+$\hat{A}: \hat{a}_{i,j} = \rho_{V_i, V_j | V^{-i,j}}, i, j \in V$ between all
+pair of neuron $i$ and $j$. One could retrieve an estimated graph by thresholding
+the matrix $\hat{A}$.
+By contrast, we also have $V_i \perp V_j$ if the Pearson correlation
+coefficient
+\[
+\rho_{V_i,V_j} = \frac{\Sigma_{ij}}{\sqrt{\Sigma_{ii}
+\Sigma_{jj}}}
+\]
+is equal to zero.
 
 % Speak about why averaging
-The quality of the signal filtering and network inference is dependent upon
+The quality of the signal filtering and network inference depends
 good hyper-parameter selection, which are themselves dependent on the properties
 of the targeted network and measurement conditions, e.g. signal to noise ratio.
-Ensemble methods are known to improve robustness with respect to parameter
-selection [todo cite] and improve performance [todo cite].
-A weighted average $\hat{y}$ of partial correlation matrices was estimated
-from the timeseris $X \in \mathcal{R}^{n \times p}$
-by varying unifthe hard-threshold value $\tau \in \mathcal{T}$  and the design
-of the low-pass filter (coefficients
-$(c_l)_{-3}^2 \forall l \in \left\{1,\ldots,4\right\}$)
-\begin{align}
-\hat{y} = \frac{1}{\sum_{l=1}^4 w_l |\mathcal{T}|} \sum_{l=1}^4  w_l \sum_{\tau \in \mathcal{T}} G^{\tau,m}(X)
-\end{align}
-where $G^{k, \tau}(X)$ gives the connectivity score matrix for
-a given  $\tau$ and a set of coefficient $c_l$. following
-the methodology described in previous section, associated to a weight
-$w_p$ whose values are $w_1 = 0.01 , w_2 =1, w_3 = 0.7, w_4 = 0.9$.
+In order to improve robustness, a weighted average of partial correlation
+matrices was estimated from the time series by varying the hard-threshold value
+$\tau$ and the design of the low-pass filter (coefficients $(c_l^k)_{l=-3}^k$).
 
@@
 
+In previous study \cite{shipley2002cause}, it has been suggested to
+consider correlation coefficients of all possible orders,
+i.e. conditioned on every subsets of the set of $p-2$ other variables. This
+would take into account multiple indirect paths between a given pair of
+variables.
+
 % Possible extensions

### 2014-06-13 article.tex
averaging + stacking values

--- 2014-06-13 article.tex
@@
 
-\begin{abstract}
-Understanding how the brain works is a key
-to treat brain disorders such as Parkinson's disease,
-epilepsy. Retrieving connectomes, the neurons wiring map, will shed a new
-light on the anatomical and functional connectivity of the brain. In the
+\begin{abstract} Understanding how the brain works is a key to understand and
+to treat brain pathologies and disorders such as Parkinson's disease,
+epilepsy. Retrieving the connectomes, neurons connectivity map, will shed new
+lights on the anatomical and functional connectivity of the brain. In the
 context of the Connectomics challenge, we propose a simple  algorithm made of
 four stages, using preprocessing and partial correlation to achieve a network
-inference of high quality. We put in perspective our method
-with other inference methods such as GTE (\cite{stetter2012model}) and Genie3
-(\cite{huynhthu2010inferring}).
+inference of high quality. We put in perspective our method by comparing
+with other inference method such as GTE \cite{stetter2012model}, another
+method proposed to infer a neural network from calcium fluorescent imaging,
+and Genie3 [], a tree-based approach very competitive in several gene
+inference challenge (i.e. DREAM4 and DREAM5).
 
@@
 % BG : brain, complex organ
-The human brain is a complex biological organ, formed by 100
-billions of neurons with 7000 synaptic connections on average.
-Cutting edge optical devices have been developed to track in real-time
-the neuronal activity of thousands of neurons through a fluorescent
-calcium indicator  [todo cite]. Automatic and analytical methods are required to infer
-the connectomes from those time series.
+The human brain is a complex biological organ, which is formed by 100
+billions of neurons with 7000 synaptic connections on average. Inferring the
+neuron connectivity network through dissection would be an impossible
+and a daunting task. Cutting edge optical devices [todo cite] allow to track
+simultaneously the neural activity of thousands of neurons through a fluorescent
+calcium indicator.
+
+From those observational data, the neural connectivity inference consists in
+highlighting direct relationships between neurons. However, those imaging
+systems have a sampling rate smaller than the neuron firing speed and are
+limited to two dimensional image, while the neuronal network is a
+three dimensional structure, which may lead to superpose the observed activity
+of different neurons. Furthermore, the decay of the fluorescent calcium signal
+is slower than its rise.
 
@@
 % TODO check convention for y_{ij}
-The connectomes is represented by a (un)directed graph $G = (V, E)$ comprising
-a set of nodes $V$ and a set of edges $E \subseteq \left\{(i, j) \in V \times
-V\right\}$, (un)ordered pair from $V$.
-Each node $i \in V$ represents a neuron, and each edge $(i, j) \in E$
-represents a direct link from neuron $i$ to neuron $j$.
-The network inference task is set as follows :
-\textit{Given the observations $(x_t \in \mathcal{R}^{|V|})_{t=1}^T $
-along $T$ periods of time of the $|V|$ neurons, the goal is to infer the
-adjacency matrix $A : a_{i,j} = I((i, j) \in E)$ of the graph $G$,
-where $I$ is the indicator function.}
+One way to emphasize the connections between neurons is to represent them by a
+(un)directed graph with $p$ nodes: each node represents a neuron, and each
+edge $y_{ij}$ represents a direct link from neuron  $i$ to neuron $j$. If the
+graph is undirected, then $y_{ij}$ is equal to $y_{ji}$  for all $i,j$.
+The unsupervised task may be formulated as:
+\textit{Given $X \in \mathcal{R}^{n \times p}$  a set of $p$ time series of
+fluorescent calcium concentration of size $n$ from $p$ neurons, the goal is to
+infer the connectivity graph $y \in \left\{0, 1\right\}^{p \times p}$.}
+The main challenge in the inference of the network $y$
+is to distinguish direct from indirect interactions \cite{de2004discovery}.
+For instance with the simple interaction graph $A \rightarrow B \rightarrow C$,
+we want to distinguish direct interactions $A \rightarrow B$ and $B \rightarrow C$
+from the indirect interaction $A \rightarrow C$.
+
+\textcolor{red}{AJ: Should we keep the following paragraph? While interesting
+                this might not be relevant for a 6 page abstract.}
+Since only observational data are available, the network recovery is set as an
+unsupervised learning problem. Whenever a partial knowledge of the target
+network or known networks highly similar to the unknown one is available,
+supervised learning [todo cite] and transfer learning  [todo cite] based
+approach could be considered to infer networks.
 
@@
 In this paper, we describe a simple and a theoretically grounded approach
-based on partial correlation\footnote{Source code is available at
-\url{https://github.com/asutera/kaggle-connectomics}.} to infer the neural
-network, which is the winning method of the Connectomics challenge
-\footnote{\url{http://connectomics.chalearn.org}}.
+based on partial correlation to infer the neural connectivity network.
+This is also the winning method of the Connectomics challenge
+\footnote{\url{http://connectomics.chalearn.org/}}. For reproducibility, the
+source code of the method is available at
+\url{https://github.com/asutera/kaggle-connectomics}  BSD 3-clauses
+license.
 
 \section{Signal filtering} \label{sec:filter}
-
-% Defects of the imaging device
-and will have to cope with
-a slower sampling rate than the neuron firing speed, a superposition
-of the activity of several neurons and the slow decay of fluorescent calcium
-indicator.
 
@@
 \label{sec:inference}
-
-% The main challenge in the inference of the network $y$
-% is to distinguish direct from indirect interactions \cite{de2004discovery}.
-% For instance with the simple interaction graph $A \rightarrow B \rightarrow C$,
-% we want to distinguish direct interactions $A \rightarrow B$ and $B \rightarrow C$
-% from the indirect interaction $A \rightarrow C$.
 
@@
 P-P + Weights + PCA & 0.932 & 0.931 & 0.930 & 0.928 \\
-Averaging           & & & & \\
-Stacking            & & & & \\
+Averaging (PCA)     & 0.943 & 0.942 & 0.942 & 0.939 \\
+Stacking            & 0.944 & 0.943 & 0.942 & 0.940 \\
 \bottomrule
@@
 P-P + Weights + PCA & 0.364 & 0.366 & 0.359 & 0.344\\
-Averaging           & & & & \\
-Stacking            & & & & \\
+Averaging           & 0.403 & 0.404 & 0.398 & 0.388\\
+Stacking            & 0.404 & 0.405 & 0.399 & 0.389\\
 \bottomrule
@@
 P-P + Weights       & 0.826 & 0.823 & 0.817 & 0.799\\
-Averaging           & & & & \\
-Stacking            & & & & \\
 \bottomrule
@@
 P-P + Weights       & 0.079 & 0.071 & 0.067 & 0.064\\
-Averaging           & & & & \\
 \bottomrule

### 2014-06-13 article.tex
in recap tab too

@@
 Partial correlation (best) & 0.932 & 0.931 & 0.930 & 0.928 \\
-Our approach               & & & & \\
+Our approach               & 0.943 & 0.942 & 0.942 & 0.939 \\
 GENIE3                     & & & & \\
@@
 Directivity                & 0.535 & 0.526 & 0.533 & 0.535 \\
-Our approach + dir         & & & & \\
+Our approach + dir         & 0.944 & 0.943 & 0.942 & 0.940\\
 \bottomrule
@@
 Partial correlation (best) & 0.364 & 0.366 & 0.359 & 0.344 \\
-Our approach (best)        & & & & \\
+Our approach (best)        & 0.403 & 0.404 & 0.398 & 0.388 \\
 GENIE3                     & & & & \\
 GTE                        & & & & \\
-Directivity                & 0.012 & 0.012 & 0.012 & 0.012\\
-Our approach + dir         & & & & \\
+Directivity                & 0.012 & 0.012 & 0.012 & 0.012 \\
+Our approach + dir         & 0.404 & 0.405 & 0.399 & 0.389 \\
 \bottomrule

### 2014-06-13 article.tex
wip experimetns

--- 2014-06-13 article.tex
@@
 of the Connectomics challenge : normal-1, normal-2, normal-3, normal-4. Those
-datasets are time series of size $n=179500$ of image calcium from simulated
-neuronal network \cite{stetter2012model} with $p=1000$ neurons. The networks
-to inferred have around 15000 arcs or a density of $0.15\%$ and are similar to those
+datasets are time series of size $T=179500$ of image calcium from simulated
+neuronal network \cite{stetter2012model} with $|V|=1000$ neurons. The networks
+to inferred have around 15000 edge or a density of $0.15\%$ and are similar to those
 used to rank challenge participants. Note that our parameter tuning was mainly
@@
 P-P + Weights + PCA & 0.932 & 0.931 & 0.930 & 0.928 \\
-Averaging (PCA)     & 0.943 & 0.942 & 0.942 & 0.939 \\
-Stacking            & 0.944 & 0.943 & 0.942 & 0.940 \\
+Averaging           & & & & \\
+Stacking            & & & & \\
 \bottomrule
@@
 P-P + Weights + PCA & 0.364 & 0.366 & 0.359 & 0.344\\
-Averaging           & 0.403 & 0.404 & 0.398 & 0.388\\
-Stacking            & 0.404 & 0.405 & 0.399 & 0.389\\
+Averaging           & & & & \\
+Stacking            & & & & \\
 \bottomrule
@@
 P-P + Weights       & 0.826 & 0.823 & 0.817 & 0.799\\
+Averaging           & & & & \\
+Stacking            & & & & \\
 \bottomrule
@@
 P-P + Weights       & 0.079 & 0.071 & 0.067 & 0.064\\
+Averaging           & & & & \\
 \bottomrule

### 2014-06-13 article.tex
add a warning

--- 2014-06-13 article.tex
@@
 \section{Signal filtering} \label{sec:filter}
+
+\textcolor{red}{This section should be rewritten once we get the figure
+                which displayed the effect of the different filters.}
 

### 2014-06-13 article.tex
prune metric section

@@
 To assess our method, we have used four datasets provided by the organizer
-of the Connectomics challenge : normal-1, normal-2, normal-3, normal-4. Those
-datasets are time series of size $T=179500$ of image calcium from simulated
+of the Connectomics challenge : \textit{normal-1, normal-2, normal-3, normal-4}.
+Those datasets are time series of size $T=179500$ of image calcium from simulated
 neuronal network \cite{stetter2012model} with $|V|=1000$ neurons. The networks
-to inferred have around 15000 edge or a density of $0.15\%$ and are similar to those
+to inferred have around 15000 edge and are similar to those
 used to rank challenge participants. Note that our parameter tuning was mainly
@@
 % Metrics : ROC AUC and AUPRC
-The network inference task can be viewed as a binary classification task
-where one has to correctly classified the presence or the absence of edges
-of the graph. Given the ground true network $y_{i,j} \in \left\{0, 1\right\}$,
-the connectivity score matrix $\hat{y}_{i,j} \in \mathcal{R}$
-and threshold value $\tau$, we first define the notion of
-true positive $tp(\tau) = \sum_{i=1}^p \sum_{j=1}^p I(y_{i,j} = 1, \hat{y}_{i,j} \geq \tau)$,
-true negative $tn(\tau) = \sum_{i=1}^p \sum_{j=1}^p I(y_{i,j} = 0, \hat{y}_{i,j} < \tau)$,
-false negative $fn(\tau) = \sum_{i=1}^p \sum_{j=1}^p I(y_{i,j} = 1, \hat{y}_{i,j} < \tau)$ and
-false positive $fp(\tau) = n - tp(\tau) - tn(\tau) -fn(\tau)$.
-
-We assess the accuracy of the network inference using the area under
-the ROC curve (ROC AUC) obtained by varying the threshold
-$\tau$ of the true positive rate $tpr(\tau) = \frac{tp(\tau)}{tp(\tau) + fn(\tau)}$
-as a function of the false positive rate
-$fpr(\tau) = \frac{tn(\tau)}{tn(\tau) + fp(\tau)}$.  As suggested in
-\cite{schrynemackers2013protocols},
-we also compare the same methods with the area under the precision-recall
-curve (AUPRC) obtained by varying the threshold
-$\tau$ of the precision $P(\tau) = \frac{tp(\tau)}{tp(\tau) + fp(\tau)}$
-as a function of the recall $R(\tau) = \frac{tp(\tau)}{tp(\tau) + fn(\tau)}$
-in section (todo ref).
-Since  there is no self connection (neuron connected to itself), we set
-the diagonal elements of $\hat{y}_{i,j}$ to the minimum prior evaluation.
+In supervised learning term, the network inference task can be viewed as a
+binary classification task where one has to correctly classified the presence
+or the absence of edges of the graph. Given the ground true adjacency matrix
+$A$ and a connectivity score matrix $\hat{A}$, we assess the accuracy of the
+network inference method using the area under the ROC curve (ROC AUC)
+and the area under the precision-recall curve (AUPRC)
+(\cite{schrynemackers2013protocols}). Since neurons are not self-connected
+($(i, i) \not E, \forall i \in V$) and some inference methods could spuriously
+leave maximal scores to the diagonal of $\hat{A}$, e.g. Pearson correlation,
+we set those elements to the minimum of $\hat{A}$ prior evaluating those
+algorithms.
 

### 2014-06-13 article.tex
put supplementary results in appendix

@@
 (\cite{schrynemackers2013protocols}). Since neurons are not self-connected
-($(i, i) \not E, \forall i \in V$) and some inference methods could spuriously
-leave maximal scores to the diagonal of $\hat{A}$, e.g. Pearson correlation,
-we set those elements to the minimum of $\hat{A}$ prior evaluating those
-algorithms.
+($(i, i) \not \in E, \forall i \in V$) and some inference methods could
+spuriously leave maximal scores to the diagonal of $\hat{A}$, e.g. Pearson
+correlation, we set those elements to the minimum of $\hat{A}$ prior evaluating
+those algorithms.
 
@@
 Stacking            & 0.404 & 0.405 & 0.399 & 0.389\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-\begin{table}[H]
-\centering
-\caption{Correlation (ROC). Improvement of each stage of our approach. Note that we choose the
-         \textit{best} threshold (\textcolor{red}{for now 0.11}) for stages 1 to 4.}
-\begin{tabular}{*{5}{l}}
-\toprule
-Stage               & normal-1 & normal-2 & normal-3 & normal-4 \\
-\midrule
-Nothing             & 0.681 & 0.699 & 0.683 & 0.681\\
-Weights             & 0.695 & 0.713 & 0.697 & 0.694\\
-H-T                 & 0.876 & 0.873 & 0.877 & 0.869\\
-H-T + Weights       & 0.886 & 0.884 & 0.891 & 0.877\\
-P-P                 & 0.857 & 0.850 & 0.843 & 0.832\\
-P-P + Weights       & 0.826 & 0.823 & 0.817 & 0.799\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-\begin{table}[H]
-\centering
-\caption{Correlation (P-R). Improvement of each stage of our approach. Note that we choose the
-         \textit{best} threshold (\textcolor{red}{for now 0.11}) for stages 1 to 4.}
-\begin{tabular}{*{5}{l}}
-\toprule
-Stage               & normal-1 & normal-2 & normal-3 & normal-4 \\
-\midrule
-Nothing             & 0.028 & 0.028 & 0.025 & 0.026\\
-Weights             & 0.031 & 0.030 & 0.027 & 0.028\\
-H-T                 & 0.143 & 0.128 & 0.150 & 0.129\\
-H-T + Weights       & 0.153 & 0.145 & 0.170 & 0.132\\
-P-P                 & 0.100 & 0.087 & 0.079 & 0.083\\
-P-P + Weights       & 0.079 & 0.071 & 0.067 & 0.064\\
 \bottomrule
@@
 
+\newpage
+\clearpage
+
+\appendix
+
+\section{Supplementary results}
+
+\begin{table}[htbp]
+\centering
+\caption{Correlation (ROC). Improvement of each stage of our approach. Note that we choose the
+         \textit{best} threshold (\textcolor{red}{for now 0.11}) for stages 1 to 4.}
+\begin{tabular}{*{5}{l}}
+\toprule
+Stage               & normal-1 & normal-2 & normal-3 & normal-4 \\
+\midrule
+Nothing             & 0.681 & 0.699 & 0.683 & 0.681\\
+Weights             & 0.695 & 0.713 & 0.697 & 0.694\\
+H-T                 & 0.876 & 0.873 & 0.877 & 0.869\\
+H-T + Weights       & 0.886 & 0.884 & 0.891 & 0.877\\
+P-P                 & 0.857 & 0.850 & 0.843 & 0.832\\
+P-P + Weights       & 0.826 & 0.823 & 0.817 & 0.799\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{table}[htbp]
+\centering
+\caption{Correlation (P-R). Improvement of each stage of our approach. Note that we choose the
+         \textit{best} threshold (\textcolor{red}{for now 0.11}) for stages 1 to 4.}
+\begin{tabular}{*{5}{l}}
+\toprule
+Stage               & normal-1 & normal-2 & normal-3 & normal-4 \\
+\midrule
+Nothing             & 0.028 & 0.028 & 0.025 & 0.026\\
+Weights             & 0.031 & 0.030 & 0.027 & 0.028\\
+H-T                 & 0.143 & 0.128 & 0.150 & 0.129\\
+H-T + Weights       & 0.153 & 0.145 & 0.170 & 0.132\\
+P-P                 & 0.100 & 0.087 & 0.079 & 0.083\\
+P-P + Weights       & 0.079 & 0.071 & 0.067 & 0.064\\
+\bottomrule
+\end{tabular}
+\end{table}
+
 \end{document}

### 2014-06-13 article.tex
typo

@@
 % Metrics : ROC AUC and AUPRC
-In supervised learning term, the network inference task can be viewed as a
+In supervised learning terms, the network inference task can be viewed as a
 binary classification task where one has to correctly classified the presence

### 2014-06-13 article.tex
Disambiguish notation between random variables and nodes V

@@
 Let us denote the fluorescence calcium indicators of all neuron
-as a set of random variables $V = \left\{V_1, \ldots, V_{|V|}\right\}$, which follows
-a joint probability distribution $p_\mathcal{V}$, and by
-$V^{-i,j}$ the set of all variables except $V_i$ and $V_j$.
-Two random variables $V_i$ and $V_j$ are said to be conditionally independent
-to a (possibly empty) set of random variables $Z$, denoted by $V_i \perp V_j | Z$,
+as a set of random variables $X = \left\{X_1, \ldots, X_{|V|}\right\}$, which follows
+a joint probability distribution $p_\mathcal{X}$, and by
+$X^{-i,j}$ the set of all variables except $X_i$ and $X_j$.
+Two random variables $X_i$ and $X_j$ are said to be conditionally independent
+to a (possibly empty) set of random variables $Z$, denoted by $X_i \perp X_j | Z$,
 if the joint conditional probability distribution factorizes
-$p_{\mathcal{V}_i, \mathcal{V}_j|\mathcal{Z}} = p_{\mathcal{V}_i|\mathcal{Z}}
-p_{\mathcal{V}_j|\mathcal{Z}}$.  The inference of the undirected network
+$p_{\mathcal{X}_i, \mathcal{X}_j|\mathcal{Z}} = p_{\mathcal{X}_i|\mathcal{Z}}
+p_{\mathcal{X}_j|\mathcal{Z}}$.  The inference of the undirected network
 can be formulated as inferring conditional dependences
-$V_i \not\perp V_j | V^{-i,j}$ between all pair of fluorescence signal
+$X_i \not\perp X_j | X^{-i,j}$ between all pair of fluorescence signal
 $i$ and $j$, in other words the inferred network will be
-$\hat{A}: \hat{a}_{i,j} = I(V_i \not\perp V_j | V^{-i,j}), i, j \in V$.
+$\hat{A}: \hat{a}_{i,j} = I(X_i \not\perp X_j | X^{-i,j}), \forall i, j \in V$.
 
 Since all neurons are assumed to be connected to at least one neuron,
-we thus have by definition $V_i \not\perp V_j$. However,  two random
+we thus have by definition $X_i \not\perp X_j$. However,  two random
 variables $A$ and $B$ might be dependent taken alone ($A \not\perp B$), but not
 once we observe a third variables $C$ ($A \perp B | C$).
-The conditioning over all other random variables $V^{-i,j}$ is thus necessary
+The conditioning over all other random variables $X^{-i,j}$ is thus necessary
 to avoid predicting an edge when two neurons are not directly connected.
 
-If the random variables $V$ follows a joint Gaussian distribution
-$p_\mathcal{V} \sim \mathcal{N}(\mu; \Sigma)$ of mean vector $\mu$ and
+If the random variables $X$ follows a joint Gaussian distribution
+$p_\mathcal{X} \sim \mathcal{N}(\mu; \Sigma)$ of mean vector $\mu$ and
 covariance matrix $\Sigma$, we have the conditional independence
-$V_i \perp V_j | V^{-i,j}$ if the partial correlation coefficient
+$X_i \perp X_j | X^{-i,j}$ if the partial correlation coefficient
 \[
-\rho_{V_i, V_j | V^{-i,j}}
+\rho_{X_i, X_j | X^{-i,j}}
 = \frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii} \Sigma^{-1}_{jj}}}.
@@
 is equal zero. The partial correlation gives a connectivity score
-$\hat{A}: \hat{a}_{i,j} = \rho_{V_i, V_j | V^{-i,j}}, i, j \in V$ between all
-pair of neuron $i$ and $j$. One could retrieve an estimated graph by thresholding
+$\hat{A}: \hat{a}_{i,j} = \rho_{X_i, X_j | X^{-i,j}}, \forall i, j \in V$ between all
+pairs of neuron $i$ and $j$. One could retrieve an estimated graph by thresholding
 the matrix $\hat{A}$.
-By contrast, we also have $V_i \perp V_j$ if the Pearson correlation
+By contrast, we also have $X_i \perp X_j$ if the Pearson correlation
 coefficient
 \[
-\rho_{V_i,V_j} = \frac{\Sigma_{ij}}{\sqrt{\Sigma_{ii}
+\rho_{X_i,X_j} = \frac{\Sigma_{ij}}{\sqrt{\Sigma_{ii}
 \Sigma_{jj}}}
@@
 % Speak about why averaging
-The quality of the signal filtering and network inference depends
+The quality of the signal filtering and network inference depends on
 good hyper-parameter selection, which are themselves dependent on the properties
@@
 
-\subsection{Data filtering and Signal distribution}
+% TODO
+%   - discussions about the results
+%   - discussions about the metrics (Gilles text)
 
-\subsection{Inference of neuronal network}
-
-\begin{table}[H]
+\begin{table}[htb]
 \centering
@@
 
-\begin{table}[H]
+\begin{table}[htb]
 \centering

### 2014-06-13 article.tex
wording

@@
 ($(i, i) \not \in E, \forall i \in V$) and some inference methods could
-spuriously leave maximal scores to the diagonal of $\hat{A}$, e.g. Pearson
+give maximal scores to the diagonal of $\hat{A}$, e.g. Pearson
 correlation, we set those elements to the minimum of $\hat{A}$ prior evaluating

### 2014-06-13 article.tex
typos

@@
 % Datasets
-To assess our method, we have used four datasets provided by the organizer
+To assess our method, we have used four datasets provided by the organizers
 of the Connectomics challenge : \textit{normal-1, normal-2, normal-3, normal-4}.
 Those datasets are time series of size $T=179500$ of image calcium from simulated
-neuronal network \cite{stetter2012model} with $|V|=1000$ neurons. The networks
-to inferred have around 15000 edge and are similar to those
+neuronal networks (\cite{stetter2012model}) with $|V|=1000$ neurons. The networks
+to inferred have around 15000 edges and are similar to those
 used to rank challenge participants. Note that our parameter tuning was mainly
@@
 In supervised learning terms, the network inference task can be viewed as a
-binary classification task where one has to correctly classified the presence
+binary classification task where one has to correctly classify the presence
 or the absence of edges of the graph. Given the ground true adjacency matrix

### 2014-06-13 article.tex
remove section
no low rank hypothesis

@@
 
-Finally since there is a high correlation between neurons, we made a
-low-rank hypothesis and perform noise filtering through a principal component
-analysis. From the $p$ eigen vectors, we kept $80\%$ of
-the eigen vectors which have the largest eigen value. In the context of the
-challenge, this assumption was deduced from ground truth of provided network.
+Finally since there is a high correlation between neurons, we perform noise
+filtering through a principal component analysis. From the $p$ eigen vectors,
+we kept $80\%$ of the eigen vectors which have the largest eigen value. In the
+context of the challenge, this assumption was deduced from ground truth of
+provided networks.
 
@@
 %   - discussions about the results
-%   - discussions about the metrics (Gilles text)
+%   - discussions about the metrics (Gilles' text)
 
@@
 
-\subsection{Discussion about the metric}
-\label{sec:metric}
-
 \section{Conclusion}

### 2014-06-13 article.tex
wording

@@
 % Introduce directivity
-Since the partial correlation is a symmetric measure, the causal mechanism behind the
+Since partial correlation is a symmetric measure, the causal mechanism behind the
 interaction ($A$ directly causes $B$, $B$ directly causes $A$ or both) can not
@@
 conditionally correlated to a hidden variable affecting $B$ (resp. $A$)
-\cite{de2004discovery}.} from a symmetric adjacency matrix.
+\cite{de2004discovery}.}.
 
 By ignoring the directivity, we systematically make a true positive and a
-false positive for direct link (see a more detailed discussion about the
-chosen metric in section \ref{sec:metric}). Therefore, performance might be
-improved by predicting an asymmetric adjacency matrix. Hoping to orientate
+false positive for direct link.  Hoping to orientate
 correctly the most obvious directed links, we attempt to retrieve some causal
@@
 give maximal scores to the diagonal of $\hat{A}$, e.g. Pearson
-correlation, we set those elements to the minimum of $\hat{A}$ prior evaluating
-those algorithms.
+correlation, we set those elements to the minimum of $\hat{A}$ prior
+assessment.
 

### 2014-06-13 article.tex
the converse might not be true, if we don't consider all variable

@@
 variables $A$ and $B$ might be dependent taken alone ($A \not\perp B$), but not
-once we observe a third variables $C$ ($A \perp B | C$).
+once we observe the set  $C$ of all other variables ($A \perp B | C$).
 The conditioning over all other random variables $X^{-i,j}$ is thus necessary

### 2014-06-13 article.tex
notation detail + wording

@@
 along $T$ periods of time of the $|V|$ neurons, the goal is to infer the
-adjacency matrix $A : a_{i,j} = I((i, j) \in E)$ of the graph $G$,
-where $I$ is the indicator function.}
+adjacency matrix $A : a_{i,j} = \mathbb{1}((i, j) \in E)$ of the graph $G$,
+where $\mathbb{1}$ is the indicator function.}
 
@@
 X^{\prime\prime\prime}_{t,i} &=
-{X^{\prime\prime}_{t,i}}^{0.9} I(X^{\prime\prime}_{t,i} \geq \tau) \forall i
+{X^{\prime\prime}_{t,i}}^{0.9} \mathbb{1}(X^{\prime\prime}_{t,i} \geq \tau) \forall i
 \label{eq:hard-treshold-filter}
@@
 $i$ and $j$, in other words the inferred network will be
-$\hat{A}: \hat{a}_{i,j} = I(X_i \not\perp X_j | X^{-i,j}), \forall i, j \in V$.
+$\hat{A}: \hat{a}_{i,j} = \mathbb{1}(X_i \not\perp X_j | X^{-i,j}), \forall i, j \in V$.
 
@@
 \rho_{X_i, X_j | X^{-i,j}}
-= \frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii} \Sigma^{-1}_{jj}}}.
+= \frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii} \Sigma^{-1}_{jj}}}
 \]
@@
 the matrix $\hat{A}$.
-By contrast, we also have $X_i \perp X_j$ if the Pearson correlation
+Similarly, we also have $X_i \perp X_j$ if the Pearson correlation
 coefficient

### 2014-06-13 article.tex
ortho
FIX equation for directivity

@@
 Each node $i \in V$ represents a neuron, and each edge $(i, j) \in E$
-represents a direct link from neuron $i$ to neuron $j$.
+represents a direct link from a neuron $i$ to a neuron $j$.
 The network inference task is set as follows :
@@
 our symmetric adjacency matrix a matrix of pairwise activation heuristics.
-This method computes an anti-symmetric activation score $z_{ij}$ based the
+This method computes an anti-symmetric activation score $Z$ based the
 variation of fluorescence signal of a neuron $j$ due to a neuron $i$ over all
-timesteps:
+time steps:
 \[
-z_{ij} = \sum_{t=1}^n \mathbb{1}(X_{t+1,j} \ge X_{t, i}) \cdot
-\mathbb{1}(f_1\le X_t^i \le f_2) -  \mathbb{1}(X_{t+1,i} \ge X_{t, j}) \cdot
-\mathbb{1}(f_1 \le X_t^j \le f_2)
+\hat{Z}: z_{ij} = \sum_{t=1}^{T - 1}
+    \mathbb{1}(x_{t+1,j} - x_{t, i} \in \left[f1, f2 \right]) -
+    \mathbb{1}(x_{t+1,i} - x_{t, j} \in \left[f1, f2 \right])
 \]
-where $f_1$ and $f_2$ are parameters of the method and $I$ is the indicator
-function. Prior computing $z_{ij}$ only the filter defined by Equations
-\ref{eq:low-pass}, \ref{eq:high-pass} and \ref{eq:hard-treshold-filter} were
-used.
+where $f_1$ and $f_2$ are parameters of the method.
 
@@
 %   - discussions about the metrics (Gilles' text)
+
+For the directory method, only filters defined by Equations
+\ref{eq:low-pass}, \ref{eq:high-pass} and \ref{eq:hard-treshold-filter} were
+used.
 

### 2014-06-14 article.tex
add gte results

@@
 GENIE3                     & & & & \\
-GTE                        & & & & \\
+GTE                        & 0.890 & 0.893 & 0.894 & 0.873 \\
 Directivity                & 0.535 & 0.526 & 0.533 & 0.535 \\
@@
 GENIE3                     & & & & \\
-GTE                        & & & & \\
+GTE                        & 0.171 & 0.174 & 0.197 & 0.142 \\
 Directivity                & 0.012 & 0.012 & 0.012 & 0.012 \\

### 2014-06-14 article.tex
wording

@@
 % TODO check convention for y_{ij}
-The connectomes is represented by a (un)directed graph $G = (V, E)$ comprising
+The connectomes, the neural network, is represented by a (un)directed graph $G = (V, E)$ comprising
 a set of nodes $V$ and a set of edges $E \subseteq \left\{(i, j) \in V \times
@@
 along $T$ periods of time of the $|V|$ neurons, the goal is to infer the
-adjacency matrix $A : a_{i,j} = \mathbb{1}((i, j) \in E)$ of the graph $G$,
-where $\mathbb{1}$ is the indicator function.}
+adjacency matrix $A : a_{i,j} = \mathbb{1}((i, j) \in E)$ of the neural network
+of graph $G$, where $\mathbb{1}$ is the indicator function.}
 
@@
 can be formulated as inferring conditional dependences
-$X_i \not\perp X_j | X^{-i,j}$ between all pair of fluorescence signal
-$i$ and $j$, in other words the inferred network will be
+$X_i \not\perp X_j | X^{-i,j}$ between all pairs $i$ and $j$ of fluorescence
+signals, in other words the inferred network will be
 $\hat{A}: \hat{a}_{i,j} = \mathbb{1}(X_i \not\perp X_j | X^{-i,j}), \forall i, j \in V$.

### 2014-06-15 article.tex
proper citation for independance and partial correlation
add reference
fig in filtering part

@@
 \usepackage{bbold}
+\usepackage{wrapfig}
 
@@
 
-\title{Connectome inferences using partial correlation from imaging calcium signal}
+\title{\textcolor{red}{Simple} connectome inference using partial correlation from imaging calcium signal}
 
@@
 
-\textcolor{red}{This section should be rewritten once we get the figure
-                which displayed the effect of the different filters.}
+% \textcolor{red}{This section should be rewritten once we get the figure
+                % which displayed the effect of the different filters.}
 
@@
 indicator.
+
+\begin{wrapfigure}{r}{0.7\linewidth}
+\caption{Filtering steps.}\label{wrap-fig:1}
+\includegraphics[width=\linewidth]{code/code/fig_filtering.png}
+\end{wrapfigure}
 
@@
 \]
-is equal zero. The partial correlation gives a connectivity score
+is equal to zero (\cite{koller2009probabilistic}). The partial correlation gives
+a connectivity score
 $\hat{A}: \hat{a}_{i,j} = \rho_{X_i, X_j | X^{-i,j}}, \forall i, j \in V$ between all

### 2014-06-15 article.tex
wording in the filtering part

@@
 % Defects of the imaging device
-and will have to cope with
-a slower sampling rate than the neuron firing speed, a superposition
-of the activity of several neurons and the slow decay of fluorescent calcium
-indicator.
+% and will have to cope with
+% a slower sampling rate than the neuron firing speed, a superposition
+% of the activity of several neurons and the slow decay of fluorescent calcium
+% indicator.
+
+The raw signal is the calcium fluorescence imaging representing neuron activity.
+Considering the imaging process, we have to cope with a slower sampling rate than the neuron firing frequency and the slow decay of fluorescent calcium indicator after a neuron activity burst.
 

### 2014-06-15 article.tex
some wording about H-P filter

@@
 
-The raw signal is the calcium fluorescence imaging representing neuron activity.
-Considering the imaging process, we have to cope with a slower sampling rate than the neuron firing frequency and the slow decay of fluorescent calcium indicator after a neuron activity burst.
+\textcolor{red}{The raw signal is the calcium fluorescence imaging representing neuron activity.
+Considering the imaging process, we have to cope with a slower sampling rate than the neuron firing frequency and the slow decay of fluorescent calcium indicator after a neuron activity burst.}
 
@@
 Prior inferring the network, the fluorescent calcium time series
-are smoothed using several linear and non linear filters.
-Considering the short delay for a communication between neurons, slow events
-can be neglected to retrieve direct relationships. The average time
-delay is indeed about $1ms$ or $2ms$ while the fluorescent signal time
-resolution is $20ms$. Let us also highlight that even if two neurons are
-spatially far from each other, the information is expected in the same time
-step or at most in the next time step. Thus very low frequency event can be neglected.
-However, the image fluorescence calcium signal is also very noisy. Thus,
-A low-pass filter (Equation \ref{eq:low-pass}) is first applied followed by a
-high-pass filter (Equation \ref{eq:high-pass}), the discrete derivative of
-the signal,
-\begin{align}
-X^\prime_{t,i} &= \sum_{l=-3}^2 c_l^k X_{t+l,i} \forall i, \label{eq:low-pass}\\
-X^{\prime\prime}_{t,i} &= X^{\prime}_{t,i} - X^{\prime}_{t-1,i} \forall i, \label{eq:high-pass}
-\end{align}
-where the $c_l^k$ coefficients were taken in one of the four
-following tuples
-$\left(c_l^1\right)_{l=-3}^2=(0, 0, 1, 1, 1, 1)$,
-$\left(c_l^2\right)_{l=-3}^2=(0, 0, 1, 1, 1, 0)$,
-$\left(c_l^3\right)_{l=-3}^2=(1, 1, 1, 1, 0, 0)$ or
-$\left(c_l^4\right)_{l=-3}^2=(0.4, 0.8, 1, 1, 0, 0)$.
+are smoothed using several linear and non linear filters \textcolor{red}{in order to reduce the imaging process effects. We successively apply different filters listed below.} \\
+
+% However, the image fluorescence calcium signal is also very noisy. Thus,
+% A low-pass filter (Equation \ref{eq:low-pass}) is first applied followed by a
+% high-pass filter (Equation \ref{eq:high-pass}), the discrete derivative of
+% the signal,
+% \begin{align}
+% X^\prime_{t,i} &= \sum_{l=-3}^2 c_l^k X_{t+l,i} \forall i, \label{eq:low-pass}\\
+% X^{\prime\prime}_{t,i} &= X^{\prime}_{t,i} - X^{\prime}_{t-1,i} \forall i, \label{eq:high-pass}
+% \end{align}
+% where the $c_l^k$ coefficients were taken in one of the four
+% following tuples
+% $\left(c_l^1\right)_{l=-3}^2=(0, 0, 1, 1, 1, 1)$,
+% $\left(c_l^2\right)_{l=-3}^2=(0, 0, 1, 1, 1, 0)$,
+% $\left(c_l^3\right)_{l=-3}^2=(1, 1, 1, 1, 0, 0)$ or
+% $\left(c_l^4\right)_{l=-3}^2=(0.4, 0.8, 1, 1, 0, 0)$.
+
+\textcolor{red}{As it can be seen on \textit{fig 1}, the raw signal is very noisy and a low-pass filter is therefore applied to get a cleaner version of the signal where only true variations are kept, i.e.
+without noise variations.
+However, the choice of a low-pass filter is not unique.
+In the rest of the paper, we will focus on two types, the symmetrical median filter, i.e., $X_t^i \leftarrow X_{t-1}^i + X_{t}^i + X_{t+1}^i$, and an asymmetrical weighted median filter, i.e., $X_t^i \leftarrow 0.4 X_{t-3}^i + 0.6 X_{t-2}^i + 0.8 X_{t-1}^i + X_{t}^i$.}
+
+\textcolor{red}{Considering the short delay for a communication between neurons, slow events can be neglected to retrieve direct relationships.
+Indeed, for a direct relationship, i.e.
+a neuron firing directly implying another neuron to fire, the average time is about $1ms$ or $2ms$ while the fluorescent signal time resolution is $20ms$.
+In order to find out which neurons are directly related, it is only necessary to look after the burst signal, or in other words, wether there is a signal variable, i.e.
+a burst.}
+
+% Considering the short delay for a communication between neurons, slow events
+% can be neglected to retrieve direct relationships. The average time
+% delay is indeed about $1ms$ or $2ms$ while the fluorescent signal time
+% resolution is $20ms$. Let us also highlight that even if two neurons are
+% spatially far from each other, the delay should not exceed one time step. Thus very low frequency event can be neglected.
 

### 2014-06-15 article.tex
small changes in previous wording

@@
 a neuron firing directly implying another neuron to fire, the average time is about $1ms$ or $2ms$ while the fluorescent signal time resolution is $20ms$.
-In order to find out which neurons are directly related, it is only necessary to look after the burst signal, or in other words, wether there is a signal variable, i.e.
-a burst.}
+In order to find out which neurons are directly related, it is only necessary to look after the burst signal, or in other words, whether the signal varies.}
 

### 2014-06-15 article.tex
wording about threshold and weights

@@
 However, the choice of a low-pass filter is not unique.
-In the rest of the paper, we will focus on two types, the symmetrical median filter, i.e., $X_t^i \leftarrow X_{t-1}^i + X_{t}^i + X_{t+1}^i$, and an asymmetrical weighted median filter, i.e., $X_t^i \leftarrow 0.4 X_{t-3}^i + 0.6 X_{t-2}^i + 0.8 X_{t-1}^i + X_{t}^i$.}
+In the rest of the paper, we will focus on two types, the symmetrical median filter, i.e., $X_t^i \leftarrow X_{t-1}^i + X_{t}^i + X_{t+1}^i$, and an asymmetrical weighted median filter, i.e., $X_t^i \leftarrow 0.4 X_{t-3}^i + 0.6 X_{t-2}^i + 0.8 X_{t-1}^i + X_{t}^i$.}\\
 
@@
 a neuron firing directly implying another neuron to fire, the average time is about $1ms$ or $2ms$ while the fluorescent signal time resolution is $20ms$.
-In order to find out which neurons are directly related, it is only necessary to look after the burst signal, or in other words, whether the signal varies.}
+In order to find out which neurons are directly related, it is only necessary to look after the burst signal, or in other words, whether the signal varies.
+In our approach, we choose to apply an asymmetrical discrete derivative : $X_{t,d}^{i} \leftarrow X_{t}^i - X_{t-1}^i$.}\\
+
+\textcolor{red}{By nature, the firing event is really fast and in order to retrieve the connectivity from them, it is necessary to link a burst to a couple of timesteps (ideally one).
+The small decay for the fluorescent calcium indicator implies a signal variation during a long interval and therefore, in order to only keep rising and strong transitions, we apply a hard-tresholing filter: $X_{t,d}^i = X_{t,d}^i \mathbb{1}(X_{t,d}^i \geq \tau)$
+As a result, we get a binary-like signal with the true activity when a burst happens and with a true zero when the neuron is inactive.}
 
@@
 
-Connectivity information between two neurons may be retrieved from successive
-and slightly delayed burst events. Direct links
-between two neurons should have shorter delay between fluorescence
-peaks than undirected links. However, the fluorescence signal has a slow
-decay compare to its rise. Therefore, we filter those unrelevant information
-with a hard thresholding filter
-\begin{align}
-X^{\prime\prime\prime}_{t,i} &=
-{X^{\prime\prime}_{t,i}}^{0.9} \mathbb{1}(X^{\prime\prime}_{t,i} \geq \tau) \forall i
-\label{eq:hard-treshold-filter}
-\end{align}
-where $\tau \geq 0$ is a parameter of the hard-threshold filter and the $0.9$
-exponent reduce the difference between peaks values.
+% Connectivity information between two neurons may be retrieved from successive
+% and slightly delayed burst events. Direct links
+% between two neurons should have shorter delay between fluorescence
+% peaks than undirected links. However, the fluorescence signal has a slow
+% decay compare to its rise. Therefore, we filter those unrelevant information
+% with a hard thresholding filter
+% \begin{align}
+% X^{\prime\prime\prime}_{t,i} &=
+% {X^{\prime\prime}_{t,i}}^{0.9} \mathbb{1}(X^{\prime\prime}_{t,i} \geq \tau) \forall i
+% \label{eq:hard-treshold-filter}
+% \end{align}
+% where $\tau \geq 0$ is a parameter of the hard-threshold filter and the $0.9$
+% exponent reduce the difference between peaks values.
 
-Then we apply on all remaining timesteps $T$ a non-linear filter based on the current
-activity of the systems in order to favor the association measure when
-a medium size set of neurons are firing together, while artificially
-reducing the association measure in case of extreme network activity,
-i.e. high when a network firing is happening and low when no neuron is
-active:
-\begin{equation}
-X^{\prime\prime\prime\prime}_{t,i} =
-\left\{
-  \begin{array}{l}
-    1  : r_t < 0\\
-    {(X^{\prime\prime\prime}_{t,i} + 1)^{(a_t^{-1} + 1)}}^{g(r_t)} : r_t \geq 0
-  \end{array}
-\right.
-\text{ with }
-\left\{
-  \begin{array}{ll}
-    a_t &= \sum_{i=1}^p X^{\prime\prime\prime}_{t,i} +
-                       \frac{1}{2} X^{\prime\prime\prime}_{t-1,i} \forall t \in T\\
-    r_t &= \frac{a_t}{\max_{l \in T}{a_l}} \\
-  \end{array}
-\right.
-\end{equation}
-where $g(x) = b_1 I(f_4 < x < f_5) + b_2  I(f_5 \leq x < f_6) +
-b_3 (I(x\leq f_4) + I(f_ 6 \leq x))$ is a piecewise continuous function of
-parameters $b_1, b_2, b_3, f_4, f_5, f_6$. The coefficient were tuned
-for each set $i\in\left\{1, 2, 3, 4\right\}$ of coefficient
-$\left(c_l^i\right)_{l=-3}^2$.
+\textcolor{red}{Then we apply on the entire signal a non-linear filter base on the current activity of the systems in order to favor the association measure inversely proportional to the number of neurons firing together:$ X_{t,w}^i  = (X_{t,d}^i + 1 )^{1 + \frac{1}{\sum_{j} X_{t,d}^j}} $.
+When too much neurons are firing together, i.e.
+a network burst, it is almost impossible to retrieve direct relationships: all neurons seem to be directly connected to each other.
+By favoring the association measure when the activity is low, we expect to retrieve a pair of neurons that are really directly connected together.
+}
 
-Finally since there is a high correlation between neurons, we perform noise
-filtering through a principal component analysis. From the $p$ eigen vectors,
-we kept $80\%$ of the eigen vectors which have the largest eigen value. In the
-context of the challenge, this assumption was deduced from ground truth of
-provided networks.
+% Then we apply on all remaining timesteps $T$ a non-linear filter based on the current activity of the systems in order to favor the association measure when a medium size set of neurons are firing together, while artificially
+% reducing the association measure in case of extreme network activity,
+% i.e. high when a network firing is happening and low when no neuron is
+% active:
+
+% \begin{equation}
+% X^{\prime\prime\prime\prime}_{t,i} =
+% \left\{
+%   \begin{array}{l}
+%     1  : r_t < 0\\
+%     {(X^{\prime\prime\prime}_{t,i} + 1)^{(a_t^{-1} + 1)}}^{g(r_t)} : r_t \geq 0
+%   \end{array}
+% \right.
+% \text{ with }
+% \left\{
+%   \begin{array}{ll}
+%     a_t &= \sum_{i=1}^p X^{\prime\prime\prime}_{t,i} +
+%                        \frac{1}{2} X^{\prime\prime\prime}_{t-1,i} \forall t \in T\\
+%     r_t &= \frac{a_t}{\max_{l \in T}{a_l}} \\
+%   \end{array}
+% \right.
+% \end{equation}
+% where $g(x) = b_1 I(f_4 < x < f_5) + b_2  I(f_5 \leq x < f_6) +
+% b_3 (I(x\leq f_4) + I(f_ 6 \leq x))$ is a piecewise continuous function of
+% parameters $b_1, b_2, b_3, f_4, f_5, f_6$. The coefficient were tuned
+% for each set $i\in\left\{1, 2, 3, 4\right\}$ of coefficient
+% $\left(c_l^i\right)_{l=-3}^2$.
+
+% Finally since there is a high correlation between neurons, we perform noise
+% filtering through a principal component analysis. From the $p$ eigen vectors,
+% we kept $80\%$ of the eigen vectors which have the largest eigen value. In the
+% context of the challenge, this assumption was deduced from ground truth of
+% provided networks.
 

### 2014-06-16 article.tex
fix path to image
break at 80

@@
 
-\textcolor{red}{The raw signal is the calcium fluorescence imaging representing neuron activity.
-Considering the imaging process, we have to cope with a slower sampling rate than the neuron firing frequency and the slow decay of fluorescent calcium indicator after a neuron activity burst.}
+\textcolor{red}{The raw signal is the calcium fluorescence imaging representing
+neuron activity. Considering the imaging process, we have to cope with a slower 
+sampling rate than the neuron firing frequency and the slow decay of fluorescent 
+calcium indicator after a neuron activity burst.}
 
@@
 \caption{Filtering steps.}\label{wrap-fig:1}
-\includegraphics[width=\linewidth]{code/code/fig_filtering.png}
+\includegraphics[width=\linewidth]{images/fig_filtering_recut.png}
 \end{wrapfigure}
@@
 Prior inferring the network, the fluorescent calcium time series
-are smoothed using several linear and non linear filters \textcolor{red}{in order to reduce the imaging process effects. We successively apply different filters listed below.} \\
+are smoothed using several linear and non linear filters \textcolor{red}{in 
+order to reduce the imaging process effects. We successively apply different 
+filters listed below.} \\
 
@@
 
-\textcolor{red}{As it can be seen on \textit{fig 1}, the raw signal is very noisy and a low-pass filter is therefore applied to get a cleaner version of the signal where only true variations are kept, i.e.
-without noise variations.
-However, the choice of a low-pass filter is not unique.
-In the rest of the paper, we will focus on two types, the symmetrical median filter, i.e., $X_t^i \leftarrow X_{t-1}^i + X_{t}^i + X_{t+1}^i$, and an asymmetrical weighted median filter, i.e., $X_t^i \leftarrow 0.4 X_{t-3}^i + 0.6 X_{t-2}^i + 0.8 X_{t-1}^i + X_{t}^i$.}\\
+\textcolor{red}{As it can be seen on \textit{fig 1}, the raw signal is very noisy and 
+a low-pass filter is therefore applied to get a cleaner version of the signal where only 
+true variations are kept, i.e. without noise variations. However, the choice of a low-pass 
+filter is not unique. In the rest of the paper, we will focus on two types, the 
+symmetrical median filter, i.e., $X_t^i \leftarrow X_{t-1}^i + X_{t}^i + X_{t+1}^i$, 
+and an asymmetrical weighted median filter, i.e., 
+$X_t^i \leftarrow 0.4 X_{t-3}^i + 0.6 X_{t-2}^i + 0.8 X_{t-1}^i + X_{t}^i$.}\\
 
-\textcolor{red}{Considering the short delay for a communication between neurons, slow events can be neglected to retrieve direct relationships.
-Indeed, for a direct relationship, i.e.
-a neuron firing directly implying another neuron to fire, the average time is about $1ms$ or $2ms$ while the fluorescent signal time resolution is $20ms$.
-In order to find out which neurons are directly related, it is only necessary to look after the burst signal, or in other words, whether the signal varies.
-In our approach, we choose to apply an asymmetrical discrete derivative : $X_{t,d}^{i} \leftarrow X_{t}^i - X_{t-1}^i$.}\\
+\textcolor{red}{Considering the short delay for a communication between 
+neurons, slow events can be neglected to retrieve direct relationships. 
+Indeed, for a direct relationship, i.e. a neuron firing directly implying another 
+neuron to fire, the average time is about $1ms$ or $2ms$ while the 
+fluorescent signal time resolution is $20ms$. In order to find out which neurons 
+are directly related, it is only necessary to look after the burst signal, or 
+in other words, whether the signal varies. In our approach, we choose to apply 
+an asymmetrical discrete derivative : $X_{t,d}^{i} \leftarrow X_{t}^i - X_{t-1}^i$.}\\
 
-\textcolor{red}{By nature, the firing event is really fast and in order to retrieve the connectivity from them, it is necessary to link a burst to a couple of timesteps (ideally one).
-The small decay for the fluorescent calcium indicator implies a signal variation during a long interval and therefore, in order to only keep rising and strong transitions, we apply a hard-tresholing filter: $X_{t,d}^i = X_{t,d}^i \mathbb{1}(X_{t,d}^i \geq \tau)$
-As a result, we get a binary-like signal with the true activity when a burst happens and with a true zero when the neuron is inactive.}
+\textcolor{red}{By nature, the firing event is really fast and in order to 
+retrieve the connectivity from them, it is necessary to link a burst to a 
+couple of timesteps (ideally one). The small decay for the fluorescent calcium 
+indicator implies a signal variation during a long interval and therefore, in 
+order to only keep rising and strong transitions, we apply a hard-tresholing filter: 
+$X_{t,d}^i = X_{t,d}^i \mathbb{1}(X_{t,d}^i \geq \tau)$ 
+As a result, we get a binary-like signal with the true activity when a burst 
+happens and with a true zero when the neuron is inactive.}
 
@@
 
-\textcolor{red}{Then we apply on the entire signal a non-linear filter base on the current activity of the systems in order to favor the association measure inversely proportional to the number of neurons firing together:$ X_{t,w}^i  = (X_{t,d}^i + 1 )^{1 + \frac{1}{\sum_{j} X_{t,d}^j}} $.
-When too much neurons are firing together, i.e.
-a network burst, it is almost impossible to retrieve direct relationships: all neurons seem to be directly connected to each other.
-By favoring the association measure when the activity is low, we expect to retrieve a pair of neurons that are really directly connected together.
+\textcolor{red}{Then we apply on the entire signal a non-linear filter base on the 
+current activity of the systems in order to favor the association measure inversely 
+proportional to the number of neurons firing together:
+$ X_{t,w}^i  = (X_{t,d}^i + 1 )^{1 + \frac{1}{\sum_{j} X_{t,d}^j}} $. 
+When too much neurons are firing together, i.e. a network burst, it is almost 
+impossible to retrieve direct relationships: all neurons seem to be directly 
+connected to each other. By favoring the association measure when the activity is low, 
+we expect to retrieve a pair of neurons that are really directly connected together. 
 }
@@
 Since all neurons are assumed to be connected to at least one neuron,
-we thus have by definition $X_i \not\perp X_j$. However,  two random
+we thus have by definition $X_i \not\perp X_j$ \textcolor{red}{AS: Je ne suis pas sûr de comprendre.}. However,  two random
 variables $A$ and $B$ might be dependent taken alone ($A \not\perp B$), but not

### 2014-06-16 article.tex
add ref to image in weights

@@
 four stages, using preprocessing and partial correlation to achieve a network
-inference of high quality. We put in perspective our method
+inference of high quality. An optimized variation of this simple algorithm 
+is the winning method of the Connectomics Challenge.
+
+We put in perspective our method
 with other inference methods such as GTE (\cite{stetter2012model}) and Genie3
@@
 order to only keep rising and strong transitions, we apply a hard-tresholing filter: 
-$X_{t,d}^i = X_{t,d}^i \mathbb{1}(X_{t,d}^i \geq \tau)$ 
+$X_{t,d}^i = X_{t,d}^i \mathbb{1}(X_{t,d}^i \geq \tau)$ where $\tau$ is a given threshold.
 As a result, we get a binary-like signal with the true activity when a burst 
@@
 
-\textcolor{red}{Then we apply on the entire signal a non-linear filter base on the 
+\textcolor{red}{Then we apply on the entire signal a non-linear filter based on the 
 current activity of the systems in order to favor the association measure inversely 
@@
 $ X_{t,w}^i  = (X_{t,d}^i + 1 )^{1 + \frac{1}{\sum_{j} X_{t,d}^j}} $. 
-When too much neurons are firing together, i.e. a network burst, it is almost 
+When too much neurons are firing together, i.e. in case of a network burst, it is almost 
 impossible to retrieve direct relationships: all neurons seem to be directly 
@@
 we expect to retrieve a pair of neurons that are really directly connected together. 
+In concrete terms, as it can be verified on \textit{fig 1}, peak intensity may change in function 
+of the activity of all neurons but the number and the locations of peaks is not modified.
 }

### 2014-06-16 article.tex
small modifs
notation change

@@
 The network inference task is set as follows :
-\textit{Given the observations $(x_t \in \mathcal{R}^{|V|})_{t=1}^T $
+\textit{Given the observations $(x^t \in \mathcal{R}^{|V|})_{t=1}^T $
 along $T$ periods of time of the $|V|$ neurons, the goal is to infer the

### 2014-06-16 article.tex
notation changed

@@
 is the winning method of the Connectomics Challenge.
-
 We put in perspective our method
@@
 filter is not unique. In the rest of the paper, we will focus on two types, the
-symmetrical median filter, i.e., $X_t^i \leftarrow X_{t-1}^i + X_{t}^i + X_{t+1}^i$,
+symmetrical median filter, i.e., $x^t_i \leftarrow x^{t-1}_i + x^{t}_i + x^{t+1}_i$,
 and an asymmetrical weighted median filter, i.e.,
-$X_t^i \leftarrow 0.4 X_{t-3}^i + 0.6 X_{t-2}^i + 0.8 X_{t-1}^i + X_{t}^i$.}\\
+$x^t_i \leftarrow 0.4 x^{t-3}_i + 0.6 x^{t-2}_i + 0.8 x^{t-1}_i + X^{t}_i$.}\\
 
@@
 in other words, whether the signal varies. In our approach, we choose to apply
-an asymmetrical discrete derivative : $X_{t,d}^{i} \leftarrow X_{t}^i - X_{t-1}^i$.}\\
+an asymmetrical discrete derivative : $x^{t,d}_{i} \leftarrow x^{t}_i - X^{t-1}_i$.}\\
 
@@
 retrieve the connectivity from them, it is necessary to link a burst to a
-couple of timesteps (ideally one). The small decay for the fluorescent calcium
+couple of timesteps (ideally one).
+
+The small decay for the fluorescent calcium
 indicator implies a signal variation during a long interval and therefore, in
 order to only keep rising and strong transitions, we apply a hard-tresholing filter:
-$X_{t,d}^i = X_{t,d}^i \mathbb{1}(X_{t,d}^i \geq \tau)$ where $\tau$ is a given threshold.
+$x^{t,d}_i = X^{t,d}_i \mathbb{1}(x^{t,d}_i \geq \tau)$ where $\tau$ is a given threshold 
 As a result, we get a binary-like signal with the true activity when a burst
@@
 
-Since all neurons are assumed to be connected to at least one neuron,
-we thus have by definition $X_i \not\perp X_j$ \textcolor{red}{AS: Je ne suis pas sûr de comprendre.}. However,  two random
-variables $A$ and $B$ might be dependent taken alone ($A \not\perp B$), but not
-once we observe the set  $C$ of all other variables ($A \perp B | C$).
-The conditioning over all other random variables $X^{-i,j}$ is thus necessary
-to avoid predicting an edge when two neurons are not directly connected.
+Since all neurons are assumed to be connected to at least one neuron, we thus
+have by definition $X_i \not\perp X_j$ \textcolor{red}{AS: Je ne suis pas sûr
+de comprendre.}. However,  two random variables $A$ and $B$ might be
+dependent taken alone ($A \not\perp B$), but not once we observe the set  $C$
+of all other variables ($A \perp B | C$). The conditioning over all other
+random variables $X^{-i,j}$ is thus necessary to avoid predicting an edge when
+two neurons are not directly connected.
 

### 2014-06-16 article.tex
Add notion of causality

--- 2014-06-16 article.tex
@@
 Each node $i \in V$ represents a neuron, and each edge $(i, j) \in E$
-represents a direct link from a neuron $i$ to a neuron $j$.
-The network inference task is set as follows :
+represents a direct link and interactions between neuron $i$ and a neuron $j$.
+In the directed graph, each edges also expresses a causal relationship: an
+edge $(i, j) \in E$ indicates that the state of neuron $j$ might be caused
+by the neuron $i$. The network inference task is set as follows :
 \textit{Given the observations $(x^t \in \mathcal{R}^{|V|})_{t=1}^T $

### 2014-06-16 article.tex
fix ambiguity with separated graph
re-wrote directivity section

@@
 
-Since all neurons are assumed to be connected to at least one neuron, we thus
-have by definition $X_i \not\perp X_j$ \textcolor{red}{AS: Je ne suis pas sûr
-de comprendre.}. However,  two random variables $A$ and $B$ might be
+Since all neurons are assumed to form a connected graph, we
+have by construction $X_i \not\perp X_j$. However, two random variables $A$ and $B$ might be
 dependent taken alone ($A \not\perp B$), but not once we observe the set  $C$
@@
 
-\subsection{Causal discovery methodology}
 % Introduce a custom solution to make the Y matrix asymmetric
@@
 \cite{de2004discovery}.}.
-
-By ignoring the directivity, we systematically make a true positive and a
-false positive for direct link.  Hoping to orientate
-correctly the most obvious directed links, we attempt to retrieve some causal
-information, i.e. the directivity of the links, by computing and stacking with
-our symmetric adjacency matrix a matrix of pairwise activation heuristics.
-This method computes an anti-symmetric activation score $Z$ based the
-variation of fluorescence signal of a neuron $j$ due to a neuron $i$ over all
-time steps:
+In order to retrieve causal information, we developed an
+heuristics based on the following observation. The rise of fluorescence
+indicates the activation of a neuron $i$. If a neuron $j$ have also
+an increased of fluorescence after a slight delay, this could have been
+caused by the neuron $i$. Thus, we count whenever
+such events occurred between consecutive time steps
 \[
 \hat{Z}: z_{ij} = \sum_{t=1}^{T - 1}
-    \mathbb{1}(x_{t+1,j} - x_{t, i} \in \left[f1, f2 \right]) -
-    \mathbb{1}(x_{t+1,i} - x_{t, j} \in \left[f1, f2 \right])
+    \mathbb{1}(x_j^{t+1} - x_i^t \in \left[f_1, f_2 \right]) -
+    \mathbb{1}(x_i^{t+1} - x_j^t \in \left[f_1, f_2 \right]), \forall i, j \in V
 \]
 where $f_1$ and $f_2$ are parameters of the method.
+Finally, the weighted average of correlation matrices is combined with $Z$ such
+that $Z$ has a contribution of $0.3\%$ to the connectivity score matrix.
 

### 2014-06-16 article.tex

@@
 Finally, the weighted average of correlation matrices is combined with $Z$ such
-that $Z$ has a contribution of $0.3\%$ to the connectivity score matrix.
+that $Z$ has a contribution of $0.3\%$ to the prediction of an edge.
 

### 2014-06-16 article.tex
introduction wording to define some notions

--- 2014-06-16 article.tex
@@
 Each node $i \in V$ represents a neuron, and each edge $(i, j) \in E$
-represents a direct link and interactions between neuron $i$ and a neuron $j$.
-In the directed graph, each edges also expresses a causal relationship: an
-edge $(i, j) \in E$ indicates that the state of neuron $j$ might be caused
-by the neuron $i$. The network inference task is set as follows :
+represents a direct link from a neuron $i$ to a neuron $j$.
+The network inference task is set as follows :
 \textit{Given the observations $(x^t \in \mathcal{R}^{|V|})_{t=1}^T $
@@
 of graph $G$, where $\mathbb{1}$ is the indicator function.}
+
+The directivity in the network introduce causal relations through neurons.
+A directed edge, i.e.
+$a_{i,j} = 1$ and $a_{j,i} = 0$, means that neuron $i$ causes $j$.
+The causal mechanism implies that when neuron $i$ is active, also denoted in this paper as a firing event or a burst, neuron $j$ will be consequently active aftewards.
+The reciprocal phenomenon is only possible when the edge is bidirectionnal, i.e.
+$a_{i,j} = 1 = a_{j,i} = 1$.
 
@@
 
-\textcolor{red}{The raw signal is the calcium fluorescence imaging representing
+The raw signal is the calcium fluorescence imaging representing
 neuron activity. Considering the imaging process, we have to cope with a slower
 sampling rate than the neuron firing frequency and the slow decay of fluorescent
-calcium indicator after a neuron activity burst.}
+calcium indicator after a neuron activity burst.
 
-\begin{wrapfigure}{r}{0.7\linewidth}
+\begin{figure}%{r}{0.7\linewidth}
 \caption{Filtering steps.}\label{wrap-fig:1}
 \includegraphics[width=\linewidth]{images/fig_filtering_recut.png}
-\end{wrapfigure}
+\end{figure}
 
@@
 Prior inferring the network, the fluorescent calcium time series
-are smoothed using several linear and non linear filters \textcolor{red}{in
+are smoothed using several linear and non linear filters in
 order to reduce the imaging process effects. We successively apply different
-filters listed below.} \\
+filters listed below.
 
@@
 
-\textcolor{red}{As it can be seen on \textit{fig 1}, the raw signal is very noisy and
+As it can be seen on \textit{fig 1}, the raw signal is very noisy and
 a low-pass filter is therefore applied to get a cleaner version of the signal where only
@@
 filter is not unique. In the rest of the paper, we will focus on two types, the
-symmetrical median filter, i.e., $X_t^i \leftarrow X_{t-1}^i + X_{t}^i + X_{t+1}^i$,
+symmetrical median filter, i.e., $x^t_i \leftarrow x^{t-1}_i + x^{t}_i + x^{t+1}_i$,
 and an asymmetrical weighted median filter, i.e.,
-$X_t^i \leftarrow 0.4 X_{t-3}^i + 0.6 X_{t-2}^i + 0.8 X_{t-1}^i + X_{t}^i$.}\\
+$x^t_i \leftarrow 0.4 x^{t-3}_i + 0.6 x^{t-2}_i + 0.8 x^{t-1}_i + x_{t}^i$.
 
-\textcolor{red}{Considering the short delay for a communication between
+Considering the short delay for a communication between
 neurons, slow events can be neglected to retrieve direct relationships.
@@
 in other words, whether the signal varies. In our approach, we choose to apply
-an asymmetrical discrete derivative : $X_{t,d}^{i} \leftarrow X_{t}^i - X_{t-1}^i$.}\\
+an asymmetrical discrete derivative : $x^{t,d}_{i} \leftarrow x^{t}_i - x_{t-1}^i$.
 
-\textcolor{red}{By nature, the firing event is really fast and in order to
+By nature, the firing event is really fast and in order to
 retrieve the connectivity from them, it is necessary to link a burst to a
-couple of timesteps (ideally one). The small decay for the fluorescent calcium
+couple of timesteps (ideally one).
+
+The small decay for the fluorescent calcium
 indicator implies a signal variation during a long interval and therefore, in
 order to only keep rising and strong transitions, we apply a hard-tresholing filter:
-$X_{t,d}^i = X_{t,d}^i \mathbb{1}(X_{t,d}^i \geq \tau)$ where $\tau$ is a given threshold.
+$x^{t,d}_i = X^{t,d}_i \mathbb{1}(x^{t,d}_i \geq \tau)$ where $\tau$ is a given threshold 
 As a result, we get a binary-like signal with the true activity when a burst
-happens and with a true zero when the neuron is inactive.}
+happens and with a true zero when the neuron is inactive.
 
@@
 
-\textcolor{red}{Then we apply on the entire signal a non-linear filter based on the
+Then we apply on the entire signal a non-linear filter based on the
 current activity of the systems in order to favor the association measure inversely
 proportional to the number of neurons firing together:
-$ X_{t,w}^i  = (X_{t,d}^i + 1 )^{1 + \frac{1}{\sum_{j} X_{t,d}^j}} $.
+$ X_{t,w}^i  = (x^{t,d}_i + 1 )^{1 + \frac{1}{\sum_{j} X_{t,d}^j}} $.
 When too much neurons are firing together, i.e. in case of a network burst, it is almost
@@
 of the activity of all neurons but the number and the locations of peaks is not modified.
-}
 

### 2014-06-16 article.tex
wording in filtering

@@
 $a_{i,j} = 1$ and $a_{j,i} = 0$, means that neuron $i$ causes $j$.
-The causal mechanism implies that when neuron $i$ is active, also denoted in this paper as a firing event or a burst, neuron $j$ will be consequently active aftewards.
+The causal mechanism implies that when neuron $i$ is active, also denoted in this paper as a firing event or a burst, neuron $j$ will be afterwards active consequently.
 The reciprocal phenomenon is only possible when the edge is bidirectionnal, i.e.
-$a_{i,j} = 1 = a_{j,i} = 1$.
+$a_{i,j} = a_{j,i} = 1$.
 
@@
 
-The raw signal is the calcium fluorescence imaging representing
-neuron activity. Considering the imaging process, we have to cope with a slower
-sampling rate than the neuron firing frequency and the slow decay of fluorescent
-calcium indicator after a neuron activity burst.
+The raw signal is the calcium fluorescence imaging representing neuron
+activity via a capture imaging process. Observing the fluorescent calcium as
+an indicator of neuron activity delivers a 2-D view of neuron network at each
+capture which only gives a network screenshot at given time points. It implies
+obvious issues. Some neurons may be invisible because they are not observed or
+they are confounded with another one because of the loss of the third
+dimension. The capture sample rate is also a constraint that could make
+difficult to detect in which order the neurons fire.  Moreover the activity
+indicator is highly reactive to a burst but takes some time to recover its non
+active state.
+Finally, the difficulty to distinguish direct relationships when there is a network burst, defined as a highly synchronous activity [Stetter and in Stetter [20,46,47]], is increased by the slow sampling rate.
+
+Considering the described imaging process, we try in this
+section to cope with some of these issues and, in particular, the slower
+sampling rate than the neuron firing frequency and the slow decay of
+fluorescent calcium indicator after a neuron activity burst.
 
@@
 
-As it can be seen on \textit{fig 1}, the raw signal is very noisy and
-a low-pass filter is therefore applied to get a cleaner version of the signal where only
+As it can be seen on \textit{fig 1}, the raw signal is very noisy due to light scattering artifacts that ordinarily affects the quality of the recording [in Stetter, [6]].
+Therefore, a low-pass filter is first applied to get a cleaner version of the signal where only
 true variations are kept, i.e. without noise variations. However, the choice of a low-pass
-filter is not unique. In the rest of the paper, we will focus on two types, the
+filter is not unique. In the rest of the paper, we will use two particular filters giving similar results, the
 symmetrical median filter, i.e., $x^t_i \leftarrow x^{t-1}_i + x^{t}_i + x^{t+1}_i$,
@@
 
-The small decay for the fluorescent calcium
-indicator implies a signal variation during a long interval and therefore, in
-order to only keep rising and strong transitions, we apply a hard-tresholing filter:
-$x^{t,d}_i = X^{t,d}_i \mathbb{1}(x^{t,d}_i \geq \tau)$ where $\tau$ is a given threshold 
+The small decay for the fluorescent calcium indicator implies a signal
+variation during a long time interval. Firing event are represented by 
+strong variations in the neuron activity. Therefore we apply a hard-tresholding 
+filter $x^{t,d}_i = x^{t,d}_i \mathbb{1}(x^{t,d}_i \geq \tau)$ where the threshold $\tau$ should be taken positive to keep only rising edges and non close to zeros in order to only consider strong variations.
+
 As a result, we get a binary-like signal with the true activity when a burst
@@
 proportional to the number of neurons firing together:
-$ X_{t,w}^i  = (x^{t,d}_i + 1 )^{1 + \frac{1}{\sum_{j} X_{t,d}^j}} $.
+$ x^{t,w}_i  = (x^{t,d}_i + 1 )^{1 + \frac{1}{\sum_{j} X_{t,d}^j}} $.
 When too much neurons are firing together, i.e. in case of a network burst, it is almost

### 2014-06-16 article.tex
wording in filtering

@@
 active state.
-Finally, the difficulty to distinguish direct relationships when there is a network burst, defined as a highly synchronous activity [Stetter and in Stetter [20,46,47]], is increased by the slow sampling rate.
+Finally, the difficulty to distinguish direct relationships when a network burst happens, defined as a highly synchronous activity [Stetter and in Stetter [20,46,47]], is increased by the slow sampling rate.
 

### 2014-06-16 article.tex

@@
 \cite{de2004discovery}.}.
-
-By ignoring the directivity, we systematically make a true positive and a
-false positive for direct link.  Hoping to orientate
-correctly the most obvious directed links, we attempt to retrieve some causal
-information, i.e. the directivity of the links, by computing and stacking with
-our symmetric adjacency matrix a matrix of pairwise activation heuristics.
-This method computes an anti-symmetric activation score $Z$ based the
-variation of fluorescence signal of a neuron $j$ due to a neuron $i$ over all
-time steps:
+In order to retrieve causal information, we developed an
+heuristics based on the following observation. The rise of fluorescence
+indicates the activation of a neuron $i$. If a neuron $j$ have also
+an increased of fluorescence after a slight delay, this could have been
+caused by the neuron $i$. Thus, we count whenever
+such events occurred between consecutive time steps
 \[
 \hat{Z}: z_{ij} = \sum_{t=1}^{T - 1}
-    \mathbb{1}(x_{t+1,j} - x_{t, i} \in \left[f1, f2 \right]) -
-    \mathbb{1}(x_{t+1,i} - x_{t, j} \in \left[f1, f2 \right])
+    \mathbb{1}(x_j^{t+1} - x_i^t \in \left[f_1, f_2 \right]) -
+    \mathbb{1}(x_i^{t+1} - x_j^t \in \left[f_1, f_2 \right]), \forall i, j \in V
 \]
 where $f_1$ and $f_2$ are parameters of the method.
+Finally, the weighted average of correlation matrices is combined with $Z$ such
+that $Z$ has a contribution of $0.3\%$ to the prediction of an edge.
 

### 2014-06-16 article.tex

@@
 $A$ and a connectivity score matrix $\hat{A}$, we assess the accuracy of the
-network inference method using the area under the ROC curve (ROC AUC)
+network inference method using the area under the ROC curve (AUROC)
 and the area under the precision-recall curve (AUPRC)
@@
 
-\begin{table}[htb]
+\begin{table}[tbh]
 \centering
-\caption{Inverse correlation (ROC). Improvement of each stage of our approach. Note that we choose the
-         \textit{best} threshold (\textcolor{red}{for now 0.11}) for stages 1 to 4.}
-\begin{tabular}{*{5}{l}}
+\caption{TODO}
+\begin{tabular}{@{}l *{8}{c}@{}}
 \toprule
-Stage               & normal-1 & normal-2 & normal-3 & normal-4 \\
+  & \multicolumn{4}{c}{AUROC} & \multicolumn{4}{c}{AUPRC} \\
+\cmidrule(r){2-5}\cmidrule(r){6-9}
+Methods $\backslash$ normal- & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 \\
 \midrule
-Nothing             & 0.777 & 0.767 & 0.772 & 0.774 \\
-PCA                 & 0.780 & 0.770 & 0.776 & 0.777 \\
-Weights             & 0.780 & 0.769 & 0.776 & 0.777 \\
-Weights + PCA       & 0.783 & 0.772 & 0.779 & 0.780 \\
-H-T                 & 0.893 & 0.891 & 0.891 & 0.886 \\
-H-T + PCA           & 0.894 & 0.892 & 0.891 & 0.886 \\
-H-T + Weights       & 0.899 & 0.897 & 0.896 & 0.891 \\
-H-T + Weights + PCA & 0.900 & 0.898 & 0.896 & 0.892 \\
-P-P                 & 0.925 & 0.925 & 0.924 & 0.923 \\
-P-P + PCA           & 0.926 & 0.926 & 0.925 & 0.923 \\
-P-P + Weights       & 0.931 & 0.930 & 0.928 & 0.927 \\
-P-P + Weights + PCA & 0.932 & 0.931 & 0.930 & 0.928 \\
-Averaging (PCA)     & 0.943 & 0.942 & 0.942 & 0.939 \\
-Stacking            & 0.944 & 0.943 & 0.942 & 0.940 \\
+GENIE3                 & & & & & & & & \\
+Directivity            & 0.535 & 0.526 & 0.533 & 0.535 & 0.012 & 0.012 & 0.012 & 0.012 \\
+Correlation            & 0.886 & 0.884 & 0.891 & 0.877 & 0.153 & 0.145 & 0.170 & 0.132 \\
+GTE                    & 0.890 & 0.893 & 0.894 & 0.873 & 0.171 & 0.174 & 0.197 & 0.142 \\
+Partial correlation    & 0.932 & 0.931 & 0.930 & 0.928 & 0.364 & 0.366 & 0.359 & 0.344 \\
+Our approach           & 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388 \\
+Our approach + dir     & 0.944 & 0.943 & 0.942 & 0.940 & 0.404 & 0.405 & 0.399 & 0.389 \\
 \bottomrule
@@
 
-\begin{table}[htb]
+\begin{table}[tbh]
 \centering
-\caption{Inverse correlation (P-R). Improvement of each stage of our approach. Note that we choose the
-         \textit{best} threshold (\textcolor{red}{for now 0.11}) for stages 1 to 4.}
-\begin{tabular}{*{5}{l}}
+\caption{TODO}
+\begin{tabular}{@{}l *{8}{c}@{}}
 \toprule
-Stage               & normal-1 & normal-2 & normal-3 & normal-4 \\
+  & \multicolumn{4}{c}{AUROC} & \multicolumn{4}{c}{AUPRC} \\
+\cmidrule(r){2-5}\cmidrule(r){6-9}
+Methods $\backslash$ normal- & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 \\
 \midrule
-Nothing             & 0.070 & 0.064 & 0.068 & 0.072\\
-PCA                 & 0.076 & 0.070 & 0.075 & 0.079\\
-Weights             & 0.074 & 0.067 & 0.072 & 0.076\\
-Weights + PCA       & 0.080 & 0.073 & 0.079 & 0.083\\
-H-T                 & 0.264 & 0.260 & 0.269 & 0.241\\
-H-T + PCA           & 0.266 & 0.263 & 0.273 & 0.244\\
-H-T + Weights       & 0.280 & 0.273 & 0.281 & 0.251\\
-H-T + Weights + PCA & 0.284 & 0.278 & 0.285 & 0.255\\
-P-P                 & 0.322 & 0.324 & 0.323 & 0.312\\
-P-P + PCA           & 0.347 & 0.352 & 0.355 & 0.341\\
-P-P + Weights       & 0.333 & 0.334 & 0.327 & 0.313\\
-P-P + Weights + PCA & 0.364 & 0.366 & 0.359 & 0.344\\
-Averaging           & 0.403 & 0.404 & 0.398 & 0.388\\
-Stacking            & 0.404 & 0.405 & 0.399 & 0.389\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-\begin{table}[H]
-\centering
-\caption{Comparison (ROC) with other methods (for now, $t = 0.11$)}
-\begin{tabular}{*{5}{l}}
-\toprule
-Methods             & normal-1 & normal-2 & normal-3 & normal-4 \\
-\midrule
-Correlation (best)         & 0.886 & 0.884 & 0.891 & 0.877\\
-Partial correlation (best) & 0.932 & 0.931 & 0.930 & 0.928 \\
-Our approach               & 0.943 & 0.942 & 0.942 & 0.939 \\
-GENIE3                     & & & & \\
-GTE                        & 0.890 & 0.893 & 0.894 & 0.873 \\
-Directivity                & 0.535 & 0.526 & 0.533 & 0.535 \\
-Our approach + dir         & 0.944 & 0.943 & 0.942 & 0.940\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-\begin{table}[htb]
-\centering
-\caption{Comparison (P-R) with other methods (for now, $t = 0.11$)}
-\begin{tabular}{*{5}{l}}
-\toprule
-Methods             & normal-1 & normal-2 & normal-3 & normal-4 \\
-\midrule
-Correlation (best)         & 0.153 & 0.145 & 0.170 & 0.132 \\
-Partial correlation (best) & 0.364 & 0.366 & 0.359 & 0.344 \\
-Our approach (best)        & 0.403 & 0.404 & 0.398 & 0.388 \\
-GENIE3                     & & & & \\
-GTE                        & 0.171 & 0.174 & 0.197 & 0.142 \\
-Directivity                & 0.012 & 0.012 & 0.012 & 0.012 \\
-Our approach + dir         & 0.404 & 0.405 & 0.399 & 0.389 \\
+No  filtering       & 0.777 & 0.767 & 0.772 & 0.774 & 0.070 & 0.064 & 0.068 & 0.072\\
+P                   & 0.925 & 0.925 & 0.924 & 0.923 & 0.322 & 0.324 & 0.323 & 0.312\\
+P + W               & 0.931 & 0.930 & 0.928 & 0.927 & 0.333 & 0.334 & 0.327 & 0.313\\
+P + W + PCA         & 0.932 & 0.931 & 0.930 & 0.928 & 0.364 & 0.366 & 0.359 & 0.344\\
+Averaging           & 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388\\
+Averaging + Directivity & 0.944 & 0.943 & 0.942 & 0.940 & 0.404 & 0.405 & 0.399 & 0.389\\
 \bottomrule
@@
 
+\begin{table}[htb]
+\centering
+\caption{Comparison (P-R) with other methods (for now, $t = 0.11$)}
+\begin{tabular}{*{5}{l}}
+\toprule
+Methods             & normal-1 & normal-2 & normal-3 & normal-4 \\
+\midrule
+Correlation (best)         & 0.153 & 0.145 & 0.170 & 0.132 \\
+Partial correlation (best) & 0.364 & 0.366 & 0.359 & 0.344 \\
+Our approach (best)        & 0.403 & 0.404 & 0.398 & 0.388 \\
+GENIE3                     & & & & \\
+GTE                        & 0.171 & 0.174 & 0.197 & 0.142 \\
+Directivity                & 0.012 & 0.012 & 0.012 & 0.012 \\
+Our approach + dir         & 0.404 & 0.405 & 0.399 & 0.389 \\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{table}[htb]
+\centering
+\caption{Inverse correlation (ROC). Improvement of each stage of our approach. Note that we choose the
+         \textit{best} threshold (\textcolor{red}{for now 0.11}) for stages 1 to 4.}
+\begin{tabular}{*{5}{l}}
+\toprule
+Stage               & normal-1 & normal-2 & normal-3 & normal-4 \\
+\midrule
+Nothing             & 0.777 & 0.767 & 0.772 & 0.774 \\
+PCA                 & 0.780 & 0.770 & 0.776 & 0.777 \\
+Weights             & 0.780 & 0.769 & 0.776 & 0.777 \\
+Weights + PCA       & 0.783 & 0.772 & 0.779 & 0.780 \\
+H-T                 & 0.893 & 0.891 & 0.891 & 0.886 \\
+H-T + PCA           & 0.894 & 0.892 & 0.891 & 0.886 \\
+H-T + Weights       & 0.899 & 0.897 & 0.896 & 0.891 \\
+H-T + Weights + PCA & 0.900 & 0.898 & 0.896 & 0.892 \\
+P-P                 & 0.925 & 0.925 & 0.924 & 0.923 \\
+P-P + PCA           & 0.926 & 0.926 & 0.925 & 0.923 \\
+P-P + Weights       & 0.931 & 0.930 & 0.928 & 0.927 \\
+P-P + Weights + PCA & 0.932 & 0.931 & 0.930 & 0.928 \\
+Averaging (PCA)     & 0.943 & 0.942 & 0.942 & 0.939 \\
+Stacking            & 0.944 & 0.943 & 0.942 & 0.940 \\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{table}[htb]
+\centering
+\caption{Inverse correlation (P-R). Improvement of each stage of our approach. Note that we choose the
+         \textit{best} threshold (\textcolor{red}{for now 0.11}) for stages 1 to 4.}
+\begin{tabular}{*{5}{l}}
+\toprule
+Stage               & normal-1 & normal-2 & normal-3 & normal-4 \\
+\midrule
+Nothing             & 0.070 & 0.064 & 0.068 & 0.072\\
+PCA                 & 0.076 & 0.070 & 0.075 & 0.079\\
+Weights             & 0.074 & 0.067 & 0.072 & 0.076\\
+Weights + PCA       & 0.080 & 0.073 & 0.079 & 0.083\\
+H-T                 & 0.264 & 0.260 & 0.269 & 0.241\\
+H-T + PCA           & 0.266 & 0.263 & 0.273 & 0.244\\
+H-T + Weights       & 0.280 & 0.273 & 0.281 & 0.251\\
+H-T + Weights + PCA & 0.284 & 0.278 & 0.285 & 0.255\\
+P-P                 & 0.322 & 0.324 & 0.323 & 0.312\\
+P-P + PCA           & 0.347 & 0.352 & 0.355 & 0.341\\
+P-P + Weights       & 0.333 & 0.334 & 0.327 & 0.313\\
+P-P + Weights + PCA & 0.364 & 0.366 & 0.359 & 0.344\\
+Averaging           & 0.403 & 0.404 & 0.398 & 0.388\\
+Stacking            & 0.404 & 0.405 & 0.399 & 0.389\\
+\bottomrule
+\end{tabular}
+\end{table}
+
 \end{document}

### 2014-06-16 article.tex
add comments

@@
 
-The directivity in the network introduce causal relations through neurons.
-A directed edge, i.e.
-$a_{i,j} = 1$ and $a_{j,i} = 0$, means that neuron $i$ causes $j$.
-The causal mechanism implies that when neuron $i$ is active, also denoted in this paper as a firing event or a burst, neuron $j$ will be afterwards active consequently.
-The reciprocal phenomenon is only possible when the edge is bidirectionnal, i.e.
-$a_{i,j} = a_{j,i} = 1$.
+The directivity in the network introduce causal relations through neurons. A
+directed edge, i.e. $a_{i,j} = 1$ and $a_{j,i} = 0$, means that neuron $i$
+causes $j$. The causal mechanism implies that when neuron $i$ is active, also
+denoted in this paper as a firing event or a burst, neuron $j$ will be
+afterwards active consequently \textcolor{red}{AJ: it's not always true if
+there is more than one ancestor and not true if the activation is not
+systematic.}. The
+reciprocal phenomenon is only possible
+when the edge is bidirectionnal, i.e. $a_{i,j} = a_{j,i} = 1$.
 

### 2014-06-16 article.tex
break 80 line char
one X forgotten

@@
 indicator is highly reactive to a burst but takes some time to recover its non
-active state.
-Finally, the difficulty to distinguish direct relationships when a network burst happens, defined as a highly synchronous activity [Stetter and in Stetter [20,46,47]], is increased by the slow sampling rate.
+active state.  Finally, the difficulty to distinguish direct relationships when
+ a network burst happens, defined as a highly synchronous activity
+ [Stetter and in Stetter [20,46,47]], is increased by the slow sampling rate.
 
@@
 
-As it can be seen on \textit{fig 1}, the raw signal is very noisy due to light scattering artifacts that ordinarily affects the quality of the recording [in Stetter, [6]].
-Therefore, a low-pass filter is first applied to get a cleaner version of the signal where only
+As it can be seen on \textit{fig 1}, the raw signal is very noisy due to light
+scattering artifacts that ordinarily affects the quality of the recording
+[in Stetter, [6]]. Therefore, a low-pass filter is first applied to get a
+cleaner version of the signal where only
 true variations are kept, i.e. without noise variations. However, the choice of a low-pass
@@
 strong variations in the neuron activity. Therefore we apply a hard-tresholding
-filter $x^{t,d}_i = x^{t,d}_i \mathbb{1}(x^{t,d}_i \geq \tau)$ where the threshold $\tau$ should be taken positive to keep only rising edges and non close to zeros in order to only consider strong variations.
+filter $x^{t,d}_i = x^{t,d}_i \mathbb{1}(x^{t,d}_i \geq \tau)$ where the
+threshold $\tau$ should be taken positive to keep only rising edges and non
+close to zeros in order to only consider strong variations.
 
@@
 proportional to the number of neurons firing together:
-$ x^{t,w}_i  = (x^{t,d}_i + 1 )^{1 + \frac{1}{\sum_{j} X_{t,d}^j}} $.
+$ x^{t,w}_i  = (x^{t,d}_i + 1 )^{1 + \frac{1}{\sum_{j} x_{t,d}^j}} $.
 When too much neurons are firing together, i.e. in case of a network burst, it is almost

### 2014-06-16 article.tex
some wording

@@
 As it can be seen on \textit{fig 1}, the raw signal is very noisy due to light
-scattering artifacts that ordinarily affects the quality of the recording
-[in Stetter, [6]]. Therefore, a low-pass filter is first applied to get a
-cleaner version of the signal where only
-true variations are kept, i.e. without noise variations. However, the choice of a low-pass
-filter is not unique. In the rest of the paper, we will use two particular filters giving similar results, the
-symmetrical median filter, i.e., $x^t_i \leftarrow x^{t-1}_i + x^{t}_i + x^{t+1}_i$,
-and an asymmetrical weighted median filter, i.e.,
-$x^t_i \leftarrow 0.4 x^{t-3}_i + 0.6 x^{t-2}_i + 0.8 x^{t-1}_i + x_{t}^i$.
+scattering artifacts that ordinarily affects the quality of the recording [in
+Stetter, [6]]. Therefore, a low-pass filter is first applied to get a cleaner
+version of the signal where only true variations are kept, i.e. without noise
+variations. However, the choice of a low-pass filter is not unique. In the
+rest of the paper, we will use two particular filters giving similar results,
+the symmetrical median filter, i.e., $x^t_i \leftarrow x^{t-1}_i + x^{t}_i +
+x^{t+1}_i$, and an asymmetrical weighted median filter, i.e., $x^t_i
+\leftarrow 0.4 x^{t-3}_i + 0.6 x^{t-2}_i + 0.8 x^{t-1}_i + x_{t}^i$.
 
@@
 The small decay for the fluorescent calcium indicator implies a signal
-variation during a long time interval. Firing event are represented by
-strong variations in the neuron activity. Therefore we apply a hard-tresholding
+variation during a long time interval. Firing event are represented by strong
+variations in the neuron activity. Therefore we apply a hard-tresholding
 filter $x^{t,d}_i = x^{t,d}_i \mathbb{1}(x^{t,d}_i \geq \tau)$ where the
-threshold $\tau$ should be taken positive to keep only rising edges and non
-close to zeros in order to only consider strong variations.
+threshold $\tau$ should be taken positive and non-close to zero to
+respectivelty only keep rising edges and strong variations.
 
@@
 happens and with a true zero when the neuron is inactive.
-
-% Considering the short delay for a communication between neurons, slow events
-% can be neglected to retrieve direct relationships. The average time
-% delay is indeed about $1ms$ or $2ms$ while the fluorescent signal time
-% resolution is $20ms$. Let us also highlight that even if two neurons are
-% spatially far from each other, the delay should not exceed one time step. Thus very low frequency event can be neglected.
-
-% Connectivity information between two neurons may be retrieved from successive
-% and slightly delayed burst events. Direct links
-% between two neurons should have shorter delay between fluorescence
-% peaks than undirected links. However, the fluorescence signal has a slow
-% decay compare to its rise. Therefore, we filter those unrelevant information
-% with a hard thresholding filter
-% \begin{align}
-% X^{\prime\prime\prime}_{t,i} &=
-% {X^{\prime\prime}_{t,i}}^{0.9} \mathbb{1}(X^{\prime\prime}_{t,i} \geq \tau) \forall i
-% \label{eq:hard-treshold-filter}
-% \end{align}
-% where $\tau \geq 0$ is a parameter of the hard-threshold filter and the $0.9$
-% exponent reduce the difference between peaks values.
 
@@
 of the activity of all neurons but the number and the locations of peaks is not modified.
-
-% Then we apply on all remaining timesteps $T$ a non-linear filter based on the current activity of the systems in order to favor the association measure when a medium size set of neurons are firing together, while artificially
-% reducing the association measure in case of extreme network activity,
-% i.e. high when a network firing is happening and low when no neuron is
-% active:
-
-% \begin{equation}
-% X^{\prime\prime\prime\prime}_{t,i} =
-% \left\{
-%   \begin{array}{l}
-%     1  : r_t < 0\\
-%     {(X^{\prime\prime\prime}_{t,i} + 1)^{(a_t^{-1} + 1)}}^{g(r_t)} : r_t \geq 0
-%   \end{array}
-% \right.
-% \text{ with }
-% \left\{
-%   \begin{array}{ll}
-%     a_t &= \sum_{i=1}^p X^{\prime\prime\prime}_{t,i} +
-%                        \frac{1}{2} X^{\prime\prime\prime}_{t-1,i} \forall t \in T\\
-%     r_t &= \frac{a_t}{\max_{l \in T}{a_l}} \\
-%   \end{array}
-% \right.
-% \end{equation}
-% where $g(x) = b_1 I(f_4 < x < f_5) + b_2  I(f_5 \leq x < f_6) +
-% b_3 (I(x\leq f_4) + I(f_ 6 \leq x))$ is a piecewise continuous function of
-% parameters $b_1, b_2, b_3, f_4, f_5, f_6$. The coefficient were tuned
-% for each set $i\in\left\{1, 2, 3, 4\right\}$ of coefficient
-% $\left(c_l^i\right)_{l=-3}^2$.
-
-% Finally since there is a high correlation between neurons, we perform noise
-% filtering through a principal component analysis. From the $p$ eigen vectors,
-% we kept $80\%$ of the eigen vectors which have the largest eigen value. In the
-% context of the challenge, this assumption was deduced from ground truth of
-% provided networks.
 

### 2014-06-16 article.tex
fix following AJ remark

@@
 causes $j$. The causal mechanism implies that when neuron $i$ is active, also
-denoted in this paper as a firing event or a burst, neuron $j$ will be
-afterwards active consequently \textcolor{red}{AJ: it's not always true if
-there is more than one ancestor and not true if the activation is not
-systematic.}. The
-reciprocal phenomenon is only possible
-when the edge is bidirectionnal, i.e. $a_{i,j} = a_{j,i} = 1$.
+denoted in this paper as a firing event or a burst, neuron $j$ may be
+afterwards activated consequently. Let us notice that neuron $j$ depends on
+all its ancestors and its activation may not be as straightforward as we may
+think if the causal is not systematic (stochastic?). The reciprocal
+phenomenon is only possible when the edge is bidirectionnal, i.e. $a_{i,j} =
+a_{j,i} = 1$.
 

### 2014-06-16 article.tex
fix second part

@@
 all its ancestors and its activation may not be as straightforward as we may
-think if the causal is not systematic (stochastic?). The reciprocal
+think if the causal activation is not systematic (stochastic?). The reciprocal
 phenomenon is only possible when the edge is bidirectionnal, i.e. $a_{i,j} =

### 2014-06-16 article.tex
adding motivation for past filter

@@
 the symmetrical median filter, i.e., $x^t_i \leftarrow x^{t-1}_i + x^{t}_i +
-x^{t+1}_i$, and an asymmetrical weighted median filter, i.e., $x^t_i
-\leftarrow 0.4 x^{t-3}_i + 0.6 x^{t-2}_i + 0.8 x^{t-1}_i + x_{t}^i$.
+x^{t+1}_i$, and an asymmetrical weighted median filter taking into account the
+history, i.e., $x^t_i \leftarrow 0.4 x^{t-3}_i + 0.6 x^{t-2}_i + 0.8 x^{t-1}_i
++ x_{t}^i$.
 

### 2014-06-16 article.tex
section for inference part

@@
 retrieve the connectivity from them, it is necessary to link a burst to a
-couple of timesteps (ideally one).
-
-The small decay for the fluorescent calcium indicator implies a signal
+couple of timesteps (ideally one). The small decay for the fluorescent calcium indicator implies a signal
 variation during a long time interval. Firing event are represented by strong
@@
 
-Then we apply on the entire signal a non-linear filter based on the
-current activity of the systems in order to favor the association measure inversely
-proportional to the number of neurons firing together:
-$ x^{t,w}_i  = (x^{t,d}_i + 1 )^{1 + \frac{1}{\sum_{j} x_{t,d}^j}} $.
-When too much neurons are firing together, i.e. in case of a network burst, it is almost
-impossible to retrieve direct relationships: all neurons seem to be directly
-connected to each other. By favoring the association measure when the activity is low,
-we expect to retrieve a pair of neurons that are really directly connected together.
-In concrete terms, as it can be verified on \textit{fig 1}, peak intensity may change in function
-of the activity of all neurons but the number and the locations of peaks is not modified.
+Then we apply on the entire signal a non-linear filter based on the current
+activity of the systems in order to favor the association measure inversely
+proportional to the number of neurons firing together: $ x^{t,w}_i  =
+(x^{t,d}_i + 1 )^{1 + \frac{1}{act_t}}$ where $act_t = \sum_{j} x_{t,d}^j$ is
+the activity of all neurons at time $t$. When too much neurons are firing
+together, i.e. in case of a network burst, it is almost impossible to retrieve
+direct relationships: all neurons seem to be directly connected to each other.
+By favoring the association measure when the activity is low, we expect to
+retrieve a pair of neurons that are really directly connected together. In
+concrete terms, as it can be verified on \textit{fig 1}, peak intensity may
+change in function of the activity of all neurons but the number and the
+locations of peaks is not modified.
 
-\subsection{Network inference through weighted average partial correlation
+\section{Network inference through weighted average partial correlation
             coefficients}
@@
 matrices was estimated from the time series by varying the hard-threshold value
-$\tau$ and the design of the low-pass filter (coefficients $(c_l^k)_{l=-3}^k$).
+$\tau$ and the design of the low-pass filter (mentionned in section \ref{sec:filter} and appendix \ref{app:optimized}).
 
@@
 
+\section{An optimized version of the algorithm to win the challenge}
+\label{app:optimized}
+
+%% Talk about filters future and past
+
 \end{document}

### 2014-06-16 article.tex
comment on causality

@@
 % Introduce directivity
+\textcolor{red}{Est-ce qu'on ne le ferait pas passer dans l'appendice B? Ou du moins l'équation?}
 Since partial correlation is a symmetric measure, the causal mechanism behind the

### 2014-06-16 article.tex
prune text

@@
 binary classification task where one has to correctly classify the presence
-or the absence of edges of the graph. Given the ground true adjacency matrix
-$A$ and a connectivity score matrix $\hat{A}$, we assess the accuracy of the
+or the absence of edges of the graph. We assess the accuracy of the
 network inference method using the area under the ROC curve (AUROC)

### 2014-06-16 article.tex
Move and reduce introduction paragraph

@@
 
+The fluorescent calcium image delivers at each acquisition a 2-D view of the
+neuron network activities. However, some neurons might not observed or are
+confounded with others. The low device sampling rate with respect to neuronal
+activity speed might not allow to distinguish neuron activation order,
+especially in highly synchronous activity [Stetter and in Stetter [20,46,47]]
+of a large part of the network. Moreover the fluorescent concentration is
+highly reactive to a neuron activation or a spike, but have a slow decay.
+
 % Introduce notation + goal in mathematical score
@@
 % Solution
+
 In this paper, we describe a simple and a theoretically grounded approach
@@
 \footnote{\url{http://connectomics.chalearn.org}}.
+
+\textcolor{red}{It may be useful to rewritte the following lines but I add it to not forget about a plan (request from AQ)}
+In section \ref{sec:filter}, we will describe how we filter the fluorescent calcium imaging signal.
+In section \ref{sec:inference}, we will characterize our algorithm from a theoretical point of view. 
+In section \ref{sec:results}, we will present some results and give a critical comparision with other inference methods.
+In appendix \ref{app:optimized}, we describe a fully tuned version of our algorithm which has won the Connectomics challenge.
 
@@
 
-The raw signal is the calcium fluorescence imaging representing neuron
-activity via a capture imaging process. Observing the fluorescent calcium as
-an indicator of neuron activity delivers a 2-D view of neuron network at each
-capture which only gives a network screenshot at given time points. It implies
-obvious issues. Some neurons may be invisible because they are not observed or
-they are confounded with another one because of the loss of the third
-dimension. The capture sample rate is also a constraint that could make
-difficult to detect in which order the neurons fire.  Moreover the activity
-indicator is highly reactive to a burst but takes some time to recover its non
-active state.  Finally, the difficulty to distinguish direct relationships when
- a network burst happens, defined as a highly synchronous activity
- [Stetter and in Stetter [20,46,47]], is increased by the slow sampling rate.
-
 Considering the described imaging process, we try in this
@@
 \caption{Filtering steps.}\label{wrap-fig:1}
-\includegraphics[width=\linewidth]{images/fig_filtering_recut.png}
+\includegraphics[width=\linewidth]{images/fig_filtering.pdf}
 \end{figure}
@@
 filters listed below.
-
-% However, the image fluorescence calcium signal is also very noisy. Thus,
-% A low-pass filter (Equation \ref{eq:low-pass}) is first applied followed by a
-% high-pass filter (Equation \ref{eq:high-pass}), the discrete derivative of
-% the signal,
-% \begin{align}
-% X^\prime_{t,i} &= \sum_{l=-3}^2 c_l^k X_{t+l,i} \forall i, \label{eq:low-pass}\\
-% X^{\prime\prime}_{t,i} &= X^{\prime}_{t,i} - X^{\prime}_{t-1,i} \forall i, \label{eq:high-pass}
-% \end{align}
-% where the $c_l^k$ coefficients were taken in one of the four
-% following tuples
-% $\left(c_l^1\right)_{l=-3}^2=(0, 0, 1, 1, 1, 1)$,
-% $\left(c_l^2\right)_{l=-3}^2=(0, 0, 1, 1, 1, 0)$,
-% $\left(c_l^3\right)_{l=-3}^2=(1, 1, 1, 1, 0, 0)$ or
-% $\left(c_l^4\right)_{l=-3}^2=(0.4, 0.8, 1, 1, 0, 0)$.
 
@@
 history, i.e., $x^t_i \leftarrow 0.4 x^{t-3}_i + 0.6 x^{t-2}_i + 0.8 x^{t-1}_i
-+ x_{t}^i$.
++ x^{t}_i$.
 
@@
 in other words, whether the signal varies. In our approach, we choose to apply
-an asymmetrical discrete derivative : $x^{t,d}_{i} \leftarrow x^{t}_i - x_{t-1}^i$.
+an asymmetrical discrete derivative : $x^{t,d}_{i} \leftarrow x^{t}_i - x^{t-1}_i$.
 
@@
 proportional to the number of neurons firing together: $ x^{t,w}_i  =
-(x^{t,d}_i + 1 )^{1 + \frac{1}{act_t}}$ where $act_t = \sum_{j} x_{t,d}^j$ is
+(x^{t,d}_i + 1 )^{1 + \frac{1}{act_t}}$ where $act_t = \sum_{j} x^{t,d}_j$ is
 the activity of all neurons at time $t$. When too much neurons are firing
@@
 \section{Experiments}
+\label{sec:results}
 
@@
 to inferred have around 15000 edges and are similar to those
-used to rank challenge participants. Note that our parameter tuning was mainly
-done on the \textit{normal-1} dataset and partly on \textit{normal-4} dataset,
-therefore it may justify why these networks are better retrieved despite the
-fact that some might be simpler to infer.
+used to rank challenge participants.
 
@@
 
-For the directory method, only filters defined by Equations
-\ref{eq:low-pass}, \ref{eq:high-pass} and \ref{eq:hard-treshold-filter} were
-used.
+% For the directory method, only filters defined by Equations
+% \ref{eq:low-pass}, \ref{eq:high-pass} and \ref{eq:hard-treshold-filter} were
+% used.
+
+% Dummy classifier?
+
+% GTE : Explaning the method (default parameters!)
+
+% Explaining the method (thèse de Gilles)
+% Genie3 : better in auprc while worse in auroc than GTE. Why?
+% Genie3 : "Conditioning" better and better but need a lot of trees
+% Correlation : Already give good results
+
+% Partial correlation : Obvious improvements (both metric) because of the conditioning
+
+% Directivity : ?
+
+%Opt: obviously when parameters are tuned/optimized, it's slightly better --> see appendix for a full description of the method
+% Avg.: Averaging over the threholds and L-P filters improves a lot both metrics.
+
+GTE is a method which characterizes a relationship between neurons by an
+estimation of the generalized transfer entropy (\cite{stetter2012model}). The
+goal of this method tries to see if the next time step value is better from
+the previous values of this time series or from time series of other neurons.
+
+GENIE3 is a tree-based method which sees the network inference problem as $p$,
+the number of variables, independent supervised learning problems (todo cite:
+Irrthum?Van Anh?Pierre?). Formally, each sub-problem consists in the
+prediction of one variable, the target, from the remaining $p-1$ variables.
+This method uses random forests to estimate the target variable and variable
+importances can be derived to estimate the adjacency matrix $A$ (see (todo
+cite) for a more detailed description of the inference method).
+
+At first sight, it appears on \textit{Table 1} that partial correlation
+methods outperform other methods. Two main reasons may explain this method
+hierarchy. First, the quality of the infered network seems related to the
+conditioning part of the method. In every method except with partial
+correlation, indirect links are confounded with direct links.  Secondly, the
+gaussian assumption seems verified and thus linear method appears to be
+competitive, e.g. the method correlation already gives good results, with a
+non-linear method such as GENIE3.
+
+% Discussion about
 
@@
 GENIE3                 & & & & & & & & \\
-Directivity            & 0.535 & 0.526 & 0.533 & 0.535 & 0.012 & 0.012 & 0.012 & 0.012 \\
+Directivity \textcolor{red}{appendix?} & 0.535 & 0.526 & 0.533 & 0.535 & 0.012 & 0.012 & 0.012 & 0.012 \\
 Correlation            & 0.886 & 0.884 & 0.891 & 0.877 & 0.153 & 0.145 & 0.170 & 0.132 \\
 GTE                    & 0.890 & 0.893 & 0.894 & 0.873 & 0.171 & 0.174 & 0.197 & 0.142 \\
-Partial correlation    & 0.932 & 0.931 & 0.930 & 0.928 & 0.364 & 0.366 & 0.359 & 0.344 \\
-Our approach           & 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388 \\
-Our approach + dir     & 0.944 & 0.943 & 0.942 & 0.940 & 0.404 & 0.405 & 0.399 & 0.389 \\
+Partial correlation    & 0.930 &  0.927 &  0.926 &  0.923& 0.363  & 0.347 &  0.346 & 0.328 \\
+Partial correlation (opt.) & 0.932 & 0.931 & 0.930 & 0.928 & 0.364 & 0.366 & 0.359 & 0.344 \\
+Our approach (opt. \& avg.)    & 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388 \\
+Our approach + dir  \textcolor{red}{appendix?}   & 0.944 & 0.943 & 0.942 & 0.940 & 0.404 & 0.405 & 0.399 & 0.389 \\
 \bottomrule
@@
 \appendix
+
+\section{An optimized version of the algorithm to win the challenge}
+\label{app:optimized}
+
+The algorithm propose in sections \ref{sec:filter} and \ref{sec:inference} has been optimized at its extreme limit to win the challenge.
+In this section, we will describe the full tuned algorithm and present some results.
+
+Note that our parameter tuning was mainly
+done on the \textit{normal-1} dataset and partly on \textit{normal-4} dataset,
+therefore it may justify why these networks are better retrieved despite the
+fact that some might be simpler to infer.
 
@@
 
-\section{An optimized version of the algorithm to win the challenge}
-\label{app:optimized}
-
 %% Talk about filters future and past

### 2014-06-16 article.tex
Better link between sentences

@@
 billions of neurons with 7000 synaptic connections on average.
-Cutting edge optical devices have been developed to track in real-time
+Cutting edge optical devices delivers in real-time  2-D  images of
 the neuronal activity of thousands of neurons through a fluorescent
 calcium indicator [todo cite]. Automatic and analytical methods are required to infer
-the connectomes from those time series.
-
-The fluorescent calcium image delivers at each acquisition a 2-D view of the
-neuron network activities. However, some neurons might not observed or are
-confounded with others. The low device sampling rate with respect to neuronal
-activity speed might not allow to distinguish neuron activation order,
-especially in highly synchronous activity [Stetter and in Stetter [20,46,47]]
-of a large part of the network. Moreover the fluorescent concentration is
-highly reactive to a neuron activation or a spike, but have a slow decay.
+the connectomes from those time series. Furthermore, several experimental issues
+have to be handled. Some neurons of the network might not be
+observed or are confounded with others. The lower device sampling rate with
+respect to neuronal activity speed might not allow to distinguish neuron
+activation order, especially in highly synchronous activity
+[Stetter and in Stetter [20,46,47]] of a large part of the network. Moreover
+the fluorescent concentration is highly reactive to a neuron activation or a
+spike, but have a slow decay.
 
 % Introduce notation + goal in mathematical score
-% TODO check convention for y_{ij}
 The connectomes, the neural network, is represented by a (un)directed graph $G = (V, E)$ comprising
@@
 \section{Signal filtering} \label{sec:filter}
-
-% \textcolor{red}{This section should be rewritten once we get the figure
-                % which displayed the effect of the different filters.}
-
-% Defects of the imaging device
-% and will have to cope with
-% a slower sampling rate than the neuron firing speed, a superposition
-% of the activity of several neurons and the slow decay of fluorescent calcium
-% indicator.
 

### 2014-06-16 article.tex
fix a typo

--- 2014-06-16 article.tex
@@
 
-% However, the image fluorescence calcium signal is also very noisy. Thus,
-% A low-pass filter (Equation \ref{eq:low-pass}) is first applied followed by a
-% high-pass filter (Equation \ref{eq:high-pass}), the discrete derivative of
-% the signal,
-% \begin{align}
-% X^\prime_{t,i} &= \sum_{l=-3}^2 c_l^k X_{t+l,i} \forall i, \label{eq:low-pass}\\
-% X^{\prime\prime}_{t,i} &= X^{\prime}_{t,i} - X^{\prime}_{t-1,i} \forall i, \label{eq:high-pass}
-% \end{align}
-% where the $c_l^k$ coefficients were taken in one of the four
-% following tuples
-% $\left(c_l^1\right)_{l=-3}^2=(0, 0, 1, 1, 1, 1)$,
-% $\left(c_l^2\right)_{l=-3}^2=(0, 0, 1, 1, 1, 0)$,
-% $\left(c_l^3\right)_{l=-3}^2=(1, 1, 1, 1, 0, 0)$ or
-% $\left(c_l^4\right)_{l=-3}^2=(0.4, 0.8, 1, 1, 0, 0)$.
-
 As it can be seen on \textit{fig 1}, the raw signal is very noisy due to light
@@
 binary classification task where one has to correctly classify the presence
-or the absence of edges of the graph. We assess the accuracy of the
+or the absence of edges of the graph. Given the ground true adjacency matrix
+$A$ and a connectivity score matrix $\hat{A}$, we assess the accuracy of the
 network inference method using the area under the ROC curve (AUROC)

### 2014-06-16 article.tex
fix error
Request from AQ

@@
 
+\textcolor{red}{It may be useful to rewritte the following lines but I add it to not forget about a plan (request from AQ)}
+In section \ref{sec:filter}, we will describe how we filter the fluorescent calcium imaging signal.
+In section \ref{sec:inference}, we will characterize our algorithm from a theoretical point of view. 
+In section \ref{sec:results}, we will present some results and give a critical comparision with other inference methods.
+In appendix \ref{app:optimized}, we describe a fully tuned version of our algorithm which has won the Connectomics challenge.
+
 \section{Signal filtering} \label{sec:filter}
@@
 
-For the directory method, only filters defined by Equations
-\ref{eq:low-pass}, \ref{eq:high-pass} and \ref{eq:hard-treshold-filter} were
-used.
+% For the directory method, only filters defined by Equations
+% \ref{eq:low-pass}, \ref{eq:high-pass} and \ref{eq:hard-treshold-filter} were
+% used.
 

### 2014-06-16 article.tex
update

@@
 
+% Dummy classifier?
+
+% GTE : Explaning the method (default parameters!)
+
+% Explaining the method (thèse de Gilles)
+% Genie3 : better in auprc while worse in auroc than GTE. Why?
+% Genie3 : "Conditioning" better and better but need a lot of trees
+% Correlation : Already give good results
+
+% Partial correlation : Obvious improvements (both metric) because of the conditioning
+
+% Directivity : ?
+
+%Opt: obviously when parameters are tuned/optimized, it's slightly better --> see appendix for a full description of the method
+% Avg.: Averaging over the threholds and L-P filters improves a lot both metrics.
+
 \begin{table}[tbh]

### 2014-06-16 article.tex
first attempt of description of GTE and GENIE3

@@
 
+GTE is a method which characterizes a relationship between neurons by an estimation of the generalized transfer entropy (\cite{stetter2012model}).
+The goal of this method tries to see if the next time step value is better from the previous values of this time series or from time series of other neurons.
+
+GENIE3 is a tree-based method which sees the network inference problem as $p$, the number of variables, independent supervised learning problems (todo cite: Irrthum?Van Anh?Pierre?).
+Formally, each sub-problem consists in the prediction of one variable, the target, from the remaining $p-1$ variables.
+This method uses random forests to estimate the target variable and variable importances can be derived to estimate the adjacency matrix $A$ (see (todo cite) for a more detailed description of the inference method).
+
 \begin{table}[tbh]

### 2014-06-16 article.tex
wording in experiments

@@
 
+At first sight, it appears on \textit{Table 1} that partial correlation methods outperform other methods. Two main reasons may explain this method hierarchy.
+First, the quality of the infered network seems related to the conditioning part of the method. In every method except with partial correlation, indirect links are confounded with direct links. 
+Secondly, the gaussian assumption seems verified and thus linear method appears to be competitive, e.g. the method correlation already gives good results, with a non-linear method such as GENIE3.
+
+% Discussion about
+
 \begin{table}[tbh]

### 2014-06-16 article.tex
break at 80
rewrote low pass filter

@@
 billions of neurons with 7000 synaptic connections on average.
-Cutting edge optical devices have been developed to track in real-time
+Cutting edge optical devices delivers in real-time  2-D  images of
 the neuronal activity of thousands of neurons through a fluorescent
 calcium indicator [todo cite]. Automatic and analytical methods are required to infer
-the connectomes from those time series.
+the connectomes from those time series and have to handle several
+experimental issues. Some neurons of the network might not be
+observed or are confounded with others. The lower device sampling rate with
+respect to neuronal activity speed might not allow to distinguish neuron
+activation order, especially in highly synchronous activity
+[Stetter and in Stetter [20,46,47]] of a large part of the network. Moreover
+the fluorescent concentration is highly reactive to a neuron activation or a
+spike, but have a slow decay.
 
 % Introduce notation + goal in mathematical score
-% TODO check convention for y_{ij}
 The connectomes, the neural network, is represented by a (un)directed graph $G = (V, E)$ comprising
@@
 
-% \textcolor{red}{This section should be rewritten once we get the figure
-                % which displayed the effect of the different filters.}
+Given the image acquisition process, the fluorescent calcium time series
+are smoothed using several linear and non linear filters in
+order to reduce the imaging process effects. The overall filtering approach
+is displayed at Figure \ref{fig:fitlering}.
 
-% Defects of the imaging device
-% and will have to cope with
-% a slower sampling rate than the neuron firing speed, a superposition
-% of the activity of several neurons and the slow decay of fluorescent calcium
-% indicator.
-
-The raw signal is the calcium fluorescence imaging representing neuron
-activity via a capture imaging process. Observing the fluorescent calcium as
-an indicator of neuron activity delivers a 2-D view of neuron network at each
-capture which only gives a network screenshot at given time points. It implies
-obvious issues. Some neurons may be invisible because they are not observed or
-they are confounded with another one because of the loss of the third
-dimension. The capture sample rate is also a constraint that could make
-difficult to detect in which order the neurons fire.  Moreover the activity
-indicator is highly reactive to a burst but takes some time to recover its non
-active state.  Finally, the difficulty to distinguish direct relationships when
- a network burst happens, defined as a highly synchronous activity
- [Stetter and in Stetter [20,46,47]], is increased by the slow sampling rate.
-
-Considering the described imaging process, we try in this
-section to cope with some of these issues and, in particular, the slower
-sampling rate than the neuron firing frequency and the slow decay of
-fluorescent calcium indicator after a neuron activity burst.
-
-\begin{figure}%{r}{0.7\linewidth}
-\caption{Filtering steps.}\label{wrap-fig:1}
+\begin{figure}[bth]
 \includegraphics[width=\linewidth]{images/fig_filtering_recut.png}
+\caption{Filtering steps. \textcolor{red}{TODO remake in pdf}}
+\label{fig:fitlering}
 \end{figure}
 
-% Explain why we need to filter
-
-Prior inferring the network, the fluorescent calcium time series
-are smoothed using several linear and non linear filters in
-order to reduce the imaging process effects. We successively apply different
-filters listed below.
-
-As it can be seen on \textit{fig 1}, the raw signal is very noisy due to light
-scattering artifacts that ordinarily affects the quality of the recording [in
-Stetter, [6]]. Therefore, a low-pass filter is first applied to get a cleaner
-version of the signal where only true variations are kept, i.e. without noise
-variations. However, the choice of a low-pass filter is not unique. In the
-rest of the paper, we will use two particular filters giving similar results,
-the symmetrical median filter, i.e., $x^t_i \leftarrow x^{t-1}_i + x^{t}_i +
-x^{t+1}_i$, and an asymmetrical weighted median filter taking into account the
-history, i.e., $x^t_i \leftarrow 0.4 x^{t-3}_i + 0.6 x^{t-2}_i + 0.8 x^{t-1}_i
-+ x^{t}_i$.
+The raw signal (original signal of Figure \ref{fig:fitlering}) is very noisy
+due to light scattering artifacts that ordinarily affects the quality of the
+recording (\cite{lichtman2011big}). A low-pass filter is first applied to
+filter high frequency noise with one of the following designs
+\begin{align}
+% symmetrical median filter
+x^t_i &\leftarrow x^{t-1}_i + x^{t}_i + x^{t+1}_i \label{eq:symetric-median}, \\
+% asymmetrical weighted median
+x^t_i &\leftarrow 0.4 x^{t-3}_i + 0.6 x^{t-2}_i + 0.8 x^{t-1}_i + x_{t}^i.
+\label{eq:weighted-asymetric-median}.
+\end{align}
 
@@
 
-GTE is a method which characterizes a relationship between neurons by an estimation of the generalized transfer entropy (\cite{stetter2012model}).
-The goal of this method tries to see if the next time step value is better from the previous values of this time series or from time series of other neurons.
+GTE is a method which characterizes a relationship between neurons by an
+estimation of the generalized transfer entropy (\cite{stetter2012model}). The
+goal of this method tries to see if the next time step value is better from
+the previous values of this time series or from time series of other neurons.
 
-GENIE3 is a tree-based method which sees the network inference problem as $p$, the number of variables, independent supervised learning problems (todo cite: Irrthum?Van Anh?Pierre?).
-Formally, each sub-problem consists in the prediction of one variable, the target, from the remaining $p-1$ variables.
-This method uses random forests to estimate the target variable and variable importances can be derived to estimate the adjacency matrix $A$ (see (todo cite) for a more detailed description of the inference method).
+GENIE3 is a tree-based method which sees the network inference problem as $p$,
+the number of variables, independent supervised learning problems (todo cite:
+Irrthum?Van Anh?Pierre?). Formally, each sub-problem consists in the
+prediction of one variable, the target, from the remaining $p-1$ variables.
+This method uses random forests to estimate the target variable and variable
+importances can be derived to estimate the adjacency matrix $A$ (see (todo
+cite) for a more detailed description of the inference method).
 
-At first sight, it appears on \textit{Table 1} that partial correlation methods outperform other methods. Two main reasons may explain this method hierarchy.
-First, the quality of the infered network seems related to the conditioning part of the method. In every method except with partial correlation, indirect links are confounded with direct links. 
-Secondly, the gaussian assumption seems verified and thus linear method appears to be competitive, e.g. the method correlation already gives good results, with a non-linear method such as GENIE3.
+At first sight, it appears on \textit{Table 1} that partial correlation
+methods outperform other methods. Two main reasons may explain this method
+hierarchy. First, the quality of the infered network seems related to the
+conditioning part of the method. In every method except with partial
+correlation, indirect links are confounded with direct links.  Secondly, the
+gaussian assumption seems verified and thus linear method appears to be
+competitive, e.g. the method correlation already gives good results, with a
+non-linear method such as GENIE3.
 

### 2014-06-16 article.tex
improve high pass filter

@@
 recording (\cite{lichtman2011big}). A low-pass filter is first applied to
-filter high frequency noise with one of the following designs
+filter high frequency noises with one of the following filter designs
 \begin{align}
@@
 
-Considering the short delay for a communication between
-neurons, slow events can be neglected to retrieve direct relationships.
-Indeed, for a direct relationship, i.e. a neuron firing directly implying another
-neuron to fire, the average time is about $1ms$ or $2ms$ while the
-fluorescent signal time resolution is $20ms$. In order to find out which neurons
-are directly related, it is only necessary to look after the burst signal, or
-in other words, whether the signal varies. In our approach, we choose to apply
-an asymmetrical discrete derivative : $x^{t,d}_{i} \leftarrow x^{t}_i - x^{t-1}_i$.
+A neuron spike lasts on average $1ms$ to $2ms$, while current optical
+device have a time resolution of $20ms$. Considering the short delay for a
+communication between neurons and slow decay of fluorescence signal, we
+can filter low frequencies through an asymmetrical discrete derivative filter
+\begin{align}
+x^{t,d}_{i} \leftarrow x^{t}_i - x_{t-1}^i.
+\end{align}
+When slow signals variations are filtered (H-P signals of figure
+\ref{fig:filtering}), only remains spike positions.
+\textcolor{red}{Pourquoi sur la figure, on a pas de signal avec une dérivée
+                négative?}
 

### 2014-06-16 article.tex
break line + don't make quation inline

@@
 retrieve the connectivity from them, it is necessary to link a burst to a
-couple of timesteps (ideally one). The small decay for the fluorescent calcium indicator implies a signal
+couple of timesteps (ideally one). The small decay for the fluorescent calcium
+indicator implies a signal
 variation during a long time interval. Firing event are represented by strong
 variations in the neuron activity. Therefore we apply a hard-tresholding
-filter $x^{t,d}_i = x^{t,d}_i \mathbb{1}(x^{t,d}_i \geq \tau)$ where the
-threshold $\tau$ should be taken positive and non-close to zero to
-respectivelty only keep rising edges and strong variations.
+filter
+\begin{align}
+x^{t,d}_i &= x^{t,d}_i \mathbb{1}(x^{t,d}_i \geq \tau)
+\end{align}
+where the threshold $\tau$ should be taken positive and non-close to zero to
+respectively only keep rising edges and strong variations.
 

### 2014-06-17 article.tex
fix notation
image format pdf

--- 2014-06-16 article.tex
@@
 billions of neurons with 7000 synaptic connections on average.
-Cutting edge optical devices delivers in real-time  2-D  images of
+Cutting edge optical devices have been developed to track in real-time
 the neuronal activity of thousands of neurons through a fluorescent
 calcium indicator  [todo cite]. Automatic and analytical methods are required to infer
-the connectomes from those time series and have to handle several
-experimental issues. Some neurons of the network might not be
-observed or are confounded with others. The lower device sampling rate with
-respect to neuronal activity speed might not allow to distinguish neuron
-activation order, especially in highly synchronous activity
-[Stetter and in Stetter [20,46,47]] of a large part of the network. Moreover
-the fluorescent concentration is highly reactive to a neuron activation or a
-spike, but have a slow decay.
+the connectomes from those time series.
 
 % Introduce notation + goal in mathematical score
+% TODO check convention for y_{ij}
 The connectomes, the neural network, is represented by a (un)directed graph $G = (V, E)$ comprising
@@
 
-Given the image acquisition process, the fluorescent calcium time series
-are smoothed using several linear and non linear filters in
-order to reduce the imaging process effects. The overall filtering approach
-is displayed at Figure \ref{fig:fitlering}.
+% \textcolor{red}{This section should be rewritten once we get the figure
+                % which displayed the effect of the different filters.}
 
-\begin{figure}[bth]
-\includegraphics[width=\linewidth]{images/fig_filtering_recut.png}
-\caption{Filtering steps. \textcolor{red}{TODO remake in pdf}}
-\label{fig:fitlering}
+% Defects of the imaging device
+% and will have to cope with
+% a slower sampling rate than the neuron firing speed, a superposition
+% of the activity of several neurons and the slow decay of fluorescent calcium
+% indicator.
+
+The raw signal is the calcium fluorescence imaging representing neuron
+activity via a capture imaging process. Observing the fluorescent calcium as
+an indicator of neuron activity delivers a 2-D view of neuron network at each
+capture which only gives a network screenshot at given time points. It implies
+obvious issues. Some neurons may be invisible because they are not observed or
+they are confounded with another one because of the loss of the third
+dimension. The capture sample rate is also a constraint that could make
+difficult to detect in which order the neurons fire.  Moreover the activity
+indicator is highly reactive to a burst but takes some time to recover its non
+active state.  Finally, the difficulty to distinguish direct relationships when
+ a network burst happens, defined as a highly synchronous activity
+ [Stetter and in Stetter [20,46,47]], is increased by the slow sampling rate.
+
+Considering the described imaging process, we try in this
+section to cope with some of these issues and, in particular, the slower
+sampling rate than the neuron firing frequency and the slow decay of
+fluorescent calcium indicator after a neuron activity burst.
+
+\begin{figure}%{r}{0.7\linewidth}
+\caption{Filtering steps.}\label{wrap-fig:1}
+\includegraphics[width=\linewidth]{images/fig_filtering.pdf}
 \end{figure}
 
-The raw signal (original signal of Figure \ref{fig:fitlering}) is very noisy
-due to light scattering artifacts that ordinarily affects the quality of the
-recording (\cite{lichtman2011big}). A low-pass filter is first applied to
-filter high frequency noise with one of the following designs
-\begin{align}
-% symmetrical median filter
-x^t_i &\leftarrow x^{t-1}_i + x^{t}_i + x^{t+1}_i \label{eq:symetric-median}, \\
-% asymmetrical weighted median
-x^t_i &\leftarrow 0.4 x^{t-3}_i + 0.6 x^{t-2}_i + 0.8 x^{t-1}_i + x_{t}^i.
-\label{eq:weighted-asymetric-median}.
-\end{align}
+% Explain why we need to filter
+
+Prior inferring the network, the fluorescent calcium time series
+are smoothed using several linear and non linear filters in
+order to reduce the imaging process effects. We successively apply different
+filters listed below.
+
+As it can be seen on \textit{fig 1}, the raw signal is very noisy due to light
+scattering artifacts that ordinarily affects the quality of the recording [in
+Stetter, [6]]. Therefore, a low-pass filter is first applied to get a cleaner
+version of the signal where only true variations are kept, i.e. without noise
+variations. However, the choice of a low-pass filter is not unique. In the
+rest of the paper, we will use two particular filters giving similar results,
+the symmetrical median filter, i.e., $x^t_i \leftarrow x^{t-1}_i + x^{t}_i +
+x^{t+1}_i$, and an asymmetrical weighted median filter taking into account the
+history, i.e., $x^t_i \leftarrow 0.4 x^{t-3}_i + 0.6 x^{t-2}_i + 0.8 x^{t-1}_i
++ x^{t}_i$.
 

### 2014-06-17 article.tex
capitalize figure
use appropriate figure
rewrote section on the hard treshold signal

--- 2014-06-16 article.tex
@@
 \begin{figure}[bth]
-\includegraphics[width=\linewidth]{images/fig_filtering_recut.png}
+\includegraphics[width=\linewidth]{images/fig_filtering}
 \caption{Filtering steps. \textcolor{red}{TODO remake in pdf}}
-\label{fig:fitlering}
+\label{fig:filtered-signal}
 \end{figure}
 
-The raw signal (original signal of Figure \ref{fig:fitlering}) is very noisy
+The raw signal (original signal of Figure \ref{fig:filtered-signal}) is very noisy
 due to light scattering artifacts that ordinarily affects the quality of the
@@
 communication between neurons and slow decay of fluorescence signal, we
-can filter low frequencies through an asymmetrical discrete derivative filter
+filter low frequencies through a high pass filter
 \begin{align}
-x^{t,d}_{i} \leftarrow x^{t}_i - x_{t-1}^i.
+% an asymmetrical discrete derivative filter
+x^{t,d}_{i} &\leftarrow x^{t}_i - x_{t-1}^i. \label{eq:high-pass-filter}
 \end{align}
-When slow signals variations are filtered (H-P signals of figure
-\ref{fig:filtering}), only remains spike positions.
-\textcolor{red}{Pourquoi sur la figure, on a pas de signal avec une dérivée
-                négative?}
 
-By nature, the firing event is really fast and in order to
-retrieve the connectivity from them, it is necessary to link a burst to a
-couple of timesteps (ideally one). The small decay for the fluorescent calcium indicator implies a signal
-variation during a long time interval. Firing event are represented by strong
-variations in the neuron activity. Therefore we apply a hard-tresholding
-filter $x^{t,d}_i = x^{t,d}_i \mathbb{1}(x^{t,d}_i \geq \tau)$ where the
-threshold $\tau$ should be taken positive and non-close to zero to
-respectivelty only keep rising edges and strong variations.
-
-As a result, we get a binary-like signal with the true activity when a burst
-happens and with a true zero when the neuron is inactive.
+Whenever the low and high pass filtered have been applied, the remaining signal
+(H-P signal of Figure \ref{fig:filtered-signal}) is the discrete
+derivative of the fluorescence calcium concentration. To further filter out
+small signal variations which are due to noise, we apply a hard-threshold
+filter
+\begin{align}
+x^{t,d}_i &\leftarrow x^{t,d}_i \mathbb{1}(x^{t,d}_i \geq \tau) \text{ with } \tau > 0.
+\end{align}
 

### 2014-06-17 article.tex
add some comments

@@
 order to reduce the imaging process effects. The overall filtering approach
-is displayed at Figure \ref{fig:fitlering}.
+is displayed at Figure \ref{fig:filtered-signal}.
 
 \begin{figure}[bth]
-\includegraphics[width=\linewidth]{images/fig_filtering}
-\caption{Filtering steps. \textcolor{red}{TODO remake in pdf}}
+\centering
+\includegraphics[width=0.8\linewidth]{images/fig_filtering}
+\caption{Filtering steps.}
 \label{fig:filtered-signal}
@@
 
-Then we apply on the entire signal a non-linear filter based on the current
-activity of the systems in order to favor the association measure inversely
-proportional to the number of neurons firing together: $ x^{t,w}_i  =
-(x^{t,d}_i + 1 )^{1 + \frac{1}{act_t}}$ where $act_t = \sum_{j} x^{t,d}_j$ is
-the activity of all neurons at time $t$. When too much neurons are firing
-together, i.e. in case of a network burst, it is almost impossible to retrieve
-direct relationships: all neurons seem to be directly connected to each other.
-By favoring the association measure when the activity is low, we expect to
-retrieve a pair of neurons that are really directly connected together. In
-concrete terms, as it can be verified on \textit{fig 1}, peak intensity may
-change in function of the activity of all neurons but the number and the
-locations of peaks is not modified.
+After those 3 first filters, the fluorescence signal (Thresh. signal of
+Figure \ref{fig:filtered-signal}) only contains clean spikes. However when a large
+part of the network is firing, it's difficult to detect pairwise neuron
+interactions. In order to reduce false interaction detection,
+the signal is smoothed with a non-linear filter which penalizes
+the filtered signal when a large part of the network is firing
+\textcolor{red}{This equation doesn't correspond to the what we have done.}
+\begin{align}
+ x^{t,w}_i  &\leftarrow (x^{t,d}_i + 1 )^{1 + \frac{1}{\sum_{j} x^{t,d}_j}}.
+\end{align}
+Once this filtered has been applied (Weights signal of
+Figure \ref{fig:filtered-signal}), peak intensities have
+changed depending on the overall network activity, but not their numbers and
+locations.
+
+\textcolor{red}{PCA?}
 

### 2014-06-17 article.tex
remove word
wording

@@
 recording (\cite{lichtman2011big}). A low-pass filter is first applied to
-filter high frequency noises with one of the following filter designs
+filter high frequency noises with one of the following designs
 \begin{align}
@@
 device have a time resolution of $20ms$. Considering the short delay for a
-communication between neurons and slow decay of fluorescence signal, we
+communication between neurons and the slow decay of fluorescence signal, we
 filter low frequencies through a high pass filter

### 2014-06-17 article.tex
add some words about pca

@@
 
-\textcolor{red}{PCA?}
+\textcolor{red}{PCA?} Finally since there is a high correlation between neurons,
+we filter some more noise through a principal component analysis. From the $|V|$
+eigen vectors, we kept $80\%$ of the eigen vectors which have the largest eigen
+value. In the context of the challenge, this assumption was deduced from ground
+truth of provided networks.
 

### 2014-06-17 article.tex
resize fig
re-wrote presentation fo the paper

@@
 
-\textcolor{red}{It may be useful to rewritte the following lines but I add it to not forget about a plan (request from AQ)}
-In section \ref{sec:filter}, we will describe how we filter the fluorescent calcium imaging signal.
-In section \ref{sec:inference}, we will characterize our algorithm from a theoretical point of view.
-In section \ref{sec:results}, we will present some results and give a critical comparision with other inference methods.
-In appendix \ref{app:optimized}, we describe a fully tuned version of our algorithm which has won the Connectomics challenge.
+The rest of the paper is structured as follows: Section \ref{sec:filter}
+describes the pre-processing applied on fluorescent calcium timeseries;
+Section \ref{sec:inference} presents the proposed approach and
+their theoretical properties; Section \ref{sec:results} provide
+empirical analysis and comparison with other network inference method,
+whereas Section \ref{sec:conclusion} discusses our work and provides further
+research directions.
 
@@
 \centering
-\includegraphics[width=0.8\linewidth]{images/fig_filtering}
+\includegraphics[width=0.4\linewidth]{images/fig_filtering}
 \caption{Filtering steps.}
@@
 
-\section{Conclusion}
+\section{Conclusion} \label{sec:conclusion}
 

### 2014-06-17 article.tex
wording

@@
 % Solution
-
-In this paper, we describe a simple and a theoretically grounded approach
-based on partial correlation\footnote{Source code is available at
-\url{https://github.com/asutera/kaggle-connectomics}.} to infer the neural
-network, which is the winning method of the Connectomics challenge
-\footnote{\url{http://connectomics.chalearn.org}}.
-
-The rest of the paper is structured as follows: Section \ref{sec:filter}
+In this paper, we describe the winning method of the Connectomics challenge
+\footnote{\url{http://connectomics.chalearn.org}}, a simple and theoretically
+grounded approach, based on partial correlation\footnote{Source code is available
+at \url{https://github.com/asutera/kaggle-connectomics}.} to infer the neural
+network. The rest of the paper is structured as follows: Section \ref{sec:filter}
 describes the pre-processing applied on fluorescent calcium timeseries;

### 2014-06-17 article.tex
typo

@@
 their theoretical properties; Section \ref{sec:results} provide
-empirical analysis and comparison with other network inference method,
+empirical analysis and comparison with other network inference methods,
 whereas Section \ref{sec:conclusion} discusses our work and provides further

### 2014-06-17 article.tex
merged part on causality

@@
 % Introduce notation + goal in mathematical score
-The connectomes, the neural network, is represented by a (un)directed graph $G = (V, E)$ comprising
+The connectomes, the neural network, is represented by a (un)directed graph
+$G = (V, E)$ comprising
 a set of nodes $V$ and a set of edges $E \subseteq \left\{(i, j) \in V \times
-V\right\}$, (un)ordered pair from $V$.
+V\right\}$, (un)ordered pairs from $V$.
 Each node $i \in V$ represents a neuron, and each edge $(i, j) \in E$
-represents a direct link and interactions between neuron $i$ and a neuron $j$.
-In the directed graph, each edges also expresses a causal relationship: an
-edge $(i, j) \in E$ indicates that the state of neuron $j$ might be caused
-by the neuron $i$. The network inference task is set as follows :
+represents a direct link and interaction between neuron $i$ and $j$.
+In the directed graph, edges also express causality: the
+state of a neuron $i$ might be due to the state of one or several of its
+parents $\left\{j : (j, i) \in E, j \in V\right\}$.
+The network inference task is set as follows :
 \textit{Given the observations $(x^t \in \mathcal{R}^{|V|})_{t=1}^T $
@@
 of graph $G$, where $\mathbb{1}$ is the indicator function.}
-
-The directivity in the network introduce causal relations through neurons. A
-directed edge, i.e. $a_{i,j} = 1$ and $a_{j,i} = 0$, means that neuron $i$
-causes $j$. The causal mechanism implies that when neuron $i$ is active, also
-denoted in this paper as a firing event or a burst, neuron $j$ may be
-afterwards activated consequently. Let us notice that neuron $j$ depends on
-all its ancestors and its activation may not be as straightforward as we may
-think if the causal activation is not systematic (stochastic?). The reciprocal
-phenomenon is only possible when the edge is bidirectionnal, i.e. $a_{i,j} =
-a_{j,i} = 1$.
 

### 2014-06-17 article.tex
Abstract + Intro

@@
-   %\documentclass[wcp,gray]{jmlr} % test grayscale version
 \documentclass[wcp]{jmlr}
 
-%% Personnal package
 \usepackage{enumerate}
 \usepackage{bbold}
-\usepackage{wrapfig}
-
- % The following packages will be automatically loaded:
- % amsmath, amssymb, natbib, graphicx, url, algorithm2e
-
- %\usepackage{rotating}% for sideways figures and tables
-% \usepackage{longtable}% for long tables
-
- % The booktabs package is used by this sample document
- % (it provides \toprule, \midrule and \bottomrule).
- % Remove the next line if you don't require it.
 \usepackage{booktabs}
- % The siunitx package is used by this sample document
- % to align numbers in a column by their decimal point.
- % Remove the next line if you don't require it.
-\usepackage[load-configurations=version-1]{siunitx} % newer version
- %\usepackage{siunitx}
+\usepackage{natbib}
 \usepackage[utf8]{inputenc}
@@
 
-% % Define an unnumbered theorem just for this sample document:
-%\theorembodyfont{\upshape}
-%\theoremheaderfont{\scshape}
-%\theorempostheader{:}
-%\theoremsep{\newline}
-%\newtheorem*{note}{Note}
+ % change the arguments, as appropriate, in the following:
+%\jmlrvolume{1}
+%\jmlryear{2014}
+%\jmlrworkshop{\textcolor{red}{Neural Connectomics Workshop}}
+\jmlrproceedings{}{}
 
- % change the arguments, as appropriate, in the following:
-\jmlrvolume{1}
-\jmlryear{2014}
-\jmlrworkshop{\textcolor{red}{Neural Connectomics Workshop}}
+\title{Simple connectome inference from partial correlation statistics in calcium imaging}
 
-% \title[Connectomics challenge]{Inferring neural networks from fluorescent
-%                                calcium imaging using partial correlation and
-%                                sample weighting \textcolor{red}{plus court} : Simple and robust inference of connectomes using partial correlation coefficients
-% ?}
-
-% \title[Inference of connectomes using partial correlation coefficients]{Simple and robust inference of connectomes using partial correlation coefficients}
-
-\title{\textcolor{red}{Simple} connectome inference using partial correlation from imaging calcium signal}
-
-% %%
-% Discovery/Infering/Retrieving/... connectomes
-% Robust
-% Using partial correlation
-% [from calcium imaging]
-
- % Use \Name{Author Name} to specify the name.
- % If the surname contains spaces, enclose the surname
- % in braces, e.g. \Name{John {Smith Jones}} similarly
- % if the name has a "von" part, e.g \Name{Jane {de Winter}}.
- % If the first letter in the forenames is a diacritic
- % enclose the diacritic in braces, e.g. \Name{{\'E}louise Smith}
-
- % Two authors with the same address
-%  \author{\Name{Author Name1\nametag{\thanks{with a note}}} \Email{abc@sample.com}\and
-%   \Name{Author Name2} \Email{xyz@sample.com}\\
-%   \addr Address}
-
- % Three or more authors with the same address:
- % \author{ Antonio Sutera %\and
- %         % \Name{Arnaud Joly} \and
- %         % \Name{Vincent Fran\c{c}ois-Lavet} \and
- %         % \Name{Aaron Qiu} \and
- %         % \Name{Gilles Louppe} \and
- %         % \Name{Damien Ernst} \and
- %         % \name{Pierre Geurts}}
- %         }
 \author{Antonio Sutera,
@@
 \begin{abstract}
-Understanding how the brain works is a key
-to treat brain disorders such as Parkinson's disease,
-epilepsy. Retrieving connectomes, the neurons wiring map, will shed a new
-light on the anatomical and functional connectivity of the brain. In the
-context of the Connectomics challenge, we propose a simple algorithm made of
-four stages, using preprocessing and partial correlation to achieve a network
-inference of high quality. An optimized variation of this simple algorithm
-is the winning method of the Connectomics Challenge.
-We put in perspective our method
-with other inference methods such as GTE (\cite{stetter2012model}) and Genie3
-(\cite{huynhthu2010inferring}).
-
-% Discussion on the metrics?
-%\textcolor{red}{Discussion on the order of the partial correlation}
-
+In this work, we propose a simple and mathematically motivated method for the
+problem of connectome inference in calcium imaging data. The proposed algorithm
+consists in i) processing the raw signals to detect neural peak activities and ii)
+inferring the degree of association between neurons from partial correlation
+statistics.  This paper summarizes the methodology that led us to win the
+Connectomics Challenge, proposes a simplified version of our method and finally
+discusses our results with respect to other inference methods.
 \end{abstract}
@@
 \begin{keywords}
-Network inference - Partial correlation - Precision matrix - GENIE3
+Connectomics - Network inference - Partial correlation
 \end{keywords}
@@
 
-% BG : brain, complex organ
-The human brain is a complex biological organ, formed by 100
-billions of neurons with 7000 synaptic connections on average.
-Cutting edge optical devices delivers in real-time  2-D  images of
-the neuronal activity of thousands of neurons through a fluorescent
-calcium indicator [todo cite]. Automatic and analytical methods are required to infer
-the connectomes from those time series and have to handle several
-experimental issues. Some neurons of the network might not be
-observed or are confounded with others. The lower device sampling rate with
-respect to neuronal activity speed might not allow to distinguish neuron
-activation order, especially in highly synchronous activity
-[Stetter and in Stetter [20,46,47]] of a large part of the network. Moreover
-the fluorescent concentration is highly reactive to a neuron activation or a
-spike, but have a slow decay.
+The human brain is a complex biological organ made of 100 billions of neurons,
+each connected to 7000 other neurons on average. Unfortunately, direct
+observations of the connectome, the wiring diagram of the brain, is not yet
+technically feasible. Without being perfect, calcium imaging currently allows
+the realtime and simultaneous observation of neuron activities from thousands
+of neurons, producing individual time series representing their fluoresence
+intensity. In this context,  the connectome inference problem consists in
+retrieving the synaptic connections between neurons on the basis of the
+fluoresence time series. In particular, this problem is often made difficult
+because of experimental issues, including masking effects making some of the
+neurons not to be observed or confounded with others, a low sampling rate of
+the optical device with respect to the neural activity speed or the slow decay
+of fluoresence.
 
-% Introduce notation + goal in mathematical score
-The connectomes, the neural network, is represented by a (un)directed graph
-$G = (V, E)$ comprising
-a set of nodes $V$ and a set of edges $E \subseteq \left\{(i, j) \in V \times
-V\right\}$, (un)ordered pairs from $V$.
-Each node $i \in V$ represents a neuron, and each edge $(i, j) \in E$
-represents a direct link and interaction between neuron $i$ and $j$.
-In the directed graph, edges also express causality: the
-state of a neuron $i$ might be due to the state of one or several of its
-parents $\left\{j : (j, i) \in E, j \in V\right\}$.
-The network inference task is set as follows :
-\textit{Given the observations $(x^t \in \mathcal{R}^{|V|})_{t=1}^T $
-along $T$ periods of time of the $|V|$ neurons, the goal is to infer the
-adjacency matrix $A : a_{i,j} = \mathbb{1}((i, j) \in E)$ of the neural network
-of graph $G$, where $\mathbb{1}$ is the indicator function.}
+Formally, the connectome can be represented as a directed graph $G=(V,E)$,
+where $V$ is a set of $p$ nodes, representing neurons, and $E \subseteq
+\left\{(i, j) \in V \times V\right\}$ is a set of edges, representing direct
+synaptic connections between neurons. Causal interactions are expressed by the
+direction of edges: $(i, j) \in E$ indicates that the state of neuron $j$ might
+be caused by the activity of neuron $i$. In those terms,  the connectome
+inference problem is formally stated as follows:  \textit{Given the sampled
+observations $\{ x^t_i \in \mathbb{R}^{p} | i \in V, t = 1, \dots T \}$ of $p$
+neurons for $T$ time intervals, the goal is to infer the set $E$ of connections in $G$.}
 
-% Solution
-In this paper, we describe the winning method of the Connectomics challenge
-\footnote{\url{http://connectomics.chalearn.org}}, a simple and theoretically
-grounded approach, based on partial correlation\footnote{Source code is available
-at \url{https://github.com/asutera/kaggle-connectomics}.} to infer the neural
-network. The rest of the paper is structured as follows: Section \ref{sec:filter}
-describes the pre-processing applied on fluorescent calcium timeseries;
-Section \ref{sec:inference} presents the proposed approach and
-their theoretical properties; Section \ref{sec:results} provide
-empirical analysis and comparison with other network inference methods,
-whereas Section \ref{sec:conclusion} discusses our work and provides further
-research directions.
+In this paper, we describe the winning method\footnote{Code available at
+\url{https://github.com/asutera/kaggle-connectomics}} of the Connectomics
+Challenge\footnote{\url{http://connectomics.chalearn.org}}, a simple and
+theoretically grounded approach based on signal processing techniques and
+partial correlation statistics to infer the neural network. The rest of the
+paper is structured as follows: Section \ref{sec:filter} describes the signal
+processing methods applied on fluorescent calcium time series; Section
+\ref{sec:inference} then presents the proposed approach and its theoretical
+properties; Section \ref{sec:results} provides an empirical analysis and
+comparison with other network inference methods, while Section
+\ref{sec:conclusion} finally discusses our work and provides further research
+directions.
 
@@
 
-\section{Network inference through weighted average partial correlation
-         coefficients}
+\section{Connectome inference from partial correlation statistics}
 \label{sec:inference}
@@
 
-\section{Conclusion} \label{sec:conclusion}
+\section{Conclusions} \label{sec:conclusion}
 
@@
 
-\begin{scriptsize}
+\section*{Acknowledgements}
 
-\paragraph{Acknowledgements.} A. Joly and G. Louppe are research fellows of
+A. Joly and G. Louppe are research fellows of
 the FNRS, Belgium.  A. Sutera is  is recipient of
@@
 Belgian State, Science Policy Office.
-
-\end{scriptsize}
 

### 2014-06-17 article.tex
first genie3 results

@@
 At first sight, it appears on \textit{Table 1} that partial correlation
-methods outperform other methods. Two main reasons may explain this method
-hierarchy. First, the quality of the infered network seems related to the
-conditioning part of the method. In every method except with partial
-correlation, indirect links are confounded with direct links.  Secondly, the
-gaussian assumption seems verified and thus linear method appears to be
-competitive, e.g. the method correlation already gives good results, with a
-non-linear method such as GENIE3.
+outperforms other methods. Two main reasons may explain this. First, the
+quality of the infered network seems related to the conditioning part of the
+method. In every method except with partial correlation, indirect links are
+confounded with direct links.  Secondly, the gaussian assumption seems
+verified and thus linear method appears to be competitive, e.g. the method
+correlation already gives good results, with a non-linear method such as
+GENIE3.
 
-% Discussion about
+% Discussion about the metrics
 
@@
 \midrule
-GENIE3                 & & & & & & & & \\
+GENIE3 (depth = 1)     & 0.890 & & & & 0.236 & & & \\
+GENIE3 (depth = 2)     & 0.895 & & & & 0.269 & & & \\
+GENIE3 (depth = 3)     & & & & & & & & \\
 Directivity \textcolor{red}{appendix?} & 0.535 & 0.526 & 0.533 & 0.535 & 0.012 & 0.012 & 0.012 & 0.012 \\

### 2014-06-17 article.tex
add unsymmetrized genie3 results

@@
 \midrule
-GENIE3 (depth = 1)     & 0.890 & & & & 0.236 & & & \\
-GENIE3 (depth = 2)     & 0.895 & & & & 0.269 & & & \\
-GENIE3 (depth = 3)     & & & & & & & & \\
+
 Directivity \textcolor{red}{appendix?} & 0.535 & 0.526 & 0.533 & 0.535 & 0.012 & 0.012 & 0.012 & 0.012 \\
@@
 GTE                    & 0.890 & 0.893 & 0.894 & 0.873 & 0.171 & 0.174 & 0.197 & 0.142 \\
+GENIE3 (depth = 1)     & 0.878 & & & & 0.184 & & & \\
+GENIE3 (depth = 2)     & 0.889 & & & & 0.217 & & & \\
+GENIE3 (depth = 3)     & & & & & & & & \\
 Partial correlation    & 0.930 &  0.927 &  0.926 &  0.923& 0.363  & 0.347 &  0.346 & 0.328 \\

### 2014-06-17 article.tex
Signal filtering

--- 2014-06-17 article.tex
@@
 \url{https://github.com/asutera/kaggle-connectomics}} of the Connectomics
-Challenge\footnote{\url{http://connectomics.chalearn.org}}, a simple and
+Challenge\footnote{\url{http://connectomics.chalearn.org}}, as a simple and
 theoretically grounded approach based on signal processing techniques and
-partial correlation statistics to infer the neural network. The rest of the
+partial correlation statistics. The rest of the
 paper is structured as follows: Section \ref{sec:filter} describes the signal
@@
 
-Given the image acquisition process, the fluorescent calcium time series
-are smoothed using several linear and non linear filters in
-order to reduce the imaging process effects. The overall filtering approach
-is displayed at Figure \ref{fig:filtered-signal}.
+Under the simplifying assumption that neurons are on-off units, characterized
+by short periods of intense activities, or peaks, and longer periods of
+inactivity, the first part of our algorithm consists in cleaning the raw
+fluoresence data. More specifically, time series are processed using standard
+signal processing filters in order to remove noise due light scattering
+effects, account for fluorescence  low decay and reduce the importance of
+global high activity in the network. The overall process is illustrated on
+Figure~\ref{fig:filtered-signal}.
 
-\begin{figure}[bth]
+\begin{figure}
 \centering
 \includegraphics[width=0.4\linewidth]{images/fig_filtering}
-\caption{Filtering steps.}
+\caption{Signal processing process.}
 \label{fig:filtered-signal}
@@
 
-The raw signal (original signal of Figure \ref{fig:filtered-signal}) is very noisy
-due to light scattering artifacts that ordinarily affects the quality of the
-recording (\cite{lichtman2011big}). A low-pass filter is first applied to
-filter high frequency noises with one of the following designs
+As the first plot in Figure~\ref{fig:filtered-signal} illustrates, due to
+light scattering artifacts that ordinarily affects the quality of the
+recording~\citep{lichtman2011big}, the raw fluoresence signal is very noisy.
+Accordingly, the first step of our pipeline is to use a low-pass filter for
+filtering out high frequency noise, using one of the following designs,
+resulting in the second plot in the figure:
 \begin{align}
@@
 x^t_i &\leftarrow 0.4 x^{t-3}_i + 0.6 x^{t-2}_i + 0.8 x^{t-1}_i + x_{t}^i.
-\label{eq:weighted-asymetric-median}.
+\label{eq:weighted-asymetric-median}
 \end{align}
 
-A neuron spike lasts on average $1ms$ to $2ms$, while current optical
-device have a time resolution of $20ms$. Considering the short delay for a
-communication between neurons and the slow decay of fluorescence signal, we
-filter low frequencies through a high pass filter
+Considering the short delay of communication between neurons and the slow decay
+of fluorescence signal, the second step of our pipeline consists in identifying
+neuron spikes -- characterized by high frequencies -- by filtering out low
+frequencies through a high-pass filter, resulting in third plot of the figure:
 \begin{align}
@@
 
-Whenever the low and high pass filtered have been applied, the remaining signal
-(H-P signal of Figure \ref{fig:filtered-signal}) is the discrete
-derivative of the fluorescence calcium concentration. To further filter out
-small signal variations which are due to noise, we apply a hard-threshold
-filter
+Once the low- and and high-pass filters have been applied, the remaining signal
+corresponds to the discrete derivative of the fluorescence time series. To
+further filter out small signal variations, mostly due to noise, the third step
+consists in a  hard-threshold filter, yielding the fourth plot in the figure:
 \begin{align}
@@
 
-After those 3 first filters, the fluorescence signal (Thresh. signal of
-Figure \ref{fig:filtered-signal}) only contains clean spikes. However when a large
-part of the network is firing, it's difficult to detect pairwise neuron
-interactions. In order to reduce false interaction detection,
-the signal is smoothed with a non-linear filter which penalizes
-the filtered signal when a large part of the network is firing
-\textcolor{red}{This equation doesn't correspond to the what we have done.}
+At this step, the processed signal only contains clean spikes. However, when a
+large of the network is firing, detecting pairwise neuron interactions is a
+difficult task. \textcolor{red}{G: say that neurons may fire because of global
+high activity, without any actual cause -- see generator.}
+Accordingly, in order to reduce false interaction detection,
+peak intensities at time $t$ are regularized by the global activity of all
+neurons, thereby reducing the importance of peaks identified during global high activity periods:
 \begin{align}
@@
 \end{align}
-Once this filtered has been applied (Weights signal of
-Figure \ref{fig:filtered-signal}), peak intensities have
-changed depending on the overall network activity, but not their numbers and
-locations.
 
+\textcolor{red}{G: Let's drop that? or reformulate...}
 \textcolor{red}{PCA?} Finally since there is a high correlation between neurons,
@@
 truth of provided networks.
+
+\textcolor{red}{G: Change notations for $f(x^t) = ...$, $g(x^t) = ...$}
 
@@
 \]
-is equal to zero (\cite{koller2009probabilistic}). The partial correlation gives
+is equal to zero \citep{koller2009probabilistic}. The partial correlation gives
 a connectivity score
@@
 conditionally correlated to a hidden variable affecting $B$ (resp. $A$)
-\cite{de2004discovery}.}.
+\citep{de2004discovery}.}.
 In order to retrieve causal information, we developed an
@@
 Those datasets are time series of size $T=179500$ of image calcium from simulated
-neuronal networks (\cite{stetter2012model}) with $|V|=1000$ neurons. The networks
+neuronal networks \citep{stetter2012model} with $|V|=1000$ neurons. The networks
 to inferred have around 15000 edges and are similar to those
@@
 and the area under the precision-recall curve (AUPRC)
-(\cite{schrynemackers2013protocols}). Since neurons are not self-connected
+\citep{schrynemackers2013protocols}. Since neurons are not self-connected
 ($(i, i) \not \in E, \forall i \in V$) and some inference methods could
@@
 GTE is a method which characterizes a relationship between neurons by an
-estimation of the generalized transfer entropy (\cite{stetter2012model}). The
+estimation of the generalized transfer entropy \citep{stetter2012model}. The
 goal of this method tries to see if the next time step value is better from
@@
 
-In previous study \cite{shipley2002cause}, it has been suggested to
+In previous study \citep{shipley2002cause}, it has been suggested to
 consider correlation coefficients of all possible orders,

### 2014-06-17 article.tex

@@
 \midrule
-GENIE3                 & & & & & & & & \\
+
 Directivity \textcolor{red}{appendix?} & 0.535 & 0.526 & 0.533 & 0.535 & 0.012 & 0.012 & 0.012 & 0.012 \\

### 2014-06-17 article.tex
discussion about the metric

--- 2014-06-17 article.tex
@@
 
-At first sight, it appears on \textit{Table 1} that partial correlation
-outperforms other methods. Two main reasons may explain this. First, the
-quality of the infered network seems related to the conditioning part of the
-method. In every method except with partial correlation, indirect links are
-confounded with direct links.  Secondly, the gaussian assumption seems
-verified and thus linear method appears to be competitive, e.g. the method
-correlation already gives good results, with a non-linear method such as
-GENIE3.
+At first sight, it appears on Tab.\ref{tab:tab1} that partial
+correlation outperforms other methods. Two main reasons may explain this.
+First, the quality of the infered network seems related to the conditioning
+part of the method. In every method except with partial correlation, indirect
+links are confounded with direct links.  Secondly, the gaussian assumption
+seems verified and thus linear method appears to be competitive, e.g. the
+method correlation already gives good results, with a non-linear method such
+as GENIE3.\\
 
 % Discussion about the metrics
+
+However, the metrics used in the contest, i.e.
+the ROC AUC, does not seem to be consistent with the goal of the challenge, and thus to assess the quality of the \textbf{directed} infered network.
+Observing Tab.\ref{tab:tab1}, it appears that best methods only infer the \textbf{undirected} network by giving the same weights to both edges $(i,j)$ and $(j,i)$.
+
+Indeed, if we consider that the infered network is the true network undirected, i.e.
+if for all links $(i,j)$, back links $(j,i)$ are added, then we get a very high score (about $0.9956$) according to this metric.
+Therefore, if we want to maximize the ROC AUC score, we only need to detect the links, no matter their direction.
+Doing that, we only give up a gain margin of about $0.005\%$ which is not really interesting in the context of this challenge.
+We think that AUC PRC is more adapted because if we perform the same experiment, we get a score of about $0.7897$. In this case, the gain margin is about $0.2103$ which is much more interesting.
 
@@
 Correlation            & 0.886 & 0.884 & 0.891 & 0.877 & 0.153 & 0.145 & 0.170 & 0.132 \\
-GTE                    & 0.890 & 0.893 & 0.894 & 0.873 & 0.171 & 0.174 & 0.197 & 0.142 \\
 GENIE3 (depth = 1)     & 0.878 & & & & 0.184 & & & \\
@@
 GENIE3 (depth = 3)     & & & & & & & & \\
+GTE                    & 0.890 & 0.893 & 0.894 & 0.873 & 0.171 & 0.174 & 0.197 & 0.142 \\
 Partial correlation    & 0.930 &  0.927 &  0.926 &  0.923& 0.363  & 0.347 &  0.346 & 0.328 \\
@@
 \end{tabular}
+\label{tab:tab1}
 \end{table}

### 2014-06-17 article.tex
wording with Gilles

@@
 
-In this paper, we describe the winning method\footnote{Code available at
-\url{https://github.com/asutera/kaggle-connectomics}} of the Connectomics
+In this paper, we present a simplified -- yet nearly as good -- version of
+the winning method\footnote{Code available at \url{https://github.com/asutera
+/kaggle-connectomics}} of the Connectomics
 Challenge\footnote{\url{http://connectomics.chalearn.org}}, as a simple and
 theoretically grounded approach based on signal processing techniques and
-partial correlation statistics. The rest of the
-paper is structured as follows: Section \ref{sec:filter} describes the signal
-processing methods applied on fluorescent calcium time series; Section
-\ref{sec:inference} then presents the proposed approach and its theoretical
-properties; Section \ref{sec:results} provides an empirical analysis and
-comparison with other network inference methods, while Section
-\ref{sec:conclusion} finally discusses our work and provides further research
-directions.
+partial correlation statistics. The rest of the paper is structured as
+follows: Section \ref{sec:filter} describes the signal processing methods
+applied on fluorescent calcium time series; Section \ref{sec:inference} then
+presents the proposed approach and its theoretical properties; Section
+\ref{sec:results} provides an empirical analysis and comparison with other
+network inference methods, while Section \ref{sec:conclusion} finally
+discusses our work and provides further research directions. Additionnaly, Appendix
+\ref{app:optimized} further describes our actual winning method, giving slightly
+better results than the method presented in the paper but highly tuned for the
+challenge.
 
-\section{Signal filtering} \label{sec:filter}
+\section{Signal processing} \label{sec:filter}
 
@@
 recording~\citep{lichtman2011big}, the raw fluoresence signal is very noisy.
-Accordingly, the first step of our pipeline is to use a low-pass filter for
-filtering out high frequency noise, using one of the following designs,
+Accordingly, the first step of our pipeline is to smoothen the signal, using a low-pass filter for
+filtering out high frequency noise, applying one of the following designs and
 resulting in the second plot in the figure:
@@
 
-Considering the short delay of communication between neurons and the slow decay
-of fluorescence signal, the second step of our pipeline consists in identifying
+Considering the short delay of communication between neurons and the slow
+decay of fluorescence, the second step of our pipeline consists in identifying
 neuron spikes -- characterized by high frequencies -- by filtering out low
 frequencies through a high-pass filter, resulting in third plot of the figure:
-\begin{align}
-% an asymmetrical discrete derivative filter
+\begin{align} % an asymmetrical discrete derivative filter 
 x^{t,d}_{i} &\leftarrow x^{t}_i - x_{t-1}^i. \label{eq:high-pass-filter} 
@@
 At this step, the processed signal only contains clean spikes. However, when a
-large of the network is firing, detecting pairwise neuron interactions is a
+large part of the network is firing, detecting pairwise neuron interactions is a
 difficult task. \textcolor{red}{G: say that neurons may fire because of global
@@
 \end{align}
-
-\textcolor{red}{G: Let's drop that? or reformulate...}
-\textcolor{red}{PCA?} Finally since there is a high correlation between neurons,
-we filter some more noise through a principal component analysis. From the $|V|$
-eigen vectors, we kept $80\%$ of the eigen vectors which have the largest eigen
-value. In the context of the challenge, this assumption was deduced from ground
-truth of provided networks.
 
@@
 $X_i \not\perp X_j | X^{-i,j}$ between all pairs $i$ and $j$ of fluorescence
-signals, in other words the inferred network will be
-$\hat{A}: \hat{a}_{i,j} = \mathbb{1}(X_i \not\perp X_j | X^{-i,j}), \forall i, j \in V$.
+signals.
 
@@
 is equal to zero \citep{koller2009probabilistic}. The partial correlation gives
-a connectivity score
-$\hat{A}: \hat{a}_{i,j} = \rho_{X_i, X_j | X^{-i,j}}, \forall i, j \in V$ between all
-pairs of neuron $i$ and $j$. One could retrieve an estimated graph by thresholding
-the matrix $\hat{A}$.
+an estimate of the degree of association between all
+pairs of neuron $i$ and $j$. 
 Similarly, we also have $X_i \perp X_j$ if the Pearson correlation
@@
 
-% Introduce a custom solution to make the Y matrix asymmetric
-% Introduce directivity
-\textcolor{red}{Est-ce qu'on ne le ferait pas passer dans l'appendice B? Ou du moins l'équation?}
-Since partial correlation is a symmetric measure, the causal mechanism behind the
-interaction ($A$ directly causes $B$, $B$ directly causes $A$ or both) can not
-be directly inferred\footnote{Also note that two other causal mechanisms might be
-implied while having a non-zero partial coefficient: (i) a pair of variables
-is induced by a common (hidden) variable; (ii) $A$ (respectively $B$) is
-conditionally correlated to a hidden variable affecting $B$ (resp. $A$)
-\citep{de2004discovery}.}.
-In order to retrieve causal information, we developed an
-heuristics based on the following observation. The rise of fluorescence
-indicates the activation of a neuron $i$. If a neuron $j$ have also
-an increased of fluorescence after a slight delay, this could have been
-caused by the neuron $i$. Thus, we count whenever
-such events occurred between consecutive time steps
-\[
-\hat{Z}: z_{ij} = \sum_{t=1}^{T - 1}
-    \mathbb{1}(x_j^{t+1} - x_i^t \in \left[f_1, f_2 \right]) -
-    \mathbb{1}(x_i^{t+1} - x_j^t \in \left[f_1, f_2 \right]), \forall i, j \in V
-\]
-where $f_1$ and $f_2$ are parameters of the method.
-Finally, the weighted average of correlation matrices is combined with $Z$ such
-that $Z$ has a contribution of $0.3\%$ to the prediction of an edge.
+\textcolor{red}{Say that we use PCA to derive the precision matrix + ref!.}
+
+Finally since there is a high correlation between neurons,
+we filter some more noise through a principal component analysis. From the $|V|$
+eigen vectors, we kept $80\%$ of the eigen vectors which have the largest eigen
+value. In the context of the challenge, this assumption was deduced from ground
+truth of provided networks.
 
@@
 
+% Introduce a custom solution to make the Y matrix asymmetric
+% Introduce directivity
+\textcolor{red}{Est-ce qu'on ne le ferait pas passer dans l'appendice B? Ou du moins l'équation?}
+Since partial correlation is a symmetric measure, the causal mechanism behind the
+interaction ($A$ directly causes $B$, $B$ directly causes $A$ or both) can not
+be directly inferred\footnote{Also note that two other causal mechanisms might be
+implied while having a non-zero partial coefficient: (i) a pair of variables
+is induced by a common (hidden) variable; (ii) $A$ (respectively $B$) is
+conditionally correlated to a hidden variable affecting $B$ (resp. $A$)
+\citep{de2004discovery}.}.
+In order to retrieve causal information, we developed an
+heuristics based on the following observation. The rise of fluorescence
+indicates the activation of a neuron $i$. If a neuron $j$ have also
+an increased of fluorescence after a slight delay, this could have been
+caused by the neuron $i$. Thus, we count whenever
+such events occurred between consecutive time steps
+\[
+\hat{Z}: z_{ij} = \sum_{t=1}^{T - 1}
+    \mathbb{1}(x_j^{t+1} - x_i^t \in \left[f_1, f_2 \right]) -
+    \mathbb{1}(x_i^{t+1} - x_j^t \in \left[f_1, f_2 \right]), \forall i, j \in V
+\]
+where $f_1$ and $f_2$ are parameters of the method.
+Finally, the weighted average of correlation matrices is combined with $Z$ such
+that $Z$ has a contribution of $0.3\%$ to the prediction of an edge.
+
 \section{Supplementary results}

### 2014-06-17 article.tex
modfis

@@
 
-\begin{table}[tbh]
+\begin{table}
+\small
 \centering
-\caption{TODO}
 \begin{tabular}{@{}l *{8}{c}@{}}
-\toprule
   & \multicolumn{4}{c}{AUROC} & \multicolumn{4}{c}{AUPRC} \\
@@
 Methods $\backslash$ normal- & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 \\
-\midrule
-
-Directivity \textcolor{red}{appendix?} & 0.535 & 0.526 & 0.533 & 0.535 & 0.012 & 0.012 & 0.012 & 0.012 \\
+\hline \hline
+% Directivity \textcolor{red}{appendix?} & 0.535 & 0.526 & 0.533 & 0.535 & 0.012 & 0.012 & 0.012 & 0.012 \\
 Correlation            & 0.886 & 0.884 & 0.891 & 0.877 & 0.153 & 0.145 & 0.170 & 0.132 \\
@@
 Our approach (opt. \& avg.)    & 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388 \\
-Our approach + dir  \textcolor{red}{appendix?}   & 0.944 & 0.943 & 0.942 & 0.940 & 0.404 & 0.405 & 0.399 & 0.389 \\
-\bottomrule
+% Our approach + dir  \textcolor{red}{appendix?}   & 0.944 & 0.943 & 0.942 & 0.940 & 0.404 & 0.405 & 0.399 & 0.389 \\
 \end{tabular}
 \label{tab:tab1}
+\caption{TODO}
 \end{table}
@@
 \begin{tabular}{@{}l *{8}{c}@{}}
-\toprule
   & \multicolumn{4}{c}{AUROC} & \multicolumn{4}{c}{AUPRC} \\
@@
 Averaging + Directivity & 0.944 & 0.943 & 0.942 & 0.940 & 0.404 & 0.405 & 0.399 & 0.389\\
-\bottomrule
 \end{tabular}

### 2014-06-18 article.tex
discussion about the metric

@@
 % Discussion about the metrics
-
-However, the metrics used in the contest, i.e.
-the ROC AUC, does not seem to be consistent with the goal of the challenge, and thus to assess the quality of the \textbf{directed} infered network.
 Observing Tab.\ref{tab:tab1}, it appears that best methods only infer the \textbf{undirected} network by giving the same weights to both edges $(i,j)$ and $(j,i)$.
-
-Indeed, if we consider that the infered network is the true network undirected, i.e.
-if for all links $(i,j)$, back links $(j,i)$ are added, then we get a very high score (about $0.9956$) according to this metric.
-Therefore, if we want to maximize the ROC AUC score, we only need to detect the links, no matter their direction.
-Doing that, we only give up a gain margin of about $0.005\%$ which is not really interesting in the context of this challenge.
-We think that AUC PRC is more adapted because if we perform the same experiment, we get a score of about $0.7897$. In this case, the gain margin is about $0.2103$ which is much more interesting.
+This is quite surprising considering the goal of the challenge, namely predicted directed connections between neurons.
+Besides, if the true network undirected, i.e.
+for all links $(i,j)$, back links are added, is the infered network then the score obtained according to the ROC AUC metric is very high ($\sim 0.9956$ on \textit{normal-1}).
+Therefore, an undirected infered network seems sufficient to maximize the ROC AUC score without trying to identify the link direction.
+Indeed, predicting perfectly directivity only yields a small gain ($\sim 0.005$ on \textit{normal-1}) which is is not very rewarding.
+In contrast, the same experiment with the precision recall metric rewards less the undirected network and the gain margin in predicting the link directivity is large enough to be interesting.
+For these reason, it seems that the metric used in the contest, i.e.
+the ROC AUC, does not seem consistent with the goal of predicting directed connections between neurons.
+Another metric, such as the AUC PRC, is maybe more appropriate to assess the quality of the \textbf{directed} infered network.
 
@@
 \end{tabular}
+\caption{TODO}
 \label{tab:tab1}
-\caption{TODO}
 \end{table}

### 2014-06-18 article.tex
add comment about metric

@@
 
-% Discussion about the metrics
-Observing Tab.\ref{tab:tab1}, it appears that best methods only infer the \textbf{undirected} network by giving the same weights to both edges $(i,j)$ and $(j,i)$.
-This is quite surprising considering the goal of the challenge, namely predicted directed connections between neurons.
-Besides, if the true network undirected, i.e.
-for all links $(i,j)$, back links are added, is the infered network then the score obtained according to the ROC AUC metric is very high ($\sim 0.9956$ on \textit{normal-1}).
-Therefore, an undirected infered network seems sufficient to maximize the ROC AUC score without trying to identify the link direction.
-Indeed, predicting perfectly directivity only yields a small gain ($\sim 0.005$ on \textit{normal-1}) which is is not very rewarding.
-In contrast, the same experiment with the precision recall metric rewards less the undirected network and the gain margin in predicting the link directivity is large enough to be interesting.
-For these reason, it seems that the metric used in the contest, i.e.
-the ROC AUC, does not seem consistent with the goal of predicting directed connections between neurons.
-Another metric, such as the AUC PRC, is maybe more appropriate to assess the quality of the \textbf{directed} infered network.
+% Discussion about the metrics Observing Tab.\ref{tab:tab1}, it appears that
+best methods only infer the \textbf{undirected} network by giving the same
+weights to both edges $(i,j)$ and $(j,i)$. This is quite surprising
+considering the goal of the challenge, namely predicted directed connections
+between neurons. Besides, if the true network undirected, i.e. for all links
+$(i,j)$, back links are added, is the infered network then the score obtained
+according to the ROC AUC metric is very high ($\sim 0.9956$ on
+\textit{normal-1}). Therefore, an undirected infered network seems sufficient
+to maximize the ROC AUC score without trying to identify the link direction.
+Indeed, predicting perfectly directivity only yields a small gain ($\sim
+0.005$ on \textit{normal-1}) which is is not very rewarding. In contrast, the
+same experiment with the precision recall metric rewards less the undirected
+network and the gain margin in predicting the link directivity is large enough
+to be interesting. For these reason, it seems that the metric used in the
+contest, i.e. the ROC AUC, does not seem consistent with the goal of
+predicting directed connections between neurons. Another metric, such as the
+AUC PRC, is maybe more appropriate to assess the quality of the
+\textbf{directed} infered network.
+
+Interestingly, an easy way to improve results for asymmetric method (see Tab.\ref{tab:tab2}), namely GTE and GENIE3, is to make undirected the infered network.
 
@@
 \label{tab:tab1}
+\end{table}
+
+\begin{table}
+\small
+\centering
+\begin{tabular}{@{}l *{8}{c}@{}}
+  & \multicolumn{4}{c}{AUROC} & \multicolumn{4}{c}{AUPRC} \\
+\cmidrule(r){2-5}\cmidrule(r){6-9}
+Methods $\backslash$ normal- & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 \\
+\hline \hline
+% Directivity \textcolor{red}{appendix?} & 0.535 & 0.526 & 0.533 & 0.535 & 0.012 & 0.012 & 0.012 & 0.012 \\
+GENIE3 (depth = 1)     &  & & & & & & & \\
+GENIE3 (depth = 2)     &  & & & & & & & \\
+GENIE3 (depth = 3)     &  & & & & & & & \\
+GTE                    &  & & & & & & & \\
+% Our approach + dir  \textcolor{red}{appendix?}   & 0.944 & 0.943 & 0.942 & 0.940 & 0.404 & 0.405 & 0.399 & 0.389 \\
+\end{tabular}
+\caption{TODO (network are undirected)}
+\label{tab:tab2}
 \end{table}

### 2014-06-18 article.tex
comment modified

@@
 
-% Discussion about the metrics Observing Tab.\ref{tab:tab1}, it appears that
+%% Depth -- Gilles chapitre 7
+
+% Discussion about the metrics
+
+Observing Tab.\ref{tab:tab1}, it appears that
 best methods only infer the \textbf{undirected} network by giving the same
@@
 
-Interestingly, an easy way to improve results for asymmetric method (see Tab.\ref{tab:tab2}), namely GTE and GENIE3, is to make undirected the infered network.
+Interestingly, an easy way to improve results for asymmetric method (see
+Tab.\ref{tab:tab2}), namely GTE and GENIE3, is to make undirected the infered
+network. It proves once again that trying to detect the link direction is more
+penalizing than rewarding.
 

### 2014-06-18 article.tex
add parameters for GTE and GENIE3

@@
 % Explaining the method (thèse de Gilles)
-% Genie3 : better in auprc while worse in auroc than GTE. Why?
-% Genie3 : "Conditioning" better and better but need a lot of trees
-% Correlation : Already give good results
-
-% Partial correlation : Obvious improvements (both metric) because of the conditioning
 
@@
 
-GTE is a method which characterizes a relationship between neurons by an
-estimation of the generalized transfer entropy \citep{stetter2012model}. The
-goal of this method tries to see if the next time step value is better from
-the previous values of this time series or from time series of other neurons.
+\textcolor{red}{à vérifier} GTE is a method which characterizes a relationship
+between neurons by an estimation of the generalized transfer entropy
+\citep{stetter2012model}. The goal of this method tries to see if the next
+time step value is better from the previous values of this time series or from
+time series of other neurons. In Tab.\ref{tab:tab1}, default parameters were
+used to infer networks.
 
@@
 importances can be derived to estimate the adjacency matrix $A$ (see (todo
-cite) for a more detailed description of the inference method).
+cite) for a more detailed description of the inference method). We compute
+$10000$ trees for each subproblem with the randomization parameter equals to
+$\log_2{p}$ and we limite the tree max-depth to respectively $1$, $2$ and $3$.
+
+% Partial correlation : Obvious improvements (both metric) because of the conditioning
+% Correlation : Already give good results
 
@@
 %% Depth -- Gilles chapitre 7
+% Genie3 : better in auprc while worse in auroc than GTE. Why?
+% Genie3 : "Conditioning" better and better but need a lot of trees
 
@@
 
-Interestingly, an easy way to improve results for asymmetric method (see
+Interestingly, an easy way to improve results for asymmetric methods (see
 Tab.\ref{tab:tab2}), namely GTE and GENIE3, is to make undirected the infered

### 2014-06-18 article.tex
add averaging discussion in experiments + corr ack

@@
 % symmetrical median filter
-x^t_i &\leftarrow x^{t-1}_i + x^{t}_i + x^{t+1}_i \label{eq:symetric-median}, \\
+f_1(x^t_i) &= x^{t-1}_i + x^{t}_i + x^{t+1}_i \label{eq:symetric-median}, \\
 % asymmetrical weighted median
-x^t_i &\leftarrow 0.4 x^{t-3}_i + 0.6 x^{t-2}_i + 0.8 x^{t-1}_i + x_{t}^i.
+f_2(x^t_i) &= 0.4 x^{t-3}_i + 0.6 x^{t-2}_i + 0.8 x^{t-1}_i + x_{t}^i.
 \label{eq:weighted-asymetric-median}
@@
 \begin{align} % an asymmetrical discrete derivative filter 
-x^{t,d}_{i} &\leftarrow x^{t}_i - x_{t-1}^i. \label{eq:high-pass-filter} 
+g(x^{t}_{i}) &= x^{t}_i - x^{t-1}_i. \label{eq:high-pass-filter} 
 \end{align}
@@
 \begin{align}
-x^{t,d}_i &\leftarrow x^{t,d}_i \mathbb{1}(x^{t,d}_i \geq \tau) \text{ with } \tau > 0.
+h(x^{t}_i) &= x^{t}_i \mathbb{1}(x^{t}_i \geq \tau) \text{ with } \tau > 0.
 \end{align}
@@
 \begin{align}
- x^{t,w}_i  &\leftarrow (x^{t,d}_i + 1 )^{1 + \frac{1}{\sum_{j} x^{t,d}_j}}.
+ w(x^{t}_i) &= (x^{t}_i + 1 )^{1 + \frac{1}{\sum_{j} x^{t}_j}}.
 \end{align}
 
-\textcolor{red}{G: Change notations for $f(x^t) = ...$, $g(x^t) = ...$}
+The full signal processing of our approach is defined by
+\begin{align}
+w(h(g(f_k(x_i^t)))) 
+\end{align}
+where $f_k$ is one of the low-pass filter designs.
 
@@
 method correlation already gives good results, with a non-linear method such
-as GENIE3.\\
+as GENIE3.
+
+% Averaging
+
+It also appears that the averaging over the low-pass filter designs and the
+threshold values increases significantly the quality of the infered network
+according to both metrics.
 
@@
 
-Observing Tab.\ref{tab:tab1}, it appears that
-best methods only infer the \textbf{undirected} network by giving the same
-weights to both edges $(i,j)$ and $(j,i)$. This is quite surprising
-considering the goal of the challenge, namely predicted directed connections
-between neurons. Besides, if the true network undirected, i.e. for all links
-$(i,j)$, back links are added, is the infered network then the score obtained
-according to the ROC AUC metric is very high ($\sim 0.9956$ on
-\textit{normal-1}). Therefore, an undirected infered network seems sufficient
-to maximize the ROC AUC score without trying to identify the link direction.
-Indeed, predicting perfectly directivity only yields a small gain ($\sim
-0.005$ on \textit{normal-1}) which is is not very rewarding. In contrast, the
-same experiment with the precision recall metric rewards less the undirected
-network and the gain margin in predicting the link directivity is large enough
-to be interesting. For these reason, it seems that the metric used in the
-contest, i.e. the ROC AUC, does not seem consistent with the goal of
-predicting directed connections between neurons. Another metric, such as the
-AUC PRC, is maybe more appropriate to assess the quality of the
-\textbf{directed} infered network.
+Observing Tab.\ref{tab:tab1}, it appears that best methods only infer the
+\textbf{undirected} network by giving the same weights to both edges $(i,j)$
+and $(j,i)$. This is quite surprising considering the goal of the challenge,
+namely predicted directed connections between neurons. Besides, if the true
+network undirected, i.e. for all links $(i,j)$, back links are added, is the
+infered network then the score obtained according to the ROC AUC metric is
+very high ($\approx 0.9956$ on \textit{normal-1}). Therefore, an undirected
+infered network seems sufficient to maximize the ROC AUC score without trying
+to identify the link direction. Indeed, predicting perfectly directivity only
+yields a small gain ($\approx 0.005$ on \textit{normal-1}) which is is not
+very rewarding. In contrast, the same experiment with the precision recall
+metric rewards less the undirected network ($\approx 0.789$ on
+\textit{normal-1}) and the gain margin in predicting the link directivity is
+large enough to be interesting ($\approx 0.211$ on \textit{normal-1}). For
+these reason, it seems that the metric used in the contest, i.e. the ROC AUC,
+does not seem consistent with the goal of predicting directed connections
+between neurons. Another metric, such as the AUC PRC, is maybe more
+appropriate to assess the quality of the \textbf{directed} infered network.
 
@@
 A. Joly and G. Louppe are research fellows of
-the FNRS, Belgium.  A. Sutera is  is recipient of
+the FNRS, Belgium.  A. Sutera is recipient of
 a F.R.I.A. fellowship of F.R.S.-FNRS, Belgium.

### 2014-06-18 article.tex
second draft of gte and geni3

@@
 
+We compare our approach to the Pearson correlation, the generalized transfer
+entropy (GTE) and GENIE3.
+
+GTE, the baseline of the challenge, measures for all pairs of
+neurons $i$ and $j$ the reduction of uncertainty in predicting future values of
+$i$ given the observation of the time series of the neuron $j$
+conditionally to the observation of past time series of neuron $i$,
+whenever the average fluorescence is over a conditioning level.
+Conditioning level was set to reproduce baseline of the challenge.
+
+GENIE3 (\cite{huynhthu2010inferring}) translates the inference of the
+network of $p$ neurons into $p$ significant variable tasks. For each task,
+the fluorescence level of a neuron is predicted from the fluorescence
+of all other neurons using a tree based ensemble such as
+random forest (\cite{breiman2001random}). The importances
+(\cite{louppe2013understanding}) given by the tree ensemble to predict
+the time series of a neuron given the others are used to infer
+a connectivity score matrix. The following parameters are used
+$10000$ trees, $\log_2{p}$ neurons are randomly selected at each tree
+node to split the data and the maximal tree depth is constrained
+to 1, 2 or 3.
+
 % TODO
@@
 % Avg.: Averaging over the threholds and L-P filters improves a lot both metrics.
-
-\textcolor{red}{à vérifier} GTE is a method which characterizes a relationship
-between neurons by an estimation of the generalized transfer entropy
-\citep{stetter2012model}. The goal of this method tries to see if the next
-time step value is better from the previous values of this time series or from
-time series of other neurons. In Tab.\ref{tab:tab1}, default parameters were
-used to infer networks.
-
-GENIE3 is a tree-based method which sees the network inference problem as $p$,
-the number of variables, independent supervised learning problems (todo cite:
-Irrthum?Van Anh?Pierre?). Formally, each sub-problem consists in the
-prediction of one variable, the target, from the remaining $p-1$ variables.
-This method uses random forests to estimate the target variable and variable
-importances can be derived to estimate the adjacency matrix $A$ (see (todo
-cite) for a more detailed description of the inference method). We compute
-$10000$ trees for each subproblem with the randomization parameter equals to
-$\log_2{p}$ and we limite the tree max-depth to respectively $1$, $2$ and $3$.
 

### 2014-06-18 article.tex
wording

@@
 
-We compare our approach to the Pearson correlation, the generalized transfer
-entropy (GTE) and GENIE3.
-
-GTE, the baseline of the challenge, measures for all pairs of
+We compare our approach to the Pearson correlation (see Section
+\ref{sec:inference}), the generalized transfer entropy (GTE) and GENIE3.
+\begin{description}
+\item[GTE], the baseline of the challenge, measures for all pairs of
 neurons $i$ and $j$ the reduction of uncertainty in predicting future values of
@@
 
-GENIE3 (\cite{huynhthu2010inferring}) translates the inference of the
-network of $p$ neurons into $p$ significant variable tasks. For each task,
-the fluorescence level of a neuron is predicted from the fluorescence
+\item[GENIE3] (\cite{huynhthu2010inferring}) translates the inference of the
+network of $p$ neurons into $p$ supervised learning tasks. For each task,
+the fluorescence of a neuron is predicted from the fluorescence
 of all other neurons using a tree based ensemble such as
-random forest (\cite{breiman2001random}). The importances
-(\cite{louppe2013understanding}) given by the tree ensemble to predict
-the time series of a neuron given the others are used to infer
-a connectivity score matrix. The following parameters are used
+random forest (\cite{breiman2001random}). The tree ensemble associate a
+variable importance scores (\cite{louppe2013understanding})
+to each neuron used in the predictions.
+
+The following parameters are used
 $10000$ trees, $\log_2{p}$ neurons are randomly selected at each tree
@@
 to 1, 2 or 3.
+\end{description}
 

### 2014-06-18 article.tex
update text on pca

@@
 
-Finally since there is a high correlation between neurons,
-we filter some more noise through a principal component analysis. From the $|V|$
-eigen vectors, we kept $80\%$ of the eigen vectors which have the largest eigen
-value. In the context of the challenge, this assumption was deduced from ground
-truth of provided networks.
+To filter more noise before computing the partial correlation, we kept
+$80\%$ of the eigen vectors which have the largest eigen
+value (\cite{tipping1999mixtures}). In the context of the challenge, this
+assumption was deduced from ground truth of provided networks.
 
@@
 variable importance scores (\cite{louppe2013understanding})
-to each neuron used in the predictions.
-
-The following parameters are used
+to each neuron used in the predictions, which is used as a connectivity
+score. The following parameters are used
 $10000$ trees, $\log_2{p}$ neurons are randomly selected at each tree

### 2014-06-18 article.tex
intro to section experiment

--- 2014-06-18 article.tex
@@
 
-The full signal processing of our approach is defined by
-\begin{align}
-w(h(g(f_k(x_i^t))))
-\end{align}
+The full signal processing of our approach is defined by the composed function
+$
+w \cdot h \cdot g \cdot f_k 
+$
 where $f_k$ is one of the low-pass filter designs.
@@
 
+\textcolor{red}{SEUIL 0.11 for tabulars!!!}
+
+In this section, we will first describe datasets and methods used for the comparison.
+Then, on Tab.\ref{tab:tab3}, our approach is decomposed to show the contribution of each stages .
+Afterwards, we will perform a comparison between several methods on Tab.\ref{tab:tab1} (or Fig.?).
+Note that two metrics are used to evaluate the performance.
+The end of this section is devoted to a discussion about the choice of metric and its relevance for the challenge.
+
 % Datasets
@@
 
-We compare our approach to the Pearson correlation, the generalized transfer
-entropy (GTE) and GENIE3.
-
-GTE, the baseline of the challenge, measures for all pairs of
-neurons $i$ and $j$ the reduction of uncertainty in predicting future values of
-$i$ given the observation of the time series of the neuron $j$
-conditionally to the observation of past time series of neuron $i$,
-whenever the average fluorescence is over a conditioning level.
-Conditioning level was set to reproduce baseline of the challenge.
-
-GENIE3 (\cite{huynhthu2010inferring}) translates the inference of the
-network of $p$ neurons into $p$ significant variable tasks. For each task,
-the fluorescence level of a neuron is predicted from the fluorescence
-of all other neurons using a tree based ensemble such as
-random forest (\cite{breiman2001random}). The importances
-(\cite{louppe2013understanding}) given by the tree ensemble to predict
-the time series of a neuron given the others are used to infer
-a connectivity score matrix. The following parameters are used
-$10000$ trees, $\log_2{p}$ neurons are randomly selected at each tree
-node to split the data and the maximal tree depth is constrained
-to 1, 2 or 3.
-
 % TODO
@@
 % Avg.: Averaging over the threholds and L-P filters improves a lot both metrics.
+
+\textcolor{red}{à vérifier} GTE is a method which characterizes a relationship
+between neurons by an estimation of the generalized transfer entropy
+\citep{stetter2012model}. The goal of this method tries to see if the next
+time step value is better from the previous values of this time series or from
+time series of other neurons. In Tab.\ref{tab:tab1}, default parameters were
+used to infer networks.
+
+GENIE3 is a tree-based method which sees the network inference problem as $p$,
+the number of variables, independent supervised learning problems (todo cite:
+Irrthum?Van Anh?Pierre?). Formally, each sub-problem consists in the
+prediction of one variable, the target, from the remaining $p-1$ variables.
+This method uses random forests to estimate the target variable and variable
+importances can be derived to estimate the adjacency matrix $A$ (see (todo
+cite) for a more detailed description of the inference method). We compute
+$10000$ trees for each subproblem with the randomization parameter equals to
+$\log_2{p}$ and we limite the tree max-depth to respectively $1$, $2$ and $3$.
 
@@
 % Genie3 : "Conditioning" better and better but need a lot of trees
+
+\textcolor{red}{TODO : Discussion depth}
 
@@
 
+\begin{table}[tbh]
+\centering
+\begin{tabular}{@{}l *{8}{c}@{}}
+\hline
+  & \multicolumn{4}{c}{AUROC} & \multicolumn{4}{c}{AUPRC} \\
+\hline
+Methods $\backslash$ normal- & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 \\
+No  filtering       & 0.777 & 0.767 & 0.772 & 0.774 & 0.070 & 0.064 & 0.068 & 0.072\\
+P                   & 0.925 & 0.925 & 0.924 & 0.923 & 0.322 & 0.324 & 0.323 & 0.312\\
+P + W               & 0.931 & 0.930 & 0.928 & 0.927 & 0.333 & 0.334 & 0.327 & 0.313\\
+P + W + PCA         & 0.932 & 0.931 & 0.930 & 0.928 & 0.364 & 0.366 & 0.359 & 0.344\\
+Averaging           & 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388\\
+Averaging + Directivity & 0.944 & 0.943 & 0.942 & 0.940 & 0.404 & 0.405 & 0.399 & 0.389\\
+\end{tabular}
+\caption{TODO \textcolor{red}{version simple!!}}
+\label{tab:tab3}
+\end{table}
+
 \begin{table}
@@
   & \multicolumn{4}{c}{AUROC} & \multicolumn{4}{c}{AUPRC} \\
-\cmidrule(r){2-5}\cmidrule(r){6-9}
+\hline \hline
 Methods $\backslash$ normal- & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 \\
@@
 Partial correlation    & 0.930 &  0.927 &  0.926 &  0.923& 0.363  & 0.347 &  0.346 & 0.328 \\
+Partial correlation (avg.) & 0.938 & & & 0.932& 0.391 & & & 0.374\\
+% Our approach simple + dir & 0.939 & & & 0.933& 0.392 & & & 0.375\\
 Partial correlation (opt.) & 0.932 & 0.931 & 0.930 & 0.928 & 0.364 & 0.366 & 0.359 & 0.344 \\

### 2014-06-18 article.tex

@@
 
+We compare our approach to the Pearson correlation (see Section
+\ref{sec:inference}), the generalized transfer entropy (GTE) and GENIE3.
+\begin{description}
+\item[GTE], the baseline of the challenge, measures for all pairs of
+neurons $i$ and $j$ the reduction of uncertainty in predicting future values of
+$i$ given the observation of the time series of the neuron $j$
+conditionally to the observation of past time series of neuron $i$,
+whenever the average fluorescence is over a conditioning level.
+Conditioning level was set to reproduce baseline of the challenge.
+
+\item[GENIE3] (\cite{huynhthu2010inferring}) translates the inference of the
+network of $p$ neurons into $p$ supervised learning tasks. For each task,
+the fluorescence of a neuron is predicted from the fluorescence
+of all other neurons using a tree based ensemble such as
+random forest (\cite{breiman2001random}). The tree ensemble associate a
+variable importance scores (\cite{louppe2013understanding})
+to each neuron used in the predictions, which is used as a connectivity
+score. The following parameters are used
+$10000$ trees, $\log_2{p}$ neurons are randomly selected at each tree
+node to split the data and the maximal tree depth is constrained
+to 1, 2 or 3.
+\end{description}
+
 % TODO

### 2014-06-18 article.tex
add results

@@
 
-\textcolor{red}{SEUIL 0.11 for tabulars!!!}
+%\textcolor{red}{SEUIL 0.11 for tabulars!!!}
 
-In this section, we will first describe datasets and methods used for the comparison.
-Then, on Tab.\ref{tab:tab3}, our approach is decomposed to show the contribution of each stages .
-Afterwards, we will perform a comparison between several methods on Tab.\ref{tab:tab1} (or Fig.?).
-Note that two metrics are used to evaluate the performance.
-The end of this section is devoted to a discussion about the choice of metric and its relevance for the challenge.
+\begin{figure}
+\centering
+\includegraphics[width=0.7\linewidth]{images/curves}
+\caption{Method precision-recall and roc curves.}
+\label{fig:curves}
+\end{figure}
+
+In this section, we will first describe datasets and methods used for the
+comparison. Then, on Tab.\ref{tab:tab3}, our approach is decomposed to show
+the contribution of each stages . Afterwards, we will perform a comparison
+between several methods on Fig.\ref{fig:curves} and Tab.\ref{tab:tab1}. Note that two
+metrics are used to evaluate the performance and a single low-pass filter is used (Eq.\ref{eq:symetric-median}) and a threshold, i.e. $\tau = 0.11$. The end of this section is
+devoted to a discussion about the choice of metric and its relevance for the
+challenge.\\
 
@@
 correlation, we set those elements to the minimum of $\hat{A}$ prior
-assessment.
+assessment.\\
+
+On Tab.\ref{tab:tab3}, it can be seen that each step of our approach globally improves the score on both metrics.
+However, processing, weights and averaging (respectively denoted as $P$,$W$ and $Averaging$ in Tab.\ref{tab:tab3}) as described in section \ref{sec:filter} are the key steps of our algorithm.
 
@@
 \ref{sec:inference}), the generalized transfer entropy (GTE) and GENIE3.
-\begin{description}
-\item[GTE], the baseline of the challenge, measures for all pairs of
+
+\textbf{GTE} \citep{stetter2012model}
+, the baseline of the challenge, measures for all pairs of
 neurons $i$ and $j$ the reduction of uncertainty in predicting future values of
@@
 
-\item[GENIE3] (\cite{huynhthu2010inferring}) translates the inference of the
+\textbf{GENIE3} \citep{huynhthu2010inferring} translates the inference of the
 network of $p$ neurons into $p$ supervised learning tasks. For each task,
@@
 of all other neurons using a tree based ensemble such as
-random forest (\cite{breiman2001random}). The tree ensemble associate a
-variable importance scores (\cite{louppe2013understanding})
+random forest \citep{breiman2001random}. The tree ensemble associate a
+variable importance scores \citep{louppe2013understanding}
 to each neuron used in the predictions, which is used as a connectivity
@@
 node to split the data and the maximal tree depth is constrained
-to 1, 2 or 3.
-\end{description}
+to 1, 2 or 3.\\
 
@@
 
-At first sight, it appears on Tab.\ref{tab:tab1} that partial
-correlation outperforms other methods. Two main reasons may explain this.
-First, the quality of the infered network seems related to the conditioning
-part of the method. In every method except with partial correlation, indirect
-links are confounded with direct links.  Secondly, the gaussian assumption
-seems verified and thus linear method appears to be competitive, e.g. the
-method correlation already gives good results, with a non-linear method such
-as GENIE3.
+At first sight, it appears on Fig.\ref{fig:curves} %Tab.\ref{tab:tab1}   
+that partial correlation outperforms other methods. Two main reasons may explain
+this. First, the quality of the infered network seems related to the
+conditioning part of the method. In every method except with partial
+correlation, indirect links are confounded with direct links.  Secondly, the
+gaussian assumption seems verified and thus linear method appears to be
+competitive, e.g. the method correlation already gives good results, with a
+non-linear method such as GENIE3.
 
@@
 Averaging           & 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388\\
-Averaging + Directivity & 0.944 & 0.943 & 0.942 & 0.940 & 0.404 & 0.405 & 0.399 & 0.389\\
+%Averaging + Directivity & 0.944 & 0.943 & 0.942 & 0.940 & 0.404 & 0.405 & 0.399 & 0.389\\
 \end{tabular}
@@
 Partial correlation    & 0.930 &  0.927 &  0.926 &  0.923& 0.363  & 0.347 &  0.346 & 0.328 \\
-Partial correlation (avg.) & 0.938 & & & 0.932& 0.391 & & & 0.374\\
-% Our approach simple + dir & 0.939 & & & 0.933& 0.392 & & & 0.375\\
+Partial correlation (avg.) & 0.938 & 0.936 & 0.936 & 0.932& 0.391 & 0.389 & 0.385 & 0.374\\
+% Our approach simple + dir & 0.939 & 0.936 & 0.937 & 0.933& 0.392 & 0.390 & 0.386 & 0.375\\
 Partial correlation (opt.) & 0.932 & 0.931 & 0.930 & 0.928 & 0.364 & 0.366 & 0.359 & 0.344 \\
@@
 
+% Possible extensions
+% partial autocorrelation function (sometimes "partial correlation function")
+% conditional independence test
+% Speak about the complexity and parallelization of the methods
+
+In this paper, we present the winning method of the Connectomics challenge.
+This approach is simple and theorically grounded.
+We also evaluate the method in a more detailed way and perform a comparison with other inference methods.
+We also discuss the relevance of the metric used in the challenge.
+
+Obviously, we give a hint about limiting the depth of trees in the GENIE3 method to infer the network. It should be interesting to see if there is a optimum value for the maxmimal depth.
+
 In previous study \citep{shipley2002cause}, it has been suggested to
@@
 variables.
+Instead of considering only the highest order, it may be useful to study with accuracy the infered network at all orders.
+In this case, it may not be very relevant but interesting in case of dymanical networks.
 
-% Possible extensions
-% partial autocorrelation function (sometimes "partial correlation function")
-% conditional independence test
-% Speak about the complexity and parallelization of the methods
+As we mentionned, in order to maximize the ROC AUC, it was not necessary to discover causal relationships. It may be, in future works, promising to focus on that particular topic.
 

### 2014-06-19 article.tex
missing references

@@
 
-To filter more noise before computing the partial correlation, we kept
+To filter even more noise before computing the partial correlation, we kept
 $80\%$ of the eigen vectors which have the largest eigen

### 2014-06-19 article.tex
break 80 line char

@@
 
-\textcolor{red}{Say that we use PCA to derive the precision matrix + ref!.}
-
 To filter even more noise before computing the partial correlation, we kept
@@
 between several methods on Fig.\ref{fig:curves} and Tab.\ref{tab:tab1}. Note that two
-metrics are used to evaluate the performance and a single low-pass filter is used (Eq.\ref{eq:symetric-median}) and a threshold, i.e. $\tau = 0.11$. The end of this section is
-devoted to a discussion about the choice of metric and its relevance for the
-challenge.\\
+metrics are used to evaluate the performance and a single low-pass filter is
+used (Eq.\ref{eq:symetric-median}) and a threshold, i.e. $\tau = 0.11$. The end
+of this section is devoted to a discussion about the choice of metric and its
+relevance for the challenge.
 
@@
 
-On Tab.\ref{tab:tab3}, it can be seen that each step of our approach globally improves the score on both metrics.
-However, processing, weights and averaging (respectively denoted as $P$,$W$ and $Averaging$ in Tab.\ref{tab:tab3}) as described in section \ref{sec:filter} are the key steps of our algorithm.
+On Tab.\ref{tab:tab3}, it can be seen that each step of our approach globally
+improves the score on both metrics. However, processing, weights and averaging
+(respectively denoted as $P$,$W$ and $Averaging$ in Tab.\ref{tab:tab3}) as
+described in section \ref{sec:filter} are the key steps of our algorithm.
 
@@
 In this paper, we present the winning method of the Connectomics challenge.
-This approach is simple and theorically grounded.
-We also evaluate the method in a more detailed way and perform a comparison with other inference methods.
+This approach is simple and theorically grounded. We also evaluate the method
+in a more detailed way and perform a comparison with other inference methods.
 We also discuss the relevance of the metric used in the challenge.
 
-Obviously, we give a hint about limiting the depth of trees in the GENIE3 method to infer the network. It should be interesting to see if there is a optimum value for the maxmimal depth.
+Obviously, we give a hint about limiting the depth of trees in the GENIE3
+method to infer the network. It should be interesting to see if there is a
+optimum value for the maxmimal depth.
 
@@
 would take into account multiple indirect paths between a given pair of
-variables.
-Instead of considering only the highest order, it may be useful to study with accuracy the infered network at all orders.
-In this case, it may not be very relevant but interesting in case of dymanical networks.
+variables. Instead of considering only the highest order, it may be useful to
+study with accuracy the infered network at all orders. In this case, it may not
+be very relevant but interesting in case of dymanical networks.
 
-As we mentionned, in order to maximize the ROC AUC, it was not necessary to discover causal relationships. It may be, in future works, promising to focus on that particular topic.
+As we mentionned, in order to maximize the ROC AUC, it was not necessary to
+discover causal relationships. It may be, in future works, promising to focus
+on that particular topic.
 

### 2014-06-19 article.tex
re-order text

@@
 
-\section{Experiments}
-\label{sec:results}
+\section{Empirical experiments} \label{sec:results}
 
@@
 
-\begin{figure}
-\centering
-\includegraphics[width=0.7\linewidth]{images/curves}
-\caption{Method precision-recall and roc curves.}
-\label{fig:curves}
-\end{figure}
+% In this section, we will first describe datasets and methods used for the
+% comparison. Then, on Table \ref{tab:tab3}, our approach is decomposed to show
+% the contribution of each pre-processing steps. Afterwards, we will perform a comparison
+% between several methods on Figure \ref{fig:curves} and Table \ref{tab:tab1}. Note that two
+% metrics are used to evaluate the performance and a single low-pass filter is
+% used (Eq. \ref{eq:symetric-median}) and a threshold, i.e. $\tau = 0.11$. The end
+% of this section is devoted to a discussion about the choice of metric and its
+% relevance for the challenge.
 
-In this section, we will first describe datasets and methods used for the
-comparison. Then, on Tab.\ref{tab:tab3}, our approach is decomposed to show
-the contribution of each stages . Afterwards, we will perform a comparison
-between several methods on Fig.\ref{fig:curves} and Tab.\ref{tab:tab1}. Note that two
-metrics are used to evaluate the performance and a single low-pass filter is
-used (Eq.\ref{eq:symetric-median}) and a threshold, i.e. $\tau = 0.11$. The end
-of this section is devoted to a discussion about the choice of metric and its
-relevance for the challenge.
+% \subsection{Assessment methodology}
 
@@
 of the Connectomics challenge : \textit{normal-1, normal-2, normal-3, normal-4}.
-Those datasets are time series of size $T=179500$ of image calcium from simulated
-neuronal networks \citep{stetter2012model} with $|V|=1000$ neurons. The networks
-to inferred have around 15000 edges and are similar to those
-used to rank challenge participants.
+Those datasets have $|V|=1000$ time series of length $T=179500$ of image
+calcium from simulated neuronal networks \citep{stetter2012model}. Those
+networks have approximately 15000 edges.
 
@@
 ($(i, i) \not \in E, \forall i \in V$) and some inference methods could
-give maximal scores to the diagonal of $\hat{A}$, e.g. Pearson
-correlation, we set those elements to the minimum of $\hat{A}$ prior
-assessment.\\
+give maximal scores to those edges, e.g. Pearson
+correlation, those elements are set to have minimal connectivity score prior
+assessment.
 
-On Tab.\ref{tab:tab3}, it can be seen that each step of our approach globally
-improves the score on both metrics. However, processing, weights and averaging
-(respectively denoted as $P$,$W$ and $Averaging$ in Tab.\ref{tab:tab3}) as
-described in section \ref{sec:filter} are the key steps of our algorithm.
+We will compare our approach to the Pearson correlation (see Section
+\ref{sec:inference}), the generalized transfer entropy (GTE) and GENIE3:
+\begin{itemize}
 
-We compare our approach to the Pearson correlation (see Section
-\ref{sec:inference}), the generalized transfer entropy (GTE) and GENIE3.
-
-\textbf{GTE} \citep{stetter2012model}
+\item \textbf{GTE} \citep{stetter2012model}
 , the baseline of the challenge, measures for all pairs of
@@
 
-\textbf{GENIE3} \citep{huynhthu2010inferring} translates the inference of the
+\item \textbf{GENIE3} \citep{huynhthu2010inferring} translates the inference of the
 network of $p$ neurons into $p$ supervised learning tasks. For each task,
@@
 score. The following parameters are used
-$10000$ trees, $\log_2{p}$ neurons are randomly selected at each tree
-node to split the data and the maximal tree depth is constrained
-to 1, 2 or 3.\\
+$10000$ trees, $\log_2{p}$ variables are randomly selected to split a tree
+node and the maximal tree depth is constrained to 1, 2 or 3.
+\end{itemize}
 
-% TODO
-%   - discussions about the results
-%   - discussions about the metrics (Gilles' text)
-
-% For the directory method, only filters defined by Equations
-% \ref{eq:low-pass}, \ref{eq:high-pass} and \ref{eq:hard-treshold-filter} were
-% used.
-
-% Dummy classifier?
-
-% GTE : Explaning the method (default parameters!)
-
-% Explaining the method (thèse de Gilles)
-
-% Directivity : ?
-
-%Opt: obviously when parameters are tuned/optimized, it's slightly better --> see appendix for a full description of the method
-% Avg.: Averaging over the threholds and L-P filters improves a lot both metrics.
-
-% Partial correlation : Obvious improvements (both metric) because of the conditioning
-% Correlation : Already give good results
+\subsection*{Comparison with state-of-the art methods}
 
@@
 
-% Averaging
+\begin{figure}[bth]
+\centering
+\includegraphics[width=0.6\linewidth]{images/curves}
+\caption{Method precision-recall and roc curves.}
+\label{fig:curves}
+\end{figure}
 
@@
 according to both metrics.
-
-%% Depth -- Gilles chapitre 7
-% Genie3 : better in auprc while worse in auroc than GTE. Why?
-% Genie3 : "Conditioning" better and better but need a lot of trees
-
-\textcolor{red}{TODO : Discussion depth}
-
-% Discussion about the metrics
 
@@
 
-\begin{table}[tbh]
-\centering
-\begin{tabular}{@{}l *{8}{c}@{}}
-\hline
-  & \multicolumn{4}{c}{AUROC} & \multicolumn{4}{c}{AUPRC} \\
-\hline
-Methods $\backslash$ normal- & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 \\
-No  filtering       & 0.777 & 0.767 & 0.772 & 0.774 & 0.070 & 0.064 & 0.068 & 0.072\\
-P                   & 0.925 & 0.925 & 0.924 & 0.923 & 0.322 & 0.324 & 0.323 & 0.312\\
-P + W               & 0.931 & 0.930 & 0.928 & 0.927 & 0.333 & 0.334 & 0.327 & 0.313\\
-P + W + PCA         & 0.932 & 0.931 & 0.930 & 0.928 & 0.364 & 0.366 & 0.359 & 0.344\\
-Averaging           & 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388\\
-%Averaging + Directivity & 0.944 & 0.943 & 0.942 & 0.940 & 0.404 & 0.405 & 0.399 & 0.389\\
-\end{tabular}
-\caption{TODO \textcolor{red}{version simple!!}}
-\label{tab:tab3}
-\end{table}
+% TODO
+%   - discussions about the results
+%   - discussions about the metrics (Gilles' text)
+
+% Dummy classifier?
+
+% GTE : Explaning the method (default parameters!)
+
+% Explaining the method (thèse de Gilles)
+
+% Directivity : ?
+
+% Opt: obviously when parameters are tuned/optimized, it's slightly better -->
+% see appendix for a full description of the method
+% Avg.: Averaging over the threholds and L-P filters improves a lot both metrics.
+
+% Partial correlation : Obvious improvements (both metric) because of the conditioning
+% Correlation : Already give good results
+
+% Averaging
+
+%% Depth -- Gilles chapitre 7
+% Genie3 : better in auprc while worse in auroc than GTE. Why?
+% Genie3 : "Conditioning" better and better but need a lot of trees
+
+\textcolor{red}{TODO: depth discussion }
+
+% Discussion about the metrics
 
@@
 
-\begin{table}
-\small
-\centering
-\begin{tabular}{@{}l *{8}{c}@{}}
-  & \multicolumn{4}{c}{AUROC} & \multicolumn{4}{c}{AUPRC} \\
-\cmidrule(r){2-5}\cmidrule(r){6-9}
-Methods $\backslash$ normal- & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 \\
-\hline \hline
-% Directivity \textcolor{red}{appendix?} & 0.535 & 0.526 & 0.533 & 0.535 & 0.012 & 0.012 & 0.012 & 0.012 \\
-GENIE3 (depth = 1)     &  & & & & & & & \\
-GENIE3 (depth = 2)     &  & & & & & & & \\
-GENIE3 (depth = 3)     &  & & & & & & & \\
-GTE                    &  & & & & & & & \\
-% Our approach + dir  \textcolor{red}{appendix?}   & 0.944 & 0.943 & 0.942 & 0.940 & 0.404 & 0.405 & 0.399 & 0.389 \\
-\end{tabular}
-\caption{TODO (network are undirected)}
-\label{tab:tab2}
-\end{table}
+% \begin{table}
+% \small
+% \centering
+% \begin{tabular}{@{}l *{8}{c}@{}}
+%   & \multicolumn{4}{c}{AUROC} & \multicolumn{4}{c}{AUPRC} \\
+% \cmidrule(r){2-5}\cmidrule(r){6-9}
+% Methods $\backslash$ normal- & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 \\
+% \hline \hline
+% % Directivity \textcolor{red}{appendix?} & 0.535 & 0.526 & 0.533 & 0.535 & 0.012 & 0.012 & 0.012 & 0.012 \\
+% GENIE3 (depth = 1)     &  & & & & & & & \\
+% GENIE3 (depth = 2)     &  & & & & & & & \\
+% GENIE3 (depth = 3)     &  & & & & & & & \\
+% GTE                    &  & & & & & & & \\
+% % Our approach + dir  \textcolor{red}{appendix?}   & 0.944 & 0.943 & 0.942 & 0.940 & 0.404 & 0.405 & 0.399 & 0.389 \\
+% \end{tabular}
+% \caption{TODO (network are undirected)}
+% \label{tab:tab2}
+% \end{table}
+
+\subsection*{Signal processing highly improves performance}
+
+On Table \ref{tab:tab3}, it can be seen that each step of our approach globally
+improves the score on both metrics. However, processing, weights and averaging
+(respectively denoted as $P$,$W$ and $Averaging$ in Tab.\ref{tab:tab3}) as
+described in Section \ref{sec:filter} are the key steps of our algorithm.
 
@@
 \centering
-\caption{TODO}
 \begin{tabular}{@{}l *{8}{c}@{}}
+\hline
   & \multicolumn{4}{c}{AUROC} & \multicolumn{4}{c}{AUPRC} \\
-\cmidrule(r){2-5}\cmidrule(r){6-9}
+\hline
 Methods $\backslash$ normal- & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 \\
-\midrule
 No  filtering       & 0.777 & 0.767 & 0.772 & 0.774 & 0.070 & 0.064 & 0.068 & 0.072\\
@@
 Averaging           & 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388\\
-Averaging + Directivity & 0.944 & 0.943 & 0.942 & 0.940 & 0.404 & 0.405 & 0.399 & 0.389\\
+%Averaging + Directivity & 0.944 & 0.943 & 0.942 & 0.940 & 0.404 & 0.405 & 0.399 & 0.389\\
 \end{tabular}
+\caption{TODO \textcolor{red}{version simple!!}}
+\label{tab:tab3}
 \end{table}
@@
 \section*{Acknowledgements}
-
 A. Joly and G. Louppe are research fellows of
@@
 that $Z$ has a contribution of $0.3\%$ to the prediction of an edge.
+
+% For the directory method, only filters defined by Equations
+% \ref{eq:low-pass}, \ref{eq:high-pass} and \ref{eq:hard-treshold-filter} were
+% used.
 

### 2014-06-19 article.tex
wording comparison state of the art

@@
 We will compare our approach to the Pearson correlation (see Section
-\ref{sec:inference}), the generalized transfer entropy (GTE) and GENIE3:
+\ref{sec:inference}), the generalized transfer entropy (GTE) and GENIE3.
 \begin{itemize}
-
 \item \textbf{GTE} \citep{stetter2012model}
@@
 Conditioning level was set to reproduce baseline of the challenge.
+\textcolor{red}{Talk about pre-processing}
 
@@
 
-At first sight, it appears on Fig.\ref{fig:curves} %Tab.\ref{tab:tab1}
-that partial correlation outperforms other methods. Two main reasons may explain
-this. First, the quality of the infered network seems related to the
-conditioning part of the method. In every method except with partial
-correlation, indirect links are confounded with direct links.  Secondly, the
-gaussian assumption seems verified and thus linear method appears to be
-competitive, e.g. the method correlation already gives good results, with a
-non-linear method such as GENIE3.
+Figure \ref{fig:curves} shows the ROC curve and precision-recall curve
+for correlation, GTE and partial correlation on the \textcolor{red}{normal-?}
+dataset. The partial correlation outperforms other state-of-the-art methods
+by at least factor of 2 in AUPRC and an increased of $5\%$ in AUROC. There
+are two reasons that explains such overwhelming difference: (i) among
+those methods only the partial correlation make the distinction between
+direct and indirect connection, (ii) the simulated network from the
+\citep{stetter2012model} generator could be reduced to a linear model after
+pre-processing.
 
@@
 \includegraphics[width=0.6\linewidth]{images/curves}
-\caption{Method precision-recall and roc curves.}
+\caption{Method precision-recall and roc curves. \textcolor{red}{GENI3?}}
 \label{fig:curves}
@@
 
-It also appears that the averaging over the low-pass filter designs and the
-threshold values increases significantly the quality of the infered network
-according to both metrics.
-
-Observing Tab.\ref{tab:tab1}, it appears that best methods only infer the
+Observing Table \ref{tab:tab1}, it appears that best methods only infer the
 \textbf{undirected} network by giving the same weights to both edges $(i,j)$
@@
 described in Section \ref{sec:filter} are the key steps of our algorithm.
+
+It also appears that the averaging over the low-pass filter designs and the
+threshold values increases significantly the quality of the infered network
+according to both metrics.
 

### 2014-06-19 article.tex
Wordings (1+2)

--- 2014-06-19 article.tex
@@
 of neurons, producing individual time series representing their fluoresence
-intensity. In this context,  the connectome inference problem consists in
+intensity. From these data, the connectome inference problem consists in
 retrieving the synaptic connections between neurons on the basis of the
 fluoresence time series. In particular, this problem is often made difficult
-because of experimental issues, including masking effects making some of the
-neurons not to be observed or confounded with others, a low sampling rate of
+because of experimental issues, including masking effects (making some of the
+neurons not to be observed or confounded with others), the low sampling rate of
 the optical device with respect to the neural activity speed or the slow decay
@@
 
-In this paper, we present a simplified -- yet nearly as good -- version of
-the winning method\footnote{Code available at \url{https://github.com/asutera
+In this paper, we present a simplified -- yet nearly as good -- version of the
+winning method\footnote{Code available at \url{https://github.com/asutera
 /kaggle-connectomics}} of the Connectomics
@@
 theoretically grounded approach based on signal processing techniques and
-partial correlation statistics. The rest of the paper is structured as
-follows: Section \ref{sec:filter} describes the signal processing methods
-applied on fluorescent calcium time series; Section \ref{sec:inference} then
-presents the proposed approach and its theoretical properties; Section
-\ref{sec:results} provides an empirical analysis and comparison with other
-network inference methods, while Section \ref{sec:conclusion} finally
-discusses our work and provides further research directions. Additionnaly, Appendix
-\ref{app:optimized} further describes our actual winning method, giving slightly
-better results than the method presented in the paper but highly tuned for the
+partial correlation statistics. The paper is structured as follows: Section
+\ref{sec:filter} describes the signal processing methods applied on fluorescent
+calcium time series; Section \ref{sec:inference} then presents the proposed
+approach and its theoretical properties; Section \ref{sec:results} provides an
+empirical analysis and comparison with other network inference methods, while
+Section \ref{sec:conclusion} finally discusses our work and provides further
+research directions. Additionnaly, Appendix \ref{app:optimized} further
+describes, in all details, our actual winning method, giving slightly better
+results than the method presented in the paper but highly tuned for the
 challenge.
@@
 \includegraphics[width=0.4\linewidth]{images/fig_filtering}
-\caption{Signal processing process.}
+\caption{Signal processing process for extracting peaks from the raw fluorescence data.}
 \label{fig:filtered-signal}
@@
 
-As the first plot in Figure~\ref{fig:filtered-signal} illustrates, due to
-light scattering artifacts that ordinarily affects the quality of the
-recording~\citep{lichtman2011big}, the raw fluoresence signal is very noisy.
-Accordingly, the first step of our pipeline is to smoothen the signal, using a low-pass filter for
-filtering out high frequency noise, applying one of the following designs and
-resulting in the second plot in the figure:
+As the first plot in Figure~\ref{fig:filtered-signal} illustrates, the raw
+fluoresence signal is very noisy due to light scattering artifacts that
+ordinarily affects the quality of the recording~\citep{lichtman2011big}.
+Accordingly, the first step of our pipeline is to smoothen the signal, using a
+low-pass filter for filtering out high frequency noise and resulting in the
+second plot in the figure:
 \begin{align}
@@
 % asymmetrical weighted median
-f_2(x^t_i) &= 0.4 x^{t-3}_i + 0.6 x^{t-2}_i + 0.8 x^{t-1}_i + x_{t}^i.
+f_2(x^t_i) &= 0.4 x^{t-3}_i + 0.6 x^{t-2}_i + 0.8 x^{t-1}_i + x_{t}^i,
 \label{eq:weighted-asymetric-median}
 \end{align}
+where $f_1$ is the filter proposed in the simplified variant of our approach
+and $f_2$ is the filter actually used within our winning algorithm.
 
@@
 
-The full signal processing of our approach is defined by the composed function
-$
-w \cdot h \cdot g \cdot f_k
-$
-where $f_k$ is one of the low-pass filter designs.
+In those terms, the full signal processing pipeline of our approach is defined
+by the composed function $w \cdot h \cdot g \cdot f_1$ (resp $f_2$).
 

### 2014-06-19 article.tex
second pass on metric choice

@@
 matrices was estimated from the time series by varying the hard-threshold value
-$\tau$ and the design of the low-pass filter (mentionned in section \ref{sec:filter} and appendix \ref{app:optimized}).
+$\tau$ and the design of the low-pass filter (mentionned in section
+\ref{sec:filter} and appendix \ref{app:optimized}).
 
@@
 \section{Empirical experiments} \label{sec:results}
-
-%\textcolor{red}{SEUIL 0.11 for tabulars!!!}
-
-% In this section, we will first describe datasets and methods used for the
-% comparison. Then, on Table \ref{tab:tab3}, our approach is decomposed to show
-% the contribution of each pre-processing steps. Afterwards, we will perform a comparison
-% between several methods on Figure \ref{fig:curves} and Table \ref{tab:tab1}. Note that two
-% metrics are used to evaluate the performance and a single low-pass filter is
-% used (Eq. \ref{eq:symetric-median}) and a threshold, i.e. $\tau = 0.11$. The end
-% of this section is devoted to a discussion about the choice of metric and its
-% relevance for the challenge.
-
-% \subsection{Assessment methodology}
 
@@
 
-\subsection*{Comparison with state-of-the art methods}
+\subsection{Partial correlation compare favorably with other state-of-the art methods}
 
@@
 dataset. The partial correlation outperforms other state-of-the-art methods
-by at least factor of 2 in AUPRC and an increased of $5\%$ in AUROC. There
-are two reasons that explains such overwhelming difference: (i) among
-those methods only the partial correlation make the distinction between
-direct and indirect connection, (ii) the simulated network from the
+by at least factor of 2 in AUPRC reaching $0.347$ and an increased of $0.05$ in
+AUROC.
+
+Two reasons might explain such overwhelming difference: (i) among
+those methods only the partial correlation makes the distinction between
+direct and indirect connections, (ii) the simulated network from the
 \citep{stetter2012model} generator could be reduced to a linear model after
-pre-processing.
+pre-processing. \textcolor{red}{Those results generalized over the other
+datasets see Appendix REF.}
+
+\textcolor{red}{TODO: depth discussion }
+
+% Opt: obviously when parameters are tuned/optimized, it's slightly better -->
+% see appendix for a full description of the method
 
@@
 \includegraphics[width=0.6\linewidth]{images/curves}
-\caption{Method precision-recall and roc curves. \textcolor{red}{GENI3?}}
+\caption{Method precision-recall and roc curves. \textcolor{red}{GENI3?}
+         $\tau=0.11$}
 \label{fig:curves}
 \end{figure}
-
-Observing Table \ref{tab:tab1}, it appears that best methods only infer the
-\textbf{undirected} network by giving the same weights to both edges $(i,j)$
-and $(j,i)$. This is quite surprising considering the goal of the challenge,
-namely predicted directed connections between neurons. Besides, if the true
-network undirected, i.e. for all links $(i,j)$, back links are added, is the
-infered network then the score obtained according to the ROC AUC metric is
-very high ($\approx 0.9956$ on \textit{normal-1}). Therefore, an undirected
-infered network seems sufficient to maximize the ROC AUC score without trying
-to identify the link direction. Indeed, predicting perfectly directivity only
-yields a small gain ($\approx 0.005$ on \textit{normal-1}) which is is not
-very rewarding. In contrast, the same experiment with the precision recall
-metric rewards less the undirected network ($\approx 0.789$ on
-\textit{normal-1}) and the gain margin in predicting the link directivity is
-large enough to be interesting ($\approx 0.211$ on \textit{normal-1}). For
-these reason, it seems that the metric used in the contest, i.e. the ROC AUC,
-does not seem consistent with the goal of predicting directed connections
-between neurons. Another metric, such as the AUC PRC, is maybe more
-appropriate to assess the quality of the \textbf{directed} infered network.
-
-Interestingly, an easy way to improve results for asymmetric methods (see
-Tab.\ref{tab:tab2}), namely GTE and GENIE3, is to make undirected the infered
-network. It proves once again that trying to detect the link direction is more
-penalizing than rewarding.
-
-% TODO
-%   - discussions about the results
-%   - discussions about the metrics (Gilles' text)
-
-% Dummy classifier?
-
-% GTE : Explaning the method (default parameters!)
-
-% Explaining the method (thèse de Gilles)
-
-% Directivity : ?
-
-% Opt: obviously when parameters are tuned/optimized, it's slightly better -->
-% see appendix for a full description of the method
-% Avg.: Averaging over the threholds and L-P filters improves a lot both metrics.
-
-% Partial correlation : Obvious improvements (both metric) because of the conditioning
-% Correlation : Already give good results
-
-% Averaging
-
-%% Depth -- Gilles chapitre 7
-% Genie3 : better in auprc while worse in auroc than GTE. Why?
-% Genie3 : "Conditioning" better and better but need a lot of trees
-
-\textcolor{red}{TODO: depth discussion }
-
-% Discussion about the metrics
-
-\begin{table}
-\small
-\centering
-\begin{tabular}{@{}l *{8}{c}@{}}
-  & \multicolumn{4}{c}{AUROC} & \multicolumn{4}{c}{AUPRC} \\
-\hline \hline
-Methods $\backslash$ normal- & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 \\
-\hline \hline
-% Directivity \textcolor{red}{appendix?} & 0.535 & 0.526 & 0.533 & 0.535 & 0.012 & 0.012 & 0.012 & 0.012 \\
-Correlation            & 0.886 & 0.884 & 0.891 & 0.877 & 0.153 & 0.145 & 0.170 & 0.132 \\
-GENIE3 (depth = 1)     & 0.878 & & & & 0.184 & & & \\
-GENIE3 (depth = 2)     & 0.889 & & & & 0.217 & & & \\
-GENIE3 (depth = 3)     & & & & & & & & \\
-GTE                    & 0.890 & 0.893 & 0.894 & 0.873 & 0.171 & 0.174 & 0.197 & 0.142 \\
-Partial correlation    & 0.930 &  0.927 &  0.926 &  0.923& 0.363  & 0.347 &  0.346 & 0.328 \\
-Partial correlation (avg.) & 0.938 & 0.936 & 0.936 & 0.932& 0.391 & 0.389 & 0.385 & 0.374\\
-% Our approach simple + dir & 0.939 & 0.936 & 0.937 & 0.933& 0.392 & 0.390 & 0.386 & 0.375\\
-Partial correlation (opt.) & 0.932 & 0.931 & 0.930 & 0.928 & 0.364 & 0.366 & 0.359 & 0.344 \\
-Our approach (opt. \& avg.)    & 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388 \\
-% Our approach + dir  \textcolor{red}{appendix?}   & 0.944 & 0.943 & 0.942 & 0.940 & 0.404 & 0.405 & 0.399 & 0.389 \\
-\end{tabular}
-\caption{TODO}
-\label{tab:tab1}
-\end{table}
 
@@
 
+% Explaining the method (thèse de Gilles)
+% Avg.: Averaging over the threholds and L-P filters improves a lot both metrics.
+% Averaging
+
+%% Depth -- Gilles chapitre 7
+% Genie3 : better in auprc while worse in auroc than GTE. Why?
+% Genie3 : "Conditioning" better and better but need a lot of trees
+
 \begin{table}[tbh]
@@
 \end{table}
+
+\subsection{Area under the ROC curve is a poor metric for network inference}
+
+The best method only infers the \textbf{undirected} network by giving the
+same connectivity score to both edges $(i,j)$ and $(j,i)$. This is quite
+surprising considering the problem statement.
+
+If one would infer perfectly the undirected network, it would already yield
+high AUROC score for instance $\approx{}0.996$ on \textit{normal-1}. Trying
+to infer edge directivity is likely to be counter-productive or yield
+small AUROC gain. The area under the ROC curve is not a consistent metric
+with respect to the problem statement.
+By contrast, the same experiment with AUPRC would yield
+to a score of $\approx 0.789$ on \textit{normal-1}. Thus inferring
+correctly directivity would be more rewarding in AUPRC term.
+Interestingly, methods that takes into account directivity, namely GTE and
+GENIE3, improve their AUROC and AUPRC by giving the same way to directed edges.
+Trying to detect the link direction is more penalizing than rewarding.
+
+For these reasons, we strongly advice to avoid the AUROC
+for the assessment network inference using a more appropriate
+metric such as the area under the precision-recall curve (AUPRC). Those
+conclusions are in line with \cite{schrynemackers2013protocols}.
 
@@
 % used.
+
+\section{Extended results}
+
+\begin{table}
+\small
+\centering
+\begin{tabular}{@{}l *{8}{c}@{}}
+  & \multicolumn{4}{c}{AUROC} & \multicolumn{4}{c}{AUPRC} \\
+\hline \hline
+Methods $\backslash$ normal- & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 \\
+\hline \hline
+% Directivity \textcolor{red}{appendix?} & 0.535 & 0.526 & 0.533 & 0.535 & 0.012 & 0.012 & 0.012 & 0.012 \\
+Correlation            & 0.886 & 0.884 & 0.891 & 0.877 & 0.153 & 0.145 & 0.170 & 0.132 \\
+GENIE3 (depth = 1)     & 0.878 & & & & 0.184 & & & \\
+GENIE3 (depth = 2)     & 0.889 & & & & 0.217 & & & \\
+GENIE3 (depth = 3)     & & & & & & & & \\
+GTE                    & 0.890 & 0.893 & 0.894 & 0.873 & 0.171 & 0.174 & 0.197 & 0.142 \\
+Partial correlation    & 0.930 &  0.927 &  0.926 &  0.923& 0.363  & 0.347 &  0.346 & 0.328 \\
+Partial correlation (avg.) & 0.938 & 0.936 & 0.936 & 0.932& 0.391 & 0.389 & 0.385 & 0.374\\
+% Our approach simple + dir & 0.939 & 0.936 & 0.937 & 0.933& 0.392 & 0.390 & 0.386 & 0.375\\
+Partial correlation (opt.) & 0.932 & 0.931 & 0.930 & 0.928 & 0.364 & 0.366 & 0.359 & 0.344 \\
+Our approach (opt. \& avg.)    & 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388 \\
+% Our approach + dir  \textcolor{red}{appendix?}   & 0.944 & 0.943 & 0.942 & 0.940 & 0.404 & 0.405 & 0.399 & 0.389 \\
+\end{tabular}
+\caption{TODO}
+\label{tab:tab1}
+\end{table}
 

### 2014-06-19 article.tex
wording

@@
 It also appears that the averaging over the low-pass filter designs and the
-threshold values increases significantly the quality of the infered network
+threshold values increases significantly the quality of the inferred network
 according to both metrics.
@@
 
-If one would infer perfectly the undirected network, it would already yield
+If the undirected network is perfectly, it would already yield
 high AUROC score for instance $\approx{}0.996$ on \textit{normal-1}. Trying
 to infer edge directivity is likely to be counter-productive or yield
-small AUROC gain. The area under the ROC curve is not a consistent metric
-with respect to the problem statement.
+small gain.
 By contrast, the same experiment with AUPRC would yield
@@
 
-For these reasons, we strongly advice to avoid the AUROC
-for the assessment network inference using a more appropriate
-metric such as the area under the precision-recall curve (AUPRC). Those
+The area under the ROC curve is not consistent metric
+with respect to the problem statement. We strongly advice to avoid the AUROC
+for the assessment of network inference method. An alternative metric would
+be to use the area under the precision-recall curve (AUPRC). Those
 conclusions are in line with \cite{schrynemackers2013protocols}.

### 2014-06-19 article.tex
typo
wording

@@
 
-\subsection{Partial correlation compare favorably with other state-of-the art methods}
+\subsection{Partial correlation improves over state-of-the-art methods}
 
@@
 The area under the ROC curve is not consistent metric
-with respect to the problem statement. We strongly advice to avoid the AUROC
+with respect to the problem statement. We advice to avoid the AUROC
 for the assessment of network inference method. An alternative metric would
-be to use the area under the precision-recall curve (AUPRC). Those
+be the area under the precision-recall curve (AUPRC). Those
 conclusions are in line with \cite{schrynemackers2013protocols}.

### 2014-06-19 article.tex
cosmit
image curves

--- 2014-06-19 article.tex
@@
 Figure \ref{fig:curves} shows the ROC curve and precision-recall curve
-for correlation, GTE and partial correlation on the \textcolor{red}{normal-?}
+for correlation, GTE and partial correlation on the \textit{normal-2}
 dataset. The partial correlation outperforms other state-of-the-art methods
@@
 \citep{stetter2012model} generator could be reduced to a linear model after
-pre-processing. \textcolor{red}{Those results generalized over the other
-datasets see Appendix REF.}
-
-\textcolor{red}{TODO: depth discussion }
+pre-processing. Those results is obviously generalized over the other
+datasets see Appendix \textcolor{red}{REF}.
 
@@
 \centering
-\includegraphics[width=0.6\linewidth]{images/curves}
+\includegraphics[width=\linewidth]{images/curves}
 \caption{Method precision-recall and roc curves. \textcolor{red}{GENI3?}

### 2014-06-19 article.tex

--- 2014-06-19 article.tex
@@
 
-\subsection{Partial correlation improves over state-of-the-art methods}
+\subsection*{Partial correlation improves over state-of-the-art methods}
 
 Figure \ref{fig:curves} shows the ROC curve and precision-recall curve
-for correlation, GTE and partial correlation on the \textcolor{red}{normal-?}
+for correlation, GTE and partial correlation on the \textit{normal-2}
 dataset. The partial correlation outperforms other state-of-the-art methods
@@
 
-\subsection{Area under the ROC curve is a poor metric for network inference}
+\subsection*{Area under the ROC curve is a poor metric for network inference}
 

### 2014-06-19 article.tex
add note

--- 2014-06-19 article.tex
@@
 
-\subsection{Partial correlation improves over state-of-the-art methods}
+\subsection*{Partial correlation improves over state-of-the-art methods}
 
@@
 
+\textcolor{red}{The whole sub-section should be moved to the appendix and
+                replace by one or two sentences.}
+
 On Table \ref{tab:tab3}, it can be seen that each step of our approach globally

### 2014-06-19 article.tex
wording
discuss about depth

--- 2014-06-19 article.tex
@@
 
+As it can also be seen on Figure \ref{fig:curves}, the GENIE3 performance increases with deeper trees.
+The reason is twofold.
+First, the deeper the tree, the larger is the conditioning.
+As it was observed in the comparison between correlation and partial correlation, it screens indirect links in the infered network.
+Second, the number of trees when trees are small need to be much higher in order to correctly estimate all pairs.
+However, as suggested by \cite{Gilles2014understanding}, limiting the maximal depth of trees may help to reduce the misestimation bias in variable importance comuting, i.e.
+infering the strengh of a link.
+
 % Opt: obviously when parameters are tuned/optimized, it's slightly better -->
@@
 \centering
+\small
 \begin{tabular}{@{}l *{8}{c}@{}}

### 2014-06-19 article.tex

@@
 
-If the undirected network is perfectly, it would already yield
+If the undirected network is perfectly inferred, it would already yield
 high AUROC score for instance $\approx{}0.996$ on \textit{normal-1}. Trying

### 2014-06-19 article.tex
break at 80

@@
 
-As it can also be seen on Figure \ref{fig:curves}, the GENIE3 performance increases with deeper trees.
-The reason is twofold.
-First, the deeper the tree, the larger is the conditioning.
-As it was observed in the comparison between correlation and partial correlation, it screens indirect links in the infered network.
-Second, the number of trees when trees are small need to be much higher in order to correctly estimate all pairs.
-However, as suggested by \cite{Gilles2014understanding}, limiting the maximal depth of trees may help to reduce the misestimation bias in variable importance comuting, i.e.
+As it can also be seen on Figure \ref{fig:curves}, the GENIE3 performance
+increases with deeper trees. The reason is twofold. First, the deeper the
+tree, the larger is the conditioning. As it was observed in the comparison
+between correlation and partial correlation, it screens indirect links in the
+infered network. Second, the number of trees when trees are small need to be
+much higher in order to correctly estimate all pairs. However, as suggested by
+\cite{Gilles2014understanding}, limiting the maximal depth of trees may help
+to reduce the misestimation bias in variable importance comuting, i.e.
 infering the strengh of a link.

### 2014-06-19 article.tex
we use both filter in the final approach

@@
 As the first plot in Figure~\ref{fig:filtered-signal} illustrates, the raw
-fluoresence signal is very noisy due to light scattering artifacts that
+fluorescence signal is very noisy due to light scattering artifacts that
 ordinarily affects the quality of the recording~\citep{lichtman2011big}.
-Accordingly, the first step of our pipeline is to smoothen the signal, using a
-low-pass filter for filtering out high frequency noise and resulting in the
-second plot in the figure:
+Accordingly, the first step of our pipeline is to smoothen the signal, using
+one the following low-pass filter for filtering out high frequency noise :
 \begin{align}
@@
 \end{align}
-where $f_1$ is the filter proposed in the simplified variant of our approach
-and $f_2$ is the filter actually used within our winning algorithm.
+where \textcolor{red}{$f_?$} effect is shown in the second plot in the figure.
 
@@
 Figure \ref{fig:curves} shows the ROC curve and precision-recall curve
-for correlation, GTE and partial correlation on the \textit{normal-2}
+for correlation, GTE and partial correlation on the \textcolor{red}{normal-?}
 dataset. The partial correlation outperforms other state-of-the-art methods
@@
 \citep{stetter2012model} generator could be reduced to a linear model after
-pre-processing. Those results is obviously generalized over the other
-datasets see Appendix \textcolor{red}{REF}.
+pre-processing. \textcolor{red}{Those results generalized over the other
+datasets see Appendix REF.}
 
-As it can also be seen on Figure \ref{fig:curves}, the GENIE3 performance
-increases with deeper trees. The reason is twofold. First, the deeper the
-tree, the larger is the conditioning. As it was observed in the comparison
-between correlation and partial correlation, it screens indirect links in the
-infered network. Second, the number of trees when trees are small need to be
-much higher in order to correctly estimate all pairs. However, as suggested by
-\cite{Gilles2014understanding}, limiting the maximal depth of trees may help
-to reduce the misestimation bias in variable importance comuting, i.e.
-infering the strengh of a link.
+\textcolor{red}{TODO: depth discussion }
 
@@
 \centering
-\includegraphics[width=\linewidth]{images/curves}
+\includegraphics[width=0.6\linewidth]{images/curves}
 \caption{Method precision-recall and roc curves. \textcolor{red}{GENI3?}
@@
 \centering
-\small
 \begin{tabular}{@{}l *{8}{c}@{}}

### 2014-06-19 article.tex
add depth discussion

--- 2014-06-19 article.tex
@@
 As it can also be seen on Figure \ref{fig:curves}, the GENIE3 performance
-increases with deeper trees. The reason is twofold. First, the deeper the
-tree, the larger is the conditioning. As it was observed in the comparison
-between correlation and partial correlation, it screens indirect links in the
-infered network. Second, the number of trees when trees are small need to be
-much higher in order to correctly estimate all pairs. However, as suggested by
-\cite{Gilles2014understanding}, limiting the maximal depth of trees may help
+increases with deeper trees in addition to be computionnally feasible. The
+reason is twofold. First, the deeper the tree, the larger is the conditioning.
+As it was observed in the comparison between correlation and partial
+correlation, it screens indirect links in the infered network. Second, the
+number of small trees need to be much higher than deep trees in order to
+observe - and evaluate - all pairs.  However, as suggested by
+\cite{louppe2014understanding}, limiting the maximal depth of trees may help
 to reduce the misestimation bias in variable importance comuting, i.e.
-infering the strengh of a link.
+infering the strengh of a link. Therefore a trade-off of the maximal depth may give the best of both worlds.
 

### 2014-06-19 article.tex
hard to distinguish methods on roc curves
inverse curve fig + concl

@@
 The area under the ROC curve is not consistent metric
-with respect to the problem statement. We advice to avoid the AUROC
+with respect to the problem statement. A clear hierachy is also difficult to derive based on ROC curve of Figure \ref{fig:curves}. We advice to avoid the AUROC
 for the assessment of network inference method. An alternative metric would
@@
 
-Obviously, we give a hint about limiting the depth of trees in the GENIE3
+In the discussion, we give hints about limiting the depth of trees in the GENIE3
 method to infer the network. It should be interesting to see if there is a
-optimum value for the maxmimal depth.
+optimum value for the maxmimal depth. And of course, it may also rewarding to increase considerably the number of trees to get more stable predictions.
 

### 2014-06-19 article.tex
fix notation
typo

@@
 of the Connectomics challenge : \textit{normal-1, normal-2, normal-3, normal-4}.
-Those datasets have $|V|=1000$ time series of length $T=179500$ of image
+Those datasets have $p=1000$ time series of length $T=179500$ of image
 calcium from simulated neuronal networks \citep{stetter2012model}. Those
@@
 score. The following parameters are used
-$10000$ trees, $\log_2{p}$ variables are randomly selected to split a tree
-node and the maximal tree depth is constrained to 1, 2 or 3.
+$10000$ trees, $\log_2{p}$ variables are randomly selected to split tree
+nodes and the maximal tree depth is constrained to 1, 2 or 3.
 \end{itemize}

### 2014-06-19 article.tex
Correlation statistics

--- 2014-06-19 article.tex
@@
 As the first plot in Figure~\ref{fig:filtered-signal} illustrates, the raw
-fluorescence signal is very noisy due to light scattering artifacts that
+fluoresence signal is very noisy due to light scattering artifacts that
 ordinarily affects the quality of the recording~\citep{lichtman2011big}.
-Accordingly, the first step of our pipeline is to smoothen the signal, using
-one the following low-pass filter for filtering out high frequency noise :
+Accordingly, the first step of our pipeline is to smoothen the signal, using a
+low-pass filter for filtering out high frequency noise and resulting in the
+second plot in the figure:
 \begin{align}
@@
 \end{align}
-where \textcolor{red}{$f_?$} effect is shown in the second plot in the figure.
+where $f_1$ is the filter proposed in the simplified variant of our approach
+and $f_2$ is the filter actually used within our winning algorithm.
 
@@
 
-In those terms, the full signal processing pipeline of our approach is defined
-by the composed function $w \cdot h \cdot g \cdot f_1$ (resp $f_2$).
+In those terms, the full signal processing pipeline of our (simplified)
+approach is defined by the composed function $w \cdot h \cdot g \cdot f_1$
+(resp. $f_2$ for the winning method).
 
@@
 
-Let us denote the fluorescence calcium indicators of all neuron
-as a set of random variables $X = \left\{X_1, \ldots, X_{|V|}\right\}$, which follows
-a joint probability distribution $p_\mathcal{X}$, and by
-$X^{-i,j}$ the set of all variables except $X_i$ and $X_j$.
-Two random variables $X_i$ and $X_j$ are said to be conditionally independent
-to a (possibly empty) set of random variables $Z$, denoted by $X_i \perp X_j | Z$,
-if the joint conditional probability distribution factorizes
-$p_{\mathcal{X}_i, \mathcal{X}_j|\mathcal{Z}} = p_{\mathcal{X}_i|\mathcal{Z}}
-p_{\mathcal{X}_j|\mathcal{Z}}$.  The inference of the undirected network
-can be formulated as inferring conditional dependences
-$X_i \not\perp X_j | X^{-i,j}$ between all pairs $i$ and $j$ of fluorescence
-signals.
+Let us model the fluorescence indicators of all $p$ neurons as a set of random
+variables $X = \{X_1, \dots, X_p\}$ following a joint probability distribution
+$P_X$. In the statistical framework, two random variables $X_i$ and $X_j$ are
+said to be conditionally independent to a (possibly empty) set of controlling
+random variables $Z$, denoted $X_i \perp X_j | Z$, if the joint conditional
+probability distribution $P_{X_i, X_j | Z}$ factorizes into $P_{X_i|Z}
+P_{X_j|Z}$. In particular, when $X_i$ and $X_j$ are conditionally independent
+with respect to all the other variables, denoted $X_i \perp X_j | X^{-i,j}$, then the
+observation of $X_i$ given the knowledge of $X^{-i,j}$ provides no information
+about $X_j$, and vice-versa. From a graphical point of view and assuming no
+hidden variable, this indicates that $X_i$ and $X_j$ do not directly interact
+(i.e., $(i,j) \notin E$). By opposition, if $X_i$ and $X_j$ are conditionally
+dependent with respect to all other variables, denoted $X_i \not\perp X_j |
+X^{-i,j}$, then the observation of one of the two variables provides some
+information about the other, therefore highlighting a direct interaction
+between the two random variables (i.e., $(i, j) \in E$).
 
-Since all neurons are assumed to form a connected graph, we
-have by construction $X_i \not\perp X_j$. However, two random variables $A$ and $B$ might be
-dependent taken alone ($A \not\perp B$), but not once we observe the set  $C$
-of all other variables ($A \perp B | C$). The conditioning over all other
-random variables $X^{-i,j}$ is thus necessary to avoid predicting an edge when
-two neurons are not directly connected.
+Under that assumption that random variables follow a joint Gaussian
+distribution $\mathcal{N}(\mu; \Sigma)$ of mean vector $\mu$ and covariance
+matrix $\Sigma$, $X_i$ and $X_j$ are conditionnally independent with respect to
+the other variables $X^{-i,j}$ if their \textit{partial correlation} statistic
+is null~\citep{koller2009probabilistic}, i.e., if
+\begin{equation}
+\rho_{X_i, X_j | X^{-i,j}} = -\frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii} \Sigma^{-1}_{jj}}} = 0.
+\end{equation}
+Conversely, $X_i$ and $X_j$ are conditionally dependent if $\rho_{X_i, X_j | X^{-i,j}} \neq 0$,
+where $\rho_{X_i, X_j | X^{-i,j}}$ can now be interpreted as the degree of association
+between the two variables (i.e., the larger the value, the stronger the interaction).
+Together, the partial correlation statistics correspond to the inverse
+$\Sigma^{-1}$ of the covariance matrix, also known as the concentration of
+precision matrix. Computationnally, they can be estimated efficiently in
+$O(M^3)$ (instead of $O(p^3)$) from the $M$ first principal components
+extracted through PCA~\citep{bishop2006pattern} on the processed data. In our experiments, $M$ is set
+to $0.8 p$, thereby allowing us to further filter noise in the data.
 
-If the random variables $X$ follows a joint Gaussian distribution
-$p_\mathcal{X} \sim \mathcal{N}(\mu; \Sigma)$ of mean vector $\mu$ and
-covariance matrix $\Sigma$, we have the conditional independence
-$X_i \perp X_j | X^{-i,j}$ if the partial correlation coefficient
-\[
-\rho_{X_i, X_j | X^{-i,j}}
-= \frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii} \Sigma^{-1}_{jj}}}
-\]
-is equal to zero \citep{koller2009probabilistic}. The partial correlation gives
-an estimate of the degree of association between all
-pairs of neuron $i$ and $j$.
-Similarly, we also have $X_i \perp X_j$ if the Pearson correlation
-coefficient
-\[
-\rho_{X_i,X_j} = \frac{\Sigma_{ij}}{\sqrt{\Sigma_{ii}
-\Sigma_{jj}}}
-\]
-is equal to zero.
+To highlight the benefits of measuring the partial dependence conditional to
+all other variables, we compare in Section~\ref{sec:results} with
+\textit{Pearson correlation} statistics, which measure instead the linear dependence
+between variables, independently of the others. Accordingly, $X_i$ and $X_j$ are
+independent if their Pearson correlation statistic is zero, that is if
+\begin{equation}
+\rho_{X_i,X_j} = \frac{\Sigma_{ij}}{\sqrt{\Sigma_{ii} \Sigma_{jj}}} = 0.
+\end{equation}
 
-% Speak about why averaging
-The quality of the signal filtering and network inference depends on
-good hyper-parameter selection, which are themselves dependent on the properties
-of the targeted network and measurement conditions, e.g. signal to noise ratio.
-In order to improve robustness, a weighted average of partial correlation
-matrices was estimated from the time series by varying the hard-threshold value
-$\tau$ and the design of the low-pass filter (mentionned in section
-\ref{sec:filter} and appendix \ref{app:optimized}).
-
-To filter even more noise before computing the partial correlation, we kept
-$80\%$ of the eigen vectors which have the largest eigen
-value (\cite{tipping1999mixtures}). In the context of the challenge, this
-assumption was deduced from ground truth of provided networks.
+Finally, let us remark that performance shows to be quite sensitive the choice
+of hyper-parameters in our signal processing pipeline (e.g., $f_1$ or $f_2$ or
+the value of the threshold $\tau$). To further improve robustness, the last
+step of our method therefore consists in averaging correlation statistics over
+various values of the parameters, thereby reducing the variance of our
+predictions. Further details are provided in Appendix~\ref{app:optimized}.
 
 \section{Empirical experiments} \label{sec:results}
+
+%\textcolor{red}{SEUIL 0.11 for tabulars!!!}
+
+% In this section, we will first describe datasets and methods used for the
+% comparison. Then, on Table \ref{tab:tab3}, our approach is decomposed to show
+% the contribution of each pre-processing steps. Afterwards, we will perform a comparison
+% between several methods on Figure \ref{fig:curves} and Table \ref{tab:tab1}. Note that two
+% metrics are used to evaluate the performance and a single low-pass filter is
+% used (Eq. \ref{eq:symetric-median}) and a threshold, i.e. $\tau = 0.11$. The end
+% of this section is devoted to a discussion about the choice of metric and its
+% relevance for the challenge.
+
+% \subsection{Assessment methodology}
 
@@
 
-\subsection*{Partial correlation improves over state-of-the-art methods}
+\subsection*{Comparison with state-of-the art methods}
 
 Figure \ref{fig:curves} shows the ROC curve and precision-recall curve
-for correlation, GTE and partial correlation on the \textit{normal-2}
+for correlation, GTE and partial correlation on the \textcolor{red}{normal-?}
 dataset. The partial correlation outperforms other state-of-the-art methods
-by at least factor of 2 in AUPRC reaching $0.347$ and an increased of $0.05$ in
-AUROC.
+by at least factor of 2 in AUPRC and an increased of $5\%$ in AUROC. There
+are two reasons that explains such overwhelming difference: (i) among
+those methods only the partial correlation make the distinction between
+direct and indirect connection, (ii) the simulated network from the
+\citep{stetter2012model} generator could be reduced to a linear model after
+pre-processing.
 
-Two reasons might explain such overwhelming difference: (i) among
-those methods only the partial correlation makes the distinction between
-direct and indirect connections, (ii) the simulated network from the
-\citep{stetter2012model} generator could be reduced to a linear model after
-pre-processing. Those results is obviously generalized over the other
-datasets see Appendix \textcolor{red}{REF}.
+\begin{figure}[bth]
+\centering
+\includegraphics[width=0.6\linewidth]{images/curves}
+\caption{Method precision-recall and roc curves. \textcolor{red}{GENI3?}}
+\label{fig:curves}
+\end{figure}
 
-As it can also be seen on Figure \ref{fig:curves}, the GENIE3 performance
-increases with deeper trees in addition to be computionnally feasible. The
-reason is twofold. First, the deeper the tree, the larger is the conditioning.
-As it was observed in the comparison between correlation and partial
-correlation, it screens indirect links in the infered network. Second, the
-number of small trees need to be much higher than deep trees in order to
-observe - and evaluate - all pairs.  However, as suggested by
-\cite{louppe2014understanding}, limiting the maximal depth of trees may help
-to reduce the misestimation bias in variable importance comuting, i.e.
-infering the strengh of a link. Therefore a trade-off of the maximal depth may give the best of both worlds.
+Observing Table \ref{tab:tab1}, it appears that best methods only infer the
+\textbf{undirected} network by giving the same weights to both edges $(i,j)$
+and $(j,i)$. This is quite surprising considering the goal of the challenge,
+namely predicted directed connections between neurons. Besides, if the true
+network undirected, i.e. for all links $(i,j)$, back links are added, is the
+infered network then the score obtained according to the ROC AUC metric is
+very high ($\approx 0.9956$ on \textit{normal-1}). Therefore, an undirected
+infered network seems sufficient to maximize the ROC AUC score without trying
+to identify the link direction. Indeed, predicting perfectly directivity only
+yields a small gain ($\approx 0.005$ on \textit{normal-1}) which is is not
+very rewarding. In contrast, the same experiment with the precision recall
+metric rewards less the undirected network ($\approx 0.789$ on
+\textit{normal-1}) and the gain margin in predicting the link directivity is
+large enough to be interesting ($\approx 0.211$ on \textit{normal-1}). For
+these reason, it seems that the metric used in the contest, i.e. the ROC AUC,
+does not seem consistent with the goal of predicting directed connections
+between neurons. Another metric, such as the AUC PRC, is maybe more
+appropriate to assess the quality of the \textbf{directed} infered network.
+
+Interestingly, an easy way to improve results for asymmetric methods (see
+Tab.\ref{tab:tab2}), namely GTE and GENIE3, is to make undirected the infered
+network. It proves once again that trying to detect the link direction is more
+penalizing than rewarding.
+
+% TODO
+%   - discussions about the results
+%   - discussions about the metrics (Gilles' text)
+
+% Dummy classifier?
+
+% GTE : Explaning the method (default parameters!)
+
+% Explaining the method (thèse de Gilles)
+
+% Directivity : ?
 
@@
 % see appendix for a full description of the method
+% Avg.: Averaging over the threholds and L-P filters improves a lot both metrics.
 
-\begin{figure}[bth]
+% Partial correlation : Obvious improvements (both metric) because of the conditioning
+% Correlation : Already give good results
+
+% Averaging
+
+%% Depth -- Gilles chapitre 7
+% Genie3 : better in auprc while worse in auroc than GTE. Why?
+% Genie3 : "Conditioning" better and better but need a lot of trees
+
+\textcolor{red}{TODO: depth discussion }
+
+% Discussion about the metrics
+
+\begin{table}
+\small
 \centering
-\includegraphics[width=\linewidth]{images/curves}
-\caption{Method precision-recall and roc curves. \textcolor{red}{GENI3?}
-         $\tau=0.11$}
-\label{fig:curves}
-\end{figure}
+\begin{tabular}{@{}l *{8}{c}@{}}
+  & \multicolumn{4}{c}{AUROC} & \multicolumn{4}{c}{AUPRC} \\
+\hline \hline
+Methods $\backslash$ normal- & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 \\
+\hline \hline
+% Directivity \textcolor{red}{appendix?} & 0.535 & 0.526 & 0.533 & 0.535 & 0.012 & 0.012 & 0.012 & 0.012 \\
+Correlation            & 0.886 & 0.884 & 0.891 & 0.877 & 0.153 & 0.145 & 0.170 & 0.132 \\
+GENIE3 (depth = 1)     & 0.878 & & & & 0.184 & & & \\
+GENIE3 (depth = 2)     & 0.889 & & & & 0.217 & & & \\
+GENIE3 (depth = 3)     & & & & & & & & \\
+GTE                    & 0.890 & 0.893 & 0.894 & 0.873 & 0.171 & 0.174 & 0.197 & 0.142 \\
+Partial correlation    & 0.930 &  0.927 &  0.926 &  0.923& 0.363  & 0.347 &  0.346 & 0.328 \\
+Partial correlation (avg.) & 0.938 & 0.936 & 0.936 & 0.932& 0.391 & 0.389 & 0.385 & 0.374\\
+% Our approach simple + dir & 0.939 & 0.936 & 0.937 & 0.933& 0.392 & 0.390 & 0.386 & 0.375\\
+Partial correlation (opt.) & 0.932 & 0.931 & 0.930 & 0.928 & 0.364 & 0.366 & 0.359 & 0.344 \\
+Our approach (opt. \& avg.)    & 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388 \\
+% Our approach + dir  \textcolor{red}{appendix?}   & 0.944 & 0.943 & 0.942 & 0.940 & 0.404 & 0.405 & 0.399 & 0.389 \\
+\end{tabular}
+\caption{TODO}
+\label{tab:tab1}
+\end{table}
 
@@
 
-\textcolor{red}{The whole sub-section should be moved to the appendix and
-                replace by one or two sentences.}
-
 On Table \ref{tab:tab3}, it can be seen that each step of our approach globally
@@
 It also appears that the averaging over the low-pass filter designs and the
-threshold values increases significantly the quality of the inferred network
+threshold values increases significantly the quality of the infered network
 according to both metrics.
-
-% Explaining the method (thèse de Gilles)
-% Avg.: Averaging over the threholds and L-P filters improves a lot both metrics.
-% Averaging
-
-%% Depth -- Gilles chapitre 7
-% Genie3 : better in auprc while worse in auroc than GTE. Why?
-% Genie3 : "Conditioning" better and better but need a lot of trees
 
@@
 \end{table}
-
-\subsection*{Area under the ROC curve is a poor metric for network inference}
-
-The best method only infers the \textbf{undirected} network by giving the
-same connectivity score to both edges $(i,j)$ and $(j,i)$. This is quite
-surprising considering the problem statement.
-
-If the undirected network is perfectly inferred, it would already yield
-high AUROC score for instance $\approx{}0.996$ on \textit{normal-1}. Trying
-to infer edge directivity is likely to be counter-productive or yield
-small gain.
-By contrast, the same experiment with AUPRC would yield
-to a score of $\approx 0.789$ on \textit{normal-1}. Thus inferring
-correctly directivity would be more rewarding in AUPRC term.
-Interestingly, methods that takes into account directivity, namely GTE and
-GENIE3, improve their AUROC and AUPRC by giving the same way to directed edges.
-Trying to detect the link direction is more penalizing than rewarding.
-
-The area under the ROC curve is not consistent metric
-with respect to the problem statement. We advice to avoid the AUROC
-for the assessment of network inference method. An alternative metric would
-be the area under the precision-recall curve (AUPRC). Those
-conclusions are in line with \cite{schrynemackers2013protocols}.
 
@@
 % used.
-
-\section{Extended results}
-
-\begin{table}
-\small
-\centering
-\begin{tabular}{@{}l *{8}{c}@{}}
-  & \multicolumn{4}{c}{AUROC} & \multicolumn{4}{c}{AUPRC} \\
-\hline \hline
-Methods $\backslash$ normal- & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 \\
-\hline \hline
-% Directivity \textcolor{red}{appendix?} & 0.535 & 0.526 & 0.533 & 0.535 & 0.012 & 0.012 & 0.012 & 0.012 \\
-Correlation            & 0.886 & 0.884 & 0.891 & 0.877 & 0.153 & 0.145 & 0.170 & 0.132 \\
-GENIE3 (depth = 1)     & 0.878 & & & & 0.184 & & & \\
-GENIE3 (depth = 2)     & 0.889 & & & & 0.217 & & & \\
-GENIE3 (depth = 3)     & & & & & & & & \\
-GTE                    & 0.890 & 0.893 & 0.894 & 0.873 & 0.171 & 0.174 & 0.197 & 0.142 \\
-Partial correlation    & 0.930 &  0.927 &  0.926 &  0.923& 0.363  & 0.347 &  0.346 & 0.328 \\
-Partial correlation (avg.) & 0.938 & 0.936 & 0.936 & 0.932& 0.391 & 0.389 & 0.385 & 0.374\\
-% Our approach simple + dir & 0.939 & 0.936 & 0.937 & 0.933& 0.392 & 0.390 & 0.386 & 0.375\\
-Partial correlation (opt.) & 0.932 & 0.931 & 0.930 & 0.928 & 0.364 & 0.366 & 0.359 & 0.344 \\
-Our approach (opt. \& avg.)    & 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388 \\
-% Our approach + dir  \textcolor{red}{appendix?}   & 0.944 & 0.943 & 0.942 & 0.940 & 0.404 & 0.405 & 0.399 & 0.389 \\
-\end{tabular}
-\caption{TODO}
-\label{tab:tab1}
-\end{table}
 

### 2014-06-19 article.tex

--- 2014-06-19 article.tex
@@
 
-Let us denote the fluorescence calcium indicators of all neuron
-as a set of random variables $X = \left\{X_1, \ldots, X_{|V|}\right\}$, which follows
-a joint probability distribution $p_\mathcal{X}$, and by
-$X^{-i,j}$ the set of all variables except $X_i$ and $X_j$.
-Two random variables $X_i$ and $X_j$ are said to be conditionally independent
-to a (possibly empty) set of random variables $Z$, denoted by $X_i \perp X_j | Z$,
-if the joint conditional probability distribution factorizes
-$p_{\mathcal{X}_i, \mathcal{X}_j|\mathcal{Z}} = p_{\mathcal{X}_i|\mathcal{Z}}
-p_{\mathcal{X}_j|\mathcal{Z}}$.  The inference of the undirected network
-can be formulated as inferring conditional dependences
-$X_i \not\perp X_j | X^{-i,j}$ between all pairs $i$ and $j$ of fluorescence
-signals.
+Let us model the fluorescence indicators of all $p$ neurons as a set of random
+variables $X = \{X_1, \dots, X_p\}$ following a joint probability distribution
+$P_X$. In the statistical framework, two random variables $X_i$ and $X_j$ are
+said to be conditionally independent to a (possibly empty) set of controlling
+random variables $Z$, denoted $X_i \perp X_j | Z$, if the joint conditional
+probability distribution $P_{X_i, X_j | Z}$ factorizes into $P_{X_i|Z}
+P_{X_j|Z}$. In particular, when $X_i$ and $X_j$ are conditionally independent
+with respect to all the other variables, denoted $X_i \perp X_j | X^{-i,j}$, then the
+observation of $X_i$ given the knowledge of $X^{-i,j}$ provides no information
+about $X_j$, and vice-versa. From a graphical point of view and assuming no
+hidden variable, this indicates that $X_i$ and $X_j$ do not directly interact
+(i.e., $(i,j) \notin E$). By opposition, if $X_i$ and $X_j$ are conditionally
+dependent with respect to all other variables, denoted $X_i \not\perp X_j |
+X^{-i,j}$, then the observation of one of the two variables provides some
+information about the other, therefore highlighting a direct interaction
+between the two random variables (i.e., $(i, j) \in E$).
 
-Since all neurons are assumed to form a connected graph, we
-have by construction $X_i \not\perp X_j$. However, two random variables $A$ and $B$ might be
-dependent taken alone ($A \not\perp B$), but not once we observe the set  $C$
-of all other variables ($A \perp B | C$). The conditioning over all other
-random variables $X^{-i,j}$ is thus necessary to avoid predicting an edge when
-two neurons are not directly connected.
+Under that assumption that random variables follow a joint Gaussian
+distribution $\mathcal{N}(\mu; \Sigma)$ of mean vector $\mu$ and covariance
+matrix $\Sigma$, $X_i$ and $X_j$ are conditionnally independent with respect to
+the other variables $X^{-i,j}$ if their \textit{partial correlation} statistic
+is null~\citep{koller2009probabilistic}, i.e., if
+\begin{equation}
+\rho_{X_i, X_j | X^{-i,j}} = -\frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii} \Sigma^{-1}_{jj}}} = 0.
+\end{equation}
+Conversely, $X_i$ and $X_j$ are conditionally dependent if $\rho_{X_i, X_j | X^{-i,j}} \neq 0$,
+where $\rho_{X_i, X_j | X^{-i,j}}$ can now be interpreted as the degree of association
+between the two variables (i.e., the larger the value, the stronger the interaction).
+Together, the partial correlation statistics correspond to the inverse
+$\Sigma^{-1}$ of the covariance matrix, also known as the concentration of
+precision matrix. Computationnally, they can be estimated efficiently in
+$O(M^3)$ (instead of $O(p^3)$) from the $M$ first principal components
+extracted through PCA~\citep{bishop2006pattern} on the processed data. In our experiments, $M$ is set
+to $0.8 p$, thereby allowing us to further filter noise in the data.
 
-If the random variables $X$ follows a joint Gaussian distribution
-$p_\mathcal{X} \sim \mathcal{N}(\mu; \Sigma)$ of mean vector $\mu$ and
-covariance matrix $\Sigma$, we have the conditional independence
-$X_i \perp X_j | X^{-i,j}$ if the partial correlation coefficient
-\[
-\rho_{X_i, X_j | X^{-i,j}}
-= \frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii} \Sigma^{-1}_{jj}}}
-\]
-is equal to zero \citep{koller2009probabilistic}. The partial correlation gives
-an estimate of the degree of association between all
-pairs of neuron $i$ and $j$.
-Similarly, we also have $X_i \perp X_j$ if the Pearson correlation
-coefficient
-\[
-\rho_{X_i,X_j} = \frac{\Sigma_{ij}}{\sqrt{\Sigma_{ii}
-\Sigma_{jj}}}
-\]
-is equal to zero.
+To highlight the benefits of measuring the partial dependence conditional to
+all other variables, we compare in Section~\ref{sec:results} with
+\textit{Pearson correlation} statistics, which measure instead the linear dependence
+between variables, independently of the others. Accordingly, $X_i$ and $X_j$ are
+independent if their Pearson correlation statistic is zero, that is if
+\begin{equation}
+\rho_{X_i,X_j} = \frac{\Sigma_{ij}}{\sqrt{\Sigma_{ii} \Sigma_{jj}}} = 0.
+\end{equation}
 
-% Speak about why averaging
-The quality of the signal filtering and network inference depends on
-good hyper-parameter selection, which are themselves dependent on the properties
-of the targeted network and measurement conditions, e.g. signal to noise ratio.
-In order to improve robustness, a weighted average of partial correlation
-matrices was estimated from the time series by varying the hard-threshold value
-$\tau$ and the design of the low-pass filter (mentionned in section
-\ref{sec:filter} and appendix \ref{app:optimized}).
-
-To filter even more noise before computing the partial correlation, we kept
-$80\%$ of the eigen vectors which have the largest eigen
-value (\cite{tipping1999mixtures}). In the context of the challenge, this
-assumption was deduced from ground truth of provided networks.
+Finally, let us remark that performance shows to be quite sensitive the choice
+of hyper-parameters in our signal processing pipeline (e.g., $f_1$ or $f_2$ or
+the value of the threshold $\tau$). To further improve robustness, the last
+step of our method therefore consists in averaging correlation statistics over
+various values of the parameters, thereby reducing the variance of our
+predictions. Further details are provided in Appendix~\ref{app:optimized}.
 

### 2014-06-19 article.tex
typos

@@
 technically feasible. Without being perfect, calcium imaging currently allows
-the realtime and simultaneous observation of neuron activities from thousands
-of neurons, producing individual time series representing their fluoresence
+the real-time and simultaneous observation of neuron activities from thousands
+of neurons, producing individual time series representing their fluorescence
 intensity. From these data, the connectome inference problem consists in
 retrieving the synaptic connections between neurons on the basis of the
-fluoresence time series. In particular, this problem is often made difficult
+fluorescence time series. In particular, this problem is often made difficult
 because of experimental issues, including masking effects (making some of the
@@
 the optical device with respect to the neural activity speed or the slow decay
-of fluoresence.
+of fluorescence.
 
@@
 Section \ref{sec:conclusion} finally discusses our work and provides further
-research directions. Additionnaly, Appendix \ref{app:optimized} further
+research directions. Additionally, Appendix \ref{app:optimized} further
 describes, in all details, our actual winning method, giving slightly better
@@
 inactivity, the first part of our algorithm consists in cleaning the raw
-fluoresence data. More specifically, time series are processed using standard
+fluorescence data. More specifically, time series are processed using standard
 signal processing filters in order to remove noise due light scattering
@@
 distribution $\mathcal{N}(\mu; \Sigma)$ of mean vector $\mu$ and covariance
-matrix $\Sigma$, $X_i$ and $X_j$ are conditionnally independent with respect to
+matrix $\Sigma$, $X_i$ and $X_j$ are conditionally independent with respect to
 the other variables $X^{-i,j}$ if their \textit{partial correlation} statistic
@@
 $\Sigma^{-1}$ of the covariance matrix, also known as the concentration of
-precision matrix. Computationnally, they can be estimated efficiently in
+precision matrix. Computationally, they can be estimated efficiently in
 $O(M^3)$ (instead of $O(p^3)$) from the $M$ first principal components
@@
 As it can also be seen on Figure \ref{fig:curves}, the GENIE3 performance
-increases with deeper trees in addition to be computionnally feasible. The
+increases with deeper trees in addition to be computationally feasible. The
 reason is twofold. First, the deeper the tree, the larger is the conditioning.
 As it was observed in the comparison between correlation and partial
-correlation, it screens indirect links in the infered network. Second, the
+correlation, it screens indirect links in the inferred network. Second, the
 number of small trees need to be much higher than deep trees in order to
@@
 \cite{louppe2014understanding}, limiting the maximal depth of trees may help
-to reduce the misestimation bias in variable importance comuting, i.e.
-infering the strengh of a link. Therefore a trade-off of the maximal depth may give the best of both worlds.
+to reduce the misestimation bias in variable importance computing, i.e.
+inferring the strength of a link. Therefore a trade-off of the maximal depth may give the best of both worlds.
 
@@
 \includegraphics[width=\linewidth]{images/curves}
-\caption{Method precision-recall and roc curves. \textcolor{red}{GENI3?}
+\caption{Method precision-recall and ROC curves. \textcolor{red}{GENI3?}
          $\tau=0.11$}
@@
 The area under the ROC curve is not consistent metric
-with respect to the problem statement. A clear hierachy is also difficult to derive based on ROC curve of Figure \ref{fig:curves}. We advice to avoid the AUROC
+with respect to the problem statement. A clear hierarchy is also difficult to derive based on ROC curve of Figure \ref{fig:curves}. We advice to avoid the AUROC
 for the assessment of network inference method. An alternative metric would
@@
 In this paper, we present the winning method of the Connectomics challenge.
-This approach is simple and theorically grounded. We also evaluate the method
+This approach is simple and theoretically grounded. We also evaluate the method
 in a more detailed way and perform a comparison with other inference methods.
@@
 method to infer the network. It should be interesting to see if there is a
-optimum value for the maxmimal depth. And of course, it may also rewarding to increase considerably the number of trees to get more stable predictions.
+optimum value for the maximal depth. And of course, it may also rewarding to increase considerably the number of trees to get more stable predictions.
 
@@
 variables. Instead of considering only the highest order, it may be useful to
-study with accuracy the infered network at all orders. In this case, it may not
-be very relevant but interesting in case of dymanical networks.
+study with accuracy the inferred network at all orders. In this case, it may not
+be very relevant but interesting in case of dynamical networks.
 
-As we mentionned, in order to maximize the ROC AUC, it was not necessary to
+As we mentioned, in order to maximize the ROC AUC, it was not necessary to
 discover causal relationships. It may be, in future works, promising to focus
@@
 
-\section*{Acknowledgements}
+\section*{Acknowledgments}
 A. Joly and G. Louppe are research fellows of

### 2014-06-19 article.tex
Update article.tex

@@
 Together, the partial correlation statistics correspond to the inverse
-$\Sigma^{-1}$ of the covariance matrix, also known as the concentration of
+$\Sigma^{-1}$ of the covariance matrix, also known as the concentration or
 precision matrix. Computationally, they can be estimated efficiently in

### 2014-06-19 article.tex
Update article.tex
shorter title
say that we focus on normal-1

@@
 
-\section{Empirical experiments} \label{sec:results}
+\textcolor{red}{G: Mention that correlation statistics are symmetric and do not account for direction.}
+
+\section{Experiments} \label{sec:results}
 
 % Datasets
-To assess our method, we have used four datasets provided by the organizers
-of the Connectomics challenge : \textit{normal-1, normal-2, normal-3, normal-4}.
+To assess our method, we focus on the \textit{normal-1} dataset
+provided by the organizers of the Connectomics challenge. Experiments
+were also carried out on  \textit{normal-2, normal-3, normal-4} and show
+similar trends.
 Those datasets have $p=1000$ time series of length $T=179500$ of image

### 2014-06-19 article.tex
precisie preprocessing
use subfigure

@@
 whenever the average fluorescence is over a conditioning level.
-Conditioning level was set to reproduce baseline of the challenge.
-\textcolor{red}{Talk about pre-processing}
+Pre-processing and conditioning level were set to reproduce baseline of the
+challenge.
 
@@
 \centering
-\includegraphics[width=\linewidth]{images/curves}
+\subfigure[]{\includegraphics[width=0.45\textwidth]{images/curve_roc} \label{fig:roc_curve}}
+\subfigure[]{\includegraphics[width=0.45\textwidth]{images/curve_pr} \label{fig:pr_curve}}
 \caption{Method precision-recall and ROC curves. \textcolor{red}{GENI3?}

### 2014-06-19 article.tex
update experimental sction

@@
 \end{align}
-where \textcolor{red}{$f_?$} effect is shown in the second plot in the figure.
+where $f_1$x effect is shown in the second plot in the figure.
 
@@
 % Datasets
-To assess our method, we focus on the \textit{normal-1} dataset
+To assess our method, we focus on the \textit{normal-2} dataset
 provided by the organizers of the Connectomics challenge. Experiments
-were also carried out on  \textit{normal-2, normal-3, normal-4} and show
-similar trends.
+on \textit{normal-1, normal-3, normal-4} show similar trends to
+\textit{normal-2} and are presented in the Appendix \textcolor{red}{REF}.
 Those datasets have $p=1000$ time series of length $T=179500$ of image
@@
 
-Two reasons might explain such overwhelming difference: (i) among
+\begin{figure}[bth]
+\centering
+\subfigure[]{\includegraphics[width=0.45\textwidth]{images/curve_roc} \label{fig:roc_curve}}
+\subfigure[]{\includegraphics[width=0.45\textwidth]{images/curve_pr} \label{fig:pr_curve}}
+\caption{The weighted average of partial correlation matrix, winning approach
+         of the challenge, yields better than AUROC and AUPRC than all
+         other state-of-the-art methods. (parameters: $\tau=0.11$, partial
+         correlation used filer $f_1$).}
+\label{fig:curves}
+\end{figure}
+
+Two reasons might explain such differences: (i) among
 those methods only the partial correlation makes the distinction between
@@
 
+\textcolor{red}{AJ: GENI3 is not on the figure}
 As it can also be seen on Figure \ref{fig:curves}, the GENIE3 performance
@@
 to reduce the misestimation bias in variable importance computing, i.e.
-inferring the strength of a link. Therefore a trade-off of the maximal depth may give the best of both worlds.
+inferring the strength of a link. Therefore a trade-off of the maximal depth
+may give the best of both worlds.
 
@@
 % see appendix for a full description of the method
-
-\begin{figure}[bth]
-\centering
-\subfigure[]{\includegraphics[width=0.45\textwidth]{images/curve_roc} \label{fig:roc_curve}}
-\subfigure[]{\includegraphics[width=0.45\textwidth]{images/curve_pr} \label{fig:pr_curve}}
-\caption{Method precision-recall and ROC curves. \textcolor{red}{GENI3?}
-         $\tau=0.11$}
-\label{fig:curves}
-\end{figure}
 
@@
 
-\subsection*{Signal processing highly improves performance}
-
-\textcolor{red}{The whole sub-section should be moved to the appendix and
-                replace by one or two sentences.}
-
-On Table \ref{tab:tab3}, it can be seen that each step of our approach globally
-improves the score on both metrics. However, processing, weights and averaging
-(respectively denoted as $P$,$W$ and $Averaging$ in Tab.\ref{tab:tab3}) as
-described in Section \ref{sec:filter} are the key steps of our algorithm.
-
-It also appears that the averaging over the low-pass filter designs and the
-threshold values increases significantly the quality of the inferred network
-according to both metrics.
-
-% Explaining the method (thèse de Gilles)
-% Avg.: Averaging over the threholds and L-P filters improves a lot both metrics.
-% Averaging
-
-%% Depth -- Gilles chapitre 7
-% Genie3 : better in auprc while worse in auroc than GTE. Why?
-% Genie3 : "Conditioning" better and better but need a lot of trees
-
-\begin{table}[tbh]
-\centering
-\small
-\begin{tabular}{@{}l *{8}{c}@{}}
-\hline
-  & \multicolumn{4}{c}{AUROC} & \multicolumn{4}{c}{AUPRC} \\
-\hline
-Methods $\backslash$ normal- & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 \\
-No  filtering       & 0.777 & 0.767 & 0.772 & 0.774 & 0.070 & 0.064 & 0.068 & 0.072\\
-P                   & 0.925 & 0.925 & 0.924 & 0.923 & 0.322 & 0.324 & 0.323 & 0.312\\
-P + W               & 0.931 & 0.930 & 0.928 & 0.927 & 0.333 & 0.334 & 0.327 & 0.313\\
-P + W + PCA         & 0.932 & 0.931 & 0.930 & 0.928 & 0.364 & 0.366 & 0.359 & 0.344\\
-Averaging           & 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388\\
-%Averaging + Directivity & 0.944 & 0.943 & 0.942 & 0.940 & 0.404 & 0.405 & 0.399 & 0.389\\
-\end{tabular}
-\caption{TODO \textcolor{red}{version simple!!}}
-\label{tab:tab3}
-\end{table}
-
 \subsection*{Area under the ROC curve is a poor metric for network inference}
@@
 The area under the ROC curve is not consistent metric
-with respect to the problem statement. A clear hierarchy is also difficult to derive based on ROC curve of Figure \ref{fig:curves}. We advice to avoid the AUROC
+with respect to the problem statement. A clear hierarchy is also difficult to
+derive based on ROC curve of Figure \ref{fig:curves}. We advice to avoid the AUROC
 for the assessment of network inference method. An alternative metric would
@@
 
+\section{Signal processing highly improves performance}
+
+On Table \ref{tab:tab3}, it can be seen that each step of our approach globally
+improves the score on both metrics. However, processing, weights and averaging
+(respectively denoted as $P$,$W$ and $Averaging$ in Tab.\ref{tab:tab3}) as
+described in Section \ref{sec:filter} are the key steps of our algorithm.
+
+It also appears that the averaging over the low-pass filter designs and the
+threshold values increases significantly the quality of the inferred network
+according to both metrics.
+
+% Explaining the method (thèse de Gilles)
+% Avg.: Averaging over the threholds and L-P filters improves a lot both metrics.
+% Averaging
+
+%% Depth -- Gilles chapitre 7
+% Genie3 : better in auprc while worse in auroc than GTE. Why?
+% Genie3 : "Conditioning" better and better but need a lot of trees
+
+\begin{table}[tbh]
+\centering
+\small
+\begin{tabular}{@{}l *{8}{c}@{}}
+\hline
+  & \multicolumn{4}{c}{AUROC} & \multicolumn{4}{c}{AUPRC} \\
+\hline
+Methods $\backslash$ normal- & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 \\
+No  filtering       & 0.777 & 0.767 & 0.772 & 0.774 & 0.070 & 0.064 & 0.068 & 0.072\\
+P                   & 0.925 & 0.925 & 0.924 & 0.923 & 0.322 & 0.324 & 0.323 & 0.312\\
+P + W               & 0.931 & 0.930 & 0.928 & 0.927 & 0.333 & 0.334 & 0.327 & 0.313\\
+P + W + PCA         & 0.932 & 0.931 & 0.930 & 0.928 & 0.364 & 0.366 & 0.359 & 0.344\\
+Averaging           & 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388\\
+%Averaging + Directivity & 0.944 & 0.943 & 0.942 & 0.940 & 0.404 & 0.405 & 0.399 & 0.389\\
+\end{tabular}
+\caption{TODO \textcolor{red}{version simple!!}}
+\label{tab:tab3}
+\end{table}
+
 %% Talk about filters future and past

### 2014-06-20 article.tex
add a note

@@
 
+\textcolor{red}{AJ: It's not clear on which datset we focus on}
+
 % Datasets
@@
 
+Two reasons might explain such differences: (i) among
+those methods only the partial correlation makes the distinction between
+direct and indirect connections, (ii) the simulated network from the
+\citep{stetter2012model} generator could be reduced to a linear model after
+pre-processing. Those results is obviously generalized over the other
+datasets see Appendix \textcolor{red}{REF}.
+
 \begin{figure}[bth]
@@
          of the challenge, yields better than AUROC and AUPRC than all
-         other state-of-the-art methods. (parameters: $\tau=0.11$, partial
-         correlation used filer $f_1$).}
+         other state-of-the-art methods. (parameters: $\tau=0.11$ except for
+         averaging method, partial correlation used filer $f_1$).}
 \label{fig:curves}
 \end{figure}
-
-Two reasons might explain such differences: (i) among
-those methods only the partial correlation makes the distinction between
-direct and indirect connections, (ii) the simulated network from the
-\citep{stetter2012model} generator could be reduced to a linear model after
-pre-processing. Those results is obviously generalized over the other
-datasets see Appendix \textcolor{red}{REF}.
 
@@
 
-\subsection*{Area under the ROC curve is a poor metric for network inference}
+\subsection*{Area under the ROC curve a poor metric for network inference}
 

### 2014-06-20 article.tex
wording

@@
 
-\textcolor{red}{AJ: It's not clear on which datset we focus on}
+\textcolor{red}{AJ: It's not clear on which dataset we focus on}
 
@@
 by at least factor of 2 in AUPRC reaching $0.347$ and an increased of $0.05$ in
-AUROC.
-
-Two reasons might explain such differences: (i) among
+AUROC. Two reasons might explain such differences: (i) among
 those methods only the partial correlation makes the distinction between
 direct and indirect connections, (ii) the simulated network from the
-\citep{stetter2012model} generator could be reduced to a linear model after
-pre-processing. Those results is obviously generalized over the other
-datasets see Appendix \textcolor{red}{REF}.
+\citep{stetter2012model} generator or the neural network in general could be
+reduced to a linear model after pre-processing. Those results is obviously
+generalized over the other datasets see Appendix \textcolor{red}{REF}.
+
+From the pre-processing to the weighted averaging of partial correlation
+matrix, all pre-processing and post-processing is useful to improve score
 
@@
 \centering
-\subfigure[]{\includegraphics[width=0.45\textwidth]{images/curve_roc} \label{fig:roc_curve}}
-\subfigure[]{\includegraphics[width=0.45\textwidth]{images/curve_pr} \label{fig:pr_curve}}
+\subfigure[ROC curves]{\includegraphics[width=0.45\textwidth]{images/curve_roc} \label{fig:roc_curve}}
+\subfigure[Precision-recall curves]{\includegraphics[width=0.45\textwidth]{images/curve_pr} \label{fig:pr_curve}}
 \caption{The weighted average of partial correlation matrix, winning approach
@@
          other state-of-the-art methods. (parameters: $\tau=0.11$ except for
-         averaging method, partial correlation used filer $f_1$).}
+         averaging method, partial correlation used filter $f_1$).}
 \label{fig:curves}
@@
 GENIE3, improve their AUROC and AUPRC by giving the same way to directed edges.
+(see GTE and GTE(undirected) in Figure \ref{fig:curves}
+\textcolor{red}{AJ: Figure \ref{fig:curves}  contradicts this message,
+especially pr-curve.}).
 Trying to detect the link direction is more penalizing than rewarding.

### 2014-06-20 article.tex
remove unfinish sentence
wording

@@
 
-From the pre-processing to the weighted averaging of partial correlation
-matrix, all pre-processing and post-processing is useful to improve score
-
 \begin{figure}[bth]
@@
          other state-of-the-art methods. (parameters: $\tau=0.11$ except for
-         averaging method, partial correlation used filter $f_1$).}
+         averaged partial correlation method, partial correlation used
+         filter $f_1$).}
 \label{fig:curves}

### 2014-06-20 article.tex
typos

--- 2014-06-20 article.tex
@@
 neuron spikes -- characterized by high frequencies -- by filtering out low
-frequencies through a high-pass filter, resulting in third plot of the figure:
+frequencies through a high-pass filter, resulting in the third plot of the figure:
 \begin{align} % an asymmetrical discrete derivative filter
@@
 
-Under that assumption that random variables follow a joint Gaussian
+Under the assumption that random variables follow a joint Gaussian
 distribution $\mathcal{N}(\mu; \Sigma)$ of mean vector $\mu$ and covariance
@@
 To highlight the benefits of measuring the partial dependence conditional to
-all other variables, we compare in Section~\ref{sec:results} with
+all other variables, we compare in Section~\ref{sec:results} with the
 \textit{Pearson correlation} statistics, which measure instead the linear dependence
@@
 
-Finally, let us remark that performance shows to be quite sensitive the choice
-of hyper-parameters in our signal processing pipeline (e.g., $f_1$ or $f_2$ or
+Finally, let us remark that performance shows to be quite sensitive to the choice
+of hyper-parameters in the signal processing pipeline (e.g., $f_1$ or $f_2$ or
 the value of the threshold $\tau$). To further improve robustness, the last

### 2014-06-20 article.tex

@@
 by at least factor of 2 in AUPRC reaching $0.347$ and an increased of $0.05$ in
-AUROC.
-
-Two reasons might explain such differences: (i) among
+AUROC. Two reasons might explain such differences: (i) among
 those methods only the partial correlation makes the distinction between
 direct and indirect connections, (ii) the simulated network from the
-\citep{stetter2012model} generator could be reduced to a linear model after
-pre-processing. Those results is obviously generalized over the other
-datasets see Appendix \textcolor{red}{REF}.
+\citep{stetter2012model} generator or the neural network in general could be
+reduced to a linear model after pre-processing. Those results is obviously
+generalized over the other datasets see Appendix \textcolor{red}{REF}.
 
@@
          other state-of-the-art methods. (parameters: $\tau=0.11$ except for
-         averaging method, partial correlation used filer $f_1$).}
+         averaged partial correlation method, partial correlation used
+         filter $f_1$).}
 \label{fig:curves}

### 2014-06-20 article.tex
small wording

@@
 Interestingly, methods that takes into account directivity, namely GTE and
-GENIE3, improve their AUROC and AUPRC by giving the same way to directed edges.
+GENIE3, slightly improve their AUROC and AUPRC by giving the same way to directed edges.
 (see GTE and GTE(undirected) in Figure \ref{fig:curves}

### 2014-06-20 article.tex
small wording

--- 2014-06-20 article.tex
@@
 GENIE3, improve their AUROC and AUPRC by giving the same way to directed edges.
-(see GTE and GTE(undirected) in Figure \ref{fig:curves}
+(see GTE and GTE(undirected) in particular Figure \ref{fig:pr_curve}
 \textcolor{red}{AJ: Figure \ref{fig:curves}  contradicts this message,
-especially pr-curve.}).
+especially pr-curve.} and Table \ref{tab:tab1} in Appendix \textcolor{red}{REF}).
 Trying to detect the link direction is more penalizing than rewarding.
@@
 
-In the discussion, we give hints about limiting the depth of trees in the GENIE3
-method to infer the network. It should be interesting to see if there is a
-optimum value for the maximal depth. And of course, it may also rewarding to increase considerably the number of trees to get more stable predictions.
+In the discussion, we give hints about limiting the depth of trees in the
+GENIE3 method to infer the network. It should be interesting to see if there
+is a optimum value for the maximal depth. And of course, it may also rewarding
+to increase considerably the number of trees to get more stable predictions.
 

### 2014-06-20 article.tex
small wording
blabla

--- 2014-06-20 article.tex
@@
 
-The human brain is a complex biological organ made of 100 billions of neurons,
+\textcolor{red}{To improve (style):} The human brain is a complex biological organ made of 100 billions of neurons,
 each connected to 7000 other neurons on average. Unfortunately, direct
@@
 between the two variables (i.e., the larger the value, the stronger the interaction).
+Note however that the partial correlation statistic is symmetric (i.e., $\rho_{X_i, X_j | X^{-i,j}} = \rho_{X_j, X_i | X^{-j,i}}$) and therefore does not account for the direction of the interaction.
 Together, the partial correlation statistics correspond to the inverse
@@
 various values of the parameters, thereby reducing the variance of our
-predictions. Further details are provided in Appendix~\ref{app:optimized}.
-
-\textcolor{red}{G: Mention that correlation statistics are symmetric and do not account for direction.}
+predictions. In this case, the method is referred to as \textit{Averaged Partial correlation} statistics. Further details are provided in Appendix~\ref{app:optimized}.
 
 \section{Experiments} \label{sec:results}
-
-\textcolor{red}{AJ: It's not clear on which dataset we focus on}
 
@@
 of all other neurons using a tree based ensemble such as
-random forest \citep{breiman2001random}. The tree ensemble associate a
-variable importance scores \citep{louppe2013understanding}
-to each neuron used in the predictions, which is used as a connectivity
-score. The following parameters are used
+random forest \citep{breiman2001random}. The tree ensemble associates a
+variable importance score \citep{louppe2013understanding}
+to each neuron used in the predictions, which is used as a degree of associate. The following parameters are used
 $10000$ trees, $\log_2{p}$ variables are randomly selected to split tree
@@
 GENIE3, improve their AUROC and AUPRC by giving the same way to directed edges.
-(see GTE and GTE(undirected) in Figure \ref{fig:curves}
+(in particular see GTE and GTE(undirected) in Figure \ref{fig:pr_curve}
 \textcolor{red}{AJ: Figure \ref{fig:curves}  contradicts this message,
-especially pr-curve.}).
+especially pr-curve. AS:And now?} and Table \ref{tab:tab1} in Appendix \textcolor{red}{REF}).
 Trying to detect the link direction is more penalizing than rewarding.
@@
 % Directivity \textcolor{red}{appendix?} & 0.535 & 0.526 & 0.533 & 0.535 & 0.012 & 0.012 & 0.012 & 0.012 \\
-Correlation            & 0.886 & 0.884 & 0.891 & 0.877 & 0.153 & 0.145 & 0.170 & 0.132 \\
+Pearson correlation    & 0.886 & 0.884 & 0.891 & 0.877 & 0.153 & 0.145 & 0.170 & 0.132 \\
 GENIE3 (depth = 1)     & 0.878 & & & & 0.184 & & & \\

### 2014-06-20 article.tex
wordings

--- 2014-06-20 article.tex
@@
 
-We will compare our approach to the Pearson correlation (see Section
-\ref{sec:inference}), the generalized transfer entropy (GTE) and GENIE3.
+The proposed approach is compared to Pearson correlation statistics (as
+described in Section~\ref{sec:inference}), generalized transfer entropy (GTE)
+and the GENIE3 algorithm.
 \begin{itemize}
-\item \textbf{GTE} \citep{stetter2012model}
-, the baseline of the challenge, measures for all pairs of
+\item \textbf{GTE} \citep{stetter2012model}, the baseline of the challenge, measures for all pairs of
 neurons $i$ and $j$ the reduction of uncertainty in predicting future values of
@@
 Interestingly, methods that takes into account directivity, namely GTE and
-GENIE3, slightly improve their AUROC and AUPRC by giving the same way to directed edges.
+GENIE3, improve their AUROC and AUPRC by giving the same way to directed edges.
 (see GTE and GTE(undirected) in Figure \ref{fig:curves}

### 2014-06-20 article.tex
some modifs : version ready for Damien + new images

--- 2014-06-20 article.tex
@@
 
-\begin{abstract}
-In this work, we propose a simple and mathematically motivated method for the
-problem of connectome inference in calcium imaging data. The proposed algorithm
-consists in i) processing the raw signals to detect neural peak activities and ii)
-inferring the degree of association between neurons from partial correlation
-statistics.  This paper summarizes the methodology that led us to win the
-Connectomics Challenge, proposes a simplified version of our method and finally
-discusses our results with respect to other inference methods.
-\end{abstract}
+\begin{abstract} In this work, we propose a simple and mathematically
+motivated method for the problem of connectome inference in calcium imaging
+data. The proposed algorithm is made of two steps. First, processing the raw
+signals to detect neural peak activities. Second, inferring the degree of
+association between neurons from partial correlation statistics. This paper
+summarizes the methodology that led us to win the Connectomics Challenge,
+proposes a simplified version of our method and finally discusses our results
+with respect to other inference methods. \end{abstract}
 
@@
 
-\textcolor{red}{To improve (style):} The human brain is a complex biological organ made of 100 billions of neurons,
-each connected to 7000 other neurons on average. Unfortunately, direct
-observations of the connectome, the wiring diagram of the brain, is not yet
-technically feasible. Without being perfect, calcium imaging currently allows
-the real-time and simultaneous observation of neuron activities from thousands
-of neurons, producing individual time series representing their fluorescence
-intensity. From these data, the connectome inference problem consists in
-retrieving the synaptic connections between neurons on the basis of the
-fluorescence time series. In particular, this problem is often made difficult
-because of experimental issues, including masking effects (making some of the
-neurons not to be observed or confounded with others), the low sampling rate of
-the optical device with respect to the neural activity speed or the slow decay
-of fluorescence.
+%%%%%%% !!!!!!!! \textcolor{red}{To improve (style):} !!!! %%%%%%%%
+The human brain is a complex biological
+organ made of 100 billions of neurons, each connected to 7000 other neurons on
+average. Unfortunately, direct observations of the connectome, the wiring
+diagram of the brain, is not yet technically feasible. Without being perfect,
+calcium imaging currently allows the real-time and simultaneous observation of
+neuron activities from thousands of neurons, producing individual time series
+representing their fluorescence intensity. From these data, the connectome
+inference problem consists in retrieving the synaptic connections between
+neurons on the basis of the fluorescence time series. In particular, this
+problem is often made difficult because of experimental issues, including
+masking effects (making some of the neurons not to be observed or confounded
+with others), the low sampling rate of the optical device with respect to the
+neural activity speed or the slow decay of fluorescence.
+%%%%%%%%%%% !!!!!!!!!!!!!! %%%%%%%%%%%%%%%%
 
@@
 \centering
-\includegraphics[width=0.4\linewidth]{images/fig_filtering}
+\subfigure[Original]{\includegraphics[width=0.3\textwidth]{images/original_curve.pdf} \label{fig:original_curve}}
+\subfigure[Low-pass $f_1(x_i^t)$]{\includegraphics[width=0.3\textwidth]{images/filter_curve.pdf} \label{fig:lp_curve}}\\
+\subfigure[High-pass $g(x_i^t)$]{\includegraphics[width=0.3\textwidth]{images/diff_curve.pdf} \label{fig:hp_curve}}
+\subfigure[Thresholding $h(x_i^t)$]{\includegraphics[width=0.3\textwidth]{images/threshold_curve.pdf} \label{fig:threshold_curve}}\\
+
+\subfigure[Weights $w(x_i^t)$]{\includegraphics[width=0.3\textwidth]{images/weights_curve.pdf} \label{fig:original_curve}}
 \caption{Signal processing process for extracting peaks from the raw fluorescence data.}
@@
 \end{figure}
+
+% \begin{figure}
+% \centering
+% \includegraphics[width=0.4\linewidth]{images/fig_filtering}
+% \caption{Signal processing process for extracting peaks from the raw fluorescence data.}
+% \label{fig:filtered-signal}
+% \end{figure}
 
@@
 large part of the network is firing, detecting pairwise neuron interactions is a
-difficult task. \textcolor{red}{G: say that neurons may fire because of global
-high activity, without any actual cause -- see generator.}
+difficult task. Futhermore, it is even possible that neurons fire because of global high activity, without actual cause (see \cite{stetter2012model}).
+% \textcolor{red}{G: say that neurons may fire because of global
+% high activity, without any actual cause -- see generator.}
 Accordingly, in order to reduce false interaction detection,
@@
 In supervised learning terms, the network inference task can be viewed as a
-binary classification task where one has to correctly classify the presence
-or the absence of edges of the graph. We assess the accuracy of the
-network inference method using the area under the ROC curve (AUROC)
-and the area under the precision-recall curve (AUPRC)
-\citep{schrynemackers2013protocols}. Since neurons are not self-connected
-($(i, i) \not \in E, \forall i \in V$) and some inference methods could
-give maximal scores to those edges, e.g. Pearson
+binary classification task where one has to correctly classify the presence or
+the absence of edges of the graph. We assess the accuracy of the network
+inference method using the area under the ROC curve (AUROC) and the area under
+the precision-recall curve (AUPRC) \citep{schrynemackers2013protocols}. Since
+neurons are not self-connected ($(i, i) \not \in E, \forall i \in V$) and some
+inference methods could give maximal scores to those edges, e.g. Pearson
 correlation, those elements are set to have minimal connectivity score prior
@@
 
-\item \textbf{GENIE3} \citep{huynhthu2010inferring} translates the inference of the
-network of $p$ neurons into $p$ supervised learning tasks. For each task,
-the fluorescence of a neuron is predicted from the fluorescence
-of all other neurons using a tree based ensemble such as
-random forest \citep{breiman2001random}. The tree ensemble associates a
-variable importance score \citep{louppe2013understanding}
-to each neuron used in the predictions, which is used as a degree of associate. The following parameters are used
-$10000$ trees, $\log_2{p}$ variables are randomly selected to split tree
-nodes and the maximal tree depth is constrained to 1, 2 or 3.
-\end{itemize}
+\item \textbf{GENIE3} \citep{huynhthu2010inferring} translates the inference
+of the network of $p$ neurons into $p$ supervised learning tasks. For each
+task, the fluorescence of a neuron is predicted from the fluorescence of all
+other neurons using a tree based ensemble such as random forest
+\citep{breiman2001random}. The tree ensemble associates a variable importance
+score \citep{louppe2013understanding} to each neuron used in the predictions,
+which is used as a degree of associate. The following parameters are used
+$10000$ trees, $\log_2{p}$ variables are randomly selected to split tree nodes
+and the maximal tree depth is constrained to 1, 2 or 3. \end{itemize}
 
@@
          averaged partial correlation method, partial correlation used
-         filter $f_1$).}
+         filter $f_1$). }
 \label{fig:curves}
@@
 
-The best method only infers the \textbf{undirected} network by giving the
-same connectivity score to both edges $(i,j)$ and $(j,i)$. This is quite
-surprising considering the problem statement.
+The best method only infers the \textbf{undirected} network by giving the same
+degree of association to both edges $(i,j)$ and $(j,i)$. This is quite
+surprising considering the problem statement. Trying to direct links could be
+more penalizing than rewarding. For example, symmetrizing the degree of
+association matrix does not necessarily degrade AUPRC and AUROC.
 
-If the undirected network is perfectly inferred, it would already yield
-high AUROC score for instance $\approx{}0.996$ on \textit{normal-1}. Trying
-to infer edge directivity is likely to be counter-productive or yield
-small gain.
-By contrast, the same experiment with AUPRC would yield
-to a score of $\approx 0.789$ on \textit{normal-1}. Thus inferring
+If the inferred network corresponds to the undirected network, it would
+already yield high AUROC score for instance $\approx 0.996$ on
+\textit{normal-1}. Infering edge directivity is likely to be counter-
+productive or yield small gain. By contrast, the same experiment with AUPRC
+would yield to a score of $\approx 0.789$ on \textit{normal-1}. Thus inferring
 correctly directivity would be more rewarding in AUPRC term.
-Interestingly, methods that takes into account directivity, namely GTE and
-GENIE3, improve their AUROC and AUPRC by giving the same way to directed edges.
-(in particular see GTE and GTE(undirected) in Figure \ref{fig:pr_curve}
-\textcolor{red}{AJ: Figure \ref{fig:curves}  contradicts this message,
-especially pr-curve. AS:And now?} and Table \ref{tab:tab1} in Appendix \textcolor{red}{REF}).
-Trying to detect the link direction is more penalizing than rewarding.
+
+% Interestingly, methods that takes into account directivity, namely GTE and
+% GENIE3, improve their AUROC and AUPRC by giving the same way to directed edges.
+% (in particular see GTE and GTE(undirected) in Figure \ref{fig:pr_curve}
+% \textcolor{red}{AJ: Figure \ref{fig:curves}  contradicts this message,
+% especially pr-curve. AS:And now?} and Table \ref{tab:tab1} in Appendix \textcolor{red}{REF}).
+% Trying to detect the link direction is more penalizing than rewarding.
 
@@
 with respect to the problem statement. A clear hierarchy is also difficult to
-derive based on ROC curve of Figure \ref{fig:curves}. We advice to avoid the AUROC
+derive based on ROC curve of Figure \ref{fig:roc_curve}. We advice to avoid the AUROC
 for the assessment of network inference method. An alternative metric would

### 2014-06-20 article.tex
some modifs

@@
 
-\textcolor{red}{AJ: GENI3 is not on the figure}
 As it can also be seen on Figure \ref{fig:curves}, the GENIE3 performance
@@
 \cite{louppe2014understanding}, limiting the maximal depth of trees may help
-to reduce the misestimation bias in variable importance computing, i.e.
-inferring the strength of a link. Therefore a trade-off of the maximal depth
+to improve the variable importance computing, i.e.
+inferring the degree of association. Therefore a trade-off of the maximal depth
 may give the best of both worlds.
@@
 In this paper, we present the winning method of the Connectomics challenge.
-This approach is simple and theoretically grounded. We also evaluate the method
+Our approach is simple and theoretically sounded and made of two main stages: the signal is first preprocessed with several filters and then we derive the degree of association matrix by computing the partial correlation statistics matrix.
+We also evaluate the method
 in a more detailed way and perform a comparison with other inference methods.
-We also discuss the relevance of the metric used in the challenge.
+We finally discuss the relevance of the metric used in the challenge and we point out that it was not necessary to
+discover causal relationships to maximize the ROC AUC. Thus, it may be  promising to focus
+on that particular topic in future works.
 
-In the discussion, we give hints about limiting the depth of trees in the
-GENIE3 method to infer the network. It should be interesting to see if there
-is a optimum value for the maximal depth. And of course, it may also rewarding
-to increase considerably the number of trees to get more stable predictions.
+% In the discussion, we give hints about limiting the depth of trees in the
+% GENIE3 method to infer the network. It should be interesting to see if there
+% is a optimum value for the maximal depth. And of course, it may also rewarding
+% to increase considerably the number of trees to get more stable predictions.
 
-In previous study \citep{shipley2002cause}, it has been suggested to
-consider correlation coefficients of all possible orders,
-i.e. conditioned on every subsets of the set of $p-2$ other variables. This
-would take into account multiple indirect paths between a given pair of
-variables. Instead of considering only the highest order, it may be useful to
-study with accuracy the inferred network at all orders. In this case, it may not
-be very relevant but interesting in case of dynamical networks.
+% In previous study \citep{shipley2002cause}, it has been suggested to
+% consider correlation coefficients of all possible orders,
+% i.e. conditioned on every subsets of the set of $p-2$ other variables. This
+% would take into account multiple indirect paths between a given pair of
+% variables. Instead of considering only the highest order, it may be useful to
+% study with accuracy the inferred network at all orders. In this case, it may not
+% be very relevant but interesting in case of dynamical networks.
 
-As we mentioned, in order to maximize the ROC AUC, it was not necessary to
-discover causal relationships. It may be, in future works, promising to focus
-on that particular topic.
+% As we mentioned, in order to maximize the ROC AUC, it was not necessary to
+% discover causal relationships. It may be, in future works, promising to focus
+% on that particular topic.
 

### 2014-06-21 article.tex
wording + commments

@@
 direct and indirect connections, (ii) the simulated network from the
-\citep{stetter2012model} generator or the neural network in general could be
+\citep{stetter2012model} generator or neural networks in general could be
 reduced to a linear model after pre-processing. Those results is obviously
@@
 
-As it can also be seen on Figure \ref{fig:curves}, the GENIE3 performance
-increases with deeper trees in addition to be computationally feasible. The
+As observed on Figure \ref{fig:curves}, the GENIE3 performance
+increases with deeper trees while being still computationally feasible. The
 reason is twofold. First, the deeper the tree, the larger is the conditioning.
+\textcolor{red}{AJ: conditioning?}
 As it was observed in the comparison between correlation and partial
-correlation, it screens indirect links in the inferred network. Second, the
+correlation, it screens indirect links in the inferred network.
+\textcolor{red}{AJ: I don't understand the link with GENIE3}
+Second, the
 number of small trees need to be much higher than deep trees in order to
@@
 to improve the variable importance computing, i.e.
-inferring the degree of association. Therefore a trade-off of the maximal depth
-may give the best of both worlds.
+inferring the degree of association. \textcolor{red}{AJ: there is no explanation
+of why it would be better apart for computational reason.} Therefore a trade-off
+ of the maximal depth may give the best of both worlds. \textcolor{red}{AJ:
+ Which tradeoff? Which worlds?}
 

### 2014-06-21 article.tex
Comment + make 3-2 rows

@@
 \subfigure[Original]{\includegraphics[width=0.3\textwidth]{images/original_curve.pdf} \label{fig:original_curve}}
-\subfigure[Low-pass $f_1(x_i^t)$]{\includegraphics[width=0.3\textwidth]{images/filter_curve.pdf} \label{fig:lp_curve}}\\
-\subfigure[High-pass $g(x_i^t)$]{\includegraphics[width=0.3\textwidth]{images/diff_curve.pdf} \label{fig:hp_curve}}
-\subfigure[Thresholding $h(x_i^t)$]{\includegraphics[width=0.3\textwidth]{images/threshold_curve.pdf} \label{fig:threshold_curve}}\\
-
+\subfigure[Low-pass $f_1(x_i^t)$]{\includegraphics[width=0.3\textwidth]{images/filter_curve.pdf} \label{fig:lp_curve}}
+\subfigure[High-pass $g(x_i^t)$]{\includegraphics[width=0.3\textwidth]{images/diff_curve.pdf} \label{fig:hp_curve}}\\
+\subfigure[Thresholding $h(x_i^t)$]{\includegraphics[width=0.3\textwidth]{images/threshold_curve.pdf} \label{fig:threshold_curve}}
 \subfigure[Weights $w(x_i^t)$]{\includegraphics[width=0.3\textwidth]{images/weights_curve.pdf} \label{fig:original_curve}}
-\caption{Signal processing process for extracting peaks from the raw fluorescence data.}
+\caption{Signal processing process for extracting peaks from the raw fluorescence data.
+         \textcolor{red}{AJ: The bottom axe is hidden on some figures.}}
 \label{fig:filtered-signal}

### 2014-06-21 article.tex
80 char break
wording + comment

@@
 
-Finally, let us remark that performance shows to be quite sensitive to the choice
-of hyper-parameters in the signal processing pipeline (e.g., $f_1$ or $f_2$ or
-the value of the threshold $\tau$). To further improve robustness, the last
-step of our method therefore consists in averaging correlation statistics over
-various values of the parameters, thereby reducing the variance of our
-predictions. In this case, the method is referred to as \textit{Averaged Partial correlation} statistics. Further details are provided in Appendix~\ref{app:optimized}.
+Finally, let us remark that performance shows to be quite sensitive to the
+choice of hyper-parameters in the signal processing pipeline (e.g., $f_1$ or
+$f_2$ or the value of the threshold $\tau$). To further improve robustness, the
+last step of our method therefore consists in averaging correlation statistics
+over various values of the parameters, thereby reducing the variance of our
+predictions. In this case, the method is referred to as \textit{Averaged
+Partial correlation} statistics. Further details are provided in
+Appendix~\ref{app:optimized}.
 
@@
 \begin{itemize}
-\item \textbf{GTE} \citep{stetter2012model}, the baseline of the challenge, measures for all pairs of
-neurons $i$ and $j$ the reduction of uncertainty in predicting future values of
-$i$ given the observation of the time series of the neuron $j$
-conditionally to the observation of past time series of neuron $i$,
-whenever the average fluorescence is over a conditioning level.
-Pre-processing and conditioning level were set to reproduce baseline of the
-challenge.
+\item \textbf{GTE} \citep{stetter2012model}, the baseline of the challenge,
+measures for all pairs of neurons $i$ and $j$ the reduction of uncertainty in
+predicting future values of $i$ given the observation of the time series of the
+neuron $j$ conditionally to the observation of past time series of neuron $i$,
+whenever the average fluorescence is over a conditioning level. Pre-processing
+and conditioning level were set to reproduce baseline of the challenge.
 
@@
 $10000$ trees, $\log_2{p}$ variables are randomly selected to split tree nodes
-and the maximal tree depth is constrained to 1, 2 or 3. \end{itemize}
+and the maximal tree depth is constrained to 1, 2 or 3. \textcolor{red}{AJ Which
+depth is represented on the graph?}
+\end{itemize}
 
@@
 dataset. The partial correlation outperforms other state-of-the-art methods
-by at least factor of 2 in AUPRC reaching $0.347$ and an increased of $0.05$ in
-AUROC. Two reasons might explain such differences: (i) among
-those methods only the partial correlation makes the distinction between
-direct and indirect connections, (ii) the simulated network from the
+by at least factor of 2 in AUPRC reaching $0.347$ and an increased of $0.03$ in
+AUROC. Averaging Partial correlation matrix over a wide of parameters
+further improves AUPRC to $0.389$ and improve AUROC by $0.009$.
+Two reasons might explain such differences: (i) only the partial
+correlation-based methods and GENI3 at lesser extent distinguish
+direct links from indirect one, (ii) simulated networks from the
 \citep{stetter2012model} generator or neural networks in general could be
-reduced to a linear model after pre-processing. Those results is obviously
-generalized over the other datasets see Appendix \textcolor{red}{REF}.
+reduced to a linear model after pre-processing. Those results
+generalizes over the other datasets see Appendix \textcolor{red}{REF}.
 
@@
 
-As observed on Figure \ref{fig:curves}, the GENIE3 performance
-increases with deeper trees while being still computationally feasible. The
-reason is twofold. First, the deeper the tree, the larger is the conditioning.
-\textcolor{red}{AJ: conditioning?}
-As it was observed in the comparison between correlation and partial
-correlation, it screens indirect links in the inferred network.
-\textcolor{red}{AJ: I don't understand the link with GENIE3}
-Second, the
-number of small trees need to be much higher than deep trees in order to
-observe - and evaluate - all pairs.  However, as suggested by
-\cite{louppe2014understanding}, limiting the maximal depth of trees may help
-to improve the variable importance computing, i.e.
-inferring the degree of association. \textcolor{red}{AJ: there is no explanation
-of why it would be better apart for computational reason.} Therefore a trade-off
- of the maximal depth may give the best of both worlds. \textcolor{red}{AJ:
- Which tradeoff? Which worlds?}
-
-% Opt: obviously when parameters are tuned/optimized, it's slightly better -->
-% see appendix for a full description of the method
-
-% \begin{table}
-% \small
-% \centering
-% \begin{tabular}{@{}l *{8}{c}@{}}
-%   & \multicolumn{4}{c}{AUROC} & \multicolumn{4}{c}{AUPRC} \\
-% \cmidrule(r){2-5}\cmidrule(r){6-9}
-% Methods $\backslash$ normal- & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 \\
-% \hline \hline
-% % Directivity \textcolor{red}{appendix?} & 0.535 & 0.526 & 0.533 & 0.535 & 0.012 & 0.012 & 0.012 & 0.012 \\
-% GENIE3 (depth = 1)     &  & & & & & & & \\
-% GENIE3 (depth = 2)     &  & & & & & & & \\
-% GENIE3 (depth = 3)     &  & & & & & & & \\
-% GTE                    &  & & & & & & & \\
-% % Our approach + dir  \textcolor{red}{appendix?}   & 0.944 & 0.943 & 0.942 & 0.940 & 0.404 & 0.405 & 0.399 & 0.389 \\
-% \end{tabular}
-% \caption{TODO (network are undirected)}
-% \label{tab:tab2}
-% \end{table}
+\textcolor{red}{Only one GENI3, thus it can't be observed.}
+As observed on Figure \ref{fig:curves}, the GENIE3 performance increases with
+deeper trees while being still computationally feasible. The reason is twofold.
+First, the deeper the tree, the larger is the conditioning. \textcolor{red}{AJ:
+conditioning?} As it was observed in the comparison between correlation and
+partial correlation, it screens indirect links in the inferred network.
+\textcolor{red}{AJ: I don't understand the link with GENIE3} Second, the number
+of small trees need to be much higher than deep trees in order to observe - and
+evaluate - all pairs.  However, as suggested by \cite{louppe2014understanding},
+limiting the maximal depth of trees may help to improve the variable importance
+computing, i.e. inferring the degree of association. \textcolor{red}{AJ: there
+is no explanation of why it would be better apart for computational reason.}
+Therefore a trade-off  of the maximal depth may give the best of both worlds.
+\textcolor{red}{AJ:  Which tradeoff? Which worlds?}
 
@@
 productive or yield small gain. By contrast, the same experiment with AUPRC
-would yield to a score of $\approx 0.789$ on \textit{normal-1}. Thus inferring
+would yield a score of $\approx 0.789$ on \textit{normal-1}. Thus inferring
 correctly directivity would be more rewarding in AUPRC term.
@@
 
-The area under the ROC curve is not consistent metric
-with respect to the problem statement. A clear hierarchy is also difficult to
-derive based on ROC curve of Figure \ref{fig:roc_curve}. We advice to avoid the AUROC
-for the assessment of network inference method. An alternative metric would
-be the area under the precision-recall curve (AUPRC). Those
-conclusions are in line with \cite{schrynemackers2013protocols}.
+The area under the ROC curve is not a consistent metric with respect to the
+problem statement. A clear hierarchy is also difficult to derive from ROC
+curves as shown on Figure \ref{fig:roc_curve}. We advice to avoid the AUROC for
+the assessment of network inference method. An alternative would be to assess
+network inference using the area under the precision-recall curve (AUPRC).
+Those conclusions are in line with \cite{schrynemackers2013protocols}.
 
@@
 
-In this paper, we present the winning method of the Connectomics challenge.
-Our approach is simple and theoretically sounded and made of two main stages: the signal is first preprocessed with several filters and then we derive the degree of association matrix by computing the partial correlation statistics matrix.
-We also evaluate the method
-in a more detailed way and perform a comparison with other inference methods.
-We finally discuss the relevance of the metric used in the challenge and we point out that it was not necessary to
-discover causal relationships to maximize the ROC AUC. Thus, it may be  promising to focus
-on that particular topic in future works.
+In this paper, we present the winning method of the Connectomics challenge. Our
+approach is simple and theoretically sounded and made of two main stages: the
+signal is first preprocessed with several filters and then we derive the degree
+of association matrix by computing the partial correlation statistics matrix.
+We also evaluate the method in a more detailed way and perform a comparison
+with other inference methods. We finally discuss the relevance of the metric
+used in the challenge and we point out that it was not necessary to discover
+causal relationships to maximize the ROC AUC. Thus, it may be  promising to
+focus on that particular topic in future works.
 

### 2014-06-21 article.tex
explain better the graph
math caption to actual filtering stpe

@@
 \centering
-\subfigure[Original]{\includegraphics[width=0.3\textwidth]{images/original_curve.pdf} \label{fig:original_curve}}
-\subfigure[Low-pass $f_1(x_i^t)$]{\includegraphics[width=0.3\textwidth]{images/filter_curve.pdf} \label{fig:lp_curve}}
-\subfigure[High-pass $g(x_i^t)$]{\includegraphics[width=0.3\textwidth]{images/diff_curve.pdf} \label{fig:hp_curve}}\\
-\subfigure[Thresholding $h(x_i^t)$]{\includegraphics[width=0.3\textwidth]{images/threshold_curve.pdf} \label{fig:threshold_curve}}
-\subfigure[Weights $w(x_i^t)$]{\includegraphics[width=0.3\textwidth]{images/weights_curve.pdf} \label{fig:original_curve}}
+\subfigure[Raw signal]{\includegraphics[width=0.3\textwidth]{images/original_curve.pdf} \label{fig:original_curve}}
+\subfigure[Low-pass filter $f_1$]{\includegraphics[width=0.3\textwidth]{images/filter_curve.pdf} \label{fig:lp_curve}}
+\subfigure[High-pass filter $g$]{\includegraphics[width=0.3\textwidth]{images/diff_curve.pdf} \label{fig:hp_curve}}\\
+\subfigure[Hard-threshold filter $h$]{\includegraphics[width=0.3\textwidth]{images/threshold_curve.pdf} \label{fig:threshold_curve}}
+\subfigure[Global regularization $w$]{\includegraphics[width=0.3\textwidth]{images/weights_curve.pdf} \label{fig:original_curve}}
 \caption{Signal processing process for extracting peaks from the raw fluorescence data.
@@
 large part of the network is firing, detecting pairwise neuron interactions is a
-difficult task. Futhermore, it is even possible that neurons fire because of global high activity, without actual cause (see \cite{stetter2012model}).
+difficult task. Furthermore, it is even possible that neurons spike because of
+a global high activity, without any actual cause (see \cite{stetter2012model}).
 % \textcolor{red}{G: say that neurons may fire because of global
@@
 peak intensities at time $t$ are regularized by the global activity of all
-neurons, thereby reducing the importance of peaks identified during global high activity periods:
+neurons, thereby reducing the importance of peaks identified during global
+high activity periods:
 \begin{align}
@@
          averaged partial correlation method, partial correlation used
-         filter $f_1$). }
+         filter $f_1$). Area under the curves are given between $()$
+         for the corresponding methods.}
 \label{fig:curves}

### 2014-06-23 article.tex
methods is not mathematically motivated

@@
 
-\begin{abstract} In this work, we propose a simple and mathematically
-motivated method for the problem of connectome inference in calcium imaging
-data. The proposed algorithm is made of two steps. First, processing the raw
-signals to detect neural peak activities. Second, inferring the degree of
-association between neurons from partial correlation statistics. This paper
-summarizes the methodology that led us to win the Connectomics Challenge,
-proposes a simplified version of our method and finally discusses our results
-with respect to other inference methods. \end{abstract}
+\begin{abstract} In this work, we propose a simple, but yet efficient,
+methodologically motivated method for the problem of connectome inference in
+calcium imaging data. The proposed algorithm is made of two steps. First,
+processing the raw signals to detect neural peak activities. Second, inferring
+the degree of association between neurons from partial correlation statistics.
+This paper summarizes the methodology that led us to win the Connectomics
+Challenge, proposes a simplified version of our method and finally discusses
+our results with respect to other inference methods.\end{abstract}
 

### 2014-06-23 article.tex
wording

@@
 inference problem is formally stated as follows:  \textit{Given the sampled
-observations $\{ x^t_i \in \mathbb{R}^{p} | i \in V, t = 1, \dots T \}$ of $p$
+observations $\{ x^t_i \in \mathbb{R} | i \in V, t = 1, \dots, T \}$ of $p$
 neurons for $T$ time intervals, the goal is to infer the set $E$ of connections in $G$.}
@@
 describes, in all details, our actual winning method, giving slightly better
-results than the method presented in the paper but highly tuned for the
-challenge.
+results than the method presented in the paper at a price of significant
+tuning.
 

### 2014-06-23 article.tex
wording Damien + references

@@
 \subfigure[Hard-threshold filter $h$]{\includegraphics[width=0.3\textwidth]{images/threshold_curve.pdf} \label{fig:threshold_curve}}
-\subfigure[Global regularization $w$]{\includegraphics[width=0.3\textwidth]{images/weights_curve.pdf} \label{fig:original_curve}}
+\subfigure[Global regularization $w$]{\includegraphics[width=0.3\textwidth]{images/weights_curve.pdf} \label{fig:weight_curve}}
 \caption{Signal processing process for extracting peaks from the raw fluorescence data.
@@
 
-As the first plot in Figure~\ref{fig:filtered-signal} illustrates, the raw
+As the Figure~\ref{fig:original_curve} illustrates, the raw
 fluorescence signal is very noisy due to light scattering artifacts that
@@
 % symmetrical median filter
-f_1(x^t_i) &= x^{t-1}_i + x^{t}_i + x^{t+1}_i \label{eq:symetric-median}, \\
+f_1(x^t_i) &= x^{t-1}_i + x^t_i + x^{t+1}_i \label{eq:symetric-median}, \\
 % asymmetrical weighted median
-f_2(x^t_i) &= 0.4 x^{t-3}_i + 0.6 x^{t-2}_i + 0.8 x^{t-1}_i + x_{t}^i,
+f_2(x^t_i) &= 0.4 x^{t-3}_i + 0.6 x^{t-2}_i + 0.8 x^{t-1}_i + x_i^t,
 \label{eq:weighted-asymetric-median}
 \end{align}
-where $f_1$x effect is shown in the second plot in the figure.
+where $f_1$ effect is shown in Figure \ref{fig:lp_curve}.
 
@@
 neuron spikes -- characterized by high frequencies -- by filtering out low
-frequencies through a high-pass filter, resulting in the third plot of the figure:
-\begin{align} % an asymmetrical discrete derivative filter
+frequencies through a high-pass filter, resulting in the plot of
+Figure \ref{fig:hp_curve}:
+\begin{align}
 g(x^{t}_{i}) &= x^{t}_i - x^{t-1}_i. \label{eq:high-pass-filter}
@@
 Once the low- and and high-pass filters have been applied, the remaining signal
-corresponds to the discrete derivative of the fluorescence time series. To
-further filter out small signal variations, mostly due to noise, the third step
-consists in a  hard-threshold filter, yielding the fourth plot in the figure:
+corresponds to the finite backward difference of the fluorescence time series.
+To further filter out small signal variations, mostly due to noise, the third
+step consists in a  hard-threshold filter, yielding the Figure
+\ref{fig:threshold_curve}:
 \begin{align}
@@
 approach is defined by the composed function $w \cdot h \cdot g \cdot f_1$
-(resp. $f_2$ for the winning method).
+(resp. $f_2$) and results in the plot of Figure \ref{fig:weight_curve}.
 

### 2014-06-23 article.tex
remove dot in acknowledgement
add damien remark

@@
 
+\textcolor{red}{DE: la phrase ne veut rien dire}
 Considering the short delay of communication between neurons and the slow
@@
 \section*{Acknowledgments}
-A. Joly and G. Louppe are research fellows of
-the FNRS, Belgium.  A. Sutera is recipient of
-a F.R.I.A. fellowship of F.R.S.-FNRS, Belgium.
-This work is supported by PASCAL2 and the IUAP DYSCO, initiated by the
-Belgian State, Science Policy Office.
+A Joly and G Louppe are research fellows of the FNRS, Belgium.  A Sutera is
+recipient of a FRIA fellowship of FRS-FNRS, Belgium. This work is supported by
+PASCAL2 and the IUAP DYSCO, initiated by the Belgian State, Science Policy
+Office.
 

### 2014-06-23 article.tex
80 char line break

@@
 P_{X_j|Z}$. In particular, when $X_i$ and $X_j$ are conditionally independent
-with respect to all the other variables, denoted $X_i \perp X_j | X^{-i,j}$, then the
-observation of $X_i$ given the knowledge of $X^{-i,j}$ provides no information
-about $X_j$, and vice-versa. From a graphical point of view and assuming no
-hidden variable, this indicates that $X_i$ and $X_j$ do not directly interact
-(i.e., $(i,j) \notin E$). By opposition, if $X_i$ and $X_j$ are conditionally
-dependent with respect to all other variables, denoted $X_i \not\perp X_j |
-X^{-i,j}$, then the observation of one of the two variables provides some
-information about the other, therefore highlighting a direct interaction
-between the two random variables (i.e., $(i, j) \in E$).
+with respect to all the other variables, denoted $X_i \perp X_j | X^{-i,j}$,
+then the observation of $X_i$ given the knowledge of $X^{-i,j}$ provides no
+information about $X_j$, and vice-versa. From a graphical point of view and
+assuming no hidden variable, this indicates that $X_i$ and $X_j$ do not
+directly interact (i.e., $(i,j) \notin E$). By opposition, if $X_i$ and $X_j$
+are conditionally dependent with respect to all other variables, denoted $X_i
+\not\perp X_j | X^{-i,j}$, then the observation of one of the two variables
+provides some information about the other, therefore highlighting a direct
+interaction between the two random variables (i.e., $(i, j) \in E$).
 
@@
 \end{equation}
-Conversely, $X_i$ and $X_j$ are conditionally dependent if $\rho_{X_i, X_j | X^{-i,j}} \neq 0$,
-where $\rho_{X_i, X_j | X^{-i,j}}$ can now be interpreted as the degree of association
-between the two variables (i.e., the larger the value, the stronger the interaction).
-Note however that the partial correlation statistic is symmetric (i.e., $\rho_{X_i, X_j | X^{-i,j}} = \rho_{X_j, X_i | X^{-j,i}}$) and therefore does not account for the direction of the interaction.
-Together, the partial correlation statistics correspond to the inverse
-$\Sigma^{-1}$ of the covariance matrix, also known as the concentration or
-precision matrix. Computationally, they can be estimated efficiently in
+Conversely, $X_i$ and $X_j$ are conditionally dependent if $\rho_{X_i, X_j |
+X^{-i,j}} \neq 0$, where $\rho_{X_i, X_j | X^{-i,j}}$ can now be interpreted as
+the degree of association between the two variables (i.e., the larger the
+value, the stronger the interaction). Note however that the partial correlation
+statistic is symmetric (i.e., $\rho_{X_i, X_j | X^{-i,j}} = \rho_{X_j, X_i |
+X^{-j,i}}$) and therefore does not account for the direction of the
+interaction. Together, the partial correlation statistics correspond to the
+inverse $\Sigma^{-1}$ of the covariance matrix, also known as the concentration
+or precision matrix. Computationally, they can be estimated efficiently in
 $O(M^3)$ (instead of $O(p^3)$) from the $M$ first principal components
-extracted through PCA~\citep{bishop2006pattern} on the processed data. In our experiments, $M$ is set
-to $0.8 p$, thereby allowing us to further filter noise in the data.
+extracted through PCA~\citep{bishop2006pattern} on the processed data. In our
+experiments, $M$ is set to $0.8 p$, thereby allowing us to further filter noise
+in the data.
 

### 2014-06-23 article.tex
remove comment
explain which noise in pca

@@
 At this step, the processed signal only contains clean spikes. However, when a
-large part of the network is firing, detecting pairwise neuron interactions is a
-difficult task. Furthermore, it is even possible that neurons spike because of
-a global high activity, without any actual cause (see \cite{stetter2012model}).
-% \textcolor{red}{G: say that neurons may fire because of global
-% high activity, without any actual cause -- see generator.}
-Accordingly, in order to reduce false interaction detection,
-peak intensities at time $t$ are regularized by the global activity of all
-neurons, thereby reducing the importance of peaks identified during global
-high activity periods:
+large part of the network is firing, detecting pairwise neuron interactions is
+a difficult task. Furthermore, it is even possible that neurons spike because
+of a global high activity, without any actual cause (see
+\cite{stetter2012model}). Accordingly, in order to reduce false interaction
+detection, peak intensities at time $t$ are regularized by the global activity
+of all neurons, thereby reducing the importance of peaks identified during
+global high activity periods:
 \begin{align}
@@
 extracted through PCA~\citep{bishop2006pattern} on the processed data. In our
-experiments, $M$ is set to $0.8 p$, thereby allowing us to further filter noise
-in the data.
+experiments, $M$ is set to $0.8 p$, thereby allowing us to further filter the
+the data by removing the contribution of principal components which are
+likely due to noise.
 

### 2014-06-23 article.tex
put in evidence the stationary ot the stochastic process

@@
 
-Let us model the fluorescence indicators of all $p$ neurons as a set of random
+Let us model the fluorescence concentration of all $p$ neurons as a set of random
 variables $X = \{X_1, \dots, X_p\}$ following a joint probability distribution
-$P_X$. In the statistical framework, two random variables $X_i$ and $X_j$ are
+$P_X$, a stationary stochastic process.
+In the statistical framework, two random variables $X_i$ and $X_j$ are
 said to be conditionally independent to a (possibly empty) set of controlling

### 2014-06-23 article.tex
wording

@@
 experiments, $M$ is set to $0.8 p$, thereby allowing us to further filter the
-the data by removing the contribution of principal components which are
+the data by removing the contribution of principal components
 likely due to noise.

### 2014-06-23 article.tex
wording

@@
 
-\textcolor{red}{DE: la phrase ne veut rien dire}
-Considering the short delay of communication between neurons and the slow
-decay of fluorescence, the second step of our pipeline consists in identifying
-neuron spikes -- characterized by high frequencies -- by filtering out low
+Low frequencies of the signal correspond to the the slow
+decay of fluorescence, while communication between neurons are
+characterized by short delay. The second step of our pipeline consists in
+identifying neuron spikes -- of high frequencies -- by filtering out low
 frequencies through a high-pass filter, resulting in the plot of

### 2014-06-23 article.tex
wording

@@
 
-Low frequencies of the signal correspond to the the slow
-decay of fluorescence, while communication between neurons are
-characterized by short delay. The second step of our pipeline consists in
-identifying neuron spikes -- of high frequencies -- by filtering out low
-frequencies through a high-pass filter, resulting in the plot of
+Neurons communicates through short peaks, characterized by a high
+frequency, while low frequencies of the signal corresponds to the slow
+decay of fluorescence. The second step of our pipeline consists in
+identifying neuron spikes by filtering out
+low frequencies through a high-pass filter, resulting in the plot of
 Figure \ref{fig:hp_curve}:

### 2014-06-23 article.tex
emphaze the time invariance assumption

@@
 
-Let us model the fluorescence concentration of all $p$ neurons as a set of random
-variables $X = \{X_1, \dots, X_p\}$ following a joint probability distribution
-$P_X$, a stationary stochastic process.
-In the statistical framework, two random variables $X_i$ and $X_j$ are
+Let us assume that the fluorescence concentrations of all $p$ neurons modeled
+as a set of random variables $X = \{X_1, \dots, X_p\}$ are drawn from a time
+invariant joint probability distribution $P_X$.
+In the probability framework, two random variables $X_i$ and $X_j$ are
 said to be conditionally independent to a (possibly empty) set of controlling

### 2014-06-23 article.tex
add some word about conditional dependancy estimate in practice

@@
 Conversely, $X_i$ and $X_j$ are conditionally dependent if $\rho_{X_i, X_j |
-X^{-i,j}} \neq 0$, where $\rho_{X_i, X_j | X^{-i,j}}$ can now be interpreted as
-the degree of association between the two variables (i.e., the larger the
-value, the stronger the interaction). Note however that the partial correlation
+X^{-i,j}} \neq 0$, where $\rho_{X_i, X_j | X^{-i,j}} \in [-1;1]$ can now be
+interpreted as the degree of association between the two variables (i.e., the larger the
+value, the stronger the interaction). In practice due to the finite size of
+time series, noise and modeling assumptions, the partial correlation
+$\rho_{X_i, X_j | X^{-i,j}}$ will never be zero and will estimate
+conditional dependences. Note also that the partial correlation
 statistic is symmetric (i.e., $\rho_{X_i, X_j | X^{-i,j}} = \rho_{X_j, X_i |

### 2014-06-23 article.tex
wording

@@
 $\rho_{X_i, X_j | X^{-i,j}}$ will never be zero and will estimate
-conditional dependences. Note also that the partial correlation
+conditional independences. Note also that the partial correlation
 statistic is symmetric (i.e., $\rho_{X_i, X_j | X^{-i,j}} = \rho_{X_j, X_i |

### 2014-06-23 article.tex
wording

--- 2014-06-23 article.tex
@@
 time series, noise and modeling assumptions, the partial correlation
-$\rho_{X_i, X_j | X^{-i,j}}$ will never be zero and will estimate
-conditional dependences. Note also that the partial correlation
+$\rho_{X_i, X_j | X^{-i,j}}$ will never be zero and would require a statistical
+test to assert the conditional independence. Note also that the partial correlation
 statistic is symmetric (i.e., $\rho_{X_i, X_j | X^{-i,j}} = \rho_{X_j, X_i |

### 2014-06-23 article.tex
say what to do to obtain a graph

--- 2014-06-23 article.tex
@@
 the other variables $X^{-i,j}$ if their \textit{partial correlation} statistic
-is null~\citep{koller2009probabilistic}, i.e., if
+is null~\citep{baba2004partial}, i.e., if
 \begin{equation}
@@
 time series, noise and modeling assumptions, the partial correlation
-$\rho_{X_i, X_j | X^{-i,j}}$ will never be zero and will estimate
-conditional dependences. Note also that the partial correlation
+$\rho_{X_i, X_j | X^{-i,j}}$ will never be zero. If instead of a degree
+of correlation, one would want to infer the underlying graph a statistical
+test would be required to assert the conditional independence. Note also that
+the partial correlation
 statistic is symmetric (i.e., $\rho_{X_i, X_j | X^{-i,j}} = \rho_{X_j, X_i |

### 2014-06-23 article.tex
wording

@@
 $\rho_{X_i, X_j | X^{-i,j}}$ will never be zero. If instead of a degree
-of correlation, one would want to infer the underlying graph a statistical
-test would be required to assert the conditional independence. Note also that
+of association, one would want to infer the underlying graph a statistical
+test would be required to assert conditional independences. Note also that
 the partial correlation

### 2014-06-23 article.tex
fix

@@
 extracted through PCA~\citep{bishop2006pattern} on the processed data. In our
-experiments, $M$ is set to $0.8 p$, thereby allowing us to further filter the
+experiments, $M$ is set to $0.8 p$, thereby allowing us to further filter
 the data by removing the contribution of principal components

### 2014-06-23 article.tex
Damien & Arnaud thoughts and writing

--- 2014-06-23 article.tex
@@
 
-Let us assume that the fluorescence concentrations of all $p$ neurons modeled
-as a set of random variables $X = \{X_1, \dots, X_p\}$ are drawn from a time
-invariant joint probability distribution $P_X$.
-In the probability framework, two random variables $X_i$ and $X_j$ are
-said to be conditionally independent to a (possibly empty) set of controlling
-random variables $Z$, denoted $X_i \perp X_j | Z$, if the joint conditional
-probability distribution $P_{X_i, X_j | Z}$ factorizes into $P_{X_i|Z}
-P_{X_j|Z}$. In particular, when $X_i$ and $X_j$ are conditionally independent
-with respect to all the other variables, denoted $X_i \perp X_j | X^{-i,j}$,
-then the observation of $X_i$ given the knowledge of $X^{-i,j}$ provides no
-information about $X_j$, and vice-versa. From a graphical point of view and
-assuming no hidden variable, this indicates that $X_i$ and $X_j$ do not
-directly interact (i.e., $(i,j) \notin E$). By opposition, if $X_i$ and $X_j$
-are conditionally dependent with respect to all other variables, denoted $X_i
-\not\perp X_j | X^{-i,j}$, then the observation of one of the two variables
-provides some information about the other, therefore highlighting a direct
-interaction between the two random variables (i.e., $(i, j) \in E$).
+Our  connection inference  procedure  relies  on several  assumptions. First,
+we will assume that  the fluorescence concentrations of all $p$ neurons can be
+modeled as a set of random variables $X = \{X_1, \dots, X_p\}$  that are drawn
+from a time invariant joint  probability distribution $P_X$. Or, say otherwise,
+we assume that there exists a probability distribution $P_X$ such that the
+fluorescence concentrations at a particular time $t$ can be seen as an
+independent realization of $P_X$.
 
-Under the assumption that random variables follow a joint Gaussian
-distribution $\mathcal{N}(\mu; \Sigma)$ of mean vector $\mu$ and covariance
-matrix $\Sigma$, $X_i$ and $X_j$ are conditionally independent with respect to
-the other variables $X^{-i,j}$ if their \textit{partial correlation} statistic
-is null~\citep{baba2004partial}, i.e., if
+To a joint probability distribution $P_X$ corresponds a minimal dependency
+graph. Each node of this graph is a random variable. Two random variables are
+only connected if they are dependent. We consider that two neurons are
+connected if  and only if,  there exists  in this dependency  graph an edge
+that connects  directly the  two random  variables to  which they correspond.
+This is equivalent to writing that two neurons $i$ and $j$ are  not  directly
+connected  if and only if  $X_i$  and $X_j$  are  conditionally independent
+with  respect to all  other variables. We remind  that two random  variables
+$X_i$  and  $X_j$  are  said  to  be  conditionally independent to a (possibly
+empty)  set of controlling random variables $Z$, denoted $X_i \perp X_j | Z$,
+if the joint conditional probability distribution   $P_{X_i,  X_j   |   Z}$
+factorizes  into   $P_{X_i|Z} P_{X_j|Z}$.  In particular,  when  $X_i$ and
+$X_j$ are  conditionally independent  with respect  to all  the other
+variables, denoted  $X_i \perp  X_j  | X^{-i,j}$,  then  the  observation  of
+$X_i$  given  the knowledge  of  $X^{-i,j}$ provides  no  information  about
+$X_j$,  and vice-versa.
+
+In the  particular case   where $P_X$ is  a joint  Gaussian distribution
+$\mathcal{N}(\mu; \Sigma)$ of mean  vector $\mu$ and covariance matrix
+$\Sigma$, $X_i$  and $X_j$ are conditionally  independent with respect to   the
+other   variables   $X^{-i,j}$   if  their   \textit{partial   correlation}
+statistic is null~\citep{baba2004partial}, i.e., if
 \begin{equation}
@@
 Conversely, $X_i$ and $X_j$ are conditionally dependent if $\rho_{X_i, X_j |
-X^{-i,j}} \neq 0$, where $\rho_{X_i, X_j | X^{-i,j}} \in [-1;1]$ can now be
-interpreted as the degree of association between the two variables (i.e., the larger the
-value, the stronger the interaction). In practice due to the finite size of
-time series, noise and modeling assumptions, the partial correlation
-$\rho_{X_i, X_j | X^{-i,j}}$ will never be zero. If instead of a degree
-of association, one would want to infer the underlying graph a statistical
-test would be required to assert conditional independences. Note also that
-the partial correlation
-statistic is symmetric (i.e., $\rho_{X_i, X_j | X^{-i,j}} = \rho_{X_j, X_i |
-X^{-j,i}}$) and therefore does not account for the direction of the
-interaction. Together, the partial correlation statistics correspond to the
-inverse $\Sigma^{-1}$ of the covariance matrix, also known as the concentration
-or precision matrix. Computationally, they can be estimated efficiently in
-$O(M^3)$ (instead of $O(p^3)$) from the $M$ first principal components
-extracted through PCA~\citep{bishop2006pattern} on the processed data. In our
-experiments, $M$ is set to $0.8 p$, thereby allowing us to further filter the
-the data by removing the contribution of principal components
-likely due to noise.
+X^{-i,j}} \neq 0$, where $\rho_{X_i, X_j | X^{-i,j}} \in [-1;1]$. Note that the
+larger the value of this term, the stronger the dependence between variables
+$X_i$ and $X_j$.
+
+Our approach implicitly makes the additional assumption  that $P_x$ is  a joint
+Gaussian distribution since it  outputs as  degree of association between two
+neurons $i$ and $j$ an estimate of $\rho_{X_i, X_j | X^{-i,j}}$. Note also that
+the partial correlation statistic is symmetric  (i.e., $\rho_{X_i, X_j |
+X^{-i,j}} = \rho_{X_j, X_i | X^{-j,i}}$) and therefore does not account for the
+direction of the interaction.
+
+We detail now our procedure for estimating $\rho_{X_i, X_j | X^{-i,j}}$ from
+the data. The partial correlation statistics is computed through the inverse
+$\Sigma^{-1}$ of the covariance matrix $\Sigma$, also known as the
+concentration or precision matrix. Computationally, they can be estimated
+efficiently in $O(M^3)$ (instead of $O(p^3)$) from the $M$ first principal
+components extracted through PCA~\citep{bishop2006pattern} on the processed
+data. In our experiments, $M$ is set to $0.8 p$, thereby allowing us to further
+filter the the data by removing the contribution of principal components likely
+due to noise.
 
@@
 all other variables, we compare in Section~\ref{sec:results} with the
-\textit{Pearson correlation} statistics, which measure instead the linear dependence
-between variables, independently of the others. Accordingly, $X_i$ and $X_j$ are
-independent if their Pearson correlation statistic is zero, that is if
+\textit{Pearson correlation} statistics, which measure instead the linear
+dependence between variables, independently of the others. Accordingly, $X_i$
+and $X_j$ are independent if their Pearson correlation statistic is zero, that
+is if
 \begin{equation}

### 2014-06-23 article.tex
DE comments

@@
 
+% check dependency map => minimal d-map with distribution?
 To a joint probability distribution $P_X$ corresponds a minimal dependency
@@
 $\Sigma$, $X_i$  and $X_j$ are conditionally  independent with respect to the
-other   variables   $X^{-i,j}$   if  their   \textit{partial   correlation}
-statistic is null~\citep{baba2004partial}, i.e., if
+other variables $X^{-i,j}$ if their \textit{partial correlation} statistic is
+null~\citep{baba2004partial}, i.e., if
 \begin{equation}
@@
 
-Our approach implicitly makes the additional assumption  that $P_x$ is  a joint
+Our approach implicitly makes the additional assumption  that $P_X$ is  a joint
 Gaussian distribution since it  outputs as  degree of association between two
@@
 We detail now our procedure for estimating $\rho_{X_i, X_j | X^{-i,j}}$ from
-the data. The partial correlation statistics is computed through the inverse
+the data. \textcolor{red}{DE finds that this sections is too complicated}
+The partial correlation statistics is computed through the inverse
 $\Sigma^{-1}$ of the covariance matrix $\Sigma$, also known as the

### 2014-06-24 article.tex
DE comments on the filter section

@@
 
-As the Figure~\ref{fig:original_curve} illustrates, the raw
+As the Figure~\ref{fig:original_curve} shows, the raw
 fluorescence signal is very noisy due to light scattering artifacts that
@@
 % asymmetrical weighted median
-f_2(x^t_i) &= 0.4 x^{t-3}_i + 0.6 x^{t-2}_i + 0.8 x^{t-1}_i + x_i^t,
+f_2(x^t_i) &= 0.4 x^{t-3}_i + 0.6 x^{t-2}_i + 0.8 x^{t-1}_i + x_i^t.
 \label{eq:weighted-asymetric-median}
 \end{align}
-where $f_1$ effect is shown in Figure \ref{fig:lp_curve}.
+For the sake of illustration, the effect of the filter $f_1$ on the signal
+is shown in Figure \ref{fig:lp_curve}.
 
-Neurons communicates through short peaks, characterized by a high
-frequency, while low frequencies of the signal corresponds to the slow
+Neurons communicate through short spikes, characterized by a high
+frequency, while low frequencies of the signal correspond to the slow
 decay of fluorescence. The second step of our pipeline consists in
-identifying neuron spikes by filtering out
-low frequencies through a high-pass filter, resulting in the plot of
-Figure \ref{fig:hp_curve}:
+a high-pass filter that transforms the time series into its backward
+difference
 \begin{align}
-g(x^{t}_{i}) &= x^{t}_i - x^{t-1}_i. \label{eq:high-pass-filter}
+g(x^{t}_{i}) &= x^{t}_i - x^{t-1}_i. \label{eq:high-pass-filter},
 \end{align}
+resulting in the plot of Figure \ref{fig:hp_curve}:
 
-Once the low- and and high-pass filters have been applied, the remaining signal
-corresponds to the finite backward difference of the fluorescence time series.
 To further filter out small signal variations, mostly due to noise, the third
-step consists in a  hard-threshold filter, yielding the Figure
-\ref{fig:threshold_curve}:
+step consists in a  hard-threshold filter
 \begin{align}
-h(x^{t}_i) &= x^{t}_i \mathbb{1}(x^{t}_i \geq \tau) \text{ with } \tau > 0.
+h(x^{t}_i) &= x^{t}_i \mathbb{1}(x^{t}_i \geq \tau) \text{ with } \tau > 0,
 \end{align}
+yielding the Figure \ref{fig:threshold_curve}.
 
@@
 % check dependency map => minimal d-map with distribution?
+\textcolor{red}{This part is better, however there is still something
+wrong with the theory.}
 To a joint probability distribution $P_X$ corresponds a minimal dependency

### 2014-06-24 article.tex
link between min dep graph and G

--- 2014-06-23 article.tex
@@
 
-Our approach implicitly makes the additional assumption  that $P_X$ is  a joint
-Gaussian distribution since it  outputs as  degree of association between two
-neurons $i$ and $j$ an estimate of $\rho_{X_i, X_j | X^{-i,j}}$. Note also that
-the partial correlation statistic is symmetric  (i.e., $\rho_{X_i, X_j |
-X^{-i,j}} = \rho_{X_j, X_i | X^{-j,i}}$) and therefore does not account for the
-direction of the interaction.
+Our approach implicitly makes the additional assumption  that $P_X$ is  a
+joint Gaussian distribution since it  outputs as  degree of association
+between two neurons $i$ and $j$ an estimate of $\rho_{X_i, X_j | X^{-i,j}}$.
+Moreover, this minimal dependency graph will be close to G undirected
+especially as this assumption is true. Note also that the partial correlation
+statistic is symmetric  (i.e., $\rho_{X_i, X_j | X^{-i,j}} = \rho_{X_j, X_i |
+X^{-j,i}}$) and therefore does not account for the direction of the
+interaction without impacting the performance. The interest to not consider directivity will be discussed in section~\ref{sec:results}.
 

### 2014-06-24 article.tex
modified
modifs DE

@@
 
-As the Figure~\ref{fig:original_curve} shows, the raw
+As Figure~\ref{fig:original_curve} shows, the raw
 fluorescence signal is very noisy due to light scattering artifacts that
-ordinarily affects the quality of the recording~\citep{lichtman2011big}.
+ordinarily affect the quality of the recording~\citep{lichtman2011big}.
 Accordingly, the first step of our pipeline is to smoothen the signal, using
-one the following low-pass filter for filtering out high frequency noise :
+one the following low-pass filter for filtering out high frequency noise:
 \begin{align}
@@
 
-Neurons communicate through short spikes, characterized by a high
+\textcolor{red}{connection}Neurons communicate through short spikes, characterized by a high
 frequency, while low frequencies of the signal correspond to the slow
-decay of fluorescence. The second step of our pipeline consists in
-a high-pass filter that transforms the time series into its backward
+decay of fluorescence. To have a signal that only has high magnitude around instances where the spikes occur, the second step of our pipeline transforms the time series into its backward
 difference
 \begin{align}
-g(x^{t}_{i}) &= x^{t}_i - x^{t-1}_i. \label{eq:high-pass-filter},
+g(x^{t}_{i}) &= x^{t}_i - x^{t-1}_i \label{eq:high-pass-filter},
 \end{align}
-resulting in the plot of Figure \ref{fig:hp_curve}:
+shown in the plot of Figure \ref{fig:hp_curve}:
 
-To further filter out small signal variations, mostly due to noise, the third
-step consists in a  hard-threshold filter
+To filter out small signal variations in the signal obtained after applying the function $g$ as well as to eliminate negative values, we use the following hard-threshold filter
 \begin{align}

### 2014-06-24 article.tex
checkpoint

@@
 yielding the Figure \ref{fig:threshold_curve}.
+As we can see, the processed signal only contains clean spikes.
 
-At this step, the processed signal only contains clean spikes. However, when a
-large part of the network is firing, detecting pairwise neuron interactions is
-a difficult task. Furthermore, it is even possible that neurons spike because
-of a global high activity, without any actual cause (see
-\cite{stetter2012model}). Accordingly, in order to reduce false interaction
-detection, peak intensities at time $t$ are regularized by the global activity
-of all neurons, thereby reducing the importance of peaks identified during
-global high activity periods:
+The last step of our filtering procedure has for objective to decrease the importance of spikes that occur when there is a high global activity in the network with respect to  spikes that occur during normal activity.
+Indeed, we have conjectured that when a large part of the network is firing, the rate at which observations are made is not high enough for being able to detect interactions and, that it would therefore be preferrable to lower their importance by changing appropriatly their magnitude.
+Additionnally, it is well-known that neurons may also spike because of a global high activity (see \cite{stetter2012model}).
+In such  context, detecting pairwise neuron interactions from the firing activity is meaningless.
+Accordingly, we have chosen to apply to the signal outputted by $h$ the following function  
 \begin{align}
@@
 \end{align}
+that has for effect to magnify the importance of spikes that occur in case of low global activity.
 
-In those terms, the full signal processing pipeline of our (simplified)
+To summarize, the full signal processing pipeline of our (simplified)
 approach is defined by the composed function $w \cdot h \cdot g \cdot f_1$
-(resp. $f_2$) and results in the plot of Figure \ref{fig:weight_curve}.
+(resp. $f_2$). When applied to the raw signal (shown on Figure \ref{fig:original_curve}), it outputs the signal shown on Figure \ref{fig:weight_curve}.
 

### 2014-06-24 article.tex
checkpoint

@@
 
-% check dependency map => minimal d-map with distribution?
-\textcolor{red}{This part is better, however there is still something
-wrong with the theory.}
-To a joint probability distribution $P_X$ corresponds a minimal dependency
-graph. Each node of this graph is a random variable. Two random variables are
-only connected if they are dependent. We consider that two neurons are
+To a joint probability distribution $P_X$ corresponds a
+graph where (i) each node is a random variable and (ii) two nodes are
+only connected if they correspond to two dependent variables. We consider that two neurons are
 connected if  and only if,  there exists  in this dependency  graph an edge
 that connects  directly the  two random  variables to  which they correspond.
-This is equivalent to writing that two neurons $i$ and $j$ are  not  directly
+In this context, it is equivalent to writing that two neurons $i$ and $j$ are  not  directly
 connected  if and only if  $X_i$  and $X_j$  are  conditionally independent
@@
 \begin{equation}
-\rho_{X_i, X_j | X^{-i,j}} = -\frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii} \Sigma^{-1}_{jj}}} = 0.
+\rho_{X_i, X_j | X^{-i,j}} = -\frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii} \Sigma^{-1}_{jj}}} = 0 \label{eq:inverse}
 \end{equation}
+where $\Sigma^{-1}$ is also known as the precision matrix or concentration. 
 Conversely, $X_i$ and $X_j$ are conditionally dependent if $\rho_{X_i, X_j |
@@
 between two neurons $i$ and $j$ an estimate of $\rho_{X_i, X_j | X^{-i,j}}$.
-Moreover, this minimal dependency graph will be close to G undirected
-especially as this assumption is true. Note also that the partial correlation
+Note also that the partial correlation
 statistic is symmetric  (i.e., $\rho_{X_i, X_j | X^{-i,j}} = \rho_{X_j, X_i |
-X^{-j,i}}$) and therefore does not account for the direction of the
-interaction without impacting the performance. The interest to not consider directivity will be discussed in section~\ref{sec:results}.
+X^{-j,i}}$).
+Therefore, our approach cannot identify the direction of the interaction.
+We will see why this only affects slightly its performances, with respect to the metric used in the Connectomics challenge, in Section~\ref{sec:results}.
 
-We detail now our procedure for estimating $\rho_{X_i, X_j | X^{-i,j}}$ from
-the data. \textcolor{red}{DE finds that this sections is too complicated}
-The partial correlation statistics is computed through the inverse
-$\Sigma^{-1}$ of the covariance matrix $\Sigma$, also known as the
-concentration or precision matrix. Computationally, they can be estimated
-efficiently in $O(M^3)$ (instead of $O(p^3)$) from the $M$ first principal
-components extracted through PCA~\citep{bishop2006pattern} on the processed
-data. In our experiments, $M$ is set to $0.8 p$, thereby allowing us to further
-filter the the data by removing the contribution of principal components likely
-due to noise.
+We detail now our procedure for estimating partial correlation statistics ($\rho_{X_i, X_j | X^{-i,j}}$) from
+the data.
+Besides the straightforward computation, a natural procedure for estimating this precision matrix is first computing an empirical estimation of the covariance matrix and then taking the inverse, applying equation \ref{eq:inverse}.
+Yet, an approximation can be obtained by only considering the first $M$principal components.
+Notice that we could have expected that a approximation of the inverse would have degraded the performance.
+However, the opposite was observed.
+We conjecture that by only taking into account the $M$ principal components filter out noise.
+In our experiments, $M$ is set to $0.8p$ (see discussion in Appendix~\ref{app:REF} \textcolor{red}{REF}).
+
+% Computationally, they can be estimated
+% % efficiently in $O(M^3)$ (instead of $O(p^3)$) 
+% from the $M$ first principal
+% components extracted through PCA~\citep{bishop2006pattern} on the processed
+% data. While speeding up computation, it allows to further 
+% filter the the data by removing the contribution of components that are respectively
+% due to redundancy or noise, i.e., with an eigen value respectively is equal to zero or close to zero.
 
@@
 dependence between variables, independently of the others. Accordingly, $X_i$
-and $X_j$ are independent if their Pearson correlation statistic is zero, that
+and $X_j$ are independent, without any conditioning, if their Pearson correlation statistic is zero, that
 is if

### 2014-06-24 article.tex
some modifs

@@
 graph where (i) each node is a random variable and (ii) two nodes are
-only connected if they correspond to two dependent variables. We consider that two neurons are
-connected if  and only if,  there exists  in this dependency  graph an edge
+only connected if they correspond to two dependent variables. We assume that two neurons are
+connected if  and only if,  there exists  in this  graph an edge
 that connects  directly the  two random  variables to  which they correspond.
@@
 \begin{equation}
-\rho_{X_i, X_j | X^{-i,j}} = -\frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii} \Sigma^{-1}_{jj}}} = 0 \label{eq:inverse}
+\rho_{X_i, X_j | X^{-i,j}} = -\frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii} \Sigma^{-1}_{jj}}} = 0, \label{eq:inverse}
 \end{equation}
-where $\Sigma^{-1}$ is also known as the precision matrix or concentration. 
+where $\Sigma^{-1}$ is known as the precision or concentration matrix. 
 Conversely, $X_i$ and $X_j$ are conditionally dependent if $\rho_{X_i, X_j |
@@
 Therefore, our approach cannot identify the direction of the interaction.
-We will see why this only affects slightly its performances, with respect to the metric used in the Connectomics challenge, in Section~\ref{sec:results}.
+We will see in Section~\ref{sec:results} why this only affects slightly its performances, with respect to the metric used in the Connectomics challenge.
 
-We detail now our procedure for estimating partial correlation statistics ($\rho_{X_i, X_j | X^{-i,j}}$) from
-the data.
-Besides the straightforward computation, a natural procedure for estimating this precision matrix is first computing an empirical estimation of the covariance matrix and then taking the inverse, applying equation \ref{eq:inverse}.
-Yet, an approximation can be obtained by only considering the first $M$principal components.
-Notice that we could have expected that a approximation of the inverse would have degraded the performance.
-However, the opposite was observed.
-We conjecture that by only taking into account the $M$ principal components filter out noise.
-In our experiments, $M$ is set to $0.8p$ (see discussion in Appendix~\ref{app:REF} \textcolor{red}{REF}).
+We now detail  our procedure for estimating partial correlation statistics
+($\rho_{X_i, X_j | X^{-i,j}}$) from the data.
+It first estimates the covariance matrix from the data.
+Afterwards, it computes the exact inverse of this matrix, from which it infers the value of $\rho_{X_i, X_j | X^{-i,j}}$ using  equation (\ref{eq:inverse}).
+Note that we have also experimented procedures where the exact inverse was replaced by an approximation of it using only the $M$ principal components of $\Sigma$~\citep{bishop2006pattern} whose associated eigen values were significantly higher than zero.
+Such an approximation is equivalent to assume that the firing activity of all neurons can be explained by only a subset of them whose size is equal to $M$.
+We observed that those procedures were often leading to better results.
+Note that we found out by running expriments that the number $M$ of principal components is around $0.8p$
+(see discussion in Appendix~\ref{app:REF}
+\textcolor{red}{REF}).
 
@@
 
+Finally, let us remark that performance of our simple method shows to be quite sensitive to the values of parameters (e.g., $f_1$ or
+$f_2$ or the value of the threshold $\tau$) in the combined function of the filering and infering processes. One approach, that we will refered to as \textit{Averaged
+Partial correlation} statistics, for improving its robustness is to average correlation statistics
+over various values of the parameters, thereby reducing the variance of its
+predictions. Further details are provided in
+Appendix~\ref{app:optimized}.
+
+\section{Experiments} \label{sec:results}
+
+\textcolor{red}{to incorporate: 
 To highlight the benefits of measuring the partial dependence conditional to
@@
 \rho_{X_i,X_j} = \frac{\Sigma_{ij}}{\sqrt{\Sigma_{ii} \Sigma_{jj}}} = 0.
-\end{equation}
-
-Finally, let us remark that performance shows to be quite sensitive to the
-choice of hyper-parameters in the signal processing pipeline (e.g., $f_1$ or
-$f_2$ or the value of the threshold $\tau$). To further improve robustness, the
-last step of our method therefore consists in averaging correlation statistics
-over various values of the parameters, thereby reducing the variance of our
-predictions. In this case, the method is referred to as \textit{Averaged
-Partial correlation} statistics. Further details are provided in
-Appendix~\ref{app:optimized}.
-
-\section{Experiments} \label{sec:results}
+\end{equation}}
 

### 2014-06-24 article.tex
values for GENIE3

@@
 Pearson correlation    & 0.886 & 0.884 & 0.891 & 0.877 & 0.153 & 0.145 & 0.170 & 0.132 \\
-GENIE3 (depth = 1)     & 0.878 & & & & 0.184 & & & \\
-GENIE3 (depth = 2)     & 0.889 & & & & 0.217 & & & \\
-GENIE3 (depth = 3)     & & & & & & & & \\
+GENIE3 (depth = 1)     & 0.878 & 0.877 & 0.873 & 0.873 & 0.184 & 0.173 & 0.182& 0.172\\
+GENIE3 (depth = 2)     & 0.889 & 0.888 & 0.883 & 0.884* & 0.217 & 0.210 & 0.220 & 0.199* \\
+GENIE3 (depth = 3)     & 0.892 & 0.891* & 0.887 & 0.887 & 0.232 & 0.226* & 0.237 & 0.215\\
 GTE                    & 0.890 & 0.893 & 0.894 & 0.873 & 0.171 & 0.174 & 0.197 & 0.142 \\
@@
 \end{tabular}
-\caption{TODO}
+\caption{TODO (* means not 10000 trees but more than 9500, to be solved.) }
 \label{tab:tab1}

### 2014-06-25 article.tex
adjust global regularization and first part of appendix

@@
 
-\begin{abstract} In this work, we propose a simple, but yet efficient,
-methodologically motivated method for the problem of connectome inference in
+\begin{abstract} In this work, we propose a simple, but yet efficient, method for the problem of connectome inference in
 calcium imaging data. The proposed algorithm is made of two steps. First,
@@
 
-\textcolor{red}{connection}Neurons communicate through short spikes, characterized by a high
-frequency, while low frequencies of the signal correspond to the slow
+Furthermore, it can be observed that neurons communicate through short spikes, characterized by a high
+frequency, while low frequencies of the signal mainly correspond to the slow
 decay of fluorescence. To have a signal that only has high magnitude around instances where the spikes occur, the second step of our pipeline transforms the time series into its backward
@@
 that has for effect to magnify the importance of spikes that occur in case of low global activity.
+Note that the particular case where $\sum_{j} x^{t}_j$ equals $0$ is solved by setting $w(x^{t}_i) = 1$.
 
@@
 
+Sections~\ref{sec:filter}~to~\ref{sec:results} describe a simplified version
+of the actual winning method. However, one could be interesting in the full
+description. This appendix will therefore follow the progress of the main
+paper highlighting optimizations.
+
+Let us remark that parameter value choices were made to maximize ROC AUC score
+on \textit{normal-1} and, to a lesser extent, \textit{normal-4}.
+
+\subsection*{Signal processing}
+
+As we introduce a composed function in section~\ref{sec:filter}, let us describe a new composed function with optimized filters to improve the quality of the inference process.
+
+Besides filters
+$f_1$ and $f_2$ respectively defined by equations \ref{eq:symetric-median} and \ref{eq:weighted-asymetric-median}, we also consider two other low-pass
+filters:
+
+\begin{align}
+f_3(x^t_i) &= x^{t-1}_i + x^{t}_i + x^{t+1}_i + x^{t+2}_i \label{eq:asymetric-median-forward}, \\
+f_4(x^t_i) &= x^{t+3}_i + x^{t+2}_i + x^{t+1}_i + x_i^t.
+\label{eq:asymetric-median}
+\end{align}
+
+Theses filters, even if individually they lead to less good performances of the inference algorithm than filters $f_1$ and
+$f_2$, the averaging approach over these four low-pass
+filters gets better.
+
+As a computation trick, it appears that using a parametrized hard-threshold filter slighlty improves performances.
+Introducing the parameter $c$ in function $h$ yields to an optimized filter denoted as $h^*$
+\begin{align}
+h^*(x^t_i) = (x_i^t)^c \text{ } \mathbb{1}(x_i^t \ge \tau) \text{ with } \tau > 0,
+\end{align}
+where $c$ is set to $0.9$ after experiments.
+
+The magnification can also be optimized by adjusting the effect differently with respect to the global activity. In that sense, we introduce the following function 
+\begin{align}
+ w^*(x^{t}_i) &= {(x^{t}_i + 1 )^{\left (1 + \frac{1}{\sum_{j} x^{t}_j}\right )}}^{m}
+\end{align}
+where $m$ depends on the low-pass filter and on the range of the global activity. We refer to our implemetation, available on ... , for the values of the parameters and especially the parameter $m$.
+
+\subsection*{Averaging the connectome inference from partial correlation statistics}
+
+\subsection*{Connectome inference from pairwise interaction statistics}
+
+% NEXT APPENDIX SECTION 
+% SUPPLEMENTARY RESULTS
+% EXPLAIN EACH TAB AND VERIFY THE EXACTITUDE - RUN OPTIMIZED VERSION ON low-noise, ... ?
+%
+
+% EXPLAIN PCA - FIG
+
+\vspace{5cm}
+
 The algorithm propose in sections \ref{sec:filter} and \ref{sec:inference} has been optimized at its extreme limit to win the challenge.

### 2014-06-26 article.tex
modif section 2 et 3

--- 2014-06-24 article.tex
@@
 fluorescence data. More specifically, time series are processed using standard
-signal processing filters in order to remove noise due light scattering
+signal processing filters in order to remove noise due to light scattering
 effects, account for fluorescence  low decay and reduce the importance of
-global high activity in the network. The overall process is illustrated on
+global high activity in the network. The overall process is illustrated in
 Figure~\ref{fig:filtered-signal}.
@@
 Accordingly, the first step of our pipeline is to smoothen the signal, using
-one the following low-pass filter for filtering out high frequency noise:
+one of the following low-pass filters for filtering out high frequency noise:
 \begin{align}
@@
 
-\textcolor{red}{connection}Neurons communicate through short spikes, characterized by a high
+Neurons communicate through short spikes, characterized by a high
 frequency, while low frequencies of the signal correspond to the slow
-decay of fluorescence. To have a signal that only has high magnitude around instances where the spikes occur, the second step of our pipeline transforms the time series into its backward
+decay of fluorescence. To have a signal that only has high magnitude around instants where the spikes occur, the second step of our pipeline transforms the time series into its backward
 difference
@@
 
-To filter out small signal variations in the signal obtained after applying the function $g$ as well as to eliminate negative values, we use the following hard-threshold filter
+To filter out small variations in the signal obtained after applying the function $g$ as well as to eliminate negative values, we use the following hard-threshold filter
 \begin{align}
@@
 
-The last step of our filtering procedure has for objective to decrease the importance of spikes that occur when there is a high global activity in the network with respect to  spikes that occur during normal activity.
+The objective of the last step of our filtering procedure is to decrease the importance of spikes that occur when there is a high global activity in the network with respect to  spikes that occur during normal activity.
 Indeed, we have conjectured that when a large part of the network is firing, the rate at which observations are made is not high enough for being able to detect interactions and, that it would therefore be preferrable to lower their importance by changing appropriatly their magnitude.
@@
 \end{align}
-that has for effect to magnify the importance of spikes that occur in case of low global activity.
+which effect is to magnify the importance of spikes that occur in case of low global activity (measured by $\sum_{j} x^{t}_j$).
 
-To summarize, the full signal processing pipeline of our (simplified)
-approach is defined by the composed function $w \cdot h \cdot g \cdot f_1$
-(resp. $f_2$). When applied to the raw signal (shown on Figure \ref{fig:original_curve}), it outputs the signal shown on Figure \ref{fig:weight_curve}.
+To summarize, the full signal processing pipeline of our simplified (resp. tuned)
+approach is defined by the composed function $w \circ h \circ g \circ f_1$
+(resp. $f_2$). When applied to the raw signal of Figure \ref{fig:original_curve}, it outputs the signal shown in Figure \ref{fig:weight_curve}.
 
@@
 
-Our  connection inference  procedure  relies  on several  assumptions. First,
-we will assume that  the fluorescence concentrations of all $p$ neurons can be
-modeled as a set of random variables $X = \{X_1, \dots, X_p\}$  that are drawn
-from a time invariant joint  probability distribution $P_X$. Or, say otherwise,
-we assume that there exists a probability distribution $P_X$ such that the
-fluorescence concentrations at a particular time $t$ can be seen as an
-independent realization of $P_X$.
+% No time assumption
 
-To a joint probability distribution $P_X$ corresponds a
-graph where (i) each node is a random variable and (ii) two nodes are
-only connected if they correspond to two dependent variables. We assume that two neurons are
-connected if  and only if,  there exists  in this  graph an edge
-that connects  directly the  two random  variables to  which they correspond.
-In this context, it is equivalent to writing that two neurons $i$ and $j$ are  not  directly
-connected  if and only if  $X_i$  and $X_j$  are  conditionally independent
-with  respect to all  other variables. We remind  that two random  variables
-$X_i$  and  $X_j$  are  said  to  be  conditionally independent to a (possibly
-empty)  set of controlling random variables $Z$, denoted $X_i \perp X_j | Z$,
-if the joint conditional probability distribution   $P_{X_i,  X_j   |   Z}$
-factorizes  into   $P_{X_i|Z} P_{X_j|Z}$.  In particular,  when  $X_i$ and
-$X_j$ are  conditionally independent  with respect  to all  the other
-variables, denoted  $X_i \perp  X_j  | X^{-i,j}$,  then  the  observation  of
-$X_i$  given  the knowledge  of  $X^{-i,j}$ provides  no information  about
-$X_j$,  and vice-versa.
+Our procedure to infer connections between neurons first assumes that
+the (filtered) fluorescence concentrations of all $p$ neurons at each
+time point can be modeled as a set of random variables $X = \{X_1,
+\dots, X_p\}$ that are idependently drawn from the same time invariant
+joint probability distribution $P_X$. %% Or, say otherwise, we assume
+%% that there exists a probability distribution $P_X$ such that the
+%% fluorescence concentrations at a particular time $t$ can be seen as an
+%% independent realization of $P_X$.
+As a consequence, our inference method does not exploit the time
+ordering of the observations (although time ordering is exploited by
+the filters).
 
-In the  particular case where $P_X$ is  a joint  Gaussian distribution
-$\mathcal{N}(\mu; \Sigma)$ of mean  vector $\mu$ and covariance matrix
-$\Sigma$, $X_i$  and $X_j$ are conditionally  independent with respect to the
-other variables $X^{-i,j}$ if their \textit{partial correlation} statistic is
-null~\citep{baba2004partial}, i.e., if
+% partial correlation: definition + motivation
+
+Given this assumption, we then propose to use as a measure of the
+strength of the connection between two neurons $i$ and $j$, the
+partial correlation coefficient $p_{i,j}$ between their corresponding
+random variables $X_i$ and $X_j$, defined by \cite{}:
 \begin{equation}
-\rho_{X_i, X_j | X^{-i,j}} = -\frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii} \Sigma^{-1}_{jj}}} = 0, \label{eq:inverse}
+p_{i,j} =
+-\frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii} \Sigma^{-1}_{jj}}}, \label{eq:inverse},
 \end{equation}
-where $\Sigma^{-1}$ is known as the precision or concentration matrix. 
-Conversely, $X_i$ and $X_j$ are conditionally dependent if $\rho_{X_i, X_j |
-X^{-i,j}} \neq 0$, where $\rho_{X_i, X_j | X^{-i,j}} \in [-1;1]$. Note that the
-larger the value of this term, the stronger the dependence between variables
-$X_i$ and $X_j$.
+where $\Sigma^{-1}$, known as the precision or concentration matrix, is the inverse of the covariance matrix $\Sigma$ of $X$.%%  Partial
+%% correlation can be interpreted in several ways. The partial
+%% correlation coefficient $p_{i,j}$ can be shown to measure the
+%% correlation between $X_i$ and $X_j$ when they are corrected for the
+%% (linear) effect of all other variables in $X$ \cite{}.
+Assuming that the distribution $P_X$ is a multivariate Gaussian
+distribution ${\cal N}(\mu,\Sigma)$, it can be shown that $p_{i,j}$ is
+zero if and only if $X_i$ and $X_j$ are independent given all other
+variables in $X$, ie. $X_i \perp X_j|X^{-i,j}$ where $X^{-i,j}= X
+\setminus\{X_i,X_j\}$. Partial correlation thus measures conditional
+dependencies between variables. As an association measures between
+neurons, it should thus naturally only detect direct associations
+between neurons and filter out spurious indirect effects. The interest
+of partial correlation as an association measure has already been
+shown for the inference of gene regulatory networks \cite{xxx}.
+%% Given a set of multivariate Gaussian
+%% random variables $X$, the (undirected) graph that connects all pairs
+%% of variables $X_i$ and $X_j$ such that $p_{i,j}\neq 0$ is called a
+%% Gaussian graphical models (GGMs). Because it measures conditional
+%% dependencies, partial correlation should naturally only detect direct
+%% associations between neurons. The superiority of partial correlation
+%% over standard correlation as an association measure have already been
+%% shown in the context of the inference of gene regulatory networks from
+%% gene expression data \cite{}. We will compare both measures in Section
+%% \ref{sec:results}.
+Note that the partial correlation statistic is symmetric
+(i.e. $p_{i,j}=p_{j,i}$). Therefore, our approach cannot identify the
+direction of the interactions between neurons. We will see in
+Section~\ref{sec:results} why this only affects slightly its
+performances, with respect to the metric used in the Connectomics
+challenge.
 
-Our approach implicitly makes the additional assumption  that $P_X$ is  a
-joint Gaussian distribution since it  outputs as degree of association
-between two neurons $i$ and $j$ an estimate of $\rho_{X_i, X_j | X^{-i,j}}$.
-Note also that the partial correlation
-statistic is symmetric  (i.e., $\rho_{X_i, X_j | X^{-i,j}} = \rho_{X_j, X_i |
-X^{-j,i}}$).
+Practically, the computation of coefficient $p_{i,j}$ using Equation
+\ref{ref} requires the estimation of the covariance matrix $\Sigma$
+and then computing its inverse. Given that we have typically more
+samples than neurons, the covariance matrix can be inverted in a
+straightforward way. We nevertheless obtained some improvement by
+replacing the exact inverse with an approximation using only the $M$
+first principal components of $\Sigma$~\citep{bishop2006pattern} (with
+$M$ set to $0.8 p$ in our experiments).
+
+Finally, let us remark that performance of our simple method shows to
+be quite sensitive to the values of parameters (e.g., $f_1$ or $f_2$
+or the value of the threshold $\tau$) in the combined function of the
+filtering and infering processes. One approach, that we will refered
+to as \textit{Averaged Partial correlation} statistics, for improving
+its robustness is to average correlation statistics over various
+values of the parameters, thereby reducing the variance of its
+predictions. Further details about parameter selection are provided in
+Appendix~\ref{app:optimized}.
+
+% Note on directionality
+
+%% Our  connection inference  procedure  relies  on several  assumptions. First,
+%% we will assume that  the fluorescence concentrations of all $p$ neurons can be
+%% modeled as a set of random variables $X = \{X_1, \dots, X_p\}$  that are drawn
+%% from a time invariant joint  probability distribution $P_X$. Or, say otherwise,
+%% we assume that there exists a probability distribution $P_X$ such that the
+%% fluorescence concentrations at a particular time $t$ can be seen as an
+%% independent realization of $P_X$.
+
+%% To assess the presence of a connection between two neurons, we will
+%% use partial correlation statistics, which has been used extensively
+%% for the inference of gene regulatory networks \cite{}.
+
+%% To a joint probability distribution $P_X$ corresponds a
+%% graph where (i) each node is a random variable and (ii) two nodes are
+%% only connected if they correspond to two dependent variables. We assume that two neurons are
+%% connected if  and only if,  there exists  in this  graph an edge
+%% that connects  directly the  two random  variables to  which they correspond.
+%% In this context, it is equivalent to writing that two neurons $i$ and $j$ are  not  directly
+%% connected  if and only if  $X_i$  and $X_j$  are  conditionally independent
+%% with  respect to all  other variables. We remind  that two random  variables
+%% $X_i$  and  $X_j$  are  said  to  be  conditionally independent to a (possibly
+%% empty)  set of controlling random variables $Z$, denoted $X_i \perp X_j | Z$,
+%% if the joint conditional probability distribution   $P_{X_i,  X_j   |   Z}$
+%% factorizes  into   $P_{X_i|Z} P_{X_j|Z}$.  In particular,  when  $X_i$ and
+%% $X_j$ are  conditionally independent  with respect  to all  the other
+%% variables, denoted  $X_i \perp  X_j  | X^{-i,j}$,  then  the  observation  of
+%% $X_i$  given  the knowledge  of  $X^{-i,j}$ provides  no information  about
+%% $X_j$,  and vice-versa.
+
+%% In the  particular case where $P_X$ is  a joint  Gaussian distribution
+%% $\mathcal{N}(\mu; \Sigma)$ of mean  vector $\mu$ and covariance matrix
+%% $\Sigma$, $X_i$  and $X_j$ are conditionally  independent with respect to the
+%% other variables $X^{-i,j}$ if their \textit{partial correlation} statistic is
+%% null~\citep{baba2004partial}, i.e., if
+%% \begin{equation}
+%% \rho_{X_i, X_j | X^{-i,j}} = -\frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii} \Sigma^{-1}_{jj}}} = 0, \label{eq:inverse}
+%% \end{equation}
+%% where $\Sigma^{-1}$ is known as the precision or concentration matrix. 
+%% Conversely, $X_i$ and $X_j$ are conditionally dependent if $\rho_{X_i, X_j |
+%% X^{-i,j}} \neq 0$, where $\rho_{X_i, X_j | X^{-i,j}} \in [-1;1]$. Note that the
+%% larger the value of this term, the stronger the dependence between variables
+%% $X_i$ and $X_j$.
+
+%% Our approach implicitly makes the additional assumption  that $P_X$ is  a
+%% joint Gaussian distribution since it  outputs as degree of association
+%% between two neurons $i$ and $j$ an estimate of $\rho_{X_i, X_j | X^{-i,j}}$.
+%% Note also that the partial correlation
+%% statistic is symmetric  (i.e., $\rho_{X_i, X_j | X^{-i,j}} = \rho_{X_j, X_i |
+%% X^{-j,i}}$).
 Therefore, our approach cannot identify the direction of the interaction.
@@
 
-We now detail  our procedure for estimating partial correlation statistics
-($\rho_{X_i, X_j | X^{-i,j}}$) from the data.
-It first estimates the covariance matrix from the data.
-Afterwards, it computes the exact inverse of this matrix, from which it infers the value of $\rho_{X_i, X_j | X^{-i,j}}$ using  equation (\ref{eq:inverse}).
-Note that we have also experimented procedures where the exact inverse was replaced by an approximation of it using only the $M$ principal components of $\Sigma$~\citep{bishop2006pattern} whose associated eigen values were significantly higher than zero.
-Such an approximation is equivalent to assume that the firing activity of all neurons can be explained by only a subset of them whose size is equal to $M$.
-We observed that those procedures were often leading to better results.
-Note that we found out by running expriments that the number $M$ of principal components is around $0.8p$
-(see discussion in Appendix~\ref{app:REF}
-\textcolor{red}{REF}).
+%% We now detail our procedure for estimating partial correlation
+%% statistics ($\rho_{X_i, X_j | X^{-i,j}}$) from the data. It first
+%% estimates the covariance matrix from the data. Afterwards, it computes
+%% the exact inverse of this matrix, from which it infers the value of
+%% $\rho_{X_i, X_j | X^{-i,j}}$ using equation (\ref{eq:inverse}). Note
+%% that we have also experimented procedures where the exact inverse was
+%% replaced by an approximation of it using only the $M$ principal
+%% components of $\Sigma$~\citep{bishop2006pattern} whose associated
+%% eigen values were significantly higher than zero. Such an
+%% approximation is equivalent to assume that the firing activity of all
+%% neurons can be explained by only a subset of them whose size is equal
+%% to $M$. We observed that those procedures were often leading to better
+%% results. Note that we found out by running expriments that the number
+%% $M$ of principal components is around $0.8p$ (see discussion in
+%% Appendix~\ref{app:REF} \textcolor{red}{REF}).
 
-% Computationally, they can be estimated
-% % efficiently in $O(M^3)$ (instead of $O(p^3)$) 
-% from the $M$ first principal
-% components extracted through PCA~\citep{bishop2006pattern} on the processed
-% data. While speeding up computation, it allows to further 
-% filter the the data by removing the contribution of components that are respectively
-% due to redundancy or noise, i.e., with an eigen value respectively is equal to zero or close to zero.
-
-Finally, let us remark that performance of our simple method shows to be quite sensitive to the values of parameters (e.g., $f_1$ or
-$f_2$ or the value of the threshold $\tau$) in the combined function of the filering and infering processes. One approach, that we will refered to as \textit{Averaged
-Partial correlation} statistics, for improving its robustness is to average correlation statistics
-over various values of the parameters, thereby reducing the variance of its
-predictions. Further details are provided in
-Appendix~\ref{app:optimized}.
+%% % Computationally, they can be estimated
+%% % % efficiently in $O(M^3)$ (instead of $O(p^3)$) 
+%% % from the $M$ first principal
+%% % components extracted through PCA~\citep{bishop2006pattern} on the processed
+%% % data. While speeding up computation, it allows to further 
+%% % filter the the data by removing the contribution of components that are respectively
+%% % due to redundancy or noise, i.e., with an eigen value respectively is equal to zero or close to zero.
 
@@
 
-\textcolor{red}{to incorporate: 
-To highlight the benefits of measuring the partial dependence conditional to
-all other variables, we compare in Section~\ref{sec:results} with the
-\textit{Pearson correlation} statistics, which measure instead the linear
-dependence between variables, independently of the others. Accordingly, $X_i$
-and $X_j$ are independent, without any conditioning, if their Pearson correlation statistic is zero, that
-is if
-\begin{equation}
-\rho_{X_i,X_j} = \frac{\Sigma_{ij}}{\sqrt{\Sigma_{ii} \Sigma_{jj}}} = 0.
-\end{equation}}
+%% \textcolor{red}{to incorporate: 
+%% To highlight the benefits of measuring the partial dependence conditional to
+%% all other variables, we compare in Section~\ref{sec:results} with the
+%% \textit{Pearson correlation} statistics, which measure instead the linear
+%% dependence between variables, independently of the others. Accordingly, $X_i$
+%% and $X_j$ are independent, without any conditioning, if their Pearson correlation statistic is zero, that
+%% is if
+%% \begin{equation}
+%% \rho_{X_i,X_j} = \frac{\Sigma_{ij}}{\sqrt{\Sigma_{ii} \Sigma_{jj}}} = 0.
+%% \end{equation}}
 
 % Datasets
-To assess our method, we focus on the \textit{normal-2} dataset
-provided by the organizers of the Connectomics challenge. Experiments
-on \textit{normal-1, normal-3, normal-4} show similar trends to
-\textit{normal-2} and are presented in the Appendix \textcolor{red}{REF}.
-Those datasets have $p=1000$ time series of length $T=179500$ of image
-calcium from simulated neuronal networks \citep{stetter2012model}. Those
-networks have approximately 15000 edges.
+We have carried out experiments with our method on the
+\textit{normal}-1,2,3, and 4 datasets provided by the organizers of
+the Connectomics challenge. Each of these datasets contains $p=1000$
+time series of length $T=179500$ of image calcium from simulated
+neuronal networks \citep{stetter2012model}. The network to infer
+contains approximately 15000 edges, ie an edge density of about
+1.5\%. All inference methods compared here provides a ranking of
+neuron pairs according to some association score. To assess the
+quality of this ranking, we use both ROC and precision-recall curves,
+and we summarize them using the area under these curves, denoted
+respectively AUROC and AUPRC. Only the AUROC was used in the context of the connectomics to rThe AUROC was
+used to rank submissions to the challenge but the precision-recall
+curve has some\citep{schrynemackers2013protocols}
 
-% Metrics : ROC AUC and AUPRC
-In supervised learning terms, the network inference task can be viewed as a
-binary classification task where one has to correctly classify the presence or
-the absence of edges of the graph. We assess the accuracy of the network
-inference method using the area under the ROC curve (AUROC) and the area under
-the precision-recall curve (AUPRC) \citep{schrynemackers2013protocols}. Since
-neurons are not self-connected ($(i, i) \not \in E, \forall i \in V$) and some
-inference methods could give maximal scores to those edges, e.g. Pearson
-correlation, those elements are set to have minimal connectivity score prior
-assessment.
+Since neurons are
+not self-connected ($(i, i) \not \in E, \forall i \in V$) and some
+inference methods could give maximal scores to those edges,
+e.g. Pearson correlation, those elements are set to have minimal
+connectivity score prior assessment.
 
-The proposed approach is compared to Pearson correlation statistics (as
-described in Section~\ref{sec:inference}), generalized transfer entropy (GTE)
-and the GENIE3 algorithm.
+\paragraph{Effect of pre-processing}
+
+The top of Table \ref{} reports AUPR and AUROC for all four networks
+progressively introducing all filtering steps and for the last step,
+the PCA based matrix inversion. All steps improves performances, with
+the bigger improvement brought by the introduction of the
+... Interestingly, while PCA does not really have an impact of AUROC,
+it significantly increases the AUPR score.
+
+\paragraph{Comparison with other methods}
+
+Then, we compare our method with several other methods:
+\begin{itemize}
+\item Standard correlation coefficient...In this case, the
+  prefiltering the same as for partial correlation.
+\item \textbf{GTE} \citep{stetter2012model}, the baseline of the
+  challenge, which is based on transfer entrey measures for all pairs
+  of neurons $i$ and $j$ the reduction of uncertainty in predicting
+  future values of $i$ given the observation of the time series of the
+  neuron $j$ conditionally to the observation of past time series of
+  neuron $i$, whenever the average fluorescence is over a conditioning
+  level. Pre-processing and conditioning level were set to reproduce
+  baseline of the challenge.
+\item \textbf{GENIE3}\citep{huynhthu2010inferring}: This method is a
+  state-of-the-art gene network inference method \cite{dream5}. It
+  translates the the inference of the network of $p$ neurons into $p$
+  supervised learning tasks. For each task, the fluorescence of a
+  neuron is predicted from the fluorescence of all other neurons using
+  a tree based ensemble such as random forest
+  \citep{breiman2001random}. The tree ensemble associates a variable
+  importance score \citep{louppe2013understanding} to each neuron used
+  in the predictions, which is used as a degree of associate.
+To reduce the computational cost of the method, we nevertheless restrained all trees to a maximum tree depth of 3.
+This is likely to be detrimental The
+  following parameters are used $10000$ trees, $\log_2{p}$ variables
+  are randomly selected to split tree nodes and the maximal tree depth
+  is constrained to 1, 2 or 3. Note that unlike the other methods, this method provides asymetric scores, meaning it can potentially predict edge directions.
+\end{itemize}
+
+Bottom of table \ref{} shows the score of these methods. ROC and PR
+curves on normal-2 are shown in Figure ... Pearson correlation is the worst method
+
+\paragraph{ROC versus PR curves.} While only ROC was , we argue here that PR scores are more appropriate in this context.
+
+%% To assess our method, we focus on the \textit{normal-2} dataset
+%% provided by the organizers of the Connectomics challenge. Experiments
+%% on \textit{normal-1, normal-3, normal-4} show similar trends to
+%% \textit{normal-2} and are presented in the Appendix \textcolor{red}{REF}.
+%% Those datasets have $p=1000$ time series of length $T=179500$ of image
+%% calcium from simulated neuronal networks \citep{stetter2012model}. Each of these
+%% networks contains approximately 15000 edges.
+
+%% % Metrics : ROC AUC and AUPRC
+%% In supervised learning terms, the network inference task can be viewed as a
+%% binary classification task where one has to correctly classify the presence or
+%% the absence of edges of the graph. We assess the accuracy of the network
+%% inference method using the area under the ROC curve (AUROC) and the area under
+%% the precision-recall curve (AUPRC) \citep{schrynemackers2013protocols}.
+
+The proposed approach is compared to Pearson correlation statistics
+(as described in Section~\ref{sec:inference}), generalized transfer
+entropy (GTE) and the GENIE3 algorithm.
 \begin{itemize}

### 2014-06-26 article.tex

@@
 
-Neurons communicate through short spikes, characterized by a high
-frequency, while low frequencies of the signal correspond to the slow
-decay of fluorescence. To have a signal that only has high magnitude around instants where the spikes occur, the second step of our pipeline transforms the time series into its backward
+Furthermore, it can be observed that neurons communicate through short spikes, characterized by a high
+frequency, while low frequencies of the signal mainly correspond to the slow
+decay of fluorescence. To have a signal that only has high magnitude around instances where the spikes occur, the second step of our pipeline transforms the time series into its backward
 difference
@@
 \end{align}
-which effect is to magnify the importance of spikes that occur in case of low global activity (measured by $\sum_{j} x^{t}_j$).
+which effect is to magnify the importance of spikes that occur in case of low global activity. Note that the particular case where $\sum_{j} x^{t}_j$ equals $0$ is solved by setting $w(x^{t}_i) = 1$.
 

### 2014-06-26 article.tex
Retouches Sections 1+2

@@
 describes, in all details, our actual winning method, giving slightly better
-results than the method presented in the paper at a price of significant
+results than the method presented in the paper, at the price of parameter
 tuning.
@@
 
-% \begin{figure}
-% \centering
-% \includegraphics[width=0.4\linewidth]{images/fig_filtering}
-% \caption{Signal processing process for extracting peaks from the raw fluorescence data.}
-% \label{fig:filtered-signal}
-% \end{figure}
-
 As Figure~\ref{fig:original_curve} shows, the raw
@@
 \end{align}
-shown in the plot of Figure \ref{fig:hp_curve}:
+as shown in Figure \ref{fig:hp_curve}.
 
-To filter out small variations in the signal obtained after applying the function $g$ as well as to eliminate negative values, we use the following hard-threshold filter
+To filter out small variations in the signal obtained after applying the
+function $g$ as well as to eliminate negative values, we use the following
+hard-threshold filter
 \begin{align}
@@
 \end{align}
-yielding the Figure \ref{fig:threshold_curve}.
+yielding Figure \ref{fig:threshold_curve}.
 As we can see, the processed signal only contains clean spikes.
 
-The objective of the last step of our filtering procedure is to decrease the importance of spikes that occur when there is a high global activity in the network with respect to  spikes that occur during normal activity.
-Indeed, we have conjectured that when a large part of the network is firing, the rate at which observations are made is not high enough for being able to detect interactions and, that it would therefore be preferrable to lower their importance by changing appropriatly their magnitude.
-Additionnally, it is well-known that neurons may also spike because of a global high activity (see \cite{stetter2012model}).
-In such  context, detecting pairwise neuron interactions from the firing activity is meaningless.
-Accordingly, we have chosen to apply to the signal outputted by $h$ the following function  
+The objective of the last step of our filtering procedure is to decrease the
+importance of spikes that occur when there is a high global activity in the
+network with respect to  spikes that occur during normal activity. Indeed, we
+have conjectured that when a large part of the network is firing, the rate at
+which observations are made is not high enough for being able to detect
+interactions and, that it would therefore be preferrable to lower their
+importance by changing appropriatly their magnitude. Additionnally, it is
+well-known that neurons may also spike because of a global high activity (see
+\cite{stetter2012model}). In such  context, detecting pairwise neuron
+interactions from the firing activity is meaningless. As such,
+the signal output by $h$ is finally applied to the following function
 \begin{align}
- w(x^{t}_i) &= (x^{t}_i + 1 )^{1 + \frac{1}{\sum_{j} x^{t}_j}}.
+ w(x^{t}_i) &= (x^{t}_i + 1 )^{1 + \frac{1}{\sum_{j} x^{t}_j}},
 \end{align}
-which effect is to magnify the importance of spikes that occur in case of low global activity. Note that the particular case where $\sum_{j} x^{t}_j$ equals $0$ is solved by setting $w(x^{t}_i) = 1$.
+which effect is to magnify the importance of spikes that occur in case of low
+global activity. Note that the particular case where $\sum_{j} x^{t}_j = 0$ is
+solved by setting $w(x^{t}_i) = 1$.
 
-To summarize, the full signal processing pipeline of our simplified (resp. tuned)
-approach is defined by the composed function $w \circ h \circ g \circ f_1$
-(resp. $f_2$). When applied to the raw signal of Figure \ref{fig:original_curve}, it outputs the signal shown in Figure \ref{fig:weight_curve}.
+To summarize, the full signal processing pipeline of our simplified (resp.
+tuned) approach is defined by the composed function $w \circ h \circ g \circ
+f_1$ (resp. $f_2$). When applied to the raw signal of Figure
+\ref{fig:original_curve}, it outputs the signal shown in Figure
+\ref{fig:weight_curve}.
 

### 2014-06-26 article.tex
appendix: work in progress

--- 2014-06-26 article.tex
@@
 fluorescence data. More specifically, time series are processed using standard
-signal processing filters in order to remove noise due to light scattering
+signal processing filters in order to remove noise due light scattering
 effects, account for fluorescence  low decay and reduce the importance of
-global high activity in the network. The overall process is illustrated in
+global high activity in the network. The overall process is illustrated on
 Figure~\ref{fig:filtered-signal}.
@@
 Accordingly, the first step of our pipeline is to smoothen the signal, using
-one of the following low-pass filters for filtering out high frequency noise:
+one the following low-pass filter for filtering out high frequency noise:
 \begin{align}
@@
 
-To filter out small variations in the signal obtained after applying the function $g$ as well as to eliminate negative values, we use the following hard-threshold filter
+To filter out small signal variations in the signal obtained after applying the function $g$ as well as to eliminate negative values, we use the following hard-threshold filter
 \begin{align}
@@
 
-The objective of the last step of our filtering procedure is to decrease the importance of spikes that occur when there is a high global activity in the network with respect to  spikes that occur during normal activity.
+The last step of our filtering procedure has for objective to decrease the importance of spikes that occur when there is a high global activity in the network with respect to  spikes that occur during normal activity.
 Indeed, we have conjectured that when a large part of the network is firing, the rate at which observations are made is not high enough for being able to detect interactions and, that it would therefore be preferrable to lower their importance by changing appropriatly their magnitude.
@@
 \end{align}
-which effect is to magnify the importance of spikes that occur in case of low global activity. Note that the particular case where $\sum_{j} x^{t}_j$ equals $0$ is solved by setting $w(x^{t}_i) = 1$.
+that has for effect to magnify the importance of spikes that occur in case of low global activity. Note that the particular case $\sum_{j} x^{t}_j$ equals $0$ is solved by setting $w(x^{t}_i) = 1$.
 
-To summarize, the full signal processing pipeline of our simplified (resp. tuned)
-approach is defined by the composed function $w \circ h \circ g \circ f_1$
-(resp. $f_2$). When applied to the raw signal of Figure \ref{fig:original_curve}, it outputs the signal shown in Figure \ref{fig:weight_curve}.
+To summarize, the full signal processing pipeline of our (simplified)
+approach is defined by the composed function $w \cdot h \cdot g \cdot f_1$
+(resp. $f_2$). When applied to the raw signal (shown on Figure \ref{fig:original_curve}), it outputs the signal shown on Figure \ref{fig:weight_curve}.
 
@@
 
-% No time assumption
+Our  connection inference  procedure  relies  on several  assumptions. First,
+we will assume that  the fluorescence concentrations of all $p$ neurons can be
+modeled as a set of random variables $X = \{X_1, \dots, X_p\}$  that are drawn
+from a time invariant joint  probability distribution $P_X$. Or, say otherwise,
+we assume that there exists a probability distribution $P_X$ such that the
+fluorescence concentrations at a particular time $t$ can be seen as an
+independent realization of $P_X$.
 
-Our procedure to infer connections between neurons first assumes that
-the (filtered) fluorescence concentrations of all $p$ neurons at each
-time point can be modeled as a set of random variables $X = \{X_1,
-\dots, X_p\}$ that are idependently drawn from the same time invariant
-joint probability distribution $P_X$. %% Or, say otherwise, we assume
-%% that there exists a probability distribution $P_X$ such that the
-%% fluorescence concentrations at a particular time $t$ can be seen as an
-%% independent realization of $P_X$.
-As a consequence, our inference method does not exploit the time
-ordering of the observations (although time ordering is exploited by
-the filters).
+To a joint probability distribution $P_X$ corresponds a
+graph where (i) each node is a random variable and (ii) two nodes are
+only connected if they correspond to two dependent variables. We assume that two neurons are
+connected if  and only if,  there exists  in this  graph an edge
+that connects  directly the  two random  variables to  which they correspond.
+In this context, it is equivalent to writing that two neurons $i$ and $j$ are  not  directly
+connected  if and only if  $X_i$  and $X_j$  are  conditionally independent
+with  respect to all  other variables. We remind  that two random  variables
+$X_i$  and  $X_j$  are  said  to  be  conditionally independent to a (possibly
+empty)  set of controlling random variables $Z$, denoted $X_i \perp X_j | Z$,
+if the joint conditional probability distribution   $P_{X_i,  X_j   |   Z}$
+factorizes  into   $P_{X_i|Z} P_{X_j|Z}$.  In particular,  when  $X_i$ and
+$X_j$ are  conditionally independent  with respect  to all  the other
+variables, denoted  $X_i \perp  X_j  | X^{-i,j}$,  then  the  observation  of
+$X_i$  given  the knowledge  of  $X^{-i,j}$ provides  no information  about
+$X_j$,  and vice-versa.
 
-% partial correlation: definition + motivation
+In the  particular case where $P_X$ is  a joint  Gaussian distribution
+$\mathcal{N}(\mu; \Sigma)$ of mean  vector $\mu$ and covariance matrix
+$\Sigma$, $X_i$  and $X_j$ are conditionally  independent with respect to the
+other variables $X^{-i,j}$ if their \textit{partial correlation} statistic is
+null~\citep{baba2004partial}, i.e., if
+\begin{equation}
+\rho_{X_i, X_j | X^{-i,j}} = -\frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii} \Sigma^{-1}_{jj}}} = 0, \label{eq:inverse}
+\end{equation}
+where $\Sigma^{-1}$ is known as the precision or concentration matrix. 
+Conversely, $X_i$ and $X_j$ are conditionally dependent if $\rho_{X_i, X_j |
+X^{-i,j}} \neq 0$, where $\rho_{X_i, X_j | X^{-i,j}} \in [-1;1]$. Note that the
+larger the value of this term, the stronger the dependence between variables
+$X_i$ and $X_j$.
 
-Given this assumption, we then propose to use as a measure of the
-strength of the connection between two neurons $i$ and $j$, the
-partial correlation coefficient $p_{i,j}$ between their corresponding
-random variables $X_i$ and $X_j$, defined by \cite{}:
-\begin{equation}
-p_{i,j} =
--\frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii} \Sigma^{-1}_{jj}}}, \label{eq:inverse},
-\end{equation}
-where $\Sigma^{-1}$, known as the precision or concentration matrix, is the inverse of the covariance matrix $\Sigma$ of $X$.%%  Partial
-%% correlation can be interpreted in several ways. The partial
-%% correlation coefficient $p_{i,j}$ can be shown to measure the
-%% correlation between $X_i$ and $X_j$ when they are corrected for the
-%% (linear) effect of all other variables in $X$ \cite{}.
-Assuming that the distribution $P_X$ is a multivariate Gaussian
-distribution ${\cal N}(\mu,\Sigma)$, it can be shown that $p_{i,j}$ is
-zero if and only if $X_i$ and $X_j$ are independent given all other
-variables in $X$, ie. $X_i \perp X_j|X^{-i,j}$ where $X^{-i,j}= X
-\setminus\{X_i,X_j\}$. Partial correlation thus measures conditional
-dependencies between variables. As an association measures between
-neurons, it should thus naturally only detect direct associations
-between neurons and filter out spurious indirect effects. The interest
-of partial correlation as an association measure has already been
-shown for the inference of gene regulatory networks \cite{xxx}.
-%% Given a set of multivariate Gaussian
-%% random variables $X$, the (undirected) graph that connects all pairs
-%% of variables $X_i$ and $X_j$ such that $p_{i,j}\neq 0$ is called a
-%% Gaussian graphical models (GGMs). Because it measures conditional
-%% dependencies, partial correlation should naturally only detect direct
-%% associations between neurons. The superiority of partial correlation
-%% over standard correlation as an association measure have already been
-%% shown in the context of the inference of gene regulatory networks from
-%% gene expression data \cite{}. We will compare both measures in Section
-%% \ref{sec:results}.
-Note that the partial correlation statistic is symmetric
-(i.e. $p_{i,j}=p_{j,i}$). Therefore, our approach cannot identify the
-direction of the interactions between neurons. We will see in
-Section~\ref{sec:results} why this only affects slightly its
-performances, with respect to the metric used in the Connectomics
-challenge.
-
-Practically, the computation of coefficient $p_{i,j}$ using Equation
-\ref{ref} requires the estimation of the covariance matrix $\Sigma$
-and then computing its inverse. Given that we have typically more
-samples than neurons, the covariance matrix can be inverted in a
-straightforward way. We nevertheless obtained some improvement by
-replacing the exact inverse with an approximation using only the $M$
-first principal components of $\Sigma$~\citep{bishop2006pattern} (with
-$M$ set to $0.8 p$ in our experiments).
-
-Finally, let us remark that performance of our simple method shows to
-be quite sensitive to the values of parameters (e.g., $f_1$ or $f_2$
-or the value of the threshold $\tau$) in the combined function of the
-filtering and infering processes. One approach, that we will refered
-to as \textit{Averaged Partial correlation} statistics, for improving
-its robustness is to average correlation statistics over various
-values of the parameters, thereby reducing the variance of its
-predictions. Further details about parameter selection are provided in
-Appendix~\ref{app:optimized}.
-
-% Note on directionality
-
-%% Our  connection inference  procedure  relies  on several  assumptions. First,
-%% we will assume that  the fluorescence concentrations of all $p$ neurons can be
-%% modeled as a set of random variables $X = \{X_1, \dots, X_p\}$  that are drawn
-%% from a time invariant joint  probability distribution $P_X$. Or, say otherwise,
-%% we assume that there exists a probability distribution $P_X$ such that the
-%% fluorescence concentrations at a particular time $t$ can be seen as an
-%% independent realization of $P_X$.
-
-%% To assess the presence of a connection between two neurons, we will
-%% use partial correlation statistics, which has been used extensively
-%% for the inference of gene regulatory networks \cite{}.
-
-%% To a joint probability distribution $P_X$ corresponds a
-%% graph where (i) each node is a random variable and (ii) two nodes are
-%% only connected if they correspond to two dependent variables. We assume that two neurons are
-%% connected if  and only if,  there exists  in this  graph an edge
-%% that connects  directly the  two random  variables to  which they correspond.
-%% In this context, it is equivalent to writing that two neurons $i$ and $j$ are  not  directly
-%% connected  if and only if  $X_i$  and $X_j$  are  conditionally independent
-%% with  respect to all  other variables. We remind  that two random  variables
-%% $X_i$  and  $X_j$  are  said  to  be  conditionally independent to a (possibly
-%% empty)  set of controlling random variables $Z$, denoted $X_i \perp X_j | Z$,
-%% if the joint conditional probability distribution   $P_{X_i,  X_j   |   Z}$
-%% factorizes  into   $P_{X_i|Z} P_{X_j|Z}$.  In particular,  when  $X_i$ and
-%% $X_j$ are  conditionally independent  with respect  to all  the other
-%% variables, denoted  $X_i \perp  X_j  | X^{-i,j}$,  then  the  observation  of
-%% $X_i$  given  the knowledge  of  $X^{-i,j}$ provides  no information  about
-%% $X_j$,  and vice-versa.
-
-%% In the  particular case where $P_X$ is  a joint  Gaussian distribution
-%% $\mathcal{N}(\mu; \Sigma)$ of mean  vector $\mu$ and covariance matrix
-%% $\Sigma$, $X_i$  and $X_j$ are conditionally  independent with respect to the
-%% other variables $X^{-i,j}$ if their \textit{partial correlation} statistic is
-%% null~\citep{baba2004partial}, i.e., if
-%% \begin{equation}
-%% \rho_{X_i, X_j | X^{-i,j}} = -\frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii} \Sigma^{-1}_{jj}}} = 0, \label{eq:inverse}
-%% \end{equation}
-%% where $\Sigma^{-1}$ is known as the precision or concentration matrix. 
-%% Conversely, $X_i$ and $X_j$ are conditionally dependent if $\rho_{X_i, X_j |
-%% X^{-i,j}} \neq 0$, where $\rho_{X_i, X_j | X^{-i,j}} \in [-1;1]$. Note that the
-%% larger the value of this term, the stronger the dependence between variables
-%% $X_i$ and $X_j$.
-
-%% Our approach implicitly makes the additional assumption  that $P_X$ is  a
-%% joint Gaussian distribution since it  outputs as degree of association
-%% between two neurons $i$ and $j$ an estimate of $\rho_{X_i, X_j | X^{-i,j}}$.
-%% Note also that the partial correlation
-%% statistic is symmetric  (i.e., $\rho_{X_i, X_j | X^{-i,j}} = \rho_{X_j, X_i |
-%% X^{-j,i}}$).
+Our approach implicitly makes the additional assumption  that $P_X$ is  a
+joint Gaussian distribution since it  outputs as degree of association
+between two neurons $i$ and $j$ an estimate of $\rho_{X_i, X_j | X^{-i,j}}$.
+Note also that the partial correlation
+statistic is symmetric  (i.e., $\rho_{X_i, X_j | X^{-i,j}} = \rho_{X_j, X_i |
+X^{-j,i}}$).
 Therefore, our approach cannot identify the direction of the interaction.
@@
 
-%% We now detail our procedure for estimating partial correlation
-%% statistics ($\rho_{X_i, X_j | X^{-i,j}}$) from the data. It first
-%% estimates the covariance matrix from the data. Afterwards, it computes
-%% the exact inverse of this matrix, from which it infers the value of
-%% $\rho_{X_i, X_j | X^{-i,j}}$ using equation (\ref{eq:inverse}). Note
-%% that we have also experimented procedures where the exact inverse was
-%% replaced by an approximation of it using only the $M$ principal
-%% components of $\Sigma$~\citep{bishop2006pattern} whose associated
-%% eigen values were significantly higher than zero. Such an
-%% approximation is equivalent to assume that the firing activity of all
-%% neurons can be explained by only a subset of them whose size is equal
-%% to $M$. We observed that those procedures were often leading to better
-%% results. Note that we found out by running expriments that the number
-%% $M$ of principal components is around $0.8p$ (see discussion in
-%% Appendix~\ref{app:REF} \textcolor{red}{REF}).
+We now detail  our procedure for estimating partial correlation statistics
+($\rho_{X_i, X_j | X^{-i,j}}$) from the data.
+It first estimates the covariance matrix from the data.
+Afterwards, it computes the exact inverse of this matrix, from which it infers the value of $\rho_{X_i, X_j | X^{-i,j}}$ using  equation (\ref{eq:inverse}).
+Note that we have also experimented procedures where the exact inverse was replaced by an approximation of it using only the $M$ principal components of $\Sigma$~\citep{bishop2006pattern} whose associated eigen values were significantly higher than zero.
+Such an approximation is equivalent to assume that the firing activity of all neurons can be explained by only a subset of them whose size is equal to $M$.
+We observed that those procedures were often leading to better results.
+Note that we found out by running expriments that the number $M$ of principal components is around $0.8p$
+(see discussion in Appendix~\ref{app:REF}
+\textcolor{red}{REF}).
 
-%% % Computationally, they can be estimated
-%% % % efficiently in $O(M^3)$ (instead of $O(p^3)$) 
-%% % from the $M$ first principal
-%% % components extracted through PCA~\citep{bishop2006pattern} on the processed
-%% % data. While speeding up computation, it allows to further 
-%% % filter the the data by removing the contribution of components that are respectively
-%% % due to redundancy or noise, i.e., with an eigen value respectively is equal to zero or close to zero.
+% Computationally, they can be estimated
+% % efficiently in $O(M^3)$ (instead of $O(p^3)$) 
+% from the $M$ first principal
+% components extracted through PCA~\citep{bishop2006pattern} on the processed
+% data. While speeding up computation, it allows to further 
+% filter the the data by removing the contribution of components that are respectively
+% due to redundancy or noise, i.e., with an eigen value respectively is equal to zero or close to zero.
+
+Finally, let us remark that performance of our simple method shows to be quite sensitive to the values of parameters (e.g., $f_1$ or
+$f_2$ or the value of the threshold $\tau$) in the combined function of the filering and infering processes. One approach, that we will refered to as \textit{Averaged
+Partial correlation} statistics, for improving its robustness is to average correlation statistics
+over various values of the parameters, thereby reducing the variance of its
+predictions. Further details are provided in
+Appendix~\ref{app:optimized}.
 
@@
 
-%% \textcolor{red}{to incorporate: 
-%% To highlight the benefits of measuring the partial dependence conditional to
-%% all other variables, we compare in Section~\ref{sec:results} with the
-%% \textit{Pearson correlation} statistics, which measure instead the linear
-%% dependence between variables, independently of the others. Accordingly, $X_i$
-%% and $X_j$ are independent, without any conditioning, if their Pearson correlation statistic is zero, that
-%% is if
-%% \begin{equation}
-%% \rho_{X_i,X_j} = \frac{\Sigma_{ij}}{\sqrt{\Sigma_{ii} \Sigma_{jj}}} = 0.
-%% \end{equation}}
+\textcolor{red}{to incorporate: 
+To highlight the benefits of measuring the partial dependence conditional to
+all other variables, we compare in Section~\ref{sec:results} with the
+\textit{Pearson correlation} statistics, which measure instead the linear
+dependence between variables, independently of the others. Accordingly, $X_i$
+and $X_j$ are independent, without any conditioning, if their Pearson correlation statistic is zero, that
+is if
+\begin{equation}
+\rho_{X_i,X_j} = \frac{\Sigma_{ij}}{\sqrt{\Sigma_{ii} \Sigma_{jj}}} = 0.
+\end{equation}}
 
 % Datasets
-We have carried out experiments with our method on the
-\textit{normal}-1,2,3, and 4 datasets provided by the organizers of
-the Connectomics challenge. Each of these datasets contains $p=1000$
-time series of length $T=179500$ of image calcium from simulated
-neuronal networks \citep{stetter2012model}. The network to infer
-contains approximately 15000 edges, ie an edge density of about
-1.5\%. All inference methods compared here provides a ranking of
-neuron pairs according to some association score. To assess the
-quality of this ranking, we use both ROC and precision-recall curves,
-and we summarize them using the area under these curves, denoted
-respectively AUROC and AUPRC. Only the AUROC was used in the context of the connectomics to rThe AUROC was
-used to rank submissions to the challenge but the precision-recall
-curve has some\citep{schrynemackers2013protocols}
+To assess our method, we focus on the \textit{normal-2} dataset
+provided by the organizers of the Connectomics challenge. Experiments
+on \textit{normal-1, normal-3, normal-4} show similar trends to
+\textit{normal-2} and are presented in the Appendix \textcolor{red}{REF}.
+Those datasets have $p=1000$ time series of length $T=179500$ of image
+calcium from simulated neuronal networks \citep{stetter2012model}. Those
+networks have approximately 15000 edges.
 
-Since neurons are
-not self-connected ($(i, i) \not \in E, \forall i \in V$) and some
-inference methods could give maximal scores to those edges,
-e.g. Pearson correlation, those elements are set to have minimal
-connectivity score prior assessment.
+% Metrics : ROC AUC and AUPRC
+In supervised learning terms, the network inference task can be viewed as a
+binary classification task where one has to correctly classify the presence or
+the absence of edges of the graph. We assess the accuracy of the network
+inference method using the area under the ROC curve (AUROC) and the area under
+the precision-recall curve (AUPRC) \citep{schrynemackers2013protocols}. Since
+neurons are not self-connected ($(i, i) \not \in E, \forall i \in V$) and some
+inference methods could give maximal scores to those edges, e.g. Pearson
+correlation, those elements are set to have minimal connectivity score prior
+assessment.
 
-\paragraph{Effect of pre-processing}
-
-The top of Table \ref{} reports AUPR and AUROC for all four networks
-progressively introducing all filtering steps and for the last step,
-the PCA based matrix inversion. All steps improves performances, with
-the bigger improvement brought by the introduction of the
-... Interestingly, while PCA does not really have an impact of AUROC,
-it significantly increases the AUPR score.
-
-\paragraph{Comparison with other methods}
-
-Then, we compare our method with several other methods:
-\begin{itemize}
-\item Standard correlation coefficient...In this case, the
-  prefiltering the same as for partial correlation.
-\item \textbf{GTE} \citep{stetter2012model}, the baseline of the
-  challenge, which is based on transfer entrey measures for all pairs
-  of neurons $i$ and $j$ the reduction of uncertainty in predicting
-  future values of $i$ given the observation of the time series of the
-  neuron $j$ conditionally to the observation of past time series of
-  neuron $i$, whenever the average fluorescence is over a conditioning
-  level. Pre-processing and conditioning level were set to reproduce
-  baseline of the challenge.
-\item \textbf{GENIE3}\citep{huynhthu2010inferring}: This method is a
-  state-of-the-art gene network inference method \cite{dream5}. It
-  translates the the inference of the network of $p$ neurons into $p$
-  supervised learning tasks. For each task, the fluorescence of a
-  neuron is predicted from the fluorescence of all other neurons using
-  a tree based ensemble such as random forest
-  \citep{breiman2001random}. The tree ensemble associates a variable
-  importance score \citep{louppe2013understanding} to each neuron used
-  in the predictions, which is used as a degree of associate.
-To reduce the computational cost of the method, we nevertheless restrained all trees to a maximum tree depth of 3.
-This is likely to be detrimental The
-  following parameters are used $10000$ trees, $\log_2{p}$ variables
-  are randomly selected to split tree nodes and the maximal tree depth
-  is constrained to 1, 2 or 3. Note that unlike the other methods, this method provides asymetric scores, meaning it can potentially predict edge directions.
-\end{itemize}
-
-Bottom of table \ref{} shows the score of these methods. ROC and PR
-curves on normal-2 are shown in Figure ... Pearson correlation is the worst method
-
-\paragraph{ROC versus PR curves.} While only ROC was , we argue here that PR scores are more appropriate in this context.
-
-%% To assess our method, we focus on the \textit{normal-2} dataset
-%% provided by the organizers of the Connectomics challenge. Experiments
-%% on \textit{normal-1, normal-3, normal-4} show similar trends to
-%% \textit{normal-2} and are presented in the Appendix \textcolor{red}{REF}.
-%% Those datasets have $p=1000$ time series of length $T=179500$ of image
-%% calcium from simulated neuronal networks \citep{stetter2012model}. Each of these
-%% networks contains approximately 15000 edges.
-
-%% % Metrics : ROC AUC and AUPRC
-%% In supervised learning terms, the network inference task can be viewed as a
-%% binary classification task where one has to correctly classify the presence or
-%% the absence of edges of the graph. We assess the accuracy of the network
-%% inference method using the area under the ROC curve (AUROC) and the area under
-%% the precision-recall curve (AUPRC) \citep{schrynemackers2013protocols}.
-
-The proposed approach is compared to Pearson correlation statistics
-(as described in Section~\ref{sec:inference}), generalized transfer
-entropy (GTE) and the GENIE3 algorithm.
+The proposed approach is compared to Pearson correlation statistics (as
+described in Section~\ref{sec:inference}), generalized transfer entropy (GTE)
+and the GENIE3 algorithm.
 \begin{itemize}
@@
 \subsection*{Averaging the connectome inference from partial correlation statistics}
+
+In our experiments, we observed that the inference process is quite sensitive about the choice of the parameter value $\tau$ and the low-pass filter.
+Therefore, in order to reduce the variance of the results and thus the robustness of our approach, we perform an average over a range of parameter value $\tau$ from $0.100$ to $0.209$.
+We also perform a weighted average over the four low-pass filters with weights
+$weight_{f_1} = 1$, $weight_{f_2} = 0.9$, $weight_{f_3} = 0.7$ and $weight_{f_4} = 0.01$, tuned to maximize the ROC AUC on \textit{normal-1}.
+The weights were adjusted to take into account that some filters outperform other but there is information hold in every filter.
 

### 2014-06-26 article.tex

--- 2014-06-26 article.tex
@@
 \end{align}
-which effect is to magnify the importance of spikes that occur in case of low
-global activity. Note that the particular case where $\sum_{j} x^{t}_j = 0$ is
-solved by setting $w(x^{t}_i) = 1$.
+that has for effect to magnify the importance of spikes that occur in case of low global activity. Note that the particular case $\sum_{j} x^{t}_j$ equals $0$ is solved by setting $w(x^{t}_i) = 1$.
 
@@
 
+In our experiments, we observed that the inference process is quite sensitive about the choice of the parameter value $\tau$ and the low-pass filter.
+Therefore, in order to reduce the variance of the results and thus the robustness of our approach, we perform an average over a range of parameter value $\tau$ from $0.100$ to $0.209$.
+We also perform a weighted average over the four low-pass filters with weights
+$weight_{f_1} = 1$, $weight_{f_2} = 0.9$, $weight_{f_3} = 0.7$ and $weight_{f_4} = 0.01$, tuned to maximize the ROC AUC on \textit{normal-1}.
+The weights were adjusted to take into account that some filters outperform other but there is information hold in every filter.
+
 \subsection*{Connectome inference from pairwise interaction statistics}

### 2014-06-26 article.tex
typo

--- 2014-06-26 article.tex
@@
 p_{i,j} =
--\frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii} \Sigma^{-1}_{jj}}}, \label{eq:inverse},
+-\frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii} \Sigma^{-1}_{jj}}}, \label{eq:inverse}
 \end{equation}
@@
 Practically, the computation of coefficient $p_{i,j}$ using Equation
-\ref{ref} requires the estimation of the covariance matrix $\Sigma$
+\ref{eq:inverse} requires the estimation of the covariance matrix $\Sigma$
 and then computing its inverse. Given that we have typically more

### 2014-06-26 article.tex
ref

--- 2014-06-26 article.tex
@@
 importance by changing appropriatly their magnitude. Additionnally, it is
-well-known that neurons may also spike because of a global high activity (see
-\cite{stetter2012model}). In such  context, detecting pairwise neuron
+well-known that neurons may also spike because of a global high activity
+\citep{stetter2012model}. In such  context, detecting pairwise neuron
 interactions from the firing activity is meaningless. As such,

### 2014-06-26 article.tex
observation of fig

@@
 \end{align}
-that has for effect to magnify the importance of spikes that occur in case of low global activity. Note that the particular case $\sum_{j} x^{t}_j$ equals $0$ is solved by setting $w(x^{t}_i) = 1$.
+that has for effect to magnify the importance of spikes that occur in case of low global activity, for example the small peak around 4 second.
+Note that the particular case where there is no activity, i.e., $\sum_{j} x^{t}_j = 0$, is solved by setting $w(x^{t}_i) = 1$.
 

### 2014-06-26 article.tex
Update article.tex

@@
 \end{align}
-that has for effect to magnify the importance of spikes that occur in case of low global activity, for example the small peak around 4 second.
+which effect is to magnify the importance of spikes that occur in case of low global activity (measured by $\sum_{j} x^{t}_j$), as observed for instance around $t=4\text{s}$ in the figure.
 Note that the particular case where there is no activity, i.e., $\sum_{j} x^{t}_j = 0$, is solved by setting $w(x^{t}_i) = 1$.

### 2014-06-26 article.tex
values for simplified version

--- 2014-06-26 article.tex
@@
 \end{align}
-where $m$ depends on the low-pass filter and on the range of the global activity. We refer to our implemetation, available on ... , for the values of the parameters and especially the parameter $m$.
+where $m$ is a piecewise linear function depending on the low-pass filter and on the range of the global activity.
+We refer to our implementation\footnote{available on \url{https://github.com/asutera/kaggle-connectomics}.} for the values of the parameters and especially the parameter $m$.
 
@@
 \subsection*{Connectome inference from pairwise interaction statistics}
+
+Since partial correlation statistics is a symmetric measure and the connectome is a directed graph, it should be rewarding to detect the edge orientation.
+In this section, we will present a heuristic trying to retrieve directivity.
+However, considering the argument in Section \ref{sec:results}, the additional gain margin of this approach compared to the undirected method is extremely limited.
+
+The heuristic is based on the following observation. The rise of fluorescence of a neuron indicates its activation.
 
@@
 \end{tabular}
-\caption{TODO \textcolor{red}{version simple!!}}
+\caption{Optimized method (TODO)}
+\label{tab:tab3}
+\end{table}
+
+\begin{table}[tbh]
+\centering
+\small
+\begin{tabular}{@{}l *{8}{c}@{}}
+\hline
+  & \multicolumn{4}{c}{AUROC} & \multicolumn{4}{c}{AUPRC} \\
+\hline
+Methods $\backslash$ normal- & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 \\
+No  filtering       & 0.777 & 0.767 & 0.772 & 0.774 & 0.070 & 0.064 & 0.068 & 0.072\\
+P                   & 0.923 & 0.925 & 0.923 & 0.922 & 0.311 & 0.315 & 0.313 & 0.304\\
+P + W               & 0.931 & 0.929 & 0.928 & 0.926 & 0.326 & 0.323 & 0.319 & 0.303\\
+P + W + PCA         & 0.932 & 0.930 & 0.928 & 0.926 & 0.355 & 0.353 & 0.350 & 0.333\\
+Averaging           & 0.938 & 0.936 & 0.936 & 0.932 & 0.391 & 0.389 & 0.385 & 0.374\\
+%Averaging + Directivity & 0.944 & 0.943 & 0.942 & 0.940 & 0.404 & 0.405 & 0.399 & 0.389\\
+\end{tabular}
+\caption{Simplified method (TODO)}
 \label{tab:tab3}

### 2014-06-26 article.tex
modif section 4 (draft, toujours en cours)

--- 2014-06-26 article.tex
@@
 describes, in all details, our actual winning method, giving slightly better
-results than the method presented in the paper, at the price of parameter
+results than the method presented in the paper at a price of significant
 tuning.
@@
 
+% \begin{figure}
+% \centering
+% \includegraphics[width=0.4\linewidth]{images/fig_filtering}
+% \caption{Signal processing process for extracting peaks from the raw fluorescence data.}
+% \label{fig:filtered-signal}
+% \end{figure}
+
 As Figure~\ref{fig:original_curve} shows, the raw
@@
 \end{align}
-as shown in Figure \ref{fig:hp_curve}.
+shown in the plot of Figure \ref{fig:hp_curve}:
 
-To filter out small variations in the signal obtained after applying the
-function $g$ as well as to eliminate negative values, we use the following
-hard-threshold filter
+To filter out small variations in the signal obtained after applying the function $g$ as well as to eliminate negative values, we use the following hard-threshold filter
 \begin{align}
@@
 \end{align}
-yielding Figure \ref{fig:threshold_curve}.
+yielding the Figure \ref{fig:threshold_curve}.
 As we can see, the processed signal only contains clean spikes.
 
-The objective of the last step of our filtering procedure is to decrease the
-importance of spikes that occur when there is a high global activity in the
-network with respect to  spikes that occur during normal activity. Indeed, we
-have conjectured that when a large part of the network is firing, the rate at
-which observations are made is not high enough for being able to detect
-interactions and, that it would therefore be preferrable to lower their
-importance by changing appropriatly their magnitude. Additionnally, it is
-well-known that neurons may also spike because of a global high activity
-\citep{stetter2012model}. In such  context, detecting pairwise neuron
-interactions from the firing activity is meaningless. As such,
-the signal output by $h$ is finally applied to the following function
+The objective of the last step of our filtering procedure is to decrease the importance of spikes that occur when there is a high global activity in the network with respect to  spikes that occur during normal activity.
+Indeed, we have conjectured that when a large part of the network is firing, the rate at which observations are made is not high enough for being able to detect interactions and, that it would therefore be preferrable to lower their importance by changing appropriatly their magnitude.
+Additionnally, it is well-known that neurons may also spike because of a global high activity (see \cite{stetter2012model}).
+In such  context, detecting pairwise neuron interactions from the firing activity is meaningless.
+Accordingly, we have chosen to apply to the signal outputted by $h$ the following function  
 \begin{align}
- w(x^{t}_i) &= (x^{t}_i + 1 )^{1 + \frac{1}{\sum_{j} x^{t}_j}},
+ w(x^{t}_i) &= (x^{t}_i + 1 )^{1 + \frac{1}{\sum_{j} x^{t}_j}}.
 \end{align}
-which effect is to magnify the importance of spikes that occur in case of low global activity (measured by $\sum_{j} x^{t}_j$), as observed for instance around $t=4\text{s}$ in the figure.
-Note that the particular case where there is no activity, i.e., $\sum_{j} x^{t}_j = 0$, is solved by setting $w(x^{t}_i) = 1$.
+which effect is to magnify the importance of spikes that occur in case of low global activity. Note that the particular case where $\sum_{j} x^{t}_j$ equals $0$ is solved by setting $w(x^{t}_i) = 1$.
 
-To summarize, the full signal processing pipeline of our simplified (resp.
-tuned) approach is defined by the composed function $w \circ h \circ g \circ
-f_1$ (resp. $f_2$). When applied to the raw signal of Figure
-\ref{fig:original_curve}, it outputs the signal shown in Figure
-\ref{fig:weight_curve}.
+To summarize, the full signal processing pipeline of our simplified (resp. tuned)
+approach is defined by the composed function $w \circ h \circ g \circ f_1$
+(resp. $f_2$). When applied to the raw signal of Figure \ref{fig:original_curve}, it outputs the signal shown in Figure \ref{fig:weight_curve}.
 
@@
 p_{i,j} =
--\frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii} \Sigma^{-1}_{jj}}}, \label{eq:inverse}
+-\frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii} \Sigma^{-1}_{jj}}}, \label{eq:inverse},
 \end{equation}
@@
 Practically, the computation of coefficient $p_{i,j}$ using Equation
-\ref{eq:inverse} requires the estimation of the covariance matrix $\Sigma$
+\ref{ref} requires the estimation of the covariance matrix $\Sigma$
 and then computing its inverse. Given that we have typically more
@@
 
-% Datasets
-We have carried out experiments with our method on the
-\textit{normal}-1,2,3, and 4 datasets provided by the organizers of
-the Connectomics challenge. Each of these datasets contains $p=1000$
-time series of length $T=179500$ of image calcium from simulated
-neuronal networks \citep{stetter2012model}. The network to infer
-contains approximately 15000 edges, ie an edge density of about
-1.5\%. All inference methods compared here provides a ranking of
-neuron pairs according to some association score. To assess the
-quality of this ranking, we use both ROC and precision-recall curves,
-and we summarize them using the area under these curves, denoted
-respectively AUROC and AUPRC. Only the AUROC was used in the context of the connectomics to rThe AUROC was
-used to rank submissions to the challenge but the precision-recall
-curve has some\citep{schrynemackers2013protocols}
+\paragraph{Data and evaluation metrics.}
 
-Since neurons are
-not self-connected ($(i, i) \not \in E, \forall i \in V$) and some
-inference methods could give maximal scores to those edges,
-e.g. Pearson correlation, those elements are set to have minimal
-connectivity score prior assessment.
+We report here experiments on the \textit{normal}-1,2,3, and 4
+datasets provided by the organizers of the Connectomics
+challenge. Each of these datasets is obtained from the simulation
+\citep{stetter2012model} of different neural networks of 1000 neurons
+and about 15000 edges each (ie., a network density of about
+1.5\%). Each neuron is described by a calcium fluorescence time series
+of length $T=179500$. All inference methods compared here provide a
+ranking of all pairs of neurons according to some association
+score. To assess the quality of this ranking, we compute both ROC and
+precision-recall curves against the ground truth network, which are
+summarized using the area under the curve, denoted respectively AUROC
+and AUPRC. Only the AUROC score was used to rank the challenge
+participants but the precision-recall curve has been shown to be a
+more sensible metric for network inference, especially when network
+density is small (see e.g. \cite{schrynemackers2013protocols}).
+Since neurons are not self-connected in the ground truth networks
+(ie., $(i, i) \not \in E, \forall i \in V$), we have manually set the
+score of such edges to the minimal possible association score before
+computing ROC and PR curves.
 
-\paragraph{Effect of pre-processing}
+\paragraph{Evaluation of the method}
 
-The top of Table \ref{} reports AUPR and AUROC for all four networks
-progressively introducing all filtering steps and for the last step,
-the PCA based matrix inversion. All steps improves performances, with
-the bigger improvement brought by the introduction of the
-... Interestingly, while PCA does not really have an impact of AUROC,
-it significantly increases the AUPR score.
+The top of Table \ref{tab:comparison} reports AUROC and AUPRC for all four networks
+using in each case partial correlation with different filtering
+functions. Except for the last two rows that uses PCA, the exact
+inverse of the covariance matrix was used in each case. These results
+clearly show the importance of the filters. AUROC increases in average from
+0.77 to 0.93. PCA does not really affect AUROC scores but it improves
+significantly AUPRC scores. Taking the average over various parameter
+setting gives an improvement of 10\% in both AUROC and AUPRC. The last
+row shows the final performance of the method specifically tuned for
+the challenge (see the Appendix for all details). Although this tuning
+was decisive to obtain the best performance at the challenge, it does
+not significantly improve neither AUROC nor AUPRC. Note that tuning
+was mainly done on the \textit{normal-1} and \textit{normal-4}
+datasets, which explains why these two networks are slightly better
+retrieved than the others.
+
+\begin{table}[t]
+\caption{Evaluation of different methods on the four \textit{normal} datasets\label{tab:comparison}}
+\centering
+\small
+\begin{tabular}{@{}l *{8}{c}@{}}
+\hline
+  & \multicolumn{4}{c}{AUROC} & \multicolumn{4}{c}{AUPRC} \\
+\hline
+Methods $\backslash$ normal- & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 \\
+No  filtering       & 0.777 & 0.767 & 0.772 & 0.774 & 0.070 & 0.064 & 0.068 & 0.072\\
+$ h \circ g \circ f_1$                 & 0.925 & 0.925 & 0.924 & 0.923 & 0.322 & 0.324 & 0.323 & 0.312\\
+$ w \circ h \circ g \circ f_1$               & 0.931 & 0.930 & 0.928 & 0.927 & 0.333 & 0.334 & 0.327 & 0.313\\
++ PCA         & 0.932 & 0.931 & 0.930 & 0.928 & 0.364 & 0.366 & 0.359 & 0.344\\
+Averaging           & 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388\\
+Full method &\\
+\hline
+%Averaging + Directivity & 0.944 & 0.943 & 0.942 & 0.940 & 0.404 & 0.405 & 0.399 & 0.389\\
+Correlation &\\
+GTE & \\
+GENIE3 &\\
+\end{tabular}
+\caption{TODO \textcolor{red}{version simple!!}}
+\label{tab:tab3}
+\end{table}
 
@@
 
-Then, we compare our method with several other methods:
-\begin{itemize}
-\item Standard correlation coefficient...In this case, the
-  prefiltering the same as for partial correlation.
-\item \textbf{GTE} \citep{stetter2012model}, the baseline of the
-  challenge, which is based on transfer entrey measures for all pairs
-  of neurons $i$ and $j$ the reduction of uncertainty in predicting
-  future values of $i$ given the observation of the time series of the
-  neuron $j$ conditionally to the observation of past time series of
-  neuron $i$, whenever the average fluorescence is over a conditioning
-  level. Pre-processing and conditioning level were set to reproduce
-  baseline of the challenge.
-\item \textbf{GENIE3}\citep{huynhthu2010inferring}: This method is a
-  state-of-the-art gene network inference method \cite{dream5}. It
-  translates the the inference of the network of $p$ neurons into $p$
-  supervised learning tasks. For each task, the fluorescence of a
-  neuron is predicted from the fluorescence of all other neurons using
-  a tree based ensemble such as random forest
-  \citep{breiman2001random}. The tree ensemble associates a variable
-  importance score \citep{louppe2013understanding} to each neuron used
-  in the predictions, which is used as a degree of associate.
-To reduce the computational cost of the method, we nevertheless restrained all trees to a maximum tree depth of 3.
-This is likely to be detrimental The
-  following parameters are used $10000$ trees, $\log_2{p}$ variables
-  are randomly selected to split tree nodes and the maximal tree depth
-  is constrained to 1, 2 or 3. Note that unlike the other methods, this method provides asymetric scores, meaning it can potentially predict edge directions.
-\end{itemize}
+In the bottom part of Table \ref{tab:comparison}, the proposed
+approach is compared with three other methods: standard (Pearson)
+correlation (PC), generalized transfer entropy (GTE), and GENIE3. ROC
+and PR curves on the \textit{normal-2} network are shown for all
+methods in Figure \ref{fig:}. Pearson correlation measures the
+unconditional linear (in)dependence between variables and it should
+thus not be able to filter out indirect interactions between
+neurons. GTE \citep{stetter2012model} was proposed as a baseline for
+the challenge. This method builds on Transfer Entropy to measure the
+association between two neurons. Unlike our approach, it can predict
+the direction of the edges. GENIE3 \citep{huynhthu2010inferring} is a
+gene regulatory network inference method that was the best performer
+of the DREAM5 challenge \cite{dream5paper}. When transposed to neural
+networks, this method uses as a confidence score for the edge going
+from neuron $i$ to neuron $j$ the importance score of variable $X_i$
+in a Random Forests model trying to predict $X_j$ from all variables
+in $X\setminus X_j$. To reduce computing times of this method, we had
+to reduce each tree in the Random Forests model to a maximum depth of
+3. This constraint potentially severly affects the performance of this
+method with respect to the use of fully grown trees. We nevertheless
+provide these results for comparison purpose. PC and GENIE3 were both
+applied on the same pre-filtered time series as partial
+correlation. For GENIE3, we built 10000 trees per neuron and we used
+default settings for all other parameters (except for the maximal tree
+depth). For GTE, we reproduced the exact same setting (conditioning
+level and pre-processing) that was used for the challenge.
 
-Bottom of table \ref{} shows the score of these methods. ROC and PR
-curves on normal-2 are shown in Figure ... Pearson correlation is the worst method
-
-\paragraph{ROC versus PR curves.} While only ROC was , we argue here that PR scores are more appropriate in this context.
+%\paragraph{ROC versus PR curves.} While only ROC was , we argue here that PR scores are more appropriate in this context.
 
@@
 
-The proposed approach is compared to Pearson correlation statistics
-(as described in Section~\ref{sec:inference}), generalized transfer
-entropy (GTE) and the GENIE3 algorithm.
-\begin{itemize}
-\item \textbf{GTE} \citep{stetter2012model}, the baseline of the challenge,
-measures for all pairs of neurons $i$ and $j$ the reduction of uncertainty in
-predicting future values of $i$ given the observation of the time series of the
-neuron $j$ conditionally to the observation of past time series of neuron $i$,
-whenever the average fluorescence is over a conditioning level. Pre-processing
-and conditioning level were set to reproduce baseline of the challenge.
+%% The proposed approach is compared to Pearson correlation statistics
+%% (as described in Section~\ref{sec:inference}), generalized transfer
+%% entropy (GTE) and the GENIE3 algorithm.
+%% \begin{itemize}
+%% \item \textbf{GTE} \citep{stetter2012model}, the baseline of the challenge,
+%% measures for all pairs of neurons $i$ and $j$ the reduction of uncertainty in
+%% predicting future values of $i$ given the observation of the time series of the
+%% neuron $j$ conditionally to the observation of past time series of neuron $i$,
+%% whenever the average fluorescence is over a conditioning level. Pre-processing
+%% and conditioning level were set to reproduce baseline of the challenge.
 
-\item \textbf{GENIE3} \citep{huynhthu2010inferring} translates the inference
-of the network of $p$ neurons into $p$ supervised learning tasks. For each
-task, the fluorescence of a neuron is predicted from the fluorescence of all
-other neurons using a tree based ensemble such as random forest
-\citep{breiman2001random}. The tree ensemble associates a variable importance
-score \citep{louppe2013understanding} to each neuron used in the predictions,
-which is used as a degree of associate. The following parameters are used
-$10000$ trees, $\log_2{p}$ variables are randomly selected to split tree nodes
-and the maximal tree depth is constrained to 1, 2 or 3. \textcolor{red}{AJ Which
-depth is represented on the graph?}
-\end{itemize}
+%% \item \textbf{GENIE3} \citep{huynhthu2010inferring} translates the inference
+%% of the network of $p$ neurons into $p$ supervised learning tasks. For each
+%% task, the fluorescence of a neuron is predicted from the fluorescence of all
+%% other neurons using a tree based ensemble such as random forest
+%% \citep{breiman2001random}. The tree ensemble associates a variable importance
+%% score \citep{louppe2013understanding} to each neuron used in the predictions,
+%% which is used as a degree of associate. The following parameters are used
+%% $10000$ trees, $\log_2{p}$ variables are randomly selected to split tree nodes
+%% and the maximal tree depth is constrained to 1, 2 or 3. \textcolor{red}{AJ Which
+%% depth is represented on the graph?}
+%% \end{itemize}
 
-\subsection*{Partial correlation improves over state-of-the-art methods}
+%% \subsection*{Partial correlation improves over state-of-the-art methods}
 
-Figure \ref{fig:curves} shows the ROC curve  and precision-recall curve
-for correlation, GTE and partial correlation on the \textit{normal-2}
-dataset. The partial correlation outperforms other state-of-the-art methods
-by at least factor of 2 in AUPRC reaching $0.347$ and an increased of $0.03$ in
+Partial correlation clearly outperforms all other methods. The improvement is more important in terms of AUPRC bu by about a factor
+of 2 in AUPRC reaching $0.347$ and an increased of $0.03$ in
 AUROC. Averaging Partial correlation matrix over a wide of parameters
-further improves AUPRC to $0.389$ and improve AUROC by $0.009$.
-Two reasons might explain such differences: (i) only the partial
+further improves AUPRC to $0.389$ and improve AUROC by $0.009$.  Two
+reasons might explain such differences: (i) only the partial
 correlation-based methods and GENI3 at lesser extent distinguish
 direct links from indirect one, (ii) simulated networks from the
-\citep{stetter2012model} generator or neural networks in general could be
-reduced to a linear model after pre-processing. Those results
+\citep{stetter2012model} generator or neural networks in general could
+be reduced to a linear model after pre-processing. Those results
 generalizes over the other datasets see Appendix \textcolor{red}{REF}.
 
-\begin{figure}[bth]
+\begin{figure}[t]
 \centering
@@
 \subfigure[Precision-recall curves]{\includegraphics[width=0.45\textwidth]{images/curve_pr} \label{fig:pr_curve}}
-\caption{The weighted average of partial correlation matrix, winning approach
-         of the challenge, yields better than AUROC and AUPRC than all
-         other state-of-the-art methods. (parameters: $\tau=0.11$ except for
-         averaged partial correlation method, partial correlation used
-         filter $f_1$). Area under the curves are given between $()$
-         for the corresponding methods.}
+\caption{ROC (left) and PR (right) curves on \text{normal-2} with different methods. Area under the curves are reported in the legend for each method.}
+
+%% The weighted average of partial correlation matrix, winning approach
+         %% of the challenge, yields better than AUROC and AUPRC than all
+         %% other state-of-the-art methods. (parameters: $\tau=0.11$ except for
+         %% averaged partial correlation method, partial correlation used
+         %% filter $f_1$). Area under the curves are given between $()$
+         %% for the corresponding methods.
+%}
 \label{fig:curves}
@@
 
-\textcolor{red}{Only one GENI3, thus it can't be observed.}
-As observed on Figure \ref{fig:curves}, the GENIE3 performance increases with
-deeper trees while being still computationally feasible. The reason is twofold.
-First, the deeper the tree, the larger is the conditioning. \textcolor{red}{AJ:
-conditioning?} As it was observed in the comparison between correlation and
-partial correlation, it screens indirect links in the inferred network.
-\textcolor{red}{AJ: I don't understand the link with GENIE3} Second, the number
-of small trees need to be much higher than deep trees in order to observe - and
-evaluate - all pairs.  However, as suggested by \cite{louppe2014understanding},
-limiting the maximal depth of trees may help to improve the variable importance
-computing, i.e. inferring the degree of association. \textcolor{red}{AJ: there
-is no explanation of why it would be better apart for computational reason.}
-Therefore a trade-off  of the maximal depth may give the best of both worlds.
-\textcolor{red}{AJ:  Which tradeoff? Which worlds?}
+%% \textcolor{red}{Only one GENI3, thus it can't be observed.}
+%% As observed on Figure \ref{fig:curves}, the GENIE3 performance increases with
+%% deeper trees while being still computationally feasible. The reason is twofold.
+%% First, the deeper the tree, the larger is the conditioning. \textcolor{red}{AJ:
+%% conditioning?} As it was observed in the comparison between correlation and
+%% partial correlation, it screens indirect links in the inferred network.
+%% \textcolor{red}{AJ: I don't understand the link with GENIE3} Second, the number
+%% of small trees need to be much higher than deep trees in order to observe - and
+%% evaluate - all pairs.  However, as suggested by \cite{louppe2014understanding},
+%% limiting the maximal depth of trees may help to improve the variable importance
+%% computing, i.e. inferring the degree of association. \textcolor{red}{AJ: there
+%% is no explanation of why it would be better apart for computational reason.}
+%% Therefore a trade-off  of the maximal depth may give the best of both worlds.
+%% \textcolor{red}{AJ:  Which tradeoff? Which worlds?}
 
-\subsection*{Area under the ROC curve a poor metric for network inference}
+\subsection*{ROC versus PR curves}
 
-The best method only infers the \textbf{undirected} network by giving the same
-degree of association to both edges $(i,j)$ and $(j,i)$. This is quite
-surprising considering the problem statement. Trying to direct links could be
-more penalizing than rewarding. For example, symmetrizing the degree of
-association matrix does not necessarily degrade AUPRC and AUROC.
+%% The best method only infers the \textbf{undirected} network by giving the same
+%% degree of association to both edges $(i,j)$ and $(j,i)$. This is quite
+%% surprising considering the problem statement. Trying to direct links could be
+%% more penalizing than rewarding. For example, symmetrizing the degree of
+%% association matrix does not necessarily degrade AUPRC and AUROC.
 
-If the inferred network corresponds to the undirected network, it would
-already yield high AUROC score for instance $\approx 0.996$ on
-\textit{normal-1}. Infering edge directivity is likely to be counter-
-productive or yield small gain. By contrast, the same experiment with AUPRC
-would yield a score of $\approx 0.789$ on \textit{normal-1}. Thus inferring
-correctly directivity would be more rewarding in AUPRC term.
+%% If the inferred network corresponds to the undirected network, it would
+%% already yield high AUROC score for instance $\approx 0.996$ on
+%% \textit{normal-1}. Infering edge directivity is likely to be counter-
+%% productive or yield small gain. By contrast, the same experiment with AUPRC
+%% would yield a score of $\approx 0.789$ on \textit{normal-1}. Thus inferring
+%% correctly directivity would be more rewarding in AUPRC term.
 
-% Interestingly, methods that takes into account directivity, namely GTE and
-% GENIE3, improve their AUROC and AUPRC by giving the same way to directed edges.
-% (in particular see GTE and GTE(undirected) in Figure \ref{fig:pr_curve}
-% \textcolor{red}{AJ: Figure \ref{fig:curves}  contradicts this message,
-% especially pr-curve. AS:And now?} and Table \ref{tab:tab1} in Appendix \textcolor{red}{REF}).
-% Trying to detect the link direction is more penalizing than rewarding.
+%% % Interestingly, methods that takes into account directivity, namely GTE and
+%% % GENIE3, improve their AUROC and AUPRC by giving the same way to directed edges.
+%% % (in particular see GTE and GTE(undirected) in Figure \ref{fig:pr_curve}
+%% % \textcolor{red}{AJ: Figure \ref{fig:curves}  contradicts this message,
+%% % especially pr-curve. AS:And now?} and Table \ref{tab:tab1} in Appendix \textcolor{red}{REF}).
+%% % Trying to detect the link direction is more penalizing than rewarding.
 
-The area under the ROC curve is not a consistent metric with respect to the
-problem statement. A clear hierarchy is also difficult to derive from ROC
-curves as shown on Figure \ref{fig:roc_curve}. We advice to avoid the AUROC for
-the assessment of network inference method. An alternative would be to assess
-network inference using the area under the precision-recall curve (AUPRC).
-Those conclusions are in line with \cite{schrynemackers2013protocols}.
+%% The area under the ROC curve is not a consistent metric with respect to the
+%% problem statement. A clear hierarchy is also difficult to derive from ROC
+%% curves as shown on Figure \ref{fig:roc_curve}. We advice to avoid the AUROC for
+%% the assessment of network inference method. An alternative would be to assess
+%% network inference using the area under the precision-recall curve (AUPRC).
+%% Those conclusions are in line with \cite{schrynemackers2013protocols}.
 
@@
 
-In this paper, we present the winning method of the Connectomics challenge. Our
+In this paper, we present the best performing method of the Connectomics challenge. Our
 approach is simple and theoretically sounded and made of two main stages: the
@@
 % the paper.
+
 \bibliography{references}
@@
 \subsection*{Averaging the connectome inference from partial correlation statistics}
-
-In our experiments, we observed that the inference process is quite sensitive about the choice of the parameter value $\tau$ and the low-pass filter.
-Therefore, in order to reduce the variance of the results and thus the robustness of our approach, we perform an average over a range of parameter value $\tau$ from $0.100$ to $0.209$.
-We also perform a weighted average over the four low-pass filters with weights
-$weight_{f_1} = 1$, $weight_{f_2} = 0.9$, $weight_{f_3} = 0.7$ and $weight_{f_4} = 0.01$, tuned to maximize the ROC AUC on \textit{normal-1}.
-The weights were adjusted to take into account that some filters outperform other but there is information hold in every filter.
 

### 2014-06-26 article.tex

@@
 \end{align}
-yielding the Figure \ref{fig:threshold_curve}.
+yielding Figure \ref{fig:threshold_curve}.
 As we can see, the processed signal only contains clean spikes.
 
-The objective of the last step of our filtering procedure is to decrease the importance of spikes that occur when there is a high global activity in the network with respect to  spikes that occur during normal activity.
-Indeed, we have conjectured that when a large part of the network is firing, the rate at which observations are made is not high enough for being able to detect interactions and, that it would therefore be preferrable to lower their importance by changing appropriatly their magnitude.
-Additionnally, it is well-known that neurons may also spike because of a global high activity (see \cite{stetter2012model}).
-In such  context, detecting pairwise neuron interactions from the firing activity is meaningless.
-Accordingly, we have chosen to apply to the signal outputted by $h$ the following function  
+The objective of the last step of our filtering procedure is to decrease the
+importance of spikes that occur when there is a high global activity in the
+network with respect to  spikes that occur during normal activity. Indeed, we
+have conjectured that when a large part of the network is firing, the rate at
+which observations are made is not high enough for being able to detect
+interactions and, that it would therefore be preferrable to lower their
+importance by changing appropriatly their magnitude. Additionnally, it is
+well-known that neurons may also spike because of a global high activity
+\citep{stetter2012model}. In such  context, detecting pairwise neuron
+interactions from the firing activity is meaningless. As such,
+the signal output by $h$ is finally applied to the following function
 \begin{align}
- w(x^{t}_i) &= (x^{t}_i + 1 )^{1 + \frac{1}{\sum_{j} x^{t}_j}}.
+ w(x^{t}_i) &= (x^{t}_i + 1 )^{1 + \frac{1}{\sum_{j} x^{t}_j}},
 \end{align}
-which effect is to magnify the importance of spikes that occur in case of low global activity. Note that the particular case where $\sum_{j} x^{t}_j$ equals $0$ is solved by setting $w(x^{t}_i) = 1$.
+which effect is to magnify the importance of spikes that occur in case of low global activity (measured by $\sum_{j} x^{t}_j$), as observed for instance around $t=4\text{s}$ in the figure.
+Note that the particular case where there is no activity, i.e., $\sum_{j} x^{t}_j = 0$, is solved by setting $w(x^{t}_i) = 1$.
 
-To summarize, the full signal processing pipeline of our simplified (resp. tuned)
-approach is defined by the composed function $w \circ h \circ g \circ f_1$
-(resp. $f_2$). When applied to the raw signal of Figure \ref{fig:original_curve}, it outputs the signal shown in Figure \ref{fig:weight_curve}.
+To summarize, the full signal processing pipeline of our simplified (resp.
+tuned) approach is defined by the composed function $w \circ h \circ g \circ
+f_1$ (resp. $f_2$). When applied to the raw signal of Figure
+\ref{fig:original_curve}, it outputs the signal shown in Figure
+\ref{fig:weight_curve}.
 
@@
 level and pre-processing) that was used for the challenge.
-
-%\paragraph{ROC versus PR curves.} While only ROC was , we argue here that PR scores are more appropriate in this context.
 
@@
 
+In our experiments, we observed that the inference process is quite sensitive about the choice of the parameter value $\tau$ and the low-pass filter.
+Therefore, in order to reduce the variance of the results and thus the robustness of our approach, we perform an average over a range of parameter value $\tau$ from $0.100$ to $0.209$.
+We also perform a weighted average over the four low-pass filters with weights
+$weight_{f_1} = 1$, $weight_{f_2} = 0.9$, $weight_{f_3} = 0.7$ and $weight_{f_4} = 0.01$, tuned to maximize the ROC AUC on \textit{normal-1}.
+The weights were adjusted to take into account that some filters outperform other but there is information hold in every filter.
+
 \subsection*{Connectome inference from pairwise interaction statistics}
+
+Since partial correlation statistics is a symmetric measure and the connectome is a directed graph, it should be rewarding to detect the edge orientation.
+In this section, we will present a heuristic trying to retrieve directivity.
+However, considering the argument in Section \ref{sec:results}, the additional gain margin of this approach compared to the undirected method is extremely limited.
+
+The heuristic is based on the following observation. The rise of fluorescence of a neuron indicates its activation.
 

### 2014-06-26 article.tex
appendix : directivity

--- 2014-06-26 article.tex
@@
 As a computation trick, it appears that using a parametrized hard-threshold filter slighlty improves performances.
-Introducing the parameter $c$ in function $h$ yields to an optimized filter denoted as $h^*$
-\begin{align}
+Introducing the parameter $c$ in function $h$ yields to an optimized filter denoted as $h^*$ \begin{align}
 h^*(x^t_i) = (x_i^t)^c \text{ } \mathbb{1}(x_i^t \ge \tau) \text{ with } \tau > 0,
@@
 
-The magnification can also be optimized by adjusting the effect differently with respect to the global activity. In that sense, we introduce the following function
-\begin{align}
+The magnification can also be optimized by adjusting the effect differently with respect to the global activity. In that sense, we introduce the following function \begin{align}
  w^*(x^{t}_i) &= {(x^{t}_i + 1 )^{\left (1 + \frac{1}{\sum_{j} x^{t}_j}\right )}}^{m}
@@
 
-In our experiments, we observed that the inference process is quite sensitive about the choice of the parameter value $\tau$ and the low-pass filter.
-Therefore, in order to reduce the variance of the results and thus the robustness of our approach, we perform an average over a range of parameter value $\tau$ from $0.100$ to $0.209$.
-We also perform a weighted average over the four low-pass filters with weights
-$weight_{f_1} = 1$, $weight_{f_2} = 0.9$, $weight_{f_3} = 0.7$ and $weight_{f_4} = 0.01$, tuned to maximize the ROC AUC on \textit{normal-1}.
-The weights were adjusted to take into account that some filters outperform other but there is information hold in every filter.
+In our experiments, we observed that the inference process is quite sensitive
+about the choice of the parameter value $\tau$ and the low-pass filter.
+Therefore, in order to reduce the variance of the results and thus the
+robustness of our approach, we perform an average over a range of parameter
+value $\tau$ from $0.100$ to $0.209$. We also perform a weighted average over
+the four low-pass filters with weights  $weight_{f_1} = 1$, $weight_{f_2} =
+0.9$, $weight_{f_3} = 0.7$ and $weight_{f_4} = 0.01$, tuned to maximize the
+ROC AUC on \textit{normal-1}. The weights were adjusted to take into account
+that some filters outperform other but there is information hold in every
+filter.
 
@@
 
-Since partial correlation statistics is a symmetric measure and the connectome is a directed graph, it should be rewarding to detect the edge orientation.
-In this section, we will present a heuristic trying to retrieve directivity.
-However, considering the argument in Section \ref{sec:results}, the additional gain margin of this approach compared to the undirected method is extremely limited.
+Since partial correlation statistics is a symmetric measure and the connectome
+is a directed graph, it should be rewarding to detect the edge orientation. In
+this section, we will present a heuristic trying to retrieve directivity.
+However, considering the argument in Section \ref{sec:results}, the additional
+gain margin of this approach compared to the undirected method is extremely
+limited.
 
-The heuristic is based on the following observation. The rise of fluorescence of a neuron indicates its activation.
+The heuristic is based on the following observation. The rise of fluorescence
+of a neuron indicates its activation. If another neuron is activated after a
+slight delay, this could have been caused by the activation of the first
+neuron and therefore highlight a (direct) directed relationship between the
+two neurons. With that in mind, the heuristic principle is to count the number
+of such events occurred between neurons $i$ and $j$ for consecutive time
+steps. It can be done by counting the number of times that a transition from
+neuron $i$ to neuron $j$ for two consecutive time steps, or mathematically we
+compute for each pair $(i,j)$
+
+\begin{align}
+s_{ij} = \sum_{t=1}^{T - 1} \mathbb{1}(x_j^{t+1} - x_i^t \in \left[\phi_1, \phi_2\right])
+\end{align}
+where $\phi_1$ and $\phi_2$ are parameters of the heuristic.
+
+Two issues may be spotted. First, this heuristic is not able to distinguish a
+directed relationships if both neurons are activated in the same time step and
+may wrongly characterize indirect relationships because of the time
+resolution. Second, it may be necessary to take into account $s_{ji}$ to
+estimate the quality of the pairwise coefficient $s_{i,j}$. Indeed, if both
+coefficients are similar ($s_{ij} \sim s_{ji}$) the directivity can not be
+inferred since the order of fluorescent rising is not well defined. On the
+contrary, different coefficients $s_{ij}$ and $s_{ji}$ mean that an order of
+fluorescent rising is well established and observable. There we choose to
+compute a differential pairwise coefficient $z_{ij}$ defined by the following
+equation
+
+\begin{align}
+z_{ij} = \sum_{t=1}^{T - 1}
+    \mathbb{1}(x_j^{t+1} - x_i^t \in \left[\phi_1, \phi_2 \right]) -
+    \mathbb{1}(x_i^{t+1} - x_j^t \in \left[\phi_1, \phi_2 \right]),
+\end{align}
+where $T$ is the number of time steps, $\phi_1$ and $\phi_2$ are parameters.
+
+At the light of the poor results of this heuristic taken on its own summarized
+on Table \ref{tab:} as \textit{directivity}, we use it to make asymmetric the
+degree of association matrix using partial correlation statistics. We expect
+that when the heuristic is highly confident (i.e., $z_{i,j} \gg 0 \gg
+z_{j,i}$) the degree of association   of edge $(i,j)$ is increased while the
+degree of association corresponding to the edge $(j,i)$ is reduced. Even if
+this adjustment is subtle, it might have a slight positive effect on the ROC
+AUC.
 

### 2014-06-26 article.tex
section 4 suite

--- 2014-06-26 article.tex
@@
 
-In the bottom part of Table \ref{tab:comparison}, the proposed
-approach is compared with three other methods: standard (Pearson)
-correlation (PC), generalized transfer entropy (GTE), and GENIE3. ROC
-and PR curves on the \textit{normal-2} network are shown for all
-methods in Figure \ref{fig:}. Pearson correlation measures the
-unconditional linear (in)dependence between variables and it should
-thus not be able to filter out indirect interactions between
-neurons. GTE \citep{stetter2012model} was proposed as a baseline for
-the challenge. This method builds on Transfer Entropy to measure the
-association between two neurons. Unlike our approach, it can predict
-the direction of the edges. GENIE3 \citep{huynhthu2010inferring} is a
-gene regulatory network inference method that was the best performer
-of the DREAM5 challenge \cite{dream5paper}. When transposed to neural
-networks, this method uses as a confidence score for the edge going
-from neuron $i$ to neuron $j$ the importance score of variable $X_i$
-in a Random Forests model trying to predict $X_j$ from all variables
-in $X\setminus X_j$. To reduce computing times of this method, we had
-to reduce each tree in the Random Forests model to a maximum depth of
-3. This constraint potentially severly affects the performance of this
-method with respect to the use of fully grown trees. We nevertheless
-provide these results for comparison purpose. PC and GENIE3 were both
-applied on the same pre-filtered time series as partial
-correlation. For GENIE3, we built 10000 trees per neuron and we used
-default settings for all other parameters (except for the maximal tree
-depth). For GTE, we reproduced the exact same setting (conditioning
-level and pre-processing) that was used for the challenge.
+In the bottom of Table \ref{tab:comparison}, we provide as a comparison the
+performance of three other methods: standard (Pearson) correlation (PC),
+generalized transfer entropy (GTE), and GENIE3. ROC and PR curves on the
+\textit{normal-2} network are shown for all methods in Figure
+\ref{fig:}. Pearson correlation measures the unconditional linear
+(in)dependence between variables and it should thus not be able to filter out
+indirect interactions between neurons. GTE \citep{stetter2012model} was
+proposed as a baseline for the challenge. This method builds on Transfer
+Entropy to measure the association between two neurons. Unlike our approach, it
+can predict the direction of the edges. GENIE3 \citep{huynhthu2010inferring} is
+a gene regulatory network inference method that was the best performer of the
+DREAM5 challenge \cite{dream5paper}. When transposed to neural networks, this
+method uses as a confidence score for the edge going from neuron $i$ to neuron
+$j$ the importance score of variable $X_i$ in a Random Forests model trying to
+predict $X_j$ from all variables in $X\setminus X_j$. To reduce computing times
+of this method, we had to reduce each tree in the Random Forests model to a
+maximum depth of 3. This constraint potentially severly affects the performance
+of this method with respect to the use of fully grown trees. We nevertheless
+provide these results for comparison purpose. PC and GENIE3 were both applied
+on the same pre-filtered time series as partial correlation. For GENIE3, we
+built 10000 trees per neuron and we used default settings for all other
+parameters (except for the maximal tree depth). For GTE, we reproduced the
+exact same setting (conditioning level and pre-processing) that was used for
+the challenge.
 
@@
 
-Partial correlation clearly outperforms all other methods. The improvement is more important in terms of AUPRC bu by about a factor
-of 2 in AUPRC reaching $0.347$ and an increased of $0.03$ in
-AUROC. Averaging Partial correlation matrix over a wide of parameters
-further improves AUPRC to $0.389$ and improve AUROC by $0.009$.  Two
-reasons might explain such differences: (i) only the partial
-correlation-based methods and GENI3 at lesser extent distinguish
-direct links from indirect one, (ii) simulated networks from the
-\citep{stetter2012model} generator or neural networks in general could
-be reduced to a linear model after pre-processing. Those results
-generalizes over the other datasets see Appendix \textcolor{red}{REF}.
+Partial correlation and average partial correlation clearly outperforms all
+other methods. The improvement is more important in terms of AUPRC than in
+terms of AUROC. As expected, Pearson correlation performs very poorly in terms
+of AUPRC. GTE and GENIE3 works much better but these two methods are
+nevertheless clearly below partial correlation. Among these two methods, GTE is
+slightly better in terms of AUROC, while GENIE3 is significantly better in
+terms of AUPRC. Given that we had to limit this latter method for computational
+reasons, these results are very promising and a comparison with the full GENIE3
+approach is certainly part of our future works.
+
+%% bu by about a factor
+%% of 2 in AUPRC reaching $0.347$ and an increased of $0.03$ in
+%% AUROC. Averaging Partial correlation matrix over a wide of parameters
+%% further improves AUPRC to $0.389$ and improve AUROC by $0.009$.  Two
+%% reasons might explain such differences: (i) only the partial
+%% correlation-based methods and GENI3 at lesser extent distinguish
+%% direct links from indirect one, (ii) simulated networks from the
+%% \citep{stetter2012model} generator or neural networks in general could
+%% be reduced to a linear model after pre-processing. Those results
+%% generalizes over the other datasets see Appendix \textcolor{red}{REF}.
 

### 2014-06-26 article.tex
modified tab 1 + correction

--- 2014-06-26 article.tex
@@
 No  filtering       					& 0.777 & 0.767 & 0.772 & 0.774 & 0.070 & 0.064 & 0.068 & 0.072\\
-$ h \circ g \circ f_1$                 & 0.925 & 0.925 & 0.924 & 0.923 & 0.322 & 0.324 & 0.323 & 0.312\\
-$ w \circ h \circ g \circ f_1$               & 0.931 & 0.930 & 0.928 & 0.927 & 0.333 & 0.334 & 0.327 & 0.313\\
-+ PCA         & 0.932 & 0.931 & 0.930 & 0.928 & 0.364 & 0.366 & 0.359 & 0.344\\
-Averaging           & 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388\\
-Full method &\\
+$ h \circ g \circ f_1$                  & 0.923 & 0.925 & 0.923 & 0.922 & 0.311 & 0.315 & 0.313 & 0.304\\
+$ w \circ h \circ g \circ f_1$          & 0.931 & 0.929 & 0.928 & 0.926 & 0.326 & 0.323 & 0.319 & 0.303\\
++ PCA         							& 0.932 & 0.930 & 0.928 & 0.926 & 0.355 & 0.353 & 0.350 & 0.333\\
+Averaging           					& 0.938 & 0.936 & 0.936 & 0.932 & 0.391 & 0.389 & 0.385 & 0.374\\
+Full method           					& 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388\\
 \hline
-%Averaging + Directivity & 0.944 & 0.943 & 0.942 & 0.940 & 0.404 & 0.405 & 0.399 & 0.389\\
-Correlation &\\
-GTE & \\
+Correlation & 0.886 & 0.884 & 0.891 &  0.877 & 0.153 & 0.145 & 0.170 & 0.132\\
+GTE & 0.890 & 0.893 & 0.894 & 0.873 & 0.171 & 0.174 & 0.197 & 0.142\\
 GENIE3 &\\
@@
 provide these results for comparison purpose. PC and GENIE3 were both
-applied on the same pre-filtered time series as partial
-correlation. For GENIE3, we built 10000 trees per neuron and we used
+applied on the same pre-filtered time series ($g \circ f_1$). For GENIE3, we built 10000 trees per neuron and we used
 default settings for all other parameters (except for the maximal tree
@@
 \begin{align}
-s_{ij} = \sum_{t=1}^{T - 1} \mathbb{1}(x_j^{t+1} - x_i^t \in \left[\phi_1, \phi_2\right])
+s_{ij} = \sum_{t=1}^{T - 1} \mathbb{1}((x_j^{t+1} - x_i^t) \in \left[\phi_1, \phi_2\right])
 \end{align}
@@
 z_{ij} = \sum_{t=1}^{T - 1}
-    \mathbb{1}(x_j^{t+1} - x_i^t \in \left[\phi_1, \phi_2 \right]) -
-    \mathbb{1}(x_i^{t+1} - x_j^t \in \left[\phi_1, \phi_2 \right]),
+    \mathbb{1}((x_j^{t+1} - x_i^t) \in \left[\phi_1, \phi_2 \right]) -
+    \mathbb{1}((x_i^{t+1} - x_j^t) \in \left[\phi_1, \phi_2 \right]),
 \end{align}
@@
 \hat{Z}: z_{ij} = \sum_{t=1}^{T - 1}
-    \mathbb{1}(x_j^{t+1} - x_i^t \in \left[f_1, f_2 \right]) -
-    \mathbb{1}(x_i^{t+1} - x_j^t \in \left[f_1, f_2 \right]), \forall i, j \in V
+    \mathbb{1}((x_j^{t+1} - x_i^t) \in \left[f_1, f_2 \right]) -
+    \mathbb{1}((x_i^{t+1} - x_j^t) \in \left[f_1, f_2 \right]), \forall i, j \in V
 \]

### 2014-06-26 article.tex

--- 2014-06-26 article.tex
@@
 provide these results for comparison purpose. PC and GENIE3 were both applied
-on the same pre-filtered time series as partial correlation. For GENIE3, we
+on the same pre-filtered time series ($g \circ f_1$). For GENIE3, we
 built 10000 trees per neuron and we used default settings for all other

### 2014-06-26 article.tex
wording

@@
 significantly AUPRC scores. Taking the average over various parameter
-setting gives an improvement of 10\% in both AUROC and AUPRC. The last
+setting gives an improvement of 10\% \textcolor{red}{AS:AUPRC ok but AUROC?} in both AUROC and AUPRC. The last
 row shows the final performance of the method specifically tuned for
-the challenge (see the Appendix for all details). Although this tuning
+the challenge (see the Appendix \ref{app:optimized} for all details). Although this tuning
 was decisive to obtain the best performance at the challenge, it does
@@
 \end{tabular}
-\caption{TODO \textcolor{red}{version simple!!}}
+\caption{Top: ROC (left) and PR (right) AUC on \text{normal-1,2,3,4} with partial correlation and different filtering functions except the last two rows with an average over various parameter settings.
+Bottom: ROC (left) and PR (right) AUC on \text{normal-1,2,3,4} with different methods.}
 \label{tab:tab3}
@@
 
-Sections~\ref{sec:filter}~to~\ref{sec:results} describe a simplified version
-of the actual winning method. However, one could be interesting in the full
-description. This appendix will therefore follow the progress of the main
-paper highlighting optimizations.
+This section is a complete description of the method specifically tuned for the challenge.
+Basically, it is an optimized version of the method presented in Sections~\ref{sec:filter}~to~\ref{sec:results}, therefore only differences between both version of our method will be highlighted.
 
-Let us remark that parameter value choices were made to maximize ROC AUC score
-on \textit{normal-1} and, to a lesser extent, \textit{normal-4}.
+Let us remark that tuning
+was mainly done on the \textit{normal-1} and \textit{normal-4}
+datasets, which explains why these two networks are slightly better
+retrieved than the others.
 
@@
 
-Theses filters, even if individually they lead to less good performances of the inference algorithm than filters $f_1$ and
-$f_2$, the averaging approach over these four low-pass
-filters gets better.
+Theses filters lead, taken individually, to worse performances
+ than filters $f_1$ and
+$f_2$ but the averaging approach over all low-pass
+filters gets better \textcolor{red}{AS:Does it necessary to show it numerically?}.
 
-As a computation trick, it appears that using a parametrized hard-threshold filter slighlty improves performances.
-Introducing the parameter $c$ in function $h$ yields to an optimized filter denoted as $h^*$ \begin{align}
+As a computation trick, it appears that using a parametrized hard-threshold filter slightly improves performances.
+Introducing the parameter $c$ in function $h$ yields to an optimized filter \begin{align}
 h^*(x^t_i) = (x_i^t)^c \text{ } \mathbb{1}(x_i^t \ge \tau) \text{ with } \tau > 0,
@@
 
-The magnification can also be optimized by adjusting the effect differently with respect to the global activity. In that sense, we introduce the following function \begin{align}
+The magnification can also be optimized by adjusting differently the effect depending on the global activity and the low-pass filter used.
+In that sense, we introduce the following function \begin{align}
  w^*(x^{t}_i) &= {(x^{t}_i + 1 )^{\left (1 + \frac{1}{\sum_{j} x^{t}_j}\right )}}^{m}
@@
 value $\tau$ from $0.100$ to $0.209$. We also perform a weighted average over
-the four low-pass filters with weights  $weight_{f_1} = 1$, $weight_{f_2} =
-0.9$, $weight_{f_3} = 0.7$ and $weight_{f_4} = 0.01$, tuned to maximize the
-ROC AUC on \textit{normal-1}. The weights were adjusted to take into account
-that some filters outperform other but there is information hold in every
-filter.
+the four low-pass filters with the following parameters
+
+\begin{align*}
+weight_{f_1} &= 1,\\
+weight_{f_2} &= 0.9, \\
+weight_{f_3} &= 0.7, \\ 
+weight_{f_4} &= 0.01
+\end{align*}
+
+tuned to maximize the
+ROC AUC on \textit{normal-1}.
 
@@
 
-The algorithm propose in sections \ref{sec:filter} and \ref{sec:inference} has been optimized at its extreme limit to win the challenge.
+% The algorithm propose in sections \ref{sec:filter} and \ref{sec:inference} has been optimized at its extreme limit to win the challenge.
 In this section, we will describe the full tuned algorithm and present some results.
 
-Note that our parameter tuning was mainly
-done on the \textit{normal-1} dataset and partly on \textit{normal-4} dataset,
-therefore it may justify why these networks are better retrieved despite the
-fact that some might be simpler to infer.
+% Note that our parameter tuning was mainly
+% done on the \textit{normal-1} dataset and partly on \textit{normal-4} dataset,
+% therefore it may justify why these networks are better retrieved despite the
+% fact that some might be simpler to infer.
 
-% Introduce a custom solution to make the Y matrix asymmetric
-% Introduce directivity
-\textcolor{red}{Est-ce qu'on ne le ferait pas passer dans l'appendice B? Ou du moins l'équation?}
-Since partial correlation is a symmetric measure, the causal mechanism behind the
-interaction ($A$ directly causes $B$, $B$ directly causes $A$ or both) can not
-be directly inferred\footnote{Also note that two other causal mechanisms might be
-implied while having a non-zero partial coefficient: (i) a pair of variables
-is induced by a common (hidden) variable; (ii) $A$ (respectively $B$) is
-conditionally correlated to a hidden variable affecting $B$ (resp. $A$)
-\citep{de2004discovery}.}.
-In order to retrieve causal information, we developed an
-heuristics based on the following observation. The rise of fluorescence
-indicates the activation of a neuron $i$. If a neuron $j$ have also
-an increased of fluorescence after a slight delay, this could have been
-caused by the neuron $i$. Thus, we count whenever
-such events occurred between consecutive time steps
-\[
-\hat{Z}: z_{ij} = \sum_{t=1}^{T - 1}
-    \mathbb{1}((x_j^{t+1} - x_i^t) \in \left[f_1, f_2 \right]) -
-    \mathbb{1}((x_i^{t+1} - x_j^t) \in \left[f_1, f_2 \right]), \forall i, j \in V
-\]
-where $f_1$ and $f_2$ are parameters of the method.
-Finally, the weighted average of correlation matrices is combined with $Z$ such
-that $Z$ has a contribution of $0.3\%$ to the prediction of an edge.
+% % Introduce a custom solution to make the Y matrix asymmetric
+% % Introduce directivity
+% \textcolor{red}{Est-ce qu'on ne le ferait pas passer dans l'appendice B? Ou du moins l'équation?}
+% Since partial correlation is a symmetric measure, the causal mechanism behind the
+% interaction ($A$ directly causes $B$, $B$ directly causes $A$ or both) can not
+% be directly inferred\footnote{Also note that two other causal mechanisms might be
+% implied while having a non-zero partial coefficient: (i) a pair of variables
+% is induced by a common (hidden) variable; (ii) $A$ (respectively $B$) is
+% conditionally correlated to a hidden variable affecting $B$ (resp. $A$)
+% \citep{de2004discovery}.}.
+% In order to retrieve causal information, we developed an
+% heuristics based on the following observation. The rise of fluorescence
+% indicates the activation of a neuron $i$. If a neuron $j$ have also
+% an increased of fluorescence after a slight delay, this could have been
+% caused by the neuron $i$. Thus, we count whenever
+% such events occurred between consecutive time steps
+% \[
+% \hat{Z}: z_{ij} = \sum_{t=1}^{T - 1}
+%     \mathbb{1}((x_j^{t+1} - x_i^t) \in \left[f_1, f_2 \right]) -
+%     \mathbb{1}((x_i^{t+1} - x_j^t) \in \left[f_1, f_2 \right]), \forall i, j \in V
+% \]
+% where $f_1$ and $f_2$ are parameters of the method.
+% Finally, the weighted average of correlation matrices is combined with $Z$ such
+% that $Z$ has a contribution of $0.3\%$ to the prediction of an edge.
 
-% For the directory method, only filters defined by Equations
-% \ref{eq:low-pass}, \ref{eq:high-pass} and \ref{eq:hard-treshold-filter} were
-% used.
+% % For the directory method, only filters defined by Equations
+% % \ref{eq:low-pass}, \ref{eq:high-pass} and \ref{eq:hard-treshold-filter} were
+% % used.
 

### 2014-06-26 article.tex
Template options
minor things

@@
 
- % The following command is just for this sample document:
-\newcommand{\cs}[1]{\texttt{\char`\\#1}}
-
- % change the arguments, as appropriate, in the following:
-%\jmlrvolume{1}
-%\jmlryear{2014}
-%\jmlrworkshop{\textcolor{red}{Neural Connectomics Workshop}}
-\jmlrproceedings{}{}
+\jmlryear{2014}
+\jmlrworkshop{Neural Connectomics Workshop: From Imaging to Connectivity}
+\jmlrauthors{A. Sutera et al}
 
@@
         Pierre Geurts}
-
- % Authors with different addresses:
- % \author{\Name{Author Name1} \Email{abc@sample.com}\\
- % \addr Address 1
- % \AND
- % \Name{Author Name2} \Email{xyz@sample.com}\\
- % \addr Address 2
- %}
-
-\editor{Editor's name}
- % \editors{List of editors' names}
 
@@
 \end{equation}
-where $\Sigma^{-1}$, known as the precision or concentration matrix, is the inverse of the covariance matrix $\Sigma$ of $X$.%%  Partial
+where $\Sigma^{-1}$, known as the precision or concentration matrix, is the inverse of the covariance matrix $\Sigma$ of $X$. %%  Partial
 %% correlation can be interpreted in several ways. The partial
@@
 
-\paragraph{Evaluation of the method}
+\paragraph{Evaluation of the method.}
 

### 2014-06-26 article.tex
cleanup table 1

@@
 
-\begin{abstract} In this work, we propose a simple, but yet efficient, method for the problem of connectome inference in
-calcium imaging data. The proposed algorithm is made of two steps. First,
-processing the raw signals to detect neural peak activities. Second, inferring
-the degree of association between neurons from partial correlation statistics.
-This paper summarizes the methodology that led us to win the Connectomics
-Challenge, proposes a simplified version of our method and finally discusses
-our results with respect to other inference methods.\end{abstract}
+\begin{abstract}
+In this work, we propose a simple, but yet efficient, method for the problem of
+connectome inference in calcium imaging data. The proposed algorithm is made of
+two steps. First, processing the raw signals to detect neural peak activities.
+Second, inferring the degree of association between neurons from partial
+correlation statistics. This paper summarizes the methodology that led us to
+win the Connectomics Challenge, proposes a simplified version of our method and
+finally discusses our results with respect to other inference methods.
+\end{abstract}
 
@@
 
-%%%%%%% !!!!!!!! \textcolor{red}{To improve (style):} !!!! %%%%%%%%
 The human brain is a complex biological
@@
 neural activity speed or the slow decay of fluorescence.
-%%%%%%%%%%% !!!!!!!!!!!!!! %%%%%%%%%%%%%%%%
 
@@
 observations $\{ x^t_i \in \mathbb{R} | i \in V, t = 1, \dots, T \}$ of $p$
-neurons for $T$ time intervals, the goal is to infer the set $E$ of connections in $G$.}
+neurons for $T$ time intervals, the goal is to infer the set $E$ of connections
+in $G$.}
 
@@
 \end{align}
-which effect is to magnify the importance of spikes that occur in case of low global activity (measured by $\sum_{j} x^{t}_j$), as observed for instance around $t=4\text{s}$ in the figure.
-Note that the particular case where there is no activity, i.e., $\sum_{j} x^{t}_j = 0$, is solved by setting $w(x^{t}_i) = 1$.
+which effect is to magnify the importance of spikes that occur in case of low
+global activity (measured by $\sum_{j} x^{t}_j$), as observed for instance
+around $t=4\text{s}$ in the figure. Note that the particular case where there
+is no activity, i.e., $\sum_{j} x^{t}_j = 0$, is solved by setting $w(x^{t}_i)
+= 1$.
 
@@
 \end{equation}
-where $\Sigma^{-1}$, known as the precision or concentration matrix, is the inverse of the covariance matrix $\Sigma$ of $X$. %%  Partial
+where $\Sigma^{-1}$, known as the precision or concentration matrix, is the inverse of the covariance matrix $\Sigma$ of $X$.%%  Partial
 %% correlation can be interpreted in several ways. The partial
@@
 replacing the exact inverse with an approximation using only the $M$
-first principal components of $\Sigma$~\citep{bishop2006pattern} (with
-$M$ set to $0.8 p$ in our experiments).
+first principal components \citep{bishop2006pattern} (with
+$M=0.8 p$ in our experiments).
 
@@
 
-\paragraph{Evaluation of the method.}
+\paragraph{Evaluation of the method}
 
@@
 
-\begin{table}[t]
-\caption{Evaluation of different methods on the four \textit{normal} datasets\label{tab:comparison}}
+\begin{table}[t]\label{tab:comparison}
+%\caption{Evaluation of different methods on the four \textit{normal} datasets\label{tab:comparison}}
 \centering
 \small
-\begin{tabular}{@{}l *{8}{c}@{}}
+\begin{tabular}{| l | c c c c | c c c c |}
 \hline
-  & \multicolumn{4}{c}{AUROC} & \multicolumn{4}{c}{AUPRC} \\
+& \multicolumn{4}{c|}{AUROC} & \multicolumn{4}{c|}{AUPRC} \\
+\textit{Method} $\backslash$ \textit{normal-} & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 \\
 \hline
-Methods $\backslash$ normal- & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 \\
+\hline
 No  filtering       					& 0.777 & 0.767 & 0.772 & 0.774 & 0.070 & 0.064 & 0.068 & 0.072\\
@@
 GTE & 0.890 & 0.893 & 0.894 & 0.873 & 0.171 & 0.174 & 0.197 & 0.142\\
-GENIE3 &\\
+GENIE3 & & & & & & & & \\
+\hline
 \end{tabular}
-\caption{Top: ROC (left) and PR (right) AUC on \text{normal-1,2,3,4} with partial correlation and different filtering functions except the last two rows with an average over various parameter settings.
+\caption{Top: ROC (left) and PR (right) AUC on \text{normal-1,2,3,4} with partial correlation and different filtering functions.
 Bottom: ROC (left) and PR (right) AUC on \text{normal-1,2,3,4} with different methods.}
-\label{tab:tab3}
 \end{table}
@@
 \subfigure[Precision-recall curves]{\includegraphics[width=0.45\textwidth]{images/curve_pr} \label{fig:pr_curve}}
-\caption{ROC (left) and PR (right) curves on \text{normal-2} with different methods. Area under the curves are reported in the legend for each method.}
-
+\caption{ROC (left) and PR (right) curves on \text{normal-2} with different methods. Areas under the curves are reported in the legend.}
 %% The weighted average of partial correlation matrix, winning approach

### 2014-06-26 article.tex
ref
workshop title

@@
 \jmlryear{2014}
-\jmlrworkshop{Neural Connectomics Workshop: From Imaging to Connectivity}
+\jmlrworkshop{Neural Connectomics Workshop}
 \jmlrauthors{A. Sutera et al}
@@
 \textit{normal-2} network are shown for all methods in Figure
-\ref{fig:}. Pearson correlation measures the unconditional linear
+\ref{fig:curves}. Pearson correlation measures the unconditional linear
 (in)dependence between variables and it should thus not be able to filter out

### 2014-06-26 article.tex
minor changes

--- 2014-06-26 article.tex
@@
 partial correlation coefficient $p_{i,j}$ between their corresponding
-random variables $X_i$ and $X_j$, defined by \cite{}:
+random variables $X_i$ and $X_j$, defined by:
 \begin{equation}
@@
 of partial correlation as an association measure has already been
-shown for the inference of gene regulatory networks \cite{xxx}.
+shown for the inference of gene regulatory networks
+\cite{de2004discovery,Schafer:2005}.
 %% Given a set of multivariate Gaussian
@@
 
-The top of Table \ref{tab:comparison} reports AUROC and AUPRC for all four networks
-using in each case partial correlation with different filtering
-functions. Except for the last two rows that uses PCA, the exact
-inverse of the covariance matrix was used in each case. These results
-clearly show the importance of the filters. AUROC increases in average from
-0.77 to 0.93. PCA does not really affect AUROC scores but it improves
-significantly AUPRC scores. Taking the average over various parameter
-setting gives an improvement of 10\% \textcolor{red}{AS:AUPRC ok but AUROC?} in both AUROC and AUPRC. The last
-row shows the final performance of the method specifically tuned for
-the challenge (see the Appendix \ref{app:optimized} for all details). Although this tuning
-was decisive to obtain the best performance at the challenge, it does
-not significantly improve neither AUROC nor AUPRC. Note that tuning
-was mainly done on the \textit{normal-1} and \textit{normal-4}
-datasets, which explains why these two networks are slightly better
-retrieved than the others.
+The top of Table \ref{tab:comparison} reports AUROC and AUPRC for all
+four networks using in each case partial correlation with different
+filtering functions. Except for the last two rows that uses PCA, the
+exact inverse of the covariance matrix was used in each case. These
+results clearly show the importance of the filters. AUROC increases in
+average from 0.77 to 0.93. PCA does not really affect AUROC scores but
+it improves significantly AUPRC scores. Taking the average over
+various parameter setting gives an improvement of 10\% in AUPRC but
+only a minor change in AUROC. The last row shows the final performance
+of the method specifically tuned for the challenge (see the Appendix
+\ref{app:optimized} for all details). Although this tuning was
+decisive to obtain the best performance at the challenge, it does not
+significantly improve neither AUROC nor AUPRC.
 
@@
 a gene regulatory network inference method that was the best performer of the
-DREAM5 challenge \cite{dream5paper}. When transposed to neural networks, this
+DREAM5 challenge \citep{marbach2012}. When transposed to neural networks, this
 method uses as a confidence score for the edge going from neuron $i$ to neuron
 $j$ the importance score of variable $X_i$ in a Random Forests model trying to
-predict $X_j$ from all variables in $X\setminus X_j$. To reduce computing times
-of this method, we had to reduce each tree in the Random Forests model to a
-maximum depth of 3. This constraint potentially severly affects the performance
-of this method with respect to the use of fully grown trees. We nevertheless
-provide these results for comparison purpose. PC and GENIE3 were both applied
-on the same pre-filtered time series ($g \circ f_1$). For GENIE3, we
-built 10000 trees per neuron and we used default settings for all other
-parameters (except for the maximal tree depth). For GTE, we reproduced the
-exact same setting (conditioning level and pre-processing) that was used for
-the challenge.
+predict $X_j$ from all variables in $X\setminus X_j$. To reduce the
+computational cost of this method, we had to limit each tree in the Random
+Forests model to a maximum depth of 3. This constraint potentially severly
+affects the performance of this method with respect to the use of fully grown
+trees. We nevertheless provide these results for comparison purpose. PC and
+GENIE3 were both applied on the same pre-filtered time series ($g \circ
+f_1$). For GENIE3, we built 10000 trees per neuron and we used default settings
+for all other parameters (except for the maximal tree depth). For GTE, we
+reproduced the exact same setting (conditioning level and pre-processing) that
+was used for the challenge.
 
@@
 
-Partial correlation and average partial correlation clearly outperforms all
+Partial correlation and average partial correlation clearly outperform all
 other methods. The improvement is more important in terms of AUPRC than in

### 2014-06-26 article.tex
citep
typo

@@
 shown for the inference of gene regulatory networks
-\cite{de2004discovery,Schafer:2005}.
+\citep{de2004discovery,Schafer:2005}.
 %% Given a set of multivariate Gaussian
@@
 or the value of the threshold $\tau$) in the combined function of the
-filtering and infering processes. One approach, that we will refered
+filtering and infering processes. One approach, further referred
 to as \textit{Averaged Partial correlation} statistics, for improving

### 2014-06-26 article.tex
wordings

@@
 which observations are made is not high enough for being able to detect
-interactions and, that it would therefore be preferrable to lower their
+interactions, and that it would therefore be preferrable to lower their
 importance by changing appropriatly their magnitude. Additionnally, it is
@@
 strength of the connection between two neurons $i$ and $j$, the
-partial correlation coefficient $p_{i,j}$ between their corresponding
+\textit{Partial correlation} coefficient $p_{i,j}$ between their corresponding
 random variables $X_i$ and $X_j$, defined by:
@@
 zero if and only if $X_i$ and $X_j$ are independent given all other
-variables in $X$, ie. $X_i \perp X_j|X^{-i,j}$ where $X^{-i,j}= X
+variables in $X$, i.e., $X_i \perp X_j|X^{-i,j}$ where $X^{-i,j}= X
 \setminus\{X_i,X_j\}$. Partial correlation thus measures conditional
-dependencies between variables. As an association measures between
+dependencies between variables. As an association measure between
 neurons, it should thus naturally only detect direct associations
@@
 Section~\ref{sec:results} why this only affects slightly its
-performances, with respect to the metric used in the Connectomics
+performance, with respect to the metric used in the Connectomics
 challenge.
 
-Practically, the computation of coefficient $p_{i,j}$ using Equation
+Practically, the computation of all $p_{i,j}$ coefficients using Equation
 \ref{eq:inverse} requires the estimation of the covariance matrix $\Sigma$
@@
 \citep{stetter2012model} of different neural networks of 1000 neurons
-and about 15000 edges each (ie., a network density of about
+and about 15000 edges each (i.e., a network density of about
 1.5\%). Each neuron is described by a calcium fluorescence time series
@@
 Since neurons are not self-connected in the ground truth networks
-(ie., $(i, i) \not \in E, \forall i \in V$), we have manually set the
+(i.e., $(i, i) \not \in E, \forall i \in V$), we have manually set the
 score of such edges to the minimal possible association score before

### 2014-06-26 article.tex
wordings

@@
 
-We report here experiments on the \textit{normal}-1,2,3, and 4
+We report here experiments on the \textit{normal-1,2,3}, and \textit{4}
 datasets provided by the organizers of the Connectomics
@@
 precision-recall curves against the ground truth network, which are
-summarized using the area under the curve, denoted respectively AUROC
+summarized using the area under the curve and respectively  denoted AUROC
 and AUPRC. Only the AUROC score was used to rank the challenge
@@
 more sensible metric for network inference, especially when network
-density is small (see e.g. \cite{schrynemackers2013protocols}).
+density is small (see e.g., \cite{schrynemackers2013protocols}).
 Since neurons are not self-connected in the ground truth networks
@@
 four networks using in each case partial correlation with different
-filtering functions. Except for the last two rows that uses PCA, the
+filtering functions. Except for the last two rows that use PCA, the
 exact inverse of the covariance matrix was used in each case. These
@@
 & \multicolumn{4}{c|}{AUROC} & \multicolumn{4}{c|}{AUPRC} \\
-\textit{Method} $\backslash$ \textit{normal-} & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 \\
+\textit{Method} $\backslash$ \textit{normal-} & \textit{1} & \textit{2} & \textit{3} & \textit{4} & \textit{1} & \textit{2} & \textit{3} & \textit{4} \\
 \hline
@@
 \hline
-Correlation & 0.886 & 0.884 & 0.891 &  0.877 & 0.153 & 0.145 & 0.170 & 0.132\\
+PC & 0.886 & 0.884 & 0.891 &  0.877 & 0.153 & 0.145 & 0.170 & 0.132\\
 GTE & 0.890 & 0.893 & 0.894 & 0.873 & 0.171 & 0.174 & 0.197 & 0.142\\
@@
 \end{tabular}
-\caption{Top: ROC (left) and PR (right) AUC on \text{normal-1,2,3,4} with partial correlation and different filtering functions.
-Bottom: ROC (left) and PR (right) AUC on \text{normal-1,2,3,4} with different methods.}
+\caption{Top: Performance on \textit{normal-1,2,3,4} with partial correlation and different filtering functions.
+Bottom: Performance on \textit{normal-1,2,3,4} with different methods.}
 \end{table}
@@
 method uses as a confidence score for the edge going from neuron $i$ to neuron
-$j$ the importance score of variable $X_i$ in a Random Forests model trying to
+$j$ the importance score of variable $X_i$ in a Random Forest model trying to
 predict $X_j$ from all variables in $X\setminus X_j$. To reduce the
 computational cost of this method, we had to limit each tree in the Random
-Forests model to a maximum depth of 3. This constraint potentially severly
+Forest model to a maximum depth of 3. This constraint potentially severly
 affects the performance of this method with respect to the use of fully grown
@@
 \subfigure[Precision-recall curves]{\includegraphics[width=0.45\textwidth]{images/curve_pr} \label{fig:pr_curve}}
-\caption{ROC (left) and PR (right) curves on \text{normal-2} with different methods. Areas under the curves are reported in the legend.}
+\caption{ROC (left) and PR (right) curves on \textit{normal-2} for the compared methods. Areas under the curves are reported in the legend.}
 %% The weighted average of partial correlation matrix, winning approach

### 2014-06-27 article.tex
typo
Typo

@@
 frequency, while low frequencies of the signal mainly correspond to the slow
-decay of fluorescence. To have a signal that only has high magnitude around instances where the spikes occur, the second step of our pipeline transforms the time series into its backward
+decay of fluorescence. To have a signal that only has high magnitudes around instances where the spikes occur, the second step of our pipeline transforms the time series into its backward
 difference
@@
 
-\paragraph{Comparison with other methods}
+\paragraph{Comparison with other methods.}
 
@@
 
-\subsection*{ROC versus PR curves}
+\subsection*{ROC versus PR curves.}
 

### 2014-06-27 article.tex
affiliations

--- 2014-06-26 article.tex
@@
 \jmlrworkshop{Neural Connectomics Workshop}
-\jmlrauthors{A. Sutera et al}
 
@@
 
-\author{Antonio Sutera,
+\author{\Name{Antonio Sutera,
     Arnaud Joly,
-        Vincent François-Lavet,
-        Aaron Qiu, \\
+        Vincent François-Lavet,\\
+        Aaron Qiu,
         Gilles Louppe,
@@
         Pierre Geurts}
+  \Email{a.sutera@ulg.ac.be}\\
+  \addr Department of EE and CS \& GIGA-R, University of Li\`ege, Belgium}
+
+%\jmlrauthors{A. Sutera et al}
+%\shortauthor{A. Sutera et al.}
 

### 2014-06-27 article.tex
section 4

@@
 various parameter setting gives an improvement of 10\% in AUPRC but
-only a minor change in AUROC. The last row shows the final performance
-of the method specifically tuned for the challenge (see the Appendix
-\ref{app:optimized} for all details). Although this tuning was
-decisive to obtain the best performance at the challenge, it does not
-significantly improve neither AUROC nor AUPRC.
+only a minor change in AUROC. The last row (``Full method'') shows the
+final performance of the method specifically tuned for the challenge
+(see the Appendix \ref{app:optimized} for all details). Although this
+tuning was decisive to obtain the best performance at the challenge,
+it does not significantly improve neither AUROC nor AUPRC.
 
@@
 predict $X_j$ from all variables in $X\setminus X_j$. To reduce the
-computational cost of this method, we had to limit each tree in the Random
-Forest model to a maximum depth of 3. This constraint potentially severly
-affects the performance of this method with respect to the use of fully grown
-trees. We nevertheless provide these results for comparison purpose. PC and
-GENIE3 were both applied on the same pre-filtered time series ($g \circ
-f_1$). For GENIE3, we built 10000 trees per neuron and we used default settings
-for all other parameters (except for the maximal tree depth). For GTE, we
-reproduced the exact same setting (conditioning level and pre-processing) that
-was used for the challenge.
+computational cost of this method, we had however to limit each tree in the
+Random Forest model to a maximum depth of 3. This constraint potentially
+severly affects the performance of this method with respect to the use of fully
+grown trees. We nevertheless provide these results for comparison purpose. PC
+and GENIE3 were both applied on the same pre-filtered time series as partial
+correlation ($h\circ g \circ f_1$). For GENIE3, we built 10000 trees per neuron
+and we used default settings for all other parameters (except for the maximal
+tree depth). For GTE, we reproduced the exact same setting (conditioning level
+and pre-processing) that was used for the challenge.
 
@@
 terms of AUROC. As expected, Pearson correlation performs very poorly in terms
-of AUPRC. GTE and GENIE3 works much better but these two methods are
+of AUPRC. GTE and GENIE3 work much better but these two methods are
 nevertheless clearly below partial correlation. Among these two methods, GTE is
@@
 approach is certainly part of our future works.
+
+The fact that our method is unable to predict edge directions does not seem to
+be a disadvantage with respect to GTE and GENIE3. Although partial correlation
+scores each edge and its opposite similarly, it can reach precision values
+higher than 0.5 (see Figure \ref{fig:curves}(b)), suggesting that it ranks high
+mainly pairs of neurons that interact in both directions (there are about XX\%
+of such pairs in the \textit{normal-2} network). %% It is interesting also to note
+%% that, on \textit{normal-2}, a method that perfectly predicts the undirected
+%% network (i.e. that gives a score of 1 to each pair $(i,j)$ such that $(i,j)\in
+%% V$ or $(j,i)\in V$, 0 otherwise) can reach an AUROC of $0.995$, which does not
+%% leave much room for improvement by predicting edge directionality. The AUPRC on
+%% the other hand would be 0.789 and thus be more sensitive to the prediction of
+%% edge directions.
 
@@
 
-\subsection*{ROC versus PR curves.}
+%\subsection*{ROC versus PR curves.}
 

### 2014-06-27 article.tex
some changes : figs + tab

--- 2014-06-27 article.tex
@@
 
-\author{\Name{Antonio Sutera,
-    Arnaud Joly,
-        Vincent François-Lavet,\\
-        Aaron Qiu,
-        Gilles Louppe,
-        Damien Ernst,
-        Pierre Geurts}
-  \Email{a.sutera@ulg.ac.be}\\
+  \author{\Name{Antonio Sutera} ,
+   \Name{Arnaud Joly},
+   \Name{Vincent François-Lavet}, \Email{a.sutera@ulg.ac.be}\\
+   \Name{Aaron Qiu},
+   \Name{Gilles Louppe},
+   \Name{Damien Ernst}\and\Name{Pierre Geurts}
+    \\
    \addr Department of EE and CS \& GIGA-R, University of Li\`ege, Belgium}
 
-%\jmlrauthors{A. Sutera et al}
-%\shortauthor{A. Sutera et al.}
+% \author{\Name{Antonio Sutera,
+%     Arnaud Joly,
+%         Vincent François-Lavet,\\
+%         Aaron Qiu,
+%         Gilles Louppe,
+%         Damien Ernst,
+%         Pierre Geurts}
+%   \Email{a.sutera@ulg.ac.be}\\
+%   \addr Department of EE and CS \& GIGA-R, University of Li\`ege, Belgium}
+
+\jmlrauthors{A. Sutera et al}
+% \shortauthor{A. Sutera et al.}
 
@@
 \subfigure[Global regularization $w$]{\includegraphics[width=0.3\textwidth]{images/weights_curve.pdf} \label{fig:weight_curve}}
-\caption{Signal processing process for extracting peaks from the raw fluorescence data.
-         \textcolor{red}{AJ: The bottom axe is hidden on some figures.}}
+\caption{Signal processing process for extracting peaks from the raw fluorescence data.}
 \label{fig:filtered-signal}
@@
 + PCA         							& 0.932 & 0.930 & 0.928 & 0.926 & 0.355 & 0.353 & 0.350 & 0.333\\
-Averaging           					& 0.938 & 0.936 & 0.936 & 0.932 & 0.391 & 0.389 & 0.385 & 0.374\\
+Averaging           					& 0.937 & 0.935 & 0.935 & 0.931 & 0.391 &  0.390 &  0.385 & 0.375\\
 Full method           					& 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388\\
@@
 
+\section{Extended results}
+
+\begin{table}[t]\label{tab:comparison}
+%\caption{Evaluation of different methods on the four \textit{normal} datasets\label{tab:comparison}}
+\centering
+\small
+\begin{tabular}{| l | c c c c c c | c c c c c c|}
+\hline
+& \multicolumn{4}{c|}{AUROC} & \multicolumn{4}{c|}{AUPRC} \\
+\textit{Method} $\backslash$ \textit{normal-} & \textit{lowcon} & \textit{highcon} & \textit{lowcc} & \textit{highcc} & \textit{normal-3-highrate} & \textit{normal-4-lownoise} & \textit{1} & \textit{2} & \textit{3} & \textit{4} & \textit{normal-3-highrate} & \textit{normal-4-lownoise}\\
+\hline
+\hline
+% No  filtering       					& 0.777 & 0.767 & 0.772 & 0.774 & 0.070 & 0.064 & 0.068 & 0.072\\
+% $ h \circ g \circ f_1$                  & 0.923 & 0.925 & 0.923 & 0.922 & 0.311 & 0.315 & 0.313 & 0.304\\
+% $ w \circ h \circ g \circ f_1$          & 0.931 & 0.929 & 0.928 & 0.926 & 0.326 & 0.323 & 0.319 & 0.303\\
+% + PCA         							& 0.932 & 0.930 & 0.928 & 0.926 & 0.355 & 0.353 & 0.350 & 0.333\\
+% Averaging           					& 0.937 & 0.935 & 0.935 & 0.931 & 0.391 &  0.390 &  0.385 & 0.375\\
+% Full method           					& 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388\\
+% \hline
+% PC & 0.886 & 0.884 & 0.891 &  0.877 & 0.153 & 0.145 & 0.170 & 0.132\\
+% GTE & 0.890 & 0.893 & 0.894 & 0.873 & 0.171 & 0.174 & 0.197 & 0.142\\
+% GENIE3 & & & & & & & & \\
+% \hline
+\end{tabular}
+\caption{Top: Performance on \textit{normal-1,2,3,4} with partial correlation and different filtering functions.
+Bottom: Performance on \textit{normal-1,2,3,4} with different methods.}
+\end{table}
+
 % NEXT APPENDIX SECTION
@@
 
-\vspace{5cm}
+%\vspace{5cm}
 
@@
 Partial correlation    & 0.930 &  0.927 &  0.926 &  0.923& 0.363  & 0.347 &  0.346 & 0.328 \\
-Partial correlation (avg.) & 0.938 & 0.936 & 0.936 & 0.932& 0.391 & 0.389 & 0.385 & 0.374\\
+Partial correlation (avg. 2) & 0.937 & 0.935 & 0.935 & 0.931 & 0.391 &  0.390 &  0.385 & 0.375  \\
+Partial correlation (avg. 4) & 0.938 & 0.936 & 0.936 & 0.932& 0.391 & 0.389 & 0.385 & 0.374\\
 % Our approach simple + dir & 0.939 & 0.936 & 0.937 & 0.933& 0.392 & 0.390 & 0.386 & 0.375\\
 Partial correlation (opt.) & 0.932 & 0.931 & 0.930 & 0.928 & 0.364 & 0.366 & 0.359 & 0.344 \\
-Our approach (opt. \& avg.)    & 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388 \\
+Our approach (opt. \& avg. 4)    & 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388 \\
 % Our approach + dir  \textcolor{red}{appendix?}   & 0.944 & 0.943 & 0.942 & 0.940 & 0.404 & 0.405 & 0.399 & 0.389 \\

### 2014-06-27 article.tex
remarque sur la direction

@@
 GTE & 0.890 & 0.893 & 0.894 & 0.873 & 0.171 & 0.174 & 0.197 & 0.142\\
-GENIE3 & & & & & & & & \\
+GENIE3 & \textcolor{red}{?} & & & & & & & \\
 \hline
@@
 scores each edge and its opposite similarly, it can reach precision values
-higher than 0.5 (see Figure \ref{fig:curves}(b)), suggesting that it ranks high
-mainly pairs of neurons that interact in both directions (there are about XX\%
-of such pairs in the \textit{normal-2} network). %% It is interesting also to note
-%% that, on \textit{normal-2}, a method that perfectly predicts the undirected
-%% network (i.e. that gives a score of 1 to each pair $(i,j)$ such that $(i,j)\in
-%% V$ or $(j,i)\in V$, 0 otherwise) can reach an AUROC of $0.995$, which does not
-%% leave much room for improvement by predicting edge directionality. The AUPRC on
-%% the other hand would be 0.789 and thus be more sensitive to the prediction of
-%% edge directions.
+higher than 0.5 (see Figure \ref{fig:curves}(b)), suggesting that it mainly ranks high
+pairs of neurons that interact in both directions.  It is interesting also to
+note that, on \textit{normal-2}, a method that perfectly predicts the
+undirected network (i.e., that gives a score of $1$ to each pair $(i,j)$ such that
+$(i,j)\in E$ or $(j,i)\in E$, and $0$ otherwise) already reaches an AUROC as high
+as $0.995$ and an AUPRC of $0.789$.
 

### 2014-06-27 article.tex
conclusions

@@
 
-% Possible extensions
-% partial autocorrelation function (sometimes "partial correlation function")
-% conditional independence test
-% Speak about the complexity and parallelization of the methods
-
-In this paper, we present the best performing method of the Connectomics challenge. Our
-approach is simple and theoretically sounded and made of two main stages: the
-signal is first preprocessed with several filters and then we derive the degree
-of association matrix by computing the partial correlation statistics matrix.
-We also evaluate the method in a more detailed way and perform a comparison
-with other inference methods. We finally discuss the relevance of the metric
-used in the challenge and we point out that it was not necessary to discover
-causal relationships to maximize the ROC AUC. Thus, it may be  promising to
-focus on that particular topic in future works.
-
-% In the discussion, we give hints about limiting the depth of trees in the
-% GENIE3 method to infer the network. It should be interesting to see if there
-% is a optimum value for the maximal depth. And of course, it may also rewarding
-% to increase considerably the number of trees to get more stable predictions.
-
-% In previous study \citep{shipley2002cause}, it has been suggested to
-% consider correlation coefficients of all possible orders,
-% i.e. conditioned on every subsets of the set of $p-2$ other variables. This
-% would take into account multiple indirect paths between a given pair of
-% variables. Instead of considering only the highest order, it may be useful to
-% study with accuracy the inferred network at all orders. In this case, it may not
-% be very relevant but interesting in case of dynamical networks.
-
-% As we mentioned, in order to maximize the ROC AUC, it was not necessary to
-% discover causal relationships. It may be, in future works, promising to focus
-% on that particular topic.
+In this paper, we outlined a simple but efficient methodology for the problem
+of connectome inference from calcium imaging data. Our approach is made of two
+steps: (i) processing fluorescence data to detect neural peak activities and
+(ii) inferring the degree of association between neurons from partial
+correlation statistics. Its simplified variant shows to outperform other
+network inference methods while its optimized version proved to be best method
+on the Connectomics challenge. Given its simplicity and good performance, we
+therefore believe that the (simplified) methodology presented in this work
+would constitute a solid and easily reproducible baseline for further work in
+the field of connectome inference.
 
 \section*{Acknowledgments}
-A Joly and G Louppe are research fellows of the FNRS, Belgium.  A Sutera is
+A. Joly and G. Louppe are research fellows of the FNRS, Belgium.  A. Sutera is
 recipient of a FRIA fellowship of FRS-FNRS, Belgium. This work is supported by

### 2014-06-27 article.tex
spellings

@@
 which observations are made is not high enough for being able to detect
-interactions, and that it would therefore be preferrable to lower their
-importance by changing appropriatly their magnitude. Additionnally, it is
+interactions, and that it would therefore be preferable to lower their
+importance by changing appropriately their magnitude. Additionally, it is
 well-known that neurons may also spike because of a global high activity
@@
 time point can be modeled as a set of random variables $X = \{X_1,
-\dots, X_p\}$ that are idependently drawn from the same time invariant
+\dots, X_p\}$ that are independently drawn from the same time invariant
 joint probability distribution $P_X$. %% Or, say otherwise, we assume
@@
 or the value of the threshold $\tau$) in the combined function of the
-filtering and infering processes. One approach, further referred
+filtering and inferring processes. One approach, further referred
 to as \textit{Averaged Partial correlation} statistics, for improving
@@
 Random Forest model to a maximum depth of 3. This constraint potentially
-severly affects the performance of this method with respect to the use of fully
+severely affects the performance of this method with respect to the use of fully
 grown trees. We nevertheless provide these results for comparison purpose. PC

### 2014-06-27 article.tex
add

--- 2014-06-27 article.tex
@@
 
-\jmlrauthors{A. Sutera et al}
+% \jmlrauthors{A. Sutera et al}
 % \shortauthor{A. Sutera et al.}
@@
 GTE & 0.890 & 0.893 & 0.894 & 0.873 & 0.171 & 0.174 & 0.197 & 0.142\\
-GENIE3 & \textcolor{red}{?} & & & & & & & \\
+GENIE3 & 0.892 & 0.891 & 0.887 & 0.887 & 0.232 & 0.221 & 0.237 & 0.215 \\
 \hline
@@
 scores each edge and its opposite similarly, it can reach precision values
-higher than 0.5 (see Figure \ref{fig:curves}(b)), suggesting that it mainly ranks high
-pairs of neurons that interact in both directions.  It is interesting also to
-note that, on \textit{normal-2}, a method that perfectly predicts the
-undirected network (i.e., that gives a score of $1$ to each pair $(i,j)$ such that
-$(i,j)\in E$ or $(j,i)\in E$, and $0$ otherwise) already reaches an AUROC as high
-as $0.995$ and an AUPRC of $0.789$.
+higher than 0.5 (see Figure \ref{fig:curves}(b)), suggesting that it ranks high
+mainly pairs of neurons that interact in both directions (there are about XX\%
+of such pairs in the \textit{normal-2} network). %% It is interesting also to note
+%% that, on \textit{normal-2}, a method that perfectly predicts the undirected
+%% network (i.e. that gives a score of 1 to each pair $(i,j)$ such that $(i,j)\in
+%% V$ or $(j,i)\in V$, 0 otherwise) can reach an AUROC of $0.995$, which does not
+%% leave much room for improvement by predicting edge directionality. The AUPRC on
+%% the other hand would be 0.789 and thus be more sensitive to the prediction of
+%% edge directions.
 
@@
 $f_2$ but the averaging approach over all low-pass
-filters gets better \textcolor{red}{AS:Does it necessary to show it numerically?}.
+filters gets better.
+
+\begin{table}[ht]\label{tab:comparison}
+%\caption{Evaluation of different methods on the four \textit{normal} datasets\label{tab:comparison}}
+\centering
+\small
+\begin{tabular}{| l | c c c c | c c c c |}
+\hline
+& \multicolumn{4}{c|}{AUROC} & \multicolumn{4}{c|}{AUPRC} \\
+\textit{Method} $\backslash$ \textit{normal-} & \textit{1} & \textit{2} & \textit{3} & \textit{4} & \textit{1} & \textit{2} & \textit{3} & \textit{4} \\
+\hline
+\hline
+Partial correlation ($f_1$ + $f_2$) & 0.937 & 0.935 & 0.935 & 0.931 & 0.391 &  0.390 &  0.385 & 0.375  \\
+Partial correlation ($f_1$ + $f_2$ + $f_3$ + $f_4$) & \textbf{0.938} & \textbf{0.936} & \textbf{0.936} & \textbf{0.932} & 0.391 & 0.389 & 0.385 & 0.374\\
+\hline
+\end{tabular}
+\caption{Performance on \textit{normal-1,2,3,4} with partial correlation with different averaging approaches.}
+\end{table}
 
@@
 
-\section{Extended results}
+\section{Supplementary results}
+
+\begin{table}[h]\label{tab:comparison_extended}
+\centering
+\small
+\begin{tabular}{| l | c c c c c c |}
+\hline
+& \multicolumn{6}{c|}{AUROC}\\
+\textit{Method} $\backslash$ \textit{normal-} & \textit{lowcon} & \textit{highcon} & \textit{lowcc} & \textit{highcc} & \textit{3-highrate} & \textit{4-lownoise} \\
+\hline
+\hline
+& \\ \hline
+& \multicolumn{6}{c|}{AUROC}\\ \hline
+& \\
+\end{tabular}
+\caption{Top: Performance on \textit{normal-1,2,3,4} with partial correlation and different filtering functions.
+Bottom: Performance on \textit{normal-1,2,3,4} with different methods.}
+\end{table}
 
@@
 \hline
-& \multicolumn{4}{c|}{AUROC} & \multicolumn{4}{c|}{AUPRC} \\
-\textit{Method} $\backslash$ \textit{normal-} & \textit{lowcon} & \textit{highcon} & \textit{lowcc} & \textit{highcc} & \textit{normal-3-highrate} & \textit{normal-4-lownoise} & \textit{1} & \textit{2} & \textit{3} & \textit{4} & \textit{normal-3-highrate} & \textit{normal-4-lownoise}\\
+& \multicolumn{6}{c|}{AUROC} & \multicolumn{6}{c|}{AUPRC} \\
+\textit{Method} $\backslash$ \textit{normal-} & \textit{lowcon} & \textit{highcon} & \textit{lowcc} & \textit{highcc} & \textit{3-highrate} & \textit{4-lownoise} & \textit{lowcon} & \textit{highcon} & \textit{lowcc} & \textit{highcc} & \textit{3-highrate} & \textit{4-lownoise}\\
 \hline

### 2014-06-27 article.tex
fix: network density
typo

@@
 \citep{stetter2012model} of different neural networks of 1000 neurons
-and about 15000 edges each (i.e., a network density of about
-1.5\%). Each neuron is described by a calcium fluorescence time series
+and about 12000 edges each (i.e., a network density of about
+1.2\%). Each neuron is described by a calcium fluorescence time series
 of length $T=179500$. All inference methods compared here provide a
@@
 correlation statistics. Its simplified variant shows to outperform other
-network inference methods while its optimized version proved to be best method
+network inference methods while its optimized version proved to be the best method
 on the Connectomics challenge. Given its simplicity and good performance, we

### 2014-06-27 article.tex
wording
section 4: precision filtering GENIE3 et PC

--- 2014-06-27 article.tex
@@
 Random Forest model to a maximum depth of 3. This constraint potentially
-severely affects the performance of this method with respect to the use of fully
-grown trees. We nevertheless provide these results for comparison purpose. PC
-and GENIE3 were both applied on the same pre-filtered time series as partial
-correlation ($h\circ g \circ f_1$). For GENIE3, we built 10000 trees per neuron
-and we used default settings for all other parameters (except for the maximal
-tree depth). For GTE, we reproduced the exact same setting (conditioning level
-and pre-processing) that was used for the challenge.
+severely affects the performance of this method with respect to the use of
+fully grown trees. PC and GENIE3 were applied on the time series filtered using
+respectively the functions $w\circ h\circ g$ and $h\circ g\circ f_1$ (which
+gave the best performance). For GENIE3, we built 10000 trees per neuron and we
+used default settings for all other parameters (except for the maximal tree
+depth). For GTE, we reproduced the exact same setting (conditioning level and
+pre-processing) that was used by the challenge organizers.
 

### 2014-06-27 article.tex

@@
 \subfigure[Global regularization $w$]{\includegraphics[width=0.3\textwidth]{images/weights_curve.pdf} \label{fig:weight_curve}}
-\caption{Signal processing process for extracting peaks from the raw fluorescence data.}
+\caption{Signal processing pipeline for extracting peaks from the raw fluorescence data.}
 \label{fig:filtered-signal}

### 2014-06-27 article.tex
essai  Please enter the commit message for your changes. Lines starting

--- 2014-06-27 article.tex
@@
 We report here experiments on the \textit{normal-1,2,3}, and \textit{4}
-datasets provided by the organizers of the Connectomics
-challenge. Each of these datasets is obtained from the simulation
-\citep{stetter2012model} of different neural networks of 1000 neurons
-and about 12000 edges each (i.e., a network density of about
-1.2\%). Each neuron is described by a calcium fluorescence time series
-of length $T=179500$. All inference methods compared here provide a
-ranking of all pairs of neurons according to some association
+datasets provided by the organizers of the Connectomics challenge (see
+Appendix~\ref{app:supp} for experiments on other datasets). Each of
+these datasets is obtained from the simulation \citep{stetter2012model} of
+different neural networks of 1000 neurons and about 15000 edges each (i.e., a
+network density of about 1.5\%). Each neuron is described by a calcium
+fluorescence time series of length $T=179500$. All inference methods compared
+here provide a ranking of all pairs of neurons according to some association
 score. To assess the quality of this ranking, we compute both ROC and
-precision-recall curves against the ground truth network, which are
-summarized using the area under the curve and respectively  denoted AUROC
-and AUPRC. Only the AUROC score was used to rank the challenge
-participants but the precision-recall curve has been shown to be a
-more sensible metric for network inference, especially when network
-density is small (see e.g., \cite{schrynemackers2013protocols}).
-Since neurons are not self-connected in the ground truth networks
-(i.e., $(i, i) \not \in E, \forall i \in V$), we have manually set the
-score of such edges to the minimal possible association score before
-computing ROC and PR curves.
+precision-recall curves against the ground truth network, which are summarized
+using the area under the curve and respectively  denoted AUROC and AUPRC. Only
+the AUROC score was used to rank the challenge participants but the precision-
+recall curve has been shown to be a more sensible metric for network
+inference, especially when network density is small (see e.g.,
+\cite{schrynemackers2013protocols}). Since neurons are not self-connected in
+the ground truth networks (i.e., $(i, i) \not \in E, \forall i \in V$), we
+have manually set the score of such edges to the minimal possible association
+score before computing ROC and PR curves.
 
@@
 Averaging           					& 0.937 & 0.935 & 0.935 & 0.931 & 0.391 &  0.390 &  0.385 & 0.375\\
-Full method           					& 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388\\
+Full method           					& \textbf{0.943} & \textbf{0.942} & \textbf{0.942} & \textbf{0.939} & \textbf{0.403} & \textbf{0.404} & \textbf{0.398} & \textbf{0.388}\\
 \hline
@@
 correlation statistics. Its simplified variant shows to outperform other
-network inference methods while its optimized version proved to be the best method
+network inference methods while its optimized version proved to be best method
 on the Connectomics challenge. Given its simplicity and good performance, we
@@
 
-\section{An optimized version of the algorithm to win the challenge}
+\section{Particularities of the ``Full method''}
 \label{app:optimized}
@@
 
-Let us remark that tuning
-was mainly done on the \textit{normal-1} and \textit{normal-4}
-datasets, which explains why these two networks are slightly better
-retrieved than the others.
+% Let us remark that tuning
+% was mainly done on the \textit{normal-1} and \textit{normal-4}
+% datasets, which explains why these two networks are slightly better
+% retrieved than the others.
 
@@
 f_3(x^t_i) &= x^{t-1}_i + x^{t}_i + x^{t+1}_i + x^{t+2}_i \label{eq:asymetric-median-forward}, \\
-f_4(x^t_i) &= x^{t+3}_i + x^{t+2}_i + x^{t+1}_i + x_i^t.
+f_4(x^t_i) &=  x_i^t + x^{t+1}_i  + x^{t+2}_i + x^{t+3}_i  .
 \label{eq:asymetric-median}
@@
 $f_2$ but the averaging approach over all low-pass
-filters gets better.
+filters gets better for the ROC AUC.
 
@@
 & \multicolumn{4}{c|}{AUROC} & \multicolumn{4}{c|}{AUPRC} \\
-\textit{Method} $\backslash$ \textit{normal-} & \textit{1} & \textit{2} & \textit{3} & \textit{4} & \textit{1} & \textit{2} & \textit{3} & \textit{4} \\
-\hline
-\hline
-Partial correlation ($f_1$ + $f_2$) & 0.937 & 0.935 & 0.935 & 0.931 & 0.391 &  0.390 &  0.385 & 0.375  \\
-Partial correlation ($f_1$ + $f_2$ + $f_3$ + $f_4$) & \textbf{0.938} & \textbf{0.936} & \textbf{0.936} & \textbf{0.932} & 0.391 & 0.389 & 0.385 & 0.374\\
+\textit{Averaging} $\backslash$ \textit{normal-} & \textit{1} & \textit{2} & \textit{3} & \textit{4} & \textit{1} & \textit{2} & \textit{3} & \textit{4} \\
+\hline
+\hline
+ with $f_1$, $f_2$ & 0.937 & 0.935 & 0.935 & 0.931 & 0.391 &  \textbf{0.390} &  0.385 & \textbf{0.375}  \\
+ with $f_1$, $f_2$, $f_3$, $f_4$ & \textbf{0.938} & \textbf{0.936} & \textbf{0.936} & \textbf{0.932} & 0.391 & 0.389 & 0.385 & 0.374\\
 \hline
@@
 the four low-pass filters with the following parameters
-
 \begin{align*}
@@
 \end{align*}
-
 tuned to maximize the
@@
 At the light of the poor results of this heuristic taken on its own summarized
-on Table \ref{tab:} as \textit{directivity}, we use it to make asymmetric the
+on Table \ref{tab:directivity} as \textit{directivity}, we use it to make asymmetric the
 degree of association matrix using partial correlation statistics. We expect
@@
 
+\begin{table}[ht]\label{tab:comparison}
+%\caption{Evaluation of different methods on the four \textit{normal} datasets\label{tab:comparison}}
+\centering
+\small
+\begin{tabular}{| l | c c c c | c c c c |}
+\hline
+& \multicolumn{4}{c|}{AUROC} & \multicolumn{4}{c|}{AUPRC} \\
+\textit{Full method} $\backslash$ \textit{normal-} & \textit{1} & \textit{2} & \textit{3} & \textit{4} & \textit{1} & \textit{2} & \textit{3} & \textit{4} \\
+\hline
+\hline
+ without directivity & 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388  \\
+  with directivity  & \textbf{0.944} & \textbf{0.943} & 0.942 & \textbf{0.940} & \textbf{0.404} & \textbf{0.405} & \textbf{0.399} & \textbf{0.389}\\
+\hline
+\end{tabular}
+\caption{Performance on \textit{normal-1,2,3,4} of the ``Full Method'' with and without the directivity heuristic.}
+\label{tab:directivity}
+\end{table}
+
 \section{Supplementary results}
-
-\begin{table}[h]\label{tab:comparison_extended}
+\label{app:supp}
+
+We report here experiments on particular datasets provided by the organizers
+which are similar to \textit{normal} datasets, i.e., made of 1000 neurons,
+except for one parameter. We compute, as done in
+Section~\ref{sec:results}, both AUROC and AUPRC and results are reported in
+Table~\ref{tab:results_appendix}. We will briefly recall what characterizes
+each datasets:
+\begin{description}
+\item[lowcon]: Similar network but with a lower number of connections per neuron on average.
+\item[highcon]: Similar network but with a higher number of connections per neuron on average.
+\item[lowcc]: Similar network but with a lower clustering coefficient on average.
+\item[highcc]: Similar network but with a higher clustering coefficient on average.
+\item[normal-3-highrate]: Same topology as \textit{normal-3} but with an higher firing frequency, i.e., with highly active neurons.
+\item[normal-4-lownoise]: Same topology as \textit{normal-4} but with a better signal to noise ratio.
+\end{description}
+
+\begin{table}[h]
 \centering
@@
 \hline
-& \\ \hline
-& \multicolumn{6}{c|}{AUROC}\\ \hline
-& \\
+Averaging     & 0.947 & 0.943 & 0.920 & 0.942 & 0.959 & 0.934 \\
+Full method   &  &  &  & & &\\
+PC & 0.782 & 0.920 &  0.846 & 0.897  & 0.898  & 0.873 \\
+GTE & 0.846 & 0.905 & 0.848 & 0.899 & 0.905 & 0.879\\
+GENIE3* & 0.781 &  0.922 & 0.875 & 0.899 & 0.886 &  0.890 \\ \hline
+& \multicolumn{6}{c|}{AUPRC}\\ \hline
+Averaging     & 0.320 & 0.429 & 0.262 & 0.478 & 0.443 & 0.412 \\
+Full method   &  &  &  & & &\\
+PC & 0.074 & 0.218 & 0.082 & 0.165  & 0.193 & 0.135 \\
+GTE & 0.094 & 0.211 & 0.081 & 0.165 & 0.210 & 0.144\\
+GENIE3* & 0.128 & 0.261 & 0.108 & 0.293 & 0.256 & 0.224\\ \hline
 \end{tabular}
-\caption{Top: Performance on \textit{normal-1,2,3,4} with partial correlation and different filtering functions.
-Bottom: Performance on \textit{normal-1,2,3,4} with different methods.}
+\caption{Performance (top: AUROC, bottom: AUPRC) on specific datasets with different methods.}
+\label{tab:results_appendix}
 \end{table}
 
-\begin{table}[t]\label{tab:comparison}
-%\caption{Evaluation of different methods on the four \textit{normal} datasets\label{tab:comparison}}
-\centering
-\small
-\begin{tabular}{| l | c c c c c c | c c c c c c|}
-\hline
-& \multicolumn{6}{c|}{AUROC} & \multicolumn{6}{c|}{AUPRC} \\
-\textit{Method} $\backslash$ \textit{normal-} & \textit{lowcon} & \textit{highcon} & \textit{lowcc} & \textit{highcc} & \textit{3-highrate} & \textit{4-lownoise} & \textit{lowcon} & \textit{highcon} & \textit{lowcc} & \textit{highcc} & \textit{3-highrate} & \textit{4-lownoise}\\
-\hline
-\hline
-% No  filtering       					& 0.777 & 0.767 & 0.772 & 0.774 & 0.070 & 0.064 & 0.068 & 0.072\\
-% $ h \circ g \circ f_1$                  & 0.923 & 0.925 & 0.923 & 0.922 & 0.311 & 0.315 & 0.313 & 0.304\\
-% $ w \circ h \circ g \circ f_1$          & 0.931 & 0.929 & 0.928 & 0.926 & 0.326 & 0.323 & 0.319 & 0.303\\
-% + PCA         							& 0.932 & 0.930 & 0.928 & 0.926 & 0.355 & 0.353 & 0.350 & 0.333\\
-% Averaging           					& 0.937 & 0.935 & 0.935 & 0.931 & 0.391 &  0.390 &  0.385 & 0.375\\
-% Full method           					& 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388\\
+% \begin{table}[t]\label{tab:comparison}
+% %\caption{Evaluation of different methods on the four \textit{normal} datasets\label{tab:comparison}}
+% \centering
+% \small
+% \begin{tabular}{| l | c c c c c c | c c c c c c|}
 % \hline
-% PC & 0.886 & 0.884 & 0.891 &  0.877 & 0.153 & 0.145 & 0.170 & 0.132\\
-% GTE & 0.890 & 0.893 & 0.894 & 0.873 & 0.171 & 0.174 & 0.197 & 0.142\\
-% GENIE3 & & & & & & & & \\
+% & \multicolumn{6}{c|}{AUROC} & \multicolumn{6}{c|}{AUPRC} \\
+% \textit{Method} $\backslash$ \textit{normal-} & \textit{lowcon} & \textit{highcon} & \textit{lowcc} & \textit{highcc} & \textit{3-highrate} & \textit{4-lownoise} & \textit{lowcon} & \textit{highcon} & \textit{lowcc} & \textit{highcc} & \textit{3-highrate} & \textit{4-lownoise}\\
 % \hline
-\end{tabular}
-\caption{Top: Performance on \textit{normal-1,2,3,4} with partial correlation and different filtering functions.
-Bottom: Performance on \textit{normal-1,2,3,4} with different methods.}
-\end{table}
+% \hline
+% % No  filtering       					& 0.777 & 0.767 & 0.772 & 0.774 & 0.070 & 0.064 & 0.068 & 0.072\\
+% % $ h \circ g \circ f_1$                  & 0.923 & 0.925 & 0.923 & 0.922 & 0.311 & 0.315 & 0.313 & 0.304\\
+% % $ w \circ h \circ g \circ f_1$          & 0.931 & 0.929 & 0.928 & 0.926 & 0.326 & 0.323 & 0.319 & 0.303\\
+% % + PCA         							& 0.932 & 0.930 & 0.928 & 0.926 & 0.355 & 0.353 & 0.350 & 0.333\\
+% % Averaging           					& 0.937 & 0.935 & 0.935 & 0.931 & 0.391 &  0.390 &  0.385 & 0.375\\
+% % Full method           					& 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388\\
+% % \hline
+% % PC & 0.886 & 0.884 & 0.891 &  0.877 & 0.153 & 0.145 & 0.170 & 0.132\\
+% % GTE & 0.890 & 0.893 & 0.894 & 0.873 & 0.171 & 0.174 & 0.197 & 0.142\\
+% % GENIE3 & & & & & & & & \\
+% % \hline
+% \end{tabular}
+% \caption{Top: Performance on \textit{normal-1,2,3,4} with partial correlation and different filtering functions.
+% Bottom: Performance on \textit{normal-1,2,3,4} with different methods.}
+% \end{table}
 
@@
 
-\section{Extended results}
-
-\begin{table}
-\small
-\centering
-\begin{tabular}{@{}l *{8}{c}@{}}
-  & \multicolumn{4}{c}{AUROC} & \multicolumn{4}{c}{AUPRC} \\
-\hline \hline
-Methods $\backslash$ normal- & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 \\
-\hline \hline
-% Directivity \textcolor{red}{appendix?} & 0.535 & 0.526 & 0.533 & 0.535 & 0.012 & 0.012 & 0.012 & 0.012 \\
-Pearson correlation    & 0.886 & 0.884 & 0.891 & 0.877 & 0.153 & 0.145 & 0.170 & 0.132 \\
-GENIE3 (depth = 1)     & 0.878 & 0.877 & 0.873 & 0.873 & 0.184 & 0.173 & 0.182& 0.172\\
-GENIE3 (depth = 2)     & 0.889 & 0.888 & 0.883 & 0.884* & 0.217 & 0.210 & 0.220 & 0.199* \\
-GENIE3 (depth = 3)     & 0.892 & 0.891* & 0.887 & 0.887 & 0.232 & 0.226* & 0.237 & 0.215\\
-GTE                    & 0.890 & 0.893 & 0.894 & 0.873 & 0.171 & 0.174 & 0.197 & 0.142 \\
-Partial correlation    & 0.930 &  0.927 &  0.926 &  0.923& 0.363  & 0.347 &  0.346 & 0.328 \\
-Partial correlation (avg. 2) & 0.937 & 0.935 & 0.935 & 0.931 & 0.391 &  0.390 &  0.385 & 0.375  \\
-Partial correlation (avg. 4) & 0.938 & 0.936 & 0.936 & 0.932& 0.391 & 0.389 & 0.385 & 0.374\\
-% Our approach simple + dir & 0.939 & 0.936 & 0.937 & 0.933& 0.392 & 0.390 & 0.386 & 0.375\\
-Partial correlation (opt.) & 0.932 & 0.931 & 0.930 & 0.928 & 0.364 & 0.366 & 0.359 & 0.344 \\
-Our approach (opt. \& avg. 4)    & 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388 \\
-% Our approach + dir  \textcolor{red}{appendix?}   & 0.944 & 0.943 & 0.942 & 0.940 & 0.404 & 0.405 & 0.399 & 0.389 \\
-\end{tabular}
-\caption{TODO (* means not 10000 trees but more than 9500, to be solved.) }
-\label{tab:tab1}
-\end{table}
-
-\section{Supplementary results}
-
-\begin{table}[htbp]
-\centering
-\caption{Correlation (ROC). Improvement of each stage of our approach. Note that we choose the
-         \textit{best} threshold (\textcolor{red}{for now 0.11}) for stages 1 to 4.}
-\begin{tabular}{*{5}{l}}
-\toprule
-Stage               & normal-1 & normal-2 & normal-3 & normal-4 \\
-\midrule
-Nothing             & 0.681 & 0.699 & 0.683 & 0.681\\
-Weights             & 0.695 & 0.713 & 0.697 & 0.694\\
-H-T                 & 0.876 & 0.873 & 0.877 & 0.869\\
-H-T + Weights       & 0.886 & 0.884 & 0.891 & 0.877\\
-P-P                 & 0.857 & 0.850 & 0.843 & 0.832\\
-P-P + Weights       & 0.826 & 0.823 & 0.817 & 0.799\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-\begin{table}[htbp]
-\centering
-\caption{Correlation (P-R). Improvement of each stage of our approach. Note that we choose the
-         \textit{best} threshold (\textcolor{red}{for now 0.11}) for stages 1 to 4.}
-\begin{tabular}{*{5}{l}}
-\toprule
-Stage               & normal-1 & normal-2 & normal-3 & normal-4 \\
-\midrule
-Nothing             & 0.028 & 0.028 & 0.025 & 0.026\\
-Weights             & 0.031 & 0.030 & 0.027 & 0.028\\
-H-T                 & 0.143 & 0.128 & 0.150 & 0.129\\
-H-T + Weights       & 0.153 & 0.145 & 0.170 & 0.132\\
-P-P                 & 0.100 & 0.087 & 0.079 & 0.083\\
-P-P + Weights       & 0.079 & 0.071 & 0.067 & 0.064\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-\begin{table}[htb]
-\centering
-\caption{Comparison (P-R) with other methods (for now, $t = 0.11$)}
-\begin{tabular}{*{5}{l}}
-\toprule
-Methods             & normal-1 & normal-2 & normal-3 & normal-4 \\
-\midrule
-Correlation (best)         & 0.153 & 0.145 & 0.170 & 0.132 \\
-Partial correlation (best) & 0.364 & 0.366 & 0.359 & 0.344 \\
-Our approach (best)        & 0.403 & 0.404 & 0.398 & 0.388 \\
-GENIE3                     & & & & \\
-GTE                        & 0.171 & 0.174 & 0.197 & 0.142 \\
-Directivity                & 0.012 & 0.012 & 0.012 & 0.012 \\
-Our approach + dir         & 0.404 & 0.405 & 0.399 & 0.389 \\
-\bottomrule
-\end{tabular}
-\end{table}
-
-\begin{table}[htb]
-\centering
-\caption{Inverse correlation (ROC). Improvement of each stage of our approach. Note that we choose the
-         \textit{best} threshold (\textcolor{red}{for now 0.11}) for stages 1 to 4.}
-\begin{tabular}{*{5}{l}}
-\toprule
-Stage               & normal-1 & normal-2 & normal-3 & normal-4 \\
-\midrule
-Nothing             & 0.777 & 0.767 & 0.772 & 0.774 \\
-PCA                 & 0.780 & 0.770 & 0.776 & 0.777 \\
-Weights             & 0.780 & 0.769 & 0.776 & 0.777 \\
-Weights + PCA       & 0.783 & 0.772 & 0.779 & 0.780 \\
-H-T                 & 0.893 & 0.891 & 0.891 & 0.886 \\
-H-T + PCA           & 0.894 & 0.892 & 0.891 & 0.886 \\
-H-T + Weights       & 0.899 & 0.897 & 0.896 & 0.891 \\
-H-T + Weights + PCA & 0.900 & 0.898 & 0.896 & 0.892 \\
-P-P                 & 0.925 & 0.925 & 0.924 & 0.923 \\
-P-P + PCA           & 0.926 & 0.926 & 0.925 & 0.923 \\
-P-P + Weights       & 0.931 & 0.930 & 0.928 & 0.927 \\
-P-P + Weights + PCA & 0.932 & 0.931 & 0.930 & 0.928 \\
-Averaging (PCA)     & 0.943 & 0.942 & 0.942 & 0.939 \\
-Stacking            & 0.944 & 0.943 & 0.942 & 0.940 \\
-\bottomrule
-\end{tabular}
-\end{table}
-
-\begin{table}[htb]
-\centering
-\caption{Inverse correlation (P-R). Improvement of each stage of our approach. Note that we choose the
-         \textit{best} threshold (\textcolor{red}{for now 0.11}) for stages 1 to 4.}
-\begin{tabular}{*{5}{l}}
-\toprule
-Stage               & normal-1 & normal-2 & normal-3 & normal-4 \\
-\midrule
-Nothing             & 0.070 & 0.064 & 0.068 & 0.072\\
-PCA                 & 0.076 & 0.070 & 0.075 & 0.079\\
-Weights             & 0.074 & 0.067 & 0.072 & 0.076\\
-Weights + PCA       & 0.080 & 0.073 & 0.079 & 0.083\\
-H-T                 & 0.264 & 0.260 & 0.269 & 0.241\\
-H-T + PCA           & 0.266 & 0.263 & 0.273 & 0.244\\
-H-T + Weights       & 0.280 & 0.273 & 0.281 & 0.251\\
-H-T + Weights + PCA & 0.284 & 0.278 & 0.285 & 0.255\\
-P-P                 & 0.322 & 0.324 & 0.323 & 0.312\\
-P-P + PCA           & 0.347 & 0.352 & 0.355 & 0.341\\
-P-P + Weights       & 0.333 & 0.334 & 0.327 & 0.313\\
-P-P + Weights + PCA & 0.364 & 0.366 & 0.359 & 0.344\\
-Averaging           & 0.403 & 0.404 & 0.398 & 0.388\\
-Stacking            & 0.404 & 0.405 & 0.399 & 0.389\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-\section{Signal processing highly improves performance}
-
-On Table \ref{tab:tab3}, it can be seen that each step of our approach globally
-improves the score on both metrics. However, processing, weights and averaging
-(respectively denoted as $P$,$W$ and $Averaging$ in Tab.\ref{tab:tab3}) as
-described in Section \ref{sec:filter} are the key steps of our algorithm.
-
-It also appears that the averaging over the low-pass filter designs and the
-threshold values increases significantly the quality of the inferred network
-according to both metrics.
-
-% Explaining the method (thèse de Gilles)
-% Avg.: Averaging over the threholds and L-P filters improves a lot both metrics.
-% Averaging
-
-%% Depth -- Gilles chapitre 7
-% Genie3 : better in auprc while worse in auroc than GTE. Why?
-% Genie3 : "Conditioning" better and better but need a lot of trees
-
-\begin{table}[tbh]
-\centering
-\small
-\begin{tabular}{@{}l *{8}{c}@{}}
-\hline
-  & \multicolumn{4}{c}{AUROC} & \multicolumn{4}{c}{AUPRC} \\
-\hline
-Methods $\backslash$ normal- & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 \\
-No  filtering       & 0.777 & 0.767 & 0.772 & 0.774 & 0.070 & 0.064 & 0.068 & 0.072\\
-P                   & 0.925 & 0.925 & 0.924 & 0.923 & 0.322 & 0.324 & 0.323 & 0.312\\
-P + W               & 0.931 & 0.930 & 0.928 & 0.927 & 0.333 & 0.334 & 0.327 & 0.313\\
-P + W + PCA         & 0.932 & 0.931 & 0.930 & 0.928 & 0.364 & 0.366 & 0.359 & 0.344\\
-Averaging           & 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388\\
-%Averaging + Directivity & 0.944 & 0.943 & 0.942 & 0.940 & 0.404 & 0.405 & 0.399 & 0.389\\
-\end{tabular}
-\caption{Optimized method (TODO)}
-\label{tab:tab3}
-\end{table}
-
-\begin{table}[tbh]
-\centering
-\small
-\begin{tabular}{@{}l *{8}{c}@{}}
-\hline
-  & \multicolumn{4}{c}{AUROC} & \multicolumn{4}{c}{AUPRC} \\
-\hline
-Methods $\backslash$ normal- & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 \\
-No  filtering       & 0.777 & 0.767 & 0.772 & 0.774 & 0.070 & 0.064 & 0.068 & 0.072\\
-P                   & 0.923 & 0.925 & 0.923 & 0.922 & 0.311 & 0.315 & 0.313 & 0.304\\
-P + W               & 0.931 & 0.929 & 0.928 & 0.926 & 0.326 & 0.323 & 0.319 & 0.303\\
-P + W + PCA         & 0.932 & 0.930 & 0.928 & 0.926 & 0.355 & 0.353 & 0.350 & 0.333\\
-Averaging           & 0.938 & 0.936 & 0.936 & 0.932 & 0.391 & 0.389 & 0.385 & 0.374\\
-%Averaging + Directivity & 0.944 & 0.943 & 0.942 & 0.940 & 0.404 & 0.405 & 0.399 & 0.389\\
-\end{tabular}
-\caption{Simplified method (TODO)}
-\label{tab:tab3}
-\end{table}
-
-%% Talk about filters future and past
+% \section{Extended results}
+
+% \begin{table}
+% \small
+% \centering
+% \begin{tabular}{@{}l *{8}{c}@{}}
+%   & \multicolumn{4}{c}{AUROC} & \multicolumn{4}{c}{AUPRC} \\
+% \hline \hline
+% Methods $\backslash$ normal- & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 \\
+% \hline \hline
+% % Directivity \textcolor{red}{appendix?} & 0.535 & 0.526 & 0.533 & 0.535 & 0.012 & 0.012 & 0.012 & 0.012 \\
+% Pearson correlation    & 0.886 & 0.884 & 0.891 & 0.877 & 0.153 & 0.145 & 0.170 & 0.132 \\
+% GENIE3 (depth = 1)     & 0.878 & 0.877 & 0.873 & 0.873 & 0.184 & 0.173 & 0.182& 0.172\\
+% GENIE3 (depth = 2)     & 0.889 & 0.888 & 0.883 & 0.884* & 0.217 & 0.210 & 0.220 & 0.199* \\
+% GENIE3 (depth = 3)     & 0.892 & 0.891* & 0.887 & 0.887 & 0.232 & 0.226* & 0.237 & 0.215\\
+% GTE                    & 0.890 & 0.893 & 0.894 & 0.873 & 0.171 & 0.174 & 0.197 & 0.142 \\
+% Partial correlation    & 0.930 &  0.927 &  0.926 &  0.923& 0.363  & 0.347 &  0.346 & 0.328 \\
+% Partial correlation (avg. 2) & 0.937 & 0.935 & 0.935 & 0.931 & 0.391 &  0.390 &  0.385 & 0.375  \\
+% Partial correlation (avg. 4) & 0.938 & 0.936 & 0.936 & 0.932& 0.391 & 0.389 & 0.385 & 0.374\\
+% % Our approach simple + dir & 0.939 & 0.936 & 0.937 & 0.933& 0.392 & 0.390 & 0.386 & 0.375\\
+% Partial correlation (opt.) & 0.932 & 0.931 & 0.930 & 0.928 & 0.364 & 0.366 & 0.359 & 0.344 \\
+% Our approach (opt. \& avg. 4)    & 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388 \\
+% % Our approach + dir  \textcolor{red}{appendix?}   & 0.944 & 0.943 & 0.942 & 0.940 & 0.404 & 0.405 & 0.399 & 0.389 \\
+% \end{tabular}
+% \caption{TODO (* means not 10000 trees but more than 9500, to be solved.) }
+% \label{tab:tab1}
+% \end{table}
+
+% \section{Supplementary results}
+
+% \begin{table}[htbp]
+% \centering
+% \caption{Correlation (ROC). Improvement of each stage of our approach. Note that we choose the
+%          \textit{best} threshold (\textcolor{red}{for now 0.11}) for stages 1 to 4.}
+% \begin{tabular}{*{5}{l}}
+% \toprule
+% Stage               & normal-1 & normal-2 & normal-3 & normal-4 \\
+% \midrule
+% Nothing             & 0.681 & 0.699 & 0.683 & 0.681\\
+% Weights             & 0.695 & 0.713 & 0.697 & 0.694\\
+% H-T                 & 0.876 & 0.873 & 0.877 & 0.869\\
+% H-T + Weights       & 0.886 & 0.884 & 0.891 & 0.877\\
+% P-P                 & 0.857 & 0.850 & 0.843 & 0.832\\
+% P-P + Weights       & 0.826 & 0.823 & 0.817 & 0.799\\
+% \bottomrule
+% \end{tabular}
+% \end{table}
+
+% \begin{table}[htbp]
+% \centering
+% \caption{Correlation (P-R). Improvement of each stage of our approach. Note that we choose the
+%          \textit{best} threshold (\textcolor{red}{for now 0.11}) for stages 1 to 4.}
+% \begin{tabular}{*{5}{l}}
+% \toprule
+% Stage               & normal-1 & normal-2 & normal-3 & normal-4 \\
+% \midrule
+% Nothing             & 0.028 & 0.028 & 0.025 & 0.026\\
+% Weights             & 0.031 & 0.030 & 0.027 & 0.028\\
+% H-T                 & 0.143 & 0.128 & 0.150 & 0.129\\
+% H-T + Weights       & 0.153 & 0.145 & 0.170 & 0.132\\
+% P-P                 & 0.100 & 0.087 & 0.079 & 0.083\\
+% P-P + Weights       & 0.079 & 0.071 & 0.067 & 0.064\\
+% \bottomrule
+% \end{tabular}
+% \end{table}
+
+% \begin{table}[htb]
+% \centering
+% \caption{Comparison (P-R) with other methods (for now, $t = 0.11$)}
+% \begin{tabular}{*{5}{l}}
+% \toprule
+% Methods             & normal-1 & normal-2 & normal-3 & normal-4 \\
+% \midrule
+% Correlation (best)         & 0.153 & 0.145 & 0.170 & 0.132 \\
+% Partial correlation (best) & 0.364 & 0.366 & 0.359 & 0.344 \\
+% Our approach (best)        & 0.403 & 0.404 & 0.398 & 0.388 \\
+% GENIE3                     & & & & \\
+% GTE                        & 0.171 & 0.174 & 0.197 & 0.142 \\
+% Directivity                & 0.012 & 0.012 & 0.012 & 0.012 \\
+% Our approach + dir         & 0.404 & 0.405 & 0.399 & 0.389 \\
+% \bottomrule
+% \end{tabular}
+% \end{table}
+
+% \begin{table}[htb]
+% \centering
+% \caption{Inverse correlation (ROC). Improvement of each stage of our approach. Note that we choose the
+%          \textit{best} threshold (\textcolor{red}{for now 0.11}) for stages 1 to 4.}
+% \begin{tabular}{*{5}{l}}
+% \toprule
+% Stage               & normal-1 & normal-2 & normal-3 & normal-4 \\
+% \midrule
+% Nothing             & 0.777 & 0.767 & 0.772 & 0.774 \\
+% PCA                 & 0.780 & 0.770 & 0.776 & 0.777 \\
+% Weights             & 0.780 & 0.769 & 0.776 & 0.777 \\
+% Weights + PCA       & 0.783 & 0.772 & 0.779 & 0.780 \\
+% H-T                 & 0.893 & 0.891 & 0.891 & 0.886 \\
+% H-T + PCA           & 0.894 & 0.892 & 0.891 & 0.886 \\
+% H-T + Weights       & 0.899 & 0.897 & 0.896 & 0.891 \\
+% H-T + Weights + PCA & 0.900 & 0.898 & 0.896 & 0.892 \\
+% P-P                 & 0.925 & 0.925 & 0.924 & 0.923 \\
+% P-P + PCA           & 0.926 & 0.926 & 0.925 & 0.923 \\
+% P-P + Weights       & 0.931 & 0.930 & 0.928 & 0.927 \\
+% P-P + Weights + PCA & 0.932 & 0.931 & 0.930 & 0.928 \\
+% Averaging (PCA)     & 0.943 & 0.942 & 0.942 & 0.939 \\
+% Stacking            & 0.944 & 0.943 & 0.942 & 0.940 \\
+% \bottomrule
+% \end{tabular}
+% \end{table}
+
+% \begin{table}[htb]
+% \centering
+% \caption{Inverse correlation (P-R). Improvement of each stage of our approach. Note that we choose the
+%          \textit{best} threshold (\textcolor{red}{for now 0.11}) for stages 1 to 4.}
+% \begin{tabular}{*{5}{l}}
+% \toprule
+% Stage               & normal-1 & normal-2 & normal-3 & normal-4 \\
+% \midrule
+% Nothing             & 0.070 & 0.064 & 0.068 & 0.072\\
+% PCA                 & 0.076 & 0.070 & 0.075 & 0.079\\
+% Weights             & 0.074 & 0.067 & 0.072 & 0.076\\
+% Weights + PCA       & 0.080 & 0.073 & 0.079 & 0.083\\
+% H-T                 & 0.264 & 0.260 & 0.269 & 0.241\\
+% H-T + PCA           & 0.266 & 0.263 & 0.273 & 0.244\\
+% H-T + Weights       & 0.280 & 0.273 & 0.281 & 0.251\\
+% H-T + Weights + PCA & 0.284 & 0.278 & 0.285 & 0.255\\
+% P-P                 & 0.322 & 0.324 & 0.323 & 0.312\\
+% P-P + PCA           & 0.347 & 0.352 & 0.355 & 0.341\\
+% P-P + Weights       & 0.333 & 0.334 & 0.327 & 0.313\\
+% P-P + Weights + PCA & 0.364 & 0.366 & 0.359 & 0.344\\
+% Averaging           & 0.403 & 0.404 & 0.398 & 0.388\\
+% Stacking            & 0.404 & 0.405 & 0.399 & 0.389\\
+% \bottomrule
+% \end{tabular}
+% \end{table}
+
+% \section{Signal processing highly improves performance}
+
+% On Table \ref{tab:tab3}, it can be seen that each step of our approach globally
+% improves the score on both metrics. However, processing, weights and averaging
+% (respectively denoted as $P$,$W$ and $Averaging$ in Tab.\ref{tab:tab3}) as
+% described in Section \ref{sec:filter} are the key steps of our algorithm.
+
+% It also appears that the averaging over the low-pass filter designs and the
+% threshold values increases significantly the quality of the inferred network
+% according to both metrics.
+
+% % Explaining the method (thèse de Gilles)
+% % Avg.: Averaging over the threholds and L-P filters improves a lot both metrics.
+% % Averaging
+
+% %% Depth -- Gilles chapitre 7
+% % Genie3 : better in auprc while worse in auroc than GTE. Why?
+% % Genie3 : "Conditioning" better and better but need a lot of trees
+
+% \begin{table}[tbh]
+% \centering
+% \small
+% \begin{tabular}{@{}l *{8}{c}@{}}
+% \hline
+%   & \multicolumn{4}{c}{AUROC} & \multicolumn{4}{c}{AUPRC} \\
+% \hline
+% Methods $\backslash$ normal- & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 \\
+% No  filtering       & 0.777 & 0.767 & 0.772 & 0.774 & 0.070 & 0.064 & 0.068 & 0.072\\
+% P                   & 0.925 & 0.925 & 0.924 & 0.923 & 0.322 & 0.324 & 0.323 & 0.312\\
+% P + W               & 0.931 & 0.930 & 0.928 & 0.927 & 0.333 & 0.334 & 0.327 & 0.313\\
+% P + W + PCA         & 0.932 & 0.931 & 0.930 & 0.928 & 0.364 & 0.366 & 0.359 & 0.344\\
+% Averaging           & 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388\\
+% %Averaging + Directivity & 0.944 & 0.943 & 0.942 & 0.940 & 0.404 & 0.405 & 0.399 & 0.389\\
+% \end{tabular}
+% \caption{Optimized method (TODO)}
+% \label{tab:tab3}
+% \end{table}
+
+% \begin{table}[tbh]
+% \centering
+% \small
+% \begin{tabular}{@{}l *{8}{c}@{}}
+% \hline
+%   & \multicolumn{4}{c}{AUROC} & \multicolumn{4}{c}{AUPRC} \\
+% \hline
+% Methods $\backslash$ normal- & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 \\
+% No  filtering       & 0.777 & 0.767 & 0.772 & 0.774 & 0.070 & 0.064 & 0.068 & 0.072\\
+% P                   & 0.923 & 0.925 & 0.923 & 0.922 & 0.311 & 0.315 & 0.313 & 0.304\\
+% P + W               & 0.931 & 0.929 & 0.928 & 0.926 & 0.326 & 0.323 & 0.319 & 0.303\\
+% P + W + PCA         & 0.932 & 0.930 & 0.928 & 0.926 & 0.355 & 0.353 & 0.350 & 0.333\\
+% Averaging           & 0.938 & 0.936 & 0.936 & 0.932 & 0.391 & 0.389 & 0.385 & 0.374\\
+% %Averaging + Directivity & 0.944 & 0.943 & 0.942 & 0.940 & 0.404 & 0.405 & 0.399 & 0.389\\
+% \end{tabular}
+% \caption{Simplified method (TODO)}
+% \label{tab:tab3}
+% \end{table}
+
+% %% Talk about filters future and past
 

### 2014-06-27 article.tex

@@
 here provide a ranking of all pairs of neurons according to some association
+ssociation
 score. To assess the quality of this ranking, we compute both ROC and

### 2014-06-27 article.tex
Appendix: ready to be proofread
Fix

@@
 
-\section*{Acknowledgments}
+\paragraph{Acknowledgments}
 A. Joly and G. Louppe are research fellows of the FNRS, Belgium.  A. Sutera is
@@
 
-\section{Particularities of the ``Full method''}
+\section{Particularities of ``Full method''}
 \label{app:optimized}
@@
 this section, we will present a heuristic trying to retrieve directivity.
-However, considering the argument in Section \ref{sec:results}, the additional
-gain margin of this approach compared to the undirected method is extremely
-limited.
+However, considering results in Section \ref{sec:results}, we expect that the
+additionnal gain margin should be extremely limited.
 
@@
 \end{tabular}
-\caption{Performance on \textit{normal-1,2,3,4} of the ``Full Method'' with and without the directivity heuristic.}
+\caption{Performance on \textit{normal-1,2,3,4} of ``Full Method'' with and without the directivity heuristic.}
 \label{tab:directivity}
@@
 GTE & 0.846 & 0.905 & 0.848 & 0.899 & 0.905 & 0.879\\
-GENIE3* & 0.781 &  0.922 & 0.875 & 0.899 & 0.886 &  0.890 \\ \hline
+GENIE3 & 0.781 &  0.922 & 0.875 & 0.899 & 0.886 &  0.890 \\ \hline
 & \multicolumn{6}{c|}{AUPRC}\\ \hline
@@
 GTE & 0.094 & 0.211 & 0.081 & 0.165 & 0.210 & 0.144\\
-GENIE3* & 0.128 & 0.261 & 0.108 & 0.293 & 0.256 & 0.224\\ \hline
+GENIE3 & 0.128 & 0.261 & 0.108 & 0.293 & 0.256 & 0.224\\ \hline
 \end{tabular}

### 2014-06-27 article.tex
break 80 char in appendix

@@
 
-This section is a complete description of the method specifically tuned for the challenge.
-Basically, it is an optimized version of the method presented in Sections~\ref{sec:filter}~to~\ref{sec:results}, therefore only differences between both version of our method will be highlighted.
+This section is a complete description of the method specifically tuned for the
+challenge. Basically, it is an optimized version of the method presented in
+Sections~\ref{sec:filter}~to~\ref{sec:results}, therefore only differences
+between both version of our method will be highlighted.
 
@@
 
-As we introduce a composed function in section~\ref{sec:filter}, let us describe a new composed function with optimized filters to improve the quality of the inference process.
-
-Besides filters
-$f_1$ and $f_2$ respectively defined by equations \ref{eq:symetric-median} and \ref{eq:weighted-asymetric-median}, we also consider two other low-pass
-filters:
+As we introduce a composed function in section~\ref{sec:filter}, let us
+describe a new composed function with optimized filters to improve the quality
+of the inference process.
+
+Besides filters $f_1$ and $f_2$ respectively defined by equations \ref{eq
+:symetric-median} and \ref{eq:weighted-asymetric-median}, we also consider two
+other low-pass filters:
 
@@
 
-Theses filters lead, taken individually, to worse performances
- than filters $f_1$ and
-$f_2$ but the averaging approach over all low-pass
-filters gets better for the ROC AUC.
+Theses filters lead, taken individually, to worse performances  than filters
+$f_1$ and $f_2$ but the averaging approach over all low-pass filters gets
+better for the ROC AUC.
 
@@
 
-As a computation trick, it appears that using a parametrized hard-threshold filter slightly improves performances.
-Introducing the parameter $c$ in function $h$ yields to an optimized filter \begin{align}
+As a computation trick, it appears that using a parametrized hard-threshold
+filter slightly improves performances. Introducing the parameter $c$ in
+function $h$ yields to an optimized filter
+\begin{align}
 h^*(x^t_i) = (x_i^t)^c \text{ } \mathbb{1}(x_i^t \ge \tau) \text{ with } \tau > 0,
@@
 
-The magnification can also be optimized by adjusting differently the effect depending on the global activity and the low-pass filter used.
-In that sense, we introduce the following function \begin{align}
+The magnification can also be optimized by adjusting differently the effect
+depending on the global activity and the low-pass filter used. In that sense,
+we introduce the following function
+\begin{align}
  w^*(x^{t}_i) &= {(x^{t}_i + 1 )^{\left (1 + \frac{1}{\sum_{j} x^{t}_j}\right )}}^{m}
 \end{align}
-where $m$ is a piecewise linear function depending on the low-pass filter and on the range of the global activity.
-We refer to our implementation\footnote{available on \url{https://github.com/asutera/kaggle-connectomics}.} for the values of the parameters and especially the parameter $m$.
+where $m$ is a piecewise linear function depending on the low-pass filter and
+on the range of the global activity. We refer to our
+implementation\footnote{available on \url{https://github.com/asutera/kaggle-
+connectomics}.} for the values of the parameters and especially the parameter
+$m$.
 
@@
 \end{align*}
-tuned to maximize the
-ROC AUC on \textit{normal-1}.
+tuned to maximize the ROC AUC on \textit{normal-1}.
 
@@
 compute for each pair $(i,j)$
-
 \begin{align}
@@
 equation
-
 \begin{align}
@@
 At the light of the poor results of this heuristic taken on its own summarized
-on Table \ref{tab:directivity} as \textit{directivity}, we use it to make asymmetric the
-degree of association matrix using partial correlation statistics. We expect
-that when the heuristic is highly confident (i.e., $z_{i,j} \gg 0 \gg
-z_{j,i}$) the degree of association   of edge $(i,j)$ is increased while the
-degree of association corresponding to the edge $(j,i)$ is reduced. Even if
-this adjustment is subtle, it might have a slight positive effect on the ROC
-AUC.
+on Table \ref{tab:directivity} as \textit{directivity}, we use it to make
+asymmetric the degree of association matrix using partial correlation
+statistics. We expect that when the heuristic is highly confident (i.e.,
+$z_{i,j} \gg 0 \gg z_{j,i}$) the degree of association   of edge $(i,j)$ is
+increased while the degree of association corresponding to the edge $(j,i)$ is
+reduced. Even if this adjustment is subtle, it might have a slight positive
+effect on the ROC AUC.
 
@@
 
-\section{Supplementary results}
-\label{app:supp}
+\section{Supplementary results} \label{app:supp}
 
@@
 which are similar to \textit{normal} datasets, i.e., made of 1000 neurons,
-except for one parameter. We compute, as done in
-Section~\ref{sec:results}, both AUROC and AUPRC and results are reported in
+except for one parameter. We compute, as done in Section~\ref{sec:results},
+both AUROC and AUPRC and results are reported in
 Table~\ref{tab:results_appendix}. We will briefly recall what characterizes

### 2014-06-27 article.tex
Introduce the difference in preprocessing

@@
 
-This section is a complete description of the method specifically tuned for the
-challenge. Basically, it is an optimized version of the method presented in
-Sections~\ref{sec:filter}~to~\ref{sec:results}, therefore only differences
-between both version of our method will be highlighted.
+This section provides a full description of the method specifically tuned for
+the challenge. Since it is no more than an optimized version of the method
+presented in Sections~\ref{sec:filter}~to~\ref{sec:results}, the description
+will be limited to explaining the differences that exist between this method
+and its optimized version.
 
@@
 
-As we introduce a composed function in section~\ref{sec:filter}, let us
-describe a new composed function with optimized filters to improve the quality
-of the inference process.
+In Section~\ref{sec:filter}, we introduce two composed filtering functions in
+order (i) to remove noise induced by light scattering artifact, (ii) to take
+into account the slow decay of fluorescence signal and (iii) to reduce the
+importance of global high activity in the network. However, in order to win the
+challenge, we have heavily optimized several different, but yet similar,
+filtering composed function. Taken alone, those composed functions in
+conjunction with partial correlation might lead to worse AUROC, but improved
+whenever they are averaged.
 
@@
 :symetric-median} and \ref{eq:weighted-asymetric-median}, we also consider two
-other low-pass filters:
-
+other low-pass filters
 \begin{align}
-f_3(x^t_i) &= x^{t-1}_i + x^{t}_i + x^{t+1}_i + x^{t+2}_i \label{eq:asymetric-median-forward}, \\
-f_4(x^t_i) &=  x_i^t + x^{t+1}_i  + x^{t+2}_i + x^{t+3}_i  .
-\label{eq:asymetric-median}
+f_3(x^t_i) &= x^{t-1}_i + x^{t}_i + x^{t+1}_i + x^{t+2}_i, \label{eq:asymetric-median-forward} \\
+f_4(x^t_i) &=  x_i^t + x^{t+1}_i  + x^{t+2}_i + x^{t+3}_i. \label{eq:asymetric-median}
 \end{align}
@@
 Theses filters lead, taken individually, to worse performances  than filters
-$f_1$ and $f_2$ but the averaging approach over all low-pass filters gets
-better for the ROC AUC.
-
+$f_1$ and $f_2$ but averaging the results of all low-pass filters leads to better ROC AUC.
 \begin{table}[ht]\label{tab:comparison}
@@
 
-As a computation trick, it appears that using a parametrized hard-threshold
+As computation trick, it appears that using a parametrized hard-threshold
 filter slightly improves performances. Introducing the parameter $c$ in
-function $h$ yields to an optimized filter
+function $h$ yields an optimized filter
 \begin{align}
@@
 Table~\ref{tab:results_appendix}. We will briefly recall what characterizes
-each datasets:
+each dataset:
 \begin{description}
@@
 \item[highcc]: Similar network but with a higher clustering coefficient on average.
-\item[normal-3-highrate]: Same topology as \textit{normal-3} but with an higher firing frequency, i.e., with highly active neurons.
+\item[normal-3-highrate]: Same topology as \textit{normal-3} but with a higher firing frequency, i.e., with highly active neurons.
 \item[normal-4-lownoise]: Same topology as \textit{normal-4} but with a better signal to noise ratio.

### 2014-06-27 article.tex
comment resuls in the middle of methods

@@
 
+\textcolor{red}{AJ: This paragraph and table should go in a separate section}
 Theses filters lead, taken individually, to worse performances  than filters

### 2014-06-27 article.tex
Instead of modifying filter h, let's introduce a separate filter

@@
 
-As computation trick, it appears that using a parametrized hard-threshold
-filter slightly improves performances. Introducing the parameter $c$ in
-function $h$ yields an optimized filter
+After the hard thresholded filter $h$, they were significant differences in
+peak magnitudes. Since most timeseries $x_i^t$  were mainly between 0 and 1,
+we smoothened the difference in peak magnitude through
 \begin{align}
-h^*(x^t_i) = (x_i^t)^c \text{ } \mathbb{1}(x_i^t \ge \tau) \text{ with } \tau > 0,
+g(x^t_i) = (x_i^t)^c
 \end{align}
-where $c$ is set to $0.9$ after experiments.
+yield slightly AUROC with $c=0.9 \in (0, 1)$.
 

### 2014-06-27 article.tex
wording
typo
Rember the purpose of w* and fix the notation

@@
 \begin{align}
- w(x^{t}_i) &= (x^{t}_i + 1 )^{1 + \frac{1}{\sum_{j} x^{t}_j}},
+ w(x^{t}_i) &= (x^{t}_i + 1 )^{1 + \frac{1}{\sum_{j} x^{t}_j}}, \label{eq:magnify-filter}
 \end{align}
@@
 After the hard thresholded filter $h$, they were significant differences in
-peak magnitudes. Since most timeseries $x_i^t$  were mainly between 0 and 1,
-we smoothened the difference in peak magnitude through
+peak magnitudes. Since timeseries $x_i^t$  were mainly between 0 and 1,
+we smoothened the difference in peak magnitudes through
 \begin{align}
@@
 
-The magnification can also be optimized by adjusting differently the effect
-depending on the global activity and the low-pass filter used. In that sense,
-we introduce the following function
+After filter $c$, we applied a filter $w^*$ similar to $w$, whose goal is also
+to magnify the importance of spikes that occur in case of low global activity.
+Instead of equation \ref{eq:magnify-filter}, we had
 \begin{align}
- w^*(x^{t}_i) &= {(x^{t}_i + 1 )^{\left (1 + \frac{1}{\sum_{j} x^{t}_j}\right )}}^{m}
+ w^*(x^{t}_i) &= {(x^{t}_i + 1 )^{\left (1 + \frac{1}{\sum_{j} x^{t}_j}\right )}}^{k(\sum_{j} x^{t}_j)}
 \end{align}
-where $m$ is a piecewise linear function depending on the low-pass filter and
-on the range of the global activity. We refer to our
-implementation\footnote{available on \url{https://github.com/asutera/kaggle-
-connectomics}.} for the values of the parameters and especially the parameter
-$m$.
+where the function $k$ is a piecewise linear function optimized for each filter
+$f_1$, $f_2$, $f_3$ and $f_4$. For more details on this aspect, we refer the
+reader to the implementation \footnote{available on
+\url{https://github.com/asutera/kaggle- connectomics}.}.
 

### 2014-06-27 article.tex
corrections du mail de DE

--- 2014-06-27 article.tex
@@
 
-In Section~\ref{sec:filter}, we introduce two composed filtering functions in
-order (i) to remove noise induced by light scattering artifact, (ii) to take
-into account the slow decay of fluorescence signal and (iii) to reduce the
-importance of global high activity in the network. However, in order to win the
-challenge, we have heavily optimized several different, but yet similar,
-filtering composed function. Taken alone, those composed functions in
-conjunction with partial correlation might lead to worse AUROC, but improved
-whenever they are averaged.
-
-Besides filters $f_1$ and $f_2$ respectively defined by equations \ref{eq
-:symetric-median} and \ref{eq:weighted-asymetric-median}, we also consider two
-other low-pass filters
+As we introduce a composed function in Section~\ref{sec:filter}, let us
+describe a new composed function with optimized filters to improve the quality
+of the inference process.
+
+Besides filters $f_1$ and $f_2$ defined by equations \ref{eq
+:symetric-median} and \ref{eq:weighted-asymetric-median}, respectively we also consider two
+other low-pass filters:
+
 \begin{align}
-f_3(x^t_i) &= x^{t-1}_i + x^{t}_i + x^{t+1}_i + x^{t+2}_i, \label{eq:asymetric-median-forward} \\
-f_4(x^t_i) &=  x_i^t + x^{t+1}_i  + x^{t+2}_i + x^{t+3}_i. \label{eq:asymetric-median}
+f_3(x^t_i) &= x^{t-1}_i + x^{t}_i + x^{t+1}_i + x^{t+2}_i \label{eq:asymetric-median-forward}, \\
+f_4(x^t_i) &=  x_i^t + x^{t+1}_i  + x^{t+2}_i + x^{t+3}_i  .
+\label{eq:asymetric-median}
 \end{align}
 
-\textcolor{red}{AJ: This paragraph and table should go in a separate section}
 Theses filters lead, taken individually, to worse performances  than filters
 $f_1$ and $f_2$ but averaging the results of all low-pass filters leads to better ROC AUC.
+
 \begin{table}[ht]\label{tab:comparison}

### 2014-06-27 article.tex
Add a comparison between w and w*
typo
wording

--- 2014-06-27 article.tex
@@
 peak magnitudes. Since timeseries $x_i^t$  were mainly between 0 and 1,
-we smoothened the difference in peak magnitudes through
+we smoothened these differences in peak magnitudes through
 \begin{align}
@@
 \end{align}
-yield slightly AUROC with $c=0.9 \in (0, 1)$.
+yielding slightly better AUROC with $c=0.9 \in (0, 1)$.
 
@@
 where the function $k$ is a piecewise linear function optimized for each filter
-$f_1$, $f_2$, $f_3$ and $f_4$. For more details on this aspect, we refer the
-reader to the implementation \footnote{available on
+$f_1$, $f_2$, $f_3$ and $f_4$. By comparison, the filter $w$ used the following
+function $k(\sum_{j} x^{t}_j) = 1$. For more details on this aspect, we refer
+the reader to the implementation \footnote{available on
 \url{https://github.com/asutera/kaggle- connectomics}.}.
@@
 However, considering results in Section \ref{sec:results}, we expect that the
-additionnal gain margin should be extremely limited.
+additional gain margin should be extremely limited.
 

### 2014-06-27 article.tex

@@
 
+\textcolor{red}{Introduce each section as in the introduction of the article }
+
 % Let us remark that tuning
@@
 \begin{align}
-g(x^t_i) = (x_i^t)^c
+p(x^t_i) = (x_i^t)^c
 \end{align}
@@
 
-After filter $c$, we applied a filter $w^*$ similar to $w$, whose goal is also
+After filter $p$, we applied a filter $w^*$ similar to $w$, whose goal is also
 to magnify the importance of spikes that occur in case of low global activity.
@@
 
-\subsection*{Averaging the connectome inference from partial correlation statistics}
-
-In our experiments, we observed that the inference process is quite sensitive
-about the choice of the parameter value $\tau$ and the low-pass filter.
-Therefore, in order to reduce the variance of the results and thus the
-robustness of our approach, we perform an average over a range of parameter
-value $\tau$ from $0.100$ to $0.209$. We also perform a weighted average over
-the four low-pass filters with the following parameters
-\begin{align*}
-weight_{f_1} &= 1,\\
-weight_{f_2} &= 0.9, \\
-weight_{f_3} &= 0.7, \\
-weight_{f_4} &= 0.01
-\end{align*}
-tuned to maximize the ROC AUC on \textit{normal-1}.
+\subsection*{Weighted average of partial correlation statistics}
+
+The AUROC performance of the conjunction of the composed function $w^* \circ p
+\circ g \circ h \circ f_1$ (respectively $f_2$, $f_3$ and $f_4$) and the
+partial correlation statistics was quite sensitive to the choice of $\tau$, the
+hard threshold value and the design of the low pass filter. Similarly to the
+simplified method, we average the partial correlation statistics obtained by
+varying $\tau$ linearly from $0.100$ to $0.209$ and the low-pass filter.
+
+Given the unequal AUROC performance of $f_1$, $f_2$, $f_3$ and $f_4$, the
+contribution of each filter in the degree of association between two neurons
+was chosen as to maximize the AUROC on \textit{normal-1} and is function of
+their individual performance. By comparison in the simple method, each filter
+$f_1$ and $f_2$ were given equal weight.
+
+% In our experiments, we observed that the inference process is quite sensitive
+% about the choice of the parameter value $\tau$ and the low-pass filter.
+% Therefore, in order to reduce the variance of the results and thus the
+% robustness of our approach, we perform an average over a range of parameter
+% value $\tau$ from $0.100$ to $0.209$. We also perform a weighted average over
+% the four low-pass filters with the following parameters
+% \begin{align*}
+% weight_{f_1} &= 1,\\
+% weight_{f_2} &= 0.9, \\
+% weight_{f_3} &= 0.7, \\
+% weight_{f_4} &= 0.01
+% \end{align*}
+% tuned to maximize the ROC AUC on \textit{normal-1}.
 

### 2014-06-27 article.tex
introduction of appendix

--- 2014-06-27 article.tex
@@
 
+This appendix is structured as follows: Section \ref{app:signal} describes the differences about the signal processing methods applied on fluorescent calcium time series; Section \ref{app:averaging} then provides a detailed explanation of the averaging approach; Section \ref{app:connectome} presents a heuristic trying to retrieve directivity from fluorescent calcium time series while Section \ref{app:results} finally present results validating some choices that have been made.
+
+%% plan
+
 % Let us remark that tuning
@@
 
-\subsection*{Signal processing}
+\subsection{Signal processing}
+\ref{sapp:signal}
 
@@
 
-Besides filters $f_1$ and $f_2$ respectively defined by equations \ref{eq
-:symetric-median} and \ref{eq:weighted-asymetric-median}, we also consider two
+Besides filters $f_1$ and $f_2$ respectively defined by equations \ref{eq:symetric-median} 
+and \ref{eq:weighted-asymetric-median}, we also consider two
 other low-pass filters
@@
 peak magnitudes. Since timeseries $x_i^t$  were mainly between 0 and 1,
-we smoothened these differences in peak magnitudes through
+we smoothened the difference in peak magnitudes through
 \begin{align}
@@
 \end{align}
-yielding slightly better AUROC with $c=0.9 \in (0, 1)$.
+yield slightly AUROC with $c=0.9 \in (0, 1)$.
 
@@
 
-\subsection*{Averaging the connectome inference from partial correlation statistics}
+\subsection{Averaging the connectome inference from partial correlation statistics}
+\ref{sapp:averaging}
+
+%% plus en évidence le weighted - tenant compte des performances
 
@@
 
-\subsection*{Connectome inference from pairwise interaction statistics}
+\subsection{Connectome inference from pairwise interaction statistics}
+\ref{sapp:connectome}
 
@@
 However, considering results in Section \ref{sec:results}, we expect that the
-additional gain margin should be extremely limited.
+additionnal gain margin should be extremely limited.
 
@@
 \end{table}
+
+\subsection{Experiments}
+\ref{sapp:results}
 

### 2014-06-27 article.tex

--- 2014-06-27 article.tex
@@
 
-\textcolor{red}{Introduce each section as in the introduction of the article }
+This appendix is structured as follows: Section \ref{app:signal} describes the differences about the signal processing methods applied on fluorescent calcium time series; Section \ref{app:averaging} then provides a detailed explanation of the averaging approach; Section \ref{app:connectome} presents a heuristic trying to retrieve directivity from fluorescent calcium time series while Section \ref{app:results} finally present results validating some choices that have been made.
 
@@
 
-\subsection*{Weighted average of partial correlation statistics}
+\subsection{Weighted average of partial correlation statistics}
 
@@
 
-% In our experiments, we observed that the inference process is quite sensitive
-% about the choice of the parameter value $\tau$ and the low-pass filter.
-% Therefore, in order to reduce the variance of the results and thus the
-% robustness of our approach, we perform an average over a range of parameter
-% value $\tau$ from $0.100$ to $0.209$. We also perform a weighted average over
-% the four low-pass filters with the following parameters
-% \begin{align*}
-% weight_{f_1} &= 1,\\
-% weight_{f_2} &= 0.9, \\
-% weight_{f_3} &= 0.7, \\
-% weight_{f_4} &= 0.01
-% \end{align*}
-% tuned to maximize the ROC AUC on \textit{normal-1}.
-
-\subsection*{Connectome inference from pairwise interaction statistics}
+\subsection{Connectome inference from pairwise interaction statistics}
+\ref{sapp:connectome}
 

### 2014-06-27 article.tex
f2 is not only for the tuned version

@@
 theoretically grounded approach based on signal processing techniques and
-partial correlation statistics. The paper is structured as follows: Section
-\ref{sec:filter} describes the signal processing methods applied on fluorescent
-calcium time series; Section \ref{sec:inference} then presents the proposed
-approach and its theoretical properties; Section \ref{sec:results} provides an
-empirical analysis and comparison with other network inference methods, while
-Section \ref{sec:conclusion} finally discusses our work and provides further
-research directions. Additionally, Appendix \ref{app:optimized} further
-describes, in all details, our actual winning method, giving slightly better
-results than the method presented in the paper, at the price of parameter
-tuning.
+partial correlation statistics. The paper is structured as follows:
+Section~\ref{sec:filter} describes the signal processing methods applied on
+fluorescent calcium time series; Section\ref{sec:inference} then presents the
+proposed approach and its theoretical properties; Section~\ref{sec:results}
+provides an empirical analysis and comparison with other network inference
+methods, while Section~\ref{sec:conclusion} finally discusses our work and
+provides further research directions. Additionally,
+Appendix~\ref{app:optimized} further describes, in all details, our actual
+winning method, giving slightly better results than the method presented in
+the paper, at the price of parameter tuning. Appendix~\ref{app:supp} provides supplementary results on other datasets.
 
@@
 
-To summarize, the full signal processing pipeline of our simplified (resp.
-tuned) approach is defined by the composed function $w \circ h \circ g \circ
+To summarize, the full signal processing pipeline of our simplified approach is defined by the composed function $w \circ h \circ g \circ
 f_1$ (resp. $f_2$). When applied to the raw signal of Figure
@@
 
-This appendix is structured as follows: Section \ref{app:signal} describes the differences about the signal processing methods applied on fluorescent calcium time series; Section \ref{app:averaging} then provides a detailed explanation of the averaging approach; Section \ref{app:connectome} presents a heuristic trying to retrieve directivity from fluorescent calcium time series while Section \ref{app:results} finally present results validating some choices that have been made.
+This appendix is structured as follows: Section~\ref{sapp:signal} describes
+the differences about the signal processing methods applied on fluorescent
+calcium time series; Section~\ref{sapp:averaging} then provides a detailed
+explanation of the averaging approach; Section~\ref{sapp:connectome} presents
+a heuristic trying to retrieve directivity from fluorescent calcium time
+series while Section~\ref{sapp:results} finally present results validating
+some choices that have been made.
 
@@
 \subsection{Signal processing}
-\ref{sapp:signal}
+\label{sapp:signal}
 
@@
 challenge, we have heavily optimized several different, but yet similar,
-filtering composed function. Taken alone, those composed functions in
+filtering composed function. Taken individually, those composed functions in
 conjunction with partial correlation might lead to worse AUROC, but improved
-whenever they are averaged.
+whenever they are averaged (see \ref{tab:} ).
 
@@
 \end{align}
-
-\textcolor{red}{AJ: This paragraph and table should go in a separate section}
-Theses filters lead, taken individually, to worse performances  than filters
-$f_1$ and $f_2$ but averaging the results of all low-pass filters leads to better ROC AUC.
-\begin{table}[ht]\label{tab:comparison}
-%\caption{Evaluation of different methods on the four \textit{normal} datasets\label{tab:comparison}}
-\centering
-\small
-\begin{tabular}{| l | c c c c | c c c c |}
-\hline
-& \multicolumn{4}{c|}{AUROC} & \multicolumn{4}{c|}{AUPRC} \\
-\textit{Averaging} $\backslash$ \textit{normal-} & \textit{1} & \textit{2} & \textit{3} & \textit{4} & \textit{1} & \textit{2} & \textit{3} & \textit{4} \\
-\hline
-\hline
- with $f_1$, $f_2$ & 0.937 & 0.935 & 0.935 & 0.931 & 0.391 &  \textbf{0.390} &  0.385 & \textbf{0.375}  \\
- with $f_1$, $f_2$, $f_3$, $f_4$ & \textbf{0.938} & \textbf{0.936} & \textbf{0.936} & \textbf{0.932} & 0.391 & 0.389 & 0.385 & 0.374\\
-\hline
-\end{tabular}
-\caption{Performance on \textit{normal-1,2,3,4} with partial correlation with different averaging approaches.}
-\end{table}
 
@@
 \subsection{Weighted average of partial correlation statistics}
+\label{sapp:averaging}
 
@@
 \subsection{Connectome inference from pairwise interaction statistics}
-\ref{sapp:connectome}
+\label{sapp:connectome}
 
@@
 
-At the light of the poor results of this heuristic taken on its own summarized
-on Table \ref{tab:directivity} as \textit{directivity}, we use it to make
+At the light of the poor results of this heuristic taken on its own
+(on Table \ref{tab:directivity} in Section~\ref{sapp:results}) as \textit{directivity}, we use it to make
 asymmetric the degree of association matrix using partial correlation
@@
 
+\subsection{Experiments}
+\label{sapp:results}
+
+Theses filters lead, taken individually, to worse performances  than filters
+$f_1$ and $f_2$ but averaging the results of all low-pass filters leads to better ROC AUC.
 \begin{table}[ht]\label{tab:comparison}
@@
 & \multicolumn{4}{c|}{AUROC} & \multicolumn{4}{c|}{AUPRC} \\
+\textit{Averaging} $\backslash$ \textit{normal-} & \textit{1} & \textit{2} & \textit{3} & \textit{4} & \textit{1} & \textit{2} & \textit{3} & \textit{4} \\
+\hline
+\hline
+ with $f_1$, $f_2$ & 0.937 & 0.935 & 0.935 & 0.931 & 0.391 &  \textbf{0.390} &  0.385 & \textbf{0.375}  \\
+ with $f_1$, $f_2$, $f_3$, $f_4$ & \textbf{0.938} & \textbf{0.936} & \textbf{0.936} & \textbf{0.932} & 0.391 & 0.389 & 0.385 & 0.374\\
+\hline
+\end{tabular}
+\caption{Performance on \textit{normal-1,2,3,4} with partial correlation with different averaging approaches.}
+\end{table}
+
+\begin{table}[ht]\label{tab:comparison}
+%\caption{Evaluation of different methods on the four \textit{normal} datasets\label{tab:comparison}}
+\centering
+\small
+\begin{tabular}{| l | c c c c | c c c c |}
+\hline
+& \multicolumn{4}{c|}{AUROC} & \multicolumn{4}{c|}{AUPRC} \\
 \textit{Full method} $\backslash$ \textit{normal-} & \textit{1} & \textit{2} & \textit{3} & \textit{4} & \textit{1} & \textit{2} & \textit{3} & \textit{4} \\
@@
 \end{table}
-
-\subsection{Experiments}
-\ref{sapp:results}
 

### 2014-06-27 article.tex
wording in the appendix: work in progress

@@
 challenge, we have heavily optimized several different, but yet similar,
-filtering composed function. Taken individually, those composed functions in
-conjunction with partial correlation might lead to worse AUROC, but improved
-whenever they are averaged (see \ref{tab:} ).
+filtering composed function.
+On the one hand, each part of the composed functions is optimized to maximize the ROC AUC (e.g., $w^*$).
+On the other hand, we introduce new functions (e.g., $f_3$ and $f_4$) leading to alternative composed functions.
+They might lead to worse ROC AUC when taken individually but they improve the overall ROC AUC when taking as a part of the averaging approach.
+
+% Taken individually, those composed functions in
+% conjunction with partial correlation might lead to worse AUROC, but improved
+% whenever they are averaged.
 
@@
 After the hard thresholded filter $h$, they were significant differences in
-peak magnitudes. Since timeseries $x_i^t$  were mainly between 0 and 1,
+peak magnitudes. Since time series $x_i^t$  were mainly between 0 and 1,
 we smoothened these differences in peak magnitudes through
@@
 
-Theses filters lead, taken individually, to worse performances  than filters
-$f_1$ and $f_2$ but averaging the results of all low-pass filters leads to better ROC AUC.
+\paragraph{On the interest of low-pass filters $f_3$ and $f_4$.}
+
+%%% SHOW DIFFERENTS COMPOSED FUNCTION
+
+% Theses filters lead, taken individually, to worse performances  than filters
+% $f_1$ and $f_2$ but averaging the results of all low-pass filters leads to better ROC AUC.
+
+As reported on Table~\ref{tab:f3f4}, averaging over all low-pass filters leads to better ROC AUC than averaging over only two low-pass filters, i.e., $f_1$ and $f_2$.
+
 \begin{table}[ht]\label{tab:comparison}
@@
 \caption{Performance on \textit{normal-1,2,3,4} with partial correlation with different averaging approaches.}
+\label{tab:f3f4}
 \end{table}
 
+\paragraph{On the contribution of the directivity heuristic.}
 \begin{table}[ht]\label{tab:comparison}
@@
 \end{description}
+
+Average partial correlation and its tuned variant, i.e.,``Full method'', clearly outperform other network inference methods on all datasets (with 1000 neurons) provided by the organizers.
+It confirm that the presented methodology in this work would constitute a very solid baseline.
 

### 2014-06-27 article.tex
changement dans l'appendice

--- 2014-06-27 article.tex
@@
 hard-threshold filter
-\begin{align}
+\begin{align}\label{eqn:hfilter}
 h(x^{t}_i) &= x^{t}_i \mathbb{1}(x^{t}_i \geq \tau) \text{ with } \tau > 0,
@@
 
-\section{Particularities of ``Full method''}
+\section{Description  of the ``Full method''}
 \label{app:optimized}
 
-This section provides a full description of the method specifically tuned for
-the challenge. Since it is no more than an optimized version of the method
-presented in Sections~\ref{sec:filter}~to~\ref{sec:results}, the description
-will be limited to explaining the differences that exist between this method
-and its optimized version.
-
-This appendix is structured as follows: Section~\ref{sapp:signal} describes
-the differences about the signal processing methods applied on fluorescent
-calcium time series; Section~\ref{sapp:averaging} then provides a detailed
-explanation of the averaging approach; Section~\ref{sapp:connectome} presents
-a heuristic trying to retrieve directivity from fluorescent calcium time
-series while Section~\ref{sapp:results} finally present results validating
-some choices that have been made.
+This section provides a detailed description of the method specifically tuned
+for the Connectomics challenge. We will restrict our description to the
+differences with respect to the simplified method presented in the main
+paper. Most parameters were tuned so as to maximize AUROC on the
+\textit{normal-1} dataset and our design choices were validated by monitoring
+the AUROC obtained by the 145 entries we submitted during the
+challenge. Although the tuned method performs better than the simplified one on
+the challenge dataset and this tuning was probably decisive to get the best
+performance, we believe that the tuned method clearly overfits the
+simulator used to generate the challenge data and that the simplified method
+should work equally well on new independent datasets. We nevertheless provide
+the tuned method here for reference purpose. Our implementation of the tuned
+method is available at \url{https://github.com/asutera/kaggle-connectomics}.
+
+This appendix is structured as follows: Section~\ref{sapp:signal} describes the
+differences in terms of signal processing. Section~\ref{sapp:averaging} then
+provides a detailed presentation of the averaging
+approach. Section~\ref{sapp:connectome} presents a heuristic to retrieve edge
+directionality. Finally, Section~\ref{sapp:results} presents some experimental
+results to validate the different steps of our proposal.
 
@@
 
-In Section~\ref{sec:filter}, we introduce two composed filtering functions in
-order (i) to remove noise induced by light scattering artifact, (ii) to take
-into account the slow decay of fluorescence signal and (iii) to reduce the
-importance of global high activity in the network. However, in order to win the
-challenge, we have heavily optimized several different, but yet similar,
-filtering composed function. Taken individually, those composed functions in
-conjunction with partial correlation might lead to worse AUROC, but improved
-whenever they are averaged (see \ref{tab:} ).
-
-Besides filters $f_1$ and $f_2$ respectively defined by equations \ref{eq:symetric-median} 
-and \ref{eq:weighted-asymetric-median}, we also consider two
-other low-pass filters
+In Section~\ref{sec:filter}, we introduce four filtering functions ($f$, $g$,
+$h$, and $w$) that are composed in sequence (i.e., $w \circ h \circ g \circ
+f$) to provide the signals from which to compute partial correlation
+statistics.
+
+Filtering is modified as follows in the tuned method:
+\begin{itemize}
+\item In addition to $f_1$ and $f_2$ (Equations \ref{eq:symetric-median} and
+  \ref{eq:weighted-asymetric-median}), two alternative low-pass filters $f_3$
+  and $f_4$ are considered:
 \begin{align}
 f_3(x^t_i) &= x^{t-1}_i + x^{t}_i + x^{t+1}_i + x^{t+2}_i, \label{eq:asymetric-median-forward} \\
-f_4(x^t_i) &=  x_i^t + x^{t+1}_i  + x^{t+2}_i + x^{t+3}_i. \label{eq:asymetric-median}
+f_4(x^t_i) &=  x_i^t + x^{t+1}_i  + x^{t+2}_i + x^{t+3}_i. \label{eq:asymetric-median}.
 \end{align}
-
-After the hard thresholded filter $h$, they were significant differences in
-peak magnitudes. Since timeseries $x_i^t$  were mainly between 0 and 1,
-we smoothened these differences in peak magnitudes through
+\item An additional filter $p$ is applied to smoothen differences in peak magnitudes
+  that might remain after the application of the hard-threshold filter $h$:
 \begin{align}
-p(x^t_i) = (x_i^t)^c
+p(x^t_i) = (x_i^t)^c,
 \end{align}
-yielding slightly better AUROC with $c=0.9 \in (0, 1)$.
-
-After filter $p$, we applied a filter $w^*$ similar to $w$, whose goal is also
-to magnify the importance of spikes that occur in case of low global activity.
-Instead of equation \ref{eq:magnify-filter}, we had
+with $c=0.9$.
+\item Filter $w$ is replaced by a more complex filter $w^*$ defined as:
 \begin{align}
@@
 \end{align}
-where the function $k$ is a piecewise linear function optimized for each filter
-$f_1$, $f_2$, $f_3$ and $f_4$. By comparison, the filter $w$ used the following
-function $k(\sum_{j} x^{t}_j) = 1$. For more details on this aspect, we refer
-the reader to the implementation \footnote{available on
-\url{https://github.com/asutera/kaggle- connectomics}.}.
+where the function $k$ is a piecewise linear function optimized separately for
+each filter $f_1$, $f_2$, $f_3$ and $f_4$ (see the implementation for full
+details). Filter $w$ in the simplified method is a special case of $w^*$ with
+$k(\sum_j x_j^t)=1$.
+\end{itemize}
+The pre-processed time-series are then obtained by the application of the
+following function: $w^*\circ p \circ h \circ g \circ f_i$ (with $i=1$,2,3, or 4)
+
+%% two composed filtering functions in
+%% order (i) to remove noise induced by light scattering artifact, (ii) to take
+%% into account the slow decay of fluorescence signal and (iii) to reduce the
+%% importance of global high activity in the network. However, in order to win the
+%% challenge, we have heavily optimized several different, but yet similar,
+%% filtering composed function. On the one hand, each part of the composed
+%% functions is optimized to maximize the ROC AUC (e.g., $w^*$). On the other
+%% hand, we introduce new functions (e.g., $f_3$ and $f_4$) leading to alternative
+%% composed functions. They might lead to worse ROC AUC when taken individually
+%% but they improve the overall ROC AUC when taking as a part of the averaging
+%% approach.
+
+% Taken individually, those composed functions in
+% conjunction with partial correlation might lead to worse AUROC, but improved
+% whenever they are averaged.
+
+%% Besides filters $f_1$ and $f_2$ respectively defined by equations \ref{eq:symetric-median} 
+%% and \ref{eq:weighted-asymetric-median}, we also consider two
+%% other low-pass filters
+%% \begin{align}
+%% f_3(x^t_i) &= x^{t-1}_i + x^{t}_i + x^{t+1}_i + x^{t+2}_i, \label{eq:asymetric-median-forward} \\
+%% f_4(x^t_i) &=  x_i^t + x^{t+1}_i  + x^{t+2}_i + x^{t+3}_i. \label{eq:asymetric-median}
+%% \end{align}
+
+%% After the hard thresholded filter $h$, they were significant differences in
+%% peak magnitudes. Since time series $x_i^t$  were mainly between 0 and 1,
+%% we smoothened these differences in peak magnitudes through
+%% \begin{align}
+%% p(x^t_i) = (x_i^t)^c
+%% \end{align}
+%% yielding slightly better AUROC with $c=0.9 \in (0, 1)$.
+
+%% After filter $p$, we applied a filter $w^*$ similar to $w$, whose goal is also
+%% to magnify the importance of spikes that occur in case of low global activity.
+%% Instead of equation \ref{eq:magnify-filter}, we had
+%% \begin{align}
+%%  w^*(x^{t}_i) &= {(x^{t}_i + 1 )^{\left (1 + \frac{1}{\sum_{j} x^{t}_j}\right )}}^{k(\sum_{j} x^{t}_j)}
+%% \end{align}
+%% where the function $k$ is a piecewise linear function optimized for each filter
+%% $f_1$, $f_2$, $f_3$ and $f_4$. By comparison, the filter $w$ used the following
+%% function $k(\sum_{j} x^{t}_j) = 1$. For more details on this aspect, we refer
+%% the reader to the implementation \footnote{available on
+%% \url{https://github.com/asutera/kaggle- connectomics}.}.
 
@@
 
-The AUROC performance of the conjunction of the composed function $w^* \circ p
-\circ g \circ h \circ f_1$ (respectively $f_2$, $f_3$ and $f_4$) and the
-partial correlation statistics was quite sensitive to the choice of $\tau$, the
-hard threshold value and the design of the low pass filter. Similarly to the
-simplified method, we average the partial correlation statistics obtained by
-varying $\tau$ linearly from $0.100$ to $0.209$ and the low-pass filter.
-
-Given the unequal AUROC performance of $f_1$, $f_2$, $f_3$ and $f_4$, the
-contribution of each filter in the degree of association between two neurons
-was chosen as to maximize the AUROC on \textit{normal-1} and is function of
-their individual performance. By comparison in the simple method, each filter
-$f_1$ and $f_2$ were given equal weight.
-
-\subsection{Connectome inference from pairwise interaction statistics}
+As discussed in Section \ref{sec:inference}, the performance of the method (in
+terms of AUROC) is sensitive to the value of the parameter $\tau$ of the
+hard-threshold filter $h$ (see Equation \ref{eqn:hfilter}), and to the choice
+of the low-pass filter (among $\{f_1, f_2, f_3, f_4\}$). Like in the simplified
+method, we therefore averaged the partial correlation statistics obtained by
+varying $\tau$ linearly from $0.100$ to $0.209$ (in step of $0.001)$ and by
+varying the low-pass filter in $\{f_1, f_2, f_3, f_4\}$. Unlike in the
+simplified method where each filter $f_1$ and $f_2$ were given equal weight in
+the averaging, in the tuned method, we weighted each of the four filters
+according to its individual performance on the \textit{normal-1}
+dataset. \textcolor{red}{PG: je ne suis pas s\^ur de comprendre comment ces
+  poids sont d\'etermin\'es}
+
+%% Given the unequal AUROC performance of $f_1$, $f_2$, $f_3$ and $f_4$, the
+%% contribution of each filter in the degree of association between two neurons
+%% was chosen as to maximize the AUROC on \textit{normal-1} and is function of
+%% their individual performance. By comparison in the simple method, each filter
+%% $f_1$ and $f_2$ were given equal weight.
+
+\subsection{Prediction of edge orientation}
 \label{sapp:connectome}
 
-Since partial correlation statistics is a symmetric measure and the connectome
-is a directed graph, it should be rewarding to detect the edge orientation. In
-this section, we will present a heuristic trying to retrieve directivity.
-However, considering results in Section \ref{sec:results}, we expect that the
-additional gain margin should be extremely limited.
-
-The heuristic is based on the following observation. The rise of fluorescence
+Partial correlation statistics is a symmetric measure, while the connectome is
+a directed graph. It could thus be beneficial to try to predict edge orientation. In
+this section, we present a heuristic to retrieve directionality. %% Note however that
+%% given the discussion at the end of Section~\ref{sec:results}, we cannot expect
+%% a very large improvement in AUROC by predicting edge orientation.
+
+This heuristic is based on the following observation. The rise of fluorescence
 of a neuron indicates its activation. If another neuron is activated after a
-slight delay, this could have been caused by the activation of the first
-neuron and therefore highlight a (direct) directed relationship between the
-two neurons. With that in mind, the heuristic principle is to count the number
-of such events occurred between neurons $i$ and $j$ for consecutive time
-steps. It can be done by counting the number of times that a transition from
-neuron $i$ to neuron $j$ for two consecutive time steps, or mathematically we
-compute for each pair $(i,j)$
+slight delay, this could be a consequence of the activation of the first neuron
+and therefore indicate a directed link in the connectome from the first to the
+second neuron. Given this analysis, the idea of our heuristic is to count the
+number of such events occurring between neurons $i$ and $j$ for consecutive
+time steps. Mathematically, we compute for each pair $(i,j)$:
 \begin{align}
-s_{ij} = \sum_{t=1}^{T - 1} \mathbb{1}((x_j^{t+1} - x_i^t) \in \left[\phi_1, \phi_2\right])
+s_{i,j} = \sum_{t=1}^{T - 1} \mathbb{1}((x_j^{t+1} - x_i^t) \in \left[\phi_1, \phi_2\right])
 \end{align}
@@
 
-Two issues may be spotted. First, this heuristic is not able to distinguish a
-directed relationships if both neurons are activated in the same time step and
-may wrongly characterize indirect relationships because of the time
-resolution. Second, it may be necessary to take into account $s_{ji}$ to
-estimate the quality of the pairwise coefficient $s_{i,j}$. Indeed, if both
-coefficients are similar ($s_{ij} \sim s_{ji}$) the directivity can not be
-inferred since the order of fluorescent rising is not well defined. On the
-contrary, different coefficients $s_{ij}$ and $s_{ji}$ mean that an order of
-fluorescent rising is well established and observable. There we choose to
-compute a differential pairwise coefficient $z_{ij}$ defined by the following
-equation
+Two issues remain with this heuristic. First, it does not allow to detect a
+directed relationship if both neurons are activated simultaneously at the same
+time step, ie., when the delay between the two activations is below the time
+resolution. Second, one needs to compare $s_{j,i}$ and $s_{i,j}$ to decide on
+edge orientation. Indeed, edge orientation can only be predicted with some
+confidence if either $s_{i,j}$ is greater than $s_{j,i}$ ($i\rightarrow j$) or
+$s_{i,j}$ is lower than $s_{j,i}$ ($i\rightarrow j$). To address these issues,
+we computed a differential pairwise coefficient $z_{ij}$ defined as follows:
 \begin{align}
@@
 
-At the light of the poor results of this heuristic taken on its own
-(on Table \ref{tab:directivity} in Section~\ref{sapp:results}) as \textit{directivity}, we use it to make
-asymmetric the degree of association matrix using partial correlation
-statistics. We expect that when the heuristic is highly confident (i.e.,
-$z_{i,j} \gg 0 \gg z_{j,i}$) the degree of association   of edge $(i,j)$ is
-increased while the degree of association corresponding to the edge $(j,i)$ is
-reduced. Even if this adjustment is subtle, it might have a slight positive
-effect on the ROC AUC.
+\textcolor{red}{PG: je ne comprends pas ce qui est fait exactement. Mettre les
+  maths? Valeurs de $\phi_1$ et $\phi_2$ ?} At the light of the poor results of this heuristic taken on its own
+(on Table \ref{tab:directivity} in Section~\ref{sapp:results}) as
+\textit{directivity}, we use it to make asymmetric the degree of association
+matrix using partial correlation statistics. We expect that when the heuristic
+is highly confident (i.e., $z_{i,j} \gg 0 \gg z_{j,i}$) the degree of
+association of edge $(i,j)$ is increased while the degree of association
+corresponding to the edge $(j,i)$ is reduced. Even if this adjustment is
+subtle, it might have a slight positive effect on the ROC AUC.
 
@@
 
-Theses filters lead, taken individually, to worse performances  than filters
-$f_1$ and $f_2$ but averaging the results of all low-pass filters leads to better ROC AUC.
-\begin{table}[ht]\label{tab:comparison}
+\paragraph{On the interest of low-pass filters $f_3$ and $f_4$.}
+
+%%% SHOW DIFFERENTS COMPOSED FUNCTION
+
+% Theses filters lead, taken individually, to worse performances  than filters
+% $f_1$ and $f_2$ but averaging the results of all low-pass filters leads to better ROC AUC.
+
+As reported in Table~\ref{tab:f3f4}, averaging over all low-pass filters leads
+to better AUROC scores than averaging over only two low-pass filters, i.e., $f_1$ and
+$f_2$. It however slightly deteriorates AUPRC.
+
+\begin{table}[ht]
+%\caption{Evaluation of different methods on the four \textit{normal} datasets\label{tab:comparison}}
+\caption{Performance on \textit{normal-1,2,3,4} with partial correlation with different averaging approaches.}
+\label{tab:f3f4}
+\centering
+\small
+\begin{tabular}{| l | c c c c | c c c c |}
+\hline
+& \multicolumn{4}{c|}{AUROC} & \multicolumn{4}{c|}{AUPRC} \\
+\textit{Averaging} $\backslash$ \textit{normal-} & \textit{1} & \textit{2} & \textit{3} & \textit{4} & \textit{1} & \textit{2} & \textit{3} & \textit{4} \\
+\hline
+\hline
+ with $f_1$, $f_2$ & 0.937 & 0.935 & 0.935 & 0.931 & 0.391 &  \textbf{0.390} &  0.385 & \textbf{0.375}  \\
+ with $f_1$, $f_2$, $f_3$, $f_4$ & \textbf{0.938} & \textbf{0.936} & \textbf{0.936} & \textbf{0.932} & 0.391 & 0.389 & 0.385 & 0.374\\
+\hline
+\end{tabular}
+\end{table}
+
+\paragraph{On the contribution of the directionality heuristic.}
+
+Table~\ref{tab:dir} compares AUROC and AUPRC with and without prediction
+of edge orientation. Both AUROC and AUPRC are (very slightly) improved by
+directing the edges.
+
+\begin{table}[ht]\label{tab:dir}
+\caption{Performance on \textit{normal-1,2,3,4} of ``Full Method'' with and
+  without prediction of edge orientation}
+\label{tab:directivity}
+
 %\caption{Evaluation of different methods on the four \textit{normal} datasets\label{tab:comparison}}
@@
 & \multicolumn{4}{c|}{AUROC} & \multicolumn{4}{c|}{AUPRC} \\
-\textit{Averaging} $\backslash$ \textit{normal-} & \textit{1} & \textit{2} & \textit{3} & \textit{4} & \textit{1} & \textit{2} & \textit{3} & \textit{4} \\
-\hline
-\hline
- with $f_1$, $f_2$ & 0.937 & 0.935 & 0.935 & 0.931 & 0.391 &  \textbf{0.390} &  0.385 & \textbf{0.375}  \\
- with $f_1$, $f_2$, $f_3$, $f_4$ & \textbf{0.938} & \textbf{0.936} & \textbf{0.936} & \textbf{0.932} & 0.391 & 0.389 & 0.385 & 0.374\\
+\textit{Full method} $\backslash$ \textit{normal-} & \textit{1} & \textit{2} & \textit{3} & \textit{4} & \textit{1} & \textit{2} & \textit{3} & \textit{4} \\
+\hline
+\hline
+ Undirected & 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388  \\
+  Directed & \textbf{0.944} & \textbf{0.943} & 0.942 & \textbf{0.940} & \textbf{0.404} & \textbf{0.405} & \textbf{0.399} & \textbf{0.389}\\
 \hline
 \end{tabular}
-\caption{Performance on \textit{normal-1,2,3,4} with partial correlation with different averaging approaches.}
 \end{table}
 
-\begin{table}[ht]\label{tab:comparison}
-%\caption{Evaluation of different methods on the four \textit{normal} datasets\label{tab:comparison}}
-\centering
-\small
-\begin{tabular}{| l | c c c c | c c c c |}
-\hline
-& \multicolumn{4}{c|}{AUROC} & \multicolumn{4}{c|}{AUPRC} \\
-\textit{Full method} $\backslash$ \textit{normal-} & \textit{1} & \textit{2} & \textit{3} & \textit{4} & \textit{1} & \textit{2} & \textit{3} & \textit{4} \\
-\hline
-\hline
- without directivity & 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388  \\
-  with directivity  & \textbf{0.944} & \textbf{0.943} & 0.942 & \textbf{0.940} & \textbf{0.404} & \textbf{0.405} & \textbf{0.399} & \textbf{0.389}\\
-\hline
-\end{tabular}
-\caption{Performance on \textit{normal-1,2,3,4} of ``Full Method'' with and without the directivity heuristic.}
-\label{tab:directivity}
-\end{table}
-
 \section{Supplementary results} \label{app:supp}
 
-We report here experiments on particular datasets provided by the organizers
-which are similar to \textit{normal} datasets, i.e., made of 1000 neurons,
-except for one parameter. We compute, as done in Section~\ref{sec:results},
-both AUROC and AUPRC and results are reported in
-Table~\ref{tab:results_appendix}. We will briefly recall what characterizes
-each dataset:
+We report in this apprendix the performance of the different methods compared
+in the paper on 6 additional datasets provided by the challenge
+organizers. These datasets, corresponding each to networks of 1000 neurons, are similar to
+the \textit{normal} datasets except for one feature:
 \begin{description}
@@
 \end{description}
+
+Results of several methods on these 6 datasets are provided in
+Table~\ref{tab:results_appendix}. They confirm what we observed on the
+\textit{normal} datasets. Average partial correlation and its tuned variant,
+i.e.,``Full method'', clearly outperform other network inference methods on all
+datasets. PC is close to GENIE3 and GTE but still slightly worse. GENIE3
+performs better than GTE most of the times.
 

### 2014-06-27 article.tex
minor change in appendix
minor changes in appendix

@@
 confidence if either $s_{i,j}$ is greater than $s_{j,i}$ ($i\rightarrow j$) or
-$s_{i,j}$ is lower than $s_{j,i}$ ($i\rightarrow j$). To address these issues,
+$s_{i,j}$ is lower than $s_{j,i}$ ($j\rightarrow i$). To address these issues,
 we computed a differential pairwise coefficient $z_{ij}$ defined as follows:
@@
 \begin{table}[h]
+\caption{Performance (top: AUROC, bottom: AUPRC) on specific datasets with different methods.}
+\label{tab:results_appendix}
 \centering
@@
 \end{tabular}
-\caption{Performance (top: AUROC, bottom: AUPRC) on specific datasets with different methods.}
-\label{tab:results_appendix}
 \end{table}

### 2014-06-28 article.tex
AQ : minor changes

@@
    \Name{Vincent François-Lavet}, \Email{a.sutera@ulg.ac.be}\\
-   \Name{Aaron Qiu},
+   \Name{Zixiao Aaron Qiu},
    \Name{Gilles Louppe},
@@
 \begin{abstract}
-In this work, we propose a simple, but yet efficient, method for the problem of
-connectome inference in calcium imaging data. The proposed algorithm is made of
+In this work, we propose a simple, but yet efficient method for the problem of
+connectome inference in calcium imaging data. The proposed algorithm consists of
 two steps. First, processing the raw signals to detect neural peak activities.
@@
 inference problem consists in retrieving the synaptic connections between
-neurons on the basis of the fluorescence time series. In particular, this
-problem is often made difficult because of experimental issues, including
-masking effects (making some of the neurons not to be observed or confounded
-with others), the low sampling rate of the optical device with respect to the
+neurons on the basis of the fluorescence time series. However, this
+problem is often difficult because of experimental issues, including
+masking effects (i.e., some of the neurons are not observed or confounded with others), the low sampling rate of the optical device with respect to the
 neural activity speed or the slow decay of fluorescence.
@@
 signal processing filters in order to remove noise due to light scattering
-effects, account for fluorescence  low decay and reduce the importance of
+effects, to account for fluorescence  low decay and to reduce the importance of
 global high activity in the network. The overall process is illustrated in
@@
 fluorescence signal is very noisy due to light scattering artifacts that
-ordinarily affect the quality of the recording~\citep{lichtman2011big}.
+usually affect the quality of the recording~\citep{lichtman2011big}.
 Accordingly, the first step of our pipeline is to smoothen the signal, using
@@
 global activity (measured by $\sum_{j} x^{t}_j$), as observed for instance
-around $t=4\text{s}$ in the figure. Note that the particular case where there
+around $t=4\text{s}$ in Figure~\ref{fig:weight_curve}. Note that the particular case where there
 is no activity, i.e., $\sum_{j} x^{t}_j = 0$, is solved by setting $w(x^{t}_i)
@@
 
-Finally, let us remark that performance of our simple method shows to
+Finally, let us note that the performance of our simple method appears to
 be quite sensitive to the values of parameters (e.g., $f_1$ or $f_2$
@@
 fluorescence time series of length $T=179500$. All inference methods compared
-here provide a ranking of all pairs of neurons according to some association
-ssociation
-score. To assess the quality of this ranking, we compute both ROC and
+here provide a ranking of all pairs of neurons according to some association score. To assess the quality of this ranking, we compute both ROC and
 precision-recall curves against the ground truth network, which are summarized
 using the area under the curve and respectively  denoted AUROC and AUPRC. Only
-the AUROC score was used to rank the challenge participants but the precision-
-recall curve has been shown to be a more sensible metric for network
+the AUROC score was used to rank the challenge participants but the precision-recall curve has been shown to be a more sensible metric for network
 inference, especially when network density is small (see e.g.,
@@
 
-\begin{table}[t]\label{tab:comparison}
+\begin{table}[t]
 %\caption{Evaluation of different methods on the four \textit{normal} datasets\label{tab:comparison}}
@@
 Bottom: Performance on \textit{normal-1,2,3,4} with different methods.}
+\label{tab:comparison}
 \end{table}
@@
 In this paper, we outlined a simple but efficient methodology for the problem
-of connectome inference from calcium imaging data. Our approach is made of two
+of connectome inference from calcium imaging data. Our approach consists of two
 steps: (i) processing fluorescence data to detect neural peak activities and
 (ii) inferring the degree of association between neurons from partial
-correlation statistics. Its simplified variant shows to outperform other
+correlation statistics. Its simplified variant outperforms other
 network inference methods while its optimized version proved to be the best method
 on the Connectomics challenge. Given its simplicity and good performance, we
-therefore believe that the (simplified) methodology presented in this work
+therefore believe that the methodology presented in this work
 would constitute a solid and easily reproducible baseline for further work in
@@
 The pre-processed time-series are then obtained by the application of the
-following function: $w^*\circ p \circ h \circ g \circ f_i$ (with $i=1$,2,3, or 4)
+following function: $w^*\circ p \circ h \circ g \circ f_i$ (with $i=1$,2,3, or 4).
 

### 2014-06-28 article.tex
AQ : minor changes in appendix

@@
 
-In Section~\ref{sec:filter}, we introduce four filtering functions ($f$, $g$,
+In Section~\ref{sec:filter}, we introduced four filtering functions ($f$, $g$,
 $h$, and $w$) that are composed in sequence (i.e., $w \circ h \circ g \circ
@@
 \begin{align}
-p(x^t_i) = (x_i^t)^c,
+r(x^t_i) = (x_i^t)^c,
 \end{align}
@@
 The pre-processed time-series are then obtained by the application of the
-following function: $w^*\circ p \circ h \circ g \circ f_i$ (with $i=1$,2,3, or 4).
+following function: $w^*\circ r \circ h \circ g \circ f_i$ (with $i=1$,2,3, or 4).
 
@@
 $s_{i,j}$ is lower than $s_{j,i}$ ($j\rightarrow i$). To address these issues,
-we computed a differential pairwise coefficient $z_{ij}$ defined as follows:
+we computed a differential pairwise coefficient $z_{i,j}$ defined as follows:
 \begin{align}
-z_{ij} = \sum_{t=1}^{T - 1}
+z_{i,j} = \sum_{t=1}^{T - 1}
     \mathbb{1}((x_j^{t+1} - x_i^t) \in \left[\phi_1, \phi_2 \right]) -
@@
 \textcolor{red}{PG: je ne comprends pas ce qui est fait exactement. Mettre les
-  maths? Valeurs de $\phi_1$ et $\phi_2$ ?} At the light of the poor results of this heuristic taken on its own
-(on Table \ref{tab:directivity} in Section~\ref{sapp:results}) as
-\textit{directivity}, we use it to make asymmetric the degree of association
+  maths? Valeurs de $\phi_1$ et $\phi_2$ ?} At the light of the poor results of this heuristic taken on its own as
+\textit{directivity} 
+(on Table \ref{tab:directivity} in Section~\ref{sapp:results}), we use it to asymmetrize the degree of association
 matrix using partial correlation statistics. We expect that when the heuristic

### 2014-06-28 article.tex
Modifications of DE and VF (in particular: new pr/roc curves)

@@
 organ made of 100 billions of neurons, each connected to 7000 other neurons on
-average. Unfortunately, direct observations of the connectome, the wiring
+average. Unfortunately, direct observation of the connectome, the wiring
 diagram of the brain, is not yet technically feasible. Without being perfect,
@@
 representing their fluorescence intensity. From these data, the connectome
-inference problem consists in retrieving the synaptic connections between
-neurons on the basis of the fluorescence time series. However, this
+inference problem amounts in retrieving the synaptic connections between
+neurons on the basis of the fluorescence time series. This
 problem is often difficult because of experimental issues, including
@@
 % symmetrical median filter
-f_1(x^t_i) &= x^{t-1}_i + x^t_i + x^{t+1}_i \label{eq:symetric-median}, \\
+f_1(x^t_i) &= x^{t-1}_i + x^t_i + x^{t+1}_i\quad, \label{eq:symetric-median} \\
 % asymmetrical weighted median
-f_2(x^t_i) &= 0.4 x^{t-3}_i + 0.6 x^{t-2}_i + 0.8 x^{t-1}_i + x_i^t.
+f_2(x^t_i) &= 0.4 x^{t-3}_i + 0.6 x^{t-2}_i + 0.8 x^{t-1}_i + x_i^t\quad.
 \label{eq:weighted-asymetric-median}
@@
 \begin{align}
-g(x^{t}_{i}) &= x^{t}_i - x^{t-1}_i \label{eq:high-pass-filter},
+g(x^{t}_{i}) &= x^{t}_i - x^{t-1}_i\quad, \label{eq:high-pass-filter}
 \end{align}
@@
 \begin{align}\label{eqn:hfilter}
-h(x^{t}_i) &= x^{t}_i \mathbb{1}(x^{t}_i \geq \tau) \text{ with } \tau > 0,
+h(x^{t}_i) &= x^{t}_i \mathbb{1}(x^{t}_i \geq \tau) \text{ with } \tau > 0\quad,
 \end{align}
@@
 \end{align}
-which effect is to magnify the importance of spikes that occur in case of low
+whose effect is to magnify the importance of spikes that occur in case of low
 global activity (measured by $\sum_{j} x^{t}_j$), as observed for instance
@@
 p_{i,j} =
--\frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii} \Sigma^{-1}_{jj}}}, \label{eq:inverse}
+-\frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii} \Sigma^{-1}_{jj}}}\quad, \label{eq:inverse}
 \end{equation}
@@
 \setminus\{X_i,X_j\}$. Partial correlation thus measures conditional
-dependencies between variables. As an association measure between
-neurons, it should thus naturally only detect direct associations
+dependencies between variables. It should thus naturally only detect direct associations
 between neurons and filter out spurious indirect effects. The interest
@@
 Finally, let us note that the performance of our simple method appears to
-be quite sensitive to the values of parameters (e.g., $f_1$ or $f_2$
+be quite sensitive to the values of parameters (e.g., choice of $f_1$ or $f_2$
 or the value of the threshold $\tau$) in the combined function of the
@@
 average from 0.77 to 0.93. PCA does not really affect AUROC scores but
-it improves significantly AUPRC scores. Taking the average over
-various parameter setting gives an improvement of 10\% in AUPRC but
+it significantly improves AUPRC scores. Taking the average over
+various parameter settings gives an improvement of 10\% in AUPRC but
 only a minor change in AUROC. The last row (``Full method'') shows the
@@
 severely affects the performance of this method with respect to the use of
-fully grown trees. PC and GENIE3 were applied on the time series filtered using
-respectively the functions $w\circ h\circ g$ and $h\circ g\circ f_1$ (which
-gave the best performance). For GENIE3, we built 10000 trees per neuron and we
+fully grown trees. PC and GENIE3 were applied on the time series filtered using the functions $w\circ h\circ g$ and $h\circ g\circ f_1$ (which
+gave the best performance), respectively. For GENIE3, we built 10000 trees per neuron and we
 used default settings for all other parameters (except for the maximal tree
 depth). For GTE, we reproduced the exact same setting (conditioning level and
-pre-processing) that was used by the challenge organizers.
+pre-processing) that was used by the organizers of the challenge.
 
@@
 challenge. Although the tuned method performs better than the simplified one on
-the challenge dataset and this tuning was probably decisive to get the best
-performance, we believe that the tuned method clearly overfits the
+the challenge dataset, we believe that the tuned method clearly overfits the
 simulator used to generate the challenge data and that the simplified method
@@
 \begin{align}
-f_3(x^t_i) &= x^{t-1}_i + x^{t}_i + x^{t+1}_i + x^{t+2}_i, \label{eq:asymetric-median-forward} \\
-f_4(x^t_i) &=  x_i^t + x^{t+1}_i  + x^{t+2}_i + x^{t+3}_i. \label{eq:asymetric-median}.
+f_3(x^t_i) &= x^{t-1}_i + x^{t}_i + x^{t+1}_i + x^{t+2}_i\quad, \label{eq:asymetric-median-forward} \\
+f_4(x^t_i) &=  x_i^t + x^{t+1}_i  + x^{t+2}_i + x^{t+3}_i\quad. \label{eq:asymetric-median}
 \end{align}
@@
 \begin{align}
-r(x^t_i) = (x_i^t)^c,
+r(x^t_i) = (x_i^t)^c\quad,
 \end{align}
@@
 The pre-processed time-series are then obtained by the application of the
-following function: $w^*\circ r \circ h \circ g \circ f_i$ (with $i=1$,2,3, or 4).
+following function: $w^*\circ r \circ h \circ g \circ f_i$ (with $i=1$, 2, 3, or 4).
 
@@
 %\caption{Evaluation of different methods on the four \textit{normal} datasets\label{tab:comparison}}
-\caption{Performance on \textit{normal-1,2,3,4} with partial correlation with different averaging approaches.}
+\caption{Performance on \textit{normal-1, 2, 3, or 4} with partial correlation with different averaging approaches.}
 \label{tab:f3f4}
@@
 \begin{description}
-\item[lowcon]: Similar network but with a lower number of connections per neuron on average.
-\item[highcon]: Similar network but with a higher number of connections per neuron on average.
-\item[lowcc]: Similar network but with a lower clustering coefficient on average.
-\item[highcc]: Similar network but with a higher clustering coefficient on average.
-\item[normal-3-highrate]: Same topology as \textit{normal-3} but with a higher firing frequency, i.e., with highly active neurons.
-\item[normal-4-lownoise]: Same topology as \textit{normal-4} but with a better signal to noise ratio.
+\item[lowcon:] Similar network but with a lower number of connections per neuron on average.
+\item[highcon:] Similar network but with a higher number of connections per neuron on average.
+\item[lowcc:] Similar network but with a lower clustering coefficient on average.
+\item[highcc:] Similar network but with a higher clustering coefficient on average.
+\item[normal-3-highrate:] Same topology as \textit{normal-3} but with a higher firing frequency, i.e., with highly active neurons.
+\item[normal-4-lownoise:] Same topology as \textit{normal-4} but with a better signal to noise ratio.
 \end{description}

### 2014-06-28 article.tex
fix authors

@@
 
-  \author{\Name{Antonio Sutera} ,
+  \author{\Name{Antonio Sutera},
    \Name{Arnaud Joly},
@@
 %\caption{Evaluation of different methods on the four \textit{normal} datasets\label{tab:comparison}}
+\caption{Top: Performance on \textit{normal-1,2,3,4} with partial correlation and different filtering functions.
+Bottom: Performance on \textit{normal-1,2,3,4} with different methods.}
+\label{tab:comparison}
 \centering
@@
 \end{tabular}
-\caption{Top: Performance on \textit{normal-1,2,3,4} with partial correlation and different filtering functions.
-Bottom: Performance on \textit{normal-1,2,3,4} with different methods.}
-\label{tab:comparison}
+
 \end{table}
@@
 varying $\tau$ linearly from $0.100$ to $0.209$ (in step of $0.001)$ and by
-varying the low-pass filter in $\{f_1, f_2, f_3, f_4\}$. Unlike in the
+varying the low-pass filter in $\{f_1, f_2, f_3, f_4\}$.
+
+\textit{Unlike in the
 simplified method where each filter $f_1$ and $f_2$ were given equal weight in
@@
 according to its individual performance on the \textit{normal-1}
-dataset. \textcolor{red}{PG: je ne suis pas s\^ur de comprendre comment ces
+dataset.} 
+\textcolor{red}{PG: je ne suis pas s\^ur de comprendre comment ces
   poids sont d\'etermin\'es}
+$\Rightarrow$
 

### 2014-06-28 article.tex
typos

@@
 representing their fluorescence intensity. From these data, the connectome
-inference problem amounts in retrieving the synaptic connections between
+inference problem amounts to retrieving the synaptic connections between
 neurons on the basis of the fluorescence time series. This
@@
 
-We report in this apprendix the performance of the different methods compared
+We report in this appendix the performance of the different methods compared
 in the paper on 6 additional datasets provided by the challenge

### 2014-06-28 article.tex
typos

@@
 frequency, while low frequencies of the signal mainly correspond to the slow
-decay of fluorescence. To have a signal that only has high magnitudes around instances where the spikes occur, the second step of our pipeline transforms the time series into its backward
+decay of fluorescence. To have a signal that only has high magnitude around instances where the spikes occur, the second step of our pipeline transforms the time series into its backward
 difference
@@
 directed relationship if both neurons are activated simultaneously at the same
-time step, ie., when the delay between the two activations is below the time
+time step, i.e., when the delay between the two activations is below the time
 resolution. Second, one needs to compare $s_{j,i}$ and $s_{i,j}$ to decide on

### 2014-06-29 article.tex
Section A.2 rewritten

--- 2014-06-28 article.tex
@@
 
-\textit{Unlike in the
-simplified method where each filter $f_1$ and $f_2$ were given equal weight in
-the averaging, in the tuned method, we weighted each of the four filters
-according to its individual performance on the \textit{normal-1}
-dataset.} 
-\textcolor{red}{PG: je ne suis pas s\^ur de comprendre comment ces
-  poids sont d\'etermin\'es}
-$\Rightarrow$
+Filters $f_1$ and $f_2$ display similar performances and thus were given equal weight in the averaging of the simplified method.
+Otherwise, filters $f_3$ and $f_4$ turn out to be, individually, less competitive to provide the signal to compute partial correlation statistics and thus were given smaller weights in the tuned averaging.
+In this way, composed functions with $f_3$ or $f_4$ (resp. $f_1$ or $f_2$) contribute less (resp. more) in the tuned averaging.
 

### 2014-06-29 article.tex

--- 2014-06-28 article.tex
@@
 
-\textit{Unlike in the
-simplified method where each filter $f_1$ and $f_2$ were given equal weight in
-the averaging, in the tuned method, we weighted each of the four filters
-according to its individual performance on the \textit{normal-1}
-dataset.}
-\textcolor{red}{PG: je ne suis pas s\^ur de comprendre comment ces
-  poids sont d\'etermin\'es}
-$\Rightarrow$
+Filters $f_1$ and $f_2$ display similar performances and thus were given equal weight in the averaging of the simplified method.
+Otherwise, filters $f_3$ and $f_4$ turn out to be, individually, less competitive to provide the signal to compute partial correlation statistics and thus were given smaller weights in the tuned averaging.
+In this way, composed functions with $f_3$ or $f_4$ (resp. $f_1$ or $f_2$) contribute less (resp. more) in the tuned averaging.
 

### 2014-06-29 article.tex
add values for phi1 and phi2
Section A.3 rewritten

@@
 \end{align}
-where $\phi_1$ and $\phi_2$ are parameters of the heuristic.
+where $\phi_1$ and $\phi_2$ are parameters of the heuristic (with $\phi_1 = 0.2$ and $\phi_2 = 0.5$ in our experiments).
 
@@
 where $T$ is the number of time steps, $\phi_1$ and $\phi_2$ are parameters.
-
-\textcolor{red}{PG: je ne comprends pas ce qui est fait exactement. Mettre les
-  maths? Valeurs de $\phi_1$ et $\phi_2$ ?} At the light of the poor results of this heuristic taken on its own as
-\textit{directivity}
-(on Table \ref{tab:directivity} in Section~\ref{sapp:results}), we use it to asymmetrize the degree of association
-matrix using partial correlation statistics. We expect that when the heuristic
-is highly confident (i.e., $z_{i,j} \gg 0 \gg z_{j,i}$) the degree of
-association of edge $(i,j)$ is increased while the degree of association
-corresponding to the edge $(j,i)$ is reduced. Even if this adjustment is
-subtle, it might have a slight positive effect on the ROC AUC.
+The coefficient $z_{i,j}$ estimates the confidence in an edge $i\rightarrow j$.
+Note that if $z_{i,j}$ is positive, then $z_{j,i}$ will be negative.
+
+This heuristic does not give good results on its own (see Table \ref{tab:directivity} in Section~\ref{sapp:results}).
+However, it can be used to asymmetrize the degree of association (symmetric) matrix given by partial correlation statistics.
+Concretely, a new matrix is computed as the linear combination of the partial correlation matrix and the heuristic matrix.
+Mathematically, we have
+\begin{align}
+q_{i,j} = weight_p * p_{i,j} + weight_z * z_{i,j}
+\end{align}
+where $weight_p$ and $weight_z$ are parameters of the method (with $weight_p = 0.997$ and $weight_z = 0.003$ in our experiments).
+
+Considering the small weight associated to this heuristic, the effect is subtle.
+It slightly increases the confidence in one edge direction and decreases the confidence in the opposite edge direction while not affecting strongly the undirected topology of the network.
+This process slightly improves the performance of our method (see Table \ref{tab:directivity} in Section~\ref{sapp:results}).
 

### 2014-06-29 article.tex
wordings

@@
 % symmetrical median filter
-f_1(x^t_i) &= x^{t-1}_i + x^t_i + x^{t+1}_i\quad, \label{eq:symetric-median} \\
+f_1(x^t_i) &= x^{t-1}_i + x^t_i + x^{t+1}_i, \label{eq:symetric-median} \\
 % asymmetrical weighted median
-f_2(x^t_i) &= 0.4 x^{t-3}_i + 0.6 x^{t-2}_i + 0.8 x^{t-1}_i + x_i^t\quad.
+f_2(x^t_i) &= 0.4 x^{t-3}_i + 0.6 x^{t-2}_i + 0.8 x^{t-1}_i + x_i^t.
 \label{eq:weighted-asymetric-median}
@@
 \begin{align}
-g(x^{t}_{i}) &= x^{t}_i - x^{t-1}_i\quad, \label{eq:high-pass-filter}
+g(x^{t}_{i}) &= x^{t}_i - x^{t-1}_i, \label{eq:high-pass-filter}
 \end{align}
@@
 \begin{align}\label{eqn:hfilter}
-h(x^{t}_i) &= x^{t}_i \mathbb{1}(x^{t}_i \geq \tau) \text{ with } \tau > 0\quad,
+h(x^{t}_i) &= x^{t}_i \mathbb{1}(x^{t}_i \geq \tau) \text{ with } \tau > 0,
 \end{align}
@@
 p_{i,j} =
--\frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii} \Sigma^{-1}_{jj}}}\quad, \label{eq:inverse}
+-\frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii} \Sigma^{-1}_{jj}}}, \label{eq:inverse}
 \end{equation}
@@
 This section provides a detailed description of the method specifically tuned
-for the Connectomics challenge. We will restrict our description to the
+for the Connectomics challenge. We restrict our description to the
 differences with respect to the simplified method presented in the main
@@
 f$) to provide the signals from which to compute partial correlation
-statistics.
-
-Filtering is modified as follows in the tuned method:
+statistics. Filtering is modified as follows in the tuned method:
+
 \begin{itemize}
@@
 \begin{align}
-f_3(x^t_i) &= x^{t-1}_i + x^{t}_i + x^{t+1}_i + x^{t+2}_i\quad, \label{eq:asymetric-median-forward} \\
-f_4(x^t_i) &=  x_i^t + x^{t+1}_i  + x^{t+2}_i + x^{t+3}_i\quad. \label{eq:asymetric-median}
+f_3(x^t_i) &= x^{t-1}_i + x^{t}_i + x^{t+1}_i + x^{t+2}_i, \label{eq:asymetric-median-forward} \\
+f_4(x^t_i) &=  x_i^t + x^{t+1}_i  + x^{t+2}_i + x^{t+3}_i. \label{eq:asymetric-median}
 \end{align}
-\item An additional filter $p$ is applied to smoothen differences in peak magnitudes
+\item An additional filter $r$ is applied to smoothen differences in peak magnitudes
   that might remain after the application of the hard-threshold filter $h$:
 \begin{align}
-r(x^t_i) = (x_i^t)^c\quad,
+r(x^t_i) = (x_i^t)^c,
 \end{align}
@@
 
-Filters $f_1$ and $f_2$ display similar performances and thus were given equal weight in the averaging of the simplified method.
-Otherwise, filters $f_3$ and $f_4$ turn out to be, individually, less competitive to provide the signal to compute partial correlation statistics and thus were given smaller weights in the tuned averaging.
-In this way, composed functions with $f_3$ or $f_4$ (resp. $f_1$ or $f_2$) contribute less (resp. more) in the tuned averaging.
+Filters $f_1$ and $f_2$ display similar performances and thus were given equal
+weight in the averaging of the simplified method. In contrast, filters $f_3$
+and $f_4$ turn out to be individually less competitive and were therefore given
+smaller weights in the tuned averaging. Yet, as further shown in
+Section~\ref{sapp:results}, combining all $4$ filters proves to slightly
+improve performance with respect to using $f_1$ and $f_2$ only.
 
@@
 \begin{align}
-z_{i,j} = \sum_{t=1}^{T - 1}
-    \mathbb{1}((x_j^{t+1} - x_i^t) \in \left[\phi_1, \phi_2 \right]) -
-    \mathbb{1}((x_i^{t+1} - x_j^t) \in \left[\phi_1, \phi_2 \right]),
+z_{i,j} = s_{i,j} - s_{j,i}.
 \end{align}
-where $T$ is the number of time steps, $\phi_1$ and $\phi_2$ are parameters.
-The coefficient $z_{i,j}$ estimates the confidence in an edge $i\rightarrow j$.
-Note that if $z_{i,j}$ is positive, then $z_{j,i}$ will be negative.
+The coefficient $z_{i,j}$ estimates the confidence in an edge $i\rightarrow j$. Note that if $z_{i,j}$ is positive, then $z_{j,i}$ will be negative.
 
@@
 GTE & 0.846 & 0.905 & 0.848 & 0.899 & 0.905 & 0.879\\
-GENIE3 & 0.781 &  0.922 & 0.875 & 0.899 & 0.886 &  0.890 \\ \hline
+GENIE3 & 0.781 &  0.922 & 0.875 & 0.899 & 0.886 &  0.890 \\ \hline \hline
 & \multicolumn{6}{c|}{AUPRC}\\ \hline

### 2014-06-29 article.tex
proposition de damien pour la A3

@@
 hard-threshold filter $h$ (see Equation \ref{eqn:hfilter}), and to the choice
-of the low-pass filter (among $\{f_1, f_2, f_3, f_4\}$). Like in the simplified
-method, we therefore averaged the partial correlation statistics obtained by
-varying $\tau$ linearly from $0.100$ to $0.209$ (in step of $0.001)$ and by
-varying the low-pass filter in $\{f_1, f_2, f_3, f_4\}$.
+of the low-pass filter (among $\{f_1, f_2, f_3, f_4\}$).
+Like in the simplified method, we have averaged the partial correlation statistics obtained for all the pairs $(\tau,\mbox{low-pass filter}) \in \{0.100,0.101,\ldots,0.209\}\times \{f_1, f_2, f_3, f_4\}$.
 
 Filters $f_1$ and $f_2$ display similar performances and thus were given equal
-weight in the averaging of the simplified method. In contrast, filters $f_3$
+weight. Additionally, this weight were chosen equal as the weight selected for the simplified method. In contrast, filters $f_3$
 and $f_4$ turn out to be individually less competitive and were therefore given
@@
 
-Partial correlation statistics is a symmetric measure, while the connectome is
-a directed graph. It could thus be beneficial to try to predict edge orientation. In
-this section, we present a heuristic to retrieve directionality. %% Note however that
-%% given the discussion at the end of Section~\ref{sec:results}, we cannot expect
-%% a very large improvement in AUROC by predicting edge orientation.
-
-This heuristic is based on the following observation. The rise of fluorescence
-of a neuron indicates its activation. If another neuron is activated after a
-slight delay, this could be a consequence of the activation of the first neuron
-and therefore indicate a directed link in the connectome from the first to the
-second neuron. Given this analysis, the idea of our heuristic is to count the
-number of such events occurring between neurons $i$ and $j$ for consecutive
-time steps. Mathematically, we compute for each pair $(i,j)$:
+Partial  correlation  statistics is  a  symmetric  measure, while  the
+connectome is a directed graph. It  could thus be beneficial to try to
+predict edge orientation. In this section, we present a heuristic that
+modifies the  $p_{ij}$ computed  by the  approach described  before to
+take into account directionality.
+
+This approach is based on the following
+observation. The rise of fluorescence of a neuron indicates its
+activation. If another neuron is activated after a slight delay, this
+could be a consequence of the activation of the first neuron and
+therefore indicates a directed link in the connectome from the first to
+the second neuron.  Given this observation, we have computed for every
+pair $(i,j)$ an empirical estimation of the  term:
 \begin{align}
-s_{i,j} = \sum_{t=1}^{T - 1} \mathbb{1}((x_j^{t+1} - x_i^t) \in \left[\phi_1, \phi_2\right])
+s_{i,j} = \sum_x \sum_{t=1}^{T - 1} \mathbb{1}((x_j^{t+1} - x_i^t) \in \left[\phi_1, \phi_2\right])
 \end{align}
-where $\phi_1$ and $\phi_2$ are parameters of the heuristic (with $\phi_1 = 0.2$ and $\phi_2 = 0.5$ in our experiments).
-
-Two issues remain with this heuristic. First, it does not allow to detect a
-directed relationship if both neurons are activated simultaneously at the same
-time step, i.e., when the delay between the two activations is below the time
-resolution. Second, one needs to compare $s_{j,i}$ and $s_{i,j}$ to decide on
-edge orientation. Indeed, edge orientation can only be predicted with some
-confidence if either $s_{i,j}$ is greater than $s_{j,i}$ ($i\rightarrow j$) or
-$s_{i,j}$ is lower than $s_{j,i}$ ($j\rightarrow i$). To address these issues,
-we computed a differential pairwise coefficient $z_{i,j}$ defined as follows:
+that could be interpreted as an image of the  number of times
+that neuron $i$ activates neuron $j$. $\phi_1$ and $\phi_2$ are
+parameters whose values have been chosen in our experiments equal to   
+$0.2$ and $0.5$, respectively. Their role is
+define when the difference between $x_j^{t+1}$  and $x_i^t$ can
+indeed be assimilated to an event where neuron $i$ activates neuron
+$j$.
+
+Afterwards, we have computed the difference between $s_{i,j}$ and
+$s_{j,i}$, that we call $z_{i,j}$, and used this difference to modify  $p_{i,j}$ and
+$p_{i,j}$ so as to take into account directionality. Naturally, îf
+$z_{i,j}$ is greater  (smaller) than $0$, we may conclude that should there  be an
+edge between $i$ and $j$, then this edge would have to be oriented
+from $i$ to $j$ ($j$ to $i$).
+
+This suggests the the new association matrix $r$:
 \begin{align}
-z_{i,j} = s_{i,j} - s_{j,i}.
+r_{i,j} =  \mathbb{1}(z_{i,j} > \phi_3)    p_{i,j}
 \end{align}
-The coefficient $z_{i,j}$ estimates the confidence in an edge $i\rightarrow j$. Note that if $z_{i,j}$ is positive, then $z_{j,i}$ will be negative.
-
-This heuristic does not give good results on its own (see Table \ref{tab:directivity} in Section~\ref{sapp:results}).
-However, it can be used to asymmetrize the degree of association (symmetric) matrix given by partial correlation statistics.
-Concretely, a new matrix is computed as the linear combination of the partial correlation matrix and the heuristic matrix.
-Mathematically, we have
+where $\phi_3 >0$ is another parameter. We found out that this new
+matrix $r$ was not giving good results, probably due to the fact that
+directivity was not well enough rewarded in the challenge.
+
+This has lead us to investigate other ways for exploiting the
+information about directionality contained in the matrix $z$. One of
+those ways that gave good performance was to use as association
+matrix: 
 \begin{align}
-q_{i,j} = weight_p * p_{i,j} + weight_z * z_{i,j}
+q_{i,j} = weight * p_{i,j} + (1-weight) * z_{i,j}
 \end{align}
-where $weight_p$ and $weight_z$ are parameters of the method (with $weight_p = 0.997$ and $weight_z = 0.003$ in our experiments).
-
-Considering the small weight associated to this heuristic, the effect is subtle.
-It slightly increases the confidence in one edge direction and decreases the confidence in the opposite edge direction while not affecting strongly the undirected topology of the network.
-This process slightly improves the performance of our method (see Table \ref{tab:directivity} in Section~\ref{sapp:results}).
+with  $weight$ chosen close to 1 ($weight=0.997$). Note that with
+values for $weight$ close to 1,   matrix $q$ only slightly uses the
+information about directivity contained in $z$ to modify the  partial
+correlation matrix $p$. We tried smaller values for $weight$ but those
+were leading to worse results.
+
+It was  this association matrix $q_{i,j}$ that actually led to the
+best results of the challenge, as shown in Table \ref{tab:directivity}
+of Section~\ref{sapp:results}.
 

### 2014-06-29 article.tex
typo

@@
 $s_{j,i}$, that we call $z_{i,j}$, and used this difference to modify  $p_{i,j}$ and
-$p_{i,j}$ so as to take into account directionality. Naturally, îf
+$p_{i,j}$ so as to take into account directionality. Naturally, if
 $z_{i,j}$ is greater  (smaller) than $0$, we may conclude that should there  be an

### 2014-06-29 article.tex
small modifs from DE

@@
 provides a detailed presentation of the averaging
-approach. Section~\ref{sapp:connectome} presents a heuristic to retrieve edge
+approach. Section~\ref{sapp:connectome} presents an approach to retrieve edge
 directionality. Finally, Section~\ref{sapp:results} presents some experimental
@@
 parameters whose values have been chosen in our experiments equal to   
-$0.2$ and $0.5$, respectively. Their role is
+$0.2$ and $0.5$, respectively. Their role is to 
 define when the difference between $x_j^{t+1}$  and $x_i^t$ can

### 2014-06-29 article.tex
DE : typo
DE: typo
DE: fix eq
de: space too much
check value GENIE3

@@
 the second neuron.  Given this observation, we have computed for every
-pair $(i,j)$ an empirical estimation of the  term:
+pair $(i,j)$ the term:
 \begin{align}
-s_{i,j} = \sum_x \sum_{t=1}^{T - 1} \mathbb{1}((x_j^{t+1} - x_i^t) \in \left[\phi_1, \phi_2\right])
+s_{i,j} = \sum_{t=1}^{T - 1} \mathbb{1}((x_j^{t+1} - x_i^t) \in \left[\phi_1, \phi_2\right])
 \end{align}
@@
 
-This suggests the the new association matrix $r$:
+This suggests the new association matrix $r$:
 \begin{align}
-r_{i,j} =  \mathbb{1}(z_{i,j} > \phi_3)    p_{i,j}
+r_{i,j} =  \mathbb{1}(z_{i,j} > \phi_3)  *  p_{i,j}
 \end{align}
@@
 GTE & 0.846 & 0.905 & 0.848 & 0.899 & 0.905 & 0.879\\
-GENIE3 & 0.781 &  0.922 & 0.875 & 0.899 & 0.886 &  0.890 \\ \hline \hline
+GENIE3 & 0.781 &  0.924 & 0.879 & 0.902 & 0.886 &  0.890 \\ \hline \hline
 & \multicolumn{6}{c|}{AUPRC}\\ \hline
@@
 GTE & 0.094 & 0.211 & 0.081 & 0.165 & 0.210 & 0.144\\
-GENIE3 & 0.128 & 0.261 & 0.108 & 0.293 & 0.256 & 0.224\\ \hline
+GENIE3 & 0.128 & 0.273 & 0.116 & 0.309 & 0.256 & 0.224\\ \hline
 \end{tabular}

### 2014-06-29 article.tex
I think this is a typo

@@
 $s_{j,i}$, that we call $z_{i,j}$, and used this difference to modify  $p_{i,j}$ and
-$p_{i,j}$ so as to take into account directionality. Naturally, if
+$p_{j,i}$ so as to take into account directionality. Naturally, if
 $z_{i,j}$ is greater  (smaller) than $0$, we may conclude that should there  be an

### 2014-06-29 article.tex
add missing values for full method in Appendix

@@
 Averaging     & 0.947 & 0.943 & 0.920 & 0.942 & 0.959 & 0.934 \\
-Full method   &  &  &  & & &\\
+Full method   & 0.955 & 0.944 &  0.925 & 0.946 & 0.961 & 0.941 \\
 PC & 0.782 & 0.920 &  0.846 & 0.897  & 0.898  & 0.873 \\
@@
 Averaging     & 0.320 & 0.429 & 0.262 & 0.478 & 0.443 & 0.412 \\
-Full method   &  &  &  & & &\\
+Full method   & 0.334 & 0.413 &  0.260 & 0.486 & 0.452 & 0.432\\
 PC & 0.074 & 0.218 & 0.082 & 0.165  & 0.193 & 0.135 \\

### 2014-06-30 article.tex
with weight values for section A.2

@@
 
-This appendix is structured as follows: Section~\ref{sapp:signal} describes the
-differences in terms of signal processing. Section~\ref{sapp:averaging} then
-provides a detailed presentation of the averaging
-approach. Section~\ref{sapp:connectome} presents an approach to retrieve edge
-directionality. Finally, Section~\ref{sapp:results} presents some experimental
-results to validate the different steps of our proposal.
+This appendix is structured as follows: Section~\ref{sapp:signal} describes
+the differences in terms of signal processing. Section~\ref{sapp:averaging}
+then provides a detailed presentation of the averaging approach.
+Section~\ref{sapp:connectome} presents an approach to correct the $p_{i,j}$
+values so as to take into account the edge directionality. Finally,
+Section~\ref{sapp:results} presents some experimental results to validate the
+different steps of our proposal.
 
@@
 
-Filters $f_1$ and $f_2$ display similar performances and thus were given equal
-weight. Additionally, this weight were chosen equal as the weight selected for the simplified method. In contrast, filters $f_3$
+Filters $f_1$ and $f_2$ display similar performances and thus were given similar
+weights (i.e., resp. $1$ and $0.9$). Additionally, these weights were chosen equal as the weights selected for the simplified method. In contrast, filters $f_3$
 and $f_4$ turn out to be individually less competitive and were therefore given
-smaller weights in the tuned averaging. Yet, as further shown in
+smaller weights in the tuned averaging (i.e., resp. $0.01$ and $0.7$). Yet, as further shown in
 Section~\ref{sapp:results}, combining all $4$ filters proves to slightly
@@
 define when the difference between $x_j^{t+1}$  and $x_i^t$ can
-indeed be assimilated to an event where neuron $i$ activates neuron
+indeed be assimilated to an event for which neuron $i$ activates neuron
 $j$.
@@
 q_{i,j} = weight * p_{i,j} + (1-weight) * z_{i,j}
+\label{eqn:qij}
 \end{align}
@@
 
-\paragraph{On the contribution of the directionality heuristic.}
-
-Table~\ref{tab:dir} compares AUROC and AUPRC with and without prediction
-of edge orientation. Both AUROC and AUPRC are (very slightly) improved by
-directing the edges.
+\paragraph{On the interest of using matrix $q$ rather than $p$ to take into account directivity.}
+
+Table~\ref{tab:dir} compares AUROC and AUPRC with or without correcting the $p_{i,j}$ values according to Equation \ref{eqn:qij}.
+Both AUROC and AUPRC are (very slightly) improved by using information about directivity.
 
@@
 \caption{Performance on \textit{normal-1,2,3,4} of ``Full Method'' with and
-  without prediction of edge orientation}
+  without using information about directivity.}
 \label{tab:directivity}
@@
 performs better than GTE most of the times.
+Note that the "Full method" reported in this table does not use Equation \ref{eqn:qij} to slightly correct the values of $p_{i,j}$  to take into account directivity.
 

### 2014-06-30 article.tex
normalized weights

@@
 Filters $f_1$ and $f_2$ display similar performances and thus were given similar
-weights (i.e., resp. $1$ and $0.9$). Additionally, these weights were chosen equal as the weights selected for the simplified method. In contrast, filters $f_3$
+weights (i.e., resp. $0.383$ and $0.345$). These weights were chosen equal as the weights selected for the simplified method. In contrast, filters $f_3$
 and $f_4$ turn out to be individually less competitive and were therefore given
-smaller weights in the tuned averaging (i.e., resp. $0.01$ and $0.7$). Yet, as further shown in
+smaller importance in the weighted average (i.e., resp. $0.004$ and $0.268$). Yet, as further shown in
 Section~\ref{sapp:results}, combining all $4$ filters proves to slightly

### 2014-06-30 article.tex
bold

@@
 Averaging     & 0.947 & 0.943 & 0.920 & 0.942 & 0.959 & 0.934 \\
-Full method   & 0.955 & 0.944 &  0.925 & 0.946 & 0.961 & 0.941 \\
+Full method   & \textbf{0.955} & \textbf{0.944} &  \textbf{0.925} & \textbf{0.946} & \textbf{0.961} & \textbf{0.941} \\
 PC & 0.782 & 0.920 &  0.846 & 0.897  & 0.898  & 0.873 \\
@@
 Averaging     & 0.320 & 0.429 & 0.262 & 0.478 & 0.443 & 0.412 \\
-Full method   & 0.334 & 0.413 &  0.260 & 0.486 & 0.452 & 0.432\\
+Full method   & \textbf{0.334} & \textbf{0.413} &  \textbf{0.260} & \textbf{0.486} & \textbf{0.452} & \textbf{0.432}\\
 PC & 0.074 & 0.218 & 0.082 & 0.165  & 0.193 & 0.135 \\

### 2014-06-30 article.tex
typo
Add reference for results
fix merge misstake
more precise

@@
 final performance of the method specifically tuned for the challenge
-(see the Appendix \ref{app:optimized} for all details). Although this
+(see Appendix \ref{app:optimized} for all details). Although this
 tuning was decisive to obtain the best performance at the challenge,
@@
 
-Partial correlation and average partial correlation clearly outperform all
-other methods. The improvement is more important in terms of AUPRC than in
-terms of AUROC. As expected, Pearson correlation performs very poorly in terms
-of AUPRC. GTE and GENIE3 work much better but these two methods are
-nevertheless clearly below partial correlation. Among these two methods, GTE is
-slightly better in terms of AUROC, while GENIE3 is significantly better in
-terms of AUPRC. Given that we had to limit this latter method for computational
-reasons, these results are very promising and a comparison with the full GENIE3
-approach is certainly part of our future works.
+Partial correlation and averaged partial correlation clearly outperform all
+other methods on all datatests (see Table \ref{tab:comparison} and Appendix \ref{app:supp}). The
+improvement is more important in terms of AUPRC than in terms of AUROC. As
+expected, Pearson correlation performs very poorly in terms of AUPRC. GTE and
+GENIE3 work much better but these two methods are nevertheless clearly below
+partial correlation. Among these two methods, GTE is slightly better in terms
+of AUROC, while GENIE3 is significantly better in terms of AUPRC. Given that we
+had to limit this latter method for computational reasons, these results are
+very promising and a comparison with the full GENIE3 approach is certainly part
+of our future works.
 

### 2014-06-30 article.tex
typo

@@
 Partial correlation and averaged partial correlation clearly outperform all
-other methods on all datatests (see Table \ref{tab:comparison} and Appendix \ref{app:supp}). The
+other methods on all datasets (see Table \ref{tab:comparison} and Appendix \ref{app:supp}). The
 improvement is more important in terms of AUPRC than in terms of AUROC. As

### 2014-07-08 article.tex
small changes

@@
 \centering
-\subfigure[Raw signal]{\includegraphics[width=0.3\textwidth]{images/original_curve.pdf} \label{fig:original_curve}}
-\subfigure[Low-pass filter $f_1$]{\includegraphics[width=0.3\textwidth]{images/filter_curve.pdf} \label{fig:lp_curve}}
-\subfigure[High-pass filter $g$]{\includegraphics[width=0.3\textwidth]{images/diff_curve.pdf} \label{fig:hp_curve}}\\
-\subfigure[Hard-threshold filter $h$]{\includegraphics[width=0.3\textwidth]{images/threshold_curve.pdf} \label{fig:threshold_curve}}
-\subfigure[Global regularization $w$]{\includegraphics[width=0.3\textwidth]{images/weights_curve.pdf} \label{fig:weight_curve}}
+\subfigure[Raw signal]{\includegraphics[width=0.3\textwidth]{original_curve.pdf} \label{fig:original_curve}}
+\subfigure[Low-pass filter $f_1$]{\includegraphics[width=0.3\textwidth]{filter_curve.pdf} \label{fig:lp_curve}}
+\subfigure[High-pass filter $g$]{\includegraphics[width=0.3\textwidth]{diff_curve.pdf} \label{fig:hp_curve}}\\
+\subfigure[Hard-threshold filter $h$]{\includegraphics[width=0.3\textwidth]{threshold_curve.pdf} \label{fig:threshold_curve}}
+\subfigure[Global regularization $w$]{\includegraphics[width=0.3\textwidth]{weights_curve.pdf} \label{fig:weight_curve}}
 \caption{Signal processing pipeline for extracting peaks from the raw fluorescence data.}
@@
 \centering
-\subfigure[ROC curves]{\includegraphics[width=0.45\textwidth]{images/curve_roc} \label{fig:roc_curve}}
-\subfigure[Precision-recall curves]{\includegraphics[width=0.45\textwidth]{images/curve_pr} \label{fig:pr_curve}}
+\subfigure[ROC curves]{\includegraphics[width=0.45\textwidth]{curve_roc} \label{fig:roc_curve}}
+\subfigure[Precision-recall curves]{\includegraphics[width=0.45\textwidth]{curve_pr} \label{fig:pr_curve}}
 \caption{ROC (left) and PR (right) curves on \textit{normal-2} for the compared methods. Areas under the curves are reported in the legend.}
@@
 Filters $f_1$ and $f_2$ display similar performances and thus were given similar
-weights (i.e., resp. $0.383$ and $0.345$). These weights were chosen equal as the weights selected for the simplified method. In contrast, filters $f_3$
+weights (i.e., resp. $0.383$ and $0.345$). These weights were chosen equal to the weights selected for the simplified method. In contrast, filters $f_3$
 and $f_4$ turn out to be individually less competitive and were therefore given

### 2014-07-16 response.tex
changes after reviews

\documentclass[wcp]{jmlr}

\usepackage{enumerate}
\usepackage{bbold}
\usepackage{booktabs}
\usepackage{natbib}
\usepackage[utf8]{inputenc}

\jmlryear{2014}
\jmlrworkshop{Neural Connectomics Workshop}

\title{Simple connectome inference from partial correlation statistics in calcium imaging}

  \author{\Name{Antonio Sutera},
   \Name{Arnaud Joly},
   \Name{Vincent François-Lavet}, \Email{a.sutera@ulg.ac.be}\\
   \Name{Zixiao Aaron Qiu},
   \Name{Gilles Louppe},
   \Name{Damien Ernst}\and\Name{Pierre Geurts}
    \\
   \addr Department of EE and CS \& GIGA-R, University of Li\`ege, Belgium}

% \author{\Name{Antonio Sutera,
%     Arnaud Joly,
%         Vincent François-Lavet,\\
%         Aaron Qiu,
%         Gilles Louppe,
%         Damien Ernst,
%         Pierre Geurts}
%   \Email{a.sutera@ulg.ac.be}\\
%   \addr Department of EE and CS \& GIGA-R, University of Li\`ege, Belgium}

% \jmlrauthors{A. Sutera et al}
% \shortauthor{A. Sutera et al.}

\begin{document}

\maketitle
\begin{center}
\vspace{-1.5cm}
\today
\end{center}

We are grateful to the reviewers for reviewing our paper and we wish to thank them for providing us with helpful and constructive criticisms.
We have modified our paper to take into account as best possible the reviewers' advices and we believe that our paper will benefit from that review.

\section*{Reviewer 1:}
\textcolor{blue}{
Better justify use of specific low-pass filters. How these filters were designed? Is this standard in the signal processing field? Will these filters apply to other problems or they need fine-tuning?}

\textbf{A}: The first low-pass filter is standard in the signal processing field while the second is designed to take into account the time. This second filter is hovewever quite classical. We add justification and motivation in the paper.\\

\noindent
\textcolor{blue}{Is there sufficient sample and power to condition on all features excluding Xi and Xj when computing partial correlation coefficient?}

\textbf{A}: It is mentioned in the paper that there are enough samples to invert the covariance matrix. We have not done a statistical analysis in the scope of this work because we only use the partial correlation to rank pairs and therefore a statistical analysis is not really needed to make that ranking. However, it would be interesting to do it in future works.

\section*{Reviewer 2:}

\textcolor{blue}{It would be necessary to have information about the computational complexity, scalability, memory requirements, and execution time for these methods.}

\textbf{A}: We obviously agree with the reviewer that such informations are interesting, especially in the context of a challenge. We add a table with some interesting figures. However, let us note that the simple method presented in the paper already gives good performances despite its light computational needs.

We also would like to mention that our code is available publicly on \url{https://github.com/asutera/kaggle-connectomics} and that some verifications, including memory requirements and execution time, of the full method are displayed on the challenge website \url{http://connectomics.chalearn.org/home/challenge-results-verification}.\\

% \textcolor{blue}{- Soundness (good experiments, good proofs):  4\\}
\noindent
\textcolor{blue}{In section 4, PC, GTE, and GENIE3 are compared with other methods. Another worthwhile experiment would be to extract features using the procedure described by the authors, do a Principal Component Analysis(PCA), and then apply PC, etc. other methods.}

\textbf{A}: We are not sure what exactly suggests the reviewer but applying PCA before PC, GTE and GENIE3 is not straighforward. Let us note that for each method we choose the preprocessing which yields the best performance.\\

\noindent
\textcolor{blue}{The authors have also used an additional relevant metric the AUPR beyond the challenge.}

\textbf{A}: We thank the reviewer to note the interest of this second metric.\\

% - Clarity: 5. 
\noindent
\textcolor{blue}{The paper, in general, is well organized. A figure/flowchart describing the workflow would be good visualization.}

\textbf{A}: Because of the constraint on the number of pages (i.e., $6$), it is not really possible to include such a figure. But we agree the reviewer that such a figure would definitely improves the paper.\\

% - Novelty/originality/insight: 4. 
\noindent
\textcolor{blue}{The paper describes preprocessing and filtering of calcium fluorescence data followed by partial correlation to identify connections.  The authors adequately describe the intuition behind the several steps of filtering they have applied.  The techniques are not new. However, this approach yielded great results.}

\textbf{A}: We wish to thank the reviewer and we are happy that he or she points out that this approach yields great results.\\

\noindent
\textcolor{blue}{“The human brain is a complex……100 billion of neurons, each connected to 7000 other neurons on average” citation needed.\\
Section 2, equation 4, symbols in equation need to be described.}
%Arnaud?\\

\textbf{A}: Introduction (Section~1) and Section~2 have been modified accordingly.\\

\noindent
\textcolor{blue}{In section 3, M principal components are used. However, the choice of M = 0.8p is not justified.}

\textbf{A}: We agree with the reviewer that this choice is not justified in the paper. We have thus included in the appendix a justication of this specific value for the parameter $M$.

%In Appendix?\\

\section*{Reviewer 3:}

\textcolor{blue}{The authors have concisely and clearly summarized their algorithm that led them to win the Connectomics Challenge. This paper is critical as a detailed explication of the winning algorithm is very useful to anyone desiring to implement this method, which will no doubt include many workshop attendees.  I have only minor corrections regarding some of the background explanations as I think clarity on the source of the problems faced by this challenge is crucial.}

\textbf{A}: We wish to thank the reviewer for his or her judicious comments about the background explanations.\\

\noindent
\textcolor{blue}{Page 2, “signal is very noisy due to light scattering”  This is not entirely correct.  The signal is noisy due to many factors including but not limited to calcium fluctuations independent of spiking activity, calcium fluctuations in nearby tissues which may be erroneously included in the region of interest due to poor region selection or poor imaging resolution, fluorescence fluctuations independent of calcium, and imaging noise in general (shot noise, dark noise,  electrical noise in the acquisition/digitisation system, etc).}

\noindent
\textcolor{blue}{Page 2, “neurons communicate through short spikes, characterized by a high frequency, while low frequencies of the signal mainly correspond to the slow decay of fluorescence”  Neurons generate electrical ‘spikes’, or action potentials, which are indeed characterized by a high frequency. However, the sharp rise in the signal observed in the fluorescent calcium indicator traces is due to the sudden influx of calcium that enters the cell during the action potential.  The decay is due to the slow decay, as stated.  But neurons communicate via neurotransmitter released by an action potential at synapses between the neurons. The ‘short spikes’ observed in the fluorescent traces therefore only very indirectly indicate whether two ‘neurons communicate’.}

\textbf{A}: We agree and we have modified Section~2 accordingly to take into account these supplementary explanations.\\

\end{document}

### 2014-07-17 article.tex
add section in appendix about the value of parameter M

@@
 
+\vspace{-0.8cm}
 \begin{abstract}
@@
 The human brain is a complex biological
-organ made of 100 billions of neurons, each connected to 7000 other neurons on
-average. Unfortunately, direct observation of the connectome, the wiring
+organ made of about 100 billions of neurons, each connected to 7000 other neurons on
+average \citep{pakkenberg2003aging}. Unfortunately, direct observation of the connectome, the wiring
 diagram of the brain, is not yet technically feasible. Without being perfect,
@@
 In this paper, we present a simplified -- yet nearly as good -- version of the
-winning method\footnote{Code available at \url{https://github.com/asutera
-/kaggle-connectomics}} of the Connectomics
+winning method\footnote{Code available at \url{https://github.com/asutera/kaggle-connectomics}} of the Connectomics
 Challenge\footnote{\url{http://connectomics.chalearn.org}}, as a simple and
@@
 inactivity, the first part of our algorithm consists in cleaning the raw
-fluorescence data. More specifically, time series are processed using standard
-signal processing filters in order to remove noise due to light scattering
-effects, to account for fluorescence  low decay and to reduce the importance of
+fluorescence data.
+More specifically, time series are processed using standard
+signal processing filters in order to (i) remove noise mainly due to fluctuations independent of calcium, calcium fluctuations independent of spiking activity, calcium fluctuations in nearby tissues that have been mistakenly captured, or simply by the imaging process (ii) to account for fluorescence low decay and (iii) to reduce the importance of
 global high activity in the network. The overall process is illustrated in
@@
 \end{align}
+These filters are standard in the signal processing field \citep{kaiser1977data, oppenheim1983signals}.
+The idea of the second one is to not consider future values and to introduce decreasing weights.
 For the sake of illustration, the effect of the filter $f_1$ on the signal
@@
 
-Furthermore, it can be observed that neurons communicate through short spikes, characterized by a high
-frequency, while low frequencies of the signal mainly correspond to the slow
+Furthermore, short spikes, characterized by a high
+frequency, can be seen as an indirect indicator of neuron communications while low frequencies of the signal mainly correspond to the slow
 decay of fluorescence. To have a signal that only has high magnitude around instances where the spikes occur, the second step of our pipeline transforms the time series into its backward
@@
 \end{align}
-yielding Figure \ref{fig:threshold_curve}.
+yielding Figure \ref{fig:threshold_curve} where $\tau$ is the threshold parameter and $\mathbb{1}$ is the indicator function.
 As we can see, the processed signal only contains clean spikes.
@@
 first principal components \citep{bishop2006pattern} (with
-$M=0.8 p$ in our experiments).
+$M=0.8 p$ in our experiments, see Appendix~\ref{app:pca}).
 
@@
 
-% Note on directionality
-
-%% Our  connection inference  procedure  relies  on several  assumptions. First,
-%% we will assume that  the fluorescence concentrations of all $p$ neurons can be
-%% modeled as a set of random variables $X = \{X_1, \dots, X_p\}$  that are drawn
-%% from a time invariant joint  probability distribution $P_X$. Or, say otherwise,
-%% we assume that there exists a probability distribution $P_X$ such that the
-%% fluorescence concentrations at a particular time $t$ can be seen as an
-%% independent realization of $P_X$.
-
-%% To assess the presence of a connection between two neurons, we will
-%% use partial correlation statistics, which has been used extensively
-%% for the inference of gene regulatory networks \cite{}.
-
-%% To a joint probability distribution $P_X$ corresponds a
-%% graph where (i) each node is a random variable and (ii) two nodes are
-%% only connected if they correspond to two dependent variables. We assume that two neurons are
-%% connected if  and only if,  there exists  in this  graph an edge
-%% that connects  directly the  two random  variables to  which they correspond.
-%% In this context, it is equivalent to writing that two neurons $i$ and $j$ are  not  directly
-%% connected  if and only if  $X_i$  and $X_j$  are  conditionally independent
-%% with  respect to all  other variables. We remind  that two random  variables
-%% $X_i$  and  $X_j$  are  said  to  be  conditionally independent to a (possibly
-%% empty)  set of controlling random variables $Z$, denoted $X_i \perp X_j | Z$,
-%% if the joint conditional probability distribution   $P_{X_i,  X_j   |   Z}$
-%% factorizes  into   $P_{X_i|Z} P_{X_j|Z}$.  In particular,  when  $X_i$ and
-%% $X_j$ are  conditionally independent  with respect  to all  the other
-%% variables, denoted  $X_i \perp  X_j  | X^{-i,j}$,  then  the  observation  of
-%% $X_i$  given  the knowledge  of  $X^{-i,j}$ provides  no information  about
-%% $X_j$,  and vice-versa.
-
-%% In the  particular case where $P_X$ is  a joint  Gaussian distribution
-%% $\mathcal{N}(\mu; \Sigma)$ of mean  vector $\mu$ and covariance matrix
-%% $\Sigma$, $X_i$  and $X_j$ are conditionally  independent with respect to the
-%% other variables $X^{-i,j}$ if their \textit{partial correlation} statistic is
-%% null~\citep{baba2004partial}, i.e., if
-%% \begin{equation}
-%% \rho_{X_i, X_j | X^{-i,j}} = -\frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii} \Sigma^{-1}_{jj}}} = 0, \label{eq:inverse}
-%% \end{equation}
-%% where $\Sigma^{-1}$ is known as the precision or concentration matrix.
-%% Conversely, $X_i$ and $X_j$ are conditionally dependent if $\rho_{X_i, X_j |
-%% X^{-i,j}} \neq 0$, where $\rho_{X_i, X_j | X^{-i,j}} \in [-1;1]$. Note that the
-%% larger the value of this term, the stronger the dependence between variables
-%% $X_i$ and $X_j$.
-
-%% Our approach implicitly makes the additional assumption  that $P_X$ is  a
-%% joint Gaussian distribution since it  outputs as degree of association
-%% between two neurons $i$ and $j$ an estimate of $\rho_{X_i, X_j | X^{-i,j}}$.
-%% Note also that the partial correlation
-%% statistic is symmetric  (i.e., $\rho_{X_i, X_j | X^{-i,j}} = \rho_{X_j, X_i |
-%% X^{-j,i}}$).
-Therefore, our approach cannot identify the direction of the interaction.
-We will see in Section~\ref{sec:results} why this only affects slightly its performances, with respect to the metric used in the Connectomics challenge.
-
-%% We now detail our procedure for estimating partial correlation
-%% statistics ($\rho_{X_i, X_j | X^{-i,j}}$) from the data. It first
-%% estimates the covariance matrix from the data. Afterwards, it computes
-%% the exact inverse of this matrix, from which it infers the value of
-%% $\rho_{X_i, X_j | X^{-i,j}}$ using equation (\ref{eq:inverse}). Note
-%% that we have also experimented procedures where the exact inverse was
-%% replaced by an approximation of it using only the $M$ principal
-%% components of $\Sigma$~\citep{bishop2006pattern} whose associated
-%% eigen values were significantly higher than zero. Such an
-%% approximation is equivalent to assume that the firing activity of all
-%% neurons can be explained by only a subset of them whose size is equal
-%% to $M$. We observed that those procedures were often leading to better
-%% results. Note that we found out by running expriments that the number
-%% $M$ of principal components is around $0.8p$ (see discussion in
-%% Appendix~\ref{app:REF} \textcolor{red}{REF}).
-
-%% % Computationally, they can be estimated
-%% % % efficiently in $O(M^3)$ (instead of $O(p^3)$)
-%% % from the $M$ first principal
-%% % components extracted through PCA~\citep{bishop2006pattern} on the processed
-%% % data. While speeding up computation, it allows to further
-%% % filter the the data by removing the contribution of components that are respectively
-%% % due to redundancy or noise, i.e., with an eigen value respectively is equal to zero or close to zero.
-
 \section{Experiments} \label{sec:results}
-
-%% \textcolor{red}{to incorporate:
-%% To highlight the benefits of measuring the partial dependence conditional to
-%% all other variables, we compare in Section~\ref{sec:results} with the
-%% \textit{Pearson correlation} statistics, which measure instead the linear
-%% dependence between variables, independently of the others. Accordingly, $X_i$
-%% and $X_j$ are independent, without any conditioning, if their Pearson correlation statistic is zero, that
-%% is if
-%% \begin{equation}
-%% \rho_{X_i,X_j} = \frac{\Sigma_{ij}}{\sqrt{\Sigma_{ii} \Sigma_{jj}}} = 0.
-%% \end{equation}}
 
@@
 
-% \begin{table}[t]\label{tab:comparison}
-% %\caption{Evaluation of different methods on the four \textit{normal} datasets\label{tab:comparison}}
-% \centering
-% \small
-% \begin{tabular}{| l | c c c c c c | c c c c c c|}
-% \hline
-% & \multicolumn{6}{c|}{AUROC} & \multicolumn{6}{c|}{AUPRC} \\
-% \textit{Method} $\backslash$ \textit{normal-} & \textit{lowcon} & \textit{highcon} & \textit{lowcc} & \textit{highcc} & \textit{3-highrate} & \textit{4-lownoise} & \textit{lowcon} & \textit{highcon} & \textit{lowcc} & \textit{highcc} & \textit{3-highrate} & \textit{4-lownoise}\\
-% \hline
-% \hline
-% % No  filtering       					& 0.777 & 0.767 & 0.772 & 0.774 & 0.070 & 0.064 & 0.068 & 0.072\\
-% % $ h \circ g \circ f_1$                  & 0.923 & 0.925 & 0.923 & 0.922 & 0.311 & 0.315 & 0.313 & 0.304\\
-% % $ w \circ h \circ g \circ f_1$          & 0.931 & 0.929 & 0.928 & 0.926 & 0.326 & 0.323 & 0.319 & 0.303\\
-% % + PCA         							& 0.932 & 0.930 & 0.928 & 0.926 & 0.355 & 0.353 & 0.350 & 0.333\\
-% % Averaging           					& 0.937 & 0.935 & 0.935 & 0.931 & 0.391 &  0.390 &  0.385 & 0.375\\
-% % Full method           					& 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388\\
-% % \hline
-% % PC & 0.886 & 0.884 & 0.891 &  0.877 & 0.153 & 0.145 & 0.170 & 0.132\\
-% % GTE & 0.890 & 0.893 & 0.894 & 0.873 & 0.171 & 0.174 & 0.197 & 0.142\\
-% % GENIE3 & & & & & & & & \\
-% % \hline
-% \end{tabular}
-% \caption{Top: Performance on \textit{normal-1,2,3,4} with partial correlation and different filtering functions.
-% Bottom: Performance on \textit{normal-1,2,3,4} with different methods.}
-% \end{table}
+\section{About the number of principal components}
+\label{app:pca}
 
-% NEXT APPENDIX SECTION
-% SUPPLEMENTARY RESULTS
-% EXPLAIN EACH TAB AND VERIFY THE EXACTITUDE - RUN OPTIMIZED VERSION ON low-noise, ... ?
-%
+The main idea of principal component analysis (PCA) is to reduce the
+dimensionality of a dataset whose variables are interrelated
+\citep{jolliffe2005principal}. It consists in finding a new ordered set of
+uncorrelated variables, called the principal components, where the most
+principal components, i.e. the first variables, hold most of the data variation, also denoted as
+variance, scattered in all the original variables.
 
-% EXPLAIN PCA - FIG
+Figure~\ref{fig:pca} shows the explained variance by compoments and gives a hint about the number of uncorrelated variables required to
+explain all the variation in the original data.
 
-%\vspace{5cm}
+The singular value decomposition (SVD) relies on the fact that every matrix -
+not only square matrices - can be decomposed into a diagonal nonnegative
+matrix with the help of two unit matrices \citep{alter2000singular}.
 
-% The algorithm propose in sections \ref{sec:filter} and \ref{sec:inference} has been optimized at its extreme limit to win the challenge.
-In this section, we will describe the full tuned algorithm and present some results.
+The terms of the diagonal matrix can be used to determine the fraction of the
+overall information hold by the components in the decomposition and therefore
+give the relative significance of the components \citep{alter2000singular}.
+Figure~\ref{fig:SVD} displays the singular value ratio of all networks in the
+challenge.
 
-% Note that our parameter tuning was mainly
-% done on the \textit{normal-1} dataset and partly on \textit{normal-4} dataset,
-% therefore it may justify why these networks are better retrieved despite the
-% fact that some might be simpler to infer.
+Obvioulsy, Figure~\ref{fig:pca} shows that for both approaches only 800
+components are required to explain the (majority of) network structures.
+Therefore, the value of the parameter $M$ is immediat and should be obviously
+set to $800$, or equivalently to $0.8p$. \\
 
-% % Introduce a custom solution to make the Y matrix asymmetric
-% % Introduce directivity
-% \textcolor{red}{Est-ce qu'on ne le ferait pas passer dans l'appendice B? Ou du moins l'équation?}
-% Since partial correlation is a symmetric measure, the causal mechanism behind the
-% interaction ($A$ directly causes $B$, $B$ directly causes $A$ or both) can not
-% be directly inferred\footnote{Also note that two other causal mechanisms might be
-% implied while having a non-zero partial coefficient: (i) a pair of variables
-% is induced by a common (hidden) variable; (ii) $A$ (respectively $B$) is
-% conditionally correlated to a hidden variable affecting $B$ (resp. $A$)
-% \citep{de2004discovery}.}.
-% In order to retrieve causal information, we developed an
-% heuristics based on the following observation. The rise of fluorescence
-% indicates the activation of a neuron $i$. If a neuron $j$ have also
-% an increased of fluorescence after a slight delay, this could have been
-% caused by the neuron $i$. Thus, we count whenever
-% such events occurred between consecutive time steps
-% \[
-% \hat{Z}: z_{ij} = \sum_{t=1}^{T - 1}
-%     \mathbb{1}((x_j^{t+1} - x_i^t) \in \left[f_1, f_2 \right]) -
-%     \mathbb{1}((x_i^{t+1} - x_j^t) \in \left[f_1, f_2 \right]), \forall i, j \in V
-% \]
-% where $f_1$ and $f_2$ are parameters of the method.
-% Finally, the weighted average of correlation matrices is combined with $Z$ such
-% that $Z$ has a contribution of $0.3\%$ to the prediction of an edge.
+\begin{figure}[t]
+\centering
+\subfigure[PCA]{\includegraphics[width=0.45\textwidth]{explained_variance_all} \label{fig:PCA}}
+\subfigure[SVD]{\includegraphics[width=0.45\textwidth]{singular_values_all} \label{fig:SVD}}
+\caption{Explained variance ratio by component (left) and singular value ratio by component (right) for all networks.}
+\label{fig:pca}
+\end{figure}
+\section{Computational information}
 
-% % For the directory method, only filters defined by Equations
-% % \ref{eq:low-pass}, \ref{eq:high-pass} and \ref{eq:hard-treshold-filter} were
-% % used.
-
-% \section{Extended results}
-
-% \begin{table}
-% \small
-% \centering
-% \begin{tabular}{@{}l *{8}{c}@{}}
-%   & \multicolumn{4}{c}{AUROC} & \multicolumn{4}{c}{AUPRC} \\
-% \hline \hline
-% Methods $\backslash$ normal- & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 \\
-% \hline \hline
-% % Directivity \textcolor{red}{appendix?} & 0.535 & 0.526 & 0.533 & 0.535 & 0.012 & 0.012 & 0.012 & 0.012 \\
-% Pearson correlation    & 0.886 & 0.884 & 0.891 & 0.877 & 0.153 & 0.145 & 0.170 & 0.132 \\
-% GENIE3 (depth = 1)     & 0.878 & 0.877 & 0.873 & 0.873 & 0.184 & 0.173 & 0.182& 0.172\\
-% GENIE3 (depth = 2)     & 0.889 & 0.888 & 0.883 & 0.884* & 0.217 & 0.210 & 0.220 & 0.199* \\
-% GENIE3 (depth = 3)     & 0.892 & 0.891* & 0.887 & 0.887 & 0.232 & 0.226* & 0.237 & 0.215\\
-% GTE                    & 0.890 & 0.893 & 0.894 & 0.873 & 0.171 & 0.174 & 0.197 & 0.142 \\
-% Partial correlation    & 0.930 &  0.927 &  0.926 &  0.923& 0.363  & 0.347 &  0.346 & 0.328 \\
-% Partial correlation (avg. 2) & 0.937 & 0.935 & 0.935 & 0.931 & 0.391 &  0.390 &  0.385 & 0.375  \\
-% Partial correlation (avg. 4) & 0.938 & 0.936 & 0.936 & 0.932& 0.391 & 0.389 & 0.385 & 0.374\\
-% % Our approach simple + dir & 0.939 & 0.936 & 0.937 & 0.933& 0.392 & 0.390 & 0.386 & 0.375\\
-% Partial correlation (opt.) & 0.932 & 0.931 & 0.930 & 0.928 & 0.364 & 0.366 & 0.359 & 0.344 \\
-% Our approach (opt. \& avg. 4)    & 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388 \\
-% % Our approach + dir  \textcolor{red}{appendix?}   & 0.944 & 0.943 & 0.942 & 0.940 & 0.404 & 0.405 & 0.399 & 0.389 \\
-% \end{tabular}
-% \caption{TODO (* means not 10000 trees but more than 9500, to be solved.) }
-% \label{tab:tab1}
-% \end{table}
-
-% \section{Supplementary results}
-
-% \begin{table}[htbp]
-% \centering
-% \caption{Correlation (ROC). Improvement of each stage of our approach. Note that we choose the
-%          \textit{best} threshold (\textcolor{red}{for now 0.11}) for stages 1 to 4.}
-% \begin{tabular}{*{5}{l}}
-% \toprule
-% Stage               & normal-1 & normal-2 & normal-3 & normal-4 \\
-% \midrule
-% Nothing             & 0.681 & 0.699 & 0.683 & 0.681\\
-% Weights             & 0.695 & 0.713 & 0.697 & 0.694\\
-% H-T                 & 0.876 & 0.873 & 0.877 & 0.869\\
-% H-T + Weights       & 0.886 & 0.884 & 0.891 & 0.877\\
-% P-P                 & 0.857 & 0.850 & 0.843 & 0.832\\
-% P-P + Weights       & 0.826 & 0.823 & 0.817 & 0.799\\
-% \bottomrule
-% \end{tabular}
-% \end{table}
-
-% \begin{table}[htbp]
-% \centering
-% \caption{Correlation (P-R). Improvement of each stage of our approach. Note that we choose the
-%          \textit{best} threshold (\textcolor{red}{for now 0.11}) for stages 1 to 4.}
-% \begin{tabular}{*{5}{l}}
-% \toprule
-% Stage               & normal-1 & normal-2 & normal-3 & normal-4 \\
-% \midrule
-% Nothing             & 0.028 & 0.028 & 0.025 & 0.026\\
-% Weights             & 0.031 & 0.030 & 0.027 & 0.028\\
-% H-T                 & 0.143 & 0.128 & 0.150 & 0.129\\
-% H-T + Weights       & 0.153 & 0.145 & 0.170 & 0.132\\
-% P-P                 & 0.100 & 0.087 & 0.079 & 0.083\\
-% P-P + Weights       & 0.079 & 0.071 & 0.067 & 0.064\\
-% \bottomrule
-% \end{tabular}
-% \end{table}
-
-% \begin{table}[htb]
-% \centering
-% \caption{Comparison (P-R) with other methods (for now, $t = 0.11$)}
-% \begin{tabular}{*{5}{l}}
-% \toprule
-% Methods             & normal-1 & normal-2 & normal-3 & normal-4 \\
-% \midrule
-% Correlation (best)         & 0.153 & 0.145 & 0.170 & 0.132 \\
-% Partial correlation (best) & 0.364 & 0.366 & 0.359 & 0.344 \\
-% Our approach (best)        & 0.403 & 0.404 & 0.398 & 0.388 \\
-% GENIE3                     & & & & \\
-% GTE                        & 0.171 & 0.174 & 0.197 & 0.142 \\
-% Directivity                & 0.012 & 0.012 & 0.012 & 0.012 \\
-% Our approach + dir         & 0.404 & 0.405 & 0.399 & 0.389 \\
-% \bottomrule
-% \end{tabular}
-% \end{table}
-
-% \begin{table}[htb]
-% \centering
-% \caption{Inverse correlation (ROC). Improvement of each stage of our approach. Note that we choose the
-%          \textit{best} threshold (\textcolor{red}{for now 0.11}) for stages 1 to 4.}
-% \begin{tabular}{*{5}{l}}
-% \toprule
-% Stage               & normal-1 & normal-2 & normal-3 & normal-4 \\
-% \midrule
-% Nothing             & 0.777 & 0.767 & 0.772 & 0.774 \\
-% PCA                 & 0.780 & 0.770 & 0.776 & 0.777 \\
-% Weights             & 0.780 & 0.769 & 0.776 & 0.777 \\
-% Weights + PCA       & 0.783 & 0.772 & 0.779 & 0.780 \\
-% H-T                 & 0.893 & 0.891 & 0.891 & 0.886 \\
-% H-T + PCA           & 0.894 & 0.892 & 0.891 & 0.886 \\
-% H-T + Weights       & 0.899 & 0.897 & 0.896 & 0.891 \\
-% H-T + Weights + PCA & 0.900 & 0.898 & 0.896 & 0.892 \\
-% P-P                 & 0.925 & 0.925 & 0.924 & 0.923 \\
-% P-P + PCA           & 0.926 & 0.926 & 0.925 & 0.923 \\
-% P-P + Weights       & 0.931 & 0.930 & 0.928 & 0.927 \\
-% P-P + Weights + PCA & 0.932 & 0.931 & 0.930 & 0.928 \\
-% Averaging (PCA)     & 0.943 & 0.942 & 0.942 & 0.939 \\
-% Stacking            & 0.944 & 0.943 & 0.942 & 0.940 \\
-% \bottomrule
-% \end{tabular}
-% \end{table}
-
-% \begin{table}[htb]
-% \centering
-% \caption{Inverse correlation (P-R). Improvement of each stage of our approach. Note that we choose the
-%          \textit{best} threshold (\textcolor{red}{for now 0.11}) for stages 1 to 4.}
-% \begin{tabular}{*{5}{l}}
-% \toprule
-% Stage               & normal-1 & normal-2 & normal-3 & normal-4 \\
-% \midrule
-% Nothing             & 0.070 & 0.064 & 0.068 & 0.072\\
-% PCA                 & 0.076 & 0.070 & 0.075 & 0.079\\
-% Weights             & 0.074 & 0.067 & 0.072 & 0.076\\
-% Weights + PCA       & 0.080 & 0.073 & 0.079 & 0.083\\
-% H-T                 & 0.264 & 0.260 & 0.269 & 0.241\\
-% H-T + PCA           & 0.266 & 0.263 & 0.273 & 0.244\\
-% H-T + Weights       & 0.280 & 0.273 & 0.281 & 0.251\\
-% H-T + Weights + PCA & 0.284 & 0.278 & 0.285 & 0.255\\
-% P-P                 & 0.322 & 0.324 & 0.323 & 0.312\\
-% P-P + PCA           & 0.347 & 0.352 & 0.355 & 0.341\\
-% P-P + Weights       & 0.333 & 0.334 & 0.327 & 0.313\\
-% P-P + Weights + PCA & 0.364 & 0.366 & 0.359 & 0.344\\
-% Averaging           & 0.403 & 0.404 & 0.398 & 0.388\\
-% Stacking            & 0.404 & 0.405 & 0.399 & 0.389\\
-% \bottomrule
-% \end{tabular}
-% \end{table}
-
-% \section{Signal processing highly improves performance}
-
-% On Table \ref{tab:tab3}, it can be seen that each step of our approach globally
-% improves the score on both metrics. However, processing, weights and averaging
-% (respectively denoted as $P$,$W$ and $Averaging$ in Tab.\ref{tab:tab3}) as
-% described in Section \ref{sec:filter} are the key steps of our algorithm.
-
-% It also appears that the averaging over the low-pass filter designs and the
-% threshold values increases significantly the quality of the inferred network
-% according to both metrics.
-
-% % Explaining the method (thèse de Gilles)
-% % Avg.: Averaging over the threholds and L-P filters improves a lot both metrics.
-% % Averaging
-
-% %% Depth -- Gilles chapitre 7
-% % Genie3 : better in auprc while worse in auroc than GTE. Why?
-% % Genie3 : "Conditioning" better and better but need a lot of trees
-
-% \begin{table}[tbh]
-% \centering
-% \small
-% \begin{tabular}{@{}l *{8}{c}@{}}
-% \hline
-%   & \multicolumn{4}{c}{AUROC} & \multicolumn{4}{c}{AUPRC} \\
-% \hline
-% Methods $\backslash$ normal- & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 \\
-% No  filtering       & 0.777 & 0.767 & 0.772 & 0.774 & 0.070 & 0.064 & 0.068 & 0.072\\
-% P                   & 0.925 & 0.925 & 0.924 & 0.923 & 0.322 & 0.324 & 0.323 & 0.312\\
-% P + W               & 0.931 & 0.930 & 0.928 & 0.927 & 0.333 & 0.334 & 0.327 & 0.313\\
-% P + W + PCA         & 0.932 & 0.931 & 0.930 & 0.928 & 0.364 & 0.366 & 0.359 & 0.344\\
-% Averaging           & 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388\\
-% %Averaging + Directivity & 0.944 & 0.943 & 0.942 & 0.940 & 0.404 & 0.405 & 0.399 & 0.389\\
-% \end{tabular}
-% \caption{Optimized method (TODO)}
-% \label{tab:tab3}
-% \end{table}
-
-% \begin{table}[tbh]
-% \centering
-% \small
-% \begin{tabular}{@{}l *{8}{c}@{}}
-% \hline
-%   & \multicolumn{4}{c}{AUROC} & \multicolumn{4}{c}{AUPRC} \\
-% \hline
-% Methods $\backslash$ normal- & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 \\
-% No  filtering       & 0.777 & 0.767 & 0.772 & 0.774 & 0.070 & 0.064 & 0.068 & 0.072\\
-% P                   & 0.923 & 0.925 & 0.923 & 0.922 & 0.311 & 0.315 & 0.313 & 0.304\\
-% P + W               & 0.931 & 0.929 & 0.928 & 0.926 & 0.326 & 0.323 & 0.319 & 0.303\\
-% P + W + PCA         & 0.932 & 0.930 & 0.928 & 0.926 & 0.355 & 0.353 & 0.350 & 0.333\\
-% Averaging           & 0.938 & 0.936 & 0.936 & 0.932 & 0.391 & 0.389 & 0.385 & 0.374\\
-% %Averaging + Directivity & 0.944 & 0.943 & 0.942 & 0.940 & 0.404 & 0.405 & 0.399 & 0.389\\
-% \end{tabular}
-% \caption{Simplified method (TODO)}
-% \label{tab:tab3}
-% \end{table}
-
-% %% Talk about filters future and past
+\begin{table}[h]
+\caption{Execution time, scalability, memory requirements for methods described in the paper. \textcolor{red}{to do.}}
+\label{tab:results_appendix}
+\centering
+\small
+\begin{tabular}{| l|c|c|c|} \hline
+Methods & Execution time & Scalability & Memory requirements \\ \hline
+Partial correlation & & & \\ 
+GTE  & & & \\
+GENIE3 & & & \\ \hline
+\end{tabular}
+\end{table}
 

### 2014-07-18 article.tex
typo
some changes in appendix C

@@
 dimensionality of a dataset whose variables are interrelated
-\citep{jolliffe2005principal}. It consists in finding a new ordered set of
-uncorrelated variables, called the principal components, where the most
-principal components, i.e. the first variables, hold most of the data variation, also denoted as
-variance, scattered in all the original variables.
+\citep{jolliffe2005principal}. It consists in finding a new set of
+uncorrelated variables, denoted as principal components, where the most
+principal components, assuming an order between the components, hold most of the variance of the data scattered in all the original variables.
 
-Figure~\ref{fig:pca} shows the explained variance by compoments and gives a hint about the number of uncorrelated variables required to
-explain all the variation in the original data.
+Figure~\ref{fig:pca} shows the explained variance (ratio) by compoments and gives a hint about the number of uncorrelated variables required to
+explain all - or, at least, the majority of -  the variation in the original data.
 
@@
 components are required to explain the (majority of) network structures.
-Therefore, the value of the parameter $M$ is immediat and should be obviously
+Therefore, the value of the parameter $M$ is immediat and should be clearly
 set to $800$, or equivalently to $0.8p$. \\
@@
 
+To perform experiments, we used a Macbook Pro (2014) with a ram memory 16Go 1600 MHz DDR3 and a processor 2.3GHz Intel Core i7.
+
+In order to compare the execution time with other methods, it takes about xx and xx hours to compute respectively GTE and GENIE3.
+However, GENIE3 is highly parallelizable (by taking several smaller forests or applying GENIE3 on subsets of variables) and the execution time can be significantly reduced.
+
 \begin{table}[h]
@@
 \small
-\begin{tabular}{| l|c|c|c|} \hline
-Methods & Execution time & Scalability & Memory requirements \\ \hline
-Partial correlation & & & \\ 
-GTE  & & & \\
-GENIE3 & & & \\ \hline
+\begin{tabular}{| l|c|c|} \hline
+Methods & Execution time  & Memory requirements \\ \hline
+PC & & $\sim$5Go\\
+Averaging & & \\
+Full Method & & \\ \hline
 \end{tabular}

### 2014-07-19 response.tex
some changes and computational information deleted

@@
 \textbf{A}: We obviously agree with the reviewer that such informations are interesting, especially in the context of a challenge.
-We add a table with some interesting figures.
+For the simplified method, it only takes a few hours (about 3 to 6 hours depending on the machine used) and a few gigabytes of memory.
+The ``Full method'' needs the double of time (about 6 to 12 hours) and it requires a few hours more to take into account the edge directionality.
+GTE and GENIE3 take more time to compute than PC and they require about xx \textcolor{red}{(AS: Need AJ to know exactly the execution time)} hours and yy hours respectively.
+However, GENIE3 is highy parallelizable (by taking several smaller forests or applying GENIE3 on subsets of variables) and the execution time can be significantly reduced.
+
 However, let us note that the simple method presented in the paper already gives good performances despite its light computational needs.
 
-We also would like to mention that our code is available publicly on \url{https://github.com/asutera/kaggle-connectomics} and that some verifications, including memory requirements and execution time, of the full method are displayed on the challenge website \url{http://connectomics.chalearn.org/home/challenge-results-verification}.\\
+We also would like to mention that our code is available publicly on \url{https://github.com/asutera/kaggle-connectomics} and that some verifications, including memory requirements and execution time, of the ``Full method'' are displayed on the challenge website \url{http://connectomics.chalearn.org/home/challenge-results-verification}.\\
 

### 2014-07-19 article.tex
some changes and computational information deleted

@@
 \end{figure}
-\section{Computational information}
 
-To perform experiments, we used a Macbook Pro (2014) with a ram memory 16Go 1600 MHz DDR3 and a processor 2.3GHz Intel Core i7.
+% \section{Computational information}
 
-In order to compare the execution time with other methods, it takes about xx and xx hours to compute respectively GTE and GENIE3.
+% To perform experiments, we used a Macbook Pro (2014) with a ram memory 16Go 1600 MHz DDR3 and a processor 2.3GHz Intel Core i7.
+
+% In order to compare the execution time with other methods, it takes about xx and xx hours to compute respectively GTE and GENIE3.
 However, GENIE3 is highly parallelizable (by taking several smaller forests or applying GENIE3 on subsets of variables) and the execution time can be significantly reduced.
 
-\begin{table}[h]
-\caption{Execution time, scalability, memory requirements for methods described in the paper. \textcolor{red}{to do.}}
-\label{tab:results_appendix}
-\centering
-\small
-\begin{tabular}{| l|c|c|} \hline
-Methods & Execution time  & Memory requirements \\ \hline
-PC & & $\sim$5Go\\
-Averaging & & \\
-Full Method & & \\ \hline
-\end{tabular}
-\end{table}
+% \begin{table}[h]
+% \caption{Execution time, scalability, memory requirements for methods described in the paper. \textcolor{red}{to do.}}
+% \label{tab:results_appendix}
+% \centering
+% \small
+% \begin{tabular}{| l|c|c|} \hline
+% Methods & Execution time  & Memory requirements \\ \hline
+% PC & & $\sim$5Go\\
+% Averaging & & \\
+% Full Method & & \\ \hline
+% \end{tabular}
+% \end{table}
 

### 2014-07-21 article.tex
modif from DE

@@
 The human brain is a complex biological
-organ made of about 100 billions of neurons, each connected to 7000 other neurons on
+organ made of about 100 billion of neurons, each connected to 7000 other neurons on
 average \citep{pakkenberg2003aging}. Unfortunately, direct observation of the connectome, the wiring
@@
 \end{align}
-These filters are standard in the signal processing field \citep{kaiser1977data, oppenheim1983signals}.
-The idea of the second one is to not consider future values and to introduce decreasing weights.
-For the sake of illustration, the effect of the filter $f_1$ on the signal
+These filters are standard in the signal processing field \citep{kaiser1977data, oppenheim1983signals}. For the sake of illustration, the effect of the filter $f_1$ on the signal
 is shown in Figure \ref{fig:lp_curve}.
@@
 Furthermore, short spikes, characterized by a high
-frequency, can be seen as an indirect indicator of neuron communications while low frequencies of the signal mainly correspond to the slow
+frequency, can be seen as an indirect indicator of neuron communication while low frequencies of the signal mainly correspond to the slow
 decay of fluorescence. To have a signal that only has high magnitude around instances where the spikes occur, the second step of our pipeline transforms the time series into its backward
@@
 components are required to explain the (majority of) network structures.
+There, we can conclude that the value of $M$ should be set to 800, or equivalently, to $0.8 p$.
+
 Therefore, the value of the parameter $M$ is immediat and should be clearly
@@
 \subfigure[SVD]{\includegraphics[width=0.45\textwidth]{singular_values_all} \label{fig:SVD}}
-\caption{Explained variance ratio by component (left) and singular value ratio by component (right) for all networks.}
+\caption{Explained variance ratio by number of principal components (left) and singular value ratio by number of principal components (right) for all networks.}
 \label{fig:pca}

### 2014-07-23 article.tex
typo
workon on appendix C

@@
 \usepackage[utf8]{inputenc}
+\usepackage[super]{nth}
 
@@
 \end{equation}
-where $\Sigma^{-1}$, known as the precision or concentration matrix, is the inverse of the covariance matrix $\Sigma$ of $X$. %%  Partial
-%% correlation can be interpreted in several ways. The partial
-%% correlation coefficient $p_{i,j}$ can be shown to measure the
-%% correlation between $X_i$ and $X_j$ when they are corrected for the
-%% (linear) effect of all other variables in $X$ \cite{}.
+where $\Sigma^{-1}$, known as the precision or concentration matrix, is the inverse of the covariance matrix $\Sigma$ of $X$.
 Assuming that the distribution $P_X$ is a multivariate Gaussian
@@
 \citep{de2004discovery,Schafer:2005}.
-%% Given a set of multivariate Gaussian
-%% random variables $X$, the (undirected) graph that connects all pairs
-%% of variables $X_i$ and $X_j$ such that $p_{i,j}\neq 0$ is called a
-%% Gaussian graphical models (GGMs). Because it measures conditional
-%% dependencies, partial correlation should naturally only detect direct
-%% associations between neurons. The superiority of partial correlation
-%% over standard correlation as an association measure have already been
-%% shown in the context of the inference of gene regulatory networks from
-%% gene expression data \cite{}. We will compare both measures in Section
-%% \ref{sec:results}.
+
 Note that the partial correlation statistic is symmetric
@@
 \begin{table}[t]
-%\caption{Evaluation of different methods on the four \textit{normal} datasets\label{tab:comparison}}
 \caption{Top: Performance on \textit{normal-1,2,3,4} with partial correlation and different filtering functions.
@@
 
-%% To assess our method, we focus on the \textit{normal-2} dataset
-%% provided by the organizers of the Connectomics challenge. Experiments
-%% on \textit{normal-1, normal-3, normal-4} show similar trends to
-%% \textit{normal-2} and are presented in the Appendix \textcolor{red}{REF}.
-%% Those datasets have $p=1000$ time series of length $T=179500$ of image
-%% calcium from simulated neuronal networks \citep{stetter2012model}. Each of these
-%% networks contains approximately 15000 edges.
-
-%% % Metrics : ROC AUC and AUPRC
-%% In supervised learning terms, the network inference task can be viewed as a
-%% binary classification task where one has to correctly classify the presence or
-%% the absence of edges of the graph. We assess the accuracy of the network
-%% inference method using the area under the ROC curve (AUROC) and the area under
-%% the precision-recall curve (AUPRC) \citep{schrynemackers2013protocols}.
-
-%% The proposed approach is compared to Pearson correlation statistics
-%% (as described in Section~\ref{sec:inference}), generalized transfer
-%% entropy (GTE) and the GENIE3 algorithm.
-%% \begin{itemize}
-%% \item \textbf{GTE} \citep{stetter2012model}, the baseline of the challenge,
-%% measures for all pairs of neurons $i$ and $j$ the reduction of uncertainty in
-%% predicting future values of $i$ given the observation of the time series of the
-%% neuron $j$ conditionally to the observation of past time series of neuron $i$,
-%% whenever the average fluorescence is over a conditioning level. Pre-processing
-%% and conditioning level were set to reproduce baseline of the challenge.
-
-%% \item \textbf{GENIE3} \citep{huynhthu2010inferring} translates the inference
-%% of the network of $p$ neurons into $p$ supervised learning tasks. For each
-%% task, the fluorescence of a neuron is predicted from the fluorescence of all
-%% other neurons using a tree based ensemble such as random forest
-%% \citep{breiman2001random}. The tree ensemble associates a variable importance
-%% score \citep{louppe2013understanding} to each neuron used in the predictions,
-%% which is used as a degree of associate. The following parameters are used
-%% $10000$ trees, $\log_2{p}$ variables are randomly selected to split tree nodes
-%% and the maximal tree depth is constrained to 1, 2 or 3. \textcolor{red}{AJ Which
-%% depth is represented on the graph?}
-%% \end{itemize}
-
-%% \subsection*{Partial correlation improves over state-of-the-art methods}
-
 Partial correlation and averaged partial correlation clearly outperform all
@@
 
-%% bu by about a factor
-%% of 2 in AUPRC reaching $0.347$ and an increased of $0.03$ in
-%% AUROC. Averaging Partial correlation matrix over a wide of parameters
-%% further improves AUPRC to $0.389$ and improve AUROC by $0.009$.  Two
-%% reasons might explain such differences: (i) only the partial
-%% correlation-based methods and GENI3 at lesser extent distinguish
-%% direct links from indirect one, (ii) simulated networks from the
-%% \citep{stetter2012model} generator or neural networks in general could
-%% be reduced to a linear model after pre-processing. Those results
-%% generalizes over the other datasets see Appendix \textcolor{red}{REF}.
-
 \begin{figure}[t]
@@
 \caption{ROC (left) and PR (right) curves on \textit{normal-2} for the compared methods. Areas under the curves are reported in the legend.}
-%% The weighted average of partial correlation matrix, winning approach
-         %% of the challenge, yields better than AUROC and AUPRC than all
-         %% other state-of-the-art methods. (parameters: $\tau=0.11$ except for
-         %% averaged partial correlation method, partial correlation used
-         %% filter $f_1$). Area under the curves are given between $()$
-         %% for the corresponding methods.
-%}
+
 \label{fig:curves}
 \end{figure}
-
-%% \textcolor{red}{Only one GENI3, thus it can't be observed.}
-%% As observed on Figure \ref{fig:curves}, the GENIE3 performance increases with
-%% deeper trees while being still computationally feasible. The reason is twofold.
-%% First, the deeper the tree, the larger is the conditioning. \textcolor{red}{AJ:
-%% conditioning?} As it was observed in the comparison between correlation and
-%% partial correlation, it screens indirect links in the inferred network.
-%% \textcolor{red}{AJ: I don't understand the link with GENIE3} Second, the number
-%% of small trees need to be much higher than deep trees in order to observe - and
-%% evaluate - all pairs.  However, as suggested by \cite{louppe2014understanding},
-%% limiting the maximal depth of trees may help to improve the variable importance
-%% computing, i.e. inferring the degree of association. \textcolor{red}{AJ: there
-%% is no explanation of why it would be better apart for computational reason.}
-%% Therefore a trade-off  of the maximal depth may give the best of both worlds.
-%% \textcolor{red}{AJ:  Which tradeoff? Which worlds?}
-
-%\subsection*{ROC versus PR curves.}
-
-%% The best method only infers the \textbf{undirected} network by giving the same
-%% degree of association to both edges $(i,j)$ and $(j,i)$. This is quite
-%% surprising considering the problem statement. Trying to direct links could be
-%% more penalizing than rewarding. For example, symmetrizing the degree of
-%% association matrix does not necessarily degrade AUPRC and AUROC.
-
-%% If the inferred network corresponds to the undirected network, it would
-%% already yield high AUROC score for instance $\approx 0.996$ on
-%% \textit{normal-1}. Infering edge directivity is likely to be counter-
-%% productive or yield small gain. By contrast, the same experiment with AUPRC
-%% would yield a score of $\approx 0.789$ on \textit{normal-1}. Thus inferring
-%% correctly directivity would be more rewarding in AUPRC term.
-
-%% % Interestingly, methods that takes into account directivity, namely GTE and
-%% % GENIE3, improve their AUROC and AUPRC by giving the same way to directed edges.
-%% % (in particular see GTE and GTE(undirected) in Figure \ref{fig:pr_curve}
-%% % \textcolor{red}{AJ: Figure \ref{fig:curves}  contradicts this message,
-%% % especially pr-curve. AS:And now?} and Table \ref{tab:tab1} in Appendix \textcolor{red}{REF}).
-%% % Trying to detect the link direction is more penalizing than rewarding.
-
-%% The area under the ROC curve is not a consistent metric with respect to the
-%% problem statement. A clear hierarchy is also difficult to derive from ROC
-%% curves as shown on Figure \ref{fig:roc_curve}. We advice to avoid the AUROC for
-%% the assessment of network inference method. An alternative would be to assess
-%% network inference using the area under the precision-recall curve (AUPRC).
-%% Those conclusions are in line with \cite{schrynemackers2013protocols}.
 
@@
 \clearpage
-
-% We allow the bibliography to be added on top of the 6 pages.
-% Supplementary material may be added in the form or a URL pointed to from
-% the paper.
 
@@
 different steps of our proposal.
-
-% Let us remark that tuning
-% was mainly done on the \textit{normal-1} and \textit{normal-4}
-% datasets, which explains why these two networks are slightly better
-% retrieved than the others.
 
@@
 
-%% two composed filtering functions in
-%% order (i) to remove noise induced by light scattering artifact, (ii) to take
-%% into account the slow decay of fluorescence signal and (iii) to reduce the
-%% importance of global high activity in the network. However, in order to win the
-%% challenge, we have heavily optimized several different, but yet similar,
-%% filtering composed function. On the one hand, each part of the composed
-%% functions is optimized to maximize the ROC AUC (e.g., $w^*$). On the other
-%% hand, we introduce new functions (e.g., $f_3$ and $f_4$) leading to alternative
-%% composed functions. They might lead to worse ROC AUC when taken individually
-%% but they improve the overall ROC AUC when taking as a part of the averaging
-%% approach.
-
-% Taken individually, those composed functions in
-% conjunction with partial correlation might lead to worse AUROC, but improved
-% whenever they are averaged.
-
-%% Besides filters $f_1$ and $f_2$ respectively defined by equations \ref{eq:symetric-median}
-%% and \ref{eq:weighted-asymetric-median}, we also consider two
-%% other low-pass filters
-%% \begin{align}
-%% f_3(x^t_i) &= x^{t-1}_i + x^{t}_i + x^{t+1}_i + x^{t+2}_i, \label{eq:asymetric-median-forward} \\
-%% f_4(x^t_i) &=  x_i^t + x^{t+1}_i  + x^{t+2}_i + x^{t+3}_i. \label{eq:asymetric-median}
-%% \end{align}
-
-%% After the hard thresholded filter $h$, they were significant differences in
-%% peak magnitudes. Since time series $x_i^t$  were mainly between 0 and 1,
-%% we smoothened these differences in peak magnitudes through
-%% \begin{align}
-%% p(x^t_i) = (x_i^t)^c
-%% \end{align}
-%% yielding slightly better AUROC with $c=0.9 \in (0, 1)$.
-
-%% After filter $p$, we applied a filter $w^*$ similar to $w$, whose goal is also
-%% to magnify the importance of spikes that occur in case of low global activity.
-%% Instead of equation \ref{eq:magnify-filter}, we had
-%% \begin{align}
-%%  w^*(x^{t}_i) &= {(x^{t}_i + 1 )^{\left (1 + \frac{1}{\sum_{j} x^{t}_j}\right )}}^{k(\sum_{j} x^{t}_j)}
-%% \end{align}
-%% where the function $k$ is a piecewise linear function optimized for each filter
-%% $f_1$, $f_2$, $f_3$ and $f_4$. By comparison, the filter $w$ used the following
-%% function $k(\sum_{j} x^{t}_j) = 1$. For more details on this aspect, we refer
-%% the reader to the implementation \footnote{available on
-%% \url{https://github.com/asutera/kaggle- connectomics}.}.
-
 \subsection{Weighted average of partial correlation statistics}
@@
 improve performance with respect to using $f_1$ and $f_2$ only.
-
-%% Given the unequal AUROC performance of $f_1$, $f_2$, $f_3$ and $f_4$, the
-%% contribution of each filter in the degree of association between two neurons
-%% was chosen as to maximize the AUROC on \textit{normal-1} and is function of
-%% their individual performance. By comparison in the simple method, each filter
-%% $f_1$ and $f_2$ were given equal weight.
 
@@
 
-%%% SHOW DIFFERENTS COMPOSED FUNCTION
-
-% Theses filters lead, taken individually, to worse performances  than filters
-% $f_1$ and $f_2$ but averaging the results of all low-pass filters leads to better ROC AUC.
-
 As reported in Table~\ref{tab:f3f4}, averaging over all low-pass filters leads
@@
 \begin{table}[ht]
-%\caption{Evaluation of different methods on the four \textit{normal} datasets\label{tab:comparison}}
 \caption{Performance on \textit{normal-1, 2, 3, or 4} with partial correlation with different averaging approaches.}
@@
 \label{tab:directivity}
-
-%\caption{Evaluation of different methods on the four \textit{normal} datasets\label{tab:comparison}}
 \centering
@@
 \hline
-\hline
 Averaging     & 0.947 & 0.943 & 0.920 & 0.942 & 0.959 & 0.934 \\
@@
 
-\section{About the number of principal components}
+\section{On the selection of the number of principal components}
 \label{app:pca}
 
-The main idea of principal component analysis (PCA) is to reduce the
-dimensionality of a dataset whose variables are interrelated
-\citep{jolliffe2005principal}. It consists in finding a new set of
-uncorrelated variables, denoted as principal components, where the most
-principal components, assuming an order between the components, hold most of the variance of the data scattered in all the original variables.
+The connectomes, defined by the graph $G = (V, E)$,  can be represented by an
+adjacency matrix $A: a_{i,j} = \mathbb{1}((i, j) \in E)$. The matrix can be
+decomposed through a singular value decomposition (SVD) or principal components
+analysis (PCA) as to determine a set of independent linear combinations of the
+variable \citep{alter2000singular} or respectively a reduced  set of linear
+combination combine which maximize the explained variance of the data
+\citep{jolliffe2005principal}. Otherwise said, both SVD and PCA aims at finding
+a reduced set of neurons whose activity can explain the rest of the network.
+Note that those two methods while having slightly different objective are
+related.
 
-Figure~\ref{fig:pca} shows the explained variance (ratio) by compoments and gives a hint about the number of uncorrelated variables required to
-explain all - or, at least, the majority of -  the variation in the original data.
+From all the available datasets, one can study the distribution of eigen value
+obtained from PCA and SVD decomposition by sorting them in descending order of
+magnitude as illustrated on Figure \ref{fig:pca}. For both methods, the  200
+lowest eigen values are zero. Thus, the behavior of the network could be
+explained by 800 linear combination of the variables which could be explained
+by the redundancy and relation between the neurons.
 
-The singular value decomposition (SVD) relies on the fact that every matrix -
-not only square matrices - can be decomposed into a diagonal nonnegative
-matrix with the help of two unit matrices \citep{alter2000singular}.
-
-The terms of the diagonal matrix can be used to determine the fraction of the
-overall information hold by the components in the decomposition and therefore
-give the relative significance of the components \citep{alter2000singular}.
-Figure~\ref{fig:SVD} displays the singular value ratio of all networks in the
-challenge.
-
-Obvioulsy, Figure~\ref{fig:pca} shows that for both approaches only 800
-components are required to explain the (majority of) network structures.
-There, we can conclude that the value of $M$ should be set to 800, or equivalently, to $0.8 p$.
-
-Therefore, the value of the parameter $M$ is immediat and should be clearly
-set to $800$, or equivalently to $0.8p$. \\
+In the context of the challenge, we exploit this information to keep only  $M =
+0.8p$ components when computing the partial correlation statistics. Without
+those comparative network, one could perform a similar decomposition analysis
+on the data.
 
@@
 \subfigure[SVD]{\includegraphics[width=0.45\textwidth]{singular_values_all} \label{fig:SVD}}
-\caption{Explained variance ratio by number of principal components (left) and singular value ratio by number of principal components (right) for all networks.}
+\caption{Explained variance ratio by index of principal components (left) and singular value ratio by index of principal components (right) for all networks sorted by descending order of magnitude.}
 \label{fig:pca}
@@
 
-% \section{Computational information}
+\section{Summary Table}
 
-% To perform experiments, we used a Macbook Pro (2014) with a ram memory 16Go 1600 MHz DDR3 and a processor 2.3GHz Intel Core i7.
-
-% In order to compare the execution time with other methods, it takes about xx and xx hours to compute respectively GTE and GENIE3.
-However, GENIE3 is highly parallelizable (by taking several smaller forests or applying GENIE3 on subsets of variables) and the execution time can be significantly reduced.
-
-% \begin{table}[h]
-% \caption{Execution time, scalability, memory requirements for methods described in the paper. \textcolor{red}{to do.}}
-% \label{tab:results_appendix}
-% \centering
-% \small
-% \begin{tabular}{| l|c|c|} \hline
-% Methods & Execution time  & Memory requirements \\ \hline
-% PC & & $\sim$5Go\\
-% Averaging & & \\
-% Full Method & & \\ \hline
-% \end{tabular}
-% \end{table}
+\begin{table}[h]
+\caption{Connectomics challenge summary.}
+\label{tab:summary}
+\centering
+\small
+\begin{tabular}{| l|c|} \hline
+Team Name & The AAAGV Team \\ \hline
+Private leaderboard position & \nth{1} \\ \hline
+Private leaderboard performance & 0.94161 \\ \hline
+Private leaderbard performance of the winner & / \\ \hline
+\end{tabular}
+\end{table}
 

### 2014-07-28 article.tex
pre-modification

@@
    \addr Department of EE and CS \& GIGA-R, University of Li\`ege, Belgium}
-
-% \author{\Name{Antonio Sutera,
-%     Arnaud Joly,
-%         Vincent François-Lavet,\\
-%         Aaron Qiu,
-%         Gilles Louppe,
-%         Damien Ernst,
-%         Pierre Geurts}
-%   \Email{a.sutera@ulg.ac.be}\\
-%   \addr Department of EE and CS \& GIGA-R, University of Li\`ege, Belgium}
-
-% \jmlrauthors{A. Sutera et al}
-% \shortauthor{A. Sutera et al.}
 
@@
 Section~\ref{sec:filter} describes the signal processing methods applied on
-fluorescent calcium time series; Section\ref{sec:inference} then presents the
+fluorescent calcium time series; Section \ref{sec:inference} then presents the
 proposed approach and its theoretical properties; Section~\ref{sec:results}
@@
 \begin{align}
-% symmetrical median filter
 f_1(x^t_i) &= x^{t-1}_i + x^t_i + x^{t+1}_i, \label{eq:symetric-median} \\
-% asymmetrical weighted median
 f_2(x^t_i) &= 0.4 x^{t-3}_i + 0.6 x^{t-2}_i + 0.8 x^{t-1}_i + x_i^t.
@@
 
-% No time assumption
-
 Our procedure to infer connections between neurons first assumes that
@@
 \dots, X_p\}$ that are independently drawn from the same time invariant
-joint probability distribution $P_X$. %% Or, say otherwise, we assume
-%% that there exists a probability distribution $P_X$ such that the
-%% fluorescence concentrations at a particular time $t$ can be seen as an
-%% independent realization of $P_X$.
+joint probability distribution $P_X$. 
 As a consequence, our inference method does not exploit the time
@@
 the filters).
-
-% partial correlation: definition + motivation
 
@@
 \citep{de2004discovery,Schafer:2005}.
-
 Note that the partial correlation statistic is symmetric
@@
 \begin{table}[t]
+
 \caption{Top: Performance on \textit{normal-1,2,3,4} with partial correlation and different filtering functions.
@@
 \caption{ROC (left) and PR (right) curves on \textit{normal-2} for the compared methods. Areas under the curves are reported in the legend.}
-
 \label{fig:curves}
@@
 \label{tab:directivity}
+
 \centering
@@
 \hline
+\hline
 Averaging     & 0.947 & 0.943 & 0.920 & 0.942 & 0.959 & 0.934 \\
@@
 
-The connectomes, defined by the graph $G = (V, E)$,  can be represented by an
-adjacency matrix $A: a_{i,j} = \mathbb{1}((i, j) \in E)$. The matrix can be
-decomposed through a singular value decomposition (SVD) or principal components
-analysis (PCA) as to determine a set of independent linear combinations of the
-variable \citep{alter2000singular} or respectively a reduced  set of linear
+The (true) network, seen as a matrix, can be decomposed through a singular value decomposition (SVD) or principal component
+analysis (PCA) as to respectively determine a set of independent linear combinations of the
+variable \citep{alter2000singular} or a reduced set of linear
 combination combine which maximize the explained variance of the data
-\citep{jolliffe2005principal}. Otherwise said, both SVD and PCA aims at finding
-a reduced set of neurons whose activity can explain the rest of the network.
-Note that those two methods while having slightly different objective are
-related.
+\citep{jolliffe2005principal}.
+Since SVD and PCA are related, they can be defined by the same goal: both aim at finding a reduced set of neurons, known as components, whose activity can explain the rest of the network.
 
-From all the available datasets, one can study the distribution of eigen value
-obtained from PCA and SVD decomposition by sorting them in descending order of
-magnitude as illustrated on Figure \ref{fig:pca}. For both methods, the  200
-lowest eigen values are zero. Thus, the behavior of the network could be
-explained by 800 linear combination of the variables which could be explained
-by the redundancy and relation between the neurons.
+The distribution of compoment eigen values obtained from PCA and SVD decompositions can be studied by sorting them in descending order of magnitude as illustrated on Figure~\ref{fig:pca}.
+It can be seen that some component eigen values are zero implying that the behavior of the network could be explained by a subset of neurons because of the
+redundancy and relations between the neurons. For all datasets, the eigen value distribution is exactly the same.
 
-In the context of the challenge, we exploit this information to keep only  $M =
-0.8p$ components when computing the partial correlation statistics. Without
-those comparative network, one could perform a similar decomposition analysis
-on the data.
+In the context of the challenge, we observe that only $800$ components seem to be necessary and we exploit this when computing partial correlation statistics.
+Therefore, the value of the parameter $M$ is immediat and should be clearly set to $800$, or equivalently to $0.8p$.
+
+Note that if the true network is not available, similar decomposition analysis could be carried on the infered network or on the data directly.\\
 
@@
 \subfigure[SVD]{\includegraphics[width=0.45\textwidth]{singular_values_all} \label{fig:SVD}}
-\caption{Explained variance ratio by index of principal components (left) and singular value ratio by index of principal components (right) for all networks sorted by descending order of magnitude.}
+\caption{Explained variance ratio by number of principal components (left) and singular value ratio by number of principal components (right) for all networks.}
 \label{fig:pca}

### 2014-07-28 article.tex
after professional editor corrections

@@
 \begin{abstract}
-In this work, we propose a simple, but yet efficient method for the problem of
+In this work, we propose a simple yet effective solution to the problem of
 connectome inference in calcium imaging data. The proposed algorithm consists of
@@
 Second, inferring the degree of association between neurons from partial
-correlation statistics. This paper summarizes the methodology that led us to
-win the Connectomics Challenge, proposes a simplified version of our method and
-finally discusses our results with respect to other inference methods.
+correlation statistics. This paper summarises the methodology that led us to
+win the Connectomics Challenge, proposes a simplified version of our method, and
+finally compares our results with respect to other inference methods.
 \end{abstract}
@@
 
-The human brain is a complex biological
-organ made of about 100 billion of neurons, each connected to 7000 other neurons on
-average \citep{pakkenberg2003aging}. Unfortunately, direct observation of the connectome, the wiring
-diagram of the brain, is not yet technically feasible. Without being perfect,
-calcium imaging currently allows the real-time and simultaneous observation of
-neuron activities from thousands of neurons, producing individual time series
-representing their fluorescence intensity. From these data, the connectome
-inference problem amounts to retrieving the synaptic connections between
-neurons on the basis of the fluorescence time series. This
-problem is often difficult because of experimental issues, including
-masking effects (i.e., some of the neurons are not observed or confounded with others), the low sampling rate of the optical device with respect to the
-neural activity speed or the slow decay of fluorescence.
+The human brain is a complex biological organ made of about 100 billion of
+neurons, each connected to, on average, 7,000 other neurons
+\citep{pakkenberg2003aging}. Unfortunately, direct observation of the
+connectome, the wiring diagram of the brain, is not yet technically feasible.
+Without being perfect, calcium imaging currently allows for real-time and
+simultaneous observation of neuron activity from thousands of neurons,
+producing individual time-series representing their fluorescence intensity.
+From these data, the connectome inference problem amounts to retrieving the
+synaptic connections between neurons on the basis of the fluorescence time-
+series. This problem is difficult to solve because of experimental issues,
+including masking effects (i.e., some of the neurons are not observed or
+confounded with others), the low sampling rate of the optical device with
+respect to the neural activity speed, or the slow decay of fluorescence.
 
 Formally, the connectome can be represented as a directed graph $G=(V,E)$,
-where $V$ is a set of $p$ nodes, representing neurons, and $E \subseteq
-\left\{(i, j) \in V \times V\right\}$ is a set of edges, representing direct
+where $V$ is a set of $p$ nodes representing neurons, and $E \subseteq
+\left\{(i, j) \in V \times V\right\}$ is a set of edges representing direct
 synaptic connections between neurons. Causal interactions are expressed by the
@@
 
-In this paper, we present a simplified -- yet nearly as good -- version of the
+In this paper, we present a simplified - and almost as good - version of the
 winning method\footnote{Code available at \url{https://github.com/asutera/kaggle-connectomics}} of the Connectomics
@@
 Section~\ref{sec:filter} describes the signal processing methods applied on
-fluorescent calcium time series; Section \ref{sec:inference} then presents the
+fluorescent calcium time series; Section\ref{sec:inference} then presents the
 proposed approach and its theoretical properties; Section~\ref{sec:results}
 provides an empirical analysis and comparison with other network inference
-methods, while Section~\ref{sec:conclusion} finally discusses our work and
-provides further research directions. Additionally,
-Appendix~\ref{app:optimized} further describes, in all details, our actual
-winning method, giving slightly better results than the method presented in
-the paper, at the price of parameter tuning. Appendix~\ref{app:supp} provides supplementary results on other datasets.
+methods, while finally, in Section~\ref{sec:conclusion} we discuss our work and
+provide further research directions. Additionally,
+Appendix~\ref{app:optimized} further describes, in full detail, our actual
+winning method which gives slightly better results than the method presented in
+this paper, at the cost of parameter tuning. Appendix~\ref{app:supp} provides supplementary results on other datasets.
 
@@
 
-Under the simplifying assumption that neurons are on-off units, characterized
-by short periods of intense activities, or peaks, and longer periods of
-inactivity, the first part of our algorithm consists in cleaning the raw
+Under the simplifying assumption that neurons are on-off units, characterised
+by short periods of intense activity, or peaks, and longer periods of
+inactivity, the first part of our algorithm consists of cleaning the raw
 fluorescence data.
 More specifically, time series are processed using standard
-signal processing filters in order to (i) remove noise mainly due to fluctuations independent of calcium, calcium fluctuations independent of spiking activity, calcium fluctuations in nearby tissues that have been mistakenly captured, or simply by the imaging process (ii) to account for fluorescence low decay and (iii) to reduce the importance of
-global high activity in the network. The overall process is illustrated in
+signal processing filters in order to : (i) remove noise mainly due to fluctuations independent of calcium, calcium fluctuations independent of spiking activity, calcium fluctuations in nearby tissues that have been mistakenly captured, or simply by the imaging process ; (ii) to account for fluorescence low decay ; and (iii) to reduce the importance of
+high global activity in the network. The overall process is illustrated in
 Figure~\ref{fig:filtered-signal}.
@@
 usually affect the quality of the recording~\citep{lichtman2011big}.
-Accordingly, the first step of our pipeline is to smoothen the signal, using
+Accordingly, the first step of our pipeline is to smoothe the signal, using
 one of the following low-pass filters for filtering out high frequency noise:
@@
 \end{align}
-These filters are standard in the signal processing field \citep{kaiser1977data, oppenheim1983signals}. For the sake of illustration, the effect of the filter $f_1$ on the signal
+These filters are standard in the signal processing field \citep{kaiser1977data, oppenheim1983signals}. For the purposes of illustration, the effect of the filter $f_1$ on the signal
 is shown in Figure \ref{fig:lp_curve}.
@@
 Furthermore, short spikes, characterized by a high
-frequency, can be seen as an indirect indicator of neuron communication while low frequencies of the signal mainly correspond to the slow
+frequency, can be seen as an indirect indicator of neuron communication, while low frequencies of the signal mainly correspond to the slow
 decay of fluorescence. To have a signal that only has high magnitude around instances where the spikes occur, the second step of our pipeline transforms the time series into its backward
@@
 To filter out small variations in the signal obtained after applying the
-function $g$ as well as to eliminate negative values, we use the following
+function $g$, as well as to eliminate negative values, we use the following
 hard-threshold filter
@@
 yielding Figure \ref{fig:threshold_curve} where $\tau$ is the threshold parameter and $\mathbb{1}$ is the indicator function.
-As we can see, the processed signal only contains clean spikes.
+As can be seen, the processed signal only contains clean spikes.
 
 The objective of the last step of our filtering procedure is to decrease the
-importance of spikes that occur when there is a high global activity in the
+importance of spikes that occur when there is high global activity in the
 network with respect to  spikes that occur during normal activity. Indeed, we
 have conjectured that when a large part of the network is firing, the rate at
-which observations are made is not high enough for being able to detect
+which observations are made is not high enough to be able to detect
 interactions, and that it would therefore be preferable to lower their
-importance by changing appropriately their magnitude. Additionally, it is
-well-known that neurons may also spike because of a global high activity
+importance by changing their magnitude appropriately. Additionally, it is
+well-known that neurons may also spike because of a high global activity
 \citep{stetter2012model}. In such  context, detecting pairwise neuron
@@
 \end{align}
-whose effect is to magnify the importance of spikes that occur in case of low
-global activity (measured by $\sum_{j} x^{t}_j$), as observed for instance
-around $t=4\text{s}$ in Figure~\ref{fig:weight_curve}. Note that the particular case where there
+whose effect is to magnify the importance of spikes that occur in cases of low
+global activity (measured by $\sum_{j} x^{t}_j$), as observed, for instance,
+around $t=4\text{s}$ in Figure~\ref{fig:weight_curve}. Note the particular case where there
 is no activity, i.e., $\sum_{j} x^{t}_j = 0$, is solved by setting $w(x^{t}_i)
@@
 
-To summarize, the full signal processing pipeline of our simplified approach is defined by the composed function $w \circ h \circ g \circ
+To summarise, the full signal processing pipeline of our simplified approach is defined by the composed function $w \circ h \circ g \circ
 f_1$ (resp. $f_2$). When applied to the raw signal of Figure
@@
 the (filtered) fluorescence concentrations of all $p$ neurons at each
-time point can be modeled as a set of random variables $X = \{X_1,
-\dots, X_p\}$ that are independently drawn from the same time invariant
+time point can be modelled as a set of random variables $X = \{X_1,
+\dots, X_p\}$ that are independently drawn from the same time-invariant
 joint probability distribution $P_X$. 
-As a consequence, our inference method does not exploit the time
-ordering of the observations (although time ordering is exploited by
+As a consequence, our inference method does not exploit the time-
+ordering of the observations (although time-ordering is exploited by
 the filters).
@@
 \setminus\{X_i,X_j\}$. Partial correlation thus measures conditional
-dependencies between variables. It should thus naturally only detect direct associations
+dependencies between variables ; therefore it should naturally only detect direct associations
 between neurons and filter out spurious indirect effects. The interest
@@
 direction of the interactions between neurons. We will see in
-Section~\ref{sec:results} why this only affects slightly its
+Section~\ref{sec:results} why this only slightly affects its
 performance, with respect to the metric used in the Connectomics
-challenge.
+Challenge.
 
-Practically, the computation of all $p_{i,j}$ coefficients using Equation
+Practically speaking, the computation of all $p_{i,j}$ coefficients using Equation
 \ref{eq:inverse} requires the estimation of the covariance matrix $\Sigma$
-and then computing its inverse. Given that we have typically more
+and then computing its inverse. Given that typically we have more
 samples than neurons, the covariance matrix can be inverted in a
@@
 
-Finally, let us note that the performance of our simple method appears to
+Finally, it should be noted that the performance of our simple method appears to
 be quite sensitive to the values of parameters (e.g., choice of $f_1$ or $f_2$
@@
 We report here experiments on the \textit{normal-1,2,3}, and \textit{4}
-datasets provided by the organizers of the Connectomics challenge (see
+datasets provided by the organisers of the Connectomics Challenge (see
 Appendix~\ref{app:supp} for experiments on other datasets). Each of
 these datasets is obtained from the simulation \citep{stetter2012model} of
-different neural networks of 1000 neurons and about 15000 edges each (i.e., a
+different neural networks of 1,000 neurons and approximately 15,000 edges (i.e., a
 network density of about 1.5\%). Each neuron is described by a calcium
-fluorescence time series of length $T=179500$. All inference methods compared
+fluorescence time-series of length $T=179500$. All inference methods compared
 here provide a ranking of all pairs of neurons according to some association score. To assess the quality of this ranking, we compute both ROC and
-precision-recall curves against the ground truth network, which are summarized
-using the area under the curve and respectively  denoted AUROC and AUPRC. Only
-the AUROC score was used to rank the challenge participants but the precision-recall curve has been shown to be a more sensible metric for network
+precision-recall curves against the ground-truth network, which are represented by
+the area under the curves and respectively  denoted AUROC and AUPRC. Only
+the AUROC score was used to rank the challenge participants, but the precision-recall curve has been shown to be a more sensible metric for network
 inference, especially when network density is small (see e.g.,
 \cite{schrynemackers2013protocols}). Since neurons are not self-connected in
-the ground truth networks (i.e., $(i, i) \not \in E, \forall i \in V$), we
-have manually set the score of such edges to the minimal possible association
+the ground-truth networks (i.e., $(i, i) \not \in E, \forall i \in V$), we
+have manually set the score of such edges to the minimum possible association
 score before computing ROC and PR curves.
@@
 The top of Table \ref{tab:comparison} reports AUROC and AUPRC for all
-four networks using in each case partial correlation with different
+four networks using, in each case, partial correlation with different
 filtering functions. Except for the last two rows that use PCA, the
@@
 results clearly show the importance of the filters. AUROC increases in
-average from 0.77 to 0.93. PCA does not really affect AUROC scores but
+average from 0.77 to 0.93. PCA does not really affect AUROC scores, but
 it significantly improves AUPRC scores. Taking the average over
@@
 (see Appendix \ref{app:optimized} for all details). Although this
-tuning was decisive to obtain the best performance at the challenge,
-it does not significantly improve neither AUROC nor AUPRC.
+tuning was decisive to obtain the best performance in the challenge,
+it does not significantly improve either AUROC or AUPRC.
 
@@
 
-In the bottom of Table \ref{tab:comparison}, we provide as a comparison the
+At the bottom of Table \ref{tab:comparison}, we provide as a comparison the
 performance of three other methods: standard (Pearson) correlation (PC),
-generalized transfer entropy (GTE), and GENIE3. ROC and PR curves on the
+generalised transfer entropy (GTE), and GENIE3. ROC and PR curves on the
 \textit{normal-2} network are shown for all methods in Figure
@@
 can predict the direction of the edges. GENIE3 \citep{huynhthu2010inferring} is
-a gene regulatory network inference method that was the best performer of the
+a gene regulatory network inference method that was the best performer in the
 DREAM5 challenge \citep{marbach2012}. When transposed to neural networks, this
-method uses as a confidence score for the edge going from neuron $i$ to neuron
-$j$ the importance score of variable $X_i$ in a Random Forest model trying to
-predict $X_j$ from all variables in $X\setminus X_j$. To reduce the
-computational cost of this method, we had however to limit each tree in the
-Random Forest model to a maximum depth of 3. This constraint potentially
-severely affects the performance of this method with respect to the use of
-fully grown trees. PC and GENIE3 were applied on the time series filtered using the functions $w\circ h\circ g$ and $h\circ g\circ f_1$ (which
-gave the best performance), respectively. For GENIE3, we built 10000 trees per neuron and we
+method uses the importance score of variable $X_i$ in a Random Forest model trying to
+predict $X_j$ from all variables in $X\setminus X_j$ as a confidence score for the edge going from neuron $i$ to neuron
+$j$. However, to reduce the
+computational cost of this method, we had to limit each tree in the
+Random Forest model to a maximum depth of 3. This constraint has a potentially
+severe effect on the performance of this method with respect to the use of
+fully-grown trees. PC and GENIE3 were applied to the time-series filtered using the functions $w\circ h\circ g$ and $h\circ g\circ f_1$ (which
+gave the best performance), respectively. For GENIE3, we built 10,000 trees per neuron and we
 used default settings for all other parameters (except for the maximal tree
 depth). For GTE, we reproduced the exact same setting (conditioning level and
-pre-processing) that was used by the organizers of the challenge.
+pre-processing) that was used by the organisers of the challenge.
 
@@
 expected, Pearson correlation performs very poorly in terms of AUPRC. GTE and
-GENIE3 work much better but these two methods are nevertheless clearly below
+GENIE3 work much better, but these two methods are nevertheless clearly below
 partial correlation. Among these two methods, GTE is slightly better in terms
@@
 be a disadvantage with respect to GTE and GENIE3. Although partial correlation
-scores each edge and its opposite similarly, it can reach precision values
+scores each edge, and its opposite, similarly, it can reach precision values
 higher than 0.5 (see Figure \ref{fig:curves}(b)), suggesting that it mainly ranks high
@@
 of connectome inference from calcium imaging data. Our approach consists of two
-steps: (i) processing fluorescence data to detect neural peak activities and
+steps: (i) processing fluorescence data to detect neural peak activities; and
 (ii) inferring the degree of association between neurons from partial
@@
 network inference methods while its optimized version proved to be the best method
-on the Connectomics challenge. Given its simplicity and good performance, we
+on the Connectomics Challenge. Given its simplicity and good performance, we
 therefore believe that the methodology presented in this work
-would constitute a solid and easily reproducible baseline for further work in
+would constitute a solid and easily-reproducible baseline for further work in
 the field of connectome inference.
@@
 \paragraph{Acknowledgments}
-A. Joly and G. Louppe are research fellows of the FNRS, Belgium.  A. Sutera is
-recipient of a FRIA fellowship of FRS-FNRS, Belgium. This work is supported by
+A. Joly and G. Louppe are research fellows of the FNRS, Belgium.  A. Sutera is a
+recipient of an FRIA fellowship of FRS-FNRS, Belgium. This work is supported by
 PASCAL2 and the IUAP DYSCO, initiated by the Belgian State, Science Policy
@@
 This section provides a detailed description of the method specifically tuned
-for the Connectomics challenge. We restrict our description to the
+for the Connectomics Challenge. We restrict our description to the
 differences with respect to the simplified method presented in the main
@@
 should work equally well on new independent datasets. We nevertheless provide
-the tuned method here for reference purpose. Our implementation of the tuned
+the tuned method here for reference purposes. Our implementation of the tuned
 method is available at \url{https://github.com/asutera/kaggle-connectomics}.
@@
 \end{align}
-\item An additional filter $r$ is applied to smoothen differences in peak magnitudes
+\item An additional filter $r$ is applied to smoothe differences in peak magnitudes
   that might remain after the application of the hard-threshold filter $h$:
@@
 \end{align}
-where the function $k$ is a piecewise linear function optimized separately for
+where the function $k$ is a piecewise linear function optimised separately for
 each filter $f_1$, $f_2$, $f_3$ and $f_4$ (see the implementation for full
@@
 of the low-pass filter (among $\{f_1, f_2, f_3, f_4\}$).
-Like in the simplified method, we have averaged the partial correlation statistics obtained for all the pairs $(\tau,\mbox{low-pass filter}) \in \{0.100,0.101,\ldots,0.209\}\times \{f_1, f_2, f_3, f_4\}$.
+As in the simplified method, we have averaged the partial correlation statistics obtained for all the pairs $(\tau,\mbox{low-pass filter}) \in \{0.100,0.101,\ldots,0.209\}\times \{f_1, f_2, f_3, f_4\}$.
 
@@
 weights (i.e., resp. $0.383$ and $0.345$). These weights were chosen equal to the weights selected for the simplified method. In contrast, filters $f_3$
-and $f_4$ turn out to be individually less competitive and were therefore given
-smaller importance in the weighted average (i.e., resp. $0.004$ and $0.268$). Yet, as further shown in
-Section~\ref{sapp:results}, combining all $4$ filters proves to slightly
-improve performance with respect to using $f_1$ and $f_2$ only.
+and $f_4$ turn out, individually, to be less competitive and were therefore given
+less importance in the weighted average (i.e., resp. $0.004$ and $0.268$). Yet, as further shown in
+Section~\ref{sapp:results}, combining all $4$ filters proves to marginally
+improve performance with respect to using only $f_1$ and $f_2$.
 
@@
 connectome is a directed graph. It  could thus be beneficial to try to
-predict edge orientation. In this section, we present a heuristic that
-modifies the  $p_{ij}$ computed  by the  approach described  before to
-take into account directionality.
+predict edge orientation. In this section, we present an heuristic that
+modifies the  $p_{ij}$ computed  by the  approach described  before which
+takes into account directionality.
 
@@
 therefore indicates a directed link in the connectome from the first to
-the second neuron.  Given this observation, we have computed for every
-pair $(i,j)$ the term:
+the second neuron.  Given this observation, we have computed the following term for every
+pair $(i,j)$:
 \begin{align}
@@
 \end{align}
-where $\phi_3 >0$ is another parameter. We found out that this new
-matrix $r$ was not giving good results, probably due to the fact that
-directivity was not well enough rewarded in the challenge.
+where $\phi_3 >0$ is another parameter. We discovered that this new
+matrix $r$ was not providing good results, probably due to the fact that
+directivity was not rewarded well enough in the challenge.
 
@@
 information about directionality contained in the matrix $z$. One of
-those ways that gave good performance was to use as association
+those ways that gave good performance was to use as an association
 matrix:
@@
 with  $weight$ chosen close to 1 ($weight=0.997$). Note that with
-values for $weight$ close to 1,   matrix $q$ only slightly uses the
-information about directivity contained in $z$ to modify the  partial
+values for $weight$ close to 1,   matrix $q$ only uses the
+information to a minimum about directivity contained in $z$ to modify the  partial
 correlation matrix $p$. We tried smaller values for $weight$ but those
-were leading to worse results.
+provided poorer results.
 
@@
 to better AUROC scores than averaging over only two low-pass filters, i.e., $f_1$ and
-$f_2$. It however slightly deteriorates AUPRC.
+$f_2$. However this slightly reduces AUPRC.
 
@@
 
-We report in this appendix the performance of the different methods compared
-in the paper on 6 additional datasets provided by the challenge
-organizers. These datasets, corresponding each to networks of 1000 neurons, are similar to
+In this appendix we report the performance of the different methods compared
+in the paper on 6 additional datasets provided by the Challenge
+organisers. These datasets, corresponding each to networks of 1,000 neurons, are similar to
 the \textit{normal} datasets except for one feature:
 \begin{description}
-\item[lowcon:] Similar network but with a lower number of connections per neuron on average.
-\item[highcon:] Similar network but with a higher number of connections per neuron on average.
-\item[lowcc:] Similar network but with a lower clustering coefficient on average.
-\item[highcc:] Similar network but with a higher clustering coefficient on average.
+\item[lowcon:] Similar network but on average with a lower number of connections per neuron.
+\item[highcon:] Similar network but on average with a higher number of connections per neuron.
+\item[lowcc:] Similar network but on average with a lower clustering coefficient.
+\item[highcc:] Similar network but on average with a higher clustering coefficient.
 \item[normal-3-highrate:] Same topology as \textit{normal-3} but with a higher firing frequency, i.e., with highly active neurons.
-\item[normal-4-lownoise:] Same topology as \textit{normal-4} but with a better signal to noise ratio.
+\item[normal-4-lownoise:] Same topology as \textit{normal-4} but with a better signal-to-noise ratio.
 \end{description}
 
-Results of several methods on these 6 datasets are provided in
+The results of several methods applied to these 6 datasets are provided in
 Table~\ref{tab:results_appendix}. They confirm what we observed on the
@@
 i.e.,``Full method'', clearly outperform other network inference methods on all
-datasets. PC is close to GENIE3 and GTE but still slightly worse. GENIE3
-performs better than GTE most of the times.
+datasets. PC is close to GENIE3 and GTE, but still slightly worse. GENIE3
+performs better than GTE most of the time.
 Note that the "Full method" reported in this table does not use Equation \ref{eqn:qij} to slightly correct the values of $p_{i,j}$  to take into account directivity.
@@
 The (true) network, seen as a matrix, can be decomposed through a singular value decomposition (SVD) or principal component
-analysis (PCA) as to respectively determine a set of independent linear combinations of the
-variable \citep{alter2000singular} or a reduced set of linear
-combination combine which maximize the explained variance of the data
+analysis (PCA), so as to respectively determine a set of independent linear combinations of the
+variable \citep{alter2000singular}, or a reduced set of linear
+combinations combine, which then maximize the explained variance of the data
 \citep{jolliffe2005principal}.
@@
 
-The distribution of compoment eigen values obtained from PCA and SVD decompositions can be studied by sorting them in descending order of magnitude as illustrated on Figure~\ref{fig:pca}.
-It can be seen that some component eigen values are zero implying that the behavior of the network could be explained by a subset of neurons because of the
+The distribution of compoment eigen values obtained from PCA and SVD decompositions can be studied by sorting them in descending order of magnitude, as illustrated in Figure~\ref{fig:pca}.
+It can be seen that some component eigen values are zero, implying that the behaviour of the network could be explained by a subset of neurons because of the
 redundancy and relations between the neurons. For all datasets, the eigen value distribution is exactly the same.
@@
 In the context of the challenge, we observe that only $800$ components seem to be necessary and we exploit this when computing partial correlation statistics.
-Therefore, the value of the parameter $M$ is immediat and should be clearly set to $800$, or equivalently to $0.8p$.
+Therefore, the value of the parameter $M$ is immediate and should be clearly set to $800$ ($=0.8p$).
 
-Note that if the true network is not available, similar decomposition analysis could be carried on the infered network or on the data directly.\\
+Note that if the true network is not available, similar decomposition analysis could be carried on the inferred network, or on the data directly.
 

### 2014-07-28 article.tex
typo pdf

@@
 From these data, the connectome inference problem amounts to retrieving the
-synaptic connections between neurons on the basis of the fluorescence time-
-series. This problem is difficult to solve because of experimental issues,
+synaptic connections between neurons on the basis of the fluorescence time-series. This problem is difficult to solve because of experimental issues,
 including masking effects (i.e., some of the neurons are not observed or
@@
 Section~\ref{sec:filter} describes the signal processing methods applied on
-fluorescent calcium time series; Section\ref{sec:inference} then presents the
+fluorescent calcium time-series; Section \ref{sec:inference} then presents the
 proposed approach and its theoretical properties; Section~\ref{sec:results}
@@
 frequency, can be seen as an indirect indicator of neuron communication, while low frequencies of the signal mainly correspond to the slow
-decay of fluorescence. To have a signal that only has high magnitude around instances where the spikes occur, the second step of our pipeline transforms the time series into its backward
+decay of fluorescence. To have a signal that only has high magnitude around instances where the spikes occur, the second step of our pipeline transforms the time-series into its backward
 difference
@@
 joint probability distribution $P_X$. 
-As a consequence, our inference method does not exploit the time-
-ordering of the observations (although time-ordering is exploited by
+As a consequence, our inference method does not exploit the time-ordering of the observations (although time-ordering is exploited by
 the filters).
@@
 generalised transfer entropy (GTE), and GENIE3. ROC and PR curves on the
-\textit{normal-2} network are shown for all methods in Figure
-\ref{fig:curves}. Pearson correlation measures the unconditional linear
+\textit{normal-2} network are shown for all methods in Figure\ref{fig:curves}. Pearson correlation measures the unconditional linear
 (in)dependence between variables and it should thus not be able to filter out

### 2014-07-28 article.tex
miss one hyphen

@@
 fluorescence data.
-More specifically, time series are processed using standard
+More specifically, time-series are processed using standard
 signal processing filters in order to : (i) remove noise mainly due to fluctuations independent of calcium, calcium fluctuations independent of spiking activity, calcium fluctuations in nearby tissues that have been mistakenly captured, or simply by the imaging process ; (ii) to account for fluorescence low decay ; and (iii) to reduce the importance of

### 2014-07-28 response.tex
last changes

@@
 \textbf{A}: The first low-pass filter is standard in the signal processing field while the second is designed to take into account the time.
-This second filter is hovewever quite classical.
+This second filter is however quite classical.
 We add justification and motivation in the paper.\\
@@
 The ``Full method'' needs the double of time (about 6 to 12 hours) and it requires a few hours more to take into account the edge directionality.
-GTE and GENIE3 take more time to compute than PC and they require about xx \textcolor{red}{(AS: Need AJ to know exactly the execution time)} hours and yy hours respectively.
-However, GENIE3 is highy parallelizable (by taking several smaller forests or applying GENIE3 on subsets of variables) and the execution time can be significantly reduced.
+GTE and GENIE3 take more time to compute than PC.
+However, GENIE3 is highy parallelizable (by taking several smaller forests or applying GENIE3 on variable subsets) and the execution time can be significantly reduced.
 
@@
 
-\textbf{A}: We are not sure what exactly suggests the reviewer but applying PCA before PC, GTE and GENIE3 is not straighforward.
+\textbf{A}: We are not sure what exactly suggests the reviewer but applying PCA before PC, GTE and GENIE3 is not straightforward.
 Let us note that for each method we choose the preprocessing which yields the best performance.\\

### 2014-07-28 article.tex
6 pages constraint + caps
last changes

@@
 \usepackage[super]{nth}
+\setlength{\textfloatsep}{15pt}
 
@@
 
-\vspace{-0.8cm}
+\vspace{-1cm}
 \begin{abstract}
@@
 \section{Experiments} \label{sec:results}
-
 \paragraph{Data and evaluation metrics.}
@@
 \end{tabular}
-
 \end{table}
@@
 as $0.995$ and an AUPRC of $0.789$.
-
 \begin{figure}[t]
@@
 \begin{table}[h]
- \caption{Connectomics challenge summary.}
+ \caption{Connectomics Challenge summary.}
  \label{tab:summary}
@@
  Private leaderboard performance & 0.94161 \\ \hline
- Private leaderbard performance of the winner & / \\ \hline
+ Private leaderboard performance of the winner & idem \\ \hline
  \end{tabular}

### 2014-09-01 interview/interview.tex
interview script

\documentclass[10pt,a4paper]{article}

% General packages
\usepackage[frenchb]{babel}
\usepackage{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{graphicx} % To include graphics
\usepackage{float}
\usepackage{multicol}

% Personnal packages
\usepackage{enumerate}
\usepackage{color}
%\usepackage{ifthen} % provides \ifthenelse test  
%\usepackage{xifthen} % provides \isempty test
\usepackage{algorithmicx} % provides algorithm environment 
\usepackage{algpseudocode} % provides pseudo-code
% Personnal functions

\newcommand{\todo}{\textcolor{red}{{\sc To Do } \\ }}
\newcommand{\todoon}[1]{{\textcolor{red}{{\sc To Do: #1}} \\ }}

\renewcommand{\paragraph}[1]{
\hspace{0.1cm} \\
 {\sc \textbf{#1}}

}
\newcommand{\nparagraph}[1]{\underline{#1}

}
\begin{document}

\begin{center}
{\Large Interview "Réflexions"}
\end{center}
\begin{description}
\item[Qui êtes-vous?]

L'équipe qui a remporté le challenge Connectomics est composée de 5 ingénieurs chercheurs de l'institut Montéfiore de l'Université de Liège. Il s'agit du département d'électricité, d'électronique et d'informatique de la faculté des Sciences appliquées. Notre équipe est en effet pluridisciplinaire car nous travaillons pour deux services différents: l'un est plus orienté sur le développement du réseau électrique du futur (smart grids), l'autre sur la compréhension et le développement d'algorithmes d'apprentissage automatique. Chacun a ses spécialités dans sa catégorie, ce qui a engendré et confronté des méthodologies de réfléxions différentes.

\item[Expliquez un peu la compétition que vous avez gagnée?]

Comme vous le savez sans doute, le cerveau humain fonctionne grâces aux nombreuses connexions qui relient un très grand nombre de neurones. Depuis des années, des chercheurs essayent de comprendre le cerveau et cette compétition a voulu mettre en avant une petite partie de cette recherche: trouver le réseau reliant un groupe de neurones à partir de leurs activités respectives. L'activité d'un neurone est exprimée comme un signal de grande intensité lorsqu'il est actif et de plus faible intensité lorsqu'il est inactif. Le but du jeu est donc de trouver comment associer les neurones par paires, pour ainsi les relier dans le réseau, en regardant simplement si et quand ils sont actifs.

La compétition a vu s'affronter 143 équipes d'horizons très différents et d'universités du monde entier pour trouver la meilleure solution à ce problème. Ce concours fut organisé par des chercheurs qui ont développé un outil qui simule artificiellement l'activité des neurones du cerveau. Leur but est double: d'une part, ils ont essayé de refléter au mieux la réalité et d'autre part, de partir de ses données pour trouver le réseau neuronal du cerveau. Savoir comment les neurones sont reliés les uns aux autres en quelque sorte. Pourquoi simuler des données? Il faut savoir qu'en pratique, il est possible d'observer l'activité des neurones mais il est cependant impossible de connaitre avec exactitude le réseau de neurones qui en est la source. L'intérêt des données artificielles est de connaitre parfaitement la source puisqu'on la définit et d'avoir les données associées.

Pour en revenir à la compétition, ces chercheurs ont développé un outil pour retrouver le réseau de neurones à partir des données générées et ont voulu voir si cet outil était compétif par rapport aux techniques existantes et donner une motivation à des chercheurs pour à leur tour développer des outils les plus performants possibles.

Certains de nos sujets de thèse s'approchaient de la problématique abordée par le concours et cela nous a poussé à y participer.  Par exemple, j'étudie de manière approfondie les réseaux de gènes, autrement dit comment les gènes interagissent entre eux, et la plupart des approches que j'utilise peuvent s'appliquer directement à d'autres types de réseaux sans vraiment tenir compte de leur nature. C'est pour cette raison que participer au concours avait un intérêt dans le cadre de ma thèse.

\item[Comment avez-vous gagné la compétition?]

Inévitablement dans ce genre de concours, il y a une grande part d'intuition. Qui aura la meilleure idée? Qui saura mettre le doigt sur la bonne technique à utiliser? Et il s'avère que dans cette compétition, nous avons pu trouver une méthode relativement simple qui marchait très bien. Un aspect important pour nous était de maitriser notre méthode et de pouvoir justifier chaque étape de notre méthodologie. Nous ne sommes pas des experts en connectivité de neurones donc nous avons conçu une solution générique que nous avons, par après, améliorée pour correspondre parfaitement à l'objectif recherché.

Notre méthode, en quelques mots, consiste à estimer l'affinité de deux neurones lorsque l'état de tous les autres neurones est connu. En d'autres mots, deux neurones semblent-ils intrinsèquement liés quelque soit l'état des autres neurones.

Notre méthode marche bien indéniablement. Cela s'explique surtout par l'énorme travail fourni par notre équipe pour l'améliorer mais aussi par notre expérience dans nos domaines respectifs.

\item[Quel est la part de l'Université dans ce succès?]
Déjà, nous devons remercier nos promoteurs, Pierre Geurts et Damien Ernst, qui nous permettent de participer à ce genre de compétition. Ensuite, il s'agit d'un travail d'équipe composée de membres de services différents et qui, a priori, ne travaillent pas ensemble. Cela met en relief la qualité de l'environnement de recherche à l'Université de Liège et la volonté de collaboration qui y règne. Car nous avons également demandé de l'aide à d'autres chercheurs qui nous ont aidé, ou au moins éclairé, sur certains points. Il faut aussi souligner l'apport des chercheurs plus aguéris de notre équipe qui ont su apporter la maturité nécessaire pour gérer une compétition sans abandonner et se relâcher avant le terme.\\

Pour des chercheurs, ce genre de concours est très intéressant. Tant du point de vue de la recherche car nous trouvons des nouvelles méthodes et des solutions à des problèmes que du point de vue personnel car c'est passionnant d'essayer de se dépasser seul ou en équipe. Cela renforce également les collaborations au sein de l'université et renforce l'esprit d'équipe.

\end{description}

\end{document}

### 2014-09-04 oral/slides.tex
slide: skeleton + draft of images

\documentclass[final]{beamer}

\usepackage[utf8]{inputenc}
\usepackage[frenchb]{babel}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{color}
\usepackage{hyperref}
\usepackage{verbatim}
\usepackage{url}

\usepackage{pifont}
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%

\usepackage{multirow}

\hypersetup{colorlinks=true, linkcolor=black, urlcolor=blue}
\beamertemplatenavigationsymbolsempty
\setbeamertemplate{sections/subsections in toc}[circle]

\selectcolormodel{cmyk}

\definecolor{i6blue}{cmyk}{1,0.305,0,0.06}
\definecolor{i6bluedark}{rgb}{0.0156,0.2578,0.5625}
\definecolor{i6colorscheme1}{HTML}{FFFFFF}  % e.g. for block title
\definecolor{i6colorblockbg}{HTML}{ADDFFF}
\definecolor{i6colorblockfg}{HTML}{FFFFFF}
\definecolor{i6colorscheme2}{HTML}{100D09}  % e.g. title in headline
\definecolor{i6colorscheme3}{HTML}{FFFFFF}  % e.g. for poster background
\definecolor{i6colorscheme4}{HTML}{000000}
\definecolor{i6colorschemeHeadline}{HTML}{FFFFFF}  % for headline bg
\definecolor{i6colorschemeFootline}{HTML}{100D09}  % for headline bg

\setbeamercolor{headline}{fg=blue,bg=i6colorschemeHeadline}
\setbeamercolor{title in headline}{fg=blue}
\setbeamercolor{author in headline}{fg=black}
\setbeamercolor{institute in headline}{fg=lightgray}
\setbeamercolor{logo in headline}{fg=black,bg=lightgray}
\setbeamercolor{separation line}{bg=i6colorscheme1}

\definecolor{lightgreen}{rgb}{0.0,0.8,0.0}
\definecolor{lightblue}{rgb}{0.3,0.8,1.0}
\definecolor{lightred}{rgb}{0.874,0.180,0.105}
\definecolor{gray}{rgb}{0.4,0.4,0.4}
\definecolor{lightgray}{rgb}{0.8,0.8,0.8}
\definecolor{shadecolor}{rgb}{0.9,0.9,0.9}

\usepackage{multirow}

\title{Simple connectome inference from partial\\[1ex]
correlation statistics in calcium imaging}
\author{{\small Antonio Sutera, Arnaud Joly, Vincent François-Lavet, Zixiao Aaron Qiu\\[1ex] Gilles Louppe, Damien Ersnt and Pierre Geurts.}}
\date{}

\begin{document}

%% Slide 1 ==================================================================

\begin{frame}

\vspace{-0cm}

	\begin{center}
	\includegraphics[width=7cm]{images/network.png}
	\end{center}

\vspace{-9.5cm}
  \begin{beamercolorbox}[wd=\paperwidth, ignorebg]{headline}
    \begin{center}

      \usebeamercolor{title in headline}{\color{fg}\Large{\textbf{\inserttitle}}\\[2ex]}
      \usebeamercolor{author in headline}{\color{fg}\small{\insertauthor}\\[1ex]}
    \end{center}
  \end{beamercolorbox}

\end{frame}

%% Slide 2 ==================================================================

\begin{frame}

\frametitle{Introduction}

From {\color{i6blue} time-series of the neuron activity}, the \textbf{goal} is to {\color{red} \textbf{infer} the directed connections between neurons}.

\end{frame}

%% Slide 3 ==================================================================

\begin{frame}

\frametitle{Introduction}

But this problem is \textbf{difficult} because of...

\begin{tabular*}{\textwidth}{l r} \hline
&\multirow{3}{*}{\includegraphics[width=2cm]{images/miss.png} \includegraphics[width=2cm]{images/hidden.png}}\\

{\color{red} \textbf{masking} effects}
& \\ 
& \\
\end{tabular}

% \begin{itemize}
% \item {\color{red} \textbf{masking} effects},
% \includegraphics[width=2cm]{images/miss.png} \includegraphics[width=2cm]{images/hidden.png}
% \item {\color{red} \textbf{low} sampling rate},
% \includegraphics[width=4cm]{images/slowsamplingrate.png}
% \item {\color{red} \textbf{slow} decay} of fluorescence.
% \includegraphics[width=4cm]{images/original_curve_gr}
% \end{itemize}

\end{frame}

%% Slide 4 ==================================================================

\begin{frame}

\frametitle{Framework of our solution  \hspace{15pt} {\small Table of contents} }

{\color{red} How-to}:
\begin{enumerate}
\item \textbf{Deal} with calcium fluorescence signals: {\color{i6blue} signal processing}.
\item \textbf{Find} the network: the {\color{i6blue} {inference} method}.
\item \textbf{Improve} the method: our {\color{i6blue} {tricks}}.
\end{enumerate}\vskip5pt

{\color{red} One step further}:
\begin{itemize}
\item Improvement of each stage of our solution.
\item Comparison with other methods.
\end{itemize}\vskip5pt

{\color{red} Even further}: 
\begin{itemize}
\item The ``full method'' in a nutshell.
\end{itemize}

\end{frame}

%% Slide 5 ==================================================================

\begin{frame}

\frametitle{Signal processing}

\begin{overprint}
\onslide<1> 
a-b

\onslide<2>
a-b-c

\onslide<3>
a-b-c-d

\onslide<4>
a-b-c-d-e
\end{overprint}

\end{frame}

%% Slide 6 ==================================================================

\begin{frame}

\frametitle{Connectome \textbf{inference} from {\color{red} partial correlation statistics}}

\begin{columns}
\begin{column}{0.5\linewidth}
diag
\end{column}
\begin{column}{0.5\linewidth}

\begin{itemize}
\item[{\color{green} \cmark}] Only direct associations
\item[{\color{green} \cmark}] Filter out spurious indirect effects
\item[{\color{green} \cmark}] Symmetric \\[5ex]
\item[{\color{red} \xmark}] Edge orientation
\item[{\color{red} \xmark}] Sensitive to the value of parameters in the filtering process
\end{itemize}

\end{column}

\end{columns}

\end{frame}

%% Slide 7 ==================================================================

\begin{frame}
\frametitle{Improvements}

\begin{itemize}
\item \textcolor{red}{\textbf{Approximation}} for partial correlation statistics using only the \textcolor{i6blue}{800 first principal components}. \\[5ex]
\item {\color{red} \textbf{Averaged} partial correlation statistics} over various values of the parameters
	\begin{itemize}
		\item[{\color{green} \cmark}] Improve robustness (over all networks)
		\item[{\color{green} \cmark}] Reduce variance of its prediction
		\item[{\color{green} \cmark}] Decrease the sensitivity to the filtering process
	\end{itemize}
\end{itemize}

\end{frame}

%% Slide 8 ==================================================================

\begin{frame}
\frametitle{Each stage of our solution is good!}

\begin{table}[t]
\caption{Performance on \textit{normal-1,2,3,4} with partial correlation and different filtering functions.}
\label{tab:comparison}
\centering
\tiny
\begin{tabular}{| l | c c c c | c c c c |}
\hline
& \multicolumn{4}{c|}{AUROC} & \multicolumn{4}{c|}{AUPRC} \\
\textit{Method} $\backslash$ \textit{normal-} & \textit{1} & \textit{2} & \textit{3} & \textit{4} & \textit{1} & \textit{2} & \textit{3} & \textit{4} \\
\hline
\hline
No  filtering       					& 0.777 & 0.767 & 0.772 & 0.774 & 0.070 & 0.064 & 0.068 & 0.072\\
$ h \circ g \circ f_1$                  & 0.923 & 0.925 & 0.923 & 0.922 & 0.311 & 0.315 & 0.313 & 0.304\\
$ w \circ h \circ g \circ f_1$          & 0.931 & 0.929 & 0.928 & 0.926 & 0.326 & 0.323 & 0.319 & 0.303\\
+ PCA         							& 0.932 & 0.930 & 0.928 & 0.926 & 0.355 & 0.353 & 0.350 & 0.333\\
Averaging           					& 0.937 & 0.935 & 0.935 & 0.931 & 0.391 &  0.390 &  0.385 & 0.375\\
Full method           					& \textbf{0.943} & \textbf{0.942} & \textbf{0.942} & \textbf{0.939} & \textbf{0.403} & \textbf{0.404} & \textbf{0.398} & \textbf{0.388}\\
\hline
\end{tabular}
\end{table}

\end{frame}

%% Slide 9 ==================================================================

\begin{frame}
\frametitle{Comparison with other methods}

\begin{table}[t]

\caption{Performance on \textit{normal-1,2,3,4} with different methods.}
\label{tab:comparison}
\centering
\tiny
\begin{tabular}{| l | c c c c | c c c c |}
\hline
& \multicolumn{4}{c|}{AUROC} & \multicolumn{4}{c|}{AUPRC} \\
\textit{Method} $\backslash$ \textit{normal-} & \textit{1} & \textit{2} & \textit{3} & \textit{4} & \textit{1} & \textit{2} & \textit{3} & \textit{4} \\
\hline
\hline
Averaging           					& 0.937 & 0.935 & 0.935 & 0.931 & 0.391 &  0.390 &  0.385 & 0.375\\
Full method           					& \textbf{0.943} & \textbf{0.942} & \textbf{0.942} & \textbf{0.939} & \textbf{0.403} & \textbf{0.404} & \textbf{0.398} & \textbf{0.388}\\
\hline
PC & 0.886 & 0.884 & 0.891 &  0.877 & 0.153 & 0.145 & 0.170 & 0.132\\
GTE & 0.890 & 0.893 & 0.894 & 0.873 & 0.171 & 0.174 & 0.197 & 0.142\\
GENIE3 & 0.892 & 0.891 & 0.887 & 0.887 & 0.232 & 0.221 & 0.237 & 0.215 \\
\hline
\end{tabular}
\end{table}

\end{frame}

%% Slide 10 =================================================================

\begin{frame}
\frametitle{An optimized version to win the challenge: ``Full method''}

\begin{itemize}
\item A \textbf{tuned} signal processing,
\item \textbf{Weighted} average of partial correlation statistics,
\item \textbf{Prediction} of edge orientation.
\end{itemize}

\end{frame}

%% Slide 11 =================================================================

\begin{frame}
\frametitle{For every details of our method...}

\textbf{The description of the method:}
\begin{itemize}
\item[] Sutera, A., Joly, A., François-Lavet, V., Qiu, Z. A., Louppe, G., Ernst, D., \& Geurts, P. (2014). Simple connectome inference from partial correlation statistics in calcium imaging.\\[7ex]
\end{itemize}

\textbf{Code available at:}
\begin{itemize}
\item[] \url{https://github.com/asutera/kaggle-connectomics}
\end{itemize}

\end{frame}

\end{document}

### 2014-09-04 poster/poster.tex
before i realize it's portrait

\documentclass[final]{beamer}

\usetheme{RJH}
\usepackage[utf8]{inputenc}
\usepackage[frenchb]{babel}
\usepackage[orientation=portrait,size=a2,scale=1.2]{beamerposter}
\usepackage[absolute,overlay]{textpos}
\usepackage{url}

\usepackage{graphicx}
\usepackage{color}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{pifont}
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\usepackage[labelformat=empty]{caption}
\usepackage{framed}
\usepackage{wrapfig}

\setlength{\TPHorizModule}{\paperwidth}
\setlength{\TPVertModule}{\paperheight}

\newcommand{\qedwhite}{\hfill \ensuremath{\Box}}

\definecolor{lightgreen}{rgb}{0.0,0.8,0.0}
\definecolor{lightblue}{rgb}{0.3,0.8,1.0}
\definecolor{lightred}{rgb}{0.874,0.180,0.105}
\definecolor{gray}{rgb}{0.4,0.4,0.4}
\definecolor{lightgray}{rgb}{0.8,0.8,0.8}
\definecolor{shadecolor}{rgb}{0.9,0.9,0.9}

\title{Simple connectome inference from partial correlation statistics in calcium imaging}
\author{Antonio Sutera, Arnaud Joly, Vincent François-Lavet, Zixiao Aaron Qiu, Gilles Louppe, Damien Ernst and Pierre Geurts\\[1.5ex]
{\tiny
\includegraphics[scale=0.16]{images/mail.png}~\url{a.sutera@ulg.ac.be}
%\includegraphics[scale=0.6]{images/twitter.png}~\href{https://twitter.com/glouppe}{@glouppe}
\includegraphics[scale=0.18]{images/github.png}~\url{https://github.com/asutera/kaggle-connectomics}
}}

\footer{}
\date{}

\makeatletter
\newcommand{\superimpose}[2]{%
  {\ooalign{$#1\@firstoftwo#2$\cr\hfil$#1\@secondoftwo#2$\hfil\cr}}}
\makeatother

\begin{document}
\begin{frame}{}

%% Column 1 ==================================================================

\begin{textblock}{0.32}(0.01,0.14)

%% Signal processing ---------------------------------------------------------

\begin{block}{Signal processing \phantom{p}}

Despite growing interest and practical use in various scientific areas, \textbf{variable
importances derived from tree-based ensemble methods are not well understood
from a theoretical point of view}. In this work we characterize the Mean Decrease
Impurity (MDI) variable importances as measured by an ensemble of totally
randomized trees in asymptotic sample and ensemble size conditions. \textbf{We derive a
three-level decomposition of the  information jointly provided by all input
variables about the output in terms of
\begin{itemize}
\item[] {\color{lightgreen}i) the MDI importance of each input variable,}
\item[] {\color{lightblue}ii) the degree of interaction of an input variable with the other input variables,}
\item[] {\color{lightred}iii) the different interaction terms of a given degree.}
\end{itemize}}
We then
show that this MDI importance of a variable is equal to zero if and only if the
variable is irrelevant and that the MDI importance of a relevant variable is
invariant with respect to the removal or the addition of irrelevant variables.
We illustrate these properties on a simple example and discuss how they may
change in the case of  non-totally randomized trees such as Random Forests and
Extra-Trees.

\vspace{2.5cm}

Despite growing interest and practical use in various scientific areas, \textbf{variable
importances derived from tree-based ensemble methods are not well understood
from a theoretical point of view}. In this work we characterize the Mean Decrease
Impurity (MDI) variable importances as measured by an ensemble of totally
randomized trees in asymptotic sample and ensemble size conditions. \textbf{We derive a
three-level decomposition of the  information jointly provided by all input
variables about the output in terms of
\begin{itemize}
\item[] {\color{lightgreen}i) the MDI importance of each input variable,}
\item[] {\color{lightblue}ii) the degree of interaction of an input variable with the other input variables,}
\item[] {\color{lightred}iii) the different interaction terms of a given degree.}
\end{itemize}}
We then
show that this MDI importance of a variable is equal to zero if and only if the
variable is irrelevant and that the MDI importance of a relevant variable is
invariant with respect to the removal or the addition of irrelevant variables.
We illustrate these properties on a simple example and discuss how they may
change in the case of  non-totally randomized trees such as Random Forests and
Extra-Trees.

\end{block}

\end{textblock}

%% Col 1 Row 2

\begin{textblock}{0.32}(0.01,0.42)

\end{textblock}

%% Col 1 Row 3

\begin{textblock}{0.32}(0.01,0.71)

\begin{center}
\includegraphics[width=0.75\linewidth]{images/network.png}
\end{center}

\end{textblock}

%% Column 2 ==================================================================

\begin{textblock}{0.32}(0.34,0.14)

%% Abstract ------------------------------------------------------------------

\begin{block}{Abstract \phantom{p}}

In this work, we propose \textbf{a simple yet effective solution} to the problem of
connectome inference in calcium imaging data. The proposed algorithm consists of
\textbf{two steps:
\begin{itemize}
\item[] {\color{lightgreen}i) processing the raw signals to detect neural peak activities,}
\item[] {\color{lightblue}ii) inferring the degree of association between neurons from partial
correlation statistics.}
\end{itemize}}
We summarises the methodology that led us to
win the Connectomics Challenge, proposes a simplified version of our method, and
finally compares our results with respect to other inference methods.

\end{block}

\end{textblock}

\begin{textblock}{0.32}(0.34,0.31)

%% Introduction ------------------------------------------------------------

\begin{block}{Context \phantom{p}}

Without being perfect, \textbf{calcium imaging} currently allows for \textbf{real-time and
simultaneous observation of neuron activity} from thousands of neurons,
producing \textbf{individual time-series representing their fluorescence intensity}.
From these data, the connectome inference problem amounts to retrieving the
synaptic connections between neurons on the basis of the fluorescence time-series. This problem is difficult to solve because of \textbf{experimental issues,
including
\begin{itemize}
\item[] {\color{lightgreen}i) masking effects (i.e., some of the neurons are not observed or
confounded with others),} 
\item[] {\color{lightblue}ii) the low sampling rate of the optical device with
respect to the neural activity speed,} or
\item[] {\color{lightred}iii) the slow decay of fluorescence.}
\end{itemize}}

\end{block}

\end{textblock}

%% Col 2 Row 2

\begin{textblock}{0.32}(0.34,0.525)

%% Connectome inference ------------------------------------------------------

\begin{block}{Connectome inference \phantom{p}}

Despite growing interest and practical use in various scientific areas, \textbf{variable
importances derived from tree-based ensemble methods are not well understood
from a theoretical point of view}. In this work we characterize the Mean Decrease
Impurity (MDI) variable importances as measured by an ensemble of totally
randomized trees in asymptotic sample and ensemble size conditions. \textbf{We derive a
three-level decomposition of the  information jointly provided by all input
variables about the output in terms of
\begin{itemize}
\item[] {\color{lightgreen}i) the MDI importance of each input variable,}
\item[] {\color{lightblue}ii) the degree of interaction of an input variable with the other input variables,}
\item[] {\color{lightred}iii) the different interaction terms of a given degree.}
\end{itemize}}
We then
show that this MDI importance of a variable is equal to zero if and only if the
variable is irrelevant and that the MDI importance of a relevant variable is
invariant with respect to the removal or the addition of irrelevant variables.
We illustrate these properties on a simple example and discuss how they may
change in the case of  non-totally randomized trees such as Random Forests and
Extra-Trees.

Despite growing interest and practical use in various scientific areas, \textbf{variable
importances derived from tree-based ensemble methods are not well understood
from a theoretical point of view}. In this work we characterize the Mean Decrease
Impurity (MDI) variable importances as measured by an ensemble of totally
randomized trees in asymptotic sample and ensemble size conditions.

\end{block}

\end{textblock}

%% Col 2 Row 3

\begin{textblock}{0.32}(0.34,0.71)

\end{textblock}

%% Column 3 ==================================================================

\begin{textblock}{0.32}(0.67,0.14)

%% Experiments ---------------------------------------------------------------

\begin{block}{Experiments \phantom{p}}

Despite growing interest and practical use in various scientific areas, \textbf{variable
importances derived from tree-based ensemble methods are not well understood
from a theoretical point of view}. In this work we characterize the Mean Decrease
Impurity (MDI) variable importances as measured by an ensemble of totally
randomized trees in asymptotic sample and ensemble size conditions. \textbf{We derive a
three-level decomposition of the  information jointly provided by all input
variables about the output in terms of
\begin{itemize}
\item[] {\color{lightgreen}i) the MDI importance of each input variable,}
\item[] {\color{lightblue}ii) the degree of interaction of an input variable with the other input variables,}
\item[] {\color{lightred}iii) the different interaction terms of a given degree.}
\end{itemize}}
We then
show that this MDI importance of a variable is equal to zero if and only if the
variable is irrelevant and that the MDI importance of a relevant variable is
invariant with respect to the removal or the addition of irrelevant variables.
We illustrate these properties on a simple example and discuss how they may
change in the case of  non-totally randomized trees such as Random Forests and
Extra-Trees.

\vspace{2.5cm}

Despite growing interest and practical use in various scientific areas, \textbf{variable
importances derived from tree-based ensemble methods are not well understood
from a theoretical point of view}. In this work we characterize the Mean Decrease
Impurity (MDI) variable importances as measured by an ensemble of totally
randomized trees in asymptotic sample and ensemble size conditions. \textbf{We derive a
three-level decomposition of the  information jointly provided by all input
variables about the output in terms of
\begin{itemize}
\item[] {\color{lightgreen}i) the MDI importance of each input variable,}
\item[] {\color{lightblue}ii) the degree of interaction of an input variable with the other input variables,}
\item[] {\color{lightred}iii) the different interaction terms of a given degree.}
\end{itemize}}
We then
show that this MDI importance of a variable is equal to zero if and only if the
variable is irrelevant and that the MDI importance of a relevant variable is
invariant with respect to the removal or the addition of irrelevant variables.
We illustrate these properties on a simple example and discuss how they may
change in the case of  non-totally randomized trees such as Random Forests and
Extra-Trees.

\end{block}

\end{textblock}

%% Col 3 Row 2

\begin{textblock}{0.32}(0.67,0.42)

\end{textblock}

%% Col 3 Row 3

\begin{textblock}{0.32}(0.67,0.71)

%% Conclusion ------------------------------------------------------------

\begin{block}{Conclusion \phantom{p}}

In this paper, we outlined a simple but efficient methodology for the problem
of connectome inference from calcium imaging data. Our approach consists of \textbf{two
steps: 
\begin{itemize}
\item[] {\color{lightgreen}i) processing fluorescence data to detect neural peak activities; and}
\item[] {\color{lightblue}ii) inferring the degree of association between neurons from partial 
correlation statistics.}
\end{itemize}}

Its simplified variant outperforms other
network inference methods while its optimized version proved to be the best method
on the Connectomics Challenge. Given its simplicity and good performance, we
therefore believe that the methodology presented in this work
would constitute a solid and easily-reproducible baseline for further work in
the field of connectome inference.\\[2ex]

\textbf{Acknowledgments}\\
A. Joly and G. Louppe are research fellows of the FNRS, Belgium.  A. Sutera is a
recipient of an FRIA fellowship of FRS-FNRS, Belgium. This work is supported by
PASCAL2 and the IUAP DYSCO, initiated by the Belgian State, Science Policy
Office.

\end{block}

\end{textblock}

\end{frame}
\end{document}

### 2014-09-06 poster/poster.tex
before i realize it's portrait
poster good first version

@@
 \usepackage{url}
+\usepackage[T1]{fontenc}
+
+\usepackage{bbold}
+
+\usepackage{wrapfig, blindtext}
+\usepackage{ragged2e}
 
@@
 \usepackage{framed}
-\usepackage{wrapfig}
+%\usepackage{wrapfig}
 
@@
 \definecolor{shadecolor}{rgb}{0.9,0.9,0.9}
+
+\newenvironment{shaded2}{%
+  \def\FrameCommand{\fboxsep=\FrameSep \colorbox{blue!20}}%
+  \MakeFramed {\FrameRestore}}%
+ {\endMakeFramed}
 
@@
 
-%% Column 1 ==================================================================
+%% Abstract ------------------------------------------------------------------
 
-\begin{textblock}{0.32}(0.01,0.14)
-
-%% Signal processing ---------------------------------------------------------
-
-\begin{block}{Signal processing \phantom{p}}
-
-Despite growing interest and practical use in various scientific areas, \textbf{variable
-importances derived from tree-based ensemble methods are not well understood
-from a theoretical point of view}. In this work we characterize the Mean Decrease
-Impurity (MDI) variable importances as measured by an ensemble of totally
-randomized trees in asymptotic sample and ensemble size conditions. \textbf{We derive a
-three-level decomposition of the  information jointly provided by all input
-variables about the output in terms of
-\begin{itemize}
-\item[] {\color{lightgreen}i) the MDI importance of each input variable,}
-\item[] {\color{lightblue}ii) the degree of interaction of an input variable with the other input variables,}
-\item[] {\color{lightred}iii) the different interaction terms of a given degree.}
-\end{itemize}}
-We then
-show that this MDI importance of a variable is equal to zero if and only if the
-variable is irrelevant and that the MDI importance of a relevant variable is
-invariant with respect to the removal or the addition of irrelevant variables.
-We illustrate these properties on a simple example and discuss how they may
-change in the case of  non-totally randomized trees such as Random Forests and
-Extra-Trees.
-
-\vspace{2.5cm}
-
-Despite growing interest and practical use in various scientific areas, \textbf{variable
-importances derived from tree-based ensemble methods are not well understood
-from a theoretical point of view}. In this work we characterize the Mean Decrease
-Impurity (MDI) variable importances as measured by an ensemble of totally
-randomized trees in asymptotic sample and ensemble size conditions. \textbf{We derive a
-three-level decomposition of the  information jointly provided by all input
-variables about the output in terms of
-\begin{itemize}
-\item[] {\color{lightgreen}i) the MDI importance of each input variable,}
-\item[] {\color{lightblue}ii) the degree of interaction of an input variable with the other input variables,}
-\item[] {\color{lightred}iii) the different interaction terms of a given degree.}
-\end{itemize}}
-We then
-show that this MDI importance of a variable is equal to zero if and only if the
-variable is irrelevant and that the MDI importance of a relevant variable is
-invariant with respect to the removal or the addition of irrelevant variables.
-We illustrate these properties on a simple example and discuss how they may
-change in the case of  non-totally randomized trees such as Random Forests and
-Extra-Trees.
-
-\end{block}
-
-\end{textblock}
-
-%% Col 1 Row 2
-
-\begin{textblock}{0.32}(0.01,0.42)
-
-\end{textblock}
-
-%% Col 1 Row 3
-
-\begin{textblock}{0.32}(0.01,0.71)
-
-\begin{center}
-\includegraphics[width=0.75\linewidth]{images/network.png}
-\end{center}
-
-\end{textblock}
-
-%% Column 2 ==================================================================
-
-\begin{textblock}{0.32}(0.34,0.14)
-
-%% Abstract ------------------------------------------------------------------
+\begin{textblock}{0.35}(0.01,0.115)
 
@@
 
+\vspace{-0.4cm}
+\begin{center}
+
+\begin{minipage}{0.95\linewidth}
+\begin{shaded}
 In this work, we propose \textbf{a simple yet effective solution} to the problem of
@@
 
+\end{shaded}
+\end{minipage}
+\end{center}
+
 \end{block}
@@
 
-\begin{textblock}{0.32}(0.34,0.31)
+%% Context ------------------------------------------------------------
 
-%% Introduction ------------------------------------------------------------
+\begin{textblock}{0.62}(0.37,0.115)
 
@@
 
-%% Col 2 Row 2
+%% Signal processing -----------------------------------------------------
 
-\begin{textblock}{0.32}(0.34,0.525)
+\begin{textblock}{0.485}(0.01,0.26)
 
-%% Connectome inference ------------------------------------------------------
+\begin{block}{Signal processing \phantom{p}}
 
-\begin{block}{Connectome inference \phantom{p}}
+Under the simplifying assumption that neurons are on-off units, characterised
+by short periods of intense activity, or peaks, and longer periods of
+inactivity, the first part of our algorithm consists of cleaning the raw
+fluorescence data.
+More specifically, time-series are processed using standard
+signal processing filters in order to : 
+\textbf{
+\begin{itemize}
+\item[] {\color{lightgreen}i) remove noise mainly due to fluctuations independent of calcium, calcium fluctuations independent of spiking activity, calcium fluctuations in nearby tissues that have been mistakenly captured, or simply by the imaging process ;}
+\item[] {\color{lightblue}ii) to account for fluorescence low decay ; and}
+\item[] {\color{lightred}iii) to reduce the importance of high global activity in the network.}
+\end{itemize}}
+\vspace{-2pt}
 
-Despite growing interest and practical use in various scientific areas, \textbf{variable
-importances derived from tree-based ensemble methods are not well understood
-from a theoretical point of view}. In this work we characterize the Mean Decrease
-Impurity (MDI) variable importances as measured by an ensemble of totally
-randomized trees in asymptotic sample and ensemble size conditions. \textbf{We derive a
-three-level decomposition of the  information jointly provided by all input
-variables about the output in terms of
-\begin{itemize}
-\item[] {\color{lightgreen}i) the MDI importance of each input variable,}
-\item[] {\color{lightblue}ii) the degree of interaction of an input variable with the other input variables,}
-\item[] {\color{lightred}iii) the different interaction terms of a given degree.}
-\end{itemize}}
-We then
-show that this MDI importance of a variable is equal to zero if and only if the
-variable is irrelevant and that the MDI importance of a relevant variable is
-invariant with respect to the removal or the addition of irrelevant variables.
-We illustrate these properties on a simple example and discuss how they may
-change in the case of  non-totally randomized trees such as Random Forests and
-Extra-Trees.
+\begin{textblock}{0.485}(0.01,0.395)
+\begin{minipage}{0.48\linewidth}
+\begin{shaded}
+\begin{center}
+\includegraphics[width=0.85\linewidth]{images/original_curve.pdf}
+\end{center}
+\end{shaded}
+\end{minipage}
+\end{textblock}
 
-Despite growing interest and practical use in various scientific areas, \textbf{variable
-importances derived from tree-based ensemble methods are not well understood
-from a theoretical point of view}. In this work we characterize the Mean Decrease
-Impurity (MDI) variable importances as measured by an ensemble of totally
-randomized trees in asymptotic sample and ensemble size conditions.
+\begin{textblock}{0.485}(0.25,0.395)
+\begin{minipage}{0.48\linewidth}
+\begin{shaded}
+\vspace{15pt}
+\hspace{1cm} {\small \textbf{Original curve}}
+\vspace{30pt}
+\end{shaded}
+\end{minipage}
+\end{textblock}
+
+\begin{textblock}{0.485}(0.25,0.43)
+\begin{minipage}{0.48\linewidth}
+\begin{shaded2}
+\begin{center}
+
+\includegraphics[width=0.85\linewidth]{images/filter_curve.pdf}
+\end{center}
+\vspace{15pt}
+\end{shaded2}
+\end{minipage}
+\end{textblock}
+
+\begin{textblock}{0.485}(0.01,0.495)
+\begin{minipage}{0.48\linewidth}
+\begin{shaded2}
+\vspace{1pt}
+{\color{lightgreen} \textbf{Applying a low-pass filter}}
+\vspace{-5pt}
+\begin{align*}
+f_1(x^t_i) &= x^{t-1}_i + x^t_i + x^{t+1}_i,\\
+f_2(x^t_i) &= 0.4 x^{t-3}_i + 0.6 x^{t-2}_i + 0.8 x^{t-1}_i + x_i^t.
+\end{align*}
+\vspace{-10pt}
+\end{shaded2}
+\end{minipage}
+\end{textblock}
+
+\begin{textblock}{0.485}(0.01,0.54)
+\begin{minipage}{0.48\linewidth}
+\begin{shaded}
+\begin{center}
+
+\includegraphics[width=0.85\linewidth]{images/diff_curve.pdf}
+\end{center}
+\end{shaded}
+\end{minipage}
+\end{textblock}
+
+\begin{textblock}{0.485}(0.25,0.54)
+\begin{minipage}{0.48\linewidth}
+\begin{shaded}
+\vspace{3pt}
+{\color{lightgreen} \textbf{Applying a high-pass filter}}
+\begin{align*}
+g(x^{t}_{i}) = x^{t}_i - x^{t-1}_i,
+\end{align*}
+\vspace{5pt}
+\end{shaded}
+\end{minipage}
+\end{textblock}
+
+\begin{textblock}{0.485}(0.25,0.58)
+\begin{minipage}{0.48\linewidth}
+\begin{shaded2}
+\begin{center}
+
+\includegraphics[width=0.85\linewidth]{images/threshold_curve.pdf}
+\end{center}
+
+\end{shaded2}
+\end{minipage}
+\end{textblock}
+
+\begin{textblock}{0.485}(0.01,0.64)
+\begin{minipage}{0.48\linewidth}
+\begin{shaded2}
+\vspace{7pt}
+{\color{lightblue} \textbf{Applying a hard-threshold filter}}
+\vspace{-5pt}
+\begin{align*}
+h(x^{t}_i) &= x^{t}_i \mathbb{1}(x^{t}_i \geq \tau) \text{ with } \tau > 0,
+\end{align*}
+\vspace{8pt}
+\end{shaded2}
+\end{minipage}
+\end{textblock}
+
+\begin{textblock}{0.485}(0.01,0.685)
+\begin{minipage}{0.48\linewidth}
+\begin{shaded}
+\begin{center}
+\includegraphics[width=0.85\linewidth]{images/original_curve.pdf}
+\end{center}
+\vspace{-14pt}
+\end{shaded}
+\end{minipage}
+\end{textblock}
+
+\begin{textblock}{0.485}(0.25,0.685)
+\begin{minipage}{0.48\linewidth}
+\begin{shaded}
+\vspace{15pt}
+{\color{lightred} \textbf{Magnify the importance of spikes that occur in cases of low global activity}}
+\begin{align*}
+w(x^{t}_i) = (x^{t}_i + 1 )^{1 + \frac{1}{\sum_{j} x^{t}_j}},
+\end{align*}\vspace{42pt}
+\end{shaded}
+\end{minipage}
+\end{textblock}
 
@@
 
-%% Col 2 Row 3
+% \begin{columns}
+% \begin{column}{0.01\linewidth}
 
-\begin{textblock}{0.32}(0.34,0.71)
+% \end{column}
+% \begin{column}{0.5\linewidth}
+% \includegraphics[width=0.9\linewidth]{images/original_curve.pdf}\\
 
-\end{textblock}
+% \begin{align*}
+% f_1(x^t_i) &= x^{t-1}_i + x^t_i + x^{t+1}_i,\\
+% f_2(x^t_i) &= 0.4 x^{t-3}_i + 0.6 x^{t-2}_i + 0.8 x^{t-1}_i + x_i^t.
+% \end{align*}
 
-%% Column 3 ==================================================================
+% \includegraphics[width=0.9\linewidth]{images/diff_curve.pdf}\\[2ex]
+% \begin{align*}
+% h(x^{t}_i) &= x^{t}_i \mathbb{1}(x^{t}_i \geq \tau) \text{ with } \tau > 0,
+% \end{align*}
+% \includegraphics[width=0.9\linewidth]{images/weights_curve.pdf}\\
 
-\begin{textblock}{0.32}(0.67,0.14)
+% \end{column}
 
-%% Experiments ---------------------------------------------------------------
+% \begin{column}{0.5\linewidth}
 
-\begin{block}{Experiments \phantom{p}}
+% Original signal \\
 
-Despite growing interest and practical use in various scientific areas, \textbf{variable
-importances derived from tree-based ensemble methods are not well understood
-from a theoretical point of view}. In this work we characterize the Mean Decrease
-Impurity (MDI) variable importances as measured by an ensemble of totally
-randomized trees in asymptotic sample and ensemble size conditions. \textbf{We derive a
-three-level decomposition of the  information jointly provided by all input
-variables about the output in terms of
+% \includegraphics[width=0.9\linewidth]{images/filter_curve.pdf}\\[2ex]
+
+% \begin{align*}
+% g(x^{t}_{i}) = x^{t}_i - x^{t-1}_i,
+% \end{align*}
+
+% \includegraphics[width=0.9\linewidth]{images/threshold_curve.pdf}\\[2ex]
+
+% \begin{align*}
+% w(x^{t}_i) = (x^{t}_i + 1 )^{1 + \frac{1}{\sum_{j} x^{t}_j}},
+% \end{align*}
+
+% \end{column}
+% \end{columns}
+
+%% Connectome inference --------------------------------------------------
+
+\begin{textblock}{0.485}(0.505,0.26)
+
+\begin{block}{Connectome inference \phantom{p}}
+
+\includegraphics[width=\linewidth]{images/partial2.png}
+
+Given the assumption of random variables drawn from the same time-invariant joint probability distribution, we then propose to use as a measure of the
+strength of the connection between two neurons $i$ and $j$, the
+\textit{Partial correlation} coefficient $p_{i,j}$ between their corresponding
+random variables $X_i$ and $X_j$, defined by:
+
+\begin{align*}
+p_{i,j} =
+-\frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii} \Sigma^{-1}_{jj}}}, \label{eq:inverse}
+\end{align*}
+where $\Sigma^{-1}$, known as the precision or concentration matrix, is the inverse of the covariance matrix $\Sigma$ of $X$.\\
+
+Assuming that the distribution $P_X$ is a multivariate Gaussian
+distribution ${\cal N}(\mu,\Sigma)$, it can be shown that $p_{i,j}$ is
+zero if and only if $X_i$ and $X_j$ are independent given all other
+variables in $X$, i.e., $X_i \perp X_j|X^{-i,j}$ where $X^{-i,j}= X
+\setminus\{X_i,X_j\}$.
+
 \begin{itemize}
-\item[] {\color{lightgreen}i) the MDI importance of each input variable,}
-\item[] {\color{lightblue}ii) the degree of interaction of an input variable with the other input variables,}
-\item[] {\color{lightred}iii) the different interaction terms of a given degree.}
-\end{itemize}}
-We then
-show that this MDI importance of a variable is equal to zero if and only if the
-variable is irrelevant and that the MDI importance of a relevant variable is
-invariant with respect to the removal or the addition of irrelevant variables.
-We illustrate these properties on a simple example and discuss how they may
-change in the case of  non-totally randomized trees such as Random Forests and
-Extra-Trees.
-
-\vspace{2.5cm}
-
-Despite growing interest and practical use in various scientific areas, \textbf{variable
-importances derived from tree-based ensemble methods are not well understood
-from a theoretical point of view}. In this work we characterize the Mean Decrease
-Impurity (MDI) variable importances as measured by an ensemble of totally
-randomized trees in asymptotic sample and ensemble size conditions. \textbf{We derive a
-three-level decomposition of the  information jointly provided by all input
-variables about the output in terms of
-\begin{itemize}
-\item[] {\color{lightgreen}i) the MDI importance of each input variable,}
-\item[] {\color{lightblue}ii) the degree of interaction of an input variable with the other input variables,}
-\item[] {\color{lightred}iii) the different interaction terms of a given degree.}
-\end{itemize}}
-We then
-show that this MDI importance of a variable is equal to zero if and only if the
-variable is irrelevant and that the MDI importance of a relevant variable is
-invariant with respect to the removal or the addition of irrelevant variables.
-We illustrate these properties on a simple example and discuss how they may
-change in the case of  non-totally randomized trees such as Random Forests and
-Extra-Trees.
+\item[{\color{green} \cmark}] Only direct associations
+\item[{\color{green} \cmark}] Filter out spurious indirect effects
+\item[{\color{green} \cmark}] Symmetric (i.e. $p_{i,j}=p_{j,i}$)\\[5ex]
+\item[{\color{red} \xmark}] Edge orientation
+\item[{\color{red} \xmark}] Sensitive to the value of parameters in the filtering process
+\end{itemize}
 
@@
 
-%% Col 3 Row 2
+%% Experiment ------------------------------------------------------------
 
-\begin{textblock}{0.32}(0.67,0.42)
+\begin{textblock}{0.69}(0.01,0.78)
+
+\begin{block}{Experiments \phantom{p}}
+
+\vspace{-5pt}
+\begin{wrapfigure}{r}{0.7\linewidth}
+\centering
+\tiny
+\begin{tabular}{| l | c c c c | c c c c |}
+\hline
+& \multicolumn{8}{c|}{Performance with partial correlation}\\ \hline
+& \multicolumn{4}{c|}{AUROC} & \multicolumn{4}{c|}{AUPRC} \\
+with \textit{Method} $\backslash$ on \textit{normal-} & \textit{1} & \textit{2} & \textit{3} & \textit{4} & \textit{1} & \textit{2} & \textit{3} & \textit{4} \\
+\hline
+\hline
+No  filtering       					& 0.777 & 0.767 & 0.772 & 0.774 & 0.070 & 0.064 & 0.068 & 0.072\\
+$ h \circ g \circ f_1$                  & 0.923 & 0.925 & 0.923 & 0.922 & 0.311 & 0.315 & 0.313 & 0.304\\
+$ w \circ h \circ g \circ f_1$          & 0.931 & 0.929 & 0.928 & 0.926 & 0.326 & 0.323 & 0.319 & 0.303\\
++ PCA         							& 0.932 & 0.930 & 0.928 & 0.926 & 0.355 & 0.353 & 0.350 & 0.333\\
+Averaging           					& 0.937 & 0.935 & 0.935 & 0.931 & 0.391 &  0.390 &  0.385 & 0.375\\
+Full method           					& \textbf{0.943} & \textbf{0.942} & \textbf{0.942} & \textbf{0.939} & \textbf{0.403} & \textbf{0.404} & \textbf{0.398} & \textbf{0.388}\\
+\hline
+PC & 0.886 & 0.884 & 0.891 &  0.877 & 0.153 & 0.145 & 0.170 & 0.132\\
+GTE & 0.890 & 0.893 & 0.894 & 0.873 & 0.171 & 0.174 & 0.197 & 0.142\\
+GENIE3 & 0.892 & 0.891 & 0.887 & 0.887 & 0.232 & 0.221 & 0.237 & 0.215 \\
+\hline
+\end{tabular}
+\end{wrapfigure}
+
+These results clearly show the importance of the filters and PCA (especially for AUPRC). Taking the average over
+various parameter settings gives an improvement of 10\% in AUPRC but
+only a minor change in AUROC. The last row (``Full method'') shows the
+final performance of the method specifically tuned for the challenge
+(see paper for all details). Although this
+tuning was decisive to obtain the best performance in the challenge,
+it does not significantly improve either AUROC or AUPRC.
+
+Partial correlation and averaged partial correlation clearly outperform all other methods on all datasets. The
+improvement is more important in terms of AUPRC than in terms of AUROC. As
+expected, Pearson correlation performs very poorly in terms of AUPRC. GTE and
+GENIE3 work much better, but these two methods are nevertheless clearly below
+partial correlation.
+
+\end{block}
 
@@
 
-%% Col 3 Row 3
-
-\begin{textblock}{0.32}(0.67,0.71)
-
 %% Conclusion ------------------------------------------------------------
 
+\begin{textblock}{0.28}(0.71,0.78)
+
 \begin{block}{Conclusion \phantom{p}}
+\vspace{-0.4cm}
+\begin{center}
+
+\begin{minipage}{0.95\linewidth}
+\begin{shaded}
 
@@
 would constitute a solid and easily-reproducible baseline for further work in
-the field of connectome inference.\\[2ex]
+the field of connectome inference.
+\end{shaded}
+\end{minipage}
+\end{center}
 
-\textbf{Acknowledgments}\\
-A. Joly and G. Louppe are research fellows of the FNRS, Belgium.  A. Sutera is a
-recipient of an FRIA fellowship of FRS-FNRS, Belgium. This work is supported by
-PASCAL2 and the IUAP DYSCO, initiated by the Belgian State, Science Policy
-Office.
+\vspace{-0.3cm}
 
@@
 
+\begin{textblock}{1}(0.01,0.99)
+{\fontsize{12}{10}\textbf{Acknowledgments:}}
+{\fontsize{8}{10}\textbf{A. Joly and G. Louppe are research fellows of the FNRS, Belgium. A. Sutera is a
+recipient of an FRIA fellowship of FRS-FNRS, Belgium. This work is supported by
+PASCAL2 and the IUAP DYSCO, initiated by the Belgian State, Science Policy
+Office.}}
+\end{textblock}
+
 \end{frame}

### 2014-09-08 poster/poster.tex
new poster

@@
 \usepackage{framed}
-%\usepackage{wrapfig}
+\usepackage{wrapfig}
+
+\usepackage[pdf]{pstricks}
 
@@
 
+\hypersetup{colorlinks=true, urlcolor=blue!60}
+
 \newenvironment{shaded2}{%
@@
 %\includegraphics[scale=0.6]{images/twitter.png}~\href{https://twitter.com/glouppe}{@glouppe}
-\includegraphics[scale=0.18]{images/github.png}~\url{https://github.com/asutera/kaggle-connectomics}
+\includegraphics[scale=0.18]{images/github.png}~Code source available at \url{https://github.com/asutera/kaggle-connectomics}
 }}
@@
 
-\begin{textblock}{0.35}(0.01,0.115)
+\begin{textblock}{0.43}(0.01,0.115)
 
@@
 
-\begin{minipage}{0.95\linewidth}
+\begin{minipage}{0.96\linewidth}
 \begin{shaded}
@@
 \end{itemize}}
-We summarises the methodology that led us to
-win the Connectomics Challenge, proposes a simplified version of our method, and
-finally compares our results with respect to other inference methods.
+We summarise the methodology that led us to
+win the Connectomics Challenge, propose a simplified version of our method, and
+finally compare our results with respect to other inference methods.
 
@@
 \end{block}
-
 \end{textblock}
@@
 
-\begin{textblock}{0.62}(0.37,0.115)
+\begin{textblock}{0.54}(0.45,0.115)
 
@@
 
-\begin{textblock}{0.485}(0.01,0.26)
+\begin{textblock}{0.485}(0.01,0.25)
 
@@
 \end{itemize}}
-\vspace{-2pt}
+\vspace{-4pt}
 
-\begin{textblock}{0.485}(0.01,0.395)
+\begin{textblock}{0.485}(0.01,0.390)
 \begin{minipage}{0.48\linewidth}
@@
 
-\begin{textblock}{0.485}(0.25,0.395)
+\begin{textblock}{0.485}(0.25,0.390)
 \begin{minipage}{0.48\linewidth}
@@
 
-\begin{textblock}{0.485}(0.25,0.43)
+\begin{textblock}{0.485}(0.25,0.425)
 \begin{minipage}{0.48\linewidth}
@@
 
-\includegraphics[width=0.85\linewidth]{images/filter_curve.pdf}
+\includegraphics[width=0.85\linewidth]{images/filter_curve_2.pdf}
 \end{center}
@@
 
-\begin{textblock}{0.485}(0.01,0.495)
+\begin{textblock}{0.485}(0.01,0.490)
 \begin{minipage}{0.48\linewidth}
@@
 
-\begin{textblock}{0.485}(0.01,0.54)
+\begin{textblock}{0.485}(0.01,0.535)
 \begin{minipage}{0.48\linewidth}
@@
 
-\begin{textblock}{0.485}(0.25,0.54)
+\begin{textblock}{0.485}(0.25,0.535)
 \begin{minipage}{0.48\linewidth}
@@
 
-\begin{textblock}{0.485}(0.25,0.58)
+\begin{textblock}{0.485}(0.25,0.575)
 \begin{minipage}{0.48\linewidth}
@@
 
-\begin{textblock}{0.485}(0.01,0.64)
+\begin{textblock}{0.485}(0.01,0.635)
 \begin{minipage}{0.48\linewidth}
@@
 
-\begin{textblock}{0.485}(0.01,0.685)
+\begin{textblock}{0.485}(0.01,0.680)
 \begin{minipage}{0.48\linewidth}
@@
 \begin{center}
-\includegraphics[width=0.85\linewidth]{images/original_curve.pdf}
+\includegraphics[width=0.85\linewidth]{images/weights_curve_2.pdf}
 \end{center}
@@
 
-\begin{textblock}{0.485}(0.25,0.685)
+\begin{textblock}{0.485}(0.25,0.680)
 \begin{minipage}{0.48\linewidth}
@@
 w(x^{t}_i) = (x^{t}_i + 1 )^{1 + \frac{1}{\sum_{j} x^{t}_j}},
-\end{align*}\vspace{42pt}
+\end{align*}\vspace{54pt}
 \end{shaded}
@@
 
-\begin{textblock}{0.485}(0.505,0.26)
+\begin{textblock}{0.485}(0.505,0.25)
 
@@
 
-\includegraphics[width=\linewidth]{images/partial2.png}
+% \includegraphics[width=\linewidth]{images/partial2.png}
+\vspace{1cm}
 
-Given the assumption of random variables drawn from the same time-invariant joint probability distribution, we then propose to use as a measure of the
-strength of the connection between two neurons $i$ and $j$, the
-\textit{Partial correlation} coefficient $p_{i,j}$ between their corresponding
+\scalebox{2}{\includegraphics{poster-pics.pdf}}
+{    \begin{pspicture}(20,20)
+
+ 	   \psellipse[fillstyle=solid,linewidth=2pt,linecolor=lightgreen,linestyle=dashed,fillcolor=lightgreen!10](2,3)(1.8,2.8)
+ 	   \psellipse[fillstyle=solid,linewidth=2pt,linecolor=lightgreen,linestyle=dashed,fillcolor=lightgreen!10](8.3,3)(1.5,2.8)
+
+    	% False network left 
+    	\psline[linewidth=2pt,linecolor=lightblue, linestyle=dashed]{--}(1.5,5)(2.7,4.3)
+    	\psline[linewidth=2pt,linecolor=lightblue, linestyle=dashed]{--}(2.7,4.3)(1,4)
+    	\psline[linewidth=2pt,linecolor=lightblue, linestyle=dashed]{--}(2.7,4.3)(4.5,3)
+    	\psline[linewidth=2pt,linecolor=lightblue, linestyle=dashed]{--}(1.3,2.3)(1.5,1)
+    	\psline[linewidth=2pt,linecolor=lightblue, linestyle=dashed]{--}(1.5,1)(2.8,1.7)
+		\psline[linewidth=2pt,linecolor=lightblue, linestyle=dashed]{--}(2.8,1.7)(4.5,3)
+		\psline[linewidth=2pt,linecolor=lightblue, linestyle=dashed]{--}(2.7,4.3)(2.8,1.7)
+
+		\pscircle[fillstyle=solid,fillcolor=lightblue!10,linewidth=2pt,linecolor=lightblue](1.5,5){0.5}
+		\pscircle[fillstyle=solid,fillcolor=lightblue!10,linewidth=2pt,linecolor=lightblue](2.7,4.3){0.5}
+		\pscircle[fillstyle=solid,fillcolor=lightblue!10,linewidth=2pt,linecolor=lightblue](1,4){0.5}
+		\pscircle[fillstyle=solid,fillcolor=lightblue!10,linewidth=2pt,linecolor=lightblue](1.3,2.5){0.5}
+		\pscircle[fillstyle=solid,fillcolor=lightblue!10,linewidth=2pt,linecolor=lightblue](2.8,1.7){0.5}
+		\pscircle[fillstyle=solid,fillcolor=lightblue!10,linewidth=2pt,linecolor=lightblue](1.5,1){0.5}
+
+		% False network right
+
+		\psline[linewidth=2pt,linecolor=lightblue, linestyle=dashed]{--}(8.5,5)(7.5,4)
+		\psline[linewidth=2pt,linecolor=lightblue, linestyle=dashed]{--}(7.8,4)(6.2,3)
+		\psline[linewidth=2pt,linecolor=lightblue, linestyle=dashed]{--}(7.8,4)(9,4)
+		\psline[linewidth=2pt,linecolor=lightblue, linestyle=dashed]{--}(9,2.5)(6.2,3)
+		\psline[linewidth=2pt,linecolor=lightblue, linestyle=dashed]{--}(7.7,2)(6.2,3)
+		\psline[linewidth=2pt,linecolor=lightblue, linestyle=dashed]{--}(7.7,2)(8.5,1)
+		%\psline[linewidth=2pt,linecolor=lightblue, linestyle=dashed]{--}(4.5,3)(8.5,5)
+		\psarc[linewidth=2pt,linecolor=lightblue, linestyle=dashed](8,1.3){3.75}{90}{150}
+
+		\pscircle[fillstyle=solid,fillcolor=lightblue!10,linewidth=2pt,linecolor=lightblue](8.5,5){0.5}
+		\pscircle[fillstyle=solid,fillcolor=lightblue!10,linewidth=2pt,linecolor=lightblue](9,4){0.5}
+		\pscircle[fillstyle=solid,fillcolor=lightblue!10,linewidth=2pt,linecolor=lightblue](7.7,4){0.5}
+		\pscircle[fillstyle=solid,fillcolor=lightblue!10,linewidth=2pt,linecolor=lightblue](9,2.5){0.5}
+		\pscircle[fillstyle=solid,fillcolor=lightblue!10,linewidth=2pt,linecolor=lightblue](7.7,2){0.5}
+		\pscircle[fillstyle=solid,fillcolor=lightblue!10,linewidth=2pt,linecolor=lightblue](8.5,1){0.5}
+
+		% connection
+		\psline[linewidth=2pt,linecolor=lightblue, linestyle=solid]{--}(4.5,3)(6.2,3)
+		% left node
+		\pscircle[fillstyle=solid,fillcolor=lightblue!20,linewidth=2pt,linecolor=lightblue](4.5,3){0.5}
+		% right node
+		\pscircle[fillstyle=solid,fillcolor=lightblue!20,linewidth=2pt,linecolor=lightblue](6.2,3){0.5}
+
+		% text
+		\rput(5.35,3.3){$p_{i,j}$}
+		\rput(5.35,2.3){{$_{\textit{partial correlation}}$}}
+		\rput(5.35,1.9){{$_=$}}
+		\rput(5.35,1.5){{$_{\textit{degree of association}}$}}
+		\rput(5.3,1.1){{$_{\textit{between neurons i and j}}$}}
+
+		\rput(4.2,5){{\color{lightgreen} \textbf{known}}}
+
+		\rput(6.3,0.6){{\color{lightgreen} \textbf{known}}}
+
+        % \psline[linewidth=2pt,linecolor=lightblue]{--}(5,9.5)(8,9.5)
+        % \pscircle[fillstyle=solid,fillcolor=white,linewidth=2pt,linecolor=lightblue](5,9.5){0.5}
+        % \pscircle[fillstyle=solid,fillcolor=white,linewidth=2pt,linecolor=lightblue](8,9.5){0.5}
+
+    \end{pspicture}}
+
+\vspace{1.5cm}
+
+Given the assumption of random variables drawn from the same time-invariant joint probability distribution, we then propose to use as \textbf{a measure of the
+degree of association of the connection between two neurons} $i$ and $j$, the  \textbf{
+\textit{Partial correlation}} coefficient $p_{i,j}$ between their corresponding
 random variables $X_i$ and $X_j$, defined by:
@@
 \end{align*}
-where $\Sigma^{-1}$, known as the precision or concentration matrix, is the inverse of the covariance matrix $\Sigma$ of $X$.\\
+where $\Sigma^{-1}$, known as the precision or concentration matrix, is the inverse of the covariance matrix $\Sigma$ of $X$.\\[2ex]
 
@@
 variables in $X$, i.e., $X_i \perp X_j|X^{-i,j}$ where $X^{-i,j}= X
-\setminus\{X_i,X_j\}$.
+\setminus\{X_i,X_j\}$.\\[3ex]
 
+\textbf{Advantages and drawbacks}:\\[2ex]
+
+\begin{minipage}{0.8\linewidth}
 \begin{itemize}
-\item[{\color{green} \cmark}] Only direct associations
-\item[{\color{green} \cmark}] Filter out spurious indirect effects
-\item[{\color{green} \cmark}] Symmetric (i.e. $p_{i,j}=p_{j,i}$)\\[5ex]
-\item[{\color{red} \xmark}] Edge orientation
-\item[{\color{red} \xmark}] Sensitive to the value of parameters in the filtering process
+\item[\vspace{1cm}{\color{green} \cmark}] Only \textbf{direct} associations
+\item[\vspace{1cm}{\color{green} \cmark}] Filter out spurious \textbf{indirect} effects
+\item[\vspace{1cm}{\color{green} \cmark}] \textbf{Symmetric} (i.e. $p_{i,j}=p_{j,i}$)\\[3ex]
+\item[\vspace{1cm}{\color{red} \xmark}] Edge orientation
+\item[\vspace{1cm}{\color{red} \xmark}] Sensitive to the value of parameters in the filtering process
 \end{itemize}
+\end{minipage}
 
@@
 
-\begin{textblock}{0.69}(0.01,0.78)
+\begin{textblock}{0.74}(0.01,0.78)
 
@@
 
-These results clearly show the importance of the filters and PCA (especially for AUPRC). Taking the average over
-various parameter settings gives an improvement of 10\% in AUPRC but
+These results \textbf{clearly} show the importance of the \textbf{filters and PCA} (especially for AUPRC). \textbf{Taking the average over
+various parameter settings} gives an improvement of 10\% in AUPRC but
 only a minor change in AUROC. The last row (``Full method'') shows the
-final performance of the method specifically tuned for the challenge
+final performance of the \textbf{method specifically tuned for the challenge}
 (see paper for all details). Although this
 tuning was decisive to obtain the best performance in the challenge,
-it does not significantly improve either AUROC or AUPRC.
+it does not significantly improve either AUROC or AUPRC.\\[1ex]
 
-Partial correlation and averaged partial correlation clearly outperform all other methods on all datasets. The
+\textbf{Partial correlation and averaged partial correlation clearly outperform all other methods on all datasets.} The
 improvement is more important in terms of AUPRC than in terms of AUROC. As
 expected, Pearson correlation performs very poorly in terms of AUPRC. GTE and
-GENIE3 work much better, but these two methods are nevertheless clearly below
-partial correlation.
+GENIE3 work much better, but \textbf{these two methods are nevertheless clearly below
+partial correlation}.
 
@@
 
-\begin{textblock}{0.28}(0.71,0.78)
+\begin{textblock}{0.22}(0.76,0.78)
 
@@
 
-In this paper, we outlined a simple but efficient methodology for the problem
-of connectome inference from calcium imaging data. Our approach consists of \textbf{two
-steps: 
-\begin{itemize}
-\item[] {\color{lightgreen}i) processing fluorescence data to detect neural peak activities; and}
-\item[] {\color{lightblue}ii) inferring the degree of association between neurons from partial 
-correlation statistics.}
-\end{itemize}}
-
-Its simplified variant outperforms other
-network inference methods while its optimized version proved to be the best method
-on the Connectomics Challenge. Given its simplicity and good performance, we
+We outlined a simple but efficient methodology for the problem
+of connectome inference from calcium imaging data consisting in processing the raw signals and then inferring the degree of association between neurons from partial correlation statistics. 
+Its \textbf{simplified variant outperforms other
+network inference methods} while \textbf{its optimized version proved to be the best method
+on the Connectomics Challenge}.
+Given its simplicity and good performance, we
 therefore believe that the methodology presented in this work
@@
 the field of connectome inference.
+
+% \textbf{All ressources} for  the ``Full Method'' and its simplified variant are \textbf{available} at \\
+
+% \begin{center}
+% \vspace{-0.9cm}
+% \textbf{{\fontsize{16}{14} \url{https://github.com/asutera/kaggle-connectomics}}}.
+% \end{center}
+
 \end{shaded}
@@
 
-\vspace{-0.3cm}
+\vspace{-1cm}
 
@@
 
-\begin{textblock}{1}(0.01,0.99)
-{\fontsize{12}{10}\textbf{Acknowledgments:}}
-{\fontsize{8}{10}\textbf{A. Joly and G. Louppe are research fellows of the FNRS, Belgium. A. Sutera is a
-recipient of an FRIA fellowship of FRS-FNRS, Belgium. This work is supported by
-PASCAL2 and the IUAP DYSCO, initiated by the Belgian State, Science Policy
-Office.}}
-\end{textblock}
+% \begin{textblock}{1}(0.01,0.99)
+% {\fontsize{12}{10}\textbf{Acknowledgments:}}
+% {\fontsize{8}{10}\textbf{A. Joly and G. Louppe are research fellows of the FNRS, Belgium. A. Sutera is a
+% recipient of an FRIA fellowship of FRS-FNRS, Belgium. This work is supported by
+% PASCAL2 and the IUAP DYSCO, initiated by the Belgian State, Science Policy
+% Office.}}
+% \end{textblock}
 

### 2014-09-08 oral/slides.tex
slides

@@
 \documentclass[final]{beamer}
+
+\usepackage{textpos}
 
@@
 
+\note{
+
+	Before the main part of this presentation, I would like to mention that we are not biologist and we are not expert of the connectome inference.
+We see the challenge as an inference problem and maybe in a naive point of view for some points.
+
+}
+
 \end{frame}
@@
 
+\vspace{-100pt}
 But this problem is \textbf{difficult} because of...
 
-\begin{tabular*}{\textwidth}{l r} \hline
-&\multirow{3}{*}{\includegraphics[width=2cm]{images/miss.png} \includegraphics[width=2cm]{images/hidden.png}}\\
+\begin{textblo}
+\begin{minipage}{0.95\linewidth}
+{\color{red} \textbf{masking} effects}
+\end{minipage}
 
+\begin{minipage}{0.95\linewidth}
 {\color{red} \textbf{masking} effects}
-& \\ 
-& \\
-\end{tabular}
+\end{minipage}
 
-% \begin{itemize}
+% \begin{tabular*}{\textwidth}{l r} \hline
+% &\multirow{3}{*}{\includegraphics[width=2cm]{images/miss.png} \includegraphics[width=2cm]{images/hidden.png}}\\
+
+% {\color{red} \textbf{masking} effects}
+% & \\ 
+% & \\
+
 % \item {\color{red} \textbf{masking} effects},

### 2014-09-12 oral/slides.tex
new version slides

@@
 
-\usepackage{textpos}
+\usepackage[absolute,overlay]{textpos}
 
@@
 \usepackage{url}
+
+\usepackage[pdf]{pstricks}
 
@@
 \selectcolormodel{cmyk}
+
+\setlength{\TPHorizModule}{\paperwidth}
+\setlength{\TPVertModule}{\paperheight}
 
@@
 
-\usepackage{multirow}
-
 \title{Simple connectome inference from partial\\[1ex]
 correlation statistics in calcium imaging}
-\author{{\small Antonio Sutera, Arnaud Joly, Vincent François-Lavet, Zixiao Aaron Qiu\\[1ex] Gilles Louppe, Damien Ersnt and Pierre Geurts.}}
+\author{{\small Antonio Sutera, Arnaud Joly, Vincent François-Lavet, Zixiao Aaron Qiu\\[1ex] Gilles Louppe, Damien Ernst and Pierre Geurts.}}
 \date{}
+
+\addtobeamertemplate{navigation symbols}{}{%
+    \usebeamerfont{footline}%
+    \usebeamercolor[fg]{footline}%
+    \hspace{1em}%
+    \insertframenumber/\inserttotalframenumber
+}
 
@@
 
-\begin{textblo}
-\begin{minipage}{0.95\linewidth}
-{\color{red} \textbf{masking} effects}
-\end{minipage}
+\begin{textblock}{0.3}(0.01,0.35)
+\begin{itemize}
+\item{\color{red}\textbf{masking} effects}
+\end{itemize}
+\end{textblock}
 
-\begin{minipage}{0.95\linewidth}
-{\color{red} \textbf{masking} effects}
-\end{minipage}
+\begin{textblock}{0.5}(0.55,0.25)
 
-% \begin{tabular*}{\textwidth}{l r} \hline
-% &\multirow{3}{*}{\includegraphics[width=2cm]{images/miss.png} \includegraphics[width=2cm]{images/hidden.png}}\\
+% \begin{pspicture}(20,20)
 
+% 	\pscircle[linewidth=2pt](10,10)
+
+%     \end{pspicture}
+% \scalebox{1}{\includegraphics[width=\paperwidth]{slides-pics.pdf}}
+
+\includegraphics[width=2cm]{images/miss.png} \includegraphics[width=2cm]{images/hidden.png}
+
+% \begin{pspicture}(0.99\textwidth,0.99\textheight)
+
+% \psframe[linewidth=0pt, linecolor=black!1](0,0)(\paperwidth,)
+
+%  	       	% \psline[linewidth=2pt,linecolor=lightblue, linestyle=dashed]{->}(0.5\paperwidth,\paperheight)(0.5\paperwidth,0)
+
+%     \end{pspicture}
+% \scalebox{1}{\includegraphics[width=\paperwidth]{slides-pics.pdf}}
+
+\end{textblock}
+
+\begin{textblock}{1}(0.01,0.55)
+\begin{itemize}
+\item {\color{red} \textbf{low} sampling rate}
+\end{itemize}
+\end{textblock}
+
+\begin{textblock}{1}(0.40,0.45)
+\includegraphics[width=3.5cm]{images/original_curve_sampling.pdf} $\Rightarrow$
+\includegraphics[width=3.5cm]{images/original_curve_sampling_2.pdf}
+\end{textblock}
+
+\begin{textblock}{1}(0.01,0.75)
+\begin{itemize}
+\item {\color{red} \textbf{slow} decay} of fluorescence.
+\end{itemize}
+\end{textblock}
+
+\begin{textblock}{1}(0.55,0.75)
+\includegraphics[width=3.5cm]{images/original_curve_gr_2.pdf}
+\end{textblock}
+
+% \begin{textblo}
+% \begin{minipage}{0.95\linewidth}
 % {\color{red} \textbf{masking} effects}
-% & \\ 
-% & \\
+% \end{minipage}
 
-% \item {\color{red} \textbf{masking} effects},
-% \includegraphics[width=2cm]{images/miss.png} \includegraphics[width=2cm]{images/hidden.png}
-% \item {\color{red} \textbf{low} sampling rate},
-% \includegraphics[width=4cm]{images/slowsamplingrate.png}
-% \item {\color{red} \textbf{slow} decay} of fluorescence.
-% \includegraphics[width=4cm]{images/original_curve_gr}
-% \end{itemize}
+% \begin{minipage}{0.95\linewidth}
+% {\color{red} \textbf{masking} effects}
+% \end{minipage}
+
+% % \begin{tabular*}{\textwidth}{l r} \hline
+% % &\multirow{3}{*}{\includegraphics[width=2cm]{images/miss.png} \includegraphics[width=2cm]{images/hidden.png}}\\
+
+% % {\color{red} \textbf{masking} effects}
+% % & \\ 
+% % & \\
+
+% % \item {\color{red} \textbf{masking} effects},
+% % \includegraphics[width=2cm]{images/miss.png} \includegraphics[width=2cm]{images/hidden.png}
+% % \item {\color{red} \textbf{low} sampling rate},
+% % \includegraphics[width=4cm]{images/slowsamplingrate.png}
+% % \item {\color{red} \textbf{slow} decay} of fluorescence.
+% % \includegraphics[width=4cm]{images/original_curve_gr}
+% % \end{itemize}
 
@@
 \item \textbf{Find} the network: the {\color{i6blue} {inference} method}.
-\item \textbf{Improve} the method: our {\color{i6blue} {tricks}}.
+\item \textbf{Improve} the method: {\color{i6blue} {averaging}} and {\color{i6blue} {tuning}}.
 \end{enumerate}\vskip5pt
@@
 
-\begin{overprint}
-\onslide<1> 
-a-b
+\begin{textblock}{1}(0.00,0.001)
+\begin{pspicture}(0.99\textwidth,0.99\textheight)
 
-\onslide<2>
-a-b-c
+\psframe[linewidth=0pt, linecolor=black!1](0,0)(\paperwidth,\paperheight)
 
-\onslide<3>
-a-b-c-d
+ 	       	% \psline[linewidth=2pt,linecolor=lightblue, linestyle=dashed]{->}(0.5\paperwidth,\paperheight)(0.5\paperwidth,0)
 
-\onslide<4>
-a-b-c-d-e
-\end{overprint}
+\psline[linewidth=2pt, linecolor=lightblue, linestyle=dashed]{->}(0.15\paperwidth,0.75\paperheight)(0.15\paperwidth,0.5\paperheight)
+
+\psline[linewidth=2pt, linecolor=lightblue, linestyle=dashed]{->}(0.85\paperwidth,0.5\paperheight)(0.85\paperwidth,0.60\paperheight)
+
+\psarc[linewidth=2pt,linecolor=lightblue, linestyle=dashed]{->}(0.33\paperwidth,0.40\paperheight){2.5}{180}{275}
+
+\psarc[linewidth=2pt,linecolor=lightblue, linestyle=dashed]{->}(0.65\paperwidth,0.40\paperheight){2.5}{270}{325}
+
+\psline[linewidth=4pt, linecolor=lightblue, linestyle=solid]{->}(0.30\paperwidth,0.75\paperheight)(0.7\paperwidth,0.75\paperheight)
+
+\rput(0.12\paperwidth,0.58\paperheight){{\color{lightblue} 1}}
+\rput(0.20\paperwidth,0.16\paperheight){{\color{lightblue} 2}}
+\rput(0.77\paperwidth,0.16\paperheight){{\color{lightblue} 3}}
+\rput(0.88\paperwidth,0.555\paperheight){{\color{lightblue} 4}}
+\rput(0.50\paperwidth,0.80\paperheight){{\color{lightblue} \textbf{Signal processing}}}
+
+    \end{pspicture}
+\scalebox{1}{\includegraphics[width=\paperwidth]{images/signal_processing.pdf}}
+\end{textblock}
+
+\begin{textblock}{1}(0.01,0.15)
+\includegraphics[width=3.5cm]{images/original_curve_2.pdf}
+\end{textblock}
+
+\begin{textblock}{1}(0.01,0.50)
+\includegraphics[width=3.5cm]{images/filter_curve_2.pdf}
+\end{textblock}
+
+\begin{textblock}{1}(0.35,0.75)
+\includegraphics[width=3.5cm]{images/diff_curve_2.pdf}
+\end{textblock}
+
+\begin{textblock}{1}(0.70,0.50)
+\includegraphics[width=3.5cm]{images/threshold_curve_3.pdf}
+\end{textblock}
+
+\begin{textblock}{1}(0.70,0.15)
+\includegraphics[width=3.5cm]{images/weights_curve_3.pdf}
+\end{textblock}
+
+\begin{textblock}{0.35}(0.3,0.3)
+
+{\footnotesize 
+\begin{enumerate}
+\item Applying a low-pass filter
+\item Applying a high-pass filer
+\item Applying a hard-threshold filter 
+\item Magnify the importance of spikes that occur in case of low global activity
+\end{enumerate}}
+
+\end{textblock}
+
+% \onslide<2>
+% a-b-c
+
+% \onslide<3>
+% a-b-c-d
+
+% \onslide<4>
+% a-b-c-d-e
+% \end{overprint}
 
@@
 \begin{columns}
-\begin{column}{0.5\linewidth}
-diag
+\begin{column}{0.55\linewidth}
+
+\includegraphics[width=6cm]{images/network.pdf}
+\vspace{10pt}
+\textbf{\textit{Partial correlation}} coefficient $p_{i,j}$ between neurons $i$ and $j$ defined by:
+\begin{align*}
+p_{i,j} =
+-\frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii} \Sigma^{-1}_{jj}}}, \label{eq:inverse}
+\end{align*}
+
 \end{column}
-\begin{column}{0.5\linewidth}
 
+\begin{column}{0.45\linewidth}
+
+\textbf{Advantages and drawbacks}:
 \begin{itemize}
@@
 \item[{\color{green} \cmark}] Filter out spurious indirect effects
-\item[{\color{green} \cmark}] Symmetric \\[5ex]
+\item[{\color{green} \cmark}] Symmetric 
+\item[{\color{green} \cmark}] Easy to compute \\ (with lots of data) \\[2ex]
 \item[{\color{red} \xmark}] Edge orientation
@@
 \begin{frame}
-\frametitle{Each stage of our solution is good!}
+\frametitle{Each stage of our solution brings some improvement}
 
-\begin{table}[t]
-\caption{Performance on \textit{normal-1,2,3,4} with partial correlation and different filtering functions.}
-\label{tab:comparison}
-\centering
-\tiny
-\begin{tabular}{| l | c c c c | c c c c |}
-\hline
-& \multicolumn{4}{c|}{AUROC} & \multicolumn{4}{c|}{AUPRC} \\
-\textit{Method} $\backslash$ \textit{normal-} & \textit{1} & \textit{2} & \textit{3} & \textit{4} & \textit{1} & \textit{2} & \textit{3} & \textit{4} \\
-\hline
-\hline
-No  filtering       					& 0.777 & 0.767 & 0.772 & 0.774 & 0.070 & 0.064 & 0.068 & 0.072\\
-$ h \circ g \circ f_1$                  & 0.923 & 0.925 & 0.923 & 0.922 & 0.311 & 0.315 & 0.313 & 0.304\\
-$ w \circ h \circ g \circ f_1$          & 0.931 & 0.929 & 0.928 & 0.926 & 0.326 & 0.323 & 0.319 & 0.303\\
-+ PCA         							& 0.932 & 0.930 & 0.928 & 0.926 & 0.355 & 0.353 & 0.350 & 0.333\\
-Averaging           					& 0.937 & 0.935 & 0.935 & 0.931 & 0.391 &  0.390 &  0.385 & 0.375\\
-Full method           					& \textbf{0.943} & \textbf{0.942} & \textbf{0.942} & \textbf{0.939} & \textbf{0.403} & \textbf{0.404} & \textbf{0.398} & \textbf{0.388}\\
-\hline
-\end{tabular}
-\end{table}
+\begin{center}
+\textit{Average scores on normal-{1,2,3,4} datasets.
+}
+\includegraphics[width=8cm]{images/data_stage.png}
+\end{center}
+
+% \begin{table}[t]
+% \caption{Performance on \textit{normal-1,2,3,4} with partial correlation and different filtering functions.}
+% \label{tab:comparison}
+% \centering
+% \tiny
+% \begin{tabular}{| l | c c c c | c c c c |}
+% \hline
+% & \multicolumn{4}{c|}{AUROC} & \multicolumn{4}{c|}{AUPRC} \\
+% \textit{Method} $\backslash$ \textit{normal-} & \textit{1} & \textit{2} & \textit{3} & \textit{4} & \textit{1} & \textit{2} & \textit{3} & \textit{4} \\
+% \hline
+% \hline
+% No  filtering       					& 0.777 & 0.767 & 0.772 & 0.774 & 0.070 & 0.064 & 0.068 & 0.072\\
+% $ h \circ g \circ f_1$                  & 0.923 & 0.925 & 0.923 & 0.922 & 0.311 & 0.315 & 0.313 & 0.304\\
+% $ w \circ h \circ g \circ f_1$          & 0.931 & 0.929 & 0.928 & 0.926 & 0.326 & 0.323 & 0.319 & 0.303\\
+% + PCA         							& 0.932 & 0.930 & 0.928 & 0.926 & 0.355 & 0.353 & 0.350 & 0.333\\
+% Averaging           					& 0.937 & 0.935 & 0.935 & 0.931 & 0.391 &  0.390 &  0.385 & 0.375\\
+% Full method           					& \textbf{0.943} & \textbf{0.942} & \textbf{0.942} & \textbf{0.939} & \textbf{0.403} & \textbf{0.404} & \textbf{0.398} & \textbf{0.388}\\
+% \hline
+% \end{tabular}
+% \end{table}
 
@@
 
-\begin{table}[t]
+\begin{center}
+\textit{Average scores on normal-{1,2,3,4} datasets.
+}
+\includegraphics[width=9cm]{images/data_method.png}
+\end{center}
+% \begin{table}[t]
 
-\caption{Performance on \textit{normal-1,2,3,4} with different methods.}
-\label{tab:comparison}
-\centering
-\tiny
-\begin{tabular}{| l | c c c c | c c c c |}
-\hline
-& \multicolumn{4}{c|}{AUROC} & \multicolumn{4}{c|}{AUPRC} \\
-\textit{Method} $\backslash$ \textit{normal-} & \textit{1} & \textit{2} & \textit{3} & \textit{4} & \textit{1} & \textit{2} & \textit{3} & \textit{4} \\
-\hline
-\hline
-Averaging           					& 0.937 & 0.935 & 0.935 & 0.931 & 0.391 &  0.390 &  0.385 & 0.375\\
-Full method           					& \textbf{0.943} & \textbf{0.942} & \textbf{0.942} & \textbf{0.939} & \textbf{0.403} & \textbf{0.404} & \textbf{0.398} & \textbf{0.388}\\
-\hline
-PC & 0.886 & 0.884 & 0.891 &  0.877 & 0.153 & 0.145 & 0.170 & 0.132\\
-GTE & 0.890 & 0.893 & 0.894 & 0.873 & 0.171 & 0.174 & 0.197 & 0.142\\
-GENIE3 & 0.892 & 0.891 & 0.887 & 0.887 & 0.232 & 0.221 & 0.237 & 0.215 \\
-\hline
-\end{tabular}
-\end{table}
+% \caption{Performance on \textit{normal-1,2,3,4} with different methods.}
+% \label{tab:comparison}
+% \centering
+% \tiny
+% \begin{tabular}{| l | c c c c | c c c c |}
+% \hline
+% & \multicolumn{4}{c|}{AUROC} & \multicolumn{4}{c|}{AUPRC} \\
+% \textit{Method} $\backslash$ \textit{normal-} & \textit{1} & \textit{2} & \textit{3} & \textit{4} & \textit{1} & \textit{2} & \textit{3} & \textit{4} \\
+% \hline
+% \hline
+% Averaging           					& 0.937 & 0.935 & 0.935 & 0.931 & 0.391 &  0.390 &  0.385 & 0.375\\
+% Full method           					& \textbf{0.943} & \textbf{0.942} & \textbf{0.942} & \textbf{0.939} & \textbf{0.403} & \textbf{0.404} & \textbf{0.398} & \textbf{0.388}\\
+% \hline
+% PC & 0.886 & 0.884 & 0.891 &  0.877 & 0.153 & 0.145 & 0.170 & 0.132\\
+% GTE & 0.890 & 0.893 & 0.894 & 0.873 & 0.171 & 0.174 & 0.197 & 0.142\\
+% GENIE3 & 0.892 & 0.891 & 0.887 & 0.887 & 0.232 & 0.221 & 0.237 & 0.215 \\
+% \hline
+% \end{tabular}
+% \end{table}
 

### 2014-10-14 crowdsource/article.tex
crowdsource

--- 2014-07-28 article.tex
@@
 
-\maketitle
-
-\vspace{-1cm}
-\begin{abstract}
-In this work, we propose a simple yet effective solution to the problem of
-connectome inference in calcium imaging data. The proposed algorithm consists of
-two steps. First, processing the raw signals to detect neural peak activities.
-Second, inferring the degree of association between neurons from partial
-correlation statistics. This paper summarises the methodology that led us to
-win the Connectomics Challenge, proposes a simplified version of our method, and
-finally compares our results with respect to other inference methods.
-\end{abstract}
-
-\begin{keywords}
-Connectomics - Network inference - Partial correlation
-\end{keywords}
-
-\section{Introduction}\label{sec:intro}
-
-The human brain is a complex biological organ made of about 100 billion of
-neurons, each connected to, on average, 7,000 other neurons
-\citep{pakkenberg2003aging}. Unfortunately, direct observation of the
-connectome, the wiring diagram of the brain, is not yet technically feasible.
-Without being perfect, calcium imaging currently allows for real-time and
-simultaneous observation of neuron activity from thousands of neurons,
-producing individual time-series representing their fluorescence intensity.
-From these data, the connectome inference problem amounts to retrieving the
-synaptic connections between neurons on the basis of the fluorescence time-series. This problem is difficult to solve because of experimental issues,
-including masking effects (i.e., some of the neurons are not observed or
-confounded with others), the low sampling rate of the optical device with
-respect to the neural activity speed, or the slow decay of fluorescence.
-
-Formally, the connectome can be represented as a directed graph $G=(V,E)$,
-where $V$ is a set of $p$ nodes representing neurons, and $E \subseteq
-\left\{(i, j) \in V \times V\right\}$ is a set of edges representing direct
-synaptic connections between neurons. Causal interactions are expressed by the
-direction of edges: $(i, j) \in E$ indicates that the state of neuron $j$ might
-be caused by the activity of neuron $i$. In those terms,  the connectome
-inference problem is formally stated as follows:  \textit{Given the sampled
-observations $\{ x^t_i \in \mathbb{R} | i \in V, t = 1, \dots, T \}$ of $p$
-neurons for $T$ time intervals, the goal is to infer the set $E$ of connections
-in $G$.}
-
-In this paper, we present a simplified - and almost as good - version of the
-winning method\footnote{Code available at \url{https://github.com/asutera/kaggle-connectomics}} of the Connectomics
-Challenge\footnote{\url{http://connectomics.chalearn.org}}, as a simple and
-theoretically grounded approach based on signal processing techniques and
-partial correlation statistics. The paper is structured as follows:
-Section~\ref{sec:filter} describes the signal processing methods applied on
-fluorescent calcium time-series; Section \ref{sec:inference} then presents the
-proposed approach and its theoretical properties; Section~\ref{sec:results}
-provides an empirical analysis and comparison with other network inference
-methods, while finally, in Section~\ref{sec:conclusion} we discuss our work and
-provide further research directions. Additionally,
-Appendix~\ref{app:optimized} further describes, in full detail, our actual
-winning method which gives slightly better results than the method presented in
-this paper, at the cost of parameter tuning. Appendix~\ref{app:supp} provides supplementary results on other datasets.
-
-\section{Signal processing} \label{sec:filter}
-
-Under the simplifying assumption that neurons are on-off units, characterised
-by short periods of intense activity, or peaks, and longer periods of
-inactivity, the first part of our algorithm consists of cleaning the raw
-fluorescence data.
-More specifically, time-series are processed using standard
-signal processing filters in order to : (i) remove noise mainly due to fluctuations independent of calcium, calcium fluctuations independent of spiking activity, calcium fluctuations in nearby tissues that have been mistakenly captured, or simply by the imaging process ; (ii) to account for fluorescence low decay ; and (iii) to reduce the importance of
-high global activity in the network. The overall process is illustrated in
-Figure~\ref{fig:filtered-signal}.
-
-\begin{figure}
-\centering
-\subfigure[Raw signal]{\includegraphics[width=0.3\textwidth]{original_curve.pdf} \label{fig:original_curve}}
-\subfigure[Low-pass filter $f_1$]{\includegraphics[width=0.3\textwidth]{filter_curve.pdf} \label{fig:lp_curve}}
-\subfigure[High-pass filter $g$]{\includegraphics[width=0.3\textwidth]{diff_curve.pdf} \label{fig:hp_curve}}\\
-\subfigure[Hard-threshold filter $h$]{\includegraphics[width=0.3\textwidth]{threshold_curve.pdf} \label{fig:threshold_curve}}
-\subfigure[Global regularization $w$]{\includegraphics[width=0.3\textwidth]{weights_curve.pdf} \label{fig:weight_curve}}
-\caption{Signal processing pipeline for extracting peaks from the raw fluorescence data.}
-\label{fig:filtered-signal}
-\end{figure}
-
-As Figure~\ref{fig:original_curve} shows, the raw
-fluorescence signal is very noisy due to light scattering artifacts that
-usually affect the quality of the recording~\citep{lichtman2011big}.
-Accordingly, the first step of our pipeline is to smoothe the signal, using
-one of the following low-pass filters for filtering out high frequency noise:
-\begin{align}
-f_1(x^t_i) &= x^{t-1}_i + x^t_i + x^{t+1}_i, \label{eq:symetric-median} \\
-f_2(x^t_i) &= 0.4 x^{t-3}_i + 0.6 x^{t-2}_i + 0.8 x^{t-1}_i + x_i^t.
-\label{eq:weighted-asymetric-median}
-\end{align}
-These filters are standard in the signal processing field \citep{kaiser1977data, oppenheim1983signals}. For the purposes of illustration, the effect of the filter $f_1$ on the signal
-is shown in Figure \ref{fig:lp_curve}.
-
-Furthermore, short spikes, characterized by a high
-frequency, can be seen as an indirect indicator of neuron communication, while low frequencies of the signal mainly correspond to the slow
-decay of fluorescence. To have a signal that only has high magnitude around instances where the spikes occur, the second step of our pipeline transforms the time-series into its backward
-difference
-\begin{align}
-g(x^{t}_{i}) &= x^{t}_i - x^{t-1}_i, \label{eq:high-pass-filter}
-\end{align}
-as shown in Figure \ref{fig:hp_curve}.
-
-To filter out small variations in the signal obtained after applying the
-function $g$, as well as to eliminate negative values, we use the following
-hard-threshold filter
-\begin{align}\label{eqn:hfilter}
-h(x^{t}_i) &= x^{t}_i \mathbb{1}(x^{t}_i \geq \tau) \text{ with } \tau > 0,
-\end{align}
-yielding Figure \ref{fig:threshold_curve} where $\tau$ is the threshold parameter and $\mathbb{1}$ is the indicator function.
-As can be seen, the processed signal only contains clean spikes.
-
-The objective of the last step of our filtering procedure is to decrease the
-importance of spikes that occur when there is high global activity in the
-network with respect to  spikes that occur during normal activity. Indeed, we
-have conjectured that when a large part of the network is firing, the rate at
-which observations are made is not high enough to be able to detect
-interactions, and that it would therefore be preferable to lower their
-importance by changing their magnitude appropriately. Additionally, it is
-well-known that neurons may also spike because of a high global activity
-\citep{stetter2012model}. In such  context, detecting pairwise neuron
-interactions from the firing activity is meaningless. As such,
-the signal output by $h$ is finally applied to the following function
-\begin{align}
- w(x^{t}_i) &= (x^{t}_i + 1 )^{1 + \frac{1}{\sum_{j} x^{t}_j}}, \label{eq:magnify-filter}
-\end{align}
-whose effect is to magnify the importance of spikes that occur in cases of low
-global activity (measured by $\sum_{j} x^{t}_j$), as observed, for instance,
-around $t=4\text{s}$ in Figure~\ref{fig:weight_curve}. Note the particular case where there
-is no activity, i.e., $\sum_{j} x^{t}_j = 0$, is solved by setting $w(x^{t}_i)
-= 1$.
-
-To summarise, the full signal processing pipeline of our simplified approach is defined by the composed function $w \circ h \circ g \circ
-f_1$ (resp. $f_2$). When applied to the raw signal of Figure
-\ref{fig:original_curve}, it outputs the signal shown in Figure
-\ref{fig:weight_curve}.
-
-\section{Connectome inference from partial correlation statistics}
-\label{sec:inference}
-
-Our procedure to infer connections between neurons first assumes that
-the (filtered) fluorescence concentrations of all $p$ neurons at each
-time point can be modelled as a set of random variables $X = \{X_1,
-\dots, X_p\}$ that are independently drawn from the same time-invariant
-joint probability distribution $P_X$. 
-As a consequence, our inference method does not exploit the time-ordering of the observations (although time-ordering is exploited by
-the filters).
-
-Given this assumption, we then propose to use as a measure of the
-strength of the connection between two neurons $i$ and $j$, the
-\textit{Partial correlation} coefficient $p_{i,j}$ between their corresponding
-random variables $X_i$ and $X_j$, defined by:
-\begin{equation}
-p_{i,j} =
--\frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii} \Sigma^{-1}_{jj}}}, \label{eq:inverse}
-\end{equation}
-where $\Sigma^{-1}$, known as the precision or concentration matrix, is the inverse of the covariance matrix $\Sigma$ of $X$. 
-Assuming that the distribution $P_X$ is a multivariate Gaussian
-distribution ${\cal N}(\mu,\Sigma)$, it can be shown that $p_{i,j}$ is
-zero if and only if $X_i$ and $X_j$ are independent given all other
-variables in $X$, i.e., $X_i \perp X_j|X^{-i,j}$ where $X^{-i,j}= X
-\setminus\{X_i,X_j\}$. Partial correlation thus measures conditional
-dependencies between variables ; therefore it should naturally only detect direct associations
-between neurons and filter out spurious indirect effects. The interest
-of partial correlation as an association measure has already been
-shown for the inference of gene regulatory networks
-\citep{de2004discovery,Schafer:2005}.
-Note that the partial correlation statistic is symmetric
-(i.e. $p_{i,j}=p_{j,i}$). Therefore, our approach cannot identify the
-direction of the interactions between neurons. We will see in
-Section~\ref{sec:results} why this only slightly affects its
-performance, with respect to the metric used in the Connectomics
-Challenge.
-
-Practically speaking, the computation of all $p_{i,j}$ coefficients using Equation
-\ref{eq:inverse} requires the estimation of the covariance matrix $\Sigma$
-and then computing its inverse. Given that typically we have more
-samples than neurons, the covariance matrix can be inverted in a
-straightforward way. We nevertheless obtained some improvement by
-replacing the exact inverse with an approximation using only the $M$
-first principal components \citep{bishop2006pattern} (with
-$M=0.8 p$ in our experiments, see Appendix~\ref{app:pca}).
-
-Finally, it should be noted that the performance of our simple method appears to
-be quite sensitive to the values of parameters (e.g., choice of $f_1$ or $f_2$
-or the value of the threshold $\tau$) in the combined function of the
-filtering and inferring processes. One approach, further referred
-to as \textit{Averaged Partial correlation} statistics, for improving
-its robustness is to average correlation statistics over various
-values of the parameters, thereby reducing the variance of its
-predictions. Further details about parameter selection are provided in
-Appendix~\ref{app:optimized}.
-
-\section{Experiments} \label{sec:results}
-\paragraph{Data and evaluation metrics.}
-
-We report here experiments on the \textit{normal-1,2,3}, and \textit{4}
-datasets provided by the organisers of the Connectomics Challenge (see
-Appendix~\ref{app:supp} for experiments on other datasets). Each of
-these datasets is obtained from the simulation \citep{stetter2012model} of
-different neural networks of 1,000 neurons and approximately 15,000 edges (i.e., a
-network density of about 1.5\%). Each neuron is described by a calcium
-fluorescence time-series of length $T=179500$. All inference methods compared
-here provide a ranking of all pairs of neurons according to some association score. To assess the quality of this ranking, we compute both ROC and
-precision-recall curves against the ground-truth network, which are represented by
-the area under the curves and respectively  denoted AUROC and AUPRC. Only
-the AUROC score was used to rank the challenge participants, but the precision-recall curve has been shown to be a more sensible metric for network
-inference, especially when network density is small (see e.g.,
-\cite{schrynemackers2013protocols}). Since neurons are not self-connected in
-the ground-truth networks (i.e., $(i, i) \not \in E, \forall i \in V$), we
-have manually set the score of such edges to the minimum possible association
-score before computing ROC and PR curves.
-
-\paragraph{Evaluation of the method.}
-
-The top of Table \ref{tab:comparison} reports AUROC and AUPRC for all
-four networks using, in each case, partial correlation with different
-filtering functions. Except for the last two rows that use PCA, the
-exact inverse of the covariance matrix was used in each case. These
-results clearly show the importance of the filters. AUROC increases in
-average from 0.77 to 0.93. PCA does not really affect AUROC scores, but
-it significantly improves AUPRC scores. Taking the average over
-various parameter settings gives an improvement of 10\% in AUPRC but
-only a minor change in AUROC. The last row (``Full method'') shows the
-final performance of the method specifically tuned for the challenge
-(see Appendix \ref{app:optimized} for all details). Although this
-tuning was decisive to obtain the best performance in the challenge,
-it does not significantly improve either AUROC or AUPRC.
-
-\begin{table}[t]
-
-\caption{Top: Performance on \textit{normal-1,2,3,4} with partial correlation and different filtering functions.
-Bottom: Performance on \textit{normal-1,2,3,4} with different methods.}
-\label{tab:comparison}
-\centering
-\small
-\begin{tabular}{| l | c c c c | c c c c |}
-\hline
-& \multicolumn{4}{c|}{AUROC} & \multicolumn{4}{c|}{AUPRC} \\
-\textit{Method} $\backslash$ \textit{normal-} & \textit{1} & \textit{2} & \textit{3} & \textit{4} & \textit{1} & \textit{2} & \textit{3} & \textit{4} \\
-\hline
-\hline
-No  filtering       					& 0.777 & 0.767 & 0.772 & 0.774 & 0.070 & 0.064 & 0.068 & 0.072\\
-$ h \circ g \circ f_1$                  & 0.923 & 0.925 & 0.923 & 0.922 & 0.311 & 0.315 & 0.313 & 0.304\\
-$ w \circ h \circ g \circ f_1$          & 0.931 & 0.929 & 0.928 & 0.926 & 0.326 & 0.323 & 0.319 & 0.303\\
-+ PCA         							& 0.932 & 0.930 & 0.928 & 0.926 & 0.355 & 0.353 & 0.350 & 0.333\\
-Averaging           					& 0.937 & 0.935 & 0.935 & 0.931 & 0.391 &  0.390 &  0.385 & 0.375\\
-Full method           					& \textbf{0.943} & \textbf{0.942} & \textbf{0.942} & \textbf{0.939} & \textbf{0.403} & \textbf{0.404} & \textbf{0.398} & \textbf{0.388}\\
-\hline
-PC & 0.886 & 0.884 & 0.891 &  0.877 & 0.153 & 0.145 & 0.170 & 0.132\\
-GTE & 0.890 & 0.893 & 0.894 & 0.873 & 0.171 & 0.174 & 0.197 & 0.142\\
-GENIE3 & 0.892 & 0.891 & 0.887 & 0.887 & 0.232 & 0.221 & 0.237 & 0.215 \\
-\hline
-\end{tabular}
-\end{table}
-
-\paragraph{Comparison with other methods.}
-
-At the bottom of Table \ref{tab:comparison}, we provide as a comparison the
-performance of three other methods: standard (Pearson) correlation (PC),
-generalised transfer entropy (GTE), and GENIE3. ROC and PR curves on the
-\textit{normal-2} network are shown for all methods in Figure\ref{fig:curves}. Pearson correlation measures the unconditional linear
-(in)dependence between variables and it should thus not be able to filter out
-indirect interactions between neurons. GTE \citep{stetter2012model} was
-proposed as a baseline for the challenge. This method builds on Transfer
-Entropy to measure the association between two neurons. Unlike our approach, it
-can predict the direction of the edges. GENIE3 \citep{huynhthu2010inferring} is
-a gene regulatory network inference method that was the best performer in the
-DREAM5 challenge \citep{marbach2012}. When transposed to neural networks, this
-method uses the importance score of variable $X_i$ in a Random Forest model trying to
-predict $X_j$ from all variables in $X\setminus X_j$ as a confidence score for the edge going from neuron $i$ to neuron
-$j$. However, to reduce the
-computational cost of this method, we had to limit each tree in the
-Random Forest model to a maximum depth of 3. This constraint has a potentially
-severe effect on the performance of this method with respect to the use of
-fully-grown trees. PC and GENIE3 were applied to the time-series filtered using the functions $w\circ h\circ g$ and $h\circ g\circ f_1$ (which
-gave the best performance), respectively. For GENIE3, we built 10,000 trees per neuron and we
-used default settings for all other parameters (except for the maximal tree
-depth). For GTE, we reproduced the exact same setting (conditioning level and
-pre-processing) that was used by the organisers of the challenge.
-
-Partial correlation and averaged partial correlation clearly outperform all
-other methods on all datasets (see Table \ref{tab:comparison} and Appendix \ref{app:supp}). The
-improvement is more important in terms of AUPRC than in terms of AUROC. As
-expected, Pearson correlation performs very poorly in terms of AUPRC. GTE and
-GENIE3 work much better, but these two methods are nevertheless clearly below
-partial correlation. Among these two methods, GTE is slightly better in terms
-of AUROC, while GENIE3 is significantly better in terms of AUPRC. Given that we
-had to limit this latter method for computational reasons, these results are
-very promising and a comparison with the full GENIE3 approach is certainly part
-of our future works.
-
-The fact that our method is unable to predict edge directions does not seem to
-be a disadvantage with respect to GTE and GENIE3. Although partial correlation
-scores each edge, and its opposite, similarly, it can reach precision values
-higher than 0.5 (see Figure \ref{fig:curves}(b)), suggesting that it mainly ranks high
-pairs of neurons that interact in both directions.  It is interesting also to
-note that, on \textit{normal-2}, a method that perfectly predicts the
-undirected network (i.e., that gives a score of $1$ to each pair $(i,j)$ such that
-$(i,j)\in E$ or $(j,i)\in E$, and $0$ otherwise) already reaches an AUROC as high
-as $0.995$ and an AUPRC of $0.789$.
-\begin{figure}[t]
-\centering
-\subfigure[ROC curves]{\includegraphics[width=0.45\textwidth]{curve_roc} \label{fig:roc_curve}}
-\subfigure[Precision-recall curves]{\includegraphics[width=0.45\textwidth]{curve_pr} \label{fig:pr_curve}}
-\caption{ROC (left) and PR (right) curves on \textit{normal-2} for the compared methods. Areas under the curves are reported in the legend.}
-\label{fig:curves}
-\end{figure}
-
-\section{Conclusions} \label{sec:conclusion}
-
-In this paper, we outlined a simple but efficient methodology for the problem
-of connectome inference from calcium imaging data. Our approach consists of two
-steps: (i) processing fluorescence data to detect neural peak activities; and
-(ii) inferring the degree of association between neurons from partial
-correlation statistics. Its simplified variant outperforms other
-network inference methods while its optimized version proved to be the best method
-on the Connectomics Challenge. Given its simplicity and good performance, we
-therefore believe that the methodology presented in this work
-would constitute a solid and easily-reproducible baseline for further work in
-the field of connectome inference.
-
-\paragraph{Acknowledgments}
-A. Joly and G. Louppe are research fellows of the FNRS, Belgium.  A. Sutera is a
-recipient of an FRIA fellowship of FRS-FNRS, Belgium. This work is supported by
-PASCAL2 and the IUAP DYSCO, initiated by the Belgian State, Science Policy
-Office.
-
-\newpage
-\clearpage
-
-\bibliography{references}
-
-\newpage
-\clearpage
-
-\appendix
-
-\section{Description  of the ``Full method''}
-\label{app:optimized}
-
-This section provides a detailed description of the method specifically tuned
-for the Connectomics Challenge. We restrict our description to the
-differences with respect to the simplified method presented in the main
-paper. Most parameters were tuned so as to maximize AUROC on the
-\textit{normal-1} dataset and our design choices were validated by monitoring
-the AUROC obtained by the 145 entries we submitted during the
-challenge. Although the tuned method performs better than the simplified one on
-the challenge dataset, we believe that the tuned method clearly overfits the
-simulator used to generate the challenge data and that the simplified method
-should work equally well on new independent datasets. We nevertheless provide
-the tuned method here for reference purposes. Our implementation of the tuned
-method is available at \url{https://github.com/asutera/kaggle-connectomics}.
-
-This appendix is structured as follows: Section~\ref{sapp:signal} describes
-the differences in terms of signal processing. Section~\ref{sapp:averaging}
-then provides a detailed presentation of the averaging approach.
-Section~\ref{sapp:connectome} presents an approach to correct the $p_{i,j}$
-values so as to take into account the edge directionality. Finally,
-Section~\ref{sapp:results} presents some experimental results to validate the
-different steps of our proposal.
-
-\subsection{Signal processing}
-\label{sapp:signal}
-
-In Section~\ref{sec:filter}, we introduced four filtering functions ($f$, $g$,
-$h$, and $w$) that are composed in sequence (i.e., $w \circ h \circ g \circ
-f$) to provide the signals from which to compute partial correlation
-statistics. Filtering is modified as follows in the tuned method:
-
-\begin{itemize}
-\item In addition to $f_1$ and $f_2$ (Equations \ref{eq:symetric-median} and
-  \ref{eq:weighted-asymetric-median}), two alternative low-pass filters $f_3$
-  and $f_4$ are considered:
-\begin{align}
-f_3(x^t_i) &= x^{t-1}_i + x^{t}_i + x^{t+1}_i + x^{t+2}_i, \label{eq:asymetric-median-forward} \\
-f_4(x^t_i) &=  x_i^t + x^{t+1}_i  + x^{t+2}_i + x^{t+3}_i. \label{eq:asymetric-median}
-\end{align}
-\item An additional filter $r$ is applied to smoothe differences in peak magnitudes
-  that might remain after the application of the hard-threshold filter $h$:
-\begin{align}
-r(x^t_i) = (x_i^t)^c,
-\end{align}
-with $c=0.9$.
-\item Filter $w$ is replaced by a more complex filter $w^*$ defined as:
-\begin{align}
- w^*(x^{t}_i) &= {(x^{t}_i + 1 )^{\left (1 + \frac{1}{\sum_{j} x^{t}_j}\right )}}^{k(\sum_{j} x^{t}_j)}
-\end{align}
-where the function $k$ is a piecewise linear function optimised separately for
-each filter $f_1$, $f_2$, $f_3$ and $f_4$ (see the implementation for full
-details). Filter $w$ in the simplified method is a special case of $w^*$ with
-$k(\sum_j x_j^t)=1$.
-\end{itemize}
-The pre-processed time-series are then obtained by the application of the
-following function: $w^*\circ r \circ h \circ g \circ f_i$ (with $i=1$, 2, 3, or 4).
-
-\subsection{Weighted average of partial correlation statistics}
-\label{sapp:averaging}
-
-As discussed in Section \ref{sec:inference}, the performance of the method (in
-terms of AUROC) is sensitive to the value of the parameter $\tau$ of the
-hard-threshold filter $h$ (see Equation \ref{eqn:hfilter}), and to the choice
-of the low-pass filter (among $\{f_1, f_2, f_3, f_4\}$).
-As in the simplified method, we have averaged the partial correlation statistics obtained for all the pairs $(\tau,\mbox{low-pass filter}) \in \{0.100,0.101,\ldots,0.209\}\times \{f_1, f_2, f_3, f_4\}$.
-
-Filters $f_1$ and $f_2$ display similar performances and thus were given similar
-weights (i.e., resp. $0.383$ and $0.345$). These weights were chosen equal to the weights selected for the simplified method. In contrast, filters $f_3$
-and $f_4$ turn out, individually, to be less competitive and were therefore given
-less importance in the weighted average (i.e., resp. $0.004$ and $0.268$). Yet, as further shown in
-Section~\ref{sapp:results}, combining all $4$ filters proves to marginally
-improve performance with respect to using only $f_1$ and $f_2$.
-
-\subsection{Prediction of edge orientation}
-\label{sapp:connectome}
-
-Partial  correlation  statistics is  a  symmetric  measure, while  the
-connectome is a directed graph. It  could thus be beneficial to try to
-predict edge orientation. In this section, we present an heuristic that
-modifies the  $p_{ij}$ computed  by the  approach described  before which
-takes into account directionality.
-
-This approach is based on the following
-observation. The rise of fluorescence of a neuron indicates its
-activation. If another neuron is activated after a slight delay, this
-could be a consequence of the activation of the first neuron and
-therefore indicates a directed link in the connectome from the first to
-the second neuron.  Given this observation, we have computed the following term for every
-pair $(i,j)$:
-\begin{align}
-s_{i,j} = \sum_{t=1}^{T - 1} \mathbb{1}((x_j^{t+1} - x_i^t) \in \left[\phi_1, \phi_2\right])
-\end{align}
-that could be interpreted as an image of the  number of times
-that neuron $i$ activates neuron $j$. $\phi_1$ and $\phi_2$ are
-parameters whose values have been chosen in our experiments equal to
-$0.2$ and $0.5$, respectively. Their role is to
-define when the difference between $x_j^{t+1}$  and $x_i^t$ can
-indeed be assimilated to an event for which neuron $i$ activates neuron
-$j$.
-
-Afterwards, we have computed the difference between $s_{i,j}$ and
-$s_{j,i}$, that we call $z_{i,j}$, and used this difference to modify  $p_{i,j}$ and
-$p_{j,i}$ so as to take into account directionality. Naturally, if
-$z_{i,j}$ is greater  (smaller) than $0$, we may conclude that should there  be an
-edge between $i$ and $j$, then this edge would have to be oriented
-from $i$ to $j$ ($j$ to $i$).
-
-This suggests the new association matrix $r$:
-\begin{align}
-r_{i,j} =  \mathbb{1}(z_{i,j} > \phi_3)  *  p_{i,j}
-\end{align}
-where $\phi_3 >0$ is another parameter. We discovered that this new
-matrix $r$ was not providing good results, probably due to the fact that
-directivity was not rewarded well enough in the challenge.
-
-This has lead us to investigate other ways for exploiting the
-information about directionality contained in the matrix $z$. One of
-those ways that gave good performance was to use as an association
-matrix:
-\begin{align}
-q_{i,j} = weight * p_{i,j} + (1-weight) * z_{i,j}
-\label{eqn:qij}
-\end{align}
-with  $weight$ chosen close to 1 ($weight=0.997$). Note that with
-values for $weight$ close to 1,   matrix $q$ only uses the
-information to a minimum about directivity contained in $z$ to modify the  partial
-correlation matrix $p$. We tried smaller values for $weight$ but those
-provided poorer results.
-
-It was  this association matrix $q_{i,j}$ that actually led to the
-best results of the challenge, as shown in Table \ref{tab:directivity}
-of Section~\ref{sapp:results}.
-
-\subsection{Experiments}
-\label{sapp:results}
-
-\paragraph{On the interest of low-pass filters $f_3$ and $f_4$.}
-
-As reported in Table~\ref{tab:f3f4}, averaging over all low-pass filters leads
-to better AUROC scores than averaging over only two low-pass filters, i.e., $f_1$ and
-$f_2$. However this slightly reduces AUPRC.
-
-\begin{table}[ht]
-\caption{Performance on \textit{normal-1, 2, 3, or 4} with partial correlation with different averaging approaches.}
-\label{tab:f3f4}
-\centering
-\small
-\begin{tabular}{| l | c c c c | c c c c |}
-\hline
-& \multicolumn{4}{c|}{AUROC} & \multicolumn{4}{c|}{AUPRC} \\
-\textit{Averaging} $\backslash$ \textit{normal-} & \textit{1} & \textit{2} & \textit{3} & \textit{4} & \textit{1} & \textit{2} & \textit{3} & \textit{4} \\
-\hline
-\hline
- with $f_1$, $f_2$ & 0.937 & 0.935 & 0.935 & 0.931 & 0.391 &  \textbf{0.390} &  0.385 & \textbf{0.375}  \\
- with $f_1$, $f_2$, $f_3$, $f_4$ & \textbf{0.938} & \textbf{0.936} & \textbf{0.936} & \textbf{0.932} & 0.391 & 0.389 & 0.385 & 0.374\\
-\hline
-\end{tabular}
-\end{table}
-
-\paragraph{On the interest of using matrix $q$ rather than $p$ to take into account directivity.}
-
-Table~\ref{tab:dir} compares AUROC and AUPRC with or without correcting the $p_{i,j}$ values according to Equation \ref{eqn:qij}.
-Both AUROC and AUPRC are (very slightly) improved by using information about directivity.
-
-\begin{table}[ht]\label{tab:dir}
-\caption{Performance on \textit{normal-1,2,3,4} of ``Full Method'' with and
-  without using information about directivity.}
-\label{tab:directivity}
-
-\centering
-\small
-\begin{tabular}{| l | c c c c | c c c c |}
-\hline
-& \multicolumn{4}{c|}{AUROC} & \multicolumn{4}{c|}{AUPRC} \\
-\textit{Full method} $\backslash$ \textit{normal-} & \textit{1} & \textit{2} & \textit{3} & \textit{4} & \textit{1} & \textit{2} & \textit{3} & \textit{4} \\
-\hline
-\hline
- Undirected & 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388  \\
-  Directed & \textbf{0.944} & \textbf{0.943} & 0.942 & \textbf{0.940} & \textbf{0.404} & \textbf{0.405} & \textbf{0.399} & \textbf{0.389}\\
-\hline
-\end{tabular}
-\end{table}
-
-\section{Supplementary results} \label{app:supp}
-
-In this appendix we report the performance of the different methods compared
-in the paper on 6 additional datasets provided by the Challenge
-organisers. These datasets, corresponding each to networks of 1,000 neurons, are similar to
-the \textit{normal} datasets except for one feature:
-\begin{description}
-\item[lowcon:] Similar network but on average with a lower number of connections per neuron.
-\item[highcon:] Similar network but on average with a higher number of connections per neuron.
-\item[lowcc:] Similar network but on average with a lower clustering coefficient.
-\item[highcc:] Similar network but on average with a higher clustering coefficient.
-\item[normal-3-highrate:] Same topology as \textit{normal-3} but with a higher firing frequency, i.e., with highly active neurons.
-\item[normal-4-lownoise:] Same topology as \textit{normal-4} but with a better signal-to-noise ratio.
-\end{description}
-
-The results of several methods applied to these 6 datasets are provided in
-Table~\ref{tab:results_appendix}. They confirm what we observed on the
-\textit{normal} datasets. Average partial correlation and its tuned variant,
-i.e.,``Full method'', clearly outperform other network inference methods on all
-datasets. PC is close to GENIE3 and GTE, but still slightly worse. GENIE3
-performs better than GTE most of the time.
-Note that the "Full method" reported in this table does not use Equation \ref{eqn:qij} to slightly correct the values of $p_{i,j}$  to take into account directivity.
-
-\begin{table}[h]
-\caption{Performance (top: AUROC, bottom: AUPRC) on specific datasets with different methods.}
-\label{tab:results_appendix}
-\centering
-\small
-\begin{tabular}{| l | c c c c c c |}
-\hline
-& \multicolumn{6}{c|}{AUROC}\\
-\textit{Method} $\backslash$ \textit{normal-} & \textit{lowcon} & \textit{highcon} & \textit{lowcc} & \textit{highcc} & \textit{3-highrate} & \textit{4-lownoise} \\
-\hline
-\hline
-Averaging     & 0.947 & 0.943 & 0.920 & 0.942 & 0.959 & 0.934 \\
-Full method   & \textbf{0.955} & \textbf{0.944} &  \textbf{0.925} & \textbf{0.946} & \textbf{0.961} & \textbf{0.941} \\
-PC & 0.782 & 0.920 &  0.846 & 0.897  & 0.898  & 0.873 \\
-GTE & 0.846 & 0.905 & 0.848 & 0.899 & 0.905 & 0.879\\
-GENIE3 & 0.781 &  0.924 & 0.879 & 0.902 & 0.886 &  0.890 \\ \hline \hline
-& \multicolumn{6}{c|}{AUPRC}\\ \hline
-Averaging     & 0.320 & 0.429 & 0.262 & 0.478 & 0.443 & 0.412 \\
-Full method   & \textbf{0.334} & \textbf{0.413} &  \textbf{0.260} & \textbf{0.486} & \textbf{0.452} & \textbf{0.432}\\
-PC & 0.074 & 0.218 & 0.082 & 0.165  & 0.193 & 0.135 \\
-GTE & 0.094 & 0.211 & 0.081 & 0.165 & 0.210 & 0.144\\
-GENIE3 & 0.128 & 0.273 & 0.116 & 0.309 & 0.256 & 0.224\\ \hline
-\end{tabular}
-\end{table}
-
-\section{On the selection of the number of principal components}
-\label{app:pca}
-
-The (true) network, seen as a matrix, can be decomposed through a singular value decomposition (SVD) or principal component
-analysis (PCA), so as to respectively determine a set of independent linear combinations of the
-variable \citep{alter2000singular}, or a reduced set of linear
-combinations combine, which then maximize the explained variance of the data
-\citep{jolliffe2005principal}.
-Since SVD and PCA are related, they can be defined by the same goal: both aim at finding a reduced set of neurons, known as components, whose activity can explain the rest of the network.
-
-The distribution of compoment eigen values obtained from PCA and SVD decompositions can be studied by sorting them in descending order of magnitude, as illustrated in Figure~\ref{fig:pca}.
-It can be seen that some component eigen values are zero, implying that the behaviour of the network could be explained by a subset of neurons because of the
-redundancy and relations between the neurons. For all datasets, the eigen value distribution is exactly the same.
-
-In the context of the challenge, we observe that only $800$ components seem to be necessary and we exploit this when computing partial correlation statistics.
-Therefore, the value of the parameter $M$ is immediate and should be clearly set to $800$ ($=0.8p$).
-
-Note that if the true network is not available, similar decomposition analysis could be carried on the inferred network, or on the data directly.
-
-\begin{figure}[t]
-\centering
-\subfigure[PCA]{\includegraphics[width=0.45\textwidth]{explained_variance_all} \label{fig:PCA}}
-\subfigure[SVD]{\includegraphics[width=0.45\textwidth]{singular_values_all} \label{fig:SVD}}
-\caption{Explained variance ratio by number of principal components (left) and singular value ratio by number of principal components (right) for all networks.}
-\label{fig:pca}
-\end{figure}
-
-\section{Summary Table}
-
-\begin{table}[h]
- \caption{Connectomics Challenge summary.}
- \label{tab:summary}
- \centering
- \small
- \begin{tabular}{| l|c|} \hline
- Team Name & The AAAGV Team \\ \hline
- Private leaderboard position & \nth{1} \\ \hline
- Private leaderboard performance & 0.94161 \\ \hline
- Private leaderboard performance of the winner & idem \\ \hline
- \end{tabular}
- \end{table}
+Type here.
 

### 2014-10-14 crowdsource/article.tex
Template

@@
 
-Type here.
+\section{A large variety of performing methods}
+
+\emph{
+In the Results section "A large variety of performing methods", we intend to
+assemble together various layman presentations of different approaches. If you
+could provide a short popular-science style description of your approach (and
+specifically of what you consider their main characterizing ingredients,
+INVERSE COVARIANCE for you) this would be very helpful for me.  Here is not
+really an issue of being precise, but of commenting substantial elements to a
+public of... ignorant biologists! What's the logic of making a certain step?
+How does the method work in a nutshell, without using equations but expressed
+in plain words, etc. ? Then, based on all the texts I will collect from you, I
+would build the section and let you edit it to correct mistakes or add
+precisions.
+}
+
+\cite{sutera2014simple}
+
+\bibliography{references}
 

### 2014-10-14 crowdsource/article.tex
Add second task
Decsribe method

@@
 
-\cite{sutera2014simple}
+A simple yet effective solution to the problem of connectome inference in
+calcium imaging data consists of two steps. \cite{sutera2014simple} First,
+processing the raw signals and to detect neural peak activities while filtering
+noise. Second, inferring the degree of association between neurons from partial
+correlation statistics, the inverse of the correlation matrix. This statitical
+measure has the property to filter indirect associations between neuron and
+gives a high degree of association between directly connected neurons. This
+approach is the winning methods of the Connectomics challenge.
+
+\section{Method}
+\emph{A second mini-text I ask you will converge to the Methods section. Here I need
+a more detailed presentation of your method. However, it has to be precise, but
+still understandable for a biologist. A bit like a recipe in a cookbook for
+beginners.}
 

### 2014-10-14 crowdsource/article.tex
A first draft for the soft introduction of the inverse covariance methodology

--- 2014-10-14 crowdsource/article.tex
@@
 would build the section and let you edit it to correct mistakes or add
-precisions.
+precisions.\\
 }
 
-\cite{sutera2014simple}
+The inference problem reduced to its simpliest shape is the identification of
+neuron pairs that are directly connected in the network. Intuitively, such
+pairs should be related somehow and in particular their activities have to be
+similar since their are dependent on the connectivity network. Therefore a way
+to identify them is to measure, or at least estimate, how closely related two
+neurons are regarding their activities. The most common measure for that
+purpose is the (Pearson) correlation.  However, correlation also measures the
+degree of association between neurons that are connected through others and so 
+connected indirectly. It means all related neurons are found but direct pairs
+are indinstinguishable from indirect ones.
 
+A variant of this classic approach is the partial correlation which measures
+the degree of association between neurons but takes into account the state
+(here, the activity state) of other neurons. If all other neurons are
+considered, the partial correlation is known as the inverse covariance. By
+conditioning on them (and under a few assumptions), inverse correlation only
+detects direct association between neuron pairs and filter out indirect
+relationships that may also be observed in data \citep{sutera2014simple}. The
+interest of partial correlation as an association measure has already been
+shown for the inference of gene regulatory networks \citep{de2004discovery,Schafer:2005}.
+
+Nevertheless, in particular for the connectome inference from fluorescent
+data, a pre-processing is required before applying either of both measures.
+Such processes (i) abstract the activity signal from fluorescent data; and
+(ii) highlight characteristics of activity signals (e.g., spikes) to make
+easier the assessement of the degree of association and therefore improve the
+quality of the estimates of both measures.
+
+Accordingly, ahead of (partial) correlation, filters are applied on fluorescent data in order to (i) smoothe the signal\footnote{I assume that noise will have been explained at this stage of the paper.
+Otherwise, we should mention something like this :\textit{Noise is due to fluctuations independent of calcium, calcium fluctuations independent of spiking activity, calcium fluctuations in nearby tissues that have been mistakenly captured, or simply by the imaging process.}}; (ii) emphasise short spikes that are indirect indicator of neuron communication; and (iii) artificially magnify spikes that occur during normal activity because we have conjectured that when a large part of the network is firing (i.e., called a network burst \citep{stetter2012model}), the estimation of degree of assocation is meaningless \citep{sutera2014simple}.
+
+\section{Method}
+\emph{A second mini-text I ask you will converge to the Methods section. Here I need
+a more detailed presentation of your method. However, it has to be precise, but
+still understandable for a biologist. A bit like a recipe in a cookbook for
+beginners.}
+
+\newpage
 \bibliography{references}

### 2014-10-14 crowdsource/article.tex
Remove conflicts symbols but keep both alternatives

@@
 
+\paragraph{A first version}
 The inference problem reduced to its simpliest shape is the identification of
@@
 
-Accordingly, ahead of (partial) correlation, filters are applied on fluorescent data in order to (i) smoothe the signal\footnote{I assume that noise will have been explained at this stage of the paper.
-Otherwise, we should mention something like this :\textit{Noise is due to fluctuations independent of calcium, calcium fluctuations independent of spiking activity, calcium fluctuations in nearby tissues that have been mistakenly captured, or simply by the imaging process.}}; (ii) emphasise short spikes that are indirect indicator of neuron communication; and (iii) artificially magnify spikes that occur during normal activity because we have conjectured that when a large part of the network is firing (i.e., called a network burst \citep{stetter2012model}), the estimation of degree of assocation is meaningless \citep{sutera2014simple}.
+Accordingly, ahead of (partial) correlation, filters are applied on
+fluorescent data in order to (i) smoothe the signal\footnote{I assume that
+noise will have been explained at this stage of the paper. Otherwise, we
+should mention something like this :\textit{Noise is due to fluctuations
+independent of calcium, calcium fluctuations independent of spiking activity,
+calcium fluctuations in nearby tissues that have been mistakenly captured, or
+simply by the imaging process.}}; (ii) emphasise short spikes that are
+indirect indicator of neuron communication; and (iii) artificially magnify
+spikes that occur during normal activity because we have conjectured that when
+a large part of the network is firing (i.e., called a network burst
+\citep{stetter2012model}), the estimation of degree of assocation is
+meaningless \citep{sutera2014simple}.
+
+\paragraph{Alternative}
+A simple yet effective solution to the problem of connectome inference in
+calcium imaging data consists of two steps. \cite{sutera2014simple} First,
+processing the raw signals and to detect neural peak activities while filtering
+noise. Second, inferring the degree of association between neurons from partial
+correlation statistics, the inverse of the correlation matrix. This statitical
+measure has the property to filter indirect associations between neuron and
+gives a high degree of association between directly connected neurons. This
+approach is the winning methods of the Connectomics challenge.
 
@@
 
+As
+
 \newpage

### 2014-10-14 crowdsource/article.tex
A first draft for the second task

@@
 \setlength{\textfloatsep}{15pt}
+
+\usepackage{algorithmic}
 
@@
 noise. Second, inferring the degree of association between neurons from partial
-correlation statistics, the inverse of the correlation matrix. This statitical
+correlation statistics, the inverse of the correlation matrix. This statistical
 measure has the property to filter indirect associations between neuron and
@@
 still understandable for a biologist. A bit like a recipe in a cookbook for
-beginners.}
+beginners.\\}
 
-As
+The method involving inverse covariance, fully described in \cite{sutera2014simple}, is presented in Table~\ref{alg:inverse-covariance-pseudocode}.
+Under the simplifying assumption that neurons are on-off units defined by short intense periods of activity (i.e., spikes) and long periods of inactivity, it is possible to extract that information from the fluorescent data by appling several filters, common in the field of signal processing \citep{kaiser1977data, oppenheim1983signals}.
+
+The first step of our pipeline is to smoothe the fluorescence signal by applying a low-pass filter for filtering out high frequency noise:
+\begin{align}
+f_1(x^t_i) &= x^{t-1}_i + x^t_i + x^{t+1}_i, \label{eq:symetric-median} \\
+f_2(x^t_i) &= 0.4 x^{t-3}_i + 0.6 x^{t-2}_i + 0.8 x^{t-1}_i + x_i^t.
+\label{eq:weighted-asymetric-median}
+\end{align}
+
+To have a signal that only has high magnitude around instances where the spikes occur, the second step of our pipeline transforms the time-series into its backward difference
+\begin{align}
+g(x^{t}_{i}) &= x^{t}_i - x^{t-1}_i. \label{eq:high-pass-filter}
+\end{align}
+
+To filter out small variations in the signal obtained after applying the function $g$, as well
+as to eliminate negative values, we use the following hard-threshold filter
+\begin{align}\label{eqn:hfilter}
+h(x^{t}_i) &= x^{t}_i \mathbb{1}(x^{t}_i \geq \tau) \text{ with } \tau > 0,
+\end{align}
+where $\tau$ is the threshold parameter and $\mathbb{1}$ is the indicator function.
+
+The objective of the last step of our filtering procedure is to decrease the importance of spikes that occur when there is high global activity in the network with respect to spikes that occur during normal activity.
+Indeed, we have conjectured that when a large part of the network is firing, the rate at which observations are made is not high enough to be able to detect interactions, and that it would therefore be preferable to lower their importance by changing their magnitude appropriately.
+Additionally, it is well-known that neurons may also spike because of a high global activity \citep{stetter2012model}.
+In such context, detecting pairwise neuron interactions from the firing activity is meaningless.
+As such, the signal output by h is finally applied to the following function
+\begin{align}
+ w(x^{t}_i) &= (x^{t}_i + 1 )^{1 + \frac{1}{\sum_{j} x^{t}_j}}, \label{eq:magnify-filter}
+\end{align}
+whose effect is to magnify the importance of spikes that occur in cases of low global activity (measured by $\sum_j x^t_j$).\\
+
+Under the assumption that fluorescence level neuron are jointly gaussian, \textit{partial correlation} thus measures conditional dependencies between variables ; therefore it should naturally only detect direct associations between neurons and filter out spurious indirect effects as mentioned before.
+
+Practically speaking, the computation of all $p_{i,j}$ coefficients requires the estimation of the covariance matrix $\Sigma$
+and then computing its inverse. Given that typically we have more
+samples than neurons, the covariance matrix can be inverted in a
+straightforward way. We nevertheless obtained some improvement by
+replacing the exact inverse with an approximation using only the $M$
+first principal components \citep{bishop2006pattern} (more details in \citep{sutera2014simple}).
+
+\begin{table}[ht]
+\begin{algorithmic}
+ \algsetup{linenodelimiter= }
+
+\STATE \textbf{Given} the sampled observation of $p$ neurons for $T$ time intervals.\\[2ex]
+
+\FOR{$(f,\tau) \in (\{f_1, f_2\}, \{\tau_1, \tau_2, \dots \})$}
+
+\STATE \vspace{1em} \textbf{Phase 1:} Apply the composed function $w \circ h \circ g \circ f$ to each fluorescent signal.
+\FOR{$x \in \{1,\dots,T\} $}
+\STATE $\bar{x}^t_i  \leftarrow w \circ h_{\tau} \circ g \circ f (x^t_i)$
+\ENDFOR\\[2ex]
+
+\STATE \textbf{Phase 2:} Compute \textit{Partial correlation} coefficient $p_{i,j}$ for each neuron pair $(i,j)$.
+\FOR{all pair $(i,j)$}
+\STATE Estimation of the covariance matrix $\Sigma$
+\STATE Computing $\Sigma^{-1}$, the inverse of $\Sigma$
+\STATE $p_{i,j} =
+-\frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii} \Sigma^{-1}_{jj}}}$
+
+\ENDFOR\\[2ex]
+\ENDFOR
+
+\end{algorithmic}
+\caption{Inverse covariance pseudo-code}
+\label{alg:inverse-covariance-pseudocode}
+\end{table}
+
+% \begin{algorithm}[h]
+%  \KwData{Given the sampled observation $\{ x^t_i \in \mathbb{R} | i \in V, t = 1, \dots, T \}$ of $p$ neurons for T time intervals}
+%  % \KwResult{how to write algorithm with \LaTeX2e }
+
+%  \textbf{Phase 1:} Apply the composed function $w \circ h \circ g \circ f$ to each fluorescent signal.\;\;
+% \ \ For
+
+% {\Indp
+%  \For{$x \in \{1,\dots,T\} $}{
+% 		$\bar{x}^t_i  \leftarrow w \circ h \circ g \circ f (x^t_i)$
+%  }
+%  }
+
+%  \While{not at end of this document}{
+%   read current\;
+%   \eIf{understand}{
+%    go to next section\;
+%    current section becomes this one\;
+%    }{
+%    go back to the beginning of current section\;
+%   }
+%  }
+%  \caption{Inverse covariance pseudo-code}
+%  \label{alg:inverse-covariance-pseudocode}
+% \end{algorithm}
 

### 2014-10-15 crowdsource/article.tex
Improve text

@@
 
+\usepackage{algorithm}
 \usepackage{algorithmic}
@@
 would build the section and let you edit it to correct mistakes or add
-precisions.\\
-}
+precisions.\\}
 
-\paragraph{A first version}
-The inference problem reduced to its simpliest shape is the identification of
+A partial correlation approach \cite{sutera2014simple}  is a simple yet effective
+solution to the problem of connectome inference in calcium imaging data.
+This winning approach of the Connectomics challenge consists of two steps.
+First, time-series are processed using standard
+signal processing filters in order to : (i) remove noise mainly due to
+fluctuations independent of calcium, calcium fluctuations independent of
+spiking activity, calcium fluctuations in nearby tissues that have been
+mistakenly captured, or simply by the imaging process ; (ii) to account for
+fluorescence low decay ; and (iii) to reduce the importance of high global
+activity in the network. Secondly, inferring the degree of association between
+neurons is then made with partial correlation statistics, the inverse of the
+correlation matrix. This statistical measure has the property to filter
+indirect associations between neurons and gives a high degree of association
+between directly connected neurons.
+
+\section{Method}
+\emph{A second mini-text I ask you will converge to the Methods section. Here I need
+a more detailed presentation of your method. However, it has to be precise, but
+still understandable for a biologist. A bit like a recipe in a cookbook for
+beginners.\\}
+
+The inference problem reduced to its simplest shape is the identification of
 neuron pairs that are directly connected in the network. Intuitively, such
@@
 connected indirectly. It means all related neurons are found but direct pairs
-are indinstinguishable from indirect ones.
+are indistinguishable from indirect ones.
 
-A variant of this classic approach is the partial correlation which measures
-the degree of association between neurons but takes into account the state
-(here, the activity state) of other neurons. If all other neurons are
-considered, the partial correlation is known as the inverse covariance. By
-conditioning on them (and under a few assumptions), inverse correlation only
-detects direct association between neuron pairs and filter out indirect
-relationships that may also be observed in data \citep{sutera2014simple}. The
-interest of partial correlation as an association measure has already been
-shown for the inference of gene regulatory networks \citep{de2004discovery,Schafer:2005}.
+A variant of this classic approach is the partial correlation
+\citep{sutera2014simple}, also known as the inverse of the correlation, which
+measures the degree of association between two neurons taking into account the
+state of all other neurons. Under technical assumptions, the inverse
+correlation can be interpreted as a measure of association between directly
+connected pairs of neurons and filter out indirectly connected pairs of
+neurons. In genetics network, partial correlation have already shown to be
+effective way to infer gene regulatory networks
+\citep{de2004discovery,Schafer:2005}. This approach is fully described in
+\cite{sutera2014simple} and is presented in Algorithm~\ref{alg:inverse-
+covariance- pseudocode}. We first describe the pre-processing of the signal,
+then explained how to compute the partial  correlation statistics.
 
-Nevertheless, in particular for the connectome inference from fluorescent
-data, a pre-processing is required before applying either of both measures.
-Such processes (i) abstract the activity signal from fluorescent data; and
-(ii) highlight characteristics of activity signals (e.g., spikes) to make
-easier the assessement of the degree of association and therefore improve the
-quality of the estimates of both measures.
-
-Accordingly, ahead of (partial) correlation, filters are applied on
-fluorescent data in order to (i) smoothe the signal\footnote{I assume that
-noise will have been explained at this stage of the paper. Otherwise, we
-should mention something like this :\textit{Noise is due to fluctuations
-independent of calcium, calcium fluctuations independent of spiking activity,
-calcium fluctuations in nearby tissues that have been mistakenly captured, or
-simply by the imaging process.}}; (ii) emphasise short spikes that are
-indirect indicator of neuron communication; and (iii) artificially magnify
-spikes that occur during normal activity because we have conjectured that when
-a large part of the network is firing (i.e., called a network burst
-\citep{stetter2012model}), the estimation of degree of assocation is
-meaningless \citep{sutera2014simple}.
-
-\paragraph{Alternative}
-A simple yet effective solution to the problem of connectome inference in
-calcium imaging data consists of two steps. \cite{sutera2014simple} First,
-processing the raw signals and to detect neural peak activities while filtering
-noise. Second, inferring the degree of association between neurons from partial
-correlation statistics, the inverse of the correlation matrix. This statistical
-measure has the property to filter indirect associations between neuron and
-gives a high degree of association between directly connected neurons. This
-approach is the winning methods of the Connectomics challenge.
-
-\section{Method}
-\emph{A second mini-text I ask you will converge to the Methods section. Here I need
-a more detailed presentation of your method. However, it has to be precise, but
-still understandable for a biologist. A bit like a recipe in a cookbook for
-beginners.\\}
-
-The method involving inverse covariance, fully described in \cite{sutera2014simple}, is presented in Table~\ref{alg:inverse-covariance-pseudocode}.
-Under the simplifying assumption that neurons are on-off units defined by short intense periods of activity (i.e., spikes) and long periods of inactivity, it is possible to extract that information from the fluorescent data by appling several filters, common in the field of signal processing \citep{kaiser1977data, oppenheim1983signals}.
-
-The first step of our pipeline is to smoothe the fluorescence signal by applying a low-pass filter for filtering out high frequency noise:
+Under the simplifying assumption that neurons are on-off units, characterised
+by short periods of intense activity, or peaks, and longer periods of
+inactivity, the first part of our algorithm consists of cleaning the raw
+fluorescence data. More specifically, time-series are processed using standard
+signal processing filters in order to : (i) remove noise mainly due to
+fluctuations independent of calcium, calcium fluctuations independent of
+spiking activity, calcium fluctuations in nearby tissues that have been
+mistakenly captured, or simply by the imaging process ; (ii) to account for
+fluorescence low decay ; and (iii) to reduce the importance of high global
+activity in the network. This data pre-processing is standard  in the field of
+signal processing \citep{kaiser1977data, oppenheim1983signals}.
+The first step of our pipeline is to smooth the fluorescence signal by applying a low-pass filter for filtering out high frequency noise:
 \begin{align}
@@
 
-To filter out small variations in the signal obtained after applying the function $g$, as well
-as to eliminate negative values, we use the following hard-threshold filter
+To filter out small variations in the signal obtained after applying the
+function $g$, as well as to eliminate negative values, we use the following
+hard-threshold filter
 \begin{align}\label{eqn:hfilter}
@@
 \end{align}
-where $\tau$ is the threshold parameter and $\mathbb{1}$ is the indicator function.
+where $\tau$ is the threshold parameter and $\mathbb{1}$ is the indicator
+function.
 
-The objective of the last step of our filtering procedure is to decrease the importance of spikes that occur when there is high global activity in the network with respect to spikes that occur during normal activity.
-Indeed, we have conjectured that when a large part of the network is firing, the rate at which observations are made is not high enough to be able to detect interactions, and that it would therefore be preferable to lower their importance by changing their magnitude appropriately.
-Additionally, it is well-known that neurons may also spike because of a high global activity \citep{stetter2012model}.
-In such context, detecting pairwise neuron interactions from the firing activity is meaningless.
-As such, the signal output by h is finally applied to the following function
+The objective of the last step of our filtering procedure is to decrease the
+importance of spikes that occur when there is high global activity in the
+network with respect to spikes that occur during normal activity. Indeed, we
+have conjectured that when a large part of the network is firing, the rate at
+which observations are made is not high enough to be able to detect
+interactions, and that it would therefore be preferable to lower their
+importance by changing their magnitude appropriately. Additionally, it is well-
+known that neurons may also spike because of a high global activity
+\citep{stetter2012model}. In such context, detecting pairwise neuron
+interactions from the firing activity is meaningless. As such, the signal
+output by h is finally applied to the following function
 \begin{align}
@@
 \end{align}
-whose effect is to magnify the importance of spikes that occur in cases of low global activity (measured by $\sum_j x^t_j$).\\
+whose effect is to magnify the importance of spikes that occur in cases of low
+global activity (measured by $\sum_j x^t_j$).
 
-Under the assumption that fluorescence level neuron are jointly gaussian, \textit{partial correlation} thus measures conditional dependencies between variables ; therefore it should naturally only detect direct associations between neurons and filter out spurious indirect effects as mentioned before.
+Under the assumption that fluorescence level neuron are jointly Gaussian,
+\textit{partial correlation} thus measures conditional dependencies between
+variables ; therefore it should naturally only detect direct associations
+between neurons and filter out spurious indirect effects as mentioned before.
 
-Practically speaking, the computation of all $p_{i,j}$ coefficients requires the estimation of the covariance matrix $\Sigma$
-and then computing its inverse. Given that typically we have more
-samples than neurons, the covariance matrix can be inverted in a
-straightforward way. We nevertheless obtained some improvement by
-replacing the exact inverse with an approximation using only the $M$
-first principal components \citep{bishop2006pattern} (more details in \citep{sutera2014simple}).
+Practically speaking, the computation of all $p_{i,j}$ coefficients requires
+the estimation of the covariance matrix $\Sigma$ and then computing its
+inverse. Given that typically we have more samples than neurons, the covariance
+matrix can be inverted in a straightforward way. We nevertheless obtained some
+improvement by replacing the exact inverse with an approximation using only the
+$M$ first principal components \citep{bishop2006pattern} (more details in
+\citep{sutera2014simple}).
 
-\begin{table}[ht]
+\begin{algorithm}[ht]
 \begin{algorithmic}
@@
 \label{alg:inverse-covariance-pseudocode}
-\end{table}
+\end{algorithm}
 

### 2014-10-17 crowdsource/article.tex
improve mini-text 1

@@
 
-A partial correlation approach \cite{sutera2014simple}  is a simple yet effective
-solution to the problem of connectome inference in calcium imaging data.
-This winning approach of the Connectomics challenge consists of two steps.
-First, time-series are processed using standard
-signal processing filters in order to : (i) remove noise mainly due to
-fluctuations independent of calcium, calcium fluctuations independent of
-spiking activity, calcium fluctuations in nearby tissues that have been
-mistakenly captured, or simply by the imaging process ; (ii) to account for
-fluorescence low decay ; and (iii) to reduce the importance of high global
-activity in the network. Secondly, inferring the degree of association between
-neurons is then made with partial correlation statistics, the inverse of the
-correlation matrix. This statistical measure has the property to filter
-indirect associations between neurons and gives a high degree of association
-between directly connected neurons.
+A partial correlation approach \cite{sutera2014simple}  is a simple yet
+effective solution to the problem of connectome inference in calcium imaging
+data. This partial correlation statistics, the inverse of the correlation
+measure, has  the property to filter indirect associations between neurons and
+gives a high degree of association between directly connected neurons. The
+winning solution of the Connectomics challenge combines two main steps:
+(i) data are pre-processed using signal processing filters; (ii)
+the network is infered through partial correlation. The pre-processing step
+highly improves the infered network by removing noise and taking into account
+specifities of the fluorecense signals.
 

### 2014-10-18 crowdsource/article.tex
small modifs

@@
 A partial correlation approach \cite{sutera2014simple}  is a simple yet
-effective solution to the problem of connectome inference in calcium imaging
-data. This partial correlation statistics, the inverse of the correlation
-measure, has  the property to filter indirect associations between neurons and
-gives a high degree of association between directly connected neurons. The
+effective solution to the problem of connectome inference from calcium imaging
+data. This partial correlation statistics, equivalent to the inverse of the correlation
+measure, has  the property to filter out indirect associations between neurons and
+only gives a high degree of association between directly connected neurons. The
 winning solution of the Connectomics challenge combines two main steps:
-(i) data are pre-processed using signal processing filters; (ii)
-the network is infered through partial correlation. The pre-processing step
-highly improves the infered network by removing noise and taking into account
+(i) A pre-processing of the data using signal processing filters; and (ii)
+The inference of the network through partial correlation. The pre-processing procedure
+highly improves the infered network quality by filtering out noise and taking into account
 specifities of the fluorecense signals.

### 2014-10-18 crowdsource/article.tex
some modifs in task2

@@
 degree of association between neurons that are connected through others and so
-connected indirectly. It means all related neurons are found but direct pairs
+connected indirectly. It means all related neurons are found but direct pairs (i.e., without any intermediates)
 are indistinguishable from indirect ones.
@@
 correlation can be interpreted as a measure of association between directly
-connected pairs of neurons and filter out indirectly connected pairs of
+connected pairs of neurons while filtering out indirectly connected pairs of
 neurons. In genetics network, partial correlation have already shown to be
@@
 \citep{de2004discovery,Schafer:2005}. This approach is fully described in
-\cite{sutera2014simple} and is presented in Algorithm~\ref{alg:inverse-
-covariance- pseudocode}. We first describe the pre-processing of the signal,
+\cite{sutera2014simple}.
+
+In the following paragraphs, we first describe the pre-processing of the signal,
 then explained how to compute the partial correlation statistics.
@@
 by short periods of intense activity, or peaks, and longer periods of
-inactivity, the first part of our algorithm consists of cleaning the raw
-fluorescence data. More specifically, time-series are processed using standard
-signal processing filters in order to : (i) remove noise mainly due to
-fluctuations independent of calcium, calcium fluctuations independent of
+inactivity, the first part of our algorithm consists in cleaning the raw
+fluorescence data. More specifically, time-series are pre-processed using
+standard signal processing filters in order to : (i) remove noise mainly due
+to fluctuations independent of calcium, calcium fluctuations independent of
 spiking activity, calcium fluctuations in nearby tissues that have been
@@
 fluorescence low decay ; and (iii) to reduce the importance of high global
-activity in the network. This data pre-processing is standard  in the field of
-signal processing \citep{kaiser1977data, oppenheim1983signals}.
-The first step of our pipeline is to smooth the fluorescence signal by applying a low-pass filter for filtering out high frequency noise:
-\begin{align}
-f_1(x^t_i) &= x^{t-1}_i + x^t_i + x^{t+1}_i, \label{eq:symetric-median} \\
-f_2(x^t_i) &= 0.4 x^{t-3}_i + 0.6 x^{t-2}_i + 0.8 x^{t-1}_i + x_i^t.
-\label{eq:weighted-asymetric-median}
+activity in the network. The first step of our pipeline is to smooth the
+fluorescence signal by applying a low-pass filter for filtering out high
+frequency noise:  
+\begin{align} f_1(x^t_i) &= x^{t-1}_i + x^t_i + x^{t+1}_i,
+\label{eq:symetric-median} \\ f_2(x^t_i) &= 0.4 x^{t-3}_i + 0.6 x^{t-2}_i +
+0.8 x^{t-1}_i + x_i^t. \label{eq:weighted- asymetric-median} 
 \end{align}
 
-To have a signal that only has high magnitude around instances where the spikes occur, the second step of our pipeline transforms the time-series into its backward difference
-\begin{align}
-g(x^{t}_{i}) &= x^{t}_i - x^{t-1}_i. \label{eq:high-pass-filter}
+To have a signal that only has high magnitude around instances where the
+spikes occur, the second step of our pipeline transforms the time-series into
+its backward difference 
+\begin{align} g(x^{t}_{i}) &= x^{t}_i - x^{t-1}_i.
+\label{eq:high-pass-filter}
 \end{align}
@@
 interactions, and that it would therefore be preferable to lower their
-importance by changing their magnitude appropriately. Additionally, it is well-
-known that neurons may also spike because of a high global activity
+importance by changing their magnitude appropriately. Additionally, it is well-known
+that neurons may also spike because of a high global activity
 \citep{stetter2012model}. In such context, detecting pairwise neuron
@@
 Under the assumption that fluorescence level neuron are jointly Gaussian,
-\textit{partial correlation} thus measures conditional dependencies between
+partial correlation thus measures conditional dependencies between
 variables ; therefore it should naturally only detect direct associations
@@
 
-\STATE \textbf{Given} the sampled observation of $p$ neurons for $T$ time intervals.\\[2ex]
+\STATE Here the pseudo-code.
+% \STATE \textbf{Given} the sampled observation of $p$ neurons for $T$ time intervals.\\[2ex]
 
-\FOR{$(f,\tau) \in (\{f_1, f_2\}, \{\tau_1, \tau_2, \dots \})$}
+% \FOR{$(f,\tau) \in (\{f_1, f_2\}, \{\tau_1, \tau_2, \dots \})$}
 
-\STATE \vspace{1em} \textbf{Phase 1:} Apply the composed function $w \circ h \circ g \circ f$ to each fluorescent signal.
-\FOR{$x \in \{1,\dots,T\} $}
-\STATE $\bar{x}^t_i  \leftarrow w \circ h_{\tau} \circ g \circ f (x^t_i)$
-\ENDFOR\\[2ex]
+% \STATE \vspace{1em} \textbf{Phase 1:} Apply the composed function $w \circ h \circ g \circ f$ to each fluorescent signal.
+% \FOR{$x \in \{1,\dots,T\} $}
+% \STATE $\bar{x}^t_i  \leftarrow w \circ h_{\tau} \circ g \circ f (x^t_i)$
+% \ENDFOR\\[2ex]
 
-\STATE \textbf{Phase 2:} Compute \textit{Partial correlation} coefficient $p_{i,j}$ for each neuron pair $(i,j)$.
-\FOR{all pair $(i,j)$}
-\STATE Estimation of the covariance matrix $\Sigma$
-\STATE Computing $\Sigma^{-1}$, the inverse of $\Sigma$
-\STATE $p_{i,j} =
--\frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii} \Sigma^{-1}_{jj}}}$
+% \STATE \textbf{Phase 2:} Compute \textit{Partial correlation} coefficient $p_{i,j}$ for each neuron pair $(i,j)$.
+% \FOR{all pair $(i,j)$}
+% \STATE Estimation of the covariance matrix $\Sigma$
+% \STATE Computing $\Sigma^{-1}$, the inverse of $\Sigma$
+% \STATE $p_{i,j} =
+% -\frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii} \Sigma^{-1}_{jj}}}$
 
-\ENDFOR\\[2ex]
-\ENDFOR
+% \ENDFOR\\[2ex]
+% \ENDFOR
 
 \end{algorithmic}
-\caption{Inverse covariance pseudo-code}
+\caption{Inverse covariance pseudo-code \textcolor{red}{TO DO}}
 \label{alg:inverse-covariance-pseudocode}

### 2014-10-20 crowdsource/article.tex
Description of the full method (PG's version)

@@
 
-A partial correlation approach \cite{sutera2014simple}  is a simple yet
-effective solution to the problem of connectome inference from calcium imaging
-data. This partial correlation statistics, equivalent to the inverse of the correlation
-measure, has  the property to filter out indirect associations between neurons and
-only gives a high degree of association between directly connected neurons. The
-winning solution of the Connectomics challenge combines two main steps:
-(i) A pre-processing of the data using signal processing filters; and (ii)
-The inference of the network through partial correlation. The pre-processing procedure
-highly improves the infered network quality by filtering out noise and taking into account
-specifities of the fluorecense signals.
+The winning solution of the Connectomics challenge \citep{sutera2014simple}
+combines two main steps: (i) a pre-processing of the raw signals to detect
+neural peak activities; and (ii) the inference of the network through partial
+correlation statistics. The pre-processing step is crucial to obtain optimal
+performance. It combines several standard filtering functions with three main
+goals: to remove the noise introduced at different levels, to account for
+fluorescence low decay, and to reduce the importance of high global activity in
+the network. From the filtered signals, the strength of the connection between two
+neurons is then assessed using partial correlations. The partial correlation
+between two random variables measures their conditional dependencies, i.e.,
+their associations when the effect of all the other variables has been
+removed. With respect to plain correlation, the main advantage of partial
+correlation for network inference is to only give a high degree of association
+to directly connected neurons and thus to filter out spurious indirect
+associations. Practically, partial correlations are also easily computed for
+all pairs of neurons at once from a simple inversion of the data covariance
+matrix.
 
@@
 
-The inference problem reduced to its simplest shape is the identification of
-neuron pairs that are directly connected in the network. Intuitively, such
-pairs should be related somehow and in particular their activities have to be
-similar since their are dependent on the connectivity network. Therefore a way
-to identify them is to measure, or at least estimate, how closely related two
-neurons are regarding their activities. The most common measure for that
-purpose is the (Pearson) correlation.  However, correlation also measures the
-degree of association between neurons that are connected through others and so
-connected indirectly. It means all related neurons are found but direct pairs (i.e., without any intermediates)
-are indistinguishable from indirect ones.
+Our approach consists of two main steps: (i) a pre-processing of the raw
+signals with several signal processing filters; and (ii) the inference of the
+network through partial correlation statistics. We describe the details of
+these two steps below as well as two techniques that slightly improve
+performance, averaging and edge orientation. Further motivations for all steps
+are given in \citep{sutera2014simple}. A simplified method is also proposed in
+the same paper with only slightly lower performance.
 
-A variant of this classic approach is the partial correlation
-\citep{sutera2014simple}, also known as the inverse of the correlation, which
-measures the degree of association between two neurons taking into account the
-state of all other neurons. Under technical assumptions, the inverse
-correlation can be interpreted as a measure of association between directly
-connected pairs of neurons while filtering out indirectly connected pairs of
-neurons. In genetics network, partial correlation have already shown to be
-effective way to infer gene regulatory networks
-\citep{de2004discovery,Schafer:2005}. This approach is fully described in
-\cite{sutera2014simple}.
-
-In the following paragraphs, we first describe the pre-processing of the signal,
-then explained how to compute the partial correlation statistics.
+\paragraph{Pre-processing.}
 
@@
 inactivity, the first part of our algorithm consists in cleaning the raw
-fluorescence data. More specifically, time-series are pre-processed using
-standard signal processing filters in order to : (i) remove noise mainly due
-to fluctuations independent of calcium, calcium fluctuations independent of
-spiking activity, calcium fluctuations in nearby tissues that have been
-mistakenly captured, or simply by the imaging process ; (ii) to account for
-fluorescence low decay ; and (iii) to reduce the importance of high global
-activity in the network. The first step of our pipeline is to smooth the
-fluorescence signal by applying a low-pass filter for filtering out high
-frequency noise:  
-\begin{align} f_1(x^t_i) &= x^{t-1}_i + x^t_i + x^{t+1}_i,
-\label{eq:symetric-median} \\ f_2(x^t_i) &= 0.4 x^{t-3}_i + 0.6 x^{t-2}_i +
-0.8 x^{t-1}_i + x_i^t. \label{eq:weighted- asymetric-median} 
+fluorescence data. This pre-processing applies successively four
+filtering functions to the original signal:
+\begin{itemize}
+  \item The first function smooths the fluorescence signal, using one of the following
+low-pass filters for filtering out high frequency noise:
+\begin{align} f_1(x^t_i) &= x^{t-1}_i + x^t_i + x^{t+1}_i, \label{eq:symetric-median} \\
+  f_2(x^t_i) &= 0.4 x^{t-3}_i + 0.6 x^{t-2}_i + 0.8 x^{t-1}_i + x_i^t.\label{eq:weighted-asymetric-median}\\
+  f_3(x^t_i) &= x^{t-1}_i + x^{t}_i + x^{t+1}_i + x^{t+2}_i, \label{eq:asymetric-median-forward} \\
+f_4(x^t_i) &=  x_i^t + x^{t+1}_i  + x^{t+2}_i + x^{t+3}_i. \label{eq:asymetric-median}
 \end{align}
-
-To have a signal that only has high magnitude around instances where the
-spikes occur, the second step of our pipeline transforms the time-series into
+\item To have a signal that only has high magnitude around instances where the
+spikes occur, the second filter function transforms the time-series into
 its backward difference 
@@
 \end{align}
-
-To filter out small variations in the signal obtained after applying the
-function $g$, as well as to eliminate negative values, we use the following
+\item To filter out small variations in the signal obtained after applying the
+function $g$, as well as to eliminate negative values, we then use the following
 hard-threshold filter
 \begin{align}\label{eqn:hfilter}
-h(x^{t}_i) &= x^{t}_i \mathbb{1}(x^{t}_i \geq \tau) \text{ with } \tau > 0,
+h(x^{t}_i) &= (x^{t}_i)^c \mathbb{1}(x^{t}_i \geq \tau) \text{ with } \tau > 0,
 \end{align}
-where $\tau$ is the threshold parameter and $\mathbb{1}$ is the indicator
+where $\tau$ is the threshold parameter, $c$ is equal to 0.9, and $\mathbb{1}$ is the indicator
 function.
+\item The last filtering functions is defined as:
+\begin{align}
+ w^*(x^{t}_i) &= {(x^{t}_i + 1 )^{\left (1 + \frac{1}{\sum_{j} x^{t}_j}\right )}}^{k(\sum_{j} x^{t}_j)}
+\end{align}
+where the function $k$ is a piecewise linear function optimised
+separately for each filter $f_1$, $f_2$, $f_3$ and $f_4$ (see the
+implementation for full details). The effect of this filtering is to
+magnify the importance of spikes that occur in cases of low global
+activity (measured by $\sum_j x^t_j$).
+\end{itemize}
+The pre-processed times-series are then obtained by the application of
+the following function: $w^*\circ h \circ g \circ f_i$ (with
+$i=1$, 2, 3, or 4).
 
-The objective of the last step of our filtering procedure is to decrease the
-importance of spikes that occur when there is high global activity in the
-network with respect to spikes that occur during normal activity. Indeed, we
-have conjectured that when a large part of the network is firing, the rate at
-which observations are made is not high enough to be able to detect
-interactions, and that it would therefore be preferable to lower their
-importance by changing their magnitude appropriately. Additionally, it is well-known
-that neurons may also spike because of a high global activity
-\citep{stetter2012model}. In such context, detecting pairwise neuron
-interactions from the firing activity is meaningless. As such, the signal
-output by h is finally applied to the following function
+\paragraph{Partial correlation.}
+In the second main step of our approach, partial correlation is used as a
+measure of the strength of the connection between neurons. Considering each
+time point of the pre-processed signals as an independent measurement
+of $p$ random variables, one for each of the $p$ neurons,
+the partial correlation coefficient $p_{i,j}$ between neurons $i$ and $j$ is
+defined by:
+\begin{equation}
+p_{i,j} =
+-\frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii} \Sigma^{-1}_{jj}}}, \label{eq:inverse}
+\end{equation}
+where $\Sigma^{-1}$, known as the precision or concentration matrix, is the
+inverse of the covariance matrix $\Sigma$ of the data. The computation of all
+$p_{i,j}$ coefficients thus requires the estimation of the covariance matrix
+$\Sigma$ and then computing its inverse. Given that typically we have more
+samples (i.e., time points) than neurons, the covariance matrix can be inverted
+in a straightforward way. We nevertheless obtained some improvement by
+replacing the exact inverse with an approximation using only the $M$ first
+principal components, with $M=0.8p$ \citep{bishop2006pattern}.
+
+\paragraph{Averaging.}
+The performance of our method is sensitive to the values of the pre-processing
+parameters: the parameter $\tau$ of the hard-threshold filter $h$ (see Equation
+\ref{eqn:hfilter}), and the choice of the low-pass filter (among $\{f_1,
+f_2, f_3, f_4\}$). To improve robustness, we average partial correlation
+statistics obtained for all pairs $(\tau,\mbox{low-pass filter}) \in
+\{0.100,0.101,\ldots,0.209\}\times \{f_1, f_2, f_3, f_4\}$. In this averaging,
+functions $f_1$, $f_2$, $f_3$, and $f_4$ were given weights respectively equal
+to $0.383$, $0.345$, $0.004$, and $0.268$.
+
+\paragraph{Edge orientation.}
+
+Partial correlation is a symmetric measure that can not be used to predict edge
+orientation. A post-processing heuristic was proposed to derive an asymmetric
+association score from the partial correlation coefficient. This heuristic is
+based on the observation that if there is directed edges from $i$ to $j$ then
+the activation of $i$ should be followed by the activation of $j$ after a
+slight delay. For every pairs $(i,j)$, we computed the following term:
 \begin{align}
- w(x^{t}_i) &= (x^{t}_i + 1 )^{1 + \frac{1}{\sum_{j} x^{t}_j}}, \label{eq:magnify-filter}
+s_{i,j} = \sum_{t=1}^{T - 1} \mathbb{1}((x_j^{t+1} - x_i^t) \in \left[\phi_1, \phi_2\right])
 \end{align}
-whose effect is to magnify the importance of spikes that occur in cases of low
-global activity (measured by $\sum_j x^t_j$).
-
-Under the assumption that fluorescence level neuron are jointly Gaussian,
-partial correlation thus measures conditional dependencies between
-variables ; therefore it should naturally only detect direct associations
-between neurons and filter out spurious indirect effects as mentioned before.
-
-Practically speaking, the computation of all $p_{i,j}$ coefficients requires
-the estimation of the covariance matrix $\Sigma$ and then computing its
-inverse. Given that typically we have more samples than neurons, the covariance
-matrix can be inverted in a straightforward way. We nevertheless obtained some
-improvement by replacing the exact inverse with an approximation using only the
-$M$ first principal components \citep{bishop2006pattern} (more details in
-\citep{sutera2014simple}).
-
-\begin{algorithm}[ht]
-\begin{algorithmic}
- \algsetup{linenodelimiter= }
-
-\STATE Here the pseudo-code.
-% \STATE \textbf{Given} the sampled observation of $p$ neurons for $T$ time intervals.\\[2ex]
-
-% \FOR{$(f,\tau) \in (\{f_1, f_2\}, \{\tau_1, \tau_2, \dots \})$}
-
-% \STATE \vspace{1em} \textbf{Phase 1:} Apply the composed function $w \circ h \circ g \circ f$ to each fluorescent signal.
-% \FOR{$x \in \{1,\dots,T\} $}
-% \STATE $\bar{x}^t_i  \leftarrow w \circ h_{\tau} \circ g \circ f (x^t_i)$
-% \ENDFOR\\[2ex]
-
-% \STATE \textbf{Phase 2:} Compute \textit{Partial correlation} coefficient $p_{i,j}$ for each neuron pair $(i,j)$.
-% \FOR{all pair $(i,j)$}
-% \STATE Estimation of the covariance matrix $\Sigma$
-% \STATE Computing $\Sigma^{-1}$, the inverse of $\Sigma$
-% \STATE $p_{i,j} =
-% -\frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii} \Sigma^{-1}_{jj}}}$
-
-% \ENDFOR\\[2ex]
-% \ENDFOR
-
-\end{algorithmic}
-\caption{Inverse covariance pseudo-code \textcolor{red}{TO DO}}
-\label{alg:inverse-covariance-pseudocode}
-\end{algorithm}
-
-% \begin{algorithm}[h]
-%  \KwData{Given the sampled observation $\{ x^t_i \in \mathbb{R} | i \in V, t = 1, \dots, T \}$ of $p$ neurons for T time intervals}
-%  % \KwResult{how to write algorithm with \LaTeX2e }
-
-%  \textbf{Phase 1:} Apply the composed function $w \circ h \circ g \circ f$ to each fluorescent signal.\;\;
-% \ \ For
-
-% {\Indp
-%  \For{$x \in \{1,\dots,T\} $}{
-% 		$\bar{x}^t_i  \leftarrow w \circ h \circ g \circ f (x^t_i)$
-%  }
-%  }
-
-%  \While{not at end of this document}{
-%   read current\;
-%   \eIf{understand}{
-%    go to next section\;
-%    current section becomes this one\;
-%    }{
-%    go back to the beginning of current section\;
-%   }
-%  }
-%  \caption{Inverse covariance pseudo-code}
-%  \label{alg:inverse-covariance-pseudocode}
-% \end{algorithm}
+that could be interpreted as an image of the number of times that neuron $i$
+activates neuron $j$. $\phi_1$ and $\phi_2$ are parameters whose values have
+been chosen equal to $0.2$ and $0.5$, respectively. The
+final association score for an edge from $i$ to $j$ was
+then the following:
+\begin{align}
+q_{i,j} = weight * p_{i,j} + (1-weight) * (s_{i,j}-s_{j,i}),
+\label{eqn:qij}
+\end{align}
+with $p_{i,j}$ the average partial correlation coefficient and the parameter
+$weight$ chosen close to 1 ($weight=0.997$). The second term is expected to be
+greater (resp. lower) than 0 when $i$ more often activates $j$ than the
+opposite and therefore in this case it makes $q_{i,j}$ greater (resp. lower)
+than $q_{j,i}$.
 

### 2014-10-20 crowdsource/article.tex
changes in edge orientation part

@@
 \paragraph{Edge orientation.}
-
 Partial correlation is a symmetric measure that can not be used to predict edge
@@
 \end{align}
-that could be interpreted as an image of the number of times that neuron $i$
-activates neuron $j$. $\phi_1$ and $\phi_2$ are parameters whose values have
-been chosen equal to $0.2$ and $0.5$, respectively. The
+where $\phi_1$ and $\phi_2$ are parameters whose values have been
+optimized through experiments to $0.2$ and $0.5$, respectively. The
 final association score for an edge from $i$ to $j$ was
@@
 with $p_{i,j}$ the average partial correlation coefficient and the parameter
-$weight$ chosen close to 1 ($weight=0.997$). The second term is expected to be
-greater (resp. lower) than 0 when $i$ more often activates $j$ than the
-opposite and therefore in this case it makes $q_{i,j}$ greater (resp. lower)
-than $q_{j,i}$.
-
+$weight$ optimized close to 1 ($weight=0.997$). 
 \newpage

### 2014-10-24 crowdsource/article.tex
Put back Pierre's explanation
Add the description of x^t_i

--- 2014-10-20 crowdsource/article.tex
@@
 fluorescence data. This pre-processing applies successively four
-filtering functions to the original signal:
+filtering functions to the original signal $x^t_i$ of each neuron $i$ where $t$ is the time step:
 \begin{itemize}
@@
 than $q_{j,i}$.
-
 \newpage

### 2014-10-24 crowdsource/article.tex

@@
 \end{align}
-that could be interpreted as an image of the number of times that neuron $i$
-activates neuron $j$. $\phi_1$ and $\phi_2$ are parameters whose values have
-been chosen equal to $0.2$ and $0.5$, respectively. The
+where $\phi_1$ and $\phi_2$ are parameters whose values have
+been optimised (equal to $0.2$ and $0.5$, respectively). The
 final association score for an edge from $i$ to $j$ was
@@
 with $p_{i,j}$ the average partial correlation coefficient and the parameter
-$weight$ chosen close to 1 ($weight=0.997$). The second term is expected to be
+$weight$ optimised close to 1 ($weight=0.997$). The second term is expected to be
 greater (resp. lower) than 0 when $i$ more often activates $j$ than the

### 2014-11-03 crowdsource/code/main.py
Ensure that the directory exists

@@ -93,6 +93,9 @@ if __name__ == "__main__":
 
     # Save data
     if "output_dir" in args:
+        if os.path.exists(args["output_dir"]):
+            os.makedirs(args["output_dir"])
+
         outname = os.path.join(args["output_dir"], job_hash)
 
         # Generate the submission file ##

### 2014-11-03 crowdsource/code/main.py
FIX path func

@@ -111,4 +111,4 @@ if __name__ == "__main__":
 
     # Indicate the job is finished
     print("job_hash %s" % job_hash)
-    sqlite3_dumps({job_hash: "JOB DONE"}, get_sqlite3_path(args["dataset"]))
+    sqlite3_dumps({job_hash: "JOB DONE"}, get_sqlite3_path())

### 2014-11-04 crowdsource/code/main.py
FIX conditinnal directory creation

@@ -93,7 +93,7 @@ if __name__ == "__main__":
 
     # Save data
     if "output_dir" in args:
-        if os.path.exists(args["output_dir"]):
+        if not os.path.exists(args["output_dir"]):
             os.makedirs(args["output_dir"])
 
         outname = os.path.join(args["output_dir"], job_hash)

### 2014-11-06 poster-DYSCO/poster.tex
Poster for DYSCO

--- 2014-09-08 poster/poster.tex
@@
 \title{Simple connectome inference from partial correlation statistics in calcium imaging}
-\author{Antonio Sutera, Arnaud Joly, Vincent François-Lavet, Zixiao Aaron Qiu, Gilles Louppe, Damien Ernst and Pierre Geurts\\[1.5ex]
+\author{Antonio Sutera, Arnaud Joly, Vincent François-Lavet, Zixiao Aaron Qiu, Gilles Louppe, Damien Ernst and Pierre Geurts\\[1ex]
 {\tiny
@@
 %\includegraphics[scale=0.6]{images/twitter.png}~\href{https://twitter.com/glouppe}{@glouppe}
-\includegraphics[scale=0.18]{images/github.png}~Code source available at \url{https://github.com/asutera/kaggle-connectomics}
-}}
+\includegraphics[scale=0.18]{images/github.png}~Code source available at \url{https://github.com/asutera/kaggle-connectomics}\\[1ex] This paper presents research results of the Belgian Network DYSCO (Dynamical Systems, Control, and Optimization), funded by the Interuniversity Attraction Poles Programme initiated by the Belgian Science Policy Office.}}
 
@@
 
-\scalebox{2}{\includegraphics{poster-pics.pdf}}
+\scalebox{2}{\includegraphics{network_poster.pdf}}
 {    \begin{pspicture}(20,20)
 
- 	   \psellipse[fillstyle=solid,linewidth=2pt,linecolor=lightgreen,linestyle=dashed,fillcolor=lightgreen!10](2,3)(1.8,2.8)
- 	   \psellipse[fillstyle=solid,linewidth=2pt,linecolor=lightgreen,linestyle=dashed,fillcolor=lightgreen!10](8.3,3)(1.5,2.8)
+ 	   % \psellipse[fillstyle=solid,linewidth=2pt,linecolor=lightgreen,linestyle=dashed,fillcolor=lightgreen!10](2,3)(1.8,2.8)
+ 	   % \psellipse[fillstyle=solid,linewidth=2pt,linecolor=lightgreen,linestyle=dashed,fillcolor=lightgreen!10](8.3,3)(1.5,2.8)
 
@@
 
+		\rput(4.5,3){{\color{lightblue} \textbf{i}}}
+		\rput(6.2,3){{\color{lightblue}  \textbf{j}}}
+
 		% text
-		\rput(5.35,3.3){$p_{i,j}$}
-		\rput(5.35,2.3){{$_{\textit{partial correlation}}$}}
-		\rput(5.35,1.9){{$_=$}}
-		\rput(5.35,1.5){{$_{\textit{degree of association}}$}}
-		\rput(5.3,1.1){{$_{\textit{between neurons i and j}}$}}
+		% \rput(5.35,3.3){$p_{i,j}$}
+		% \rput(5.35,2.3){{$_{\textit{partial correlation}}$}}
+		% \rput(5.35,1.9){{$_=$}}
+		% \rput(5.35,1.5){{$_{\textit{degree of association}}$}}
+		% \rput(5.3,1.1){{$_{\textit{between neurons i and j}}$}}
 
-		\rput(4.2,5){{\color{lightgreen} \textbf{known}}}
+		% \rput(4.2,5){{\color{lightgreen} \textbf{known}}}
 
-		\rput(6.3,0.6){{\color{lightgreen} \textbf{known}}}
+		% \rput(6.3,0.6){{\color{lightgreen} \textbf{known}}}
 
@@
 
-% \begin{textblock}{1}(0.01,0.99)
-% {\fontsize{12}{10}\textbf{Acknowledgments:}}
-% {\fontsize{8}{10}\textbf{A. Joly and G. Louppe are research fellows of the FNRS, Belgium. A. Sutera is a
-% recipient of an FRIA fellowship of FRS-FNRS, Belgium. This work is supported by
-% PASCAL2 and the IUAP DYSCO, initiated by the Belgian State, Science Policy
-% Office.}}
-% \end{textblock}
-
 \end{frame}

### 2014-11-06 spotlight/slides.tex
Spotlight presentation

--- 2014-09-04 oral/slides.tex
@@
 \documentclass[final]{beamer}
+
+\usepackage[absolute,overlay]{textpos}
 
@@
 
-\usepackage{multirow}
+\title{Simple connectome inference from partial correlation statistics\\in calcium imaging}
+\author{{\footnotesize Antonio Sutera, Arnaud Joly, Vincent François-Lavet, Zixiao Aaron Qiu, Gilles Louppe, Damien Ernst and Pierre Geurts.}}
+\date{}
 
-\title{Simple connectome inference from partial\\[1ex]
-correlation statistics in calcium imaging}
-\author{{\small Antonio Sutera, Arnaud Joly, Vincent François-Lavet, Zixiao Aaron Qiu\\[1ex] Gilles Louppe, Damien Ersnt and Pierre Geurts.}}
-\date{}
+\addtobeamertemplate{navigation symbols}{}{%
+    \usebeamerfont{footline}%
+    \usebeamercolor[fg]{footline}%
+    \hspace{1em}%
+    \insertframenumber/\inserttotalframenumber
+}
 
@@
 
-\vspace{-0cm}
-
-	\begin{center}
-	\includegraphics[width=7cm]{images/network.png}
-	\end{center}
-
-\vspace{-9.5cm}
   \begin{beamercolorbox}[wd=\paperwidth, ignorebg]{headline}
@@
 
-      \usebeamercolor{title in headline}{\color{fg}\Large{\textbf{\inserttitle}}\\[2ex]}
-      \usebeamercolor{author in headline}{\color{fg}\small{\insertauthor}\\[1ex]}
+      \usebeamercolor{title in headline}{\color{fg}\large{\textbf{\inserttitle}}\\[1ex]}
+      \usebeamercolor{author in headline}{\color{fg}\footnotesize{\insertauthor}\\[1ex]}
     \end{center}
@@
 
-\end{frame}
-
-%% Slide 2 ==================================================================
-
-\begin{frame}
-
-\frametitle{Introduction}
-
-From {\color{i6blue} time-series of the neuron activity}, the \textbf{goal} is to {\color{red} \textbf{infer} the directed connections between neurons}.
-
-\end{frame}
-
-%% Slide 3 ==================================================================
-
-\begin{frame}
-
-\frametitle{Introduction}
-
-But this problem is \textbf{difficult} because of...
-
-\begin{tabular*}{\textwidth}{l r} \hline
-&\multirow{3}{*}{\includegraphics[width=2cm]{images/miss.png} \includegraphics[width=2cm]{images/hidden.png}}\\
-
-{\color{red} \textbf{masking} effects}
-& \\ 
-& \\
-\end{tabular}
-
-% \begin{itemize}
-% \item {\color{red} \textbf{masking} effects},
-% \includegraphics[width=2cm]{images/miss.png} \includegraphics[width=2cm]{images/hidden.png}
-% \item {\color{red} \textbf{low} sampling rate},
-% \includegraphics[width=4cm]{images/slowsamplingrate.png}
-% \item {\color{red} \textbf{slow} decay} of fluorescence.
-% \includegraphics[width=4cm]{images/original_curve_gr}
-% \end{itemize}
-
-\end{frame}
-
-%% Slide 4 ==================================================================
-
-\begin{frame}
-
-\frametitle{Framework of our solution  \hspace{15pt} {\small Table of contents} }
-
-{\color{red} How-to}:
-\begin{enumerate}
-\item \textbf{Deal} with calcium fluorescence signals: {\color{i6blue} signal processing}.
-\item \textbf{Find} the network: the {\color{i6blue} {inference} method}.
-\item \textbf{Improve} the method: our {\color{i6blue} {tricks}}.
-\end{enumerate}\vskip5pt
-
-{\color{red} One step further}:
-\begin{itemize}
-\item Improvement of each stage of our solution.
-\item Comparison with other methods.
-\end{itemize}\vskip5pt
-
-{\color{red} Even further}: 
-\begin{itemize}
-\item The ``full method'' in a nutshell.
-\end{itemize}
-
-\end{frame}
-
-%% Slide 5 ==================================================================
-
-\begin{frame}
-
-\frametitle{Signal processing}
-
-\begin{overprint}
-\onslide<1> 
-a-b
-
-\onslide<2>
-a-b-c
-
-\onslide<3>
-a-b-c-d
-
-\onslide<4>
-a-b-c-d-e
-\end{overprint}
-
-\end{frame}
-
-%% Slide 6 ==================================================================
-
-\begin{frame}
-
-\frametitle{Connectome \textbf{inference} from {\color{red} partial correlation statistics}}
+\textbf{{\color{i6blue}Goal:}} From time-series of the neuron activity, infer the directed connections between neurons.\\[1.5ex]
+%This is {\color{red} difficult} task.\\[2ex]
+\textbf{{\color{red}But:}} This is not that easy because of the nature of the data.\\[1.5ex]
 
 \begin{columns}
-\begin{column}{0.5\linewidth}
-diag
+\begin{column}{0.55\linewidth}
+\includegraphics[width=6cm]{images/network.pdf}
 \end{column}
@@
 
-\begin{itemize}
-\item[{\color{green} \cmark}] Only direct associations
-\item[{\color{green} \cmark}] Filter out spurious indirect effects
-\item[{\color{green} \cmark}] Symmetric \\[5ex]
-\item[{\color{red} \xmark}] Edge orientation
-\item[{\color{red} \xmark}] Sensitive to the value of parameters in the filtering process
-\end{itemize}
+\textbf{{\color{i6blue} Steps of our solution:}}
+\begin{enumerate}[1.]
+\item Signal processing\\{\scriptsize(deal with calcium fluorescent signals)}
+\item Averaged partial correlation statistics\\{\scriptsize(find the undirected network)}
+\item Prediction of edge orientation
+\end{enumerate}
 
 \end{column}
-
 \end{columns}
@@
 
-%% Slide 7 ==================================================================
-
-\begin{frame}
-\frametitle{Improvements}
-
-\begin{itemize}
-\item \textcolor{red}{\textbf{Approximation}} for partial correlation statistics using only the \textcolor{i6blue}{800 first principal components}. \\[5ex]
-\item {\color{red} \textbf{Averaged} partial correlation statistics} over various values of the parameters
-	\begin{itemize}
-		\item[{\color{green} \cmark}] Improve robustness (over all networks)
-		\item[{\color{green} \cmark}] Reduce variance of its prediction
-		\item[{\color{green} \cmark}] Decrease the sensitivity to the filtering process
-	\end{itemize}
-\end{itemize}
-
-\end{frame}
-
-%% Slide 8 ==================================================================
-
-\begin{frame}
-\frametitle{Each stage of our solution is good!}
-
-\begin{table}[t]
-\caption{Performance on \textit{normal-1,2,3,4} with partial correlation and different filtering functions.}
-\label{tab:comparison}
-\centering
-\tiny
-\begin{tabular}{| l | c c c c | c c c c |}
-\hline
-& \multicolumn{4}{c|}{AUROC} & \multicolumn{4}{c|}{AUPRC} \\
-\textit{Method} $\backslash$ \textit{normal-} & \textit{1} & \textit{2} & \textit{3} & \textit{4} & \textit{1} & \textit{2} & \textit{3} & \textit{4} \\
-\hline
-\hline
-No  filtering       					& 0.777 & 0.767 & 0.772 & 0.774 & 0.070 & 0.064 & 0.068 & 0.072\\
-$ h \circ g \circ f_1$                  & 0.923 & 0.925 & 0.923 & 0.922 & 0.311 & 0.315 & 0.313 & 0.304\\
-$ w \circ h \circ g \circ f_1$          & 0.931 & 0.929 & 0.928 & 0.926 & 0.326 & 0.323 & 0.319 & 0.303\\
-+ PCA         							& 0.932 & 0.930 & 0.928 & 0.926 & 0.355 & 0.353 & 0.350 & 0.333\\
-Averaging           					& 0.937 & 0.935 & 0.935 & 0.931 & 0.391 &  0.390 &  0.385 & 0.375\\
-Full method           					& \textbf{0.943} & \textbf{0.942} & \textbf{0.942} & \textbf{0.939} & \textbf{0.403} & \textbf{0.404} & \textbf{0.398} & \textbf{0.388}\\
-\hline
-\end{tabular}
-\end{table}
-
-\end{frame}
-
-%% Slide 9 ==================================================================
-
-\begin{frame}
-\frametitle{Comparison with other methods}
-
-\begin{table}[t]
-
-\caption{Performance on \textit{normal-1,2,3,4} with different methods.}
-\label{tab:comparison}
-\centering
-\tiny
-\begin{tabular}{| l | c c c c | c c c c |}
-\hline
-& \multicolumn{4}{c|}{AUROC} & \multicolumn{4}{c|}{AUPRC} \\
-\textit{Method} $\backslash$ \textit{normal-} & \textit{1} & \textit{2} & \textit{3} & \textit{4} & \textit{1} & \textit{2} & \textit{3} & \textit{4} \\
-\hline
-\hline
-Averaging           					& 0.937 & 0.935 & 0.935 & 0.931 & 0.391 &  0.390 &  0.385 & 0.375\\
-Full method           					& \textbf{0.943} & \textbf{0.942} & \textbf{0.942} & \textbf{0.939} & \textbf{0.403} & \textbf{0.404} & \textbf{0.398} & \textbf{0.388}\\
-\hline
-PC & 0.886 & 0.884 & 0.891 &  0.877 & 0.153 & 0.145 & 0.170 & 0.132\\
-GTE & 0.890 & 0.893 & 0.894 & 0.873 & 0.171 & 0.174 & 0.197 & 0.142\\
-GENIE3 & 0.892 & 0.891 & 0.887 & 0.887 & 0.232 & 0.221 & 0.237 & 0.215 \\
-\hline
-\end{tabular}
-\end{table}
-
-\end{frame}
-
-%% Slide 10 =================================================================
-
-\begin{frame}
-\frametitle{An optimized version to win the challenge: ``Full method''}
-
-\begin{itemize}
-\item A \textbf{tuned} signal processing,
-\item \textbf{Weighted} average of partial correlation statistics,
-\item \textbf{Prediction} of edge orientation.
-\end{itemize}
-
-\end{frame}
-
-%% Slide 11 =================================================================
-
-\begin{frame}
-\frametitle{For every details of our method...}
-
-\textbf{The description of the method:}
-\begin{itemize}
-\item[] Sutera, A., Joly, A., François-Lavet, V., Qiu, Z. A., Louppe, G., Ernst, D., \& Geurts, P. (2014). Simple connectome inference from partial correlation statistics in calcium imaging.\\[7ex]
-\end{itemize}
-
-\textbf{Code available at:}
-\begin{itemize}
-\item[] \url{https://github.com/asutera/kaggle-connectomics}
-\end{itemize}
-
-\end{frame}
-
 \end{document}

### 2014-11-06 oral/slides.tex
several changes

@@
 correlation statistics in calcium imaging}
-\author{{\small Antonio Sutera, Arnaud Joly, Vincent François-Lavet, Zixiao Aaron Qiu\\[1ex] Gilles Louppe, Damien Ernst and Pierre Geurts.}}
+\author{{\small Antonio Sutera, Arnaud Joly, Vincent François-Lavet, Zixiao Aaron Qiu\\[1ex] Gilles Louppe, Damien Ernst and Pierre Geurts (aka The AAAGV Team).}}
 \date{}
@@
 
-From {\color{i6blue} time-series of the neuron activity}, the \textbf{goal} is to {\color{red} \textbf{infer} the directed connections between neurons}.
+\vspace{2cm}
 
-\note{
+From {\color{i6blue} time-series of the neuron activity}, the \textbf{goal} is to {\color{red} \textbf{infer} the directed connections between neurons}.\\[5ex]
 
-	Before the main part of this presentation, I would like to mention that we are not biologist and we are not expert of the connectome inference.
-We see the challenge as an inference problem and maybe in a naive point of view for some points.
-
-}
+\begin{center}
+\includegraphics[width=7cm]{images/network_2.pdf}
+\end{center}
 
@@
 \item[{\color{green} \cmark}] Filter out spurious indirect effects
-\item[{\color{green} \cmark}] Symmetric 
+% \item[{\color{green} \cmark}] Symmetric 
 \item[{\color{green} \cmark}] Easy to compute \\ (with lots of data) \\[2ex]
@@
 }
-\includegraphics[width=8cm]{images/data_stage.png}
+\includegraphics[width=8.5cm]{images/data_stage.png}
 \end{center}
@@
 }
-\includegraphics[width=9cm]{images/data_method.png}
+\includegraphics[width=10cm]{images/data_method.png}
 \end{center}

### 2014-11-06 poster/method_image.tex
several changes

\documentclass[12pt]{article}
\parindent=0pt
\usepackage{animate}

\usepackage{pst-plot,pst-xkey}
\SpecialCoor
\makeatletter
\pst@addfams{demo}%     add family demo to the list
\define@boolkey[psset]{demo}[Pst@]{showcircles}[true]{}% prefix is \Pst@
\define@boolkey[psset]{demo}[Pst@]{hypocycloid}[true]{}%  "    "   "
\define@key[psset]{demo}{nAngle}{\pst@getint{#1}\psk@nAngle}
\define@key[psset]{demo}{dAngle}{\pst@getangle{#1}\psk@dAngle}
%
\psset[demo]{showcircles=false,nAngle=6,dAngle=60,hypocycloid=false}
\newpsstyle{cycloid}{linecolor=black,linewidth=0.2\pslinewidth}
%
\def\psCycloid{\pst@object{psCycloid}}
% A pstricks object reads a star and the optional arguments
% and then cintinues with <name>@i
% we use (#1), but will test, if we have another (#2,#3),
% otherwise we use the default (0,720)
\def\psCycloid@i(#1){%
  \@ifnextchar({\psCycloid@ii(#1)}{\psCycloid@ii(#1)(0,360)}}
% (#1)   : origin
% (#2,#3): start and end angle for the parametrix plot
% #4     : radius R of the big circle 
% #5     : radius r of the small circle
% #6     : radius A of the rotatetd point 
\def\psCycloid@ii(#1)(#2,#3)#4#5#6{%
  \pst@killglue                 % no whitespace
  \begingroup%                  % hold all local
  \addbefore@par{plotpoints=500}% can be overwritten by a following user set
  \use@par%                     % set the optional arguments
  \pst@getlength{#4}\pst@tempB% get the radius in pt (screen coors)
  \pst@getlength{#5}\pst@tempC% get the 2nd radius in pt
  \pst@getlength{#6}\pst@tempD% get the distance for a in pt
  \pstVerb{                     % define it only once (in user coors!!!)
    /R \pst@tempB \pst@number\psunit div def 
    /r \pst@tempC \pst@number\psunit div def 
    /A \pst@tempD \pst@number\psunit div def
    /Rr R r \ifPst@hypocycloid sub \else add \fi def        % R +- r
    /RDivr R r div def          % R/r
    /RrDivr RDivr 1 \ifPst@hypocycloid sub \else add \fi def % (R+-r)/r
  }%
  \if@star\psset{fillstyle=eofill,fillcolor=\pslinecolor}\fi%
  \parametricplot{#2}{#3}{%
      Rr t cos mul t RrDivr mul cos A mul sub  % x(t)
      Rr t sin mul t RrDivr mul sin A mul 
      \ifPst@hypocycloid add \else sub \fi }% y(t)
  \ifPst@showcircles%
    \psset{style=cycloid}%
    \pscircle(#1){#4}%
    \multido{\rA=0.0+\psk@dAngle}{\psk@nAngle}{%
     \rput(!#4 #5 \ifPst@hypocycloid sub \else add \fi dup 
       \rA\space cos mul exch \rA\space sin mul){% user coors!!
        \pscircle{#5}\psline[linecolor=blue]{*-o}(!%
          \rA\space RrDivr mul dup % the angle
          cos A mul neg 
          exch sin A mul \ifPst@hypocycloid\else neg \fi)%
    }}%
    \psarc[arrowscale=2]{->}(#1){0.5cm}{0}{270}
  \fi%
  \endgroup%                    end of local macro
  \ignorespacesafterend%                no whitespace at the end
} 
\makeatother
\pagestyle{empty}
\parindent=0pt

\def\oneShot#1{%
\begin{pspicture}(-3,-3)(3,3)
  \psCycloid[linecolor=red,linewidth=1.5pt,showcircles,
     dAngle=10,nAngle=1][#1](0,0){2}{0.5}{0.6}
\end{pspicture}}

\begin{document}

    \begin{pspicture}(14,11)
    % Grid
    %\psgrid[subgriddiv=1,griddots=10,gridlabels=7pt]
    % Calcul
    \rput[l](9,9.5){\color{gray}{$i(t) = 0.97$}}
    \rput[l](9,8.5){\color{gray}{$i(t_L) = 0.65$}}
    \rput[l](9,7.5){\color{gray}{$i(t_R) = 0.81$}}
    \rput[l](9,6.5){\color{gray}{$\Delta i(t) = i(t) - \frac{12}{20} i(t_L) - \frac{8}{20} i(t_R)$}}
    \rput[l](10.55,5.5){\color{gray}{$= 0.25$}}
    % Parent node
        % Arrows
        \psline[linewidth=2pt,linecolor=blue]{->}(4.5,10.5)(5,10)
        \psline[linewidth=2pt,linecolor=blue]{->}(5,9)(3,7)
        \psline[linewidth=2pt,linecolor=blue]{->}(5,9)(7,7)
        % Node
        \pscircle[fillstyle=solid,fillcolor=white,linewidth=2pt,linecolor=blue](5,9){1}
        % Samples
        \psframe[fillstyle=solid,fillcolor=red,linecolor=red](4.3,9.35)(4.5,9.55)
        \psframe[fillstyle=solid,fillcolor=blue,linecolor=blue](4.6,9.35)(4.8,9.55)
        \psframe[fillstyle=solid,fillcolor=blue,linecolor=blue](4.9,9.35)(5.1,9.55)
        \psframe[fillstyle=solid,fillcolor=blue,linecolor=blue](5.2,9.35)(5.4,9.55)
        \psframe[fillstyle=solid,fillcolor=blue,linecolor=blue](5.5,9.35)(5.7,9.55)
        \psframe[fillstyle=solid,fillcolor=blue,linecolor=blue](4.3,9.05)(4.5,9.25)
        \psframe[fillstyle=solid,fillcolor=red,linecolor=red](4.6,9.05)(4.8,9.25)
        \psframe[fillstyle=solid,fillcolor=red,linecolor=red](4.9,9.05)(5.1,9.25)
        \psframe[fillstyle=solid,fillcolor=blue,linecolor=blue](5.2,9.05)(5.4,9.25)
        \psframe[fillstyle=solid,fillcolor=blue,linecolor=blue](5.5,9.05)(5.7,9.25)
        \psframe[fillstyle=solid,fillcolor=blue,linecolor=blue](4.3,8.75)(4.5,8.95)
        \psframe[fillstyle=solid,fillcolor=red,linecolor=red](4.6,8.75)(4.8,8.95)
        \psframe[fillstyle=solid,fillcolor=blue,linecolor=blue](4.9,8.75)(5.1,8.95)
        \psframe[fillstyle=solid,fillcolor=blue,linecolor=blue](5.2,8.75)(5.4,8.95)
        \psframe[fillstyle=solid,fillcolor=red,linecolor=red](5.5,8.75)(5.7,8.95)
        \psframe[fillstyle=solid,fillcolor=blue,linecolor=blue](4.3,8.45)(4.5,8.65)
        \psframe[fillstyle=solid,fillcolor=blue,linecolor=blue](4.6,8.45)(4.8,8.65)
        \psframe[fillstyle=solid,fillcolor=red,linecolor=red](4.9,8.45)(5.1,8.65)
        \psframe[fillstyle=solid,fillcolor=red,linecolor=red](5.2,8.45)(5.4,8.65)
        \psframe[fillstyle=solid,fillcolor=red,linecolor=red](5.5,8.45)(5.7,8.65)
        % Text
        \rput(6,10){$t$}
    % Left node
        % Arrows
        %\psline[linewidth=2pt,linecolor=gray](3,6)(2,5)
        %\psline[linewidth=2pt,linecolor=gray](3,6)(4,5)
        % Node
        \psline[linewidth=2pt,linecolor=lightgray]{-}(3,6)(2,5)
        \psline[linewidth=2pt,linecolor=lightgray]{-}(3,6)(4,5)
        \pscircle[fillstyle=solid,fillcolor=white,linewidth=2pt,linecolor=lightgray](3,6){1}
        % Samples
        \psframe[fillstyle=solid,fillcolor=blue,linecolor=blue](2.3,6.35)(2.5,6.55)
        \psframe[fillstyle=solid,fillcolor=blue,linecolor=blue](2.6,6.35)(2.8,6.55)
        \psframe[fillstyle=solid,fillcolor=blue,linecolor=blue](2.9,6.35)(3.1,6.55)
        \psframe[fillstyle=solid,fillcolor=blue,linecolor=blue](3.2,6.35)(3.4,6.55)
        \psframe[fillstyle=solid,fillcolor=blue,linecolor=blue](3.5,6.35)(3.7,6.55)
        \psframe[fillstyle=solid,fillcolor=blue,linecolor=blue](2.3,6.05)(2.5,6.25)
        \psframe[fillstyle=solid,fillcolor=blue,linecolor=blue](2.6,6.05)(2.8,6.25)
        \psframe[fillstyle=solid,fillcolor=red,linecolor=red](2.9,6.05)(3.1,6.25)
        \psframe[fillstyle=solid,fillcolor=blue,linecolor=blue](3.2,6.05)(3.4,6.25)
        \psframe[fillstyle=solid,fillcolor=blue,linecolor=blue](3.5,6.05)(3.7,6.25)
        \psframe[fillstyle=solid,fillcolor=blue,linecolor=blue](2.3,5.75)(2.5,5.95)
        \psframe[fillstyle=solid,fillcolor=red,linecolor=red](2.6,5.75)(2.8,5.95)
        % Text
        \rput(4,7){$t_L$}
        \rput(2.5,8){$X_m = 0$}
    % Right node
        % Arrows
        %\psline[linewidth=2pt,linecolor=gray](7,6)(6,5)
        %\psline[linewidth=2pt,linecolor=gray](7,6)(8,5)
        % Node
        \psline[linewidth=2pt,linecolor=lightgray]{-}(7,6)(6,5)
        \psline[linewidth=2pt,linecolor=lightgray]{-}(7,6)(8,5)
        \pscircle[fillstyle=solid,fillcolor=white,linewidth=2pt,linecolor=lightgray](7,6){1}
        % Samples
        \psframe[fillstyle=solid,fillcolor=red,linecolor=red](6.3,6.35)(6.5,6.55)
        \psframe[fillstyle=solid,fillcolor=red,linecolor=red](6.6,6.35)(6.8,6.55)
        \psframe[fillstyle=solid,fillcolor=blue,linecolor=blue](6.9,6.35)(7.1,6.55)
        \psframe[fillstyle=solid,fillcolor=red,linecolor=red](7.2,6.35)(7.4,6.55)
        \psframe[fillstyle=solid,fillcolor=blue,linecolor=blue](7.5,6.35)(7.7,6.55)
        \psframe[fillstyle=solid,fillcolor=red,linecolor=red](6.3,6.05)(6.5,6.25)
        \psframe[fillstyle=solid,fillcolor=red,linecolor=red](6.6,6.05)(6.8,6.25)
        \psframe[fillstyle=solid,fillcolor=red,linecolor=red](6.9,6.05)(7.1,6.25)
        % Text
        \rput(8,7){$t_R$}
        \rput(7.5,8){$X_m = 1$}
    \end{pspicture}

\end{document}

### 2014-11-06 crowdsource/code/main.py
add 'kill' arg to main.py

@@ -19,6 +19,7 @@ import numpy as np
 
 from PCA import make_simple_inference, make_tuned_inference
 from directivity import make_prediction_directivity
+from hidden import kill
 
 # Cache accelerator may be removed to save disk space
 from sklearn.externals.joblib import Memory
@@ -60,7 +61,9 @@ def parse_arguments(args=None):
     parser.add_argument('-d', '--directivity', type=int, required=False,
                         default=0, choices=[0, 1],
                         help='Consider information about directivity?')
-
+    parser.add_argument('-k', '--killing', type=int, required=False,
+                        default=0, choices=[0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10],
+                        help='Should we "kill" some neurons?')
     return vars(parser.parse_args(args))
 
 if __name__ == "__main__":
@@ -76,6 +79,10 @@ if __name__ == "__main__":
     X = np.loadtxt(args["fluorescence"], delimiter=",")
     X = np.asfortranarray(X, dtype=np.float32)
     # pos = np.loadtxt(args["position"], delimiter=",")
+    if name in ["normal-3", "normal-4"]:
+        var_kill = args["killing"]
+        if var_kill != 0:
+            X = kill(X, name, var_kill)
 
     # Producing the prediction matrix
     if args["method"] == 'tuned':

### 2014-11-06 crowdsource/code/hidden.py
add a function to kill neurons

@@ -1,0 +1,40 @@
+#!/usr/bin/env python
+
+# Authors: Aaron Qiu <zqiu@ulg.ac.be>,
+#          Antonio Sutera <a.sutera@ulg.ac.be>,
+#          Arnaud Joly <a.joly@ulg.ac.be>,
+#          Gilles Louppe <g.louppe@ulg.ac.be>,
+#          Vincent Francois <v.francois@ulg.ac.be>
+#
+# License: BSD 3 clause
+
+import numpy as np
+import os
+
+WORKING_DIR = os.path.join(os.environ["HOME"],
+                           "scikit_learn_data/connectomics")
+
+
+def kill(X, name, var):
+
+    n_samples, n_nodes = X.shape
+
+    # load name_kill_var
+    killing_file = WORKING_DIR + "{0}_kill/{0}_kill_{1}.txt".format(name, var)
+    kill = np.loadtxt(killing_file, dtype=np.int)
+
+    # make a mask
+    alive = np.ones((n_nodes,), dtype=bool)
+    alive[kill] = False
+
+    # kill neurons
+    X_kill = X[:, alive]
+
+    # Checks
+    n_samples_kill, n_nodes_kill = X_kill.shape
+    if (n_nodes - len(kill)) != n_nodes_kill:
+        raise ValueError("Kill nodes should match.")
+    if n_samples != n_samples_kill:
+        raise ValueError("Number of samples should be the same")
+
+    return X_kill

### 2014-11-07 crowdsource/code/main.py
Remove caching to gain memory

@@ -22,14 +22,10 @@ from directivity import make_prediction_directivity
 from hidden import kill
 
 # Cache accelerator may be removed to save disk space
-from sklearn.externals.joblib import Memory
 from clusterlib.storage import sqlite3_dumps
 
 WORKING_DIR = os.path.join(os.environ["HOME"],
                            "scikit_learn_data/connectomics")
-
-memory = Memory(cachedir=os.path.join(WORKING_DIR, "cachedir"), verbose=0)
-np.loadtxt = memory.cache(np.loadtxt)
 
 
 def get_sqlite3_path():

### 2014-11-07 crowdsource/code/main.py
Preserve hash for previous experiment

@@ -58,7 +58,7 @@ def parse_arguments(args=None):
                         default=0, choices=[0, 1],
                         help='Consider information about directivity?')
     parser.add_argument('-k', '--killing', type=int, required=False,
-                        default=0, choices=[0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10],
+                        choices=[1, 2, 3, 4, 5, 6, 7, 8, 9, 10],
                         help='Should we "kill" some neurons?')
     return vars(parser.parse_args(args))
 
@@ -75,10 +75,10 @@ if __name__ == "__main__":
     X = np.loadtxt(args["fluorescence"], delimiter=",")
     X = np.asfortranarray(X, dtype=np.float32)
     # pos = np.loadtxt(args["position"], delimiter=",")
-    if name in ["normal-3", "normal-4"]:
-        var_kill = args["killing"]
-        if var_kill != 0:
-            X = kill(X, name, var_kill)
+
+    # Should we remove some neurons?
+    if "killing" in args and name in ["normal-3", "normal-4"]:
+        X = kill(X, name, args["killing"])
 
     # Producing the prediction matrix
     if args["method"] == 'tuned':

### 2014-11-07 crowdsource/code/launcher.py
Update launcher for killing

@@ -28,13 +28,28 @@ ALL_NETWORKS = [x.split("_", 1)[1] if x.startswith("fluorescence_") else x
                 for x in ALL_FLUORESCENCE]
 ALL_NETWORKS = [os.path.basename(os.path.splitext(x)[0]) for x in ALL_NETWORKS]
 
-PARAMETER_GRID = ParameterGrid({
+
+NORMAL = [{
     "output_dir": [os.path.join(WORKING_DIR, "submission")],
     "network": [network],
     "fluorescence": [fluorescence],
     "method": ["simple", "tuned"],
     "directivity": [0, 1],
-} for fluorescence, network in zip(ALL_FLUORESCENCE, ALL_NETWORKS))
+} for fluorescence, network in zip(ALL_FLUORESCENCE, ALL_NETWORKS)]
+
+HIDDEN_NEURON = [{
+    "output_dir": [os.path.join(WORKING_DIR, "submission")],
+    "network": [network],
+    "fluorescence": [fluorescence],
+    "method": ["simple", "tuned"],
+    "directivity": [0, 1],
+    "killing": range(1, 11),
+}
+for fluorescence, network in zip(ALL_FLUORESCENCE, ALL_NETWORKS)
+if network in ("fluorescence_normal-3", "fluorescence_normal-4")
+]
+
+PARAMETER_GRID = ParameterGrid(NORMAL)
 
 TIME = dict()
 MEMORY = dict()

### 2014-11-07 crowdsource/code/main.py

@@ -77,8 +77,12 @@ if __name__ == "__main__":
     # pos = np.loadtxt(args["position"], delimiter=",")
 
     # Should we remove some neurons?
-    if "killing" in args and name in ["normal-3", "normal-4"]:
-        X = kill(X, name, args["killing"])
+    if "killing" in args:
+        if args["network"] in ["fluorescence_normal-3",
+                               "fluorescence_normal-4"]:
+            X = kill(X, args["network"], args["killing"])
+        else:
+            raise ValueError("No killing specified for %s" % args["network"])
 
     # Producing the prediction matrix
     if args["method"] == 'tuned':

### 2014-11-07 crowdsource/code/main.py
Update hash

@@ -34,8 +34,11 @@ def get_sqlite3_path():
 
 def make_hash(args):
     """Generate a unique hash for the experience"""
-    return "%(network)s-m=%(method)s-d=%(directivity)s" % args
+    if "killing" in args:
+        return "%(network)s-m=%(method)s-d=%(directivity)s-k%(killing)s=" % args
 
+    else:
+        return "%(network)s-m=%(method)s-d=%(directivity)s" % args
 
 def parse_arguments(args=None):
     parser = argparse.ArgumentParser(argument_default=argparse.SUPPRESS)

### 2014-11-07 crowdsource/code/main.py
FIX hash issue

@@ -42,9 +42,6 @@ def make_hash(args):
 
 def parse_arguments(args=None):
     parser = argparse.ArgumentParser(argument_default=argparse.SUPPRESS)
-
-    parser = argparse.ArgumentParser(description='Perform Connectomics '
-                                                 'modelling')
     parser.add_argument('-f', '--fluorescence', type=str, required=True,
                         help='Path to the fluorescence file')
     # parser.add_argument('-p', '--position', type=str, required=False,

### 2014-11-07 crowdsource/code/launcher.py
Add experiment with hiddens

@@ -49,7 +49,7 @@ for fluorescence, network in zip(ALL_FLUORESCENCE, ALL_NETWORKS)
 if network in ("fluorescence_normal-3", "fluorescence_normal-4")
 ]
 
-PARAMETER_GRID = ParameterGrid(NORMAL)
+PARAMETER_GRID = ParameterGrid(NORMAL + HIDDEN_NEURON)
 
 TIME = dict()
 MEMORY = dict()

### 2014-11-07 crowdsource/code/main.py
Fix typo

@@ -35,7 +35,7 @@ def get_sqlite3_path():
 def make_hash(args):
     """Generate a unique hash for the experience"""
     if "killing" in args:
-        return "%(network)s-m=%(method)s-d=%(directivity)s-k%(killing)s=" % args
+        return "%(network)s-m=%(method)s-d=%(directivity)s-k=%(killing)s" % args
 
     else:
         return "%(network)s-m=%(method)s-d=%(directivity)s" % args

### 2014-11-07 crowdsource/code/hidden.py
quick fix for hidden

@@ -19,6 +19,8 @@ def kill(X, name, var):
 
     n_samples, n_nodes = X.shape
 
+    name = name[len("fluorescence_"):]
+
     # load name_kill_var
     killing_file = WORKING_DIR + "{0}_kill/{0}_kill_{1}.txt".format(name, var)
     kill = np.loadtxt(killing_file, dtype=np.int)

### 2014-11-07 spotlight/spotlight.tex
spotlight final version

--- 2014-11-06 spotlight/slides.tex
@@
 
-\textbf{{\color{i6blue}Goal:}} From time-series of the neuron activity, infer the directed connections between neurons.\\[1.5ex]
+\textbf{{\color{i6blue}Goal:}} From time-series of the neuron activity, \textbf{infer} the directed \textbf{connections between neurons}.\\[1ex]
 %This is {\color{red} difficult} task.\\[2ex]
-\textbf{{\color{red}But:}} This is not that easy because of the nature of the data.\\[1.5ex]
+\textbf{{\color{i6blue}Results:}} Our method was the \textbf{best} performer in the recent \textit{Neural Connectomics Challenge}.\\[1ex]
 
@@
 
-\textbf{{\color{i6blue} Steps of our solution:}}
-\begin{enumerate}[1.]
+\textbf{{\color{green} Steps of our solution:}}
+\begin{enumerate}[{\color{i6blue} 1.}]
 \item Signal processing\\{\scriptsize(deal with calcium fluorescent signals)}

### 2014-11-07 crowdsource/code/hidden.py
fix path to hidden files

@@ -22,7 +22,8 @@ def kill(X, name, var):
     name = name[len("fluorescence_"):]
 
     # load name_kill_var
-    killing_file = WORKING_DIR + "{0}_kill/{0}_kill_{1}.txt".format(name, var)
+    killing_file = os.path.join(WORKING_DIR,
+                                "{0}_kill/{0}_kill_{1}.txt".format(name, var))
     kill = np.loadtxt(killing_file, dtype=np.int)
 
     # make a mask

### 2014-11-07 crowdsource/code/hidden.py
FIX path

@@ -22,8 +22,8 @@ def kill(X, name, var):
     name = name[len("fluorescence_"):]
 
     # load name_kill_var
-    killing_file = os.path.join(WORKING_DIR,
-                                "{0}_kill/{0}_kill_{1}.txt".format(name, var))
+    killing_file = os.path.join(WORKING_DIR, "datasets", "hidden-neurons"
+                                "{0}_kill_{1}.txt".format(name, var))
     kill = np.loadtxt(killing_file, dtype=np.int)
 
     # make a mask

### 2014-11-07 crowdsource/code/hidden.py
FIX path (2)

@@ -22,7 +22,7 @@ def kill(X, name, var):
     name = name[len("fluorescence_"):]
 
     # load name_kill_var
-    killing_file = os.path.join(WORKING_DIR, "datasets", "hidden-neurons"
+    killing_file = os.path.join(WORKING_DIR, "datasets", "hidden-neurons",s
                                 "{0}_kill_{1}.txt".format(name, var))
     kill = np.loadtxt(killing_file, dtype=np.int)
 

### 2014-11-07 crowdsource/code/hidden.py
FIX path (3)

@@ -22,7 +22,7 @@ def kill(X, name, var):
     name = name[len("fluorescence_"):]
 
     # load name_kill_var
-    killing_file = os.path.join(WORKING_DIR, "datasets", "hidden-neurons",s
+    killing_file = os.path.join(WORKING_DIR, "datasets", "hidden-neurons",
                                 "{0}_kill_{1}.txt".format(name, var))
     kill = np.loadtxt(killing_file, dtype=np.int)
 

### 2014-11-07 crowdsource/code/hidden.py
FIX indexing bug

@@ -28,7 +28,7 @@ def kill(X, name, var):
 
     # make a mask
     alive = np.ones((n_nodes,), dtype=bool)
-    alive[kill] = False
+    alive[kill - 1] = False  # we need to make -1 since it's matlab indexing
 
     # kill neurons
     X_kill = X[:, alive]

### 2014-11-10 crowdsource/code/launcher.py
Increase time for last job

@@ -102,7 +102,7 @@ if __name__ == "__main__":
             cmd = submit(job_command="%s main.py %s"
                                      % (sys.executable, cmd_parameters),
                          job_name=job_hash,
-                         time="48:00:00",
+                         time="60:00:00",
                          memory=20000,
                          log_directory=LOG_DIRECTORY,
                          backend="slurm")

### 2014-11-18 crowdsource/code/hidden.py
FIX network name

@@ -19,7 +19,7 @@ def kill(X, name, var):
 
     n_samples, n_nodes = X.shape
 
-    name = name[len("fluorescence_"):]
+    # name = name[len("fluorescence_"):]
 
     # load name_kill_var
     killing_file = os.path.join(WORKING_DIR, "datasets", "hidden-neurons",

### 2014-11-18 crowdsource/code/launcher.py

@@ -24,9 +24,8 @@ ALL_FLUORESCENCE = [os.path.join(WORKING_DIR, "datasets", x)
                                                      "datasets"))
                     if (x.startswith("fluorescence_"))]
 
-ALL_NETWORKS = [x.split("_", 1)[1] if x.startswith("fluorescence_") else x
+ALL_NETWORKS = [os.path.basename(os.path.splitext(x)[0]).split("_", 1)[1]
                 for x in ALL_FLUORESCENCE]
-ALL_NETWORKS = [os.path.basename(os.path.splitext(x)[0]) for x in ALL_NETWORKS]
 
 
 NORMAL = [{
@@ -46,7 +45,7 @@ HIDDEN_NEURON = [{
     "killing": range(1, 11),
 }
 for fluorescence, network in zip(ALL_FLUORESCENCE, ALL_NETWORKS)
-if network in ("fluorescence_normal-3", "fluorescence_normal-4")
+if network in ("normal-3", "normal-4")
 ]
 
 PARAMETER_GRID = ParameterGrid(NORMAL + HIDDEN_NEURON)

### 2014-11-18 crowdsource/code/main.py

@@ -78,8 +78,8 @@ if __name__ == "__main__":
 
     # Should we remove some neurons?
     if "killing" in args:
-        if args["network"] in ["fluorescence_normal-3",
-                               "fluorescence_normal-4"]:
+        if args["network"] in ["normal-3",
+                               "normal-4"]:
             X = kill(X, args["network"], args["killing"])
         else:
             raise ValueError("No killing specified for %s" % args["network"])
@@ -103,7 +103,7 @@ if __name__ == "__main__":
         if not os.path.exists(args["output_dir"]):
             os.makedirs(args["output_dir"])
 
-        outname = os.path.join(args["output_dir"], job_hash)
+        outname = os.path.join(args["output_dir"], "%s.csv" % job_hash)
 
         # Generate the submission file ##
         with open(outname, 'w') as fname:

### 2014-11-18 crowdsource/code/launcher.py
Reduce time and memory

@@ -101,8 +101,8 @@ if __name__ == "__main__":
             cmd = submit(job_command="%s main.py %s"
                                      % (sys.executable, cmd_parameters),
                          job_name=job_hash,
-                         time="60:00:00",
-                         memory=20000,
+                         time="24:00:00",
+                         memory=12000,
                          log_directory=LOG_DIRECTORY,
                          backend="slurm")
 

### 2014-11-18 crowdsource/code/PCA.py
fix notations

@@ -247,10 +247,10 @@ def make_tuned_inference(X):
             elif filtering == 'f2':
                 y_pred_agg += y_pred * 0.9
                 weight += 0.9
-            elif filtering == 'future':
+            elif filtering == 'f3':
                 y_pred_agg += y_pred * 0.01
                 weight += 0.01
-            elif filtering == 'past':
+            elif filtering == 'f4':
                 y_pred_agg += y_pred * 0.7
                 weight += 0.7
 

### 2014-11-18 article.tex
fix equation (2) and threshold max values

@@
 f_1(x^t_i) &= x^{t-1}_i + x^t_i + x^{t+1}_i, \label{eq:symetric-median} \\
-f_2(x^t_i) &= 0.4 x^{t-3}_i + 0.6 x^{t-2}_i + 0.8 x^{t-1}_i + x_i^t.
+f_2(x^t_i) &= 0.4 x^{t-3}_i + 0.8 x^{t-2}_i + x^{t-1}_i + x_i^t.
 \label{eq:weighted-asymetric-median}
@@
 of the low-pass filter (among $\{f_1, f_2, f_3, f_4\}$).
-As in the simplified method, we have averaged the partial correlation statistics obtained for all the pairs $(\tau,\mbox{low-pass filter}) \in \{0.100,0.101,\ldots,0.209\}\times \{f_1, f_2, f_3, f_4\}$.
+As in the simplified method, we have averaged the partial correlation statistics obtained for all the pairs $(\tau,\mbox{low-pass filter}) \in \{0.100,0.101,\ldots,0.210\}\times \{f_1, f_2, f_3, f_4\}$.
 

### 2015-01-06 abstract-GIGADay2015/article.tex
Long abstract for GIGADay 2015

\documentclass[wcp]{jmlr}

\usepackage{enumerate}
\usepackage{bbold}
\usepackage{booktabs}
\usepackage{natbib}
\usepackage[utf8]{inputenc}
\usepackage[super]{nth}
\setlength{\textfloatsep}{15pt}

\usepackage{algorithm}
\usepackage{algorithmic}

\jmlryear{2014}
\jmlrworkshop{Neural Connectomics Workshop}

\title{Simple connectome inference from partial correlation statistics in calcium imaging}

  \author{\Name{Antonio Sutera},
   \Name{Arnaud Joly},
   \Name{Vincent François-Lavet}, \Email{a.sutera@ulg.ac.be}\\
   \Name{Zixiao Aaron Qiu},
   \Name{Gilles Louppe},
   \Name{Damien Ernst}\and\Name{Pierre Geurts}
    \\
   \addr Department of EE and CS \& GIGA-R, University of Li\`ege, Belgium}

\begin{document}

\section*{Abstract}
The human brain is a complex biological organ made of 100 billions of neurons, each connected to 7000 other neurons on average. Unfortunately, direct observation of the connectome, the wiring diagram of the brain, is not yet technically feasible. Without being perfect, calcium imaging currently allows the real-time and simultaneous observation of neuron activities from thousands of neurons, producing individual time series representing their fluorescence intensity. From these data, the connectome inference problem amounts to retrieving the synaptic connections between neurons on the basis of the fluorescence time series. This problem is however very difficult because of various experimental issues.

In this work, we propose a novel simple yet effective solution to the problem of connectome inference in calcium imaging data. The method consists of two steps. (i) a pre-processing of the raw signals to detect neural peak activities; and (ii) the inference of the network through partial correlation statistics. The pre-processing combines several standard filters to remove the noise introduced at different levels, to account for fluorescence low decay, and to reduce the importance of high global activity in the network. From the filtered signals, the strength of the connection between two neurons is then assessed using partial correlations. With respect to plain correlation, the main advantage of partial correlation for network inference is to only give a high degree of association to directly connected neurons and thus to filter out spurious indirect associations.

This method was applied in the context of the recent Connectomics challenge (\url{http://connectomics.chalearn.org}), where we won the first position among more than 100 participating teams. The poster will present various experiments on the challenge data. The goal of these experiments is to provide a separate assessment of each step of the method and to compare it with other inference methods from the literature.

\cite{}
\newpage
\bibliography{references}

\end{document}
